\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Experienced \textbf{Java developer} specializing in creating and maintaining both \textbf{microservices} and \textbf{monolithic systems} with proven expertise in \textbf{Spring Boot} and \textbf{Hibernate} frameworks.}
    \resumeItem{Skilled in \textbf{SQL} and database optimization, adept at designing clean, efficient code while adhering to coding standards and best practices in fast-paced Agile environments.}
    \resumeItem{Proficient in \textbf{RESTful API} development, \textbf{CI/CD automation} using tools like \textbf{Jenkins}, combined with strong troubleshooting and mentoring capabilities to support and enhance production systems.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java (17 \& 21), SQL, PL/SQL, Kotlin \\ 
                \textbf{Frameworks \& Backend:} & Spring Boot, Spring MVC, Hibernate, JPA, JEE, RESTful APIs, Microservices Architecture \\
                \textbf{Databases:} & Oracle Database, PostgreSQL, MySQL, MongoDB, SQL Query Optimization \\
                \textbf{Testing \& Automation:} & JUnit, Mockito, Selenium, Postman, Test Automation, Coding Standards Enforcement \\ 
                \textbf{DevOps \& CI/CD:} & Jenkins, ArgoCD, Git, Docker, Kubernetes, Maven, Gradle \\
                \textbf{Methodologies \& Tools:} & Agile (Scrum/Kanban), Git Version Control, Code Reviews, Application Monitoring \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Developed and maintained microservices and monolithic Java applications using \textbf{Spring Boot} and \textbf{Hibernate}, increasing system reliability by 25\%.}
        \resumeItem{Built scalable \textbf{RESTful APIs} and optimized backend services, enhancing response time by 30\% and improving client satisfaction.}
        \resumeItem{Automated deployment pipelines with \textbf{Jenkins} and \textbf{ArgoCD}, accelerating CI/CD processes and reducing deployment durations by 40\%.}
        \resumeItem{Collaborated with cross-functional teams in Agile ceremonies, contributing to high-quality deliverables and iterative product improvements.}
        \resumeItem{Implemented comprehensive \textbf{unit and integration tests} with \textbf{JUnit} and \textbf{Mockito}, achieving over 95\% code coverage.}
        \resumeItem{Optimized complex \textbf{PostgreSQL} queries leading to a 20\% increase in database operation performance.}
        \resumeItem{Provided mentorship to junior developers on Java best practices, coding standards, and microservices design patterns, improving team productivity.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Engineered core banking modules using \textbf{Java} and \textbf{Spring Boot} within a microservices framework, delivering robust features for financial applications.}
        \resumeItem{Maintained monolithic services and refactored codebases to improve performance and scalability, reducing downtime by 15\%.}
        \resumeItem{Designed and integrated \textbf{RESTful APIs} ensuring smooth communication between services, boosting transaction efficiency by 25\%.}
        \resumeItem{Led automation for deployment processes using \textbf{Jenkins} integrated with \textbf{Git}, cutting deployment time by 30\%.}
        \resumeItem{Implemented SQL performance optimizations and database schema improvements, enhancing data retrieval speed by 20\%.}
        \resumeItem{Participated actively in Agile ceremonies and team code reviews to ensure adherence to coding standards and software quality.}
        \resumeItem{Enhanced production stability by monitoring and supporting live systems during KTLO activities, reducing production incidents by 35\%.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed backend Java modules using \textbf{Spring MVC} supporting supply chain management, reducing order processing latency by 15\%.}
        \resumeItem{Integrated \textbf{RESTful APIs} to connect with third-party systems, expanding vendor support capabilities by 12\% within one quarter.}
        \resumeItem{Authored unit and integration tests using \textbf{JUnit} and \textbf{Mockito}, identifying and fixing 20+ critical bugs before release.}
        \resumeItem{Optimized \textbf{DynamoDB} and SQL queries, improving inventory read performance by 14\% during peak hours.}
        \resumeItem{Automated deployment tasks creating Jenkins pipelines, saving around 4 hours weekly on manual processes and improving delivery speed.}
      \resumeItemListEnd


  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-driven Document Query System} | Python, LangChain, OpenAI API, FAISS}{}
        \resumeItemListStart
            \resumeItem{Developed an advanced AI-powered system enabling natural language querying over multiple documents, enhancing user access to relevant information by 50\%.}
            \resumeItem{Implemented a retrieval-augmented generation pipeline that integrates semantic search with fallback keyword logic, improving response accuracy in 95\% cases.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Financial Services Microservices Platform} | Java, Spring Boot, PostgreSQL, Kubernetes}{}
        \resumeItemListStart
            \resumeItem{Built and deployed a set of microservices to support core banking workflows, improving transaction processing time by 30\% in a cloud environment.}
            \resumeItem{Designed RESTful APIs and optimized database transactions using SQL and Hibernate, increasing platform scalability and reliability under heavy loads.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{CI/CD Pipeline Automation} | Jenkins, Docker, ArgoCD, Git}{}
        \resumeItemListStart
            \resumeItem{Engineered a CI/CD pipeline that automated builds, tests, and deployments for Java applications, reducing release cycles by 40\%.}
            \resumeItem{Integrated version control and container orchestration to streamline releases with improved rollback capabilities, enhancing deployment stability.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}