\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Rahul Reddy K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (714) 805-6273 ~ | ~ \href{mailto:kanrahuldo1@gmail.com}{kanrahuldo1@gmail.com}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{\textbf{Senior Software Engineer} with over \textbf{10 years} of experience in backend development, specializing in \textbf{Java} and \textbf{Spring Boot} microservices.} \vspace{-3pt}
    \resumeItem{Expert in designing scalable applications with a strong understanding of \textbf{JVM internals}, \textbf{multithreading}, and performance tuning for high-throughput systems.} \vspace{-3pt}
    \resumeItem{Proficient in \textbf{Kafka} for event-driven architectures and experienced in containerization with \textbf{Docker} and orchestration using \textbf{Kubernetes}.} \vspace{-3pt}
    \resumeItem{Strong knowledge of \textbf{AWS} cloud services and \textbf{Infrastructure as Code} using \textbf{Terraform} for automated deployments and resource management.} \vspace{-3pt}
    \resumeItem{Skilled in CI/CD practices using \textbf{Jenkins} and version control with \textbf{Git}, ensuring efficient development workflows and code quality.} \vspace{-3pt}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java (8, 11, 17), C, C++, Python, Shell Scripting \\
                \textbf{Frameworks:} & Spring Boot, Microservices, Kafka, Docker, Kubernetes (GKE, EKS) \\
                \textbf{Databases:} & Oracle, Cassandra, MySQL, PostgreSQL, MongoDB \\
                \textbf{Cloud Services:} & AWS (EC2, S3, RDS) \\
                \textbf{CI/CD:} & Jenkins, Terraform, Git/GitHub \\
                \textbf{Methodologies:} & Agile, Scrum, Test Driven Development \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Toyota Motors}{Oct 2023 -- Present}
        {C++ Embedded / Application Developer}{TX}
      \resumeItemListStart
        \resumeItem{Engineered high-performance \textbf{Java} applications using \textbf{Spring Boot} to enhance application scalability and maintainability, improving response times by 30\%.}
        \resumeItem{Architected and implemented microservices-based solutions with \textbf{Kafka} for event-driven architectures, achieving a 40\% increase in throughput.}
        \resumeItem{Utilized \textbf{Docker} for containerization and deployed applications on \textbf{Kubernetes}, ensuring efficient scaling and operational monitoring.}
        \resumeItem{Collaborated with cross-functional teams to define system specifications and deliver high-quality software solutions, reducing time-to-market by 25\%.}
        \resumeItem{Conducted performance tuning and optimization of multithreaded components to minimize latency, resulting in a 20\% improvement in processing speed.}
      \resumeItemListEnd

    \resumeSubheading
        {Texas Instruments}{Aug 2022 -- Sep 2023}
        {C/C++ Embedded Developer}{Phoenix, AZ}
      \resumeItemListStart
        \resumeItem{Developed and maintained \textbf{Java} microservices using \textbf{Spring Boot}, enhancing system reliability and reducing downtime by 15\%.}
        \resumeItem{Implemented CI/CD pipelines with \textbf{Jenkins} for automated testing and deployment, improving deployment frequency by 50\%.}
        \resumeItem{Designed and optimized data processing components with \textbf{Kafka} to handle high-throughput workloads, achieving sub-second latency.}
        \resumeItem{Integrated \textbf{AWS} services for cloud-based solutions, resulting in a 30\% cost reduction in infrastructure management.}
        \resumeItem{Conducted code reviews and mentoring sessions, fostering a culture of quality and continuous improvement within the development team.}
      \resumeItemListEnd

    \resumeSubheading
        {Texas Instruments}{May 2021 -- Jul 2022}
        {C/C++ Embedded Developer}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Developed backend services in \textbf{Java} to support embedded applications, improving system performance and reliability by 25\%.}
        \resumeItem{Utilized \textbf{Spring Boot} to create RESTful APIs for seamless integration with frontend components, enhancing user experience.}
        \resumeItem{Implemented \textbf{Terraform} for Infrastructure as Code, automating resource provisioning and reducing deployment time by 20\%.}
        \resumeItem{Collaborated with teams to design and implement event-driven architectures using \textbf{Kafka} for real-time data processing.}
      \resumeItemListEnd

    \resumeSubheading
        {Panasonic}{Feb 2020 -- Apr 2021}
        {C++ Developer}{Bengaluru, KA}
      \resumeItemListStart
        \resumeItem{Designed and implemented a real-time data processing engine using \textbf{Java} and \textbf{Spring Boot}, improving processing efficiency by 30\%.}
        \resumeItem{Engineered microservices architecture with \textbf{Docker} and \textbf{Kubernetes}, enhancing deployment speed and scalability.}
        \resumeItem{Created REST APIs for device communication, achieving a 25\% reduction in response time through optimized data handling.}
        \resumeItem{Conducted performance analysis and tuning of applications, leading to a 15\% improvement in system throughput.}
      \resumeItemListEnd

    \resumeSubheading
        {JSW Steel}{Aug 2017 -- Dec 2019}
        {C++ Embedded Developer}{India}
      \resumeItemListStart
        \resumeItem{Modernized legacy systems by implementing \textbf{Java} solutions, improving maintainability and reducing technical debt by 40\%.}
        \resumeItem{Developed high-performance web services using \textbf{Spring Boot} and \textbf{Kafka}, enhancing data processing capabilities for automotive systems.}
        \resumeItem{Designed and implemented solutions for embedded systems, integrating \textbf{NoSQL} databases for efficient data storage and retrieval.}
        \resumeItem{Collaborated with cross-functional teams to ensure seamless integration of software components, achieving project milestones ahead of schedule.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
\resumeItemListStart
    \resumeProjectHeading{\textbf{Real-Time Data Processing System}}{2023}
    \resumeItem{Developed a high-performance data processing system using \textbf{Java} and \textbf{Kafka}, enabling real-time analytics for large datasets.}
    \resumeItem{Implemented microservices architecture with \textbf{Spring Boot}, achieving a 50\% reduction in processing time for data ingestion.}

    \resumeProjectHeading{\textbf{Event-Driven Architecture Implementation}}{2022}
    \resumeItem{Architected an event-driven architecture using \textbf{Kafka} to streamline communication between microservices, improving system responsiveness by 30\%.}
    \resumeItem{Utilized \textbf{Docker} and \textbf{Kubernetes} for deployment, ensuring high availability and scalability of services in production.}

    \resumeProjectHeading{\textbf{AI-Powered Recommendation Engine}}{2021}
    \resumeItem{Developed an AI-powered recommendation engine using \textbf{Java} and \textbf{Spring Boot}, enhancing user engagement by 40\%.}
    \resumeItem{Integrated machine learning algorithms for personalized content delivery, resulting in a significant increase in user retention rates.}
\resumeItemListEnd

\end{document}