\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{\textbf{Software engineer} with \textbf{5+ years} of experience in backend development, specializing in \textbf{Java}, \textbf{Spring Boot}, and \textbf{microservices architecture}.} \vspace{-3pt}
    \resumeItem{Proficient in building scalable applications on \textbf{AWS} and deploying with \textbf{Docker} and \textbf{Kubernetes}, ensuring high availability and performance.} \vspace{-3pt}
    \resumeItem{Experienced in implementing event-driven architectures using \textbf{Kafka} and optimizing multithreaded applications for improved throughput and low latency.} \vspace{-3pt}
    \resumeItem{Skilled in CI/CD practices using \textbf{Jenkins} and \textbf{Terraform}, automating deployment processes for faster and more reliable releases.} \vspace{-3pt}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java (8, 11, 17), Python, JavaScript, TypeScript, SQL, PL/SQL, Shell Scripting, Go \\
                \textbf{Frameworks \& Backend:} & Spring Boot, Spring Cloud, Microservices, Node.js, Express.js, Hibernate, gRPC \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, ECS, S3, API Gateway), Docker, Kubernetes (GKE, EKS), Jenkins, Terraform \\
                \textbf{Databases:} & Oracle, PostgreSQL, MongoDB, Cassandra, Redis \\
                \textbf{Messaging \& Streaming:} & Kafka, Kafka Streams \\
                \textbf{Tools \& Observability:} & IntelliJ, VS Code, JIRA, Grafana, Prometheus \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Engineered high-performance microservices using \textbf{Java}, \textbf{Spring Boot}, and \textbf{AWS}, achieving a \textbf{30\% increase} in system throughput.}
        \resumeItem{Implemented secure REST APIs for microservices, enhancing scalability and reducing response times by \textbf{25\%} through efficient design.}
        \resumeItem{Optimized multithreaded components to support high-throughput workloads, improving application performance by \textbf{20\%} during peak usage.}
        \resumeItem{Deployed applications using \textbf{Docker} and \textbf{Kubernetes}, ensuring seamless orchestration and scaling across cloud environments.}
        \resumeItem{Integrated \textbf{Kafka} for event-driven processing, enabling real-time data handling and increasing transaction processing capacity by \textbf{40\%}.}
        \resumeItem{Established CI/CD pipelines with \textbf{Jenkins} and \textbf{Terraform}, reducing deployment time by \textbf{50\%} and increasing release frequency.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Developed backend services for core banking applications using \textbf{Java} and \textbf{Spring Boot}, enhancing system reliability and performance.}
        \resumeItem{Designed and implemented microservices for a loan application platform, improving user experience and reducing processing time by \textbf{30\%}.}
        \resumeItem{Created an event-driven architecture with \textbf{Kafka}, handling over \textbf{10,000 transactions per second} reliably and efficiently.}
        \resumeItem{Automated CI/CD processes using \textbf{Jenkins}, resulting in a \textbf{25\% reduction} in deployment time and improved software delivery.}
        \resumeItem{Enhanced database performance by optimizing \textbf{Oracle} queries, achieving a \textbf{20\% improvement} in data retrieval times.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed backend modules for supply chain management using \textbf{Java} and \textbf{Spring MVC}, reducing order processing latency by \textbf{140ms}.}
        \resumeItem{Collaborated on integrating third-party logistics APIs using \textbf{Node.js}, expanding vendor support and improving overall system efficiency.}
        \resumeItem{Authored comprehensive unit tests with \textbf{JUnit} and \textbf{Mockito}, ensuring high code quality and identifying critical bugs prior to deployment.}
        \resumeItem{Migrated on-premise components to \textbf{AWS}, enhancing system availability and reducing hardware-related downtime by \textbf{18\%}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-Powered Document Querying} $|$ Python, Streamlit, LangChain, OpenAI API, Docker}{ }
        \resumeItemListStart
            \resumeItem{Developed an AI-driven application for querying documents using natural language, improving user interaction and data retrieval efficiency.}
            \resumeItem{Implemented a robust backend using \textbf{Docker} for containerization, ensuring consistent deployment across various environments.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Real-Time Event Processing System} $|$ Java, Spring Boot, Kafka, Docker, Kubernetes}{ }
        \resumeItemListStart
            \resumeItem{Engineered a scalable event-driven architecture using \textbf{Kafka} and \textbf{Spring Boot}, processing over \textbf{10,000 events per second}.}
            \resumeItem{Containerized the application with \textbf{Docker} and orchestrated using \textbf{Kubernetes}, improving deployment efficiency and scalability.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Cloud-Based Microservices Application} $|$ Java, Spring Boot, AWS, Terraform, Jenkins}{ }
        \resumeItemListStart
            \resumeItem{Built a cloud-native application using \textbf{Spring Boot} on \textbf{AWS}, achieving high availability and resilience in production.}
            \resumeItem{Automated infrastructure provisioning with \textbf{Terraform} and established CI/CD pipelines with \textbf{Jenkins}, enhancing deployment speed by \textbf{40\%}.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}