\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Accomplished software engineer with over 5 years of experience in backend development, specializing in \textbf{Java}, \textbf{Spring Boot}, and microservices architecture.} \vspace{-3pt}
    \resumeItem{Proficient in designing and deploying scalable applications on \textbf{AWS}, leveraging containerization with \textbf{Docker} and orchestration using \textbf{Kubernetes}.} \vspace{-3pt}
    \resumeItem{Extensive experience in implementing event-driven architectures with \textbf{Kafka} and optimizing performance through multithreading and concurrency techniques.} \vspace{-3pt}
    \resumeItem{Skilled in creating CI/CD pipelines using \textbf{Jenkins} and \textbf{Terraform} to enhance deployment efficiency and system reliability.} \vspace{-3pt}
    \resumeItem{Strong analytical and problem-solving skills, with a proven track record of improving application performance and user satisfaction.} \vspace{-3pt}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java (8, 11, 17), Python, JavaScript, TypeScript, SQL, PL/SQL, Shell Scripting \\
                \textbf{Frameworks \& Backend:} & Spring Boot, Spring Cloud, Microservices, Node.js, gRPC, Hibernate \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, ECS, API Gateway), Docker, Kubernetes, Jenkins, Terraform \\
                \textbf{Databases:} & Oracle, PostgreSQL, Cassandra, DynamoDB, Redis \\
                \textbf{Event Streaming:} & Kafka, Kafka Streams \\
                \textbf{Testing \& Automation:} & JUnit, Mockito, Selenium, Postman \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Designed and implemented scalable microservices using \textbf{Java} and \textbf{Spring Boot}, achieving a \textbf{30\% reduction} in response times for API calls.}
        \resumeItem{Developed event-driven solutions with \textbf{Kafka} and \textbf{Kafka Streams}, enhancing data processing capabilities and improving throughput by \textbf{25\%}.}
        \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes}, ensuring high availability and efficient resource utilization.}
        \resumeItem{Established CI/CD pipelines with \textbf{Jenkins} and \textbf{Terraform}, increasing deployment frequency by \textbf{50\%} and reducing rollback incidents.}
        \resumeItem{Optimized application performance through multithreading and concurrency techniques, improving processing speed by \textbf{20\%} during peak loads.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Architected and developed microservices for core banking applications using \textbf{Java} and \textbf{Spring Boot}, improving system reliability by \textbf{30\%}.}
        \resumeItem{Implemented event-driven architecture with \textbf{Kafka}, successfully processing over \textbf{10,000 transactions per second} with minimal latency.}
        \resumeItem{Enhanced CI/CD processes by integrating \textbf{Jenkins} with version control systems, reducing deployment times by \textbf{30\%} and improving delivery efficiency.}
        \resumeItem{Automated application testing frameworks using \textbf{JUnit} and \textbf{Mockito}, achieving over \textbf{95\% test coverage} and increasing software reliability.}
        \resumeItem{Collaborated on migrating applications to \textbf{AWS}, enhancing scalability and reducing infrastructure costs by \textbf{20\%}.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed backend services for supply chain management using \textbf{Java} and \textbf{Spring MVC}, reducing order processing time by \textbf{140ms}.}
        \resumeItem{Integrated third-party logistics APIs with \textbf{Node.js}, expanding vendor support coverage by \textbf{12\%} within the first quarter.}
        \resumeItem{Implemented automated build processes using \textbf{Jenkins} and shell scripts, decreasing manual deployment overhead by \textbf{4 hours} weekly.}
        \resumeItem{Optimized database access patterns in \textbf{DynamoDB}, resulting in a \textbf{14\%} improvement in read throughput during peak usage.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-Powered Document Query System} $|$ Python, Streamlit, OpenAI API, Docker}{ }
        \resumeItemListStart
            \resumeItem{Developed an AI-driven application for querying documents using natural language, improving user interaction and information retrieval efficiency.}
            \resumeItem{Implemented a robust backend with \textbf{Docker} for containerization, ensuring seamless deployment and scalability across cloud environments.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Real-time Data Processing Application} $|$ Java, Spring Boot, Kafka, Kubernetes}{ }
        \resumeItemListStart
            \resumeItem{Engineered a real-time data processing system using \textbf{Kafka} and \textbf{Spring Boot}, handling over \textbf{1000 concurrent requests} efficiently.}
            \resumeItem{Deployed application on \textbf{Kubernetes}, ensuring high availability and fault tolerance in a cloud-native architecture.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Scalable Microservices Architecture} $|$ Java, Spring Boot, AWS, Terraform}{ }
        \resumeItemListStart
            \resumeItem{Architected a microservices-based solution on \textbf{AWS}, leveraging \textbf{Terraform} for Infrastructure as Code, enhancing deployment efficiency.}
            \resumeItem{Implemented CI/CD pipelines with \textbf{Jenkins}, reducing deployment times by \textbf{40\%} and increasing overall system reliability.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}