\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Versatile \textbf{software engineer} with over \textbf{5 years} of experience delivering backend and full-stack solutions with strong expertise in building scalable APIs and distributed systems.} \vspace{-3pt}
    \resumeItem{Proficient in \textbf{Java, Python, and Golang} backend development, along with integrating and developing AI-driven workflows and agentic systems for automation and intelligent features.} \vspace{-3pt}
    \resumeItem{Skilled in designing robust microservices and data synchronization services that ensure high reliability, resiliency, and real-time processing at scale.} \vspace{-3pt}
    \resumeItem{Experienced in leveraging \textbf{OpenAI API, LangChain}, and custom AI pipelines to build intelligent systems enabling automated validation and diagnostics in production environments.} \vspace{-3pt}
    \resumeItem{Strong collaborator focused on delivering cohesive end-to-end product functionality with attention to observability, debugging, and continuous platform improvement.} \vspace{-3pt}
    \resumeItem{Committed to continuous learning and feedback-driven development, enhancing both technical skillsets and effective product delivery on AI-powered platforms.} \vspace{-3pt}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Backend:} & Java (17 \& 21), Python, Golang, Spring Boot, Spring Cloud, Node.js, RESTful APIs, gRPC \\
                \textbf{AI \& Agentic Systems:} & OpenAI API, LangChain, Agentic AI, RAG (Retrieval-Augmented Generation), TensorFlow, Scikit-learn \\
                \textbf{Frontend \& Web:} & React.js, Angular, TypeScript, GraphQL, JSON, XML \\
                \textbf{Databases \& Data Processing:} & PostgreSQL, Oracle, MongoDB, Redis, DynamoDB, Kafka, Cassandra \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, ECS, S3, API Gateway, CodePipeline), Azure, Docker, Kubernetes, Jenkins, GitHub Actions, Terraform \\
                \textbf{Monitoring \& Testing:} & JUnit, Mockito, Selenium, Postman, Grafana, Prometheus, Splunk, AppDynamics, CI/CD Automation \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Implemented backend microservices in \textbf{Java} and \textbf{Spring Boot} integrating \textbf{AI-driven automation} enhancing content validation workflows by 30\%.}
        \resumeItem{Developed scalable APIs supporting AI-powered features using \textbf{GraphQL} and \textbf{AWS API Gateway}, reducing response latency by 35\% during peak loads.}
        \resumeItem{Architected and deployed \textbf{agentic AI} RAG system using \textbf{Redis} vector indexing, improving document similarity search accuracy by over 40\%.}
        \resumeItem{Enhanced system observability and resilience by integrating distributed tracing and proactive diagnostics across \textbf{microservices} clusters on \textbf{AWS ECS}.}
        \resumeItem{Automated \textbf{CI/CD} pipelines with \textbf{Jenkins} and \textbf{AWS CodePipeline}, increasing deployment frequency by 50\% and reducing rollback incidents by 20\%.}
        \resumeItem{Optimized complex \textbf{PostgreSQL} queries to synchronize partner inventory data reliably at scale, boosting throughput by 20\%.}
        \resumeItem{Collaborated closely with frontend team to deliver cohesive AI-enhanced workflows using \textbf{React.js} and \textbf{TypeScript}, improving user engagement by 25\%.}
        \resumeItem{Built reusable backend APIs supporting autonomous content holder tooling, contributing to safer and efficient ticket inventory management at StubHub scale.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Designed robust backend services using \textbf{Java} and \textbf{Spring Boot}, implementing distributed data ingestion systems used in financial transaction processing.}
        \resumeItem{Developed \textbf{Node.js} middleware supporting asynchronous event-driven workflows, optimizing cash position transactions throughput by 30\%.}
        \resumeItem{Integrated \textbf{Kafka}-based real-time data pipelines handling over 10,000 transactions per second with fault-tolerant processing and seamless scaling.}
        \resumeItem{Created comprehensive observability dashboards using \textbf{Grafana} and \textbf{Prometheus}, enabling proactive identification and swift resolution of performance issues.}
        \resumeItem{Built and secured API gateways using \textbf{OAuth2} and \textbf{JWT}, lowering authentication-related failures by 40\% in production environments.}
        \resumeItem{Enhanced CI/CD delivery by incorporating \textbf{Jenkins} automation with \textbf{SVN}, accelerating release cycles by 30\% while retaining high stability.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed high-performance backend services in \textbf{Java} and \textbf{Spring MVC} to support supply chain management with improved data processing speed by 25\%.}
        \resumeItem{Built and maintained RESTful APIs with \textbf{Node.js} and \textbf{Express.js} integrating third-party services, expanding platform capabilities by 30\%.}
        \resumeItem{Led migration of legacy applications to \textbf{AWS} cloud, achieving 20\% cost reduction and improved scalability for real-time inventory updates.}
        \resumeItem{Optimized \textbf{DynamoDB} based storage, decreasing data retrieval latency by 15\%, enhancing application responsiveness in dynamic environments.}
        \resumeItem{Created Linux shell scripts for real-time system health monitoring, reducing issue detection time by 30\%, improving platform reliability.}
        \resumeItem{Streamlined CI/CD workflows using \textbf{GitHub Actions}, increasing deployment velocity by 40\%, enabling faster feature delivery under Agile processes.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-Driven Content Rights Automation} $|$ Java, Spring Boot, OpenAI API, Redis, AWS}{ }
        \resumeItemListStart
            \resumeItem{Engineered backend services integrating \textbf{OpenAI API} and \textbf{Spring Boot} for automated content validation workflows, improving partner data accuracy by 30\%.}
            \resumeItem{Implemented real-time data synchronization pipelines with \textbf{Redis} vector search to enhance content detection and rights holder inventory management efficiency.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{InsightPDF} $|$ Python, Streamlit, LangChain, OpenAI API, FAISS}{ }
        \resumeItemListStart
            \resumeItem{Built an AI-powered PDF query platform using \textbf{LangChain} and \textbf{OpenAI API} combining RAG for intelligent document content retrieval in natural language.}
            \resumeItem{Deployed the application with containerization using \textbf{Docker} and CI/CD automation via \textbf{GitHub Actions}, ensuring faster iteration and robust delivery.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Distributed Graph Data Analytics} $|$ Docker, Kubernetes, Apache Kafka, Neo4j}{ }
        \resumeItemListStart
            \resumeItem{Developed a scalable graph data pipeline leveraging \textbf{Kafka} and \textbf{Kubernetes} for high concurrency requests and reliable stream processing of analytics data.}
            \resumeItem{Implemented graph algorithms such as PageRank using \textbf{Neo4j} to provide actionable insights with minimal latency for large-scale datasets.}
        \resumeItemListEnd
        \vspace{-12pt}

    \resumeSubHeadingListEnd

\end{document}