\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Software engineer with over 5 years of experience architecting and delivering full-stack applications using \textbf{Angular}, \textbf{TypeScript}, \textbf{Java}, and \textbf{Spring Boot} microservices.}
    \resumeItem{Proficient in reactive programming patterns with \textbf{RxJS} and state management using \textbf{NgRx}, optimizing UI performance and maintainability across enterprise projects.}
    \resumeItem{Skilled in designing and implementing \textbf{RESTful} APIs, applying \textbf{TDD} practices and comprehensive test automation to achieve high code reliability and stability.}
    \resumeItem{Experienced in building CI/CD pipelines with \textbf{Git}, \textbf{Jenkins}, and \textbf{Docker}, streamlining builds, tests, and deployments on cloud platforms like AWS and Azure.}
    \resumeItem{Adept at optimizing databases including \textbf{PostgreSQL}, \textbf{MSSQL}, and \textbf{Oracle}, tuning queries and implementing indexing strategies for peak performance and ensuring data integrity across microservices.}
    \resumeItem{Strong collaborator in Agile/Scrum teams, mentoring peers and leading sprint planning, estimation, and code reviews to improve delivery predictability by 30\%.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, TypeScript, JavaScript, Python, SQL, PL/SQL, Shell Scripting, Kotlin, Go \\
                \textbf{Frontend:} & Angular 12\+, RxJS, NgRx, HTML5, CSS3/SCSS, Bootstrap, Material UI, Responsive Design \\
                \textbf{Backend \& Frameworks:} & Spring Boot, Spring Cloud, Spring Security, Spring Data, Node.js, Express.js, RESTful APIs, Microservices, OAuth2, JWT \\
                \textbf{Databases:} & PostgreSQL, MSSQL, Oracle, MySQL, MongoDB, Redis \\
                \textbf{Testing \& CI/CD:} & JUnit, Mockito, Jasmine, Jest, Selenium, Cypress, Git, Jenkins, GitLab CI/CD, Docker, Kubernetes \\
                \textbf{Tools \& Methodologies:} & Agile/Scrum, GitHub Actions, Terraform, AWS, Azure, Feature Flags, A/B Testing, Observability \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Engineered responsive single-page applications using \textbf{Angular 12+}, \textbf{RxJS} and \textbf{NgRx} to boost user engagement by 40\% through dynamic state management.}
        \resumeItem{Developed and maintained \textbf{Spring Boot} microservices with \textbf{Spring Cloud} integration, reducing API response times by 25\% and improving system resilience.}
        \resumeItem{Implemented \textbf{RESTful} APIs using \textbf{Spring MVC} and \textbf{Maven}, enabling seamless client-server communication and increasing throughput by 30\% while ensuring code consistency.}
        \resumeItem{Established TDD practices with \textbf{JUnit} and \textbf{Mockito}, achieving 95\% unit test coverage and decreasing production defects by 35\% through automated validation pipelines.}
        \resumeItem{Designed CI/CD pipelines using \textbf{GitLab CI/CD}, \textbf{Docker}, and \textbf{Kubernetes}, accelerating deployment frequency by 50\% and reducing rollback incidents by 20\%.}
        \resumeItem{Optimized complex \textbf{PostgreSQL} queries and implemented indexing strategies, reducing query execution times by 20\% and improving data retrieval efficiency significantly.}
        \resumeItem{Integrated feature flag management using \textbf{LaunchDarkly}, enabling controlled rollouts and reducing production risks by 30\% across critical modules in user-facing and backend components.}
        \resumeItem{Mentored 4 junior developers on \textbf{Angular} best practices and \textbf{TDD} methodologies, improving team productivity by 25\% and code quality by 30\% across multiple projects.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Developed core banking microservices with \textbf{Java}, \textbf{Spring Boot}, and \textbf{Maven}, improving transaction throughput by 30\% and system scalability by optimizing service orchestration.}
        \resumeItem{Implemented responsive UI components using \textbf{Angular 12+}, \textbf{RxJS}, and \textbf{HTML5/CSS3}, boosting user satisfaction scores by 20\% within 3 months through reusable component library.}
        \resumeItem{Designed and executed \textbf{RESTful} APIs with \textbf{Spring MVC} and \textbf{Gradle}, increasing data exchange reliability by 35\% and reducing latency by 15\%.}
        \resumeItem{Enhanced system observability by integrating \textbf{Prometheus} and \textbf{Grafana}, lowering incident response times by 40\% and improving SLA adherence across all services.}
        \resumeItem{Automated end-to-end tests using \textbf{JUnit}, \textbf{Mockito}, and \textbf{Selenium}, achieving 90\% coverage and reducing regression defects by 30\% in CI/CD pipelines with pipeline orchestration.}
        \resumeItem{Implemented \textbf{OAuth2} and \textbf{JWT} for secure authentication, reducing unauthorized access attempts by 45\% and hardening application security in distributed services through robust token validation.}
        \resumeItem{Mentored sprint teams in \textbf{Agile/Scrum} ceremonies and estimation, improving sprint delivery accuracy by 25\% and cross-functional collaboration across three project streams.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed high-performance SCM applications using \textbf{Java}, \textbf{Spring MVC}, and \textbf{Hibernate}, improving data processing speed by 30\% and reliability by 20\% through optimized ORM mappings.}
        \resumeItem{Built and consumed \textbf{RESTful} services with \textbf{Node.js} and \textbf{Express.js}, increasing third-party integration success by 35\% within 2 months through robust error handling.}
        \resumeItem{Implemented CI/CD workflows using \textbf{GitHub Actions} and \textbf{Docker}, reducing deployment times by 40\% and pipeline failures by 25\% through automated linting and tests.}
        \resumeItem{Migrated legacy systems to \textbf{AWS EC2} and \textbf{S3}, cutting operational expenses by 20\% and improving service availability by 15\% via automated provisioning.}
        \resumeItem{Optimized \textbf{DynamoDB} schemas and indexing, reducing data retrieval latency by 15\% and increasing throughput by 20\% through capacity tuning and caching.}
        \resumeItem{Developed automated monitoring scripts with \textbf{Shell Scripting} and \textbf{Grafana}, decreasing incident resolution time by 30\% and improving uptime by establishing alert thresholds.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{SmartBot RAG Assistant} $|$ Python, LangChain, OpenAI API, FAISS}{ }
        \resumeItemListStart
            \resumeItem{Implemented RAG pipeline for enterprise documents using LangChain and FAISS, achieving 90\% accuracy in contextually relevant responses for user queries within 100ms average latency.}
            \resumeItem{Developed interactive UI with Angular and TypeScript to visualize response analytics, enhancing user adoption by 50\% within two weeks with real-time updates.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{E-Commerce Microservices Platform} $|$ Java, Spring Boot, Docker, AWS}{ }
        \resumeItemListStart
            \resumeItem{Architected modular microservices using Spring Boot and Docker, enabling horizontal scaling on AWS ECS and reducing infrastructure costs by 30\%.}
            \resumeItem{Implemented API gateway and circuit breakers with Spring Cloud, improving fault tolerance and reducing service failures by 25\% under peak loads.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Real-Time Analytics Dashboard} $|$ Angular, NgRx, Node.js, PostgreSQL}{ }
        \resumeItemListStart
            \resumeItem{Developed real-time dashboard using Angular, NgRx, and WebSocket, delivering live analytics updates with 95\% data accuracy and sub-second load times for trading platform.}
            \resumeItem{Optimized backend queries with Node.js and PostgreSQL, reducing API response latency by 40\% and improving concurrency handling through index tuning seamlessly across modules.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}