\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Results-oriented software engineer with \textbf{5+ years} of expertise in full-stack development, specializing in \textbf{Angular, TypeScript, and Java Spring Boot} applications.}
    \resumeItem{Proficient in designing and maintaining scalable \textbf{microservices} and responsive front-end systems ensuring high performance across browsers and devices.}
    \resumeItem{Experienced in \textbf{RxJS}, NgRx state management, and implementing \textbf{RESTful APIs} with comprehensive unit and integration testing using TDD practices.}
    \resumeItem{Skilled in leading Agile teams, optimizing CI/CD pipelines, executing code reviews, and mentoring junior developers to elevate code quality.}
    \resumeItem{Strong background in \textbf{cloud deployment} on AWS and Azure with container orchestration using Docker and Kubernetes for robust, secure applications.}
    \resumeItem{Hands-on knowledge of advanced security protocols including OAuth2, JWT, and encryption to safeguard applications in regulated financial domains.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java (17 \& 21), TypeScript, JavaScript (ES6+), SQL, Python, PL/SQL, Shell Scripting, Kotlin, HTML5, CSS3/SCSS \\ 
                \textbf{Frameworks \& Backend:} & Spring Boot, Spring Cloud, Spring Security, Spring Data, Angular (12+), RxJS, NgRx, Node.js, Express.js, RESTful API Design, OAuth2, JWT \\ 
                \textbf{Frontend:} & Angular, React.js, Material UI, Bootstrap, Tailwind, Redux, Responsive Design, Cross-Browser Compatibility \\ 
                \textbf{Testing \& Automation:} & JUnit, Mockito, Selenium, Cucumber, Postman, REST Assured, Test-Driven Development, CI/CD Pipeline Configuration, Jenkins, GitLab CI/CD, GitHub Actions \\ 
                \textbf{Cloud \& DevOps:} & AWS (EC2, ECS, S3, API Gateway, CodePipeline), Azure, Docker, Kubernetes, Maven, Gradle, Terraform \\ 
                \textbf{Databases \& Tools:} & PostgreSQL, Oracle Database, MSSQL, Redis, Grafana, AppDynamics, SonarQube, IntelliJ, VS Code, JIRA \\ 
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Engineered robust microservices with \textbf{Java Spring Boot} and \textbf{Spring Cloud} on \textbf{AWS ECS}, improving uptime and performance by 25\%.}
        \resumeItem{Designed responsive \textbf{Angular 12+} applications with \textbf{RxJS} and \textbf{NgRx}, increasing user engagement metrics and cross-browser compatibility.}
        \resumeItem{Led migration from monolith to microservices architecture, reducing deployment times by 30\% and enhancing system scalability for e-Commerce clients.}
        \resumeItem{Implemented \textbf{RESTful APIs} integrating secure authentication using \textbf{OAuth2} and \textbf{JWT}, improving security posture and compliance.}
        \resumeItem{Developed CI/CD pipelines using \textbf{Jenkins}, \textbf{Docker}, and \textbf{AWS CodePipeline}, increasing deployment frequency by 50\% and reducing errors.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries, boosting database response times by 20\% supporting high-volume transactional systems.}
        \resumeItem{Established unit and integration testing with \textbf{JUnit} and \textbf{Mockito}, achieving over 98\% code coverage and fostering TDD adoption.}
        \resumeItem{Monitored application performance via \textbf{AppDynamics} and \textbf{Grafana}, facilitating rapid troubleshooting and 15\% downtime decrease.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Spring Boot} microservices for banking domain, implementing core features with \textbf{Java}, and maintaining security with \textbf{Spring Security}.}
        \resumeItem{Built front-end modules using \textbf{Angular} and state management via \textbf{RxJS} and \textbf{NgRx}, enhancing user experience substantially.}
        \resumeItem{Automated CI/CD pipelines integrating \textbf{SVN} and \textbf{Jenkins}, accelerating deployment velocity by 30\% and improving software delivery efficiency.}
        \resumeItem{Architected an event-driven system using \textbf{Kafka} managing 10,000+ TPS, improving reliability and responsiveness of cash management applications.}
        \resumeItem{Implemented secure authentication with \textbf{OAuth2} and \textbf{JWT}, reducing security incidents by 40\% and increasing compliance with standards.}
        \resumeItem{Designed monitoring dashboards with \textbf{Grafana} and \textbf{Prometheus}, improving observability and enabling proactive issue resolution.}
        \resumeItem{Mentored junior developers in Agile environments, leading sprint planning and estimation, boosting team productivity by 25\%.}
        \resumeItem{Led feature flag management implementation enhancing A/B testing and controlled feature rollouts for banking applications.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{RESTful APIs} with \textbf{Node.js} and \textbf{Express.js}, integrating third-party services and increasing platform capabilities by 30\%.}
        \resumeItem{Participated in migration of legacy systems to \textbf{AWS Cloud}, reducing infrastructure costs by 20\% and increasing system scalability.}
        \resumeItem{Automated testing with \textbf{JUnit} and \textbf{Postman}, enforcing test-driven development and improving system reliability over 95\%.}
        \resumeItem{Engineered \textbf{Linux Shell} scripts for monitoring and performance optimization, reducing incident response times by 30\%.}
        \resumeItem{Streamlined CI/CD deployment using \textbf{GitHub Actions}, accelerating delivery speed by 40\% and improving release quality.}
        \resumeItem{Facilitated adoption of Agile and \textbf{Scrum} methodologies, improving project delivery time and team collaboration by 25\%.}
        \resumeItem{Optimized \textbf{DynamoDB} usage, reducing data access latency by 15\%, boosting application responsiveness.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-Driven Document Query System} | Python, LangChain, OpenAI API, FAISS, Docker}{ }
        \resumeItemListStart
            \resumeItem{Designed a RAG pipeline using \textbf{LangChain} and \textbf{OpenAI API} for multi-document querying, delivering precise natural language answers.}
            \resumeItem{Containerized with \textbf{Docker} and automated deployment through \textbf{GitHub Actions}, increasing reliability and reducing manual operations by 35\%.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Scalable Angular Microfrontend Architecture} | Angular 12+, TypeScript, RxJS, NgRx, Docker, AWS}{ }
        \resumeItemListStart
            \resumeItem{Implemented modular, reactive front-end components with \textbf{Angular 12+}, \textbf{RxJS}, and \textbf{NgRx} improving load times by 40\%.}
            \resumeItem{Deployed via \textbf{Docker} containers on \textbf{AWS}, automating blue-green deployments to reduce downtime by 30\%.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Secure Financial Services Backend} | Java, Spring Boot, PostgreSQL, OAuth2, JWT, Kubernetes, AWS}{ }
        \resumeItemListStart
            \resumeItem{Engineered secure microservices backend employing \textbf{Spring Boot}, \textbf{OAuth2}, and \textbf{JWT}, raising security compliance by 45\%.}
            \resumeItem{Orchestrated container deployment on \textbf{Kubernetes} with \textbf{AWS} integration, boosting fault tolerance and reliability by 30\%.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}