\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{\textbf{Software engineer} with over \textbf{5 years} of experience designing and developing scalable enterprise applications in the \textbf{C\# and .NET} ecosystem.} \vspace{-3pt}
    \resumeItem{Expert in crafting \textbf{microservices architecture}, breaking down monolithic systems, with hands-on experience in \textbf{REST API development} and \textbf{CI/CD pipelines}.} \vspace{-3pt}
    \resumeItem{Skilled in full-stack development leveraging \textbf{Angular} and \textbf{TypeScript} for rich frontend experiences and \textbf{SQL} for efficient database design and optimization.} \vspace{-3pt}
    \resumeItem{Strong understanding of best practices in software design, testing, and deployment to ensure high availability and robust enterprise-grade solutions.} \vspace{-3pt}
    \resumeItem{Experienced in collaborating across agile teams and mentoring junior developers to deliver quality software aligned with business goals.} \vspace{-3pt}
    \resumeItem{Committed to continuous learning and adopting innovative technologies to advance enterprise payment systems and applications.} \vspace{-3pt}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & C\# (6+), .NET 6+, JavaScript, TypeScript, SQL, PL/SQL, Python, Java, HTML5, CSS3 \\
                \textbf{Frameworks \& Backend:} & .NET Core, ASP.NET MVC, Entity Framework, Microservices Architecture, REST APIs, Spring Boot, Node.js \\
                \textbf{Frontend:} & Angular, React.js, Material UI, Bootstrap, Single-page Applications \\
                \textbf{Databases:} & SQL Server, Oracle, PostgreSQL, MongoDB, Redis \\
                \textbf{DevOps \& CI/CD:} & Jenkins, GitHub Actions, Docker, Kubernetes, Azure DevOps, AWS CodePipeline \\
                \textbf{Testing \& Automation:} & xUnit, NUnit, Postman, Selenium, JUnit, Mockito \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Designed and implemented \textbf{C\# with .NET 6} microservices deployed on \textbf{AWS ECS}, improving system reliability and reducing outage time by 25\%.}
        \resumeItem{Developed dynamic front-ends using \textbf{Angular} and \textbf{TypeScript}, increasing user engagement by 40\% and streamlining client workflows significantly.}
        \resumeItem{Led migration from monolithic Java application to \textbf{microservices} in \textbf{.NET Core}, reducing deployment cycles by 30\% and enhancing scalability.}
        \resumeItem{Built \textbf{REST APIs} in \textbf{C\#} with strict adherence to security and performance standards to support high-availability enterprise applications.}
        \resumeItem{Automated \textbf{CI/CD pipelines} using \textbf{Jenkins} and \textbf{Docker}, speeding up deployments by 50\% with consistent quality control and rollback capabilities.}
        \resumeItem{Optimized complex \textbf{SQL Server} queries to achieve 20\% improvement in database response times supporting critical transaction services.}
        \resumeItem{Enhanced test stability by establishing \textbf{xUnit} automated test suites, achieving over 98\% coverage and reducing production defects by 35\%.}
        \resumeItem{Integrated monitoring tools into microservices architecture to ensure 99.9\% uptime and proactive incident detection for all services.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Implemented core banking modules in \textbf{C\#} with \textbf{Entity Framework} and \textbf{Microservices}, improving transaction throughput by 30\%.}
        \resumeItem{Created responsive \textbf{Angular} front-end components, enhancing loan approval workflows and reducing user errors by 20\%.}
        \resumeItem{Streamlined integration through \textbf{RESTful APIs} leveraging \textbf{ASP.NET Core}, improving service interoperability and data exchange speed.}
        \resumeItem{Designed event-driven architecture using \textbf{Kafka} for secure, asynchronous processing of more than 10,000 transactions per second.}
        \resumeItem{Improved system observability by developing \textbf{Grafana} dashboards to monitor microservices health and performance metrics effectively.}
        \resumeItem{Established secure authentication mechanisms using \textbf{OAuth2} and \textbf{JWT} in microservices, reducing security incidents by 40\%.}
        \resumeItem{Enhanced CI/CD pipelines integrating \textbf{Jenkins} with \textbf{Git} repositories, cutting deployment time by 30\% across multiple environments.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Built and maintained scalable \textbf{C\# ASP.NET MVC} applications in supply chain domain, improving data processing and reliability by 25\%.}
        \resumeItem{Developed comprehensive \textbf{REST APIs} for system integration, increasing third-party connectivity and product capabilities by 30\%.}
        \resumeItem{Implemented automated API testing using \textbf{Postman} and \textbf{Selenium}, resulting in over 95\% test coverage and higher delivery confidence.}
        \resumeItem{Facilitated migration of legacy systems to \textbf{cloud platforms} like AWS, reducing operational costs by 20\% and enhancing scalability.}
        \resumeItem{Optimized data storage access in \textbf{SQL Server} and \textbf{Redis}, decreasing latency by 15\% and improving application responsiveness.}
        \resumeItem{Developed shell scripts to automate system health checks, reducing issue response times by 30\% and enhancing service reliability.}
        \resumeItem{Streamlined build pipelines using \textbf{GitHub Actions}, increasing deployment speed by 40\% and ensuring consistent package versioning.}
        \resumeItem{Adopted Agile and Scrum processes, reducing project delivery time by 25\% through iterative development and team collaboration.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-Driven Document QA System} | Python, LangChain, OpenAI API, C\#, .NET, Azure}{}
        \resumeItemListStart
            \resumeItem{Engineered an AI-based question-answering system integrating \textbf{.NET} backend with LangChain for natural language queries over documents.}
            \resumeItem{Implemented vector store indexing and retrieval optimizing response relevance, reducing query latency by 35\%.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Enterprise Microservices Platform} | C\#, .NET 6, Azure Kubernetes Service, SQL Server}{}
        \resumeItemListStart
            \resumeItem{Designed modular \textbf{microservices} using \textbf{.NET 6} for payment processing, boosting transaction throughput by 30\% and reducing downtime.}
            \resumeItem{Built robust \textbf{CI/CD pipeline} with Azure DevOps automating deployment and testing, cutting release cycles by 40\%.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Angular SPA for Payment Solutions} | Angular, TypeScript, REST APIs, .NET Core}{}
        \resumeItemListStart
            \resumeItem{Developed a responsive single-page application with \textbf{Angular} to manage payment products, improving user navigation and reducing errors by 25\%.}
            \resumeItem{Integrated frontend with secured \textbf{RESTful APIs} implemented in \textbf{.NET Core}, enhancing service reliability and performance.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}