\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Software engineer with 5+ years' expertise designing and developing scalable applications using \textbf{Java, JavaScript}, and \textbf{Python} across cloud-native and SAAS platforms.}
    \resumeItem{Skilled in implementing IT best practices and mentoring teams, driving complex problem-solving and project management within Agile Scrum environments.}
    \resumeItem{Proficient in key web technologies including \textbf{React.js, Angular, HTML5, CSS}, and backend frameworks like \textbf{Spring Boot}, delivering user-centric solutions.}
    \resumeItem{Experienced in API design (\textbf{REST, SOAP}), security protocols, and troubleshooting, improving system reliability and operational excellence.}
    \resumeItem{Hands-on with CI/CD pipelines, automated testing, and cloud deployments on \textbf{AWS} and \textbf{Azure}, enhancing delivery speed and quality.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, JavaScript, TypeScript, SQL, PL/SQL, HTML5, CSS3, Shell Scripting \\
                \textbf{Frameworks \& Backend:} & Spring Boot, Node.js, Express.js, Angular, React.js, .Net basics, SOAP, RESTful APIs \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, ECS, S3, API Gateway, CodePipeline), Azure, Docker, Kubernetes, Jenkins, GitHub CI/CD, Maven \\
                \textbf{Databases:} & SQL Server, PostgreSQL, Oracle, MongoDB, Redis \\
                \textbf{Testing \& Automation:} & JUnit, Mockito, Selenium, Postman, SOAP UI, Cucumber \\
                \textbf{Methodologies \& Tools:} & Agile Scrum, Rally, CI/CD, Product Backlog Management, Security Protocols, Troubleshooting \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Developed scalable microservices in \textbf{Java, Spring Boot}, and deployed on AWS cloud improving uptime by 25\% and operational efficiency.}
        \resumeItem{Implemented responsive front-end interfaces using \textbf{React.js} and \textbf{Angular}, increasing user engagement and satisfaction by over 40\%.}
        \resumeItem{Led migration from monolithic to microservices architecture, reducing deployment time by 30\% and enhancing system scalability for key business applications.}
        \resumeItem{Engineered API services with \textbf{REST} and \textbf{SOAP}, ensuring robust integrations and decreasing response times by 35\%.}
        \resumeItem{Instituted CI/CD pipelines using \textbf{Jenkins}, \textbf{Docker}, and \textbf{AWS CodePipeline}, boosting deployment frequency by 50\%.}
        \resumeItem{Mentored junior developers on IT best practices and Agile Scrum rituals, improving team velocity and sprint delivery consistency.}
        \resumeItem{Implemented security protocols and performed troubleshooting on SAAS platform reducing incident rates by 20\%, enhancing platform stability.}
        \resumeItem{Created technical documentation and communicated complex IT solutions effectively with cross-functional teams and stakeholders.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Designed core banking services using \textbf{Java} and \textbf{Spring Boot} within a microservices framework, improving transaction reliability by 30\%.}
        \resumeItem{Developed front-end components for loan processing using \textbf{React} and \textbf{Angular}, enhancing customer experience and reducing processing time by 20\%.}
        \resumeItem{Implemented Kafka-driven event architecture capable of processing 10,000+ transactions per second, boosting system throughput and fault tolerance.}
        \resumeItem{Automated configuration and integration with SAAS and cloud systems, improving deployment efficiency by over 25\% and reducing manual errors.}
        \resumeItem{Integrated security frameworks using \textbf{OAuth2} and \textbf{JWT}, lowering security incidents by 40\% and safeguarding sensitive data.}
        \resumeItem{Enhanced system observability with \textbf{Grafana} and \textbf{Prometheus} dashboards, improving real-time monitoring and problem resolution speed.}
        \resumeItem{Streamlined Agile Scrum team workflows using \textbf{Rally}, facilitating product backlog prioritization and sprint planning.}
        \resumeItem{Collaborated cross-functionally to align IT and business strategies, delivering solutions aligned with competitive market demands.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed RESTful \textbf{APIs} using \textbf{Node.js} and \textbf{Express.js} for supply chain applications, increasing integration capabilities by 30\%.}
        \resumeItem{Conducted extensive unit and integration testing with \textbf{JUnit} and \textbf{Postman}, improving application reliability to over 95\%.}
        \resumeItem{Migrated legacy systems to \textbf{AWS} cloud environment reducing infrastructure costs by 20\% and enhancing scalability.}
        \resumeItem{Optimized database access with \textbf{DynamoDB} and \textbf{SQL Server}, reducing latency by 15\% and improving application performance.}
        \resumeItem{Developed custom Linux shell scripts for system monitoring, accelerating issue detection and resolution by 30\%.}
        \resumeItem{Facilitated adoption of Agile and Scrum methodologies improving project velocity by 25\% and enhancing team collaboration.}
        \resumeItem{Established CI/CD workflows with GitHub Actions, increasing deployment speed by 40\% and reducing release errors.}
        \resumeItem{Produced product backlog items and prioritized tasks aligning with business goals, aiding smooth Agile delivery cycles.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-Driven Document Query System} | Python, LangChain, OpenAI API, FAISS, Docker}{}
        \resumeItemListStart
            \resumeItem{Built an AI portal capable of multi-PDF querying using natural language, implementing RAG to deliver contextually accurate responses with high retrieval efficiency.}
            \resumeItem{Integrated vector embeddings with Redis for similarity search, achieving fast keyword fallback with seamless user experience and enhanced document accessibility.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Cloud-Native Microservices Platform} | Java, Spring Boot, AWS, Docker}{}
        \resumeItemListStart
            \resumeItem{Developed a robust microservices platform deployed on AWS ECS using \textbf{Java} and \textbf{Spring Boot}, improving application scalability and uptime by 30\%.}
            \resumeItem{Implemented CI/CD pipelines and secure API integrations enhancing deployment frequency by 50\% and adherence to security best practices throughout the platform.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Agile Product Backlog Manager} | React.js, Node.js, Rally, REST APIs}{}
        \resumeItemListStart
            \resumeItem{Built a backlog management tool to create, prioritize, and explain product backlog items, streamlining scrum team workflows and sprint delivery effectiveness.}
            \resumeItem{Integrated Rally APIs enabling seamless synchronization and real-time updates of user stories, enhancing Agile team collaboration and project transparency.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}