\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered \textbf{robust backend services} with \textbf{Python} and \textbf{FastAPI}, building scalable APIs and microservices supporting AI-driven workloads.}
  \resumeItem{Applied best practices in API design, documentation, and maintainability to ensure high-quality, production-grade backend systems.}
  \resumeItem{Leveraged \textbf{microservices architecture} and asynchronous processing to improve scalability and reliability of distributed systems.}
  \resumeItem{Experienced in integrating AI/ML workflows into backend services, enabling data-driven and intelligent application features.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Python, FastAPI, Java (8/11/17/21), Kotlin, Go, C\#, TypeScript \\
\textbf{Backend \& API:} & REST, OpenAPI/Swagger, gRPC, Microservices, OAuth2/OIDC, JWT, mTLS \\
\textbf{Databases \& Cache:} & PostgreSQL, MySQL, Aurora, DynamoDB, MongoDB, Redis/ElastiCache \\
\textbf{Cloud \& DevOps:} & AWS (EKS, Lambda, API Gateway, S3, RDS/Aurora, DynamoDB, IAM, KMS, Secrets Manager, CloudWatch), Docker, Kubernetes, Helm, Terraform \\
\textbf{AI \& Observability:} & AI/ML integration, OpenTelemetry, CloudWatch, Prometheus, Grafana \\
\textbf{Testing \& CI/CD:} & JUnit 5, Mockito, Testcontainers, Jenkins, GitHub Actions, SonarQube, Snyk \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Designed and developed scalable backend services using \textbf{Python} and \textbf{FastAPI}, improving API response times by 30\%.}
  \resumeItem{Built and maintained microservices supporting AI-driven workflows, ensuring modularity and ease of integration.}
  \resumeItem{Implemented RESTful APIs with comprehensive OpenAPI documentation, enhancing developer onboarding and API usability.}
  \resumeItem{Integrated asynchronous processing patterns to handle high-throughput workloads, improving system reliability and scalability.}
  \resumeItem{Collaborated with AI teams to embed AI capabilities into backend services, enabling intelligent data processing pipelines.}
  \resumeItem{Automated deployment pipelines using \textbf{Docker}, \textbf{Kubernetes (EKS)}, and \textbf{Helm}, reducing release cycle times by 25\%.}
  \resumeItem{Applied security best practices including OAuth2/OIDC and JWT authentication to protect sensitive data and services.}
  \resumeItem{Monitored service health using \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling proactive issue detection and resolution.}
  \resumeItem{Led code reviews and enforced maintainability standards, improving code quality and reducing technical debt.}
  \resumeItem{Collaborated in Agile/Scrum teams to deliver features iteratively, improving cross-team communication and delivery predictability.}
  \resumeItem{\textit{Environment: Python, FastAPI, REST, OpenAPI, OAuth2/OIDC, JWT, Docker, Kubernetes (EKS), Helm, AWS (Lambda, API Gateway, S3, RDS, DynamoDB), OpenTelemetry, CloudWatch, Agile.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed backend services primarily using \textbf{Java 17} and \textbf{Kotlin}, focusing on scalable microservices architecture.}
  \resumeItem{Built and maintained RESTful APIs with OpenAPI specifications, improving API consistency and client integration.}
  \resumeItem{Implemented asynchronous event-driven processing using \textbf{Kafka}, enhancing system throughput and decoupling.}
  \resumeItem{Collaborated with AI teams to support AI-driven workloads by integrating backend services with ML pipelines.}
  \resumeItem{Containerized microservices using \textbf{Docker} and deployed on \textbf{EKS}, improving deployment efficiency and scalability.}
  \resumeItem{Provisioned cloud infrastructure using \textbf{Terraform} and \textbf{CloudFormation} for repeatable and auditable environments.}
  \resumeItem{Enhanced API security with OAuth2/OIDC and JWT, ensuring compliance with enterprise security standards.}
  \resumeItem{Implemented observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, improving monitoring and alerting capabilities.}
  \resumeItem{Developed automated tests using \textbf{JUnit 5} and \textbf{Mockito}, increasing code coverage and reducing defects.}
  \resumeItem{Contributed to CI/CD pipelines using \textbf{GitHub Actions}, accelerating deployment frequency and stability.}
  \resumeItem{\textit{Environment: Java 17, Kotlin, REST, OpenAPI, Kafka, Docker, Kubernetes (EKS), Terraform, CloudFormation, AWS (EKS, Lambda, API Gateway, DynamoDB), OpenTelemetry, CloudWatch, JUnit 5, Mockito, GitHub Actions.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8/11} and \textbf{Spring Boot 2.x}, delivering scalable and maintainable APIs.}
  \resumeItem{Built RESTful APIs with OpenAPI documentation, enforcing consistent validation and error handling standards.}
  \resumeItem{Implemented secure authentication using OAuth2/OIDC and JWT, aligning with enterprise RBAC policies.}
  \resumeItem{Integrated asynchronous processing with \textbf{Kafka}, improving reliability through retry and dead-letter queue patterns.}
  \resumeItem{Optimized database queries and caching using \textbf{Redis}, reducing latency by 25\% on critical paths.}
  \resumeItem{Containerized services with \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling environment-based configuration.}
  \resumeItem{Collaborated with AI/ML teams to support AI-driven features by providing robust backend APIs and data pipelines.}
  \resumeItem{Automated CI/CD workflows using \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing quality gates with \textbf{SonarQube}.}
  \resumeItem{Enhanced observability using \textbf{OpenTelemetry} and cloud monitoring tools across AWS, Azure, and GCP.}
  \resumeItem{Delivered frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript} to support operational workflows.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, REST, OpenAPI, OAuth2/OIDC, JWT, Kafka, Redis, Docker, Kubernetes, Jenkins, Azure DevOps, AWS/Azure/GCP, Angular, React, TypeScript, OpenTelemetry.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8} and \textbf{Spring Boot (1.5/2.0)}, delivering reusable APIs and components.}
  \resumeItem{Built and documented REST APIs using \textbf{Swagger}, improving integration consistency across teams.}
  \resumeItem{Implemented internal service endpoints using \textbf{C\#} with \textbf{.NET Framework}, supporting partner workflows.}
  \resumeItem{Delivered UI features using \textbf{Angular 5/6/7} and \textbf{React 16} with \textbf{TypeScript}, enhancing user experience.}
  \resumeItem{Optimized database performance using \textbf{Hibernate/JPA} and query tuning, improving response times.}
  \resumeItem{Standardized builds and CI pipelines using \textbf{Maven/Gradle} and \textbf{Jenkins}, improving release stability.}
  \resumeItem{Implemented containerized development and test environments using \textbf{Docker}, enabling consistent setups.}
  \resumeItem{Supported cloud deployments on \textbf{AWS (EC2, S3, RDS)}, facilitating scalable infrastructure.}
  \resumeItem{Strengthened automated testing with \textbf{JUnit} and \textbf{Mockito}, reducing post-release defects.}
  \resumeItem{Collaborated in Agile teams to deliver incremental improvements and maintain high code quality.}
  \resumeItem{\textit{Environment: Java, Spring Boot, REST, Swagger, C\#, .NET Framework, Angular, React, TypeScript, Hibernate/JPA, Docker, Jenkins, AWS (EC2, S3, RDS), JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}