\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Designed and developed scalable microservices using \textbf{Java 8+} and \textbf{Spring Boot}, applying Domain Driven Design principles to migrate monoliths effectively.}
  \resumeItem{Expert in \textbf{Spring ecosystem} including Spring Cloud, Spring Integration, and Spring Cloud Data Flow for enterprise-grade distributed applications.}
  \resumeItem{Implemented multithreading, distributed caching, and fault-tolerant logic to enhance performance and reliability of backend services.}
  \resumeItem{Built and optimized CI/CD pipelines using \textbf{Jenkins}, \textbf{Maven}, and \textbf{Git} for automated, high-quality delivery across platforms.}
  \resumeItem{Strong advocate of Object-Oriented Design and Test-Driven Development, ensuring maintainable and well-tested codebases.}
  \resumeItem{Skilled in performance tuning of distributed systems and developing comprehensive unit tests to improve system robustness.}
  \resumeItem{Excellent analytical and communication skills, collaborating effectively in Agile environments to deliver business value.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java (8/11/17), Spring Boot, Spring Cloud, Spring Integration, Spring Cloud Data Flow, JEE, Maven \\
\textbf{Backend \& Microservices:} & Domain Driven Design, Microservices Architecture, Multithreading, Distributed Caching, Fault Tolerance, REST, NoSQL \\
\textbf{CI/CD \& DevOps:} & Jenkins, Git, Maven, Docker, Kubernetes, Helm, Terraform \\
\textbf{Testing \& Quality:} & JUnit 5, Mockito, Test-Driven Development, Unit Testing, Performance Tuning \\
\textbf{Databases \& Caching:} & NoSQL, Redis, MongoDB, PostgreSQL \\
\textbf{Tools \& Methodologies:} & Agile/Scrum, Object-Oriented Design, GitHub Actions, SonarQube, Snyk \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Designed and developed microservices using \textbf{Java 17/21} and \textbf{Spring Boot 3}, applying Domain Driven Design to modularize legacy monoliths.}
  \resumeItem{Implemented secure authentication and authorization using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT} to enforce enterprise-grade access control.}
  \resumeItem{Built fault-tolerant distributed caching layers with \textbf{Redis} to reduce latency and improve read throughput by 25\%.}
  \resumeItem{Developed and maintained CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, automating builds and deployments with quality gates.}
  \resumeItem{Applied multithreading and asynchronous processing patterns to improve service responsiveness and scalability in distributed systems.}
  \resumeItem{Optimized API performance by tuning \textbf{Hibernate/JPA} queries and implementing caching strategies, resulting in 30-40\% faster response times.}
  \resumeItem{Containerized microservices with \textbf{Docker} and orchestrated deployments on \textbf{Kubernetes (EKS)} using \textbf{Helm} charts for repeatable releases.}
  \resumeItem{Integrated observability using \textbf{OpenTelemetry} and \textbf{CloudWatch} to monitor distributed application health and performance metrics.}
  \resumeItem{\textit{Environment: Java 17/21, Spring Boot 3, Spring Security, Spring Cloud, Redis, Jenkins, GitHub Actions, Docker, Kubernetes, Helm, Terraform, Hibernate/JPA.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed enterprise-grade microservices using \textbf{Java 17} and \textbf{Spring Boot}, focusing on modular design and fault tolerance.}
  \resumeItem{Designed and implemented RESTful APIs with \textbf{Spring MVC} and ensured contract consistency across services using OpenAPI specifications.}
  \resumeItem{Built and tuned distributed caching with \textbf{Redis} to reduce backend latency by 20-30\% on critical read paths.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Maven}, integrating static code analysis and security scanning tools.}
  \resumeItem{Applied multithreading and concurrent programming techniques to enhance throughput and stability of backend services.}
  \resumeItem{Implemented asynchronous event-driven processing using \textbf{Kafka} to decouple services and improve scalability.}
  \resumeItem{Provisioned infrastructure with \textbf{Terraform} and \textbf{CloudFormation} to enable repeatable and auditable deployments.}
  \resumeItem{Developed unit and integration tests using \textbf{JUnit 5} and \textbf{Mockito} to ensure code quality and reliability.}
  \resumeItem{\textit{Environment: Java 17, Spring Boot, Spring Cloud, Kafka, Redis, Jenkins, Maven, Terraform, CloudFormation, JUnit 5, Mockito.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Built and enhanced microservices using \textbf{Java 8/11} and \textbf{Spring Boot 2}, focusing on modularity and maintainability.}
  \resumeItem{Developed REST APIs with \textbf{OpenAPI/Swagger}, enforcing validation, versioning, and consistent error handling standards.}
  \resumeItem{Implemented secure access control using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT} to comply with enterprise RBAC policies.}
  \resumeItem{Optimized database access with \textbf{Hibernate/JPA} and caching using \textbf{Redis}, improving response times by 25\%.}
  \resumeItem{Automated builds and deployments using \textbf{Jenkins} and \textbf{Azure DevOps}, integrating quality gates with \textbf{SonarQube}.}
  \resumeItem{Applied multithreading and fault-tolerant design patterns to improve service resilience and scalability.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes} clusters with environment-specific configurations.}
  \resumeItem{Collaborated in Agile teams to deliver features aligned with business goals using Object-Oriented Design principles.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, Spring Security, REST, Hibernate/JPA, Redis, Jenkins, Azure DevOps, Docker, Kubernetes.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8} and \textbf{Spring Boot 2}, focusing on reusable components and clean layering.}
  \resumeItem{Built RESTful APIs and documented endpoints using \textbf{Swagger} to standardize interface contracts.}
  \resumeItem{Implemented scheduled workflows using \textbf{Spring Scheduling} and \textbf{Quartz} for reliable batch processing.}
  \resumeItem{Optimized database queries and indexing using \textbf{Hibernate/JPA} to improve application performance.}
  \resumeItem{Standardized build processes with \textbf{Maven} and implemented CI pipelines using \textbf{Jenkins} for automated testing and deployment.}
  \resumeItem{Containerized development and testing environments using \textbf{Docker} to streamline local setups.}
  \resumeItem{Supported cloud deployments on \textbf{AWS} including EC2, S3, and RDS for scalable infrastructure.}
  \resumeItem{Enhanced code quality and stability by implementing unit tests with \textbf{JUnit} and \textbf{Mockito}.}
  \resumeItem{\textit{Environment: Java 8, Spring Boot 2, REST, Swagger, Hibernate/JPA, Maven, Jenkins, Docker, AWS EC2/S3/RDS, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}