\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered scalable backend and frontend solutions with \textbf{Java} and \textbf{Spring Boot}, driving high-quality enterprise applications in cloud-native environments.}
  \resumeItem{Engineered microservices with secure authentication using \textbf{OAuth2/OIDC} and \textbf{JWT}, enhancing compliance and operational security across distributed systems.}
  \resumeItem{Implemented AI-driven workflows leveraging \textbf{Spring AI} and vector search, improving knowledge retrieval efficiency and auditability in enterprise contexts.}
  \resumeItem{Developed reactive frontends using \textbf{Angular} and \textbf{React} with state management, delivering intuitive user experiences for complex workflows.}
  \resumeItem{Orchestrated containerized deployments on \textbf{Kubernetes} with \textbf{Docker}, supporting CI/CD pipelines and observability through \textbf{OpenTelemetry} and cloud monitoring tools.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java, Spring Boot, Spring Security, Spring AI, Kotlin, Go, C\#, Angular, React, TypeScript \\
\textbf{Cloud \& DevOps:} & AWS (EKS, Lambda, S3, RDS, DynamoDB, IAM, KMS, Secrets Manager, CloudWatch), Azure (AKS, Azure AD, Key Vault), GCP (GKE, Pub/Sub, Cloud Monitoring), Docker, Kubernetes, Helm, Terraform \\
\textbf{API \& Integration:} & REST, gRPC, OpenAPI/Swagger, OAuth2/OIDC, JWT, mTLS, Kafka, AWS SQS/SNS, EventBridge \\
\textbf{Databases \& Caching:} & PostgreSQL, MySQL, Aurora, DynamoDB, MongoDB, Redis/ElastiCache \\
\textbf{Observability \& Testing:} & OpenTelemetry, CloudWatch, Prometheus, Grafana, JUnit 5, Mockito, Testcontainers, WireMock, Pact, Cypress \\
\textbf{CI/CD \& Security:} & Jenkins, GitHub Actions, Azure DevOps, SonarQube, Snyk, Secure coding and audit logging \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Designed and delivered microservices using \textbf{Java} and \textbf{Spring Boot}, improving modularity and reducing deployment risks by 35\%.}
  \resumeItem{Implemented secure authentication flows with \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT}, enhancing compliance for enterprise workflows.}
  \resumeItem{Developed GenAI-enabled productivity tools using \textbf{Spring AI} and \textbf{AWS Bedrock}, increasing knowledge retrieval speed by 40\%.}
  \resumeItem{Built responsive UI modules with \textbf{Angular} and \textbf{React}, improving user task efficiency by 25\% through state management and modular components.}
  \resumeItem{Automated asynchronous messaging using \textbf{Kafka} and \textbf{AWS SQS/SNS}, raising system reliability and throughput by 30\%.}
  \resumeItem{Optimized database queries and caching with \textbf{Redis}, reducing p95 latency by 25\% for critical read paths.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes (EKS)} with \textbf{Helm}, enabling consistent environment releases.}
  \resumeItem{Streamlined CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, enforcing quality gates with \textbf{SonarQube} and security scans via \textbf{Snyk}.}
  \resumeItem{Implemented observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, improving alert accuracy and reducing incident response time by 20\%.}
  \resumeItem{\textit{Environment: Java 17/21, Spring Boot 3, Spring Security, Spring AI, AWS Bedrock, REST, gRPC, Kafka, C\#, .NET 6, AWS (EKS, S3, RDS/Aurora, DynamoDB, SQS/SNS, IAM, KMS, Secrets Manager, CloudWatch), Docker, Kubernetes, Helm, Terraform, Angular 16/17, React, TypeScript, RxJS, NgRx, Redis, JUnit 5, Mockito, Testcontainers, Jenkins, GitHub Actions.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed scalable backend services with \textbf{Java} and \textbf{Kotlin}, improving API reliability and reducing error rates by 30\%.}
  \resumeItem{Built and maintained internal APIs using \textbf{gRPC} and \textbf{REST}, ensuring consistent contract and operational standards.}
  \resumeItem{Created performance-critical automation tools in \textbf{Go}, reducing manual operational effort by 40\%.}
  \resumeItem{Implemented event-driven architectures using \textbf{Kafka}, enhancing throughput and decoupling service dependencies.}
  \resumeItem{Optimized DynamoDB and Aurora PostgreSQL access patterns, improving query performance by 25\%.}
  \resumeItem{Reduced backend latency by 30\% through \textbf{Redis} caching for high-demand data paths.}
  \resumeItem{Managed containerized deployments on \textbf{Docker} and \textbf{EKS/ECS}, supporting zero-downtime rollouts.}
  \resumeItem{Provisioned cloud infrastructure using \textbf{Terraform} and \textbf{CloudFormation}, ensuring repeatable and auditable environments.}
  \resumeItem{Enhanced observability with \textbf{OpenTelemetry} and \textbf{CloudWatch}, reducing mean time to detect issues by 20\%.}
  \resumeItem{Implemented comprehensive testing with \textbf{JUnit 5}, \textbf{Mockito}, and contract testing using \textbf{Pact}, preventing cross-service regressions.}
  \resumeItem{Delivered frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, improving configuration workflows by 30\%.}
  \resumeItem{\textit{Environment: Java 17, Kotlin, Go, REST, gRPC, Kafka, AWS (EKS/ECS, Lambda, API Gateway, DynamoDB, Aurora, S3, SQS/SNS, IAM, KMS, Secrets Manager, CloudWatch), Docker, Kubernetes, Terraform, CloudFormation, OpenTelemetry, Angular, React, TypeScript, JUnit 5, Mockito, Testcontainers, WireMock, Pact.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, improving API scalability and reusability by 30\%.}
  \resumeItem{Designed REST APIs with \textbf{OpenAPI/Swagger}, enforcing validation and versioning standards, reducing integration issues by 25\%.}
  \resumeItem{Implemented secure access using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT}, aligning with enterprise RBAC policies.}
  \resumeItem{Built frontend modules with \textbf{Angular} and \textbf{React}, improving user engagement and workflow efficiency by 20\%.}
  \resumeItem{Implemented asynchronous processing using \textbf{Kafka}, enhancing system reliability through retry and DLQ mechanisms.}
  \resumeItem{Developed integration endpoints using \textbf{C\#} and \textbf{ASP.NET Core Web API}, enabling seamless partner workflows.}
  \resumeItem{Created batch automation utilities with \textbf{Go}, reducing manual processing time by 35\%.}
  \resumeItem{Optimized database queries and caching with \textbf{Hibernate/JPA} and \textbf{Redis}, improving response times by 25\%.}
  \resumeItem{Containerized services with \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling consistent environment management.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing quality gates with \textbf{SonarQube}.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, Spring Security, REST, OpenAPI, Angular 8--12, React, TypeScript, RxJS, NgRx, Kafka, C\#, ASP.NET Core, Go, PostgreSQL/MySQL, Hibernate/JPA, Redis, Docker, Kubernetes, Jenkins, Azure DevOps, AWS/Azure/GCP.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Delivered backend services using \textbf{Java} and \textbf{Spring Boot}, improving component reusability and system stability by 20\%.}
  \resumeItem{Built REST APIs and documented with \textbf{Swagger}, reducing integration defects by 15\%.}
  \resumeItem{Developed frontend features using \textbf{Angular} and \textbf{React}, enhancing user experience and modularity.}
  \resumeItem{Implemented scheduled workflows using \textbf{Quartz} and \textbf{Spring Scheduling}, improving batch processing reliability.}
  \resumeItem{Optimized database performance with \textbf{Hibernate/JPA} tuning and indexing, reducing query times by 20\%.}
  \resumeItem{Standardized builds and CI pipelines using \textbf{Maven/Gradle} and \textbf{Jenkins}, improving release cadence.}
  \resumeItem{Containerized development and testing environments using \textbf{Docker}, enabling consistent builds.}
  \resumeItem{Supported cloud deployments on \textbf{AWS}, improving scalability and availability.}
  \resumeItem{Enhanced automated testing with \textbf{JUnit} and \textbf{Mockito}, increasing test coverage and release stability.}
  \resumeItem{\textit{Environment: Java, Spring, JSF, JSP 2.0, AWS, Apache MyFaces, JMS, Hibernate, LDAP, JNDI, UDDI, WSDL, SOA, SOAP, UML, XML, HTML, Log4j, WebSphere, RAD, Oracle, SunOS UNIX, Shell Script, CVS, Ant, Windows XP.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

% ===== PROJECTS =====
\section{Projects}
\resumeItemListStart

\resumeProjectHeading
{\textbf{Enterprise GenAI Knowledge Assistant} | Internal Productivity Tool}{2024}
\resumeItemListStart
  \resumeItem{Developed an AI-powered assistant using \textbf{Spring AI} and \textbf{AWS Bedrock}, improving knowledge retrieval efficiency by 40\%.}
  \resumeItem{Implemented secure audit logging and PII-safe patterns to comply with enterprise data governance policies.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Microservices Platform Migration} | Cloud-Native Deployment}{2023}
\resumeItemListStart
  \resumeItem{Led migration of monolithic services to microservices using \textbf{Java} and \textbf{Spring Boot}, reducing deployment times by 50\%.}
  \resumeItem{Containerized services with \textbf{Docker} and orchestrated with \textbf{Kubernetes}, enabling scalable and resilient cloud deployments.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Real-time Event Processing System} | Distributed Messaging}{2022}
\resumeItemListStart
  \resumeItem{Designed and implemented event-driven workflows using \textbf{Kafka} and \textbf{AWS SQS/SNS}, improving throughput by 35\%.}
  \resumeItem{Developed APIs with \textbf{gRPC} and \textbf{REST} to support high-volume asynchronous processing and integration.}
\resumeItemListEnd

\resumeItemListEnd

\end{document}