\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Experienced \textbf{Senior Software Engineer} skilled in designing, developing, and maintaining high-quality software solutions using \textbf{C\#, Java, JavaScript} technologies.}
    \resumeItem{Strong foundation in \textbf{OOP}, \textbf{Agile methodologies}, and software development lifecycle, delivering scalable microservices and cloud-native applications on \textbf{AWS} and \textbf{Azure}.}
    \resumeItem{Proficient at reviewing, debugging, and optimizing software with continuous improvement focus to enhance performance and maintainability.}
    \resumeItem{Adept at mentoring junior engineers, fostering collaboration across teams, and driving best practices for sustainable software delivery.}
    \resumeItem{Committed to leveraging the latest frameworks such as \textbf{.NET Core, Spring Boot, React, and Angular} to build modern user-centric applications.}
    \resumeItem{Strong communicator and problem solver who thrives in dynamic Agile environments to achieve impactful project outcomes.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & C\#, Java (17 \& 21), JavaScript, TypeScript, SQL, Python, Shell Scripting \\
                \textbf{Frameworks \& Backend:} & .NET Core, .NET Framework, Spring Boot, Spring Cloud, Node.js, Express.js, Hibernate, JPA, OAuth2 \\
                \textbf{Frontend:} & React.js, Angular, Bootstrap, Material UI, Redux, JSON \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, ECS, S3, API Gateway, CodePipeline), Azure, Docker, Kubernetes, Jenkins, GitHub Actions, Terraform \\
                \textbf{Databases:} & SQL Server, Oracle, PostgreSQL, MongoDB, DynamoDB, Redis \\
                \textbf{Methodologies \& Tools:} & Agile (Scrum, Kanban), CI/CD, Microservices Architecture, RESTful APIs, JIRA, SonarQube \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Designed and developed microservices using \textbf{C\#}, \textbf{.NET Core}, and deployed on \textbf{AWS ECS}, improving service scalability by 30\%.}
        \resumeItem{Created dynamic user interfaces with \textbf{React.js} and \textbf{Bootstrap}, boosting customer satisfaction scores by 15\%.}
        \resumeItem{Refactored legacy monolithic applications into microservices architecture, reducing release cycles by 25\% and enhancing maintainability.}
        \resumeItem{Implemented advanced debugging techniques and diagnostics with \textbf{AWS CloudWatch} in production to reduce incident resolution times by 20\%.}
        \resumeItem{Collaborated in Agile ceremonies, facilitating sprint planning and retrospectives, achieving consistent on-time delivery of features.}
        \resumeItem{Mentored entry-level developers on \textbf{OOP}, \textbf{clean coding} principles, and Agile best practices, improving team productivity by 18\%.}
        \resumeItem{Developed and optimized SQL and NoSQL queries in \textbf{PostgreSQL} and \textbf{Redis}, enhancing data retrieval efficiency by 20\%.}
        \resumeItem{Engineered CI/CD pipelines using \textbf{Jenkins}, \textbf{Docker}, and \textbf{AWS CodePipeline}, doubling deployment frequency while ensuring stability.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Developed core banking modules with \textbf{Java} and \textbf{Spring Boot}, delivering tested microservices aligned with Agile processes to improve system reliability.}
        \resumeItem{Built interactive front-end features for financial applications using \textbf{Angular} and \textbf{Material UI}, increasing end-user engagement by 30\%.}
        \resumeItem{Automated deployment and registration systems integrating \textbf{Azure} services, reducing manual configuration efforts by 40\%.}
        \resumeItem{Implemented Kafka-based event processing supporting over 10,000 transactions per second to ensure robust real-time financial data handling.}
        \resumeItem{Created monitoring dashboards with \textbf{Grafana} and \textbf{Prometheus} for proactive system health checks, decreasing downtime by 22\%.}
        \resumeItem{Strengthened API security by integrating \textbf{JWT} and \textbf{OAuth2}, reducing vulnerabilities and potential breaches by 35\%.}
        \resumeItem{Improved CI/CD processes with \textbf{Jenkins} and \textbf{SVN}, accelerating release cycles by 30\% and improving quality assurance.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed backend services for Supply Chain Management using \textbf{Java}, \textbf{Spring MVC}, and \textbf{Hibernate}, enhancing data integrity by 25\%.}
        \resumeItem{Built and maintained RESTful services with \textbf{Node.js} and \textbf{Express.js}, increasing third-party integration efficiency by 30\%.}
        \resumeItem{Led migration of legacy systems to \textbf{AWS} cloud, reducing operational costs by 20\% while improving system scalability.}
        \resumeItem{Optimized \textbf{DynamoDB} data access patterns, lowering latency by 15\% to enhance application responsiveness.}
        \resumeItem{Automated performance monitoring using \textbf{Linux Shell} scripts, enabling faster issue detection and reducing downtime by 30\%.}
        \resumeItem{Established automated CI/CD pipelines through \textbf{GitHub Actions}, increasing deployment speed by 40\% and reliability.}
        \resumeItem{Encouraged Agile and Scrum adoption across teams, resulting in 25\% faster project delivery and improved team collaboration.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-Powered Document Query System} $|$ Python, Streamlit, LangChain, OpenAI API, FAISS}{ }
        \resumeItemListStart
            \resumeItem{Engineered a Retrieval-Augmented Generation pipeline for querying large PDF documents, improving answer accuracy through vector similarity search.}
            \resumeItem{Implemented a Docker-based deployment ensuring scalable, secure, and maintainable AI service availability across multiple environments.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Cloud-Native Microservices Platform} $|$ C\#, .NET Core, AWS ECS, PostgreSQL, Redis}{ }
        \resumeItemListStart
            \resumeItem{Designed and implemented scalable microservices using \textbf{.NET Core} deployed on \textbf{AWS ECS}, reducing latency by 30\% and improving uptime.}
            \resumeItem{Optimized data storage using \textbf{PostgreSQL} and caching with \textbf{Redis}, improving transaction throughput and system responsiveness by 25\%.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Real-Time Financial Dashboard} $|$ Java, Spring Boot, Angular, Kafka, Grafana}{ }
        \resumeItemListStart
            \resumeItem{Developed event-driven backend services with \textbf{Spring Boot} and \textbf{Kafka} for real-time financial data processing supporting 10,000+ transactions per second.}
            \resumeItem{Created dynamic front-end dashboards using \textbf{Angular} and \textbf{Grafana} for insightful performance monitoring, reducing system downtime by 20\%.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}