\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Software engineer with 5+ years building scalable Python backends and TypeScript/React frontends to deliver high-performance, user-centric solutions.}
    \resumeItem{Expert in designing, testing, and debugging microservices with FastAPI and Next.js, achieving 25\% faster response times in production environments.}
    \resumeItem{Proficient in cloud-native deployments on AWS, leveraging ECS, Lambda, and CodePipeline to enhance scalability and reduce operational costs by 20\%.}
    \resumeItem{Skilled communicator collaborating with cross-functional teams, translating complex technical concepts for stakeholders and improving project delivery by 30\%.}
    \resumeItem{Passionate about AI/LLM interfaces, implementing LangChain-based RAG workflows to enable contextual document search and drive business value.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Languages \& Frameworks:} & Python, TypeScript, React, Next.js, Node.js \\
                \textbf{Backend \& APIs:} & FastAPI, Django, GraphQL, REST \\
                \textbf{Cloud \& DevOps:} & AWS (ECS, Lambda, AppSync, CodePipeline), Docker, Jenkins, GitHub Actions \\
                \textbf{Databases \& Caching:} & PostgreSQL, Redis, DynamoDB, FAISS \\
                \textbf{Testing \& Automation:} & pytest, Jest, Postman \\
                \textbf{AI \& LLM:} & LangChain, OpenAI API, RAG \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Engineered Python microservices using FastAPI and AWS ECS to enhance system reliability, reducing downtime by 25\% and improving performance by 30\%.}
        \resumeItem{Developed React front-end components with TypeScript and Next.js to boost user engagement by 40\% and streamline e-commerce workflows.}
        \resumeItem{Migrated monolithic services to Dockerized Python microservices on AWS, cutting deployment times by 30\% and enabling a scalable, efficient architecture.}
        \resumeItem{Implemented GraphQL APIs via AWS API Gateway to reduce response latency by 35\% and decrease server load during peak traffic by 20\%.}
        \resumeItem{Established automated tests with pytest and Jest achieving over 98\% coverage, enhancing code quality and reducing critical defects by 45\%.}
        \resumeItem{Optimized PostgreSQL queries and designed Redis caching strategies to improve database performance by 20\% and reduce average query time by 50ms.}
        \resumeItem{Engineered CI/CD pipelines with Jenkins, Docker, and AWS CodePipeline to automate deployments, boosting release frequency by 50\% and reducing rollback incidents by 30\%.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Built RESTful APIs with Python Flask and PostgreSQL within microservices architecture, enabling seamless banking transactions and reducing latency by 25\%.}
        \resumeItem{Developed interactive React and TypeScript interfaces for loan applications, increasing user completion rates by 35\% and enhancing usability.}
        \resumeItem{Automated environment configuration tasks using custom Python scripts, saving 20 weekly hours and standardizing setups across 8 global development teams.}
        \resumeItem{Implemented Node.js middleware for real-time cash management, boosting transaction throughput by 30\% and ensuring data consistency under heavy loads during peak trading.}
        \resumeItem{Orchestrated Kafka event-driven processing handling 10,000+ TPS, improving system resiliency and reducing message loss by 99.9\% across financial distributed components.}
        \resumeItem{Built Grafana dashboards integrated with Prometheus monitoring to provide real-time insights, reducing incident response time by 40\% for production systems.}
        \resumeItem{Hardened API security using OAuth2 and JWT, decreasing unauthorized access incidents by 40\% and ensuring compliance with enterprise security standards.}
        \resumeItem{Streamlined CI/CD workflows with Jenkins and GitLab CI, reducing deployment time by 30\% and improving delivery consistency across multiple projects.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed high-performance supply chain APIs using Python Django and MySQL, improving data throughput by 30\% and reducing query times by 15\%.}
        \resumeItem{Built Node.js and Express REST services, integrating third-party APIs to extend functionality by 30\% and ensuring 99\% uptime over six months.}
        \resumeItem{Implemented unit and integration tests with pytest and Postman, raising application reliability to 95\% coverage and reducing defects by 35\%.}
        \resumeItem{Migrated on-premise Java applications to AWS EC2, lowering infrastructure costs by 20\%, improving scalability during peak demand and reducing downtime by 30\%.}
        \resumeItem{Optimized DynamoDB schemas and implemented Redis caching, cutting data access latency by 15\% and improving real-time application responsiveness by 20ms.}
        \resumeItem{Automated CI/CD workflows with GitHub Actions, reducing manual steps by 50\%, increasing deployment speed by 40\%, and aligning releases with sprint cycles.}
        \resumeItem{Facilitated Agile scrum practices across 3 teams, boosting on-time delivery by 25\% and improving cross-functional collaboration through standardized ceremonies.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{InsightPDF} | Python, Streamlit, LangChain, OpenAI API, FAISS, Docker, GitHub Actions}{}
        \resumeItemListStart
            \resumeItem{Developed RAG pipeline using LangChain and FAISS to index PDF embeddings, enabling contextual retrieval with 90\% accuracy under high concurrency conditions.}
            \resumeItem{Containerized application with Docker and configured GitHub Actions CI/CD, achieving automated deployments within 2 minutes and reducing integration errors by 30\%.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Real-Time Dashboard} | Next.js, TypeScript, GraphQL, Apollo Client, AWS AppSync, Tailwind, Docker}{}
        \resumeItemListStart
            \resumeItem{Developed Next.js dashboard with TypeScript and Apollo Client to visualize live financial data, reducing data-fetch latency by 40\% and enhancing UX consistency.}
            \resumeItem{Integrated GraphQL endpoints via AWS AppSync, achieving 30\% faster queries and enabling real-time financial updates for over 500 concurrent users.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Chatbot UI} | React, TypeScript, Next.js, OpenAI API, AWS Lambda, Tailwind}{}
        \resumeItemListStart
            \resumeItem{Built React and TypeScript chatbot UI in Next.js, integrating OpenAI API to deliver dynamic conversational experience, increasing customer engagement by 50\%.}
            \resumeItem{Deployed serverless backend on AWS Lambda, orchestrating API routes and caching with Redis, reducing response time by 35\% under 1000 concurrent sessions.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}