```latex
\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Software engineer with 5+ years building scalable \textbf{Android} applications, specializing in \textbf{Kotlin}, coroutines, flows, and reactive patterns.}
    \resumeItem{Expertise in \textbf{Gradle} multi-module builds, custom plugins, and efficient dependency management for large-scale mobile projects.}
    \resumeItem{Proficient in \textbf{Jetpack Compose}, CI/CD pipelines (GitHub Actions, Jenkins, Fastlane), and automated release strategies.}
    \resumeItem{Experienced in \textbf{Kotlin Multiplatform}, sharing core logic across Android and iOS, reducing duplication by up to 40\%.}
    \resumeItem{Advocate for AI-assisted development, leveraging tools like Copilot to cut boilerplate by 40\% while validating code quality.}
    \resumeItem{Strong communicator in Agile/Scrum teams, driving process improvements and aligning cross-functional stakeholders in high-growth environments.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Kotlin, Java, Swift \\
                \textbf{Frameworks \& SDKs:} & Android SDK, Jetpack Compose, Kotlin Multiplatform, Coroutines, Flows, LiveData \\
                \textbf{Build \& CI/CD:} & Gradle (Multi-module, Custom Plugins), GitHub Actions, Jenkins, Fastlane \\
                \textbf{Testing \& QA:} & Espresso, JUnit, Mockito \\
                \textbf{Tools \& AI Integration:} & Copilot, Cursor, Claude Code \\
                \textbf{Methodologies \& Patterns:} & Agile (Scrum/Kanban), Reactive Programming, Asynchronous Processing \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Engineered cross-platform business logic using \textbf{Kotlin Multiplatform} and \textbf{coroutines}, reducing code duplication by 35\% and improving shareability across Android and iOS.}
        \resumeItem{Developed feature-rich Android modules with \textbf{Jetpack Compose} and \textbf{flows}, enhancing UI responsiveness and reducing rendering latency by 25\% in high-load scenarios.}
        \resumeItem{Implemented \textbf{Gradle} multi-module build system and custom plugins, optimizing build times by 40\% and streamlining dependency management across 5+ modules.}
        \resumeItem{Integrated \textbf{CI/CD} pipelines with GitHub Actions and \textbf{Fastlane}, automating SDK versioning and reducing mobile release cycles by 50\% while improving deployment consistency.}
        \resumeItem{Established reactive data processing using \textbf{flows} and \textbf{coroutines}, handling asynchronous network requests with 99\% success rate and improving throughput by 30\%.}
        \resumeItem{Leveraged \textbf{AI tools} like Copilot and Cursor to generate boilerplate code, reducing development time by 40\% and improving code accuracy.}
        \resumeItem{Collaborated with cross-functional teams to refine architecture and introduced process enhancements, increasing sprint delivery efficiency by 25\% in SCRUM environment.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented \textbf{Kotlin}-based Android features with \textbf{coroutines}, improving app startup time by 30\% and enhancing battery efficiency on client devices.}
        \resumeItem{Configured \textbf{Gradle} multi-module project and custom scripts to support modular Android development, reducing build failures by 35\% and improving team productivity.}
        \resumeItem{Optimized asynchronous data streams using \textbf{flows} and \textbf{coroutines}, increasing data processing throughput by 25\% and reducing UI thread blocking incidents.}
        \resumeItem{Integrated automated UI testing with \textbf{Espresso} and \textbf{JUnit}, achieving 90\% test coverage and catching regressions 40\% faster during iterative releases.}
        \resumeItem{Implemented CI/CD pipelines with \textbf{Jenkins} and \textbf{Fastlane}, automating Android app distribution and reducing manual release errors by 50\% while improving traceability across builds.}
        \resumeItem{Led migration of core modules to \textbf{Kotlin Multiplatform}, sharing 60\% common code between Android and iOS clients, accelerating feature parity.}
        \resumeItem{Mentored 4 junior engineers on \textbf{coroutines} and \textbf{flows}, reducing debugging time by 30\% and fostering stronger cross-functional collaboration while enhancing team knowledge retention.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed native Android features using \textbf{Kotlin} and \textbf{coroutines}, reducing app crashes by 25\% and improving user retention by 15\% across monthly active users.}
        \resumeItem{Implemented reactive inventory updates with \textbf{flows} and \textbf{LiveData}, ensuring 95\% data consistency and reducing sync delays by 30\% across clients.}
        \resumeItem{Configured \textbf{Gradle} build scripts and managed dependencies for multi-module Android project, accelerating build stability by 35\% and reducing errors while improving team adoption rates.}
        \resumeItem{Collaborated on Scrum ceremonies with cross-functional stakeholders to prioritize Android features, shortening sprint planning by 20\% and boosting delivery accuracy by 30\%.}
        \resumeItem{Utilized \textbf{CI/CD} pipelines with \textbf{CircleCI}, automating APK deployments and cutting release preparation time by 40\% while ensuring consistent artifact signing across environments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-Driven Android Code Generator} | Kotlin, Copilot, Cursor, coroutines, flows}{}
        \resumeItemListStart
            \resumeItem{Developed AI-assisted Android code generator using Copilot and custom prompts to reduce boilerplate by 45\% and maintain Kotlin best practices.}
            \resumeItem{Integrated automated validation tests, detecting 90\% common pitfalls in AI-generated code, accelerating review cycles by 30\% and reducing production defects.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Cross-Platform Business Logic Library} | Kotlin Multiplatform, Gradle, Coroutines, Flows}{}
        \resumeItemListStart
            \resumeItem{Crafted a shared business logic library in Kotlin Multiplatform and Gradle, reducing Android and iOS code duplication by 60\% and accelerating feature rollout.}
            \resumeItem{Configured multi-module Gradle scripts and custom plugins to streamline multiplatform dependency management, cutting build times by 35\% and improving CI consistency.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Compose UI Component Library} | Kotlin, Jetpack Compose, Material Design}{}
        \resumeItemListStart
            \resumeItem{Designed and implemented reusable Jetpack Compose UI components with Material Design, reducing UI development time by 40\% and ensuring consistent branding.}
            \resumeItem{Integrated snapshot testing and UI automation, detecting 85\% UI regressions before release, enhancing visual stability by 30\% across 10+ modules.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}
```