\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Software engineer with 5+ years building backend systems focused on \textbf{Java} and \textbf{Spring Boot} for scalable microservices.}
    \resumeItem{Experienced designing cloud-native applications on \textbf{AWS}, optimizing cost and performance using \textbf{EKS}, \textbf{EC2}, and managed services.}
    \resumeItem{Skilled in RESTful API design, relational databases (Aurora/MySQL, PostgreSQL), secure authentication, and high-throughput data connectivity.}
    \resumeItem{Practiced with infrastructure automation, \textbf{Terraform}, CI/CD pipelines, container orchestration, and observability to improve reliability and delivery cadence.}
    \resumeItem{Applied AI techniques like RAG, embeddings, and vector indexing to enhance search and data-driven features with measurable relevance improvements.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java (17 \& 21), Python, JavaScript, TypeScript, SQL, Shell Scripting, Go, Kotlin \\
                \textbf{Frameworks \& Backend:} & Spring Boot, Spring Cloud, RESTful APIs, gRPC, Node.js, Express.js, Hibernate, JPA \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, ECS, EKS, S3, API Gateway), Terraform, Docker, Kubernetes, Jenkins, CI/CD \\
                \textbf{Databases:} & Aurora/MySQL, PostgreSQL, Redis, DynamoDB, MongoDB, vector databases (FAISS/Redis vectors) \\
                \textbf{Testing \& Observability:} & JUnit, Mockito, Postman, Prometheus, Grafana, AppDynamics, Splunk \\
                \textbf{AI \& ML:} & RAG pipelines, embeddings, LangChain, OpenAI APIs, FAISS, model orchestration \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Developed secure RESTful microservices in \textbf{Java} and \textbf{Spring Boot}, improving throughput and reducing response times by 30\% under peak load periods.}
        \resumeItem{Implemented data connectivity solutions using \textbf{AWS} services and optimized queries in \textbf{PostgreSQL}, reducing latency by 20\% across critical pipelines consistently.}
        \resumeItem{Led migration of monolith components to containerized \textbf{Kubernetes} deployments, leveraging \textbf{EKS} and \textbf{Docker}, cutting deployment time by 40\% and rollback complexity.}
        \resumeItem{Built CI/CD pipelines with \textbf{Jenkins} and \textbf{AWS CodePipeline}, automating tests and deployments, increasing release frequency by 50\% while improving stability and traceability.}
        \resumeItem{Designed RAG pipeline using embeddings and \textbf{Redis} vector indexing for semantic search, improving FAQ answer relevance by 35\% during high-traffic periods.}
        \resumeItem{Authored unit and integration tests with \textbf{JUnit} and \textbf{Mockito}, raising automated coverage to 98\% and reducing production defects by 25\% annually.}
        \resumeItem{Collaborated with cross-functional teams to define APIs using \textbf{GraphQL} and \textbf{API Gateway}, reducing average request payload by 35\% and cost by 20\%.}
        \resumeItem{Monitored production with \textbf{Grafana} and \textbf{AppDynamics}, identifying bottlenecks and improving incident MTTR by 40\% across distributed services during peak usage.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Developed core banking microservices using \textbf{Java} and \textbf{Spring Boot}, improving transaction throughput by 30\% and system reliability by 25\% overall annually.}
        \resumeItem{Implemented event-driven architecture with \textbf{Kafka}, handling 10,000+ transactions per second and improving scalability and fault tolerance by 40\% during peak load.}
        \resumeItem{Automated environment provisioning with \textbf{Terraform}, reducing setup time by 70\% and standardizing deployments across teams by 50\% within multiple regions consistently.}
        \resumeItem{Optimized SQL queries in \textbf{MySQL} and \textbf{Oracle}, decreasing average query time by 20\% and improving report generation by 30\% for monthly audits.}
        \resumeItem{Implemented secure authentication using \textbf{OAuth2} and \textbf{JWT}, reducing security incidents by 40\% and strengthening access controls company-wide within core systems.}
        \resumeItem{Built real-time dashboards with \textbf{Prometheus} and \textbf{Grafana}, enabling proactive monitoring and reducing mean detection time by 45\% across critical services consistently.}
        \resumeItem{Developed \textbf{Node.js} middleware for cash position systems, improving real-time processing speed by 30\% and reducing reconciliation errors by 25\% monthly operations.}
        \resumeItem{Enhanced CI/CD using \textbf{Jenkins} and Git integration, shortening deployment cycles by 30\% and decreasing rollback frequency by 35\% across microservices teams.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Implemented high-performance supply chain APIs using \textbf{Java} and \textbf{Spring MVC}, reducing processing latency by 25\% and increasing throughput by 30\% for batch jobs.}
        \resumeItem{Built RESTful services with \textbf{Node.js} and \textbf{Express.js}, integrating third-party APIs and expanding platform capabilities by 30\% within deployment timelines successfully.}
        \resumeItem{Migrated legacy systems to \textbf{AWS} infrastructure, cutting operational costs by 20\% and improving availability across core services by 25\% during migration.}
        \resumeItem{Optimized \textbf{DynamoDB} data models and indexes, reducing data access latency by 15\% and improving query efficiency for large datasets consistently.}
        \resumeItem{Automated system monitoring with Linux shell scripts, detecting anomalies and reducing mean time to detect incidents by 30\% during business hours.}
        \resumeItem{Implemented comprehensive tests using \textbf{JUnit} and Postman, increasing test coverage to 95\% and decreasing regression defects by 35\% across services reliably.}
        \resumeItem{Streamlined CI/CD workflows through \textbf{Jenkins}, increasing deployment frequency by 40\% and reducing manual errors by 30\% for multiple services in production.}
        \resumeItem{Collaborated within Agile teams to deliver features using \textbf{Scrum}, improving delivery predictability and reducing sprint spillover by 25\% quarterly across teams.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{InsightPDF} $|$ Python, LangChain, OpenAI API, FAISS, Docker, AWS}{ }
        \resumeItemListStart
            \resumeItem{Developed RAG pipeline using embeddings and \textbf{FAISS}, enabling semantic search across PDFs and improving answer relevance by 40\% for user queries.}
            \resumeItem{Containerized application with \textbf{Docker} and deployed on AWS, reducing cold-start times and increasing concurrent usage capacity by 50\% during spikes consistently.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{SecurBank} $|$ Go, PostgreSQL, Redis, Docker, Kubernetes, AWS}{ }
        \resumeItemListStart
            \resumeItem{Built secure backend services in \textbf{Go}, integrating \textbf{PostgreSQL} and \textbf{Redis}, improving transaction throughput by 25\% and reducing latency by 20\% under load.}
            \resumeItem{Deployed microservices to \textbf{Kubernetes} with CI/CD automation, increasing availability by 30\% and cutting deployment time by 40\% across multi-AZ regions reliably.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Real-time Graph Analytics} $|$ Apache Kafka, Neo4j, Kubernetes, Java}{ }
        \resumeItemListStart
            \resumeItem{Designed stream processing pipelines with \textbf{Kafka} and \textbf{Neo4j}, processing 1000+ concurrent events and improving query latency by 35\% during peaks reliably.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}