\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{\textbf{Python}-focused software engineer with 5+ years building cloud-native microservices and containerized platforms using Kubernetes and Docker.}
    \resumeItem{Implemented CI/CD, observability, and lightweight model-serving components to accelerate deployments and improve production reliability across services.}
    \resumeItem{Built retrieval and RAG-style pipelines and applied basic ML concepts for inference lifecycle management and model-serving validation.}
    \resumeItem{Collaborative communicator passionate about ML/AI infrastructure, distributed systems, and continuous learning to support model serving and platform engineering.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, Go, Java, JavaScript, TypeScript, Shell Scripting, SQL, C++ \\
                \textbf{Cloud \& DevOps:} & Kubernetes, Docker, AWS (ECS, EC2, S3), Terraform, Jenkins, GitHub Actions \\
                \textbf{ML \& Model Serving:} & TensorFlow Serving, PyTorch, RAG pipelines, embeddings, LangChain, model deployment basics \\
                \textbf{Observability \& Monitoring:} & Prometheus, Grafana, Splunk, AppDynamics, logging and alerting practices \\
                \textbf{Databases \& Caching:} & PostgreSQL, Redis, DynamoDB, MongoDB \\
                \textbf{Frameworks \& Backend:} & Spring Boot, Node.js, Gin, Express.js, REST, gRPC \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Implemented scalable microservices in \textbf{Java} and \textbf{Python} on \textbf{AWS ECS}, improving uptime by 25\% and reducing latency during peak traffic.}
        \resumeItem{Designed and deployed containerized applications with \textbf{Kubernetes} and \textbf{Docker}, decreasing deployment time by 30\% and increasing release frequency by 50\%.}
        \resumeItem{Implemented RAG-based \textbf{ML} retrieval using \textbf{Python} and \textbf{Redis} embeddings, improving answer relevance by 40\% and reducing search latency across services.}
        \resumeItem{Built CI/CD pipelines with \textbf{Jenkins}, \textbf{Docker}, and \textbf{Kubernetes}, increasing deployment reliability by 35\% and decreasing rollbacks by 20\% annually across teams.}
        \resumeItem{Optimized PostgreSQL queries and data models, collaborating with engineers using \textbf{Python} to reduce latency by 20\% and improve throughput system-wide.}
        \resumeItem{Led migration from monolith to microservices using \textbf{Spring Boot}, \textbf{Docker}, and \textbf{Kubernetes}, reducing deployment duration by 30\% across multiple teams to improve scalability.}
        \resumeItem{Implemented observability with \textbf{Prometheus} and \textbf{Grafana}, enabling real-time alerts and decreasing mean time to detect incidents by 40\% system-wide monthly.}
        \resumeItem{Mentored engineers on \textbf{Python}, \textbf{Kubernetes}, and \textbf{Go}, improving team productivity by 25\% and reducing onboarding time by 30\% quarterly for new hires.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Developed backend services using \textbf{Java} and \textbf{Python}, improving transaction throughput by 30\% and enhancing system reliability across modules through automated testing.}
        \resumeItem{Implemented Kafka-based event pipeline handling 10,000 TPS using \textbf{Kafka} and \textbf{Java}, reducing processing latency by 25\% across services and improving resilience.}
        \resumeItem{Automated configuration tasks with \textbf{Python} scripts, saving 20 hours weekly and accelerating environment provisioning for development teams company-wide per sprint.}
        \resumeItem{Built Grafana dashboards with \textbf{Prometheus}, improving observability and reducing incident detection time by 35\% across production systems company-wide per quarter.}
        \resumeItem{Implemented OAuth2 and JWT security for services using \textbf{Spring Boot}, decreasing security incidents by 40\% and strengthening access controls across modules.}
        \resumeItem{Enhanced CI/CD with \textbf{Jenkins} and \textbf{Docker}, reducing deployment time by 30\% and increasing release cadence for multiple teams improving stability.}
        \resumeItem{Optimized caching using \textbf{Redis}, decreasing data access latency by 15\% and improving request throughput during peak usage system-wide consistently daily.}
        \resumeItem{Facilitated Agile practices and code reviews, mentoring teams to improve delivery velocity by 25\% and reduce post-release defects by 20\%.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Implemented high-performance Java applications using \textbf{Spring MVC} and \textbf{Hibernate}, improving data processing throughput by 20\% across services consistently for clients monthly.}
        \resumeItem{Built RESTful APIs with \textbf{Node.js} and \textbf{Express.js}, expanding third-party integrations and increasing API reliability by 30\% across consumers monthly significantly.}
        \resumeItem{Implemented testing strategies using \textbf{JUnit} and \textbf{Postman}, increasing test coverage to 95\% and reducing production defects by 30\% quarterly system-wide.}
        \resumeItem{Migrated legacy components to \textbf{AWS}, reducing operational costs by 20\% and improving scalability for peak workloads across applications company-wide effectively.}
        \resumeItem{Optimized DynamoDB access patterns, reducing data access latency by 15\% and improving application responsiveness for end users system-wide consistently daily.}
        \resumeItem{Developed Linux Shell scripts for real-time monitoring, decreasing response time to incidents by 30\% and improving operational visibility across stacks company-wide.}
        \resumeItem{Streamlined CI/CD workflows using \textbf{GitHub Actions}, increasing deployment speed by 40\% and reducing manual steps during releases per sprint consistently company-wide.}
        \resumeItem{Facilitated Agile and Scrum adoption, improving project delivery time by 25\% and increasing team predictability and velocity quarterly measures consistently.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{InsightPDF} $|$ Python, Streamlit, LangChain, OpenAI API, FAISS, Docker, GitHub Actions}{ }
        \resumeItemListStart
            \resumeItem{Developed a RAG pipeline using Python, LangChain, FAISS, and OpenAI API, enabling multi-PDF QA with 95\% contextual answer relevance system-wide.}
            \resumeItem{Containerized and deployed the app with Docker and GitHub Actions, reducing deployment time by 40\% to 99\% and improving availability.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Model Serving Platform} $|$ Python, Kubernetes, Docker, TensorFlow Serving, Prometheus}{ }
        \resumeItemListStart
            \resumeItem{Built model-serving platform using Python and TensorFlow Serving on Kubernetes, achieving 50\% faster inference and 30\% improved scaling under load.}
            \resumeItem{Instrumented monitoring with Prometheus and Grafana, enabling SLA tracking and reducing mean time to recovery by 25\% monthly.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{SecurBank} $|$ Go, Gin, PostgreSQL, JWT, PASETO, Docker, Kubernetes, AWS, Redis, GitHub Actions}{ }
        \resumeItemListStart
            \resumeItem{Developed secure backend in Go and Gin with PostgreSQL, implementing JWT/PASETO and improving authentication throughput by 30\% system-wide consistently monthly.}
            \resumeItem{Deployed service with Docker and Kubernetes on AWS, enabling autoscaling and reducing downtime by 30\% while improving deployment speed significantly.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}