```latex
\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Software engineer specializing in ML infrastructure, designing Python and Go components to streamline model serving pipelines and optimize resource allocation.}
    \resumeItem{Experienced in implementing and maintaining Kubernetes deployments and Docker containerization for scalable, reliable ML inference across production environments.}
    \resumeItem{Proficient in developing automation tools and CI/CD workflows that accelerate ML model deployments, improve operational efficiency, and reduce manual errors.}
    \resumeItem{Skilled in building monitoring and logging solutions using Prometheus and Grafana to track model performance metrics and maintain system reliability.}
    \resumeItem{Adept at collaborating with cross-functional teams to drive technical discussions, adopt best practices, and balance performance optimization with robust infrastructure design.}
    \resumeItem{Familiar with distributed systems concepts and basic machine learning principles, actively learning emerging practices to support AI-driven workloads.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, Go, Shell Scripting, Bash \\
                \textbf{Containerization \& Orchestration:} & Docker, Kubernetes, Helm \\
                \textbf{Infrastructure \& Automation:} & Terraform, Jenkins, GitHub Actions, Ansible \\
                \textbf{Monitoring \& Logging:} & Prometheus, Grafana, Splunk \\
                \textbf{Cloud Platforms:} & AWS, Azure \\
                \textbf{ML \& Orchestration:} & LangChain, OpenAI API, RAG, Scikit-learn \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Developed and maintained \textbf{Go}-based microservices for ML inference pipelines, deploying via \textbf{Kubernetes} clusters, improving deployment reliability by 30\% and reducing rollbacks by 40\%.}
        \resumeItem{Implemented Python scripts to automate ML model packaging and containerization, accelerating deployment workflows by 50\% and reducing manual errors by 25\%.}
        \resumeItem{Engineered resource management modules using \textbf{Go} and Kubernetes custom controllers to optimize CPU and memory usage, reducing idle compute resources by 35\% monthly.}
        \resumeItem{Built monitoring dashboards with \textbf{Prometheus} and \textbf{Grafana} to track model performance metrics in real time, enabling 40\% faster anomaly detection and response.}
        \resumeItem{Collaborated with cross-functional teams to integrate CI/CD pipelines using Jenkins and \textbf{Docker}, deploying ML models seamlessly, increasing deployment frequency by 45\%.}
        \resumeItem{Participated in technical discussions to refine infrastructure best practices, documenting Kubernetes operators and Python-based tooling, improving team efficiency by 20\%.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Developed Kubernetes deployment manifests and Helm charts for containerized services, standardizing model serving infrastructure, reducing configuration errors by 30\% across environments.}
        \resumeItem{Implemented Python-based automation scripts for ML model deployment workflows, cutting manual deployment time by 60\% and increasing throughput by 25\%.}
        \resumeItem{Designed distributed inference orchestration using \textbf{Go} microservices and Kafka integration, handling over 5,000 model predictions per hour with 99.9\% uptime.}
        \resumeItem{Built centralized monitoring systems with \textbf{Prometheus} and \textbf{Grafana}, capturing infrastructure metrics and alerts, significantly decreasing mean-time-to-detect anomalies by 45\% across systems.}
        \resumeItem{Engineered resource scheduling solutions using Kubernetes operators and custom Python controllers, optimizing node utilization and reducing costs by 20\% system-wide.}
        \resumeItem{Collaborated with cross-functional teams to document infrastructure best practices, creating CI/CD pipeline templates to consistently accelerate deployments by 35\% across projects.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Implemented containerization strategy using Docker and Kubernetes in Minikube, reducing environment inconsistencies by 50\% and deployment times by 40\% company-wide.}
        \resumeItem{Developed Go-based RESTful APIs for model serving integration, achieving 98\% uptime and processing over 2,000 requests per hour with consistent latency under 200ms.}
        \resumeItem{Developed Prometheus exporters in Python to monitor container metrics, triggering alerts 30\% faster and reducing incident resolution time by 25\%.}
        \resumeItem{Automated infrastructure provisioning using Terraform and Python scripts, decreasing setup time by 60\% and improving reproducibility across environments by 35\%.}
        \resumeItem{Orchestrated distributed message queues using Apache Kafka and Go consumers, processing over 10,000 events daily with less than 1\% message loss.}
        \resumeItem{Documented infrastructure processes and trained team on Kubernetes best practices, improving deployment efficiency by 20\% and reducing onboarding time by 25\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{InferenceFlow} | Python, Go, Kubernetes, Docker}{}
        \resumeItemListStart
            \resumeItem{Built orchestration layer in Python to manage model deployments across Kubernetes clusters, reducing deployment failures by 40\% and standardizing workflows.}
            \resumeItem{Developed Go-based custom Kubernetes operator for dynamic resource allocation, optimizing GPU utilization by 30\% and improving inference throughput by 25\%.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{AutoScaleML} | Python, Kubernetes, Prometheus, Grafana}{}
        \resumeItemListStart
            \resumeItem{Created Python controllers to implement auto-scaling policies for ML workloads, reducing resource wastage by 35\% and ensuring 99\% SLA compliance.}
            \resumeItem{Integrated Prometheus metrics with Grafana dashboards to visualize model latency and resource usage, enabling 50\% faster troubleshooting and capacity planning.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{DocQueryAI} | Python, LangChain, OpenAI API}{}
        \resumeItemListStart
            \resumeItem{Developed RAG pipeline using LangChain and OpenAI API with FAISS to answer user queries from documents, achieving 90\% answer accuracy.}
            \resumeItem{Containerized the application with Docker and implemented GitHub Actions CI/CD, reducing build-to-deploy time by 60\% across environments and eliminating manual errors.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}
```