\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[usenames,dvipsnames]{color}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{ML infrastructure engineer proficient in Python and Go, designing scalable inference platforms for production environments.}
    \resumeItem{Experienced in containerization and orchestration with Kubernetes to automate model deployment workflows.}
    \resumeItem{Skilled in developing monitoring solutions for ML performance metrics, enabling proactive anomaly detection.}
    \resumeItem{Adept at infrastructure automation using Terraform and CI/CD pipelines to accelerate and stabilize deployments.}
    \resumeItem{Focused on resource management strategies to optimize CPU/GPU utilization and reduce operational costs.}
    \resumeItem{Collaborative team player committed to balancing performance with reliability in distributed systems.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
    \vspace{-14pt}
    \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
        \textbf{Programming \& Scripting:} & Python, Go, Shell Scripting \\
        \textbf{Containerization \& Orchestration:} & Docker, Kubernetes, Helm \\
        \textbf{Infrastructure as Code:} & Terraform, Jenkins \\
        \textbf{Monitoring \& Logging:} & Prometheus, Grafana, Alertmanager \\
        \textbf{Cloud Platforms:} & AWS (EKS, EC2, S3) \\
        \textbf{Machine Learning Concepts:} & Model Serving, Inference Pipelines \\
    \end{tabular}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Engineered Kubernetes deployments with Helm and \textbf{Go} operators to streamline ML model serving across multi-cluster environments, reducing deployment failures by 30\%.}
        \resumeItem{Developed Python CLI tools to automate ML inference workflows and container orchestration, accelerating model rollout by 40\% while ensuring consistent environment configurations.}
        \resumeItem{Implemented scalable inference orchestration layer in \textbf{Python} and \textbf{Go}, coordinating containerized services across Kubernetes clusters to maintain 99.9\% uptime for production workloads.}
        \resumeItem{Built end-to-end monitoring pipelines with Prometheus, Grafana, and Alertmanager for ML performance metrics, enabling 25\% faster anomaly detection and proactive resolution.}
        \resumeItem{Designed Python-based resource management algorithms to optimize CPU and GPU allocation across Kubernetes nodes, reducing ML infrastructure costs by 20\% during peak utilization.}
        \resumeItem{Automated infrastructure provisioning and CI/CD pipelines using Jenkins, Terraform, and Kubernetes, decreasing model deployment time by 50\% and improving system reliability.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Implemented Kubernetes-based container deployments with Docker and Helm for microservices, improving application scalability by 30\% and ensuring consistent production rollouts.}
        \resumeItem{Developed Python automation scripts for infrastructure provisioning and configuration, reducing manual deployment time by 40\% and eliminating environment drift errors.}
        \resumeItem{Configured monitoring stacks with Prometheus, Grafana, and Alertmanager to track service metrics, enabling 20\% faster incident response and improved system availability.}
        \resumeItem{Implemented Go-based resource management tools to balance CPU and memory utilization across Kubernetes clusters, reducing infrastructure costs by 15\% under peak workloads.}
        \resumeItem{Automated CI/CD workflows with Jenkins, Docker, and Kubernetes, accelerating release frequency by 50\% while decreasing deployment failures by 25\% across environments.}
        \resumeItem{Collaborated with engineering teams to design ML inference patterns, leveraging Docker and Kubernetes for reliable model deployments and achieving 99\% service uptime.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Implemented Docker containerization for backend services across multiple environments, reducing deployment inconsistencies by 30\% and streamlining microservice workflows and improving team productivity.}
        \resumeItem{Developed Python scripts to automate server configuration and log rotation, decreasing manual intervention time by 50\% and preventing unplanned downtime.}
        \resumeItem{Designed lightweight monitoring solution with Prometheus and Grafana to identify performance bottlenecks across services, reducing mean time to resolution by 20\%.}
        \resumeItem{Created real-time alerting pipelines using Alertmanager and custom \textbf{Go} utilities, improving incident response times by 25\% across distributed environments and optimizing reliability.}
        \resumeItem{Streamlined CI/CD processes with Jenkins and Docker, accelerating deployment cycles by 40\% across staging and production and minimizing rollback incidents by 30\%.}
        \resumeItem{Collaborated in Agile teams to integrate container platforms and infrastructure-as-code, reducing environment setup time by 35\% across development pipelines and enhancing deployment reliability.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{ML Inference Orchestrator} | Python, Kubernetes, Go, Docker, Prometheus, Grafana}{}
        \resumeItemListStart
            \resumeItem{Developed Python microservice to orchestrate model deployments on Kubernetes, automating rollout strategies and achieving 95\% deployment success rate in production.}
            \resumeItem{Implemented Go-based health-check probes integrated with Prometheus, reducing missing inference metrics by 30\% and improving system reliability during peak load.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Auto-Scaling ML Serving Platform} | AWS, Terraform, Docker, Go, Python, Kubernetes}{}
        \resumeItemListStart
            \resumeItem{Designed Terraform modules to provision Kubernetes clusters on AWS for ML serving, reducing cluster setup time by 60\% and lowering configuration drift.}
            \resumeItem{Developed Go and Python scripts for autoscaling based on real-time metrics, optimizing resource usage and cutting cloud costs by 25\% under demand spikes.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{DocumentQA} | Python, LangChain, OpenAI API, Docker, Kubernetes}{}
        \resumeItemListStart
            \resumeItem{Built Python-based RAG pipeline using LangChain and OpenAI API to enable document question answering, delivering 20\% faster response times on large PDF collections.}
            \resumeItem{Containerized the service with Docker and Kubernetes, ensuring 99\% uptime and facilitating seamless horizontal scaling for concurrent user queries in production.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}