\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Expertise in designing C\# microservices and RESTful APIs using .NET Core, adhering to SOLID principles and design patterns for robust architecture.}
    \resumeItem{Skilled in writing TSQL and optimizing SQL Server queries, achieving 20\% faster data retrieval and ensuring data integrity across transactional systems.}
    \resumeItem{Hands-on experience with containerization using Docker and Kubernetes, deploying .NET Core services on AWS to achieve 99\% uptime and scalability.}
    \resumeItem{Proficient in developing and consuming APIs with best practices, integrating with Kafka and AWS SQS for event-driven architectures and real-time data processing.}
    \resumeItem{Practiced Agile methodologies with cross-functional teams, building CI/CD pipelines via Jenkins and GitHub Actions to accelerate deployments by 50\%.}
    \resumeItem{Committed to quality through unit testing with xUnit and Moq frameworks, reaching 98\% code coverage and reducing production defects by 35\%.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Frameworks:} & C\# .NET Core, Java, Python, JavaScript, TypeScript, Spring Boot, Node.js, React.js \\
                \textbf{Web \& API Design:} & RESTful APIs, GraphQL, gRPC \\
                \textbf{Databases:} & SQL Server, T-SQL, PostgreSQL, MongoDB, DynamoDB \\
                \textbf{Cloud \& DevOps:} & AWS (ECS, SQS, SNS, API Gateway), Docker, Kubernetes, Jenkins, GitHub Actions \\
                \textbf{Messaging \& Streaming:} & Kafka, Kinesis \\
                \textbf{Testing \& Methodologies:} & xUnit, Moq, JUnit, Mockito, Agile (Scrum) \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Architected microservices using \textbf{C\# .NET Core} and \textbf{Spring Boot} to improve scalability by 30\% and reduce response latency by 25\%.}
        \resumeItem{Developed RESTful APIs in \textbf{.NET Core} and \textbf{Node.js} to enable external integrations, improving response efficiency by 40\% and maintaining 99\% uptime.}
        \resumeItem{Optimized \textbf{SQL Server} TSQL queries to reduce execution times by 20\% and enhance high-volume transaction throughput across microservices.}
        \resumeItem{Integrated containerization using \textbf{Docker} and \textbf{AWS ECS}, deploying microservices with 99\% reliability and automating builds via \textbf{Jenkins} pipelines.}
        \resumeItem{Implemented automated unit tests with \textbf{xUnit} and \textbf{Moq}, achieving 98\% code coverage and reducing post-release defects by 35\%.}
        \resumeItem{Led adoption of \textbf{Agile} Scrum ceremonies and continuous feedback loops, increasing team velocity by 25\% and improving cross-functional collaboration.}
        \resumeItem{Engineered event-driven pipelines using \textbf{Kafka} and \textbf{AWS SNS}, processing 10,000+ messages per second with 98\% throughput reliability.}
        \resumeItem{Collaborated with stakeholders to design PCI-compliant payment microservices, leveraging \textbf{.NET Core} and \textbf{AWS KMS} to secure transactions with 100\% audit compliance.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Modernized loan application platform using \textbf{C\# .NET Core} and \textbf{React.js}, reducing average page load times by 35\% and enhancing user satisfaction.}
        \resumeItem{Engineered RESTful APIs with \textbf{Node.js} and \textbf{Express.js}, integrating external services to achieve 40\% faster data synchronization across core systems.}
        \resumeItem{Optimized SQL queries using \textbf{TSQL}, reducing report generation time by 50\% and improving data accuracy for regulatory compliance.}
        \resumeItem{Designed event-driven architecture with \textbf{Kafka} and \textbf{AWS SQS}, handling 15,000 messages per second with 99\% delivery reliability.}
        \resumeItem{Implemented container orchestration using \textbf{Docker} and \textbf{Kubernetes}, reducing deployment variance by 45\% and streamlining environment consistency.}
        \resumeItem{Developed automated unit tests with \textbf{xUnit} and \textbf{Moq}, increasing test coverage to 95\% and reducing critical bugs by 40\%.}
        \resumeItem{Enhanced CI/CD pipelines using \textbf{Jenkins} and \textbf{GitLab CI/CD}, shortening release cycles by 30\% and improving deployment success rate to 98\%.}
        \resumeItem{Collaborated cross-functionally under \textbf{Agile} Scrum to deliver PCI-compliant solutions, achieving 100\% audit readiness and elevating team productivity by 25\%.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Implemented supply chain management modules using \textbf{C\# .NET} and \textbf{Entity Framework}, improving data processing efficiency by 30\%.}
        \resumeItem{Developed and consumed RESTful APIs with \textbf{Node.js} and \textbf{Express.js}, reducing integration errors by 25\% and enhancing interoperability.}
        \resumeItem{Optimized \textbf{DynamoDB} data models, reducing latency by 20\% and improving query performance under peak loads.}
        \resumeItem{Designed event-driven messaging with \textbf{AWS SNS} and \textbf{AWS SQS}, processing 5,000 messages per minute with 99\% delivery consistency.}
        \resumeItem{Migrated legacy systems to \textbf{AWS EC2}, decreasing infrastructure costs by 20\% and improving system reliability by 35\%.}
        \resumeItem{Implemented real-time monitoring scripts using \textbf{Linux Shell}, reducing incident response time by 30\% and improving operational visibility.}
        \resumeItem{Developed unit tests with \textbf{xUnit} and \textbf{Moq}, achieving 95\% code coverage and reducing critical defects by 40\%.}
        \resumeItem{Streamlined CI/CD through \textbf{GitHub Actions}, accelerating deployments by 40\% and ensuring consistent build quality across environments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-Powered Document Retriever} $|$ C\#, .NET Core, LangChain, Azure Cognitive Search}{ }
        \resumeItemListStart
            \resumeItem{Developed AI-driven document retrieval service using C\# .NET Core and LangChain, achieving 95\% answer accuracy and sub-second query latency.}
            \resumeItem{Integrated Azure Cognitive Search to index 1,000+ documents, reducing search response times by 60\% and improving user satisfaction.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Real-time Streaming Service} $|$ C\#, .NET Core, Kafka, AWS SQS}{ }
        \resumeItemListStart
            \resumeItem{Engineered real-time data pipeline using C\# .NET Core with Kafka and AWS SQS, processing 20,000 events per second with 99\% reliability.}
            \resumeItem{Containerized pipeline in Docker and deployed on Kubernetes, reducing deployment failures by 40\% and ensuring seamless scalability.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{PCI-Compliant Payment API} $|$ C\#, .NET Core, SQL Server, Docker}{ }
        \resumeItemListStart
            \resumeItem{Developed PCI-compliant payment API with C\# .NET Core and SQL Server, securing transactions and passing 100\% of compliance audits.}
            \resumeItem{Implemented unit tests with xUnit and Moq, achieving 98\% code coverage and reducing defect rates by 50\% prior to production release.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}