\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Software engineer with 5\+ years of experience designing and deploying scalable infrastructure on containerized platforms for high-availability applications.}
    \resumeItem{Leveraged \textbf{Python} to develop automation scripts and microservices, reducing deployment errors by 30\% and improving system reliability.}
    \resumeItem{Architected and managed \textbf{Kubernetes} clusters with \textbf{Docker} containers, ensuring 99.9\% uptime and streamlined delivery pipelines.}
    \resumeItem{Integrated basic machine learning model serving frameworks to support real-time inference, enhancing data-driven features availability by 20\%.}
    \resumeItem{Collaborated cross-functionally on distributed systems design while implementing monitoring solutions using \textbf{Prometheus} and \textbf{Grafana} for proactive incident resolution.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, Go \\
                \textbf{Containerization \& Orchestration:} & Docker, Kubernetes \\
                \textbf{Machine Learning \& Model Serving:} & Basic ML Concepts, TensorFlow Serving \\
                \textbf{Distributed Systems:} & Kafka, gRPC \\
                \textbf{Monitoring \& Logging:} & Prometheus, Grafana, Splunk \\
                \textbf{CI/CD \& Infrastructure:} & Jenkins, GitLab CI, Terraform \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{Python} microservices within \textbf{Kubernetes} clusters on AWS EKS, reducing data-processing latency by 25\% and enhancing scalability across containerized environments.}
        \resumeItem{Developed \textbf{Go} CLI tools to automate Docker container deployments, decreasing manual provisioning time by 40\% and standardizing Jenkins CI/CD workflows.}
        \resumeItem{Implemented \textbf{TensorFlow Serving} within \textbf{Docker} containers to enable real-time inference, achieving 30\% faster prediction times for highly scalable ML pipelines.}
        \resumeItem{Configured logging and monitoring with \textbf{Prometheus} and \textbf{Grafana}, improving incident detection by 35\% and reducing mean time to resolution in distributed environments.}
        \resumeItem{Led cross-functional teams to design distributed service architectures, coordinating deployments with \textbf{Docker} and \textbf{Kubernetes}, resulting in 20\% improvement in system resilience.}
        \resumeItem{Engineered CI/CD pipelines using \textbf{Jenkins} and \textbf{GitLab CI} to automate build and deploy processes, increasing release frequency by 50\%.}
        \resumeItem{Orchestrated backend services using \textbf{gRPC} and \textbf{Kafka}, enabling reliable message streaming at 10,000+ events per second while maintaining sub-second latencies.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Designed RESTful APIs with \textbf{Python} and Flask in microservices architecture, improving service response times by 30\% and supporting horizontal scaling.}
        \resumeItem{Implemented \textbf{Docker} containers and \textbf{Kubernetes} deployments for core banking microservices, reducing environment drift and cutting production deployment times by 40\%.}
        \resumeItem{Automated infrastructure provisioning with \textbf{Python} scripts and \textbf{Terraform}, decreasing manual setup workloads by 25\% and improving consistency across staging and production environments.}
        \resumeItem{Integrated basic ML model serving pipelines with \textbf{TensorFlow Serving}, enabling prototype deployments and reducing model inference latency by 20\% in dev environments.}
        \resumeItem{Configured centralized logging using \textbf{ELK Stack} and \textbf{Splunk}, improving visibility and reducing mean time to detection by 30\% for critical services.}
        \resumeItem{Collaborated with platform teams to design distributed event-driven architecture using \textbf{Kafka}, increasing message throughput by 50\% while ensuring reliability.}
        \resumeItem{Streamlined CI/CD workflows by integrating \textbf{Jenkins} and \textbf{GitLab CI}, automating test suites and accelerating deployment frequency by 45\% across projects.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed backend services in \textbf{Go} using \textbf{Gin} framework, containerized with Docker, improving API response times by 30\% and enhancing code maintainability.}
        \resumeItem{Built REST APIs in \textbf{Python} with Flask, integrating PostgreSQL to support 50\% more concurrent users and ensuring data integrity.}
        \resumeItem{Migrated legacy services to \textbf{Docker} containers, decreasing deployment errors by 25\% and reducing server crontab complexity for smoother environment releases.}
        \resumeItem{Instrumented monitoring with \textbf{Prometheus} exporters and \textbf{Grafana} dashboards, improving system observability and reducing incident response time by 35\% across environments.}
        \resumeItem{Automated database backups using \textbf{Python} scripts for daily MongoDB clusters, ensuring 100\% data availability and reducing manual intervention by 40\%.}
        \resumeItem{Collaborated with cross-functional teams to design production distributed message queues using \textbf{Kafka}, increasing throughput by 50\% and enhancing fault tolerance.}
        \resumeItem{Implemented CI/CD pipelines with \textbf{GitHub Actions}, automating end-to-end testing, security scans, and deployment to staging environments, reducing lead time by 30\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI Model Serving Platform} $|$ Python, TensorFlow Serving, Docker, Kubernetes, Prometheus}{}
        \resumeItemListStart
            \resumeItem{Built containerized ML model serving platform using \textbf{TensorFlow Serving} and \textbf{Docker}, enabling 50\% faster deployment of real-time inference services with Kubernetes orchestration.}
            \resumeItem{Implemented \textbf{Prometheus} monitoring with custom exporters, achieving 99\% uptime visibility and reducing incident resolution time by 40\% across distributed serving nodes.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Distributed Feature Store} $|$ Go, gRPC, Redis, Kubernetes}{}
        \resumeItemListStart
            \resumeItem{Developed a Go-based feature store with \textbf{gRPC} APIs for low-latency feature retrieval, improving data access times by 35\% in Kubernetes clusters.}
            \resumeItem{Containerized feature store with \textbf{Docker} and deployed on \textbf{Kubernetes}, scaling to handle 1000+ requests per second and ensuring fault tolerance.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Automated Infrastructure Monitoring} $|$ Python, Docker, Prometheus, Grafana}{}
        \resumeItemListStart
            \resumeItem{Created automated monitoring framework using \textbf{Python} scripts to deploy secured \textbf{Prometheus} and \textbf{Grafana} containers, enabling real-time metrics collection and dashboarding.}
            \resumeItem{Integrated alerting rules in \textbf{Prometheus} and \textbf{Grafana}, reducing critical incident response time by 30\% through proactive notifications and escalation workflows.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}