\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Software engineer with 5+ years of experience building scalable infrastructure for ML inference platforms, focusing on performance optimization and reliability.}
    \resumeItem{Proficient in Python and Go for developing infrastructure components and microservices to streamline ML model deployments on Kubernetes clusters.}
    \resumeItem{Skilled in designing and maintaining Kubernetes-based deployments and containerization strategies, ensuring high availability and efficient resource utilization.}
    \resumeItem{Experienced in implementing infrastructure automation with Terraform, Ansible, and CI/CD pipelines to accelerate ML deployment workflows by over 40\%.}
    \resumeItem{Adept at building monitoring solutions using Prometheus and Grafana to track ML model performance metrics and reduce incident response time.}
    \resumeItem{Collaborative team player with expertise in distributed systems and a strong interest in ML/AI infrastructure best practices and continual improvement.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, Go, Shell Scripting, SQL \\
                \textbf{Containerization \& Orchestration:} & Docker, Kubernetes, Helm \\
                \textbf{Infrastructure Automation:} & Terraform, Ansible, Jenkins, GitLab CI/CD \\
                \textbf{Monitoring \& Logging:} & Prometheus, Grafana, Splunk \\
                \textbf{Cloud Platforms:} & AWS, Azure \\
                \textbf{Machine Learning Platforms:} & MLflow, TensorFlow Serving, Seldon Core \\
        \end{tabular}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Implemented Python-based infrastructure components for ML inference platform, reducing model deployment time by 30\% via reliably automated Kubernetes deployment pipelines.}
        \resumeItem{Developed Go microservices to orchestrate ML model deployments on Kubernetes, improving resource utilization by 25\% through dynamic scaling and efficient container scheduling.}
        \resumeItem{Implemented automated Helm charts and Terraform modules for scalable deployment workflows, reducing manual setup time by 40\% and standardizing infrastructure configurations.}
        \resumeItem{Built monitoring pipelines using Prometheus and Grafana, capturing key ML model performance metrics to reduce incident response time by 35\%.}
        \resumeItem{Integrated resource management solutions using Kubernetes autoscaling and custom controllers, increasing cluster utilization efficiency by 20\% for ML workload spikes.}
        \resumeItem{Automated infrastructure tasks with Ansible and Python scripts, streamlining CI/CD workflows and reducing deployment errors by 30\% across ML model releases.}
        \resumeItem{Collaborated with data science teams to implement CI/CD best practices for model serving, improving deployment frequency by 50\% while maintaining 99.9\% service reliability.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Developed Python-based ETL microservices to preprocess ML datasets, significantly reducing data preparation time by 25\% for downstream model training workflows.}
        \resumeItem{Implemented containerized deployments using Docker and Kubernetes, significantly accelerating environment provisioning by 40\% and standardizing infrastructure across global development teams.}
        \resumeItem{Developed monitoring integrations with Prometheus and Grafana, improving visibility into ML pipeline performance and reducing mean time to detection by 30\%.}
        \resumeItem{Automated infrastructure provisioning with Terraform scripts, reducing environment setup errors by 35\% and cutting average provisioning time by 50\% across pilot deployments.}
        \resumeItem{Collaborated with cross-functional teams to securely design hybrid cloud infrastructure on AWS and Azure, significantly improving deployment portability by 45\%.}
        \resumeItem{Maintained CI/CD pipelines using Jenkins and GitLab CI/CD, elevating deployment success rate to 98\% and reducing rollback incidents by 60\%.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Engineered Go backend services for experimental ML feature store, improving data retrieval latency by 30\% and ensuring consistent model inputs.}
        \resumeItem{Developed containerized RESTful APIs with Docker and Express.js, securely enhancing third-party integration reliability by 35\% and simplifying faster deployment workflows.}
        \resumeItem{Monitored system performance using Prometheus, generating alerts and dashboards that reduced incident resolution time by 40\% for early support teams.}
        \resumeItem{Automated configuration management with Ansible playbooks, decreasing manual setup errors by 30\% and accelerating environment replication across dev and test environments.}
        \resumeItem{Implemented CI/CD pipelines in Jenkins, optimizing build frequency by 50\% and enforcing automated testing practices that improved code quality by 25\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{ML Inference Orchestrator} $|$ Python, Go, Kubernetes, Helm, Docker}{ }
        \resumeItemListStart
            \resumeItem{Architected Go-based inference orchestrator on Kubernetes, deploying ML models with Helm charts to achieve zero-downtime updates and 30\% faster rollouts.}
            \resumeItem{Implemented Python scripts for dynamic resource management, enabling automatic CPU and GPU scaling that improved cluster efficiency by 40\% during peak inference workloads.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Dynamic Autoscaling Module} $|$ Python, Kubernetes, Prometheus, Grafana}{ }
        \resumeItemListStart
            \resumeItem{Designed and implemented Python-based autoscaling module for Kubernetes using Prometheus metrics, reducing underutilized resources by 35\% and ensuring SLA compliance.}
            \resumeItem{Developed Grafana dashboards to visualize ML inference KPIs, accelerating anomaly detection and reducing alert response time by 30\% across production clusters.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Model Performance Monitor} $|$ Go, MLflow, Kubernetes, Python}{ }
        \resumeItemListStart
            \resumeItem{Built a Go-based microservice integrating MLflow model metrics into Kubernetes, enabling real-time performance tracking that reduced model drift incidents by 25\%.}
            \resumeItem{Implemented Python aggregation pipelines to process and store performance logs in PostgreSQL, decreasing data retrieval times by 50\% for analytics dashboards.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}