\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered 8+ years of expertise in \textbf{Java} full stack development, specializing in scalable microservices with \textbf{Spring Boot} and responsive frontends using \textbf{Angular} and \textbf{React}.}
  \resumeItem{Engineered resilient event-driven systems leveraging \textbf{Kafka} and optimized production support, improving system stability and reducing incident resolution times.}
  \resumeItem{Designed and maintained performant web applications with strong skills in \textbf{HTML5}, \textbf{CSS3}, and modern frontend frameworks, ensuring seamless user experiences.}
  \resumeItem{Implemented unit and integration testing using proven frameworks to enhance code quality and reduce defects in production environments.}
  \resumeItem{Applied containerization and orchestration with \textbf{Docker} and \textbf{Kubernetes} to streamline deployments and support agile delivery cycles.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java, Spring Boot, Hibernate, Angular, React, HTML5, CSS3 \\
\textbf{Microservices \& Messaging:} & Microservices architecture, Kafka, REST APIs, Spring Security \\
\textbf{Databases \& Caching:} & PostgreSQL, Redis \\
\textbf{Containerization \& Orchestration:} & Docker, Kubernetes \\
\textbf{Build \& CI/CD:} & Maven, JUnit, Git, GitHub Actions, Jenkins \\
\textbf{Methodologies \& Tools:} & Agile, Production Support, Unit Testing, System Testing \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led design and development of \textbf{Spring Boot} microservices, improving modularity and reducing deployment failures by 30\%.}
  \resumeItem{Developed reactive frontend components using \textbf{Angular} and \textbf{React}, enhancing user experience and reducing UI load times by 25\%.}
  \resumeItem{Implemented asynchronous event processing using \textbf{Kafka}, increasing throughput and fault tolerance in critical workflows by 40\%.}
  \resumeItem{Authored unit and integration tests using \textbf{JUnit}, raising code coverage to above 85\% and reducing production defects.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling 50\% faster environment provisioning.}
  \resumeItem{Automated CI/CD pipelines using \textbf{GitHub Actions} and \textbf{Jenkins}, decreasing release cycle times by 35\%.}
  \resumeItem{Monitored production systems and resolved incidents, improving mean time to recovery by 20\% in high-availability environments.}
  \resumeItem{\textit{Environment: Java 17/21, Spring Boot 3, Kafka, Angular 16/17, React, Redis, PostgreSQL, Docker, Kubernetes (EKS), Maven, JUnit 5, GitHub Actions, Jenkins, Agile.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and implemented \textbf{Java} microservices with \textbf{Spring Boot}, improving API response times by 30\% through optimized service boundaries.}
  \resumeItem{Built event-driven processing pipelines using \textbf{Kafka}, enhancing system scalability and reducing message loss by 25\%.}
  \resumeItem{Developed frontend modules with \textbf{Angular} and \textbf{React}, increasing feature delivery velocity by 20\%.}
  \resumeItem{Applied caching strategies with \textbf{Redis}, reducing database load and improving read latency by 30\%.}
  \resumeItem{Automated build and deployment pipelines using \textbf{GitHub Actions} and \textbf{Terraform}, achieving consistent and auditable releases.}
  \resumeItem{Supported production environments with proactive monitoring and incident resolution, decreasing downtime by 15\%.}
  \resumeItem{\textit{Environment: Java 17, Spring Boot, Kafka, Angular, React, Redis, PostgreSQL, Docker, Kubernetes (EKS/ECS), Maven, JUnit, GitHub Actions, Terraform, Agile.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed scalable \textbf{Java} backend services with \textbf{Spring Boot}, improving API throughput by 25\% through query and caching optimizations.}
  \resumeItem{Built responsive web applications using \textbf{Angular} and \textbf{React}, enhancing user engagement and reducing UI bugs by 30\%.}
  \resumeItem{Implemented asynchronous messaging with \textbf{Kafka}, increasing system reliability and reducing message processing failures by 20\%.}
  \resumeItem{Enhanced database performance using \textbf{PostgreSQL} tuning and \textbf{Redis} caching, improving read latency by 25\%.}
  \resumeItem{Authored unit and integration tests using \textbf{JUnit}, raising code quality and reducing regression issues.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed on \textbf{Kubernetes}, improving deployment repeatability and environment parity.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, Kafka, Angular 8--12, React, PostgreSQL, Redis, Docker, Kubernetes, Maven, JUnit, Git, Agile.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed \textbf{Java} backend services with \textbf{Spring Boot}, improving code reuse and reducing API response times by 15\%.}
  \resumeItem{Built frontend features using \textbf{Angular} and \textbf{React}, enhancing user workflows and reducing UI defects by 20\%.}
  \resumeItem{Implemented RESTful APIs and documented with \textbf{Swagger}, improving integration consistency and developer onboarding.}
  \resumeItem{Standardized builds using \textbf{Maven} and CI pipelines with \textbf{Jenkins}, reducing build failures by 30\%.}
  \resumeItem{Containerized development environments using \textbf{Docker}, improving team productivity and environment consistency.}
  \resumeItem{\textit{Environment: Java 8, Spring Boot 2, Angular, React 16, Maven, Jenkins, Docker, PostgreSQL, Agile.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

% ===== PROJECTS =====
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{AI-Enabled Customer Support Chatbot} | JP Morgan Chase}{2024}
\resumeItemListStart
  \resumeItem{Developed an AI-driven chatbot using \textbf{Spring AI} integrated with \textbf{AWS Bedrock} to automate customer query resolution, reducing support tickets by 40\%.}
  \resumeItem{Implemented secure access and audit logging, ensuring compliance with enterprise security standards and improving traceability.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Real-Time Trading Dashboard} | Amazon}{2023}
\resumeItemListStart
  \resumeItem{Built a real-time trading dashboard using \textbf{React} and \textbf{Kafka} streams, improving data refresh rates by 50\% and user engagement.}
  \resumeItem{Optimized backend microservices with \textbf{Spring Boot} to handle high-throughput data, reducing latency by 30\%.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Enterprise Web Portal Migration} | Paypal}{2021}
\resumeItemListStart
  \resumeItem{Led migration of legacy web portal to \textbf{Angular} and \textbf{Spring Boot} microservices, improving scalability and reducing page load times by 35\%.}
  \resumeItem{Implemented comprehensive unit and integration testing using \textbf{JUnit}, increasing code coverage to 90\% and reducing production defects.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}