\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8+ years} of backend software development specializing in \textbf{Java} and \textbf{Spring Boot} microservices with strong expertise in event-driven architectures using \textbf{Kafka}.}
  \resumeItem{Designed and deployed scalable cloud-native applications leveraging \textbf{AWS} services, ensuring high availability and secure access with modern security standards.}
  \resumeItem{Implemented robust asynchronous processing pipelines and streaming solutions, enhancing system reliability and throughput with \textbf{Kafka} and related messaging technologies.}
  \resumeItem{Applied database optimization and caching strategies primarily using \textbf{PostgreSQL} and \textbf{Redis} to improve application performance and reduce latency.}
  \resumeItem{Collaborated in Agile environments to deliver production-grade software with CI/CD automation, containerization, and orchestration using \textbf{Docker} and \textbf{Kubernetes}.}
  \resumeItem{Integrated emerging streaming technologies such as \textbf{Flink Kafka Streams} to enhance real-time data processing capabilities in select projects.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java, Spring Boot, Kafka, Flink Kafka Streams, PostgreSQL, Redis \\
\textbf{Cloud \& Infrastructure:} & AWS (EKS, ECS/Fargate, Lambda, S3, RDS/Aurora, DynamoDB, IAM, KMS, Secrets Manager, CloudWatch) \\
\textbf{Messaging \& Streaming:} & Kafka, AWS SQS, AWS SNS, EventBridge, Kinesis \\
\textbf{Databases \& Caching:} & PostgreSQL, MySQL, DynamoDB, Redis/ElastiCache \\
\textbf{DevOps \& CI/CD:} & Docker, Kubernetes, Helm, Terraform, CloudFormation, Jenkins, GitHub Actions, Azure DevOps \\
\textbf{Testing \& Observability:} & JUnit 5, Mockito, Testcontainers, OpenTelemetry, CloudWatch, Prometheus, Grafana \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led design and development of microservices using \textbf{Java} and \textbf{Spring Boot}, enhancing modularity and reducing deployment risks significantly.}
  \resumeItem{Implemented asynchronous event processing pipelines with \textbf{Kafka}, improving system reliability and message throughput by enabling retry and DLQ mechanisms.}
  \resumeItem{Developed secure APIs with \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT}, enforcing enterprise-grade authentication and authorization policies.}
  \resumeItem{Optimized backend data access patterns using \textbf{PostgreSQL} and caching with \textbf{Redis}, reducing latency and improving response times by 30\%.}
  \resumeItem{Containerized applications with \textbf{Docker} and orchestrated deployments using \textbf{Kubernetes (EKS)} and \textbf{Helm} charts for scalable production releases.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{GitHub Actions}, integrating quality gates and security scans to ensure robust delivery.}
  \resumeItem{Integrated \textbf{Flink Kafka Streams} for real-time stream processing to enhance event-driven workflows and analytics capabilities.}
  \resumeItem{Implemented observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling actionable metrics and alerting for production systems.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Kafka, Spring Security, OAuth2/OIDC, JWT, PostgreSQL, Redis, AWS (EKS, S3, RDS, IAM, KMS, Secrets Manager, CloudWatch), Docker, Kubernetes, Helm, Jenkins, GitHub Actions, OpenTelemetry, Flink Kafka Streams.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and implemented distributed backend services using \textbf{Java} and \textbf{Spring Boot}, improving scalability and maintainability of APIs.}
  \resumeItem{Built event-driven processing systems with \textbf{Kafka}, enhancing throughput and decoupling microservices for better fault tolerance.}
  \resumeItem{Developed and optimized data access using \textbf{PostgreSQL} and \textbf{DynamoDB}, improving query performance and data consistency.}
  \resumeItem{Automated infrastructure provisioning using \textbf{Terraform} and \textbf{CloudFormation}, ensuring reproducible and auditable cloud environments.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed on \textbf{EKS/ECS}, enabling smooth rollout and rollback strategies.}
  \resumeItem{Implemented observability and monitoring using \textbf{OpenTelemetry} and \textbf{CloudWatch}, reducing incident response times.}
  \resumeItem{Enhanced testing coverage using \textbf{JUnit 5}, \textbf{Mockito}, and contract testing with \textbf{Pact} to ensure integration reliability.}
  \resumeItem{Delivered operational UI modules with \textbf{Angular} and \textbf{React}, supporting configuration and monitoring workflows.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Kafka, PostgreSQL, DynamoDB, AWS (EKS, ECS, Lambda, S3, IAM, KMS, Secrets Manager, CloudWatch), Docker, Kubernetes, Terraform, CloudFormation, OpenTelemetry, Angular, React, JUnit 5, Mockito, Pact.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, delivering reusable modules and scalable REST APIs.}
  \resumeItem{Implemented asynchronous processing using \textbf{Kafka}, improving message reliability with retry and dead-letter queue patterns.}
  \resumeItem{Optimized database queries and indexing strategies on \textbf{PostgreSQL} and \textbf{MySQL}, improving throughput and reducing latency by 25\%.}
  \resumeItem{Built secure APIs using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT} aligned with enterprise RBAC policies.}
  \resumeItem{Delivered frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, enhancing user experience and modularity.}
  \resumeItem{Containerized microservices with \textbf{Docker} and deployed using \textbf{Kubernetes} with environment-based configurations.}
  \resumeItem{Implemented cloud integrations with \textbf{AWS}, \textbf{Azure}, and \textbf{GCP} for identity, storage, and messaging services.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing code quality using \textbf{SonarQube}.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Kafka, PostgreSQL, MySQL, Spring Security, OAuth2/OIDC, JWT, Angular, React, Docker, Kubernetes, Jenkins, Azure DevOps, AWS, Azure, GCP.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, delivering reusable components and clean layered architecture.}
  \resumeItem{Built REST APIs documented with \textbf{Swagger}, supporting internal and external integrations.}
  \resumeItem{Implemented scheduled batch jobs using \textbf{Spring Scheduling} and \textbf{Quartz} to automate periodic workflows.}
  \resumeItem{Optimized database performance with query tuning and indexing on \textbf{Hibernate/JPA} and relational databases.}
  \resumeItem{Delivered frontend features using \textbf{Angular} and \textbf{React} for internal dashboards and admin tools.}
  \resumeItem{Standardized builds and CI pipelines using \textbf{Maven/Gradle} and \textbf{Jenkins} for consistent releases.}
  \resumeItem{Supported containerized development environments using \textbf{Docker} and deployed on \textbf{AWS EC2} and \textbf{S3}.}
  \resumeItem{Improved automated testing coverage using \textbf{JUnit} and \textbf{Mockito} to enhance release stability.}
  \resumeItem{\textit{Environment: Java, Spring Boot, REST, Swagger, Angular, React, Hibernate/JPA, Docker, AWS (EC2, S3), Jenkins, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}