\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[enumitem]{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Results-driven software engineer with 5+ years delivering scalable \textbf{Python} backend services and \textbf{TypeScript} web applications in production.}
    \resumeItem{Skilled at designing RESTful APIs and optimizing \textbf{SQL} databases to support high-volume user-facing platforms with 99.9\% uptime.}
    \resumeItem{Delivered responsive frontends using \textbf{React} and \textbf{Angular}, boosting user engagement by over 40\% through intuitive interfaces.}
    \resumeItem{Proficient in building event-driven systems with \textbf{Kafka} and real-time updates via \textbf{WebSockets} to enhance application responsiveness.}
    \resumeItem{Collaborative communicator who owns projects end-to-end, ensuring production reliability and seamless CI/CD-driven deployments.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, JavaScript, TypeScript, SQL, Shell Scripting \\
                \textbf{Frameworks \& Libraries:} & Flask, FastAPI, Node.js, Express, React, Angular \\
                \textbf{Databases \& Storage:} & PostgreSQL, MongoDB, Redis, DynamoDB \\
                \textbf{DevOps \& CI/CD:} & Docker, Kubernetes, Jenkins, GitHub Actions \\
                \textbf{Real-Time \& Messaging:} & WebSockets, Kafka, SSE \\
                \textbf{Observability \& Monitoring:} & Prometheus, Grafana \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Developed backend services in \textbf{Python (Flask)} to expose RESTful APIs, improving data workflow throughput by 30\% across distributed systems overall.}
        \resumeItem{Implemented user interfaces in \textbf{TypeScript} and \textbf{React} for customer dashboards, increasing daily active user engagement by 40\% within first quarter.}
        \resumeItem{Migrated monolithic Java services to \textbf{Docker} containers orchestrated by \textbf{Kubernetes}, reducing average deployment time by 35\% and enhancing scalability overall.}
        \resumeItem{Optimized complex \textbf{PostgreSQL} queries to support high-volume transactions, decreasing query execution time by 25\% during peak daily loads.}
        \resumeItem{Established CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, automating builds and tests to increase deployment frequency by 50\% monthly.}
        \resumeItem{Integrated real-time streaming updates with \textbf{WebSockets}, enabling live notifications and reducing unnecessary data polling overhead by 60\%.}
        \resumeItem{Implemented observability using \textbf{Prometheus} and \textbf{Grafana}, improving real-time system monitoring and alert accuracy by 30\% in production.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Developed backend microservices in \textbf{Python} and \textbf{Flask} for core banking features, improving transaction processing throughput by 25\% daily system.}
        \resumeItem{Designed and implemented responsive web interfaces in \textbf{Angular} and \textbf{TypeScript}, enhancing user satisfaction scores by 22\% for loan application platform.}
        \resumeItem{Built event-driven architecture using \textbf{Kafka}, processing over 10,000 transactions per second and ensuring 99.9\% reliability for operations under peak monthly loads.}
        \resumeItem{Automated configuration management with \textbf{Python} scripts, reducing manual setup time by 15 hours weekly and streamlining continuous team development workflow.}
        \resumeItem{Developed Node.js middleware in \textbf{TypeScript} to handle real-time cash transactions, increasing processing speed by 30\% and reducing failure rates by 40\% overall.}
        \resumeItem{Created Grafana dashboards with \textbf{Prometheus} metrics, delivering real-time operational insights and reducing incident response time by 35\% across services.}
        \resumeItem{Enhanced CI/CD process using \textbf{Jenkins} and \textbf{GitLab CI/CD}, boosting deployment speed by 30\% and improving rollback reliability overall.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Optimized SQL queries in \textbf{PostgreSQL} for supply chain modules, reducing order processing latency by 140ms and improving throughput by 18\%.}
        \resumeItem{Integrated third-party logistics APIs using \textbf{Node.js} and \textbf{Express}, expanding vendor coverage by 12\% and enhancing data consistency overall across system.}
        \resumeItem{Authored unit tests with \textbf{JUnit} and \textbf{Mockito}, identifying 20+ edge-case defects, increasing code coverage to 95\% and reducing production incidents.}
        \resumeItem{Migrated on-premise services to \textbf{AWS EC2}, enhancing system availability by 18\% weekly and reducing hardware-related downtimes by 18\% overall.}
        \resumeItem{Refined \textbf{DynamoDB} indexing patterns, boosting inventory read throughput by 14\% during peak usage and optimizing storage utilization across system.}
        \resumeItem{Automated builds with \textbf{Shell} scripts and \textbf{Jenkins}, cutting manual deployment time by 4 hours weekly and streamlining release cycles overall.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{InsightPDF} $|$ Python, Streamlit, LangChain, OpenAI API, FAISS, Docker}{}
        \resumeItemListStart
            \resumeItem{Developed AI-driven PDF Q\&A application using Python, LangChain and OpenAI API, delivering 90\% accurate context-aware responses within interactive sub-second latencies.}
            \resumeItem{Implemented vector indexing with FAISS and document chunking to power similarity search, reducing query retrieval time by 50\% significantly.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{LiveNotify} $|$ Python, FastAPI, WebSockets, Redis, Docker, Kubernetes}{}
        \resumeItemListStart
            \resumeItem{Engineered real-time WebSocket service in Python with FastAPI and Redis, enabling live order status updates and cutting polling overhead by 70\%.}
            \resumeItem{Containerized application with Docker and deployed on Kubernetes, ensuring 99.5\% uptime and auto-scaling to handle 1000+ concurrent connections efficiently.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{FleetMetrics} $|$ Python, Flask, Kafka, PostgreSQL, Grafana, Docker}{}
        \resumeItemListStart
            \resumeItem{Developed vehicle telemetry ingestion pipeline using Python, Kafka and Flask, processing 5000+ telemetry events per minute with under 100ms processing latency.}
            \resumeItem{Built Grafana dashboards on PostgreSQL metrics, delivering real-time operational insights across services and reducing incident detection time by 45\%.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}