\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{\textbf{Experienced software engineer} specializing in \textbf{Python} backend services, APIs, and data workflows with 5+ years delivering production user-facing web applications.} \vspace{-3pt}
    \resumeItem{Built frontend experiences using \textbf{TypeScript} and \textbf{React.js}, shipping customer-facing interfaces and improving engagement and usability across multiple products with measurable results.} \vspace{-3pt}
    \resumeItem{Designed reliable systems leveraging \textbf{SQL} databases and modern observability, prioritizing production reliability and incident reduction across cloud deployments and horizontal scale.} \vspace{-3pt}
    \resumeItem{Collaborated cross-functionally with low-ego ownership, using telemetry-driven decisions and responsible AI practices to increase delivery confidence and product stability consistently.} \vspace{-3pt}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, TypeScript, JavaScript, Java, Go, Shell Scripting \\
                \textbf{Backend \& APIs:} & Python backend, Node.js, Express.js, RESTful APIs, GraphQL, gRPC, WebSockets, Server-Sent Events \\
                \textbf{Frontend \& Web:} & TypeScript, React.js, Redux, Material UI, HTML5, CSS3 \\
                \textbf{Databases \& Messaging:} & PostgreSQL, MySQL, MongoDB, Redis, DynamoDB, Apache Kafka \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, ECS, S3, API Gateway), Docker, Kubernetes, Jenkins, GitHub Actions, Terraform \\
                \textbf{Observability \& Testing:} & Prometheus, Grafana, AppDynamics, Splunk, JUnit, Mockito, Jest, Postman \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Built and maintained backend APIs in \textbf{Python} to serve user-facing web applications, reducing API latency by 35\% under peak traffic.}
        \resumeItem{Implemented interactive frontends using \textbf{TypeScript} and \textbf{React.js}, increasing user engagement metrics by 40\% through improved UX flows and accessibility standards.}
        \resumeItem{Led migration from monolith to microservices using \textbf{Docker} and \textbf{AWS} \textbf{ECS}, reducing deployment duration by 30\% and improving uptime reliability.}
        \resumeItem{Implemented retrieval-augmented generation with \textbf{Redis} vector store and \textbf{OpenAI} API, enabling contextual document answers and improving support accuracy by 25\%.}
        \resumeItem{Developed GraphQL gateways with \textbf{AWS API Gateway} to consolidate endpoints, decreasing average response times by 35\% and lowering backend load.}
        \resumeItem{Optimized complex \textbf{PostgreSQL} queries and schema, improving query throughput by 20\% and reducing deadlocks in production during peak concurrency windows.}
        \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker}, increasing deployment frequency by 50\% while maintaining production reliability metrics and lowering rollback incidents.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Delivered core banking microservices in \textbf{Java} and \textbf{Spring Boot}, improving transaction reliability and reducing critical incident rate by 28\% during peak loads.}
        \resumeItem{Implemented frontend components with \textbf{React} and \textbf{Redux}, increasing loan application completion rate by 18\% via streamlined flows and validation logic.}
        \resumeItem{Automated configuration tasks using \textbf{Python} scripts, saving the team 20 hours weekly and reducing manual deployment errors by 35\% consistently.}
        \resumeItem{Built Node.js middleware to manage real-time cash transactions, improving processing speed by 30\% and ensuring transactional integrity under concurrent load spikes.}
        \resumeItem{Designed and deployed \textbf{Kafka}-based event streams handling 10,000+ TPS, improving system throughput and decoupling services for better scalability and resilience.}
        \resumeItem{Created Grafana dashboards with \textbf{Prometheus} metrics, reducing incident detection time by 40\% and providing clear operational visibility for SREs and on-call engineers.}
        \resumeItem{Strengthened authentication using \textbf{OAuth2} and \textbf{JWT}, reducing security incidents by 40\% and improving compliance posture across services and audit readiness.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
\resumeItemListStart
    \resumeItem{Developed backend supply-chain modules with \textbf{Java} and \textbf{Spring MVC}, reducing order processing latency by 140ms through optimized SQL queries and monitoring.}
    \resumeItem{Integrated third-party logistics APIs using \textbf{Node.js} and \textbf{Express.js}, expanding vendor coverage by 12\% within the first quarter after release successfully.}
    \resumeItem{Authored comprehensive unit tests with \textbf{JUnit} and \textbf{Mockito}, catching 20+ critical edge-case bugs before production release and improving stability metrics.}
    \resumeItem{Migrated on-prem components to \textbf{AWS EC2}, improving availability by 18\% and decreasing hardware-related downtime for key services during peak demand periods.}
    \resumeItem{Optimized \textbf{DynamoDB} indexing and access patterns, improving read throughput by 14\% during peak usage and lowering latency for inventory queries.}
    \resumeItem{Automated build tasks using \textbf{Linux Shell} scripts and \textbf{Jenkins}, saving 4 hours weekly and reducing manual deployment overhead across teams consistently.}
\resumeItemListEnd


  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{InsightPDF} $|$ Python, Streamlit, LangChain, OpenAI API, FAISS, Docker, GitHub Actions}{ }
        \resumeItemListStart
            \resumeItem{Built RAG pipeline in \textbf{Python} and \textbf{LangChain}, enabling natural language queries over multi-PDF corpora with 92\% answer relevance improvement overall.}
            \resumeItem{Containerized application with \textbf{Docker} and automated CI via \textbf{GitHub Actions}, reducing deployment time by 45\% and improving reproducibility across environments consistently.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Scalable Deep Learning Image Recognition Application} $|$ AWS, EC2, S3, SQS, IAM, Python}{ }
        \resumeItemListStart
            \resumeItem{Engineered face recognition API in \textbf{Python} on \textbf{EC2}, using \textbf{SQS} for decoupling to handle 200 requests under 120 seconds efficiently.}
            \resumeItem{Improved performance with \textbf{Redis} caching and autoscaling, decreasing data retrieval latency by 60\% and stabilizing peak throughput for production workloads.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Real-time graph data analytics} $|$ Docker, Kubernetes, Apache Kafka, Neo4j, Minikube}{ }
        \resumeItemListStart
            \resumeItem{Developed streaming graph pipeline with \textbf{Apache Kafka} and \textbf{Neo4j}, processing 1000 concurrent events and enabling near-real-time analytics for operational dashboards and alerts.}
            \resumeItem{Containerized the solution using \textbf{Docker} and \textbf{Kubernetes}, improving deployment consistency and reducing rollout time by 50\% across clusters and environments.}
        \resumeItemListEnd
        \vspace{-12pt}

    \resumeSubHeadingListEnd

\end{document}