\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Detail-oriented software engineer with 5+ years of experience in designing, debugging, and enhancing scalable software applications focused on high-quality deliverables.}
    \resumeItem{Proficient in Java, Python, SQL, and JavaScript, with strong skills in unit testing, defect resolution, and application performance improvement methodologies.}
    \resumeItem{Experienced in relational databases such as Oracle and SQL Server, with solid knowledge of software integrity and interoperability best practices.}
    \resumeItem{Strong problem-solving capabilities, excellent communication skills, and ability to manage multiple priorities effectively in fast-paced collaborative environments.}
    \resumeItem{Committed to continuous learning and expanding expertise in software development standards and real estate industry-specific solutions.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, JavaScript, TypeScript, SQL, PL/SQL, Shell Scripting, C++, Kotlin, HTML, CSS \\
                \textbf{Frameworks \& Backend:} & Spring Boot, Spring MVC, Node.js, Express.js, Hibernate, JPA, OAuth2, RESTful APIs, SOAP \\
                \textbf{Databases:} & Oracle Database, SQL Server, PostgreSQL, MySQL, MongoDB \\
                \textbf{Testing \& Automation:} & JUnit, Mockito, Postman, Selenium, Cucumber, Jenkins, GitHub Actions \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, API Gateway, CodePipeline), Azure, Docker, Kubernetes, Jenkins, Terraform \\
                \textbf{Tools \& Methodologies:} & IntelliJ, VS Code, TOAD, JIRA, Agile (Scrum), CI/CD pipelines, Microservices Architecture \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Analyzed and debugged Java and Spring Boot microservices, improving application performance by 25\% while maintaining high code quality standards.}
        \resumeItem{Developed unit tests using JUnit and Mockito, achieving over 98\% test coverage that enhanced software reliability and usability.}
        \resumeItem{Collaborated with cross-functional teams to resolve software defects rapidly, reducing bug cycle time by 30\% and increasing customer satisfaction.}
        \resumeItem{Optimized PostgreSQL queries which improved database response times by 20\%, ensuring seamless data flow and integrity.}
        \resumeItem{Implemented CI/CD pipelines with Jenkins and AWS CodePipeline, doubling deployment frequency and reducing downtime during releases.}
        \resumeItem{Utilized AWS API Gateway to integrate GraphQL, reducing response time by 35\% and improving client-server interactions drastically.}
        \resumeItem{Assisted in web application maintenance using React.js, leading to 40\% higher user engagement and enhanced user experience.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Developed and modified Java Spring Boot microservices supporting core banking, increasing system reliability by 30\%.}
        \resumeItem{Performed root cause analysis and resolved defects using SQL and Java tools, reducing software defects by 25\%.}
        \resumeItem{Built and tested RESTful APIs and web components for loan applications, improving user satisfaction rating by 20\%.}
        \resumeItem{Created complex database queries in SQL Server, improving data retrieval efficiency by 35\%.}
        \resumeItem{Automated unit testing processes, boosting test coverage and lowering software regressions during deployment stages.}
        \resumeItem{Collaborated in Agile teams to align software development with client needs and meet critical deadlines effectively.}
        \resumeItem{Enhanced security standards by integrating OAuth2 and JWT authentication, reducing vulnerabilities in banking applications.}
        \resumeItem{Managed build and deployment automation with Jenkins and SVN, slashing delivery times by 30\% and increasing release stability.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Maintained and enhanced supply chain Java applications using Spring MVC and Hibernate, improving data accuracy by 20\%.}
        \resumeItem{Implemented RESTful APIs with Node.js and Express.js, facilitating third-party integrations and increasing application scope by 30\%.}
        \resumeItem{Conducted unit and integration testing with JUnit and Postman, raising application test coverage above 95\%.}
        \resumeItem{Migrated on-premises applications to AWS Cloud, reducing operational costs by 20\% and improving scalability.}
        \resumeItem{Optimized DynamoDB queries, resulting in 15\% faster response times and improved real-time data access.}
        \resumeItem{Developed Linux Shell scripts for system monitoring, cutting incident response times by 30\%.}
        \resumeItem{Streamlined CI/CD workflows using GitHub Actions, accelerating deployment frequency by 40\% while ensuring quality releases.}
        \resumeItem{Supported Agile development processes, enhancing project completion times by 25\% and boosting team productivity.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-Powered Document Query System} | Python, LangChain, Streamlit, OpenAI API, FAISS}{ }
        \resumeItemListStart
            \resumeItem{Developed an AI system that interprets user queries over multiple PDFs, increasing information retrieval accuracy by 30\%.}
            \resumeItem{Integrated retrieval-augmented generation (RAG) techniques with vector indexing to enhance context awareness for real estate documents.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Real-Time Web Application Performance Monitoring} | React.js, Spring Boot, PostgreSQL, Jenkins}{ }
        \resumeItemListStart
            \resumeItem{Designed a monitoring dashboard to display live application metrics, reducing issue detection time by 40\% and improving system stability.}
            \resumeItem{Implemented backend API enhancements to support real-time updates, boosting data refresh rates by 50\% for seamless client experience.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Cloud-Native Microservices for Financial Applications} | Java, Spring Boot, AWS, Docker, Kubernetes}{ }
        \resumeItemListStart
            \resumeItem{Developed and deployed microservices on AWS using Docker and Kubernetes, improving service scalability and reducing downtime by 25\%.}
            \resumeItem{Built secure authentication with JWT/OAuth2, enhancing application access control and decreasing security incidents by 35\%.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}