\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{\textbf{Software engineer} with \textbf{5+ years} specialization in Java development, Spring Boot framework, and scalable application design focused on performance and secure coding.} \vspace{-3pt}
    \resumeItem{Proficient in \textbf{unit testing} techniques using \textbf{JUnit} and \textbf{Mockito}, ensuring code reliability and maintaining high software quality standards.} \vspace{-3pt}
    \resumeItem{Skilled in writing complex \textbf{SQL queries} and optimizing RDBMS interactions, predominantly with \textbf{PostgreSQL} and \textbf{Oracle}, tailored for financial technology applications.} \vspace{-3pt}
    \resumeItem{Experienced with event-driven architectures, including messaging and middleware tools such as \textbf{Kafka}, enhancing system scalability and responsiveness.} \vspace{-3pt}
    \resumeItem{Strong advocate of Agile methodology, cross-team collaboration, and continuous improvement initiatives to align technology solutions with business objectives.} \vspace{-3pt}
    \resumeItem{Adaptable self-learner with demonstrated ability to swiftly acquire new skills and technologies including \textbf{FIX/Swift} standards and middleware communication protocols.} \vspace{-3pt}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Frameworks:} & Java (17 \& 21), Spring Boot, Object-Oriented Design, JUnit, Mockito, Python, JavaScript, TypeScript \\
                \textbf{Databases \& Querying:} & PostgreSQL, Oracle Database, SQL, PL/SQL, Query Optimization \\
                \textbf{Middleware \& Messaging:} & Apache Kafka, TIBCO RV, Solace, Event-Driven Architecture \\
                \textbf{Testing \& Automation:} & JUnit, Mockito, Cucumber, Selenium, Postman, Unit Testing Best Practices \\
                \textbf{DevOps \& Cloud:} & Docker, Kubernetes, Jenkins, AWS, Azure, CI/CD Pipelines \\
                \textbf{Methodologies \& Standards:} & Agile (Scrum/Kanban), FIX, Swift Messaging Standards, Secure Coding Practices \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{Java Spring Boot} microservices focused on Middle Office processes, improving system stability and throughput by 30\%.}
        \resumeItem{Implemented comprehensive \textbf{unit tests} using \textbf{JUnit} and \textbf{Mockito}, raising test coverage to over 95\%, thereby strengthening code reliability.}
        \resumeItem{Optimized complex \textbf{PostgreSQL} queries and application performance, achieving 25\% faster data retrieval and improved system response times.}
        \resumeItem{Collaborated with cross-functional teams to align software features with business goals, ensuring seamless integration and operational efficiency in global equities platform.}
        \resumeItem{Contributed to implementation of Agile practices, facilitating sprint planning and retrospectives to deliver high-quality software on schedule.}
        \resumeItem{Enhanced event-driven messaging solutions via \textbf{Apache Kafka} integration, increasing real-time processing capabilities and fault tolerance by 40\%.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented key enterprise features using \textbf{Java} and \textbf{Spring Boot}, improving customer service workflows within microservices architecture.}
        \resumeItem{Optimized system communication using \textbf{Kafka}-based event streaming, supporting over 10,000 transactions per second for mission-critical financial systems.}
        \resumeItem{Developed and refined SQL queries and stored procedures in \textbf{Oracle}, reducing report generation times by 20\%.}
        \resumeItem{Led security enhancements including integration of \textbf{OAuth2} and secure coding techniques, decreasing vulnerabilities and enhancing data protection.}
        \resumeItem{Implemented Agile methodologies effectively, increasing team velocity by 25\% and promoting collaborative delivery across business functions.}
        \resumeItem{Built middleware solutions integrating \textbf{FIX} protocol for financial messaging, improving transaction accuracy and operational efficiency by 30\%.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed backend services in \textbf{Java Spring MVC} for supply chain applications, boosting process efficiency and scalability by 20\%.}
        \resumeItem{Created and tested \textbf{RESTful APIs} using \textbf{Node.js}, increasing third-party integration success rate by 30\% with thorough automated testing.}
        \resumeItem{Managed \textbf{AWS} migration initiatives, reducing operational costs by roughly 20\% while maintaining service continuity and data integrity.}
        \resumeItem{Developed scripts for real-time system monitoring and performance tuning, decreasing incident detection time by 30\%.}
        \resumeItem{Applied Agile and Scrum practices to guide software development, improving team delivery speed and efficiency by 25\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-driven Document Query System} $|$ Python, LangChain, FAISS, OpenAI API}{ }
        \resumeItemListStart
            \resumeItem{Engineered an AI-enabled natural language query system over PDFs using RAG, delivering precise responses by semantic vector searching and fallback mechanisms.}
            \resumeItem{Optimized indexing of large document sets with \textbf{FAISS}, improving query speed by 50\% and enhancing operational efficiency for user requests.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Event-driven Financial Messaging Middleware} $|$ Java, Spring Boot, Apache Kafka, FIX Protocol}{ }
        \resumeItemListStart
            \resumeItem{Developed an event-driven middleware leveraging \textbf{Kafka} and \textbf{FIX} messaging standards, increasing transaction throughput by 35\% in equities trading platform.}
            \resumeItem{Implemented robust \textbf{secure coding} and message validation, reducing error rates by 25\% and enhancing system reliability under peak loads.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Real-time Monitoring and Alerts System} $|$ Spring Boot, PostgreSQL, Docker, Prometheus}{ }
        \resumeItemListStart
            \resumeItem{Built a real-time system monitoring tool using \textbf{Spring Boot} and \textbf{Prometheus}, reducing anomaly detection time by 30\% through timely alerts.}
            \resumeItem{Optimized \textbf{PostgreSQL} data operations for performance, achieving a 20\% improvement in dashboard refresh and reporting time for operational teams.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}