\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Experienced software engineer with 5+ years developing scalable web applications and services using \textbf{Java, JavaScript, and RESTful APIs}, ensuring high-quality deliverables.}
    \resumeItem{Skilled in modern frameworks like \textbf{Spring, React, and Angular}, with strong knowledge of cloud environments, particularly \textbf{AWS} and cloud-native design principles.}
    \resumeItem{Proficient in database design and integration, writing optimized \textbf{SQL} queries, and working with \textbf{third-party product integrations} for seamless enterprise solutions.}
    \resumeItem{Committed to quality through testing strategies and automation using tools like \textbf{JUnit, Mockito, and Selenium}, balancing speed and reliability effectively.}
    \resumeItem{Collaborative team player with experience in Agile methodologies, delivering projects on-time and aligning technical designs with functional business needs.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java (Spring, J2EE), JavaScript (Node.js, React, Angular), SQL, PL/SQL, Python, TypeScript, Shell Scripting \\
                \textbf{Frameworks \& Backend:} & Spring Boot, Hibernate, Apex, Servlets, JSP, REST, SOAP, OAuth2, JWT, Application Integration, Microservices \\
                \textbf{Frontend \& UI:} & React.js, Angular, Material UI, Bootstrap, Redux, JSON, XML \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, ECS, S3, API Gateway, CodePipeline), Docker, Kubernetes, Jenkins, Git, Agile/Scrum \\
                \textbf{Databases:} & Oracle, PostgreSQL, MySQL, MongoDB, DynamoDB, Redis \\
                \textbf{Tools \& Methodologies:} & IntelliJ, VS Code, JIRA, GIT, SonarQube, CI/CD, Automated Testing (JUnit, Selenium), Software Development Life Cycle Models \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Developed and maintained \textbf{Java Spring Boot} microservices and \textbf{React} front-end, improving system reliability by 25\% and enhancing user experience.}
        \resumeItem{Led migration to microservices architecture on \textbf{AWS ECS}, reducing deployment times by 30\% and enabling scalable, cloud-native application design.}
        \resumeItem{Integrated \textbf{GraphQL} APIs using \textbf{AWS API Gateway}, decreasing response times by 35\% to optimize performance and reduce server load.}
        \resumeItem{Created and executed automated \textbf{JUnit} and \textbf{Mockito} tests, achieving 98\% code coverage and enhancing software stability and quality.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries for better database efficiency, improving application performance by 20\% across critical services.}
        \resumeItem{Engineered \textbf{CI/CD pipelines} with Jenkins and AWS CodePipeline, increasing deployment frequency by 50\% and release reliability.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Developed core banking modules with \textbf{Java Spring Boot}, enhancing feature delivery and system integrity within a microservices environment.}
        \resumeItem{Implemented front-end interfaces for loan applications using \textbf{React} and \textbf{Redux}, improving user engagement and workflow efficiency.}
        \resumeItem{Designed \textbf{Node.js} middleware handling real-time transaction processing, increasing throughput by 30\% and ensuring data consistency.}
        \resumeItem{Architected \textbf{Kafka}-based event-driven systems supporting 10,000+ transactions per second, boosting scalability and fault tolerance.}
        \resumeItem{Developed monitoring dashboards in \textbf{Grafana} with \textbf{Prometheus}, enhancing operational visibility and reducing incident response times by 25\%.}
        \resumeItem{Integrated \textbf{OAuth2} and \textbf{JWT} security protocols, decreasing vulnerabilities and security incidents by 40\%.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{RESTful APIs} with \textbf{Node.js} and \textbf{Express}, expanding third-party integrations by 30\% and enhancing system interoperability.}
        \resumeItem{Implemented backend solutions using \textbf{Java Spring MVC} and \textbf{Hibernate}, increasing data processing efficiencies in supply chain management.}
        \resumeItem{Led migration of legacy systems to \textbf{AWS cloud}, reducing operational costs by 20\% and improving system scalability.}
        \resumeItem{Automated system performance monitoring with Linux shell scripts, decreasing performance issue resolution times by 30\%.}
        \resumeItem{Enhanced CI/CD processes through \textbf{GitHub Actions}, accelerating deployment frequency by 40\% while maintaining code quality.}
        \resumeItem{Supported Agile and Scrum roles to improve team delivery efficiency by 25\%, ensuring faster time to market.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-Powered Document Query System} | Python, LangChain, OpenAI API, FAISS, Docker}{ }
        \resumeItemListStart
            \resumeItem{Developed a RAG-based AI system enabling natural language queries over multiple PDFs to extract precise contextual answers, boosting user efficiency.}
            \resumeItem{Containerized the application with Docker and automated builds via GitHub Actions, ensuring consistent deployment and continuous integration.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Cloud-Native Microservices Platform} | Java Spring Boot, AWS ECS, PostgreSQL, Jenkins}{ }
        \resumeItemListStart
            \resumeItem{Engineered a microservices platform with \textbf{Spring Boot} deployed on \textbf{AWS ECS}, improving scalability and reducing downtime by 25\%.}
            \resumeItem{Implemented CI/CD pipelines using \textbf{Jenkins}, automating testing and deployment, delivering 50\% faster releases with higher reliability.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Real-Time Transaction Monitoring Dashboard} | Node.js, Kafka, Grafana, Prometheus}{ }
        \resumeItemListStart
            \resumeItem{Built a real-time transaction processing system using \textbf{Kafka} and \textbf{Node.js}, handling over 10,000 TPS with high availability.}
            \resumeItem{Developed monitoring dashboards using \textbf{Grafana} and \textbf{Prometheus}, reducing alert response times by 25\% and supporting operational decisions.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}