\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{\textbf{Full stack developer} with \textbf{5+ years} of experience delivering scalable, accessible web applications using \textbf{JavaScript, HTML, and CSS}.} \vspace{-3pt}
    \resumeItem{Skilled in implementing \textbf{responsive designs}, semantic coding practices, and advanced testing techniques with frameworks like \textbf{Jest} and \textbf{Mocha}.} \vspace{-3pt}
    \resumeItem{Experienced in collaborating within \textbf{agile teams}, contributing actively to \textbf{Scrum ceremonies}, code reviews, and pair programming to ensure quality deliverables.} \vspace{-3pt}
    \resumeItem{Proficient with \textbf{Git}, \textbf{Docker}, and cloud platforms such as \textbf{AWS} to deploy and maintain high-priority features effectively.} \vspace{-3pt}
    \resumeItem{Committed to continuous improvement in codebases and team culture, communicating effectively and supporting peers to enhance overall software quality.} \vspace{-3pt}
    \resumeItem{Adaptable and eager to learn emerging technologies, contributing to both technical innovation and positive workplace dynamics.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & JavaScript, TypeScript, HTML5, CSS3, Python, Java, SQL, Shell Scripting \\
                \textbf{Frontend:} & React.js, Angular, Redux, Material UI, Bootstrap, Tailwind, Semantic HTML, Accessibility (WCAG), Responsive Design \\
                \textbf{Backend \& Frameworks:} & Node.js, Express.js, Spring Boot, RESTful APIs, GraphQL, Microservices Architecture \\
                \textbf{Testing \& Automation:} & Jest, Jasmine, Mocha, JUnit, Mockito, Selenium, Postman, CI/CD with Jenkins and GitHub Actions \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, API Gateway, CodePipeline), Docker, Kubernetes, Terraform, PagerDuty, Jenkins \\
                \textbf{Databases \& Others:} & PostgreSQL, MongoDB, DynamoDB, SQL, NoSQL, Design Systems, Component Libraries, Atomic Design \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Developed and maintained responsive UI features using \textbf{React.js}, adhering to accessibility standards, improving user engagement by 30\%.}
        \resumeItem{Owned full feature lifecycle, from design to deployment on \textbf{AWS}, ensuring high quality through thorough testing and alerting integration.}
        \resumeItem{Collaborated effectively in a cross-functional \textbf{agile} team, participating actively in Scrum, planning, demos, and retrospectives.}
        \resumeItem{Implemented unit tests with \textbf{Jest} and \textbf{Mocha}, elevating test coverage above 95\% and reducing production bugs.}
        \resumeItem{Managed source control workflows using \textbf{Git} alongside containerization with \textbf{Docker}, streamlining development and deployment processes.}
        \resumeItem{Enhanced API performance via \textbf{GraphQL} through \textbf{AWS API Gateway}, reducing client response times by 35\%.}
        \resumeItem{Reviewed peer code and conducted pairing sessions, improving codebase quality and accelerating team delivery velocity by 20\%.}
        \resumeItem{Utilized \textbf{Kubernetes} and \textbf{PagerDuty} for production monitoring and rapid incident response, improving uptime by 15\%.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Built scalable \textbf{full stack} solutions using \textbf{Java} and \textbf{React}, incorporating responsive design and semantic HTML practices.}
        \resumeItem{Implemented core backend microservices with \textbf{Spring Boot}, improving service scalability and reducing latency by 25\%.}
        \resumeItem{Automated deployment pipelines with \textbf{Jenkins} and integrated \textbf{Docker} containers, accelerating release cycles by 30\%.}
        \resumeItem{Developed real-time transactional middleware with \textbf{Node.js}, increasing throughput by 30\% and supporting high availability.}
        \resumeItem{Created visualization dashboards using \textbf{Grafana} integrated with \textbf{Prometheus}, enhancing system observability and incident resolution speed.}
        \resumeItem{Enhanced security by integrating \textbf{OAuth2} and \textbf{JWT}, reducing vulnerabilities and security incidents by over 40\%.}
        \resumeItem{Contributed to \textbf{Agile} ceremonies and continuous improvement initiatives, improving team productivity by 25\%.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented robust \textbf{RESTful APIs} with \textbf{Node.js} and \textbf{Express.js}, expanding integrations by 30\%.}
        \resumeItem{Conducted unit and integration testing using \textbf{JUnit} and \textbf{Postman}, achieving 95\% test coverage and better reliability.}
        \resumeItem{Migrated legacy systems to \textbf{AWS}, reducing operational costs by 20\% and improving deployment performance.}
        \resumeItem{Optimized interactions with \textbf{DynamoDB}, cutting data retrieval latency by 15\% and improving app response times.}
        \resumeItem{Implemented \textbf{CI/CD} pipelines with \textbf{GitHub Actions} to automate testing and deployment, increasing deployment frequency by 40\%.}
        \resumeItem{Supported team Agile process adoption, resulting in 25\% faster delivery and improved collaboration.}
        \resumeItem{Authored shell scripts for system monitoring, reducing issue detection times by 30\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-Driven Document Query Application} $|$ Python, Streamlit, LangChain, OpenAI API, FAISS, Docker}{}
        \resumeItemListStart
            \resumeItem{Designed an AI-powered app enabling natural language queries on documents using a retrieval-augmented generation pipeline for relevant responses.}
            \resumeItem{Containerized and automated deployments with \textbf{Docker} and CI pipelines, ensuring scalable, reliable usage in dynamic environments.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Responsive Advertisement Integration Platform} $|$ JavaScript, React.js, AWS, Jest}{}
        \resumeItemListStart
            \resumeItem{Developed an advertisement integration system with responsive design, leveraging \textbf{AWS} for deployment and \textbf{Jest} for unit testing achieving 90\% coverage.}
            \resumeItem{Implemented A\slash B testing capabilities within the platform to optimize ad performance and consumer interaction based on data insights.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Cloud-Enabled Full Stack Microservices Application} $|$ Node.js, Express.js, React.js, MongoDB, AWS, Docker, Kubernetes}{}
        \resumeItemListStart
            \resumeItem{Built and deployed a microservices architecture on \textbf{AWS} using \textbf{Docker} and \textbf{Kubernetes}, improving scalability and fault tolerance by 30\%.}
            \resumeItem{Developed code with accessibility and semantic UI principles, resulting in a 40\% increase in mobile and desktop user experience scores.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}