\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Innovative \textbf{software engineer} with \textbf{5+ years} of experience delivering full-stack solutions leveraging modern cloud-native architectures and DevOps practices.}
    \resumeItem{Skilled in designing scalable \textbf{Java Spring Boot} backend services alongside \textbf{React} and \textbf{Node.js} frontends, improving performance and user engagement.}
    \resumeItem{Experienced in integrating complex systems with robust \textbf{RESTful APIs} and automating deployment pipelines using \textbf{Docker, Kubernetes}, and CI/CD tools.}
    \resumeItem{Proficient in managing accounting workflow systems and media-related payment processes, contributing to enhanced monetization and distribution platforms.}
    \resumeItem{Strong collaborator able to translate product requirements into scalable, maintainable code while driving agile delivery and continuous improvement.}
    \resumeItem{Motivated to solve complex technical challenges with a passion for innovation, operational excellence, and delivering business value at scale.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java (17 \& 21), Kotlin, JavaScript, TypeScript, SQL, Python, Shell Scripting, HTML5, CSS3 \\
                \textbf{Frameworks \& Backend:} & Spring Boot, Spring Cloud, Node.js, Express.js, React.js, OAuth2, RESTful Services, gRPC \\
                \textbf{DevOps \& Cloud:} & Docker, Kubernetes, Jenkins, GitLab CI/CD, AWS (EC2, ECS, S3, API Gateway, CodePipeline), Azure, Terraform \\
                \textbf{Databases:} & PostgreSQL, Oracle Database, MySQL, MongoDB, Redis, DynamoDB \\
                \textbf{Testing \& Automation:} & JUnit, Mockito, Selenium, Postman, Cucumber, Rest Assured, Jenkins Pipelines \\
                \textbf{Tools \& Methodologies:} & Agile (Scrum/Kanban), CI/CD Automation, Microservices Architecture, Git, JIRA, Grafana, SonarQube, Performance Profiling \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Developed scalable microservices architecture with \textbf{Java Spring Boot} deployed on \textbf{AWS ECS}, boosting system uptime and reliability by 25\%.}
        \resumeItem{Built dynamic user interfaces using \textbf{React.js} and \textbf{Node.js} that increased application usability and user interaction metrics by 40\%.}
        \resumeItem{Migrated legacy monolithic systems to cloud-native architecture using \textbf{Docker} and \textbf{Kubernetes}, cutting deployment time by 30\%.}
        \resumeItem{Implemented a \textbf{RAG} AI solution integrating \textbf{Redis} vector search to enhance content retrieval accuracy for customer queries.}
        \resumeItem{Refined API design using \textbf{GraphQL} through \textbf{AWS API Gateway}, improving response time by 35\% during peak traffic.}
        \resumeItem{Created and maintained CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker}, increasing release frequency by 50\%.}
        \resumeItem{Optimized complex database queries with \textbf{PostgreSQL} resulting in 20\% faster transactional processing for key business workflows.}
        \resumeItem{Led automated testing efforts using \textbf{JUnit} and \textbf{Mockito}, ensuring over 98\% code coverage for critical modules.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Engineered backend solutions with \textbf{Java Spring Boot} APIs for financial workflows, improving payment processing accuracy by 30\%.}
        \resumeItem{Developed front-end components in \textbf{React} and \textbf{Redux}, enhancing loan application platform responsiveness and user satisfaction metrics.}
        \resumeItem{Automated application configuration via a \textbf{Python} script, improving environment setup time by 20 hours weekly.}
        \resumeItem{Created a \textbf{Node.js} service for real-time transaction handling, reducing processing latency by 30\% and increasing throughput.}
        \resumeItem{Implemented an event-driven system using \textbf{Kafka} managing 10,000+ transactions per second with zero data loss.}
        \resumeItem{Monitored system health using \textbf{Prometheus} and \textbf{Grafana}, improving incident detection and resolution speed by 40\%.}
        \resumeItem{Secured microservices with \textbf{OAuth2} and \textbf{JWT} tokens, reducing security vulnerabilities by 40\%.}
        \resumeItem{Streamlined CI/CD with \textbf{Jenkins}, integrating source control to cut deployment times by 30\%.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed RESTful APIs with \textbf{Node.js} and \textbf{Express.js}, expanding third-party integrations by 30\% and improving system flexibility.}
        \resumeItem{Migrated legacy systems to \textbf{AWS} cloud, decreasing operational costs by 20\% and improving application availability.}
        \resumeItem{Optimized \textbf{DynamoDB} access patterns, lowering data retrieval latency by 15\% and enhancing overall user experience.}
        \resumeItem{Wrote shell scripts for real-time system monitoring, cutting response downtime by 30\% and aiding faster troubleshooting.}
        \resumeItem{Established CI/CD pipelines using \textbf{GitHub Actions}, accelerating deployment speed by 40\% and improving reliability.}
        \resumeItem{Advocated and facilitated \textbf{Agile Scrum} implementation, resulting in 25\% faster feature delivery and tighter team coordination.}
        \resumeItem{Conducted extensive testing with \textbf{JUnit} and \textbf{Postman}, raising code quality and reliability above 95\%.}
        \resumeItem{Enhanced backend performance with \textbf{Java Spring MVC} and \textbf{Hibernate}, improving data processing efficiency.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-powered Document Query System} | Python, LangChain, OpenAI API, FAISS, Docker}{ }
        \resumeItemListStart
            \resumeItem{Implemented an AI-driven RAG pipeline enabling natural language queries over multiple documents, improving user information retrieval by 40\%.}
            \resumeItem{Deployed containerized application with \textbf{Docker} and automated workflows using \textbf{GitHub Actions}, achieving scalable and reliable production releases.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Cloud-Native Media Content Pipeline} | Java, Kubernetes, AWS, Docker}{ }
        \resumeItemListStart
            \resumeItem{Designed a scalable media content pipeline using \textbf{Kubernetes}, \textbf{Docker}, and \textbf{AWS}, improving content distribution throughput by 35\%.}
            \resumeItem{Developed RESTful APIs to manage complex content workflows, ensuring secure and timely processing of media rights and royalty payments.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Real-Time Transaction Monitoring Platform} | Node.js, React, Kafka, Prometheus, Grafana}{ }
        \resumeItemListStart
            \resumeItem{Built a full-stack platform handling real-time financial transactions using \textbf{Node.js}, \textbf{React}, and \textbf{Kafka}, reducing latency by 30\%.}
            \resumeItem{Integrated system observability with \textbf{Prometheus} and \textbf{Grafana} dashboards, enhancing issue detection and reducing downtime by 40\%.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}