\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Versatile \textbf{software engineer} with \textbf{5+ years} experience delivering backend and full stack solutions aligned with compliance and risk management demands.}
    \resumeItem{Skilled in \textbf{Java}, \textbf{JavaScript}, and \textbf{API development} with proven ability to build scalable backend systems and optimize database interactions.}
    \resumeItem{Experienced with \textbf{ServiceNow}, \textbf{Agile} methodologies, and \textbf{CI/CD pipelines} automating secure deployment processes in enterprise environments.}
    \resumeItem{Adept at leveraging \textbf{cloud platforms} and \textbf{containerization} to enhance solution scalability, reliability, and performance in compliance-driven contexts.}
    \resumeItem{Strong communicator with a demonstrated ability to collaborate effectively with cross-functional teams and support strategic technology roadmap initiatives.}
    \resumeItem{Interested and growing knowledge in \textbf{GRC/IRM} industry trends and \textbf{Machine Learning}, providing future-proof technology insight for risk and compliance applications.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java (8, 17 \& 21), JavaScript, TypeScript, SQL, Python, XML, Jelly scripting, Shell Scripting \\
                \textbf{Frameworks \& Backend:} & Spring Boot, Node.js, Express.js, Angular, React.js, ServiceNow Configuration, RESTful API design \\
                \textbf{Databases:} & PostgreSQL, MySQL, Oracle, MongoDB, Redis, NoSQL databases, optimized SQL queries \\
                \textbf{Cloud \& DevOps:} & GCP (BigQuery, PubSub), AWS, Azure, Docker, Kubernetes, Jenkins, GitHub Actions, Maven, Gradle, CI/CD pipelines \\
                \textbf{Testing \& Automation:} & JUnit, Mockito, Selenium, Postman, Cucumber, Integration and unit testing \\
                \textbf{Methodologies \& Tools:} & Agile (Scrum, SAFe), Rally, Git, OAuth2, JWT, Microservices Architecture, Machine Learning foundations \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Designed and configured \textbf{ServiceNow} solutions to streamline compliance workflows, enhancing operational efficiency across risk management systems.}
        \resumeItem{Developed scalable microservices using \textbf{Java} and \textbf{Spring Boot}, improving application uptime by 25\% and enabling seamless risk data processing.}
        \resumeItem{Implemented \textbf{RESTful APIs} with \textbf{GraphQL} and \textbf{AWS API Gateway}, lowering response times by 35\% while decreasing server load.}
        \resumeItem{Established robust CI/CD pipelines using \textbf{GitHub Actions} and \textbf{Jenkins}, increasing deployment frequency by 50\% and reducing errors.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries to improve performance by 20\% and ensure data integrity vital to risk and compliance applications.}
        \resumeItem{Enhanced front-end interfaces with \textbf{React.js} and \textbf{Angular}, boosting user engagement and compliance reporting accuracy by 15\%.}
        \resumeItem{Contributed to technology roadmap discussions identifying tooling gaps and security improvements for compliance-focused product evolutions.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Implemented backend systems using \textbf{Java} and \textbf{Spring Boot} for compliance and risk domain features, elevating transaction processing speed by 30\%.}
        \resumeItem{Maintained relational and NoSQL databases such as \textbf{Oracle}, \textbf{MySQL}, and \textbf{MongoDB} with optimized \textbf{SQL} queries improving data retrieval by 25\%.}
        \resumeItem{Built and integrated \textbf{Kafka}-based event-processing architecture handling over 10,000 transactions per second for compliance data feeds.}
        \resumeItem{Automated deployments with \textbf{Jenkins} and implemented secure authentication using \textbf{OAuth2} and \textbf{JWT}, reducing security incidents by 40\%.}
        \resumeItem{Created observability dashboards with \textbf{Grafana} and \textbf{Prometheus}, improving system monitoring and compliance issue response times by 30\%.}
        \resumeItem{Collaborated in scaled \textbf{Agile} environment using \textbf{SAFe} framework, enhancing team delivery speed by 25\% through streamlined sprint executions.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java}-based backend solutions with \textbf{Spring MVC} and \textbf{Hibernate} for secure compliance and data management applications.}
        \resumeItem{Designed and maintained \textbf{Node.js} \textbf{RESTful APIs} enhancing third-party integrations by 30\% in fintech and compliance workflows.}
        \resumeItem{Migrated legacy systems to \textbf{AWS} cloud, decreasing operational costs by 20\% and boosting availability for risk compliance services.}
        \resumeItem{Improved \textbf{DynamoDB} latency by 15\% through optimized data indexing supporting compliance rule enforcement use cases.}
        \resumeItem{Streamlined \textbf{CI/CD} processes with \textbf{GitHub Actions} automation, improving deployment speed and reliability by 40\%.}
        \resumeItem{Facilitated adoption of \textbf{Agile Scrum} practices improving project delivery accuracy by 25\% through enhanced team collaboration.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Compliance AI Risk Assistant} $|$ Python, LangChain, OpenAI API, ServiceNow, Docker}{ }
        \resumeItemListStart
            \resumeItem{Developed an AI-enabled tool integrating \textbf{ServiceNow} data and \textbf{OpenAI GPT} to provide contextual answers supporting compliance workflows.}
            \resumeItem{Utilized \textbf{LangChain} for embedding compliance documents and logs, improving query response accuracy by 30\% in risk assessments.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Risk & Compliance Microservices Platform} $|$ Java, Spring Boot, PostgreSQL, REST API, Docker, Kubernetes}{ }
        \resumeItemListStart
            \resumeItem{Engineered a microservices architecture handling compliance data through REST APIs, reducing processing latency by 25\%.}
            \resumeItem{Deployed on Kubernetes with Docker containers ensuring 99.9\% uptime and scalable infrastructure supporting 1000+ daily active users.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Secure API Gateway with AI Monitoring} $|$ Node.js, Express.js, GCP PubSub, TensorFlow, MongoDB}{ }
        \resumeItemListStart
            \resumeItem{Created secure RESTful APIs with \textbf{Node.js} and \textbf{Express}, integrating \textbf{GCP PubSub} for event-driven monitoring.}
            \resumeItem{Implemented an AI model using \textbf{TensorFlow} to detect anomalous patterns in API usage, enhancing security and compliance by 20\%.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}