\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Software engineer with expertise in \textbf{automation, systems integration}, and workflow optimization, delivering scalable and reliable software solutions.}
    \resumeItem{Skilled in \textbf{software engineering}, systems testing, and acceptance testing processes with strong experience in \textbf{C\# and algorithms} development.}
    \resumeItem{Proficient in managing \textbf{software projects} and collaborating on \textbf{motion controls, robotics design}, and semiconductor systems engineering.}
    \resumeItem{Experienced in \textbf{data collection}, measurement calibration, and metrology techniques to ensure system accuracy and quality standards.}
    \resumeItem{Strong problem-solving skills combined with developing and deploying automated \textbf{workflows} and testing frameworks improving system reliability.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & C\#, Java, Python, JavaScript, SQL, Shell Scripting, Gherkin \\
                \textbf{Automation \& Testing:} & JUnit, Mockito, Selenium, Postman, Acceptance Testing, Systems Testing, Cucumber, Robot Framework \\
                \textbf{Systems \& Software Engineering:} & Systems Integration, Software Project Management, Algorithms, Microservices Architecture, CI/CD Pipelines \\
                \textbf{Controls \& Robotics:} & Motion Controls, Robotics Design and Production, Systems Engineering, Calibration and Metrology \\
                \textbf{Cloud \& DevOps:} & AWS, Azure, Docker, Kubernetes, Jenkins, GitHub Actions, Terraform \\
                \textbf{Databases \& Data Collection:} & PostgreSQL, Oracle, MongoDB, Redis, Prometheus, Data Acquisition Techniques \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Developed and automated \textbf{workflows} integrating \textbf{C\# and Java} services, improving system efficiency by 30\% and reducing manual errors.}
        \resumeItem{Engineered \textbf{software systems} with \textbf{Spring Boot} and \textbf{AWS}, enhancing system scalability and uptime by 25\% across critical applications.}
        \resumeItem{Designed and executed \textbf{acceptance and system tests} with \textbf{JUnit} and \textbf{Selenium}, increasing test coverage to over 98\% and reliability.}
        \resumeItem{Led \textbf{systems integration} across multiple services using \textbf{GraphQL} and REST APIs, cutting latency by 35\% and improving data flow.}
        \resumeItem{Managed \textbf{software projects} and collaborated on \textbf{motion control} software modules, improving product performance by 20\%.}
        \resumeItem{Implemented \textbf{vector similarity search} using Redis to enhance AI-driven document query efficiency in internal tools.}
        \resumeItem{Automated \textbf{CI/CD pipelines} with \textbf{Jenkins} and \textbf{Docker}, accelerating deployment frequency by 50\% and reducing downtime.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries and monitoring dashboards, improving performance and observability by 20\%.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Developed automated \textbf{calibration and measurement} software modules for \textbf{semiconductor} equipment, increasing accuracy by 25\%.}
        \resumeItem{Integrated \textbf{systems engineering} solutions using \textbf{Java}, \textbf{Spring Boot}, and \textbf{Kafka}, handling 10,000 TPS with low latency.}
        \resumeItem{Created \textbf{automation workflows} for banking platforms, reducing manual processing time by 30\% and improving service reliability.}
        \resumeItem{Enhanced system security by implementing \textbf{OAuth2} and \textbf{JWT}, decreasing security incidents by 40\%.}
        \resumeItem{Developed \textbf{real-time monitoring} dashboards with \textbf{Grafana} and \textbf{Prometheus}, boosting issue detection speed by 35\%.}
        \resumeItem{Led \textbf{system testing} using automated and manual methods to increase quality assurance and reduce bugs by 28\%.}
        \resumeItem{Streamlined \textbf{CI/CD} with \textbf{Jenkins} integrations, cutting deployment times by 30\% and improving release reliability.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented \textbf{system integration} solutions for supply chain software using \textbf{Java} and \textbf{Spring MVC}, improving throughput 20\%.}
        \resumeItem{Developed \textbf{automation scripts} in \textbf{Python} and shell for data collection and monitoring, reducing manual tasks by 30 hours weekly.}
        \resumeItem{Built \textbf{RESTful APIs} enabling third-party integration, boosting capabilities by 30\% and expanding system flexibility.}
        \resumeItem{Conducted \textbf{acceptance testing} with \textbf{JUnit} and \textbf{Postman}, enhancing product stability rating above 95\%.}
        \resumeItem{Migrated legacy applications to \textbf{AWS cloud}, reducing costs and improving availability by 20\%.}
        \resumeItem{Implemented monitoring with \textbf{DynamoDB} optimizations, reducing data access latency by 15\%.}
        \resumeItem{Automated CI/CD pipelines using \textbf{GitHub Actions}, increasing deployment speed by 40\%.}
        \resumeItem{Adopted \textbf{Agile methodologies} accelerating delivery by 25\% and improving team collaboration.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-based Document Workflow Automation} | Python, LangChain, OpenAI API, Redis, Docker}{ }
        \resumeItemListStart
            \resumeItem{Developed an AI-augmented document processing pipeline using \textbf{RAG} architecture, automating data extraction and improving response accuracy by 40\%.}
            \resumeItem{Implemented vector similarity search with \textbf{Redis} enhancing query speed by 50\% and integrating seamlessly into existing document management workflows.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Precision Measurement and Calibration System} | C\#, .NET, SQL Server, Robotics}{ }
        \resumeItemListStart
            \resumeItem{Engineered a comprehensive calibration software for robotic subsystems, improving measurement accuracy by 30\% and reducing downtime by 25\%.}
            \resumeItem{Integrated data collection workflows with real-time analytics, enhancing predictive maintenance and system performance metrics.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Automated Motion Control System} | C\#, Robotics, Azure IoT, Algorithms}{ }
        \resumeItemListStart
            \resumeItem{Designed and implemented motion control algorithms for robotic arms, increasing precision by 35\% and reducing cycle time by 20\%.}
            \resumeItem{Leveraged \textbf{Azure IoT} for real-time telemetry and remote system calibration, improving operational reliability significantly.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}