\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Experienced \textbf{software developer} with \textbf{5+ years} delivering secure, scalable, and efficient applications emphasizing HR and enterprise software needs.}
    \resumeItem{Skilled in \textbf{API development}, microservices, and data pipelines aligned with Agile methodologies to improve business workflows and stakeholder communication.}
    \resumeItem{Proficient with \textbf{Java, Spring Boot, MongoDB, Postgres, GraphQL}, and \textbf{REST}, driving process optimization and application performance enhancements.}
    \resumeItem{Adept at collaborating with cross-functional teams and translating complex business requirements into functional software solutions supporting HR systems.}
    \resumeItem{Strong communication and analytical skills with a proven ability to manage full software development lifecycle and drive continuous process improvements.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Frameworks:} & Java (17 \& 21), Spring Boot, Python, Golang, Node.js, Express.js, TypeScript, React.js \\
                \textbf{Integration \& API Technologies:} & REST, GraphQL, Microservices, APIs, Workday ecosystem familiarity \\
                \textbf{Databases \& Storage:} & MongoDB, PostgreSQL, Oracle, Redis \\
                \textbf{Cloud \& DevOps:} & AWS (ECS, API Gateway), Docker, Kubernetes, Jenkins, GitHub Actions, CI/CD pipelines \\
                \textbf{Testing \& Agile:} & JUnit, Mockito, Selenium, Postman, Agile (Scrum/Kanban) methodologies \\
                \textbf{Tools \& Methodologies:} & SDLC, OAuth2, JWT, RAG (Retrieval-Augmented Generation), Agentic AI, Prompt Engineering \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Developed and maintained \textbf{Java Spring Boot} microservices improving uptime by 25\% while ensuring seamless \textbf{API} integration and data integrity.}
        \resumeItem{Led design of scalable \textbf{GraphQL} APIs through \textbf{AWS API Gateway}, decreasing response times by 35\% and reducing server load efficiently.}
        \resumeItem{Collaborated with HR and business partners to translate requirements into software solutions, enhancing workflows and system user satisfaction by 15\%.}
        \resumeItem{Implemented CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker}, accelerating deployment frequency by 50\% with automated quality assurance.}
        \resumeItem{Engineered \textbf{PostgreSQL} query optimizations improving database performance by 20\%, ensuring reliable support for business-critical applications.}
        \resumeItem{Pioneered integration of \textbf{Agentic RAG} AI-powered retrieval system using embeddings and \textbf{Redis} for enhanced contextual document search capabilities.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Delivered enterprise-level \textbf{Java Spring Boot} microservices handling core banking features with robust API-based communication increasing efficiency by 30\%.}
        \resumeItem{Enhanced security protocols by integrating \textbf{OAuth2} and \textbf{JWT}, reducing vulnerabilities and improving secure access management by 40\%.}
        \resumeItem{Built real-time data processing middleware in \textbf{Node.js} enabling swift financial transactions and improving system throughput by 30\%.}
        \resumeItem{Implemented event-driven architecture with \textbf{Kafka} managing over 10,000 transactions per second with high availability and fault tolerance.}
        \resumeItem{Created comprehensive \textbf{Grafana} dashboards with \textbf{Prometheus} metrics, improving observability of system health and reducing downtime.}
        \resumeItem{Streamlined build and deployment via integration of \textbf{Jenkins} with \textbf{SVN}, accelerating release cycles by 30\% and enhancing DevOps workflow.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Built scalable \textbf{RESTful APIs} with \textbf{Node.js} and \textbf{Express.js} improving third-party integrations and expanding product reach by 30\%.}
        \resumeItem{Migrated legacy systems to \textbf{AWS} cloud, reducing costs by 20\% and increasing deployment agility with cloud-native technologies.}
        \resumeItem{Optimized \textbf{DynamoDB} schema to minimize latency by 15\%, enhancing real-time data retrieval for business applications.}
        \resumeItem{Improved CI/CD workflows using \textbf{GitHub Actions}, accelerating deployment speed by 40\% while enforcing code quality with automated tests.}
        \resumeItem{Led Agile and Scrum adoption improving project delivery time by 25\% and ensuring better alignment with client objectives and requirements.}
        \resumeItem{Developed Linux shell scripts for monitoring system performance and reducing incident response times by 30\% ensuring high availability.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-Powered Document Query System} | Python, LangChain, OpenAI API, FAISS, Docker}{ }
        \resumeItemListStart
            \resumeItem{Designed an AI-driven RAG system for HR document search using embeddings and vector databases, achieving highly accurate contextual answers.}
            \resumeItem{Streamlined natural language querying across multiple PDFs improving user interaction time by 40\% with scalable dockerized deployment.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Enterprise Integration Microservices} | Java Spring Boot, GraphQL, PostgreSQL, AWS ECS}{ }
        \resumeItemListStart
            \resumeItem{Built microservices with \textbf{Java} and \textbf{Spring Boot} handling complex HR integrations, reducing API response latency by 35\%.}
            \resumeItem{Deployed on AWS ECS with CI/CD pipelines, improving application uptime by 25\% and streamlining cross-system data integrity processes.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Real-Time Event Processing System} | Node.js, Kafka, Kubernetes, MongoDB}{ }
        \resumeItemListStart
            \resumeItem{Developed event-driven microservices handling 10,000+ transactions/second with \textbf{Kafka} and \textbf{Kubernetes}, enhancing transaction reliability.}
            \resumeItem{Monitored system health with custom dashboards, reducing latency fluctuations by 20\% and supporting seamless event flow in financial applications.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}