```latex
\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Versatile \textbf{Backend Engineer} with over \textbf{5 years} of experience in designing and building scalable \textbf{software solutions} that support business goals and improve processes.} \vspace{-3pt}
    \resumeItem{Proficient in \textbf{Ruby, JavaScript}, and \textbf{SQL}, skilled in optimizing backend services to handle high transaction volumes and enhance security measures.} \vspace{-3pt}
    \resumeItem{Strong advocate for \textbf{continuous improvement}, leveraging automation and experimentation to foster innovation and maintain high-quality standards.} \vspace{-3pt}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
    \vspace{-14pt}
    \begin{table}[h]
        \fontsize{9pt}{10pt}\selectfont
        \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
            \textbf{Programming \& Scripting:} & Ruby, JavaScript, TypeScript, SQL, Python, Java, C++ \\
            \textbf{Frameworks \& Libraries:} & Spring Boot, Node.js, React.js, Angular, Cypress, Selenium \\
            \textbf{Backend \& Databases:} & RESTful APIs, SQL, NoSQL, Redis, MongoDB, PostgreSQL \\
            \textbf{DevOps \& Tools:} & Docker, Kubernetes, Jenkins, GitLab CI/CD, AWS, Azure \\
            \textbf{Testing \& Automation:} & JUnit, Mockito, Postman, Cypress, Jest, Selenium \\
            \textbf{Methodologies:} & Agile (Scrum/Kanban), CI/CD, Domain Driven Design \\
        \end{tabular}
    \end{table}
\vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Developed \textbf{scalable services} using \textbf{Ruby} and \textbf{JavaScript}, enhancing system capacity to manage a 30\% increase in data transactions.}
        \resumeItem{Collaborated with cross-functional teams to establish a robust test automation framework, achieving 95\% code coverage and minimizing production defects.}
        \resumeItem{Refactored critical backend components for improved integration with \textbf{RESTful APIs}, reducing response times by \textbf{25\%} and boosting platform efficiency.}
        \resumeItem{Implemented \textbf{security best practices} in backend services, reducing vulnerability exposure and ensuring client data protection and integrity.}
        \resumeItem{Optimized \textbf{SQL} and \textbf{NoSQL} query performance, accelerating database access times by \textbf{40\%} and significantly enhancing user satisfaction.}
        \resumeItem{Led \textbf{continuous delivery} initiatives, streamlining deployment processes and decreasing deployment timeframes by \textbf{50\%}.}
        \resumeItem{Devised innovative solutions to migrate legacy systems to modern cloud infrastructure, achieving \textbf{20\%} cost savings and operational efficiency.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Integrated advanced analytical tools into core applications, enabling real-time data insights and improving decision-making processes by \textbf{30\%}.}
        \resumeItem{Designed a microservices-oriented architecture that elevated system throughput by 35\% while maintaining high availability and reliability.}
        \resumeItem{Launched comprehensive documentation practices that improved knowledge transfer and new team member onboarding efficiency by \textbf{50\%}.}
        \resumeItem{Enhanced backend service reliability by implementing effective fault-tolerant strategies, reducing system downtime incidents by \textbf{20\%}.}
        \resumeItem{Automated testing and deployment processes, achieving a deployment accuracy rate of \textbf{99\%} and reducing manual intervention requirements significantly.}
        \resumeItem{Implemented robust data handling protocols, securing sensitive information and aligning services with regulatory compliance requirements.}
        \resumeItem{Collaborated with product managers to prioritize development tasks, aligning 90\% of deliverables with critical business and customer needs.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Executed efficient migration of complex systems to cloud infrastructure, resulting in operational cost reductions of about \textbf{30\%}.}
        \resumeItem{Advanced API development and testing practices by implementing \textbf{Cypress} and \textbf{Jest}, enhancing frontend and backend integration reliability.}
        \resumeItem{Designed and maintained scalable backend architecture, significantly improving performance during peak traffic by \textbf{40\%}.}
        \resumeItem{Optimized data storage solutions, reducing data access latency by \textbf{25\%} and enhancing overall application responsiveness.}
        \resumeItem{Collaborated in designing data processing pipelines for efficient handling of high transaction volumes, supporting business growth.}
        \resumeItem{Streamlined CI/CD workflows through automated build and deployment strategies, increasing deployment frequency by \textbf{60\%}.}
        \resumeItem{Contributed to agile project management processes, enhancing project delivery accuracy rates by approximately \textbf{15\%}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Data Safety Platform} | Ruby, JavaScript, SQL, AWS, Docker, Kubernetes}{}
        \resumeItemListStart
            \resumeItem{Developed a robust backend service to safeguard sensitive data, achieving a \textbf{50\%} reduction in data exposure risks through advanced security mechanisms.}
            \resumeItem{Leveraged \textbf{Docker} and \textbf{Kubernetes} for streamlined deployment processes, enhancing development cycle efficiency by \textbf{35\%}.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{AI-Driven Analytics System} | Python, TensorFlow, Azure, SQL, RESTful APIs}{}
        \resumeItemListStart
            \resumeItem{Implemented an AI-based platform for real-time analytics, boosting data processing capabilities to manage over \textbf{100,000 requests per second}.}
            \resumeItem{Enhanced analytical accuracy by \textbf{45\%} through the integration of \textbf{TensorFlow} models, improving data-driven decision-making.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Scalable Payment Gateway} | Java, Spring Boot, Redis, Microservices, Jenkins}{}
        \resumeItemListStart
            \resumeItem{Created a scalable payment processing gateway handling a 40\% increase in transaction volume while maintaining accuracy and service reliability.}
            \resumeItem{Optimized codebase to reduce latency by \textbf{30\%}, leveraging \textbf{Spring Boot} and \textbf{Redis} for high availability and performance.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}
```