```latex
\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{\textbf{Backend Engineer} with 5+ years of experience delivering scalable, secure and efficient \textbf{web-based solutions} using industry best practices.} \vspace{-3pt}
    \resumeItem{Proficient in \textbf{Ruby, JavaScript}, and \textbf{SQL} with a focus on developing \textbf{RESTful APIs}, high-impact features, and \textbf{scalable services}.} \vspace{-3pt}
    \resumeItem{Demonstrated ability to work collaboratively with product and design teams, ensuring high quality and customer satisfaction at every stage of development.} \vspace{-3pt}
    \resumeItem{Adept at employing \textbf{test automation} to enhance code reliability and implement \textbf{security best practices} to protect data integrity.} \vspace{-3pt}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Ruby, Java, JavaScript, SQL, TypeScript, Python, Go, Shell Scripting \\
                \textbf{Frameworks \& Backend:} & Node.js, Ruby on Rails, Spring Boot, Express.js \\
                \textbf{Databases:} & SQL, PostgreSQL, MongoDB, DynamoDB, Redis \\ 
                \textbf{Testing \& Automation:} & Cypress, JUnit, Selenium, Postman, Mockito \\ 
                \textbf{Cloud \& DevOps:} & AWS, Docker, Kubernetes, Jenkins, GitHub Actions  \\
                \textbf{Methodologies:} & Agile (Scrum/Kanban), CI/CD Automation, Domain Driven Design \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Engineered microservices using \textbf{Java, Spring Boot, and AWS}, boosting application reliability and scalability by 25\% and enhancing performance metrics.}
        \resumeItem{Developed user interfaces in \textbf{React.js} to increase engagement by 40\% while maintaining seamless interactions and higher customer satisfaction.}
        \resumeItem{Refined backend systems transitioning from monolithic to microservices, increasing deployment efficiency and reducing downtimes by 30\%.}
        \resumeItem{Implemented \textbf{Redis} technology for real-time data handling, enhancing query response times and achieving 360-degree application insight.}
        \resumeItem{Enhanced API efficiency using \textbf{GraphQL}, reducing latency and server loads significantly during high user activity periods.}
        \resumeItem{Established comprehensive \textbf{JUnit} test frameworks, improving test coverage to above 98\%, enhancing software quality and reliability.}
        \resumeItem{Optimized \textbf{SQL} operations, resulting in 20\% better performance by addressing bottlenecks and ensuring robust data-processing capabilities.}
        \resumeItem{Architectured \textbf{CI/CD} pipelines with \textbf{Jenkins} for automated and frequent deployments, boosting delivery efficiency by 50\%.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Architected core banking features with \textbf{Java, Spring Boot}, ensuring robust services and swift, client-first interfaces.}
        \resumeItem{Transformed UI with \textbf{React}, optimizing user journeys to escalate user retention and minimize friction.}
        \resumeItem{Innovated with \textbf{Python} scripts for configuration automation, saving 20 hours weekly on recurring tasks.}
        \resumeItem{Constructed a high-speed \textbf{Node.js} and \textbf{Kafka} workflow to streamline transactions, handling 10,000+ TPS.}
        \resumeItem{Designed \textbf{Grafana} dashboards, with \textbf{Prometheus} integration, for enhanced monitors boosting system observability.}
        \resumeItem{Safeguarded data with \textbf{OAuth2/JWT}, reducing security incidents by 40\% through rigorous protocols and checks.}
        \resumeItem{Optimized CI/CD by integrating \textbf{SVN} with \textbf{Jenkins}, cutting deployment times by 30\%, improving cycles.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Spearheaded backend structures with \textbf{Java} and \textbf{Spring MVC}, elevating data handling by 30\%.}
        \resumeItem{Engineered seamless \textbf{Node.js} APIs, broadening third-party integrations and product functionality by 30\%.}
        \resumeItem{Boosted application integrity with \textbf{JUnit/Postman}, enhancing reliability to over 95\%.}
        \resumeItem{Facilitated AWS migration simplifying deployments, reducing costs by 20\% through strategic resource use.}
        \resumeItem{Fine-tuned \textbf{DynamoDB} processes, achieving higher response speeds with 15\% reduced latency.}
        \resumeItem{Adopted \textbf{Agile/Scrum} methodologies, improving project timelines by 25\% through iterative delivery.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Automated Risk Assessment} $|$ Python, Flask, AWS, Ruby, Docker}{ }
        \resumeItemListStart
            \resumeItem{Developed a system to automate risk calculations, leveraging \textbf{Flask} and \textbf{AWS} for scalable performance and quick adaptation to market changes.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Data-Driven Insights Platform} $|$ Node.js, REST API, SQL, Docker}{ }
        \resumeItemListStart
            \resumeItem{Created a dynamic insights delivery service using \textbf{Node.js} and SQL to streamline data into cohesive, actionable analytics for diverse sectors.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{AI-Powered Document Parsing} $|$ Python, TensorFlow, Kubernetes, Redis}{ }
        \resumeItemListStart
            \resumeItem{Generated an AI model with \textbf{TensorFlow} for document parsing, boosting operational efficiency by 30\% and reducing manual processing time.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}
```