\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Results-driven software engineer with 5+ years designing and deploying scalable backend services and APIs, improving performance and reliability.}
    \resumeItem{Proficient in Ruby, JavaScript, SQL, and NoSQL databases with solid expertise in RESTful API development and microservices architecture.}
    \resumeItem{Skilled in test automation with frameworks like Cypress, enhancing code quality and deployment frequency in fast-paced environments.}
    \resumeItem{Experienced in collaborating cross-functionally to deliver secure, maintainable features impacting hundreds of thousands of transactions daily.}
    \resumeItem{Strong advocate of continuous delivery, Domain Driven Design, and agile methodologies, driving improvements in system stability and scalability.}
    \resumeItem{Committed to innovation, learning, and fostering team-oriented culture aligned with organizational objectives and customer-centric solutions.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Ruby, JavaScript, TypeScript, Python, Java, SQL, PL/SQL, Shell Scripting \\
                \textbf{Frameworks \& Backend:} & Node.js, Express.js, Ruby on Rails, Spring Boot, RESTful API development, Microservices \\
                \textbf{Databases:} & PostgreSQL, MongoDB, DynamoDB, Redis, Cassandra \\
                \textbf{Testing \& Automation:} & Cypress, JUnit, Mockito, Selenium, Postman, Jest \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, API Gateway, CodePipeline), Docker, Kubernetes, Jenkins, GitHub Actions \\
                \textbf{Methodologies \& Practices:} & Domain Driven Design, Continuous Delivery, Extreme Programming (XP), Agile (Scrum/Kanban) \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Engineered and deployed scalable microservices using \textbf{Java}, \textbf{Spring Boot}, and \textbf{AWS ECS}, improving uptime by 25\%.}
        \resumeItem{Developed maintainable backend APIs and frontend components with \textbf{React.js}, increasing end-user engagement by 40\%.}
        \resumeItem{Migrated monolithic applications to microservices, cutting deployment duration by 30\% and enhancing platform scalability.}
        \resumeItem{Implemented an \textbf{Agentic RAG} system leveraging \textbf{Redis} embeddings for high relevance and performance in query responses.}
        \resumeItem{Integrated \textbf{GraphQL} via \textbf{AWS API Gateway}, reducing server load and improving response time by 35\%.}
        \resumeItem{Established comprehensive automated testing using \textbf{JUnit} and \textbf{Mockito}, achieving over 98\% test coverage.}
        \resumeItem{Optimized complex \textbf{PostgreSQL} queries, improving database efficiency and application response times by 20\%.}
        \resumeItem{Designed CI/CD pipelines with \textbf{Jenkins}, \textbf{Docker}, and \textbf{AWS CodePipeline}, increasing deployment frequency by 50\%.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Developed core banking microservices using \textbf{Java} and \textbf{Spring Boot}, improving account management and customer interactions.}
        \resumeItem{Enhanced frontend UX by building responsive components with \textbf{React} and \textbf{Redux}, raising client satisfaction scores.}
        \resumeItem{Automated configuration management with \textbf{Python} scripts, boosting team efficiency by saving 20 hours per week.}
        \resumeItem{Created \textbf{Node.js} middleware enabling real-time cash position processing, increasing throughput by 30\%.}
        \resumeItem{Implemented \textbf{Kafka}-based event-driven systems supporting 10,000+ transactions per second reliably.}
        \resumeItem{Built performance dashboards with \textbf{Grafana} and \textbf{Prometheus} for enhanced monitoring and operational insights.}
        \resumeItem{Fortified security via \textbf{OAuth2} and \textbf{JWT}, cutting security incidents by 40\%.}
        \resumeItem{Streamlined CI/CD with \textbf{SVN} and \textbf{Jenkins}, reducing deployment times by 30\%.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Designed scalable Supply Chain applications utilizing \textbf{Java}, \textbf{Spring MVC}, and \textbf{Hibernate}, enhancing processing speed.}
        \resumeItem{Developed RESTful APIs with \textbf{Node.js} and \textbf{Express.js}, increasing third-party integrations by 30\%.}
        \resumeItem{Boosted application reliability to over 95\% through rigorous \textbf{JUnit} testing and \textbf{Postman} validation.}
        \resumeItem{Led legacy system migration to \textbf{AWS}, reducing infrastructure costs by 20\%.}
        \resumeItem{Optimized \textbf{DynamoDB} queries, decreasing data access latency by 15\%.}
        \resumeItem{Automated system monitoring with \textbf{Shell} scripts, speeding up performance issue response by 30\%.}
        \resumeItem{Enhanced deployment speeds by 40\% implementing CI/CD pipelines with \textbf{GitHub Actions}.}
        \resumeItem{Facilitated Agile adoption improving delivery efficiency and team collaboration by 25\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI Document Query System} | Python, LangChain, OpenAI API, FAISS, Docker}{}
        \resumeItemListStart
            \resumeItem{Developed an AI-powered RAG pipeline enabling natural language queries across multiple documents, delivering contextually relevant answers.}
            \resumeItem{Containerized the system with Docker and automated deployment through GitHub Actions, ensuring consistent and scalable releases.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{High Scale Backend Services} | Go, Gin, PostgreSQL, Redis, Docker, Kubernetes}{}
        \resumeItemListStart
            \resumeItem{Built scalable backend with secure authentication using JWT/PASETO, increasing reliability and throughput by 30\% across services.}
            \resumeItem{Integrated Redis caching and background workers, improving service efficiency by 25\% and reducing deployment times by 40\% via CI/CD.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Real-time Event Processing Platform} | Docker, Kubernetes, Apache Kafka, Neo4j}{}
        \resumeItemListStart
            \resumeItem{Engineered a graph analytics platform using Kafka and Neo4j, supporting 1000+ concurrent requests with efficient load balancing.}
            \resumeItem{Deployed on Kubernetes with Docker for container orchestration, ensuring high availability and fault tolerance.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}