\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Results-driven software engineer with 5+ years delivering scalable backend services and robust APIs, emphasizing reliability and security for high-volume transactions.} \vspace{-3pt}
    \resumeItem{Proficient in \textbf{Ruby, JavaScript}, SQL, NoSQL, and designing RESTful APIs supporting asynchronous processing in distributed service architectures.} \vspace{-3pt}
    \resumeItem{Experienced in test automation using Cypress and other frameworks, driving quality and continuous delivery through strong DevOps and XP practices.} \vspace{-3pt}
    \resumeItem{Skilled collaborator with product and design teams to innovate and deploy client-focused features impacting mission-critical data platforms.} \vspace{-3pt}
    \resumeItem{Strong ownership of feature lifecycle from design through deployment and maintenance, maintaining high documentation standards and security best practices.} \vspace{-3pt}
    \resumeItem{Passionate about continuous learning and fostering team-oriented cultures that promote experimentation, automation, and improvement.} \vspace{-3pt}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Ruby, JavaScript, TypeScript, SQL, PL/SQL, Python, Shell Scripting \\
                \textbf{Backend \& Frameworks:} & Spring Boot, Node.js, Express.js, Ruby on Rails, RESTful API development, Microservices, OAuth2, JWT \\
                \textbf{Databases:} & PostgreSQL, Oracle, MongoDB, DynamoDB, Redis, Cassandra \\
                \textbf{Testing \& Automation:} & Cypress, JUnit, Mockito, Selenium, Postman, Jest, CI/CD with Jenkins, GitHub Actions \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, ECS, S3, API Gateway, CodePipeline), Docker, Kubernetes, Terraform \\
                \textbf{Methodologies \& Practices:} & Agile (Scrum/Kanban), Domain Driven Design, XP practices, Continuous Delivery, Component-based Design \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Architected and deployed scalable \textbf{microservices} using \textbf{Java}, \textbf{Spring Boot}, and \textbf{AWS ECS}, improving uptime and transaction throughput by 25\%.}
        \resumeItem{Engineered efficient user interfaces using \textbf{React.js}, facilitating a 40\% increase in user engagement and elevating customer satisfaction scores by 15\%.}
        \resumeItem{Transitioned legacy monoliths to microservices, reducing deployment cycle time by 30\%, while enhancing scalability and resilience for critical applications.}
        \resumeItem{Implemented \textbf{Redis}-based top-k similarity search for RAG system, improving data retrieval response and relevancy for internal knowledge base queries.}
        \resumeItem{Integrated \textbf{GraphQL} APIs via \textbf{AWS API Gateway}, reducing backend response latency by 35\%, significantly improving application performance during peak loads.}
        \resumeItem{Established comprehensive unit and integration test coverage using \textbf{JUnit} and \textbf{Mockito}, elevating code stability and maintainability above 98\%.}
        \resumeItem{Optimized complex \textbf{PostgreSQL} queries and NoSQL data handling, enhancing database response times by 20\% for core business workflows.}
        \resumeItem{Devised and maintained scalable CI/CD workflows with \textbf{Jenkins}, \textbf{Docker}, and \textbf{AWS CodePipeline}, increasing deployment frequency by 50\%.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Developed modular backend features for core banking using \textbf{Java}, \textbf{Spring Boot}, and \textbf{Maven}, within a secure, scalable microservices architecture.}
        \resumeItem{Built responsive web apps using \textbf{React} and \textbf{Redux}, improving loan platform user experience and customer workflow efficiency significantly.}
        \resumeItem{Automated environment configurations using \textbf{Python} scripts, saving 20 weekly hours in operational setup and configuration tasks.}
        \resumeItem{Created \textbf{Node.js} middleware to handle real-time financial transactions, accelerating processing speeds by 30\%.}
        \resumeItem{Designed event-driven \textbf{Kafka} architecture supporting over 10,000 transactions per second with high reliability and fault tolerance.}
        \resumeItem{Constructed detailed monitoring dashboards using \textbf{Grafana} and \textbf{Prometheus} to enhance system observability and performance tracking.}
        \resumeItem{Enhanced system security with OAuth2 and JWT integration, decreasing security incidents by 40\% and strengthening data protection.}
        \resumeItem{Improved CI/CD pipelines by integrating \textbf{SVN} with \textbf{Jenkins}, reducing release times by 30\%, boosting delivery efficiency.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Implemented high-performance supply chain applications using \textbf{Java}, \textbf{Spring MVC}, and \textbf{Hibernate}, enhancing data processing efficiency.}
        \resumeItem{Developed and maintained \textbf{RESTful APIs} with \textbf{Node.js} and \textbf{Express.js}, increasing third-party integration capabilities by 30\%.}
        \resumeItem{Devised rigorous testing strategies using \textbf{JUnit} and \textbf{Postman}, improving application reliability to over 95\%.}
        \resumeItem{Migrated legacy systems to \textbf{AWS} cloud, reducing operational costs by 20\% and improving availability.}
        \resumeItem{Optimized \textbf{DynamoDB} storage with indexing improvements, decreasing data access latency by 15\%.}
        \resumeItem{Created Linux shell scripts for real-time system monitoring, lowering issue response times by 30\%.}
        \resumeItem{Streamlined CI/CD pipelines with \textbf{GitHub Actions}, accelerating deployment speed by 40\%.}
        \resumeItem{Led Agile and Scrum adoption, enhancing team delivery speed by 25\% and project transparency.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-Driven Document Query System} | Python, LangChain, OpenAI API, FAISS}{ }
        \resumeItemListStart
            \resumeItem{Developed an AI-based RAG pipeline to query PDFs using natural language, delivering precise and contextually relevant answers efficiently.}
            \resumeItem{Containerized the system with Docker and automated deployments with GitHub Actions to ensure robust scalable access to document data.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Secure Microservices Backend Platform} | Go, Gin, PostgreSQL, JWT, Redis, Docker, Kubernetes}{ }
        \resumeItemListStart
            \resumeItem{Designed and deployed a secure backend service with authentication using JWT and PASETO, improving scalability and reliability by 30\%.}
            \resumeItem{Implemented efficient caching and background processing with Redis, reducing response times and deployment intervals by up to 40\%.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Real-time Event Processing with Kafka and Kubernetes} | Docker, Kubernetes, Apache Kafka, Neo4j}{ }
        \resumeItemListStart
            \resumeItem{Built an event-driven graph analytics platform capable of handling 1000+ concurrent requests using Kafka and Kubernetes for scalable performance.}
            \resumeItem{Integrated Neo4j graph algorithms for insightful data analysis and maintained system reliability through container orchestration with Kubernetes.}
        \resumeItemListEnd
        \vspace{-12pt}

    \resumeSubHeadingListEnd

\end{document}