\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Experienced \textbf{software engineer} with 5+ years designing and developing rich user interfaces and components using \textbf{C#}, \textbf{WPF}, and \textbf{C++} for complex real-world applications.} \vspace{-3pt}
    \resumeItem{Proficient in asynchronous programming and Task Parallel Library for enhancing performance and responsiveness in agile software development environments.} \vspace{-3pt}
    \resumeItem{Skilled in object-oriented design patterns including \textbf{MVVM} to build maintainable and scalable software solutions supporting 2D and 3D workflows.} \vspace{-3pt}
    \resumeItem{Strong collaborative skills working across teams to deliver quality software with expertise in diagnosing and resolving software behaviors and failures.} \vspace{-3pt}
    \resumeItem{Experienced in designing intuitive user interfaces that simplify complex workflows while maintaining flexibility for dynamic scenarios and unknown use cases.} \vspace{-3pt}
    \resumeItem{Committed to Agile methodologies and continuous integration to build, test, and ship high-quality software in demanding and evolving environments.} \vspace{-3pt}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming:} & C\#, C++ (including C++11 and modern idioms), Python, Java, JavaScript, TypeScript \\
                \textbf{Frameworks \& UI:} & WPF, MVVM, .NET, React.js, Angular, Material UI \\
                \textbf{Asynchronous \& Parallel Programming:} & Task Parallel Library, Async/Await, Event-driven Architecture \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3), Docker, Kubernetes, Jenkins, CI/CD Pipelines \\
                \textbf{Databases:} & PostgreSQL, Oracle, MongoDB, Redis \\
                \textbf{Methodologies \& Tools:} & Agile (Scrum/Kanban), Git, JIRA, Unit Testing (JUnit, NUnit), Design Patterns \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Implemented user interface components using \textbf{C#} and \textbf{React.js}, enhancing application responsiveness and user interaction by 30\%.}
        \resumeItem{Applied \textbf{asynchronous programming} techniques with \textbf{Task Parallel Library} to improve backend service scalability and reduce latency by 25\%.}
        \resumeItem{Collaborated in an agile team to design and build software frameworks supporting 2D and 3D geospatial data workflows for enterprise clients.}
        \resumeItem{Engineered integration of \textbf{microservices} using \textbf{Spring Boot} and \textbf{AWS ECS}, achieving a 20\% improvement in deployment frequency.}
        \resumeItem{Developed automated unit and integration tests increasing software reliability by over 95\%, utilizing \textbf{JUnit} and \textbf{NUnit} frameworks.}
        \resumeItem{Optimized database queries in \textbf{PostgreSQL} and enhanced caching layers with \textbf{Redis}, reducing data access times by 15\%.}
        \resumeItem{Led CI/CD pipeline improvements using \textbf{Jenkins} and \textbf{Docker}, shortening release cycles by 40\% and improving deployment consistency.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented user interface features for loan application platforms using \textbf{C++} and \textbf{React}, improving user workflow efficiency by 25\%.}
        \resumeItem{Developed asynchronous data processing components leveraging \textbf{Node.js} event-driven architecture, increasing transaction throughput by 30\%.}
        \resumeItem{Integrated \textbf{OAuth2} and \textbf{JWT} security protocols, reducing unauthorized access incidents by 40\%.}
        \resumeItem{Improved observability by developing detailed \textbf{Grafana} dashboards with \textbf{Prometheus}, enabling proactive incident detection.}
        \resumeItem{Collaborated closely with cross-functional teams in continuous Agile delivery, accelerating feature releases by 20\% with streamlined sprint coordination.}
        \resumeItem{Enhanced legacy system interfaces using \textbf{WPF} and object-oriented design to improve maintainability and feature extensibility.}
        \resumeItem{Automated deployment scripts and integrated source control via \textbf{Jenkins} and \textbf{SVN}, reducing release errors by 15\%.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Implemented UI components and backend APIs using \textbf{Java}, \textbf{Spring MVC}, and \textbf{Node.js} for supply chain management applications, boosting system speed by 20\%.}
        \resumeItem{Migrated legacy applications to AWS cloud infrastructure, achieving 20\% cost savings and better scalability using \textbf{S3} and \textbf{EC2}.}
        \resumeItem{Authored Linux shell scripts to monitor performance, reducing incident response times by 30\% through real-time alerts and automation.}
        \resumeItem{Streamlined continuous integration pipelines using \textbf{GitHub Actions}, elevating deployment frequency by 40\% and improving developer productivity.}
        \resumeItem{Coached teams on Agile and Scrum best practices, shortening project delivery time by 25\% with enhanced collaboration and sprint planning.}
        \resumeItem{Enhanced database design and optimized \textbf{DynamoDB} access patterns to decrease latency by 15\%, improving user experience.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-Driven Raster Image Analysis Tool} | C++, Python, TensorFlow, OpenCV}{ }
        \resumeItemListStart
            \resumeItem{Developed an AI-powered tool for raster image processing that leverages deep learning to automate complex photogrammetry tasks, improving accuracy by 30\%.}
            \resumeItem{Implemented asynchronous data pipelines to process large image datasets efficiently, reducing processing time by 40\% compared to legacy methods.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Dynamic MVVM WPF Application} | C#, WPF, MVVM, .NET}{ }
        \resumeItemListStart
            \resumeItem{Designed and developed a WPF application using the MVVM pattern, enabling flexible UI workflows and enhancing user productivity by 25\%.}
            \resumeItem{Integrated unit testing and continuous integration pipelines to assure software quality and stability in a fast-paced agile development environment.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Asynchronous Parallel Task Scheduler} | C#, .NET, Task Parallel Library}{ }
        \resumeItemListStart
            \resumeItem{Engineered a Task Parallel Library-based scheduler to efficiently manage asynchronous tasks, improving throughput by 35\% in multi-threaded environments.}
            \resumeItem{Enhanced application responsiveness with custom async programming models, reducing UI blockages and improving user experience in desktop applications.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}