\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Experienced backend engineer with 5+ years in building scalable financial platforms leveraging \textbf{Node.js}, \textbf{TypeScript}, and \textbf{Serverless AWS} technologies.}
    \resumeItem{Proficient in designing robust financial transaction systems with expertise in \textbf{GraphQL, PostgreSQL}, and event-driven architectures enhancing system reliability.}
    \resumeItem{Strong knowledge of integrating third-party APIs such as \textbf{NetSuite}, \textbf{Salesforce}, and banking APIs to streamline complex workflows efficiently.}
    \resumeItem{Skilled in SQL optimization and debugging, with focus on idempotency, error handling, and improving platform scalability for mission-critical fintech solutions.}
    \resumeItem{Committed to fostering team growth through mentoring, conducting code reviews, and cross-functional collaboration to achieve business and technical goals.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & JavaScript, TypeScript, Java, Python, SQL, Shell Scripting \\
                \textbf{Backend \& Frameworks:} & Node.js, Express.js, Spring Boot, Serverless Framework, GraphQL, REST APIs \\
                \textbf{Cloud \& Infrastructure:} & AWS (Lambda, API Gateway, ECS, S3, RDS), Docker, Kubernetes, Jenkins, Terraform \\
                \textbf{Databases:} & PostgreSQL, MySQL, Oracle, DynamoDB, Redis \\
                \textbf{Testing \& Automation:} & JUnit, Mockito, Selenium, Postman, Jest, Cucumber, GitHub Actions \\
                \textbf{Tools \& Methodologies:} & Agile, CI/CD, Microservices Architecture, OAuth2, JWT, Salesforce, NetSuite Integrations \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Led backend development using \textbf{Node.js}, \textbf{GraphQL}, and \textbf{AWS Lambda}, improving platform scalability by 30\% for complex financial workflows.}
        \resumeItem{Implemented robust, production-ready features with \textbf{TypeScript} ensuring 98\% test coverage and significantly reducing runtime errors in critical financial services.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries and fixed transaction inconsistencies improving data integrity and performance by 25\% on high-volume fintech applications.}
        \resumeItem{Integrated \textbf{third-party APIs} including \textbf{NetSuite} and \textbf{Salesforce} to automate financial reconciliation workflows, reducing manual effort by 40\%.}
        \resumeItem{Established a strong focus on system health via on-call rotation and effective incident response lowering downtime by 20\% during peak usage periods.}
        \resumeItem{Mentored junior engineers through rigorous code reviews and pair programming, improving team productivity and software quality across core services by 15\%.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Designed and maintained event-driven transaction services using \textbf{Kafka} and \textbf{Node.js}, supporting over 10,000 transactions per second for banking platform.}
        \resumeItem{Architected resilient, serverless microservices on \textbf{AWS Lambda} with \textbf{API Gateway}, resulting in 35\% reduction in latency and smoother financial operations.}
        \resumeItem{Enhanced system observability by creating detailed \textbf{Grafana} dashboards, enabling proactive performance monitoring and quick incident resolution across services.}
        \resumeItem{Implemented \textbf{OAuth2} and \textbf{JWT} security protocols reducing unauthorized access incidents by 40\% and increasing platform trustworthiness.}
        \resumeItem{Streamlined CI/CD pipelines integrating \textbf{Jenkins} and SVN repositories, reducing deployment cycle time by 30\% and speeding feature delivery.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed scalable backend services in \textbf{Node.js} and \textbf{Express.js} for supply chain fintech apps, improving API response times by 30\%.}
        \resumeItem{Built and optimized \textbf{DynamoDB} schemas and queries, reducing data access latency by 15\% and improving transactional throughput.}
        \resumeItem{Automated cloud migration to \textbf{AWS} and implemented monitoring scripts, decreasing system downtime by 20\% and operational costs.}
        \resumeItem{Designed and executed comprehensive testing with \textbf{JUnit} and \textbf{Postman}, increasing application stability and reducing bugs in production by 25\%.}
        \resumeItem{Collaborated with cross-functional teams under \textbf{Agile} to enhance software delivery speed by 25\% and improve customer feature satisfaction.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{FinTech Transaction Reconciliation Platform} | Node.js, AWS Lambda, PostgreSQL, GraphQL}{ }
        \resumeItemListStart
            \resumeItem{Developed an event-driven reconciliation engine with \textbf{GraphQL} API interface, boosting financial transaction matching accuracy by 30\%.}
            \resumeItem{Implemented seamless AWS \textbf{serverless architecture} reducing infrastructure costs by 25\% and improving response times during peak processing windows.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{AI-Driven Financial Insights Analyzer} | Python, LangChain, OpenAI API, AWS S3}{ }
        \resumeItemListStart
            \resumeItem{Built AI-powered NLP pipeline querying financial documents, providing contextual answers that accelerated decision-making by 40\% using LangChain and OpenAI.}
            \resumeItem{Leveraged scalable \textbf{AWS S3} storage and AI embeddings indexing to enhance query speed and accuracy for complex financial datasets.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Secure Banking Backend Service} | Go, Gin, PostgreSQL, Redis, Kubernetes}{ }
        \resumeItemListStart
            \resumeItem{Engineered backend microservices with \textbf{Go} and \textbf{PostgreSQL} incorporating JWT based auth, increasing platform security and reducing breaches by 30\%.}
            \resumeItem{Implemented caching via \textbf{Redis} and container orchestration with Kubernetes, improving throughput and scaling capacity by 25\%.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}