\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8+ years} of robust full stack development focusing on \textbf{JavaScript} and \textbf{Node.js} backend services, driving scalable cloud-native solutions.}
  \resumeItem{Engineered and deployed microservices leveraging \textbf{Node.js} and \textbf{JavaScript} with strong expertise in \textbf{GCP} cloud infrastructure and container orchestration.}
  \resumeItem{Designed and implemented responsive frontend applications using modern JavaScript frameworks, enhancing user experience and operational efficiency.}
  \resumeItem{Applied cloud-native best practices on \textbf{GCP}, including containerization, serverless functions, and managed services to optimize deployment pipelines.}
  \resumeItem{Collaborated across teams to deliver secure, performant APIs and integrations, emphasizing \textbf{API-first} design and automated CI/CD workflows.}
  \resumeItem{Focused on continuous improvement and observability using cloud monitoring tools, ensuring high availability and system reliability in production environments.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & JavaScript, Node.js, TypeScript, Java, Spring Boot, Angular, React \\
\textbf{Cloud Platforms:} & Google Cloud Platform (GKE, Cloud Storage, Pub/Sub, Cloud Logging/Monitoring), AWS, Azure \\
\textbf{Containerization \& Orchestration:} & Docker, Kubernetes, Helm \\
\textbf{API \& Integration:} & REST, gRPC, OpenAPI/Swagger, OAuth2/OIDC, JWT \\
\textbf{DevOps \& CI/CD:} & Jenkins, GitHub Actions, Azure DevOps, Terraform \\
\textbf{Observability \& Monitoring:} & OpenTelemetry, GCP Cloud Monitoring, Prometheus, Grafana \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led development of backend microservices using \textbf{Node.js} and \textbf{JavaScript}, improving modularity and reducing deployment risks significantly.}
  \resumeItem{Designed and implemented RESTful APIs with \textbf{OpenAPI} standards, ensuring consistent versioning and validation across services.}
  \resumeItem{Integrated secure authentication using \textbf{OAuth2/OIDC} and \textbf{JWT}, enhancing compliance with enterprise security policies.}
  \resumeItem{Developed frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, increasing UI responsiveness and maintainability.}
  \resumeItem{Built asynchronous processing pipelines leveraging \textbf{Kafka} and \textbf{GCP Pub/Sub}, improving message reliability and throughput.}
  \resumeItem{Optimized caching strategies using \textbf{Redis}, reducing backend latency by 25\% for high-traffic endpoints.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed on \textbf{GKE}, enabling scalable and repeatable cloud deployments.}
  \resumeItem{Automated CI/CD pipelines using \textbf{GitHub Actions} and \textbf{Jenkins}, enforcing quality and security scans with \textbf{SonarQube} and \textbf{Snyk}.}
  \resumeItem{Implemented observability using \textbf{OpenTelemetry} and \textbf{GCP Cloud Monitoring}, improving alerting and incident response times.}
  \resumeItem{\textit{Environment: JavaScript, Node.js, Angular, React, GCP (GKE, Pub/Sub, Cloud Monitoring), Docker, Kubernetes, Jenkins, GitHub Actions, OAuth2, JWT, Redis, Kafka, OpenAPI.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed scalable backend services using \textbf{Node.js} and \textbf{JavaScript}, enhancing API reliability and throughput across distributed systems.}
  \resumeItem{Designed and maintained REST and gRPC APIs, ensuring seamless integration and contract consistency with client applications.}
  \resumeItem{Built event-driven architectures using \textbf{Kafka} and \textbf{GCP Pub/Sub}, increasing asynchronous processing efficiency by 30\%.}
  \resumeItem{Implemented infrastructure as code using \textbf{Terraform} and \textbf{CloudFormation} for repeatable cloud resource provisioning.}
  \resumeItem{Containerized services with \textbf{Docker} and orchestrated deployments on \textbf{GKE} and \textbf{EKS}, improving scalability and resilience.}
  \resumeItem{Automated testing and CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, reducing deployment errors by 40\%.}
  \resumeItem{Enhanced frontend operations using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, improving user workflows and configuration management.}
  \resumeItem{\textit{Environment: Node.js, JavaScript, Angular, React, Kafka, GCP (GKE, Pub/Sub), Docker, Kubernetes, Terraform, Jenkins, GitHub Actions, REST, gRPC.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Node.js} and \textbf{JavaScript}, delivering scalable APIs for payment processing workflows.}
  \resumeItem{Built REST APIs with \textbf{OpenAPI} specifications, ensuring consistent validation and error handling across services.}
  \resumeItem{Implemented secure authentication using \textbf{OAuth2/OIDC} and \textbf{JWT}, aligning with enterprise RBAC policies.}
  \resumeItem{Delivered frontend modules using \textbf{Angular} and \textbf{TypeScript}, creating reusable components for workflow-heavy applications.}
  \resumeItem{Improved asynchronous processing with \textbf{Kafka}, increasing message reliability and throughput by 25\%.}
  \resumeItem{Built integration endpoints using \textbf{Node.js} and \textbf{C\#}, enabling partner orchestration and internal workflows.}
  \resumeItem{Optimized database queries and caching using \textbf{Redis}, reducing response times by 20\%.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling efficient environment-based configuration.}
  \resumeItem{Implemented cloud integrations using \textbf{GCP}, \textbf{AWS}, and \textbf{Azure} for messaging, storage, and identity management.}
  \resumeItem{\textit{Environment: Node.js, JavaScript, Angular, React, Kafka, C\#, OAuth2, JWT, Redis, Docker, Kubernetes, GCP, AWS, Azure, OpenAPI.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{JavaScript} and \textbf{Node.js}, delivering APIs for internal web applications and tooling.}
  \resumeItem{Built RESTful APIs documented with \textbf{Swagger}, improving API discoverability and integration.}
  \resumeItem{Delivered frontend features using \textbf{Angular} and \textbf{React}, creating reusable UI components for admin dashboards.}
  \resumeItem{Implemented scheduled processing and batch jobs to automate internal workflows, improving operational efficiency.}
  \resumeItem{Optimized database access patterns and indexing strategies, improving query performance and throughput.}
  \resumeItem{Standardized builds and CI pipelines using \textbf{Jenkins}, improving release stability and deployment speed.}
  \resumeItem{Containerized development and test environments with \textbf{Docker}, enabling consistent developer workflows.}
  \resumeItem{Supported cloud deployments on \textbf{AWS}, leveraging EC2, S3, and RDS for scalable infrastructure.}
  \resumeItem{\textit{Environment: JavaScript, Node.js, Angular, React, REST, Swagger, Jenkins, Docker, AWS (EC2, S3, RDS).}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}