\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Deliver robust backend solutions with \textbf{Java} and \textbf{Spring Boot}, specializing in microservices architecture and cloud-native development on \textbf{Microsoft Azure}.}
  \resumeItem{Design and maintain scalable APIs and services with strong emphasis on clean code, debugging, and performance optimization in distributed systems.}
  \resumeItem{Leverage expertise in \textbf{SQL} and \textbf{NoSQL} databases, container orchestration using \textbf{Kubernetes}, and implement CI/CD pipelines for efficient deployment.}
  \resumeItem{Collaborate cross-functionally to ensure security, scalability, and maintainability, applying DevOps best practices and cloud monitoring for production reliability.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java, Spring Boot, Spring Security, Hibernate/JPA, SQL, NoSQL (MongoDB, DynamoDB) \\
\textbf{Cloud \& DevOps:} & Microsoft Azure (AKS, App Service, Azure Monitor, Azure AD, Key Vault), Docker, Kubernetes, CI/CD (Jenkins, Azure DevOps, GitHub Actions) \\
\textbf{Databases:} & PostgreSQL, MySQL, MongoDB, DynamoDB, Redis \\
\textbf{API \& Integration:} & REST, gRPC, OpenAPI/Swagger, OAuth2/OIDC, JWT \\
\textbf{Testing \& Observability:} & JUnit, Mockito, Testcontainers, OpenTelemetry, Azure Monitor, Prometheus, Grafana \\
\textbf{Tools \& Version Control:} & Git, IntelliJ, VS Code, Jira, Confluence \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Designed and developed scalable backend services using \textbf{Java} and \textbf{Spring Boot} microservices, improving modularity and deployment efficiency.}
  \resumeItem{Implemented secure APIs with \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT}, enhancing authentication and authorization flows.}
  \resumeItem{Built and maintained RESTful and gRPC APIs following \textbf{OpenAPI} standards, ensuring consistent validation and error handling.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed on \textbf{Kubernetes (AKS)}, improving release automation and scalability.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, reducing deployment time and enforcing quality gates.}
  \resumeItem{Monitored applications with \textbf{OpenTelemetry} and \textbf{Azure Monitor}, proactively resolving performance and reliability issues.}
  \resumeItem{Collaborated with product and QA teams to deliver end-to-end features, ensuring clean code and maintainability.}
  \resumeItem{Optimized database queries and caching strategies using \textbf{SQL} and \textbf{Redis}, improving API response times by 30\%.}
  \resumeItem{Developed asynchronous processing workflows to enhance system resilience and throughput.}
  \resumeItem{Participated in code reviews and technical discussions to align on best practices and design patterns.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Spring Security, REST, gRPC, OpenAPI, Docker, Kubernetes (AKS), Jenkins, GitHub Actions, Azure Monitor, SQL, Redis, OAuth2/OIDC, JWT.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed microservices-based backend systems using \textbf{Java} and \textbf{Spring Boot}, enhancing service scalability and fault tolerance.}
  \resumeItem{Implemented REST and gRPC APIs with strong contract validation and versioning to support internal integrations.}
  \resumeItem{Designed and optimized data access patterns for \textbf{SQL} and \textbf{NoSQL} databases, improving query efficiency and throughput.}
  \resumeItem{Containerized services using \textbf{Docker} and orchestrated deployments on \textbf{Kubernetes}, ensuring smooth rollouts and rollbacks.}
  \resumeItem{Automated infrastructure provisioning and CI/CD workflows using \textbf{Terraform} and \textbf{GitHub Actions}, increasing deployment reliability.}
  \resumeItem{Implemented observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling proactive monitoring and alerting.}
  \resumeItem{Built unit and integration tests with \textbf{JUnit} and \textbf{Mockito}, improving code coverage and reducing defects.}
  \resumeItem{Collaborated with cross-functional teams to deliver secure, maintainable, and performant APIs.}
  \resumeItem{Enhanced asynchronous processing using event-driven architectures, improving system responsiveness.}
  \resumeItem{Managed secrets and access controls using AWS IAM and KMS to ensure secure service communication.}
  \resumeItem{\textit{Environment: Java, Spring Boot, REST, gRPC, Docker, Kubernetes, Terraform, GitHub Actions, OpenTelemetry, JUnit, Mockito, SQL, NoSQL.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, delivering scalable APIs with clean code and modular design.}
  \resumeItem{Implemented secure authentication and authorization using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT} aligned with enterprise policies.}
  \resumeItem{Built REST APIs with \textbf{OpenAPI/Swagger} specifications, ensuring consistent validation and error handling.}
  \resumeItem{Optimized database performance using \textbf{SQL} tuning and caching with \textbf{Redis}, reducing latency by 25\%.}
  \resumeItem{Containerized microservices using \textbf{Docker} and deployed on \textbf{Kubernetes}, improving environment consistency and scalability.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing quality and security standards.}
  \resumeItem{Collaborated with QA and product teams to deliver high-quality features with comprehensive unit and integration tests.}
  \resumeItem{Implemented asynchronous messaging using \textbf{Kafka}, enhancing system reliability and throughput.}
  \resumeItem{Supported multi-cloud deployments integrating \textbf{AWS}, \textbf{Azure}, and \textbf{GCP} services for identity and storage.}
  \resumeItem{Participated in code reviews and technical discussions to improve system design and maintainability.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Spring Security, REST, OpenAPI, Docker, Kubernetes, Jenkins, Azure DevOps, Kafka, SQL, Redis, OAuth2/OIDC, JWT.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services with \textbf{Java} and \textbf{Spring Boot}, delivering reusable components and scalable APIs.}
  \resumeItem{Built RESTful APIs and documented endpoints using \textbf{Swagger} to standardize integration interfaces.}
  \resumeItem{Improved database performance using query optimization and indexing with \textbf{Hibernate/JPA}.}
  \resumeItem{Implemented containerized development and testing environments using \textbf{Docker} for enhanced consistency.}
  \resumeItem{Supported cloud deployments on \textbf{AWS}, focusing on scalability and reliability of backend services.}
  \resumeItem{Strengthened automated testing using \textbf{JUnit} and \textbf{Mockito}, improving release stability.}
  \resumeItem{Collaborated in Agile teams to deliver features with clean code and maintainable architecture.}
  \resumeItem{Participated in CI/CD pipeline setup using \textbf{Jenkins} to streamline build and deployment processes.}
  \resumeItem{Implemented scheduled batch processing using \textbf{Spring Scheduling} for periodic workflows.}
  \resumeItem{Assisted in troubleshooting and debugging complex backend and database issues to improve system uptime.}
  \resumeItem{\textit{Environment: Java, Spring Boot, REST, Swagger, Hibernate/JPA, Docker, Jenkins, AWS, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}