\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Designed and architected scalable full-stack applications leveraging \textbf{Angular}, \textbf{React}, \textbf{NodeJS}, and \textbf{Python}, delivering robust UI/UX and backend solutions.}
  \resumeItem{Led architecture ownership across frontend, backend, APIs, and data layers, balancing scalability, security, and extensibility for enterprise-grade applications.}
  \resumeItem{Implemented cloud-native solutions with \textbf{AWS}, \textbf{Azure}, and \textbf{GCP}, integrating CI/CD pipelines, infrastructure as code, and observability for high availability.}
  \resumeItem{Applied secure coding and compliance standards including authentication, authorization, and data protection models aligned with enterprise policies.}
  \resumeItem{Integrated AI-driven automation and real-time messaging technologies, enhancing data workflows and interactive dashboard tools for stakeholder insights.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Frontend:} & Angular, React, TypeScript, JavaScript, RxJS, NgRx, Angular Material, Material UI, HTML5, CSS3/SCSS \\
\textbf{Backend:} & NodeJS, Python, REST APIs, Microservices, Event-driven architecture, Express.js, Flask \\
\textbf{Databases:} & MongoDB, PostgreSQL, MySQL, NoSQL, Relational Modeling, Caching Strategies, Redis \\
\textbf{Cloud \& DevOps:} & AWS, Azure, GCP, Docker, Kubernetes, Helm, Terraform, CloudFormation, CI/CD Pipelines, Infrastructure as Code \\
\textbf{Security:} & OAuth2/OIDC, JWT, Authentication \& Authorization, Secure Coding Practices, Data Protection, Compliance Standards \\
\textbf{AI \& Messaging:} & AI Workflow Automation, Real-time Technologies, Message Queues (Kafka, SQS), Observability, Logging, Monitoring \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Architected and owned full-stack solutions using \textbf{Angular}, \textbf{React}, \textbf{NodeJS}, and \textbf{Python}, improving system scalability and UI consistency.}
  \resumeItem{Designed RESTful and event-driven APIs with \textbf{NodeJS} and \textbf{Python}, applying microservices patterns to enhance fault tolerance and resiliency.}
  \resumeItem{Led cloud-native deployments on \textbf{AWS} with container orchestration using \textbf{Docker} and \textbf{Kubernetes}, improving release velocity and availability.}
  \resumeItem{Implemented secure authentication and authorization flows using \textbf{OAuth2/OIDC} and \textbf{JWT}, aligning with enterprise compliance requirements.}
  \resumeItem{Developed interactive dashboards and admin modules with \textbf{React} and \textbf{Angular}, improving stakeholder insights and operational efficiency.}
  \resumeItem{Built asynchronous processing pipelines using \textbf{Kafka} and \textbf{AWS SQS/SNS}, enhancing system reliability and throughput.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{GitHub Actions}, enforcing quality and security gates with \textbf{SonarQube} and \textbf{Snyk}.}
  \resumeItem{Implemented observability frameworks using \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling proactive monitoring and alerting.}
  \resumeItem{\textit{Environment: Angular, React, NodeJS, Python, AWS, Docker, Kubernetes, Kafka, OAuth2, JWT, Jenkins, GitHub Actions, OpenTelemetry, Redis.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed scalable backend services using \textbf{NodeJS} and \textbf{Python}, designing REST and event-driven APIs to support distributed systems.}
  \resumeItem{Delivered frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, enhancing user experience and state management with \textbf{NgRx} and \textbf{Redux}.}
  \resumeItem{Implemented cloud infrastructure on \textbf{AWS} using \textbf{Terraform} and \textbf{CloudFormation}, enabling repeatable and secure deployments.}
  \resumeItem{Built real-time messaging workflows with \textbf{Kafka} and \textbf{AWS SQS/SNS}, improving asynchronous processing and system decoupling.}
  \resumeItem{Applied caching and data consistency strategies using \textbf{Redis} and \textbf{PostgreSQL}, reducing latency and database load.}
  \resumeItem{Designed secure authentication and authorization mechanisms with \textbf{OAuth2/OIDC} and \textbf{JWT}, ensuring compliance with enterprise security policies.}
  \resumeItem{Automated CI/CD pipelines using \textbf{GitHub Actions} and \textbf{Azure DevOps}, improving release reliability and speed.}
  \resumeItem{Integrated observability tools with \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling detailed monitoring and diagnostics.}
  \resumeItem{\textit{Environment: NodeJS, Python, Angular, React, AWS, Terraform, Kafka, OAuth2, JWT, Redis, PostgreSQL, GitHub Actions, OpenTelemetry.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed full-stack applications using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, improving UI modularity and workflow consistency.}
  \resumeItem{Built backend services using \textbf{NodeJS} and \textbf{Python}, designing REST APIs with secure authentication and authorization using \textbf{OAuth2/OIDC} and \textbf{JWT}.}
  \resumeItem{Implemented asynchronous processing with \textbf{Kafka}, improving system throughput and fault tolerance.}
  \resumeItem{Optimized database performance using \textbf{PostgreSQL} and \textbf{MongoDB}, applying caching strategies with \textbf{Redis} to reduce latency.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling scalable and repeatable environments.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing code quality with \textbf{SonarQube}.}
  \resumeItem{Integrated cloud services across \textbf{AWS}, \textbf{Azure}, and \textbf{GCP}, standardizing identity, storage, and messaging patterns.}
  \resumeItem{Developed internal dashboards and admin tools enhancing operational visibility and user experience.}
  \resumeItem{\textit{Environment: Angular, React, NodeJS, Python, Kafka, PostgreSQL, MongoDB, Redis, Docker, Kubernetes, Jenkins, Azure DevOps, AWS, Azure, GCP.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Delivered frontend features using \textbf{Angular} and \textbf{React}, building reusable components and improving UI/UX consistency.}
  \resumeItem{Developed backend services using \textbf{NodeJS} and \textbf{Python}, designing RESTful APIs and integrating with databases.}
  \resumeItem{Improved data access and query performance using \textbf{PostgreSQL} with indexing and caching strategies.}
  \resumeItem{Implemented containerized development environments with \textbf{Docker}, streamlining testing and deployment workflows.}
  \resumeItem{Supported cloud deployments on \textbf{AWS}, enhancing system scalability and availability.}
  \resumeItem{Enhanced automated testing using \textbf{JUnit} and \textbf{Mockito} to increase release stability and code quality.}
  \resumeItem{Collaborated in Agile teams to deliver incremental enhancements and maintain high-quality standards.}
  \resumeItem{Built internal dashboard modules improving administrative workflows and operational monitoring.}
  \resumeItem{\textit{Environment: Angular, React, NodeJS, Python, PostgreSQL, Docker, AWS, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}