\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Leverage over \textbf{8+ years} of experience architecting and delivering scalable backend services using \textbf{Java} and \textbf{Spring Boot} within microservices environments.}
  \resumeItem{Drive end-to-end AI/ML production deployments integrating \textbf{LLMs}, vector databases, and retrieval-augmented generation to enhance enterprise workflows.}
  \resumeItem{Expert in full stack development with strong command of \textbf{TypeScript}, \textbf{React}, and \textbf{Redux} for building responsive user interfaces.}
  \resumeItem{Manage containerized cloud-native applications using \textbf{Docker} and \textbf{Kubernetes (EKS)}, optimizing CI/CD pipelines for continuous delivery.}
  \resumeItem{Implement secure authentication and authorization frameworks using \textbf{OAuth2} and \textbf{OpenID Connect} aligned with enterprise security standards.}
  \resumeItem{Skilled in leveraging messaging platforms like \textbf{Kafka} and caching technologies such as \textbf{Redis} to improve system performance and reliability.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Backend \& Frameworks:} & Java, Spring Boot, Microservices, Node.js, Spring Security, OAuth2, OpenID Connect \\
\textbf{Frontend:} & React (Hooks), Redux, TypeScript, Angular, RxJS, NgRx \\
\textbf{AI/ML \& Data:} & LLM Integration (Gemini, Claude), Vector Databases, RAG, MCP Development, PostgreSQL, Redis, Kafka \\
\textbf{Cloud \& DevOps:} & Kubernetes (EKS), Docker, CI/CD Pipelines (Jenkins, GitHub Actions, Azure DevOps), Terraform, Helm \\
\textbf{Messaging \& Streaming:} & Kafka, AWS SQS/SNS, Event-Driven Architectures \\
\textbf{Testing \& Observability:} & JUnit, Mockito, Testcontainers, OpenTelemetry, Prometheus, Grafana \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led design and development of backend microservices using \textbf{Java} and \textbf{Spring Boot}, improving modularity and deployment efficiency.}
  \resumeItem{Developed secure APIs with \textbf{REST} and \textbf{gRPC}, enforcing standards for validation, versioning, and error handling.}
  \resumeItem{Implemented authentication using \textbf{Spring Security}, \textbf{OAuth2}, and \textbf{OpenID Connect}, enhancing enterprise security compliance.}
  \resumeItem{Integrated \textbf{LLMs} and \textbf{RAG} techniques via \textbf{Spring AI} and \textbf{AWS Bedrock} to automate internal workflows with audit logging.}
  \resumeItem{Built frontend modules using \textbf{React} with \textbf{TypeScript} and \textbf{Redux}, accelerating UI delivery and state management.}
  \resumeItem{Developed asynchronous processing pipelines leveraging \textbf{Kafka} and \textbf{AWS SQS/SNS}, increasing system reliability and throughput.}
  \resumeItem{Optimized data access and caching using \textbf{Redis}, reducing latency by 25\% for critical read paths.}
  \resumeItem{Containerized services with \textbf{Docker} and deployed on \textbf{Kubernetes (EKS)} using \textbf{Helm}, enabling repeatable and scalable releases.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, enforcing quality and security gates with \textbf{SonarQube} and \textbf{Snyk}.}
  \resumeItem{Implemented observability with \textbf{OpenTelemetry} and \textbf{CloudWatch}, delivering actionable metrics and real-time alerts.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Spring Security, OAuth2, OpenID Connect, Spring AI, AWS Bedrock, REST, gRPC, Kafka, React, TypeScript, Redux, Redis, Docker, Kubernetes, Helm, Jenkins, GitHub Actions, SonarQube, Snyk, OpenTelemetry.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and implemented backend services using \textbf{Java} and \textbf{Spring Boot}, enhancing service scalability and reliability.}
  \resumeItem{Built APIs with \textbf{REST} and \textbf{gRPC}, ensuring consistent integration and contract adherence across distributed systems.}
  \resumeItem{Developed event-driven architectures using \textbf{Kafka}, improving decoupling and throughput for asynchronous workflows.}
  \resumeItem{Optimized database access patterns on \textbf{PostgreSQL} and \textbf{Redis}, reducing latency by 30\% for performance-critical operations.}
  \resumeItem{Containerized applications with \textbf{Docker} and orchestrated deployments on \textbf{Kubernetes (EKS)}, streamlining release cycles.}
  \resumeItem{Provisioned infrastructure using \textbf{Terraform} and \textbf{CloudFormation} to enable repeatable and auditable environments.}
  \resumeItem{Implemented CI/CD pipelines with \textbf{GitHub Actions} and \textbf{Jenkins}, improving deployment automation and reliability.}
  \resumeItem{Delivered frontend features using \textbf{React} and \textbf{TypeScript}, enhancing user experience and maintainability.}
  \resumeItem{Applied security best practices using \textbf{OAuth2} and \textbf{OpenID Connect} for API access control.}
  \resumeItem{\textit{Environment: Java, Spring Boot, REST, gRPC, Kafka, PostgreSQL, Redis, Docker, Kubernetes, Terraform, CloudFormation, Jenkins, GitHub Actions, React, TypeScript, OAuth2, OpenID Connect.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend microservices using \textbf{Java} and \textbf{Spring Boot}, delivering scalable APIs with consistent validation and error handling.}
  \resumeItem{Implemented secure authentication and authorization using \textbf{Spring Security}, \textbf{OAuth2}, and \textbf{OpenID Connect} aligned with RBAC policies.}
  \resumeItem{Built frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript} and \textbf{Redux}, improving UI responsiveness and state predictability.}
  \resumeItem{Implemented asynchronous processing with \textbf{Kafka}, enhancing reliability through retry and dead-letter queue mechanisms.}
  \resumeItem{Optimized database queries and caching with \textbf{PostgreSQL} and \textbf{Redis}, resulting in 25\% faster response times.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling environment-based configuration management.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing code quality and security standards.}
  \resumeItem{Integrated multi-cloud platform services across \textbf{AWS}, \textbf{Azure}, and \textbf{GCP} to support identity, storage, and messaging requirements.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Spring Security, OAuth2, OpenID Connect, REST, Angular, React, TypeScript, Redux, Kafka, PostgreSQL, Redis, Docker, Kubernetes, Jenkins, Azure DevOps, AWS, Azure, GCP.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, delivering reusable components and clean API layers.}
  \resumeItem{Built RESTful APIs and documented endpoints using \textbf{OpenAPI/Swagger} to standardize integration.}
  \resumeItem{Implemented frontend features with \textbf{Angular} and \textbf{React} using \textbf{TypeScript}, enhancing admin and user workflows.}
  \resumeItem{Improved database performance using \textbf{Hibernate/JPA} with query optimization and indexing strategies.}
  \resumeItem{Containerized development and testing environments using \textbf{Docker}, improving consistency across teams.}
  \resumeItem{Supported cloud deployments on \textbf{AWS}, leveraging EC2, S3, and RDS services for scalability.}
  \resumeItem{Enhanced automated testing coverage using \textbf{JUnit} and \textbf{Mockito}, reducing production defects.}
  \resumeItem{\textit{Environment: Java, Spring Boot, REST, OpenAPI, Angular, React, TypeScript, Hibernate/JPA, Docker, AWS, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}