\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Deliver robust enterprise web applications and microservices with \textbf{Java}, \textbf{Angular}, and \textbf{Node.js}, driving scalable and maintainable solutions.}
  \resumeItem{Leverage event-driven architectures using \textbf{Apache Kafka} to enable reliable asynchronous processing and high-throughput data pipelines.}
  \resumeItem{Build and deploy serverless functions on \textbf{AWS Lambda}, optimizing cloud-native workflows and reducing operational overhead.}
  \resumeItem{Apply strong full stack expertise integrating frontend frameworks with backend services to create seamless user experiences and performant APIs.}
  \resumeItem{Drive continuous delivery and observability with modern DevOps tools to ensure production stability and rapid iteration cycles.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java, Node.js, Angular, TypeScript, Spring Boot, REST, Kafka \\
\textbf{Cloud \& Serverless:} & AWS Lambda, AWS (EKS, S3, DynamoDB, IAM, CloudWatch), Serverless Architectures \\
\textbf{Messaging \& Streaming:} & Apache Kafka, AWS SQS, SNS, EventBridge \\
\textbf{Databases \& Caching:} & PostgreSQL, MySQL, DynamoDB, Redis \\
\textbf{DevOps \& CI/CD:} & Docker, Kubernetes, Jenkins, GitHub Actions, Terraform, CloudFormation \\
\textbf{Testing \& Observability:} & JUnit, Mockito, OpenTelemetry, CloudWatch, Prometheus, Grafana \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Designed and developed scalable backend services using \textbf{Java} and \textbf{Spring Boot}, enhancing modularity and reducing deployment risks.}
  \resumeItem{Implemented asynchronous event processing using \textbf{Apache Kafka}, improving system reliability and throughput with retry and dead-letter queue strategies.}
  \resumeItem{Built interactive frontend modules with \textbf{Angular} and \textbf{TypeScript}, delivering workflow-heavy user experiences with state management.}
  \resumeItem{Developed serverless functions on \textbf{AWS Lambda} to handle event-driven tasks, reducing infrastructure management overhead.}
  \resumeItem{Integrated secure authentication and authorization using \textbf{Spring Security} with OAuth2 and JWT, enforcing compliance and access control.}
  \resumeItem{Containerized microservices with \textbf{Docker} and orchestrated deployments on \textbf{Kubernetes}, enabling scalable and repeatable releases.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, incorporating quality gates and security scans for robust delivery.}
  \resumeItem{Monitored production systems using \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling proactive issue detection and alerting.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Angular, TypeScript, Apache Kafka, AWS Lambda, Docker, Kubernetes, Jenkins, GitHub Actions, OpenTelemetry, CloudWatch.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed distributed backend services using \textbf{Java} and \textbf{Node.js}, improving API scalability and reliability across multiple teams.}
  \resumeItem{Implemented event-driven workflows leveraging \textbf{Apache Kafka}, enhancing decoupling and throughput for critical data pipelines.}
  \resumeItem{Built efficient serverless applications on \textbf{AWS Lambda}, reducing latency and operational costs for event-triggered processes.}
  \resumeItem{Created frontend operational tools using \textbf{Angular} and \textbf{TypeScript}, improving usability and configuration management.}
  \resumeItem{Optimized database access patterns with \textbf{DynamoDB} and \textbf{Aurora PostgreSQL}, increasing query performance and reducing latency.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{EKS/ECS}, enabling scalable cloud-native infrastructure.}
  \resumeItem{Provisioned infrastructure with \textbf{Terraform} and \textbf{CloudFormation}, ensuring consistent and auditable environments.}
  \resumeItem{Implemented observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, facilitating real-time monitoring and alerting.}
  \resumeItem{\textit{Environment: Java, Node.js, Angular, Apache Kafka, AWS Lambda, DynamoDB, Aurora, Docker, Kubernetes, Terraform, CloudFormation, OpenTelemetry, CloudWatch.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Built backend microservices using \textbf{Java} and \textbf{Spring Boot}, delivering scalable REST APIs aligned with enterprise standards.}
  \resumeItem{Developed frontend web applications using \textbf{Angular} and \textbf{TypeScript}, creating reusable components and enhancing user workflows.}
  \resumeItem{Implemented asynchronous messaging with \textbf{Apache Kafka}, improving system resilience and event processing reliability.}
  \resumeItem{Built integration endpoints with \textbf{Node.js} and \textbf{C\#}, enabling partner orchestration and internal service communication.}
  \resumeItem{Improved database performance using \textbf{Hibernate/JPA} optimizations and caching with \textbf{Redis}, reducing response times by 25\%.}
  \resumeItem{Containerized services with \textbf{Docker} and deployed using \textbf{Kubernetes}, standardizing environment configurations.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing code quality and security best practices.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Angular, TypeScript, Apache Kafka, Node.js, C\#, Redis, Docker, Kubernetes, Jenkins, Azure DevOps.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services with \textbf{Java} and \textbf{Spring Boot}, delivering reusable APIs and improving system maintainability.}
  \resumeItem{Built frontend features using \textbf{Angular} and \textbf{TypeScript}, enhancing user interfaces and component reuse.}
  \resumeItem{Implemented REST APIs following \textbf{Swagger/OpenAPI} standards, ensuring consistent documentation and validation.}
  \resumeItem{Optimized database queries using \textbf{Hibernate/JPA}, improving performance and reducing latency.}
  \resumeItem{Containerized development environments with \textbf{Docker}, streamlining testing and deployment processes.}
  \resumeItem{Supported cloud deployments on \textbf{AWS}, managing storage and compute resources effectively.}
  \resumeItem{Enhanced automated testing with \textbf{JUnit} and \textbf{Mockito}, increasing release stability and reducing defects.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Angular, TypeScript, REST, Swagger, Hibernate/JPA, Docker, AWS, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}