\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Experienced software engineer specializing in \textbf{Java} backend development with strong proficiency in cross-platform solutions on \textbf{Linux} and \textbf{Windows} environments.}
  \resumeItem{Skilled in designing and delivering scalable, high-quality software using \textbf{Rust} and \textbf{C\#}, emphasizing robust problem-solving and debugging capabilities.}
  \resumeItem{Proficient in modern development practices including version control, CI/CD pipelines, and automated testing to ensure engineering excellence and operational reliability.}
  \resumeItem{Hands-on experience with containerization, orchestration, and cloud infrastructure, enabling seamless deployment and maintenance of distributed systems.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Operating Systems:} & Linux, Windows, macOS \\
\textbf{Languages:} & Java, Rust, C\#, C++, Go, Kotlin, TypeScript, Python \\
\textbf{Frameworks \& Tools:} & Spring Boot, ASP.NET Core Web API, REST, gRPC, OpenAPI/Swagger, OAuth2/OIDC, JWT, mTLS \\
\textbf{Cloud \& DevOps:} & AWS, Azure, GCP, Docker, Kubernetes, Helm, Terraform, CloudFormation, Jenkins, GitHub Actions, Azure DevOps \\
\textbf{Databases \& Caching:} & PostgreSQL, MySQL, DynamoDB, MongoDB, Redis \\
\textbf{Testing \& Observability:} & JUnit, Mockito, Testcontainers, SonarQube, OpenTelemetry, Prometheus, Grafana \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led development of backend services using \textbf{Java} and \textbf{Spring Boot}, enhancing modularity and reducing deployment risks significantly.}
  \resumeItem{Designed and implemented secure API layers with \textbf{REST} and \textbf{gRPC}, ensuring consistency in validation and error handling.}
  \resumeItem{Integrated authentication mechanisms using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT} to enforce enterprise-grade security policies.}
  \resumeItem{Developed internal integration services using \textbf{C\#} and \textbf{ASP.NET Core Web API} to streamline partner and platform workflows.}
  \resumeItem{Implemented asynchronous processing with \textbf{Kafka} and \textbf{AWS SQS/SNS}, improving system reliability and scalability.}
  \resumeItem{Optimized database interactions using indexing and caching with \textbf{Redis}, reducing latency by 25\% on critical paths.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling repeatable and scalable releases.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, enforcing quality and security standards via SonarQube and Snyk.}
  \resumeItem{Monitored production systems using \textbf{OpenTelemetry} and \textbf{CloudWatch}, delivering actionable insights and alerts.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Spring Security, REST, gRPC, C\#, ASP.NET Core, Kafka, AWS, Docker, Kubernetes, Jenkins, GitHub Actions, Redis, OpenTelemetry.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed distributed backend services primarily using \textbf{Java} and \textbf{Kotlin}, improving API scalability and reliability.}
  \resumeItem{Implemented internal APIs with \textbf{gRPC} and \textbf{REST}, ensuring robust contract consistency across services.}
  \resumeItem{Built performance-critical automation tooling in \textbf{Go}, reducing manual intervention and improving throughput.}
  \resumeItem{Designed event-driven architectures using \textbf{Kafka}, enhancing decoupling and scalability of services.}
  \resumeItem{Optimized data access patterns for \textbf{DynamoDB} and \textbf{Aurora PostgreSQL}, improving query efficiency and reducing latency.}
  \resumeItem{Secured AWS resources using \textbf{IAM}, \textbf{KMS}, and secrets management, ensuring compliance with security best practices.}
  \resumeItem{Containerized microservices with \textbf{Docker} and orchestrated deployments on \textbf{EKS/ECS}, enabling seamless rollouts.}
  \resumeItem{Provisioned infrastructure as code with \textbf{Terraform} and \textbf{CloudFormation} for repeatable environments.}
  \resumeItem{Implemented observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, improving system monitoring and alerting.}
  \resumeItem{\textit{Environment: Java, Kotlin, Go, REST, gRPC, Kafka, AWS, Docker, Kubernetes, Terraform, CloudFormation, OpenTelemetry.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, delivering scalable and reusable APIs for enterprise applications.}
  \resumeItem{Built secure REST APIs with \textbf{OpenAPI/Swagger}, enforcing validation, versioning, and error handling standards.}
  \resumeItem{Implemented authentication and authorization using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT} to meet compliance requirements.}
  \resumeItem{Delivered frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, improving user experience and modularity.}
  \resumeItem{Built integration endpoints using \textbf{C\#} and \textbf{ASP.NET Core Web API} for partner orchestration workflows.}
  \resumeItem{Implemented asynchronous processing with \textbf{Kafka}, enhancing reliability through retry and dead-letter queue patterns.}
  \resumeItem{Improved database performance with \textbf{Hibernate/JPA} tuning and \textbf{Redis} caching, reducing response times by 25\%.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed using \textbf{Kubernetes}, supporting environment-based configuration.}
  \resumeItem{Automated CI/CD workflows with \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing code quality with SonarQube.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Spring Security, REST, Angular, React, TypeScript, Kafka, C\#, ASP.NET Core, Hibernate, Redis, Docker, Kubernetes, Jenkins, Azure DevOps.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Delivered backend services using \textbf{Java} and \textbf{Spring Boot}, improving modularity and maintainability of web applications.}
  \resumeItem{Built RESTful APIs and documented them using \textbf{Swagger}, standardizing endpoint contracts.}
  \resumeItem{Developed frontend features using \textbf{Angular} and \textbf{React}, enhancing UI modularity and user workflows.}
  \resumeItem{Implemented scheduled processing using \textbf{Quartz} and \textbf{Spring Scheduling} to automate periodic tasks.}
  \resumeItem{Optimized database queries and indexing with \textbf{Hibernate/JPA}, improving application performance.}
  \resumeItem{Standardized build and CI pipelines using \textbf{Maven/Gradle} and \textbf{Jenkins} for reliable releases.}
  \resumeItem{Containerized development and test environments using \textbf{Docker}, enabling consistent setups.}
  \resumeItem{Supported cloud deployments on \textbf{AWS}, improving scalability and availability of services.}
  \resumeItem{Strengthened automated testing using \textbf{JUnit} and \textbf{Mockito}, enhancing release stability.}
  \resumeItem{\textit{Environment: Java, Spring Boot, REST, Angular, React, Hibernate, Docker, Jenkins, AWS.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}