\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8+ years} of expertise in backend development using \textbf{Java} and \textbf{J2EE} technologies, focusing on scalable distributed systems.}
  \resumeItem{Designed and implemented cloud-native applications leveraging \textbf{AWS} and \textbf{Azure} services with container orchestration and infrastructure automation.}
  \resumeItem{Engineered reliable coordination and distributed state management solutions using \textbf{Zookeeper} to support high-availability microservices.}
  \resumeItem{Applied strong API-first design principles using \textbf{REST} and \textbf{gRPC}, securing services with \textbf{Spring Security}, \textbf{OAuth2}, and \textbf{JWT}.}
  \resumeItem{Implemented asynchronous processing and messaging with \textbf{Kafka} and cloud-native queues, improving system resilience and throughput.}
  \resumeItem{Built and maintained observability and CI/CD pipelines ensuring production-grade deployments and monitoring across multi-cloud environments.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java, J2EE, Spring Boot, Spring Security, Hibernate/JPA, Zookeeper, REST, gRPC \\
\textbf{Cloud Platforms:} & AWS (EKS, ECS, Lambda, S3, RDS, DynamoDB, IAM, KMS, Secrets Manager), Azure (AKS, App Service, Azure AD, Key Vault) \\
\textbf{Messaging \& Coordination:} & Apache Kafka, AWS SQS/SNS, Zookeeper \\
\textbf{Containerization \& Orchestration:} & Docker, Kubernetes, Helm \\
\textbf{DevOps \& Automation:} & Jenkins, GitHub Actions, Azure DevOps, Terraform, CloudFormation \\
\textbf{Observability \& Testing:} & OpenTelemetry, CloudWatch, Prometheus, Grafana, JUnit, Mockito, Testcontainers \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led design and development of backend services using \textbf{Java} and \textbf{Spring Boot}, improving modularity and system scalability.}
  \resumeItem{Implemented secure APIs with \textbf{REST} and \textbf{gRPC}, ensuring compliance with OpenAPI standards and consistent error handling.}
  \resumeItem{Configured authentication and authorization using \textbf{Spring Security}, \textbf{OAuth2}, and \textbf{JWT} to secure enterprise workflows.}
  \resumeItem{Developed asynchronous processing pipelines leveraging \textbf{Kafka} and \textbf{AWS SQS/SNS}, enhancing reliability and throughput.}
  \resumeItem{Integrated \textbf{Zookeeper} for distributed coordination and service discovery, increasing system availability and fault tolerance.}
  \resumeItem{Containerized microservices with \textbf{Docker} and deployed on \textbf{Kubernetes (EKS)} using \textbf{Helm} for consistent releases.}
  \resumeItem{Automated CI/CD workflows using \textbf{Jenkins} and \textbf{GitHub Actions}, enforcing quality and security gates.}
  \resumeItem{Implemented observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling proactive monitoring and alerting.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Spring Security, OAuth2, JWT, REST, gRPC, Kafka, Zookeeper, AWS (EKS, S3, RDS, DynamoDB, SQS/SNS), Docker, Kubernetes, Helm, Jenkins, GitHub Actions.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and developed distributed backend services using \textbf{Java} and \textbf{Kotlin}, improving system reliability and scalability.}
  \resumeItem{Built and maintained APIs with \textbf{REST} and \textbf{gRPC}, ensuring robust contract management and versioning.}
  \resumeItem{Implemented event-driven architectures using \textbf{Kafka}, enhancing throughput and decoupling service dependencies.}
  \resumeItem{Managed infrastructure provisioning using \textbf{Terraform} and \textbf{CloudFormation}, ensuring reproducible cloud environments.}
  \resumeItem{Applied \textbf{Zookeeper} for distributed locking and cluster management, improving coordination across microservices.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed on \textbf{EKS/ECS}, following best practices for rollouts.}
  \resumeItem{Implemented security best practices using \textbf{AWS IAM}, encryption with \textbf{KMS}, and secrets management.}
  \resumeItem{Developed observability using \textbf{OpenTelemetry} and \textbf{CloudWatch} dashboards to monitor system health.}
  \resumeItem{\textit{Environment: Java, Kotlin, REST, gRPC, Kafka, Zookeeper, AWS (EKS, ECS, Lambda, DynamoDB, S3, KMS), Docker, Kubernetes, Terraform, CloudFormation, OpenTelemetry.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, delivering scalable APIs with high availability.}
  \resumeItem{Implemented secure access controls using \textbf{Spring Security}, \textbf{OAuth2}, and \textbf{JWT} aligned with RBAC policies.}
  \resumeItem{Built asynchronous messaging solutions with \textbf{Kafka}, improving system resilience and throughput.}
  \resumeItem{Integrated \textbf{Zookeeper} for distributed configuration and service coordination to enhance fault tolerance.}
  \resumeItem{Improved database performance using \textbf{Hibernate/JPA} tuning and caching strategies with \textbf{Redis}.}
  \resumeItem{Containerized services using \textbf{Docker} and orchestrated deployments with \textbf{Kubernetes}, enabling environment consistency.}
  \resumeItem{Implemented multi-cloud platform integrations across \textbf{AWS}, \textbf{Azure}, and \textbf{GCP} for identity and messaging services.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing code quality with \textbf{SonarQube}.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Spring Security, OAuth2, JWT, Kafka, Zookeeper, Redis, Docker, Kubernetes, AWS, Azure, Jenkins, Azure DevOps.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{J2EE} frameworks, delivering reusable and maintainable components.}
  \resumeItem{Built REST APIs with \textbf{Swagger} documentation, ensuring consistent interface design and versioning.}
  \resumeItem{Implemented scheduled batch processing and workflow automation using \textbf{Quartz} and \textbf{Spring Scheduling}.}
  \resumeItem{Improved database performance through query optimization and indexing with \textbf{Hibernate/JPA}.}
  \resumeItem{Containerized development and test environments using \textbf{Docker} to accelerate delivery cycles.}
  \resumeItem{Supported cloud deployments on \textbf{AWS} leveraging EC2, S3, and RDS services for scalable infrastructure.}
  \resumeItem{Strengthened automated testing using \textbf{JUnit} and \textbf{Mockito} to enhance release stability.}
  \resumeItem{\textit{Environment: Java, J2EE, REST, Swagger, Quartz, Hibernate/JPA, Docker, AWS (EC2, S3, RDS), JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}