\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Deliver over 8 years of expertise in full stack development with a focus on \textbf{C\#}, \textbf{.NET Core}, \textbf{Angular}, and \textbf{SQL Server} to build scalable enterprise applications.}
  \resumeItem{Architect and implement cloud-native solutions leveraging \textbf{Azure} services to enhance deployment agility and operational efficiency.}
  \resumeItem{Develop rich interactive frontends using \textbf{Angular} and \textbf{JavaScript (jQuery)}, ensuring seamless user experiences and maintainability.}
  \resumeItem{Design and optimize backend APIs with \textbf{ASP.NET Core Web API}, enforcing security, performance, and extensibility standards.}
  \resumeItem{Apply strong database skills on \textbf{SQL Server 2019+} with query tuning and schema design to support high-throughput applications.}
  \resumeItem{Utilize \textbf{Node.js} for server-side scripting and automation, integrating with modern cloud platforms and microservices architectures.}
  \resumeItem{Implement CI/CD pipelines and containerized deployments to streamline delivery and maintain high-quality releases.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & C\#, \textbf{.NET Core}, Angular, JavaScript (jQuery), Node.js, TypeScript \\
\textbf{Backend \& API:} & ASP.NET Core Web API, REST, OAuth2/OIDC, JWT, API versioning, secure authentication \\
\textbf{Databases:} & SQL Server 2019+, T-SQL, query optimization, indexing, schema design \\
\textbf{Cloud \& DevOps:} & Azure (App Service, Azure AD, Key Vault, Azure Monitor), Docker, Kubernetes, Azure DevOps Pipelines, CI/CD \\
\textbf{Frontend:} & Angular (5--17), JavaScript (jQuery), TypeScript, RxJS, NgRx, Angular Material, HTML5, CSS3/SCSS \\
\textbf{Tools \& Testing:} & Visual Studio, VS Code, Git, Postman, JUnit, Mockito, SonarQube, Snyk \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led development of secure backend services using \textbf{C\#} and \textbf{ASP.NET Core Web API}, improving platform integrations and reducing latency by 30\%.}
  \resumeItem{Designed and implemented responsive frontend modules with \textbf{Angular} and \textbf{TypeScript}, enhancing user workflows and reducing UI errors by 25\%.}
  \resumeItem{Developed and maintained SQL Server databases with optimized queries and indexing strategies, improving data retrieval times by 35\%.}
  \resumeItem{Integrated \textbf{Azure} services including App Service and Azure AD to enable secure, scalable cloud deployments and identity management.}
  \resumeItem{Automated deployment pipelines using \textbf{Azure DevOps} and containerized applications with \textbf{Docker} and \textbf{Kubernetes}, accelerating release cycles.}
  \resumeItem{Implemented asynchronous messaging patterns with \textbf{Kafka} and \textbf{AWS SQS/SNS} to improve system reliability and scalability.}
  \resumeItem{Enhanced API security using \textbf{OAuth2/OIDC} and \textbf{JWT} tokens, ensuring compliance with enterprise security standards.}
  \resumeItem{Collaborated in Agile teams to deliver features iteratively, improving sprint velocity and stakeholder satisfaction.}
  \resumeItem{Monitored application performance and health using \textbf{Azure Monitor} and \textbf{OpenTelemetry}, reducing incident response times by 40\%.}
  \resumeItem{Developed internal tools using \textbf{Node.js} to automate workflows and improve developer productivity.}
  \resumeItem{Optimized frontend state management using \textbf{NgRx} and \textbf{RxJS}, enabling predictable UI behavior and easier maintenance.}
  \resumeItem{Improved API documentation and versioning practices using \textbf{OpenAPI}, facilitating smoother integrations.}
  \resumeItem{\textit{Environment: C\#, .NET Core, ASP.NET Core Web API, Angular, TypeScript, JavaScript (jQuery), SQL Server 2019+, Azure, Docker, Kubernetes, Node.js, OAuth2/OIDC, JWT, Kafka, Azure DevOps, OpenTelemetry.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed scalable backend services using \textbf{C\#} and \textbf{ASP.NET Core Web API}, enhancing API responsiveness and reliability by 25\%.}
  \resumeItem{Built dynamic frontend components with \textbf{Angular} and \textbf{JavaScript (jQuery)}, improving user engagement and reducing load times.}
  \resumeItem{Designed and optimized \textbf{SQL Server} databases with indexing and query tuning, resulting in 30\% faster transaction processing.}
  \resumeItem{Implemented cloud-native solutions leveraging \textbf{Azure} services for secure and cost-effective deployments.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Azure DevOps}, enabling faster and reliable application delivery.}
  \resumeItem{Created server-side scripts and automation tools using \textbf{Node.js}, streamlining operational tasks and reducing manual errors.}
  \resumeItem{Integrated authentication and authorization using \textbf{OAuth2/OIDC} and \textbf{JWT}, strengthening security posture.}
  \resumeItem{Collaborated with cross-functional teams in Agile environments to deliver high-quality software on schedule.}
  \resumeItem{Containerized applications with \textbf{Docker} and orchestrated deployments using \textbf{Kubernetes} to improve scalability.}
  \resumeItem{Enhanced frontend state management using \textbf{NgRx} and \textbf{RxJS}, improving maintainability of complex UI workflows.}
  \resumeItem{Monitored system health and performance using \textbf{Azure Monitor} and custom telemetry, reducing downtime by 30\%.}
  \resumeItem{Documented APIs using \textbf{OpenAPI}, ensuring clarity and ease of integration for internal and external consumers.}
  \resumeItem{\textit{Environment: C\#, .NET Core, ASP.NET Core Web API, Angular, JavaScript (jQuery), SQL Server 2019+, Azure, Docker, Kubernetes, Node.js, OAuth2/OIDC, JWT, Azure DevOps, OpenAPI.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed and maintained backend services using \textbf{C\#} and \textbf{ASP.NET Core}, improving API scalability and reducing response times by 20\%.}
  \resumeItem{Built rich frontend interfaces with \textbf{Angular} and \textbf{TypeScript}, enhancing user experience and reducing bugs by 15\%.}
  \resumeItem{Optimized \textbf{SQL Server} databases with indexing and query tuning, improving throughput for high-volume transactions.}
  \resumeItem{Implemented secure authentication mechanisms using \textbf{OAuth2/OIDC} and \textbf{JWT} tokens, aligning with enterprise security policies.}
  \resumeItem{Automated deployment and build processes using \textbf{Azure DevOps} and containerized applications with \textbf{Docker} and \textbf{Kubernetes}.}
  \resumeItem{Developed internal integration endpoints with \textbf{Node.js} to support partner workflows and data synchronization.}
  \resumeItem{Enhanced frontend state management using \textbf{NgRx} and \textbf{RxJS}, enabling efficient handling of complex UI states.}
  \resumeItem{Collaborated in Agile teams to deliver features iteratively, improving sprint completion rates and quality metrics.}
  \resumeItem{Monitored application health and performance using \textbf{Azure Monitor}, reducing incident resolution times.}
  \resumeItem{Improved API documentation and versioning using \textbf{OpenAPI}, facilitating smoother third-party integrations.}
  \resumeItem{Implemented asynchronous messaging patterns to improve system resilience and throughput.}
  \resumeItem{Supported cloud deployments using \textbf{Azure} services, enhancing scalability and security.}
  \resumeItem{\textit{Environment: C\#, .NET Core, ASP.NET Core, Angular, TypeScript, JavaScript (jQuery), SQL Server 2019+, Azure, Docker, Kubernetes, Node.js, OAuth2/OIDC, JWT, Azure DevOps, OpenAPI.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{C\#} and \textbf{ASP.NET Core}, delivering reusable APIs and improving system reliability.}
  \resumeItem{Built frontend features with \textbf{Angular} and \textbf{JavaScript (jQuery)}, enhancing user interaction and responsiveness.}
  \resumeItem{Optimized \textbf{SQL Server} database queries and indexing, improving data access performance by 20\%.}
  \resumeItem{Implemented secure authentication and authorization using \textbf{OAuth2} standards to protect sensitive user data.}
  \resumeItem{Automated builds and deployments using \textbf{Jenkins} and containerized applications with \textbf{Docker} for consistent environments.}
  \resumeItem{Collaborated with cross-functional teams in Agile settings to deliver timely software releases.}
  \resumeItem{Developed internal dashboards using \textbf{React} and \textbf{TypeScript} to support administrative workflows.}
  \resumeItem{Monitored application performance and resolved issues proactively, reducing downtime.}
  \resumeItem{Enhanced API documentation using \textbf{Swagger/OpenAPI} for better developer experience.}
  \resumeItem{Supported cloud deployments on \textbf{Azure} and \textbf{AWS}, improving scalability and availability.}
  \resumeItem{Improved test coverage using unit and integration testing frameworks, enhancing release stability.}
  \resumeItem{Maintained legacy systems while migrating to modern \textbf{.NET Core} and frontend frameworks.}
  \resumeItem{\textit{Environment: C\#, .NET Core, ASP.NET Core, Angular, JavaScript (jQuery), SQL Server, Azure, AWS, Docker, Jenkins, React, TypeScript, OAuth2, Swagger/OpenAPI.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}