\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Accomplished software engineer with strong expertise in \textbf{Java} and \textbf{C\#}, complemented by experience in \textbf{Rust} for systems-level programming.}
  \resumeItem{Delivered cross-platform software solutions targeting both \textbf{Linux} and \textbf{Windows} environments, emphasizing reliability and performance.}
  \resumeItem{Applied modern development practices including \textbf{CI/CD}, automated testing, and version control to ensure high-quality, maintainable codebases.}
  \resumeItem{Skilled in debugging complex issues and driving engineering excellence through clean design and scalable architectures.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Operating Systems:} & Linux, Windows, macOS \\
\textbf{Languages:} & Java, C\#, C++, Rust, Kotlin, Go, TypeScript, Python \\
\textbf{Frameworks \& Tools:} & Spring Boot, ASP.NET Core Web API, REST, gRPC, OpenAPI/Swagger, OAuth2/OIDC, JWT, mTLS \\
\textbf{DevOps \& CI/CD:} & Jenkins, GitHub Actions, Azure DevOps, Docker, Kubernetes, Helm, Terraform, CloudFormation \\
\textbf{Databases \& Caching:} & PostgreSQL, MySQL, DynamoDB, Redis, MongoDB \\
\textbf{Observability \& Testing:} & OpenTelemetry, CloudWatch, Prometheus, Grafana, JUnit, Mockito, Testcontainers, Pact \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led design and development of backend services using \textbf{Java} and \textbf{Spring Boot}, improving modularity and system scalability.}
  \resumeItem{Developed secure API layers with \textbf{REST} and \textbf{gRPC}, enforcing consistent validation and error handling across platforms.}
  \resumeItem{Implemented authentication and authorization using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT}, ensuring enterprise-grade security compliance.}
  \resumeItem{Delivered internal integration endpoints using \textbf{C\#} with \textbf{ASP.NET Core Web API}, enabling efficient service orchestration.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes}, streamlining environment consistency and deployment speed.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{GitHub Actions}, improving release frequency and quality assurance.}
  \resumeItem{Enhanced observability by integrating \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling proactive monitoring and alerting.}
  \resumeItem{Improved backend performance by optimizing data access patterns and caching strategies using \textbf{Redis}, reducing latency by 25\%.}
  \resumeItem{Collaborated in Agile teams to deliver cross-platform software compatible with \textbf{Linux} and \textbf{Windows} environments.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Spring Security, OAuth2/OIDC, JWT, REST, gRPC, C\#, ASP.NET Core, Docker, Kubernetes, Jenkins, GitHub Actions, OpenTelemetry, CloudWatch, Redis.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and implemented distributed services using \textbf{Java} and \textbf{Kotlin}, enhancing system reliability and scalability.}
  \resumeItem{Built APIs using \textbf{REST} and \textbf{gRPC}, ensuring consistent contract definitions and integration across services.}
  \resumeItem{Developed automation tooling with \textbf{Go} to optimize operational workflows and reduce manual intervention.}
  \resumeItem{Implemented event-driven architectures using \textbf{Kafka}, improving throughput and decoupling service dependencies.}
  \resumeItem{Optimized database access patterns for \textbf{DynamoDB} and \textbf{Aurora PostgreSQL}, increasing query efficiency by 20\%.}
  \resumeItem{Secured cloud resources with \textbf{IAM}, encryption via \textbf{KMS}, and secrets management using \textbf{Secrets Manager}.}
  \resumeItem{Containerized services with \textbf{Docker} and deployed on \textbf{EKS/ECS}, enabling scalable and reliable cloud infrastructure.}
  \resumeItem{Provisioned infrastructure using \textbf{Terraform} and \textbf{CloudFormation} to maintain repeatable and auditable environments.}
  \resumeItem{Implemented observability with \textbf{OpenTelemetry} and \textbf{CloudWatch}, improving incident detection and resolution times.}
  \resumeItem{\textit{Environment: Java, Kotlin, Go, REST, gRPC, Kafka, AWS (EKS, ECS, DynamoDB, Aurora, S3), Docker, Kubernetes, Terraform, CloudFormation, OpenTelemetry, CloudWatch.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, delivering scalable APIs with consistent validation and error handling.}
  \resumeItem{Implemented secure access controls using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT}, aligning with enterprise RBAC policies.}
  \resumeItem{Built integration endpoints using \textbf{C\#} with \textbf{ASP.NET Core Web API}, enabling partner and internal orchestration workflows.}
  \resumeItem{Delivered frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, improving user experience and modularity.}
  \resumeItem{Implemented asynchronous processing with \textbf{Kafka}, enhancing reliability through retry and dead-letter queue patterns.}
  \resumeItem{Optimized database queries and caching using \textbf{Hibernate/JPA} and \textbf{Redis}, improving response times by 25\%.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed on \textbf{Kubernetes}, supporting environment-based configurations.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing quality gates with \textbf{SonarQube}.}
  \resumeItem{Integrated cloud platform services across \textbf{AWS}, \textbf{Azure}, and \textbf{GCP} for identity, storage, and messaging.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Spring Security, OAuth2/OIDC, JWT, C\#, ASP.NET Core, Kafka, Angular, React, Redis, Docker, Kubernetes, Jenkins, Azure DevOps, AWS, Azure, GCP.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, delivering reusable components and clean API layers.}
  \resumeItem{Built RESTful APIs and documented endpoints using \textbf{Swagger}, improving integration and maintainability.}
  \resumeItem{Delivered frontend features using \textbf{Angular} and \textbf{React}, enhancing user interfaces with reusable components.}
  \resumeItem{Implemented scheduled workflows using \textbf{Quartz} and \textbf{Spring Scheduling}, automating periodic tasks.}
  \resumeItem{Improved database performance through query optimization and indexing with \textbf{Hibernate/JPA}.}
  \resumeItem{Standardized build and deployment pipelines using \textbf{Maven}, \textbf{Gradle}, and \textbf{Jenkins}, enhancing release stability.}
  \resumeItem{Containerized development and testing environments with \textbf{Docker}, improving consistency across teams.}
  \resumeItem{Supported cloud deployments using \textbf{AWS EC2}, \textbf{S3}, and \textbf{RDS}, enabling scalable infrastructure.}
  \resumeItem{Enhanced automated testing coverage using \textbf{JUnit} and \textbf{Mockito}, reducing defects in production.}
  \resumeItem{\textit{Environment: Java, Spring Boot, REST, Swagger, Angular, React, Hibernate/JPA, Docker, Jenkins, AWS EC2, S3, RDS, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}