\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Deliver full lifecycle software solutions specializing in \textbf{Java} backend development and \textbf{Angular} frontend frameworks for scalable enterprise applications.}
  \resumeItem{Design and implement event-driven architectures using \textbf{Apache Kafka} to ensure reliable asynchronous processing and high throughput.}
  \resumeItem{Develop and deploy serverless functions leveraging \textbf{AWS Lambda} to optimize cloud resource utilization and reduce operational overhead.}
  \resumeItem{Apply expertise in microservices, RESTful APIs, and secure authentication to build robust, maintainable, and scalable distributed systems.}
  \resumeItem{Drive frontend innovation with \textbf{Angular} and TypeScript, delivering responsive, state-managed user interfaces aligned with business goals.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java, Angular, Node.js, TypeScript, Spring Boot, REST, gRPC \\
\textbf{Messaging \& Streaming:} & Apache Kafka, AWS Lambda, AWS SQS, AWS SNS \\
\textbf{Cloud \& Serverless:} & AWS (Lambda, API Gateway, S3, IAM, CloudWatch), Azure, GCP \\
\textbf{Databases \& Caching:} & PostgreSQL, MySQL, DynamoDB, Redis \\
\textbf{DevOps \& CI/CD:} & Docker, Kubernetes, Jenkins, GitHub Actions, Terraform \\
\textbf{Testing \& Observability:} & JUnit, Mockito, OpenTelemetry, Prometheus, Grafana \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led development of microservices using \textbf{Java} and \textbf{Spring Boot}, enhancing modularity and reducing deployment risks significantly.}
  \resumeItem{Engineered asynchronous data pipelines with \textbf{Apache Kafka}, improving system scalability and fault tolerance by decoupling components.}
  \resumeItem{Implemented secure APIs with \textbf{REST} and \textbf{OAuth2}, ensuring compliance with enterprise security standards and reducing vulnerabilities.}
  \resumeItem{Developed dynamic user interfaces using \textbf{Angular} and \textbf{TypeScript}, increasing frontend responsiveness and maintainability.}
  \resumeItem{Built serverless workflows with \textbf{AWS Lambda}, optimizing resource usage and accelerating feature deployment cycles.}
  \resumeItem{Containerized applications with \textbf{Docker} and orchestrated deployments using \textbf{Kubernetes}, enabling scalable and reliable releases.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, reducing manual errors and speeding up delivery.}
  \resumeItem{Monitored application health with \textbf{OpenTelemetry} and \textbf{CloudWatch}, improving incident response times and system reliability.}
  \resumeItem{Collaborated on frontend dashboard modules using \textbf{React} and \textbf{TypeScript}, enhancing administrative workflows.}
  \resumeItem{Optimized database queries and caching strategies with \textbf{Redis}, reducing latency by 25\% in critical read paths.}
  \resumeItem{Implemented event-driven integrations with \textbf{C\#} and \textbf{.NET Core}, enabling seamless service orchestration.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Apache Kafka, AWS Lambda, REST, OAuth2, Angular, React, Docker, Kubernetes, Jenkins, GitHub Actions, Redis, OpenTelemetry, CloudWatch.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and delivered distributed backend services using \textbf{Java} and \textbf{Node.js}, improving API scalability and reliability.}
  \resumeItem{Developed event-driven architectures leveraging \textbf{Apache Kafka} to decouple services and increase throughput.}
  \resumeItem{Implemented serverless solutions with \textbf{AWS Lambda}, reducing infrastructure costs and improving deployment agility.}
  \resumeItem{Built and maintained frontend modules using \textbf{Angular} and \textbf{TypeScript}, enhancing user experience and maintainability.}
  \resumeItem{Automated infrastructure provisioning using \textbf{Terraform} and \textbf{CloudFormation}, ensuring consistent environment setups.}
  \resumeItem{Improved data access performance through optimized queries on \textbf{DynamoDB} and \textbf{Aurora}, reducing latency by 20\%.}
  \resumeItem{Containerized services with \textbf{Docker} and deployed on \textbf{EKS/ECS}, enabling scalable cloud-native applications.}
  \resumeItem{Implemented secure service communication using \textbf{IAM} roles and encrypted secrets management, enhancing platform security.}
  \resumeItem{Established observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, facilitating proactive monitoring and alerting.}
  \resumeItem{Developed integration tests and contract testing to prevent regressions and ensure API reliability.}
  \resumeItem{Delivered operational UI components with \textbf{Angular} and \textbf{React}, streamlining internal workflows.}
  \resumeItem{\textit{Environment: Java, Node.js, Apache Kafka, AWS Lambda, Angular, TypeScript, Docker, Kubernetes, Terraform, OpenTelemetry, CloudWatch.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, delivering scalable APIs with consistent error handling.}
  \resumeItem{Built asynchronous processing pipelines using \textbf{Apache Kafka}, improving system reliability and message throughput.}
  \resumeItem{Implemented secure authentication and authorization using \textbf{Spring Security} and \textbf{OAuth2}, aligning with enterprise compliance.}
  \resumeItem{Created rich frontend experiences with \textbf{Angular} and \textbf{TypeScript}, enabling workflow-driven user interfaces.}
  \resumeItem{Managed state predictably using \textbf{NgRx}, enhancing frontend maintainability and testability.}
  \resumeItem{Developed integration endpoints with \textbf{C\#} and \textbf{ASP.NET Core Web API}, enabling partner system orchestration.}
  \resumeItem{Optimized database performance on \textbf{PostgreSQL} and \textbf{MySQL} with indexing and query tuning, improving response times by 25\%.}
  \resumeItem{Implemented caching strategies using \textbf{Redis}, reducing database load and improving latency.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed using \textbf{Kubernetes}, enabling environment consistency.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing quality and security standards.}
  \resumeItem{Integrated cloud platform services across \textbf{AWS}, \textbf{Azure}, and \textbf{GCP} for identity, storage, and messaging.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Apache Kafka, Angular, TypeScript, NgRx, C\#, ASP.NET Core, PostgreSQL, MySQL, Redis, Docker, Kubernetes, Jenkins, Azure DevOps, AWS, Azure, GCP.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, creating reusable modules and RESTful APIs.}
  \resumeItem{Built frontend features using \textbf{Angular} and \textbf{TypeScript}, enhancing user engagement with reusable components.}
  \resumeItem{Implemented asynchronous processing using messaging queues, improving system throughput and reliability.}
  \resumeItem{Optimized database queries and indexing with \textbf{Hibernate/JPA}, improving performance of critical workflows.}
  \resumeItem{Standardized build and deployment pipelines using \textbf{Maven} and \textbf{Jenkins}, reducing release errors.}
  \resumeItem{Supported cloud deployments on \textbf{AWS}, improving scalability and availability of applications.}
  \resumeItem{Containerized development and test environments with \textbf{Docker}, enhancing developer productivity.}
  \resumeItem{Strengthened automated testing with \textbf{JUnit} and \textbf{Mockito}, improving code quality and stability.}
  \resumeItem{Delivered internal dashboards and tooling using \textbf{React}, improving operational efficiency.}
  \resumeItem{Collaborated in Agile teams to deliver features and enhancements, improving sprint delivery predictability.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Angular, TypeScript, REST, Hibernate, Docker, Jenkins, AWS, JUnit, Mockito, React.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}