\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8+ years} of robust backend solutions specializing in \textbf{Java} and \textbf{Spring Boot} for scalable distributed systems and cloud-native platforms.}
  \resumeItem{Engineered resilient microservices with \textbf{J2EE} architectures, integrating cloud services on \textbf{AWS} and \textbf{Azure} to optimize performance and scalability.}
  \resumeItem{Implemented distributed coordination and state management using \textbf{Apache Zookeeper}, enhancing system reliability and fault tolerance in complex environments.}
  \resumeItem{Led secure API development with \textbf{OAuth2/OIDC} and \textbf{JWT}, ensuring enterprise-grade authentication and authorization compliance.}
  \resumeItem{Automated deployments and infrastructure provisioning with \textbf{Terraform} and \textbf{Kubernetes}, enabling efficient CI/CD pipelines and observability.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages:} & Java (8/11/17/21), Kotlin, Go, C\#, TypeScript, SQL \\
\textbf{Backend Frameworks:} & J2EE, Spring Boot, Spring Security, Hibernate/JPA, ASP.NET Core Web API \\
\textbf{Cloud \& Orchestration:} & AWS (EKS, Lambda, S3, RDS, DynamoDB), Azure (AKS, App Service), Kubernetes, Docker, Terraform \\
\textbf{Distributed Systems:} & Apache Zookeeper, Kafka, AWS SQS/SNS, EventBridge \\
\textbf{API \& Security:} & REST, gRPC, OAuth2/OIDC, JWT, mTLS \\
\textbf{Observability \& CI/CD:} & OpenTelemetry, CloudWatch, Prometheus, Jenkins, GitHub Actions, SonarQube \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Architected and delivered \textbf{Java} microservices with \textbf{Spring Boot}, improving modularity and reducing deployment failures by 35\%.}
  \resumeItem{Integrated distributed coordination using \textbf{Zookeeper}, enhancing system fault tolerance and reducing downtime by 20\%.}
  \resumeItem{Implemented secure APIs with \textbf{OAuth2/OIDC} and \textbf{JWT}, increasing compliance with enterprise security standards by 40\%.}
  \resumeItem{Deployed containerized applications on \textbf{AWS EKS} using \textbf{Docker} and \textbf{Helm}, accelerating release cycles by 50\%.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{GitHub Actions}, reducing manual errors and improving deployment frequency.}
  \resumeItem{Enhanced observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling proactive incident response and reducing MTTR by 30\%.}
  \resumeItem{Developed asynchronous workflows with \textbf{Kafka} and \textbf{AWS SQS/SNS}, improving message throughput and reliability by 25\%.}
  \resumeItem{\textit{Environment: Java 17/21, Spring Boot 3, Spring Security, Apache Zookeeper, AWS (EKS, S3, RDS, DynamoDB, SQS/SNS), Docker, Kubernetes, Helm, Terraform, Jenkins, GitHub Actions.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and implemented \textbf{Java} and \textbf{Kotlin} services with \textbf{J2EE} patterns, improving system scalability by 30\%.}
  \resumeItem{Built and maintained distributed systems with \textbf{Zookeeper} for service coordination, reducing service outages by 15\%.}
  \resumeItem{Developed REST and gRPC APIs secured with \textbf{OAuth2} and \textbf{JWT}, enhancing internal platform security posture.}
  \resumeItem{Provisioned cloud infrastructure using \textbf{Terraform} and \textbf{CloudFormation}, ensuring repeatable deployments and compliance.}
  \resumeItem{Containerized applications with \textbf{Docker}, deployed on \textbf{EKS/ECS}, improving deployment consistency and rollback capabilities.}
  \resumeItem{Implemented event-driven architectures using \textbf{Kafka}, increasing throughput and reducing coupling between services.}
  \resumeItem{Enhanced observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, improving monitoring coverage and alert accuracy.}
  \resumeItem{\textit{Environment: Java 17, Kotlin, J2EE, Apache Zookeeper, AWS (EKS, Lambda, DynamoDB, SQS/SNS), Docker, Kubernetes, Terraform, CloudFormation, OpenTelemetry.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed \textbf{Java} backend services using \textbf{Spring Boot} and \textbf{J2EE} standards, increasing API throughput by 25\%.}
  \resumeItem{Implemented secure authentication with \textbf{OAuth2/OIDC} and \textbf{JWT}, improving access control compliance by 35\%.}
  \resumeItem{Built asynchronous messaging workflows using \textbf{Kafka}, improving processing reliability and latency by 20\%.}
  \resumeItem{Integrated cloud services across \textbf{AWS}, \textbf{Azure}, and \textbf{GCP}, enabling multi-cloud deployment strategies and reducing vendor lock-in.}
  \resumeItem{Containerized applications and orchestrated deployments with \textbf{Kubernetes} and \textbf{Docker}, accelerating environment provisioning by 40\%.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, reducing release cycle times by 30\%.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, OAuth2/OIDC, Kafka, AWS, Azure, GCP, Docker, Kubernetes, Jenkins, Azure DevOps.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{J2EE} components, improving code reuse and maintainability by 30\%.}
  \resumeItem{Built RESTful APIs with \textbf{Swagger} documentation, enhancing integration capabilities across teams.}
  \resumeItem{Implemented scheduled workflows using \textbf{Spring Scheduling} and \textbf{Quartz}, increasing automation and reducing manual intervention.}
  \resumeItem{Supported cloud deployments on \textbf{AWS EC2} and \textbf{S3}, improving scalability and availability of applications.}
  \resumeItem{Containerized development environments using \textbf{Docker}, improving developer productivity and consistency.}
  \resumeItem{\textit{Environment: Java 8, J2EE, Spring Boot 2, REST, Swagger, AWS EC2, S3, Docker, Jenkins, Hibernate/JPA.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

% ===== PROJECTS =====
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{AI-Driven Workflow Automation} | Internal Productivity Tool}{JP Morgan Chase}
\resumeItemListStart
  \resumeItem{Implemented GenAI features using \textbf{Spring AI} and \textbf{AWS Bedrock}, improving task automation efficiency by 35\%.}
  \resumeItem{Designed secure data access patterns and audit logging, ensuring compliance with enterprise security policies.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Distributed Coordination Service} | Service Reliability Enhancement}{Amazon}
\resumeItemListStart
  \resumeItem{Developed distributed locking and leader election mechanisms using \textbf{Apache Zookeeper}, reducing system failures by 20\%.}
  \resumeItem{Integrated \textbf{Java} microservices with \textbf{Zookeeper} for dynamic configuration management, improving system responsiveness.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Cloud-Native Microservices Platform} | Multi-Cloud Deployment}{Paypal}
\resumeItemListStart
  \resumeItem{Engineered scalable \textbf{Java} microservices deployed on \textbf{AWS}, \textbf{Azure}, and \textbf{GCP}, reducing vendor dependency by 30\%.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Azure DevOps}, accelerating release frequency and reducing manual errors.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}