\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8+ years} of expertise in designing and maintaining multi-tier enterprise applications using \textbf{Core Java}, \textbf{J2EE}, and \textbf{Spring Boot} frameworks.}
  \resumeItem{Applied strong object-oriented design principles and design patterns to develop scalable RESTful and SOAP web services for diverse business domains.}
  \resumeItem{Implemented microservices architectures leveraging \textbf{Spring Boot} and \textbf{Hibernate} with robust database design using \textbf{SQL} and \textbf{PL/SQL}.}
  \resumeItem{Developed web applications using \textbf{Servlets}, \textbf{JSP}, and frameworks like \textbf{Struts} and \textbf{Spring MVC}, ensuring maintainability and performance.}
  \resumeItem{Proficient in designing and optimizing backend services with \textbf{ORM} tools, application servers, and delivering solutions aligned to enterprise standards.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java (Core, J2EE), Spring Boot, Struts, Hibernate, JSP, Servlets, RESTful Web Services, SOAP Web Services, Microservices \\
\textbf{Databases \& SQL:} & SQL, PL/SQL, Oracle, MySQL, PostgreSQL, Database Design, ORM (Hibernate) \\
\textbf{Design \& Architecture:} & Object-Oriented Design, Design Patterns, Design Principles, Multi-Tier Application Development \\
\textbf{Web \& Application Servers:} & Apache Tomcat, WebSphere, JBoss, Application Server Management \\
\textbf{Tools \& DevOps:} & Maven, Jenkins, Git, Docker, Kubernetes, CI/CD Pipelines \\
\textbf{Other Technologies:} & Angular, React, C\# \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led design and development of multi-tier applications using \textbf{Java}, \textbf{Spring Boot}, and \textbf{RESTful} services, improving modularity and maintainability.}
  \resumeItem{Implemented secure and scalable microservices architectures with \textbf{Spring Boot} and \textbf{Hibernate}, enhancing system performance by 30\%.}
  \resumeItem{Developed and maintained SOAP and REST APIs integrating with internal and external systems, ensuring compliance with enterprise standards.}
  \resumeItem{Applied object-oriented design and design patterns to refactor legacy \textbf{JSP} and \textbf{Servlet} components, reducing technical debt.}
  \resumeItem{Optimized database interactions using \textbf{SQL} and \textbf{PL/SQL}, improving query performance and reducing latency by 25\%.}
  \resumeItem{Managed deployment on application servers such as \textbf{WebSphere} and \textbf{Tomcat}, ensuring high availability and stability.}
  \resumeItem{Automated build and deployment pipelines using \textbf{Jenkins}, \textbf{Docker}, and \textbf{Kubernetes}, accelerating release cycles.}
  \resumeItem{Collaborated with frontend teams using \textbf{Angular} and \textbf{React} to deliver seamless user experiences aligned with backend services.}
  \resumeItem{Implemented authentication and authorization using \textbf{Spring Security} with OAuth2 and JWT, securing enterprise workflows.}
  \resumeItem{Enhanced service reliability by applying retry and circuit breaker patterns within \textbf{microservices} architecture.}
  \resumeItem{Improved API documentation and versioning using OpenAPI specifications, facilitating smoother integrations.}
  \resumeItem{Conducted code reviews and mentored junior developers on \textbf{Java} best practices and design principles.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Hibernate, REST, SOAP, JSP, Servlets, SQL, PL/SQL, WebSphere, Tomcat, Jenkins, Docker, Kubernetes, Angular, React, Spring Security, OAuth2, JWT.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and developed backend services using \textbf{Java} and \textbf{Spring Boot} to support scalable microservices and API-first applications.}
  \resumeItem{Built and maintained RESTful and SOAP web services, ensuring robust contract compliance and error handling.}
  \resumeItem{Applied object-oriented design and design patterns to improve code quality and maintainability across distributed systems.}
  \resumeItem{Developed database schemas and optimized queries using \textbf{SQL} and \textbf{PL/SQL}, improving data access efficiency by 20\%.}
  \resumeItem{Integrated \textbf{Hibernate} ORM for seamless object-relational mapping and transaction management.}
  \resumeItem{Implemented service orchestration and communication using \textbf{microservices} principles and \textbf{Spring Cloud} components.}
  \resumeItem{Containerized applications using \textbf{Docker} and orchestrated deployments with \textbf{Kubernetes} for scalable cloud-native solutions.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Git}, reducing deployment times by 35\%.}
  \resumeItem{Collaborated with frontend teams to integrate \textbf{Angular} and \textbf{React} components with backend APIs for enhanced user experience.}
  \resumeItem{Ensured application security using \textbf{Spring Security} and implemented role-based access controls.}
  \resumeItem{Monitored application performance and reliability, applying fixes to reduce latency and improve throughput.}
  \resumeItem{Participated in Agile ceremonies and contributed to sprint planning and retrospectives.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Hibernate, REST, SOAP, Microservices, SQL, PL/SQL, Docker, Kubernetes, Jenkins, Angular, React, Spring Security.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed enterprise web applications using \textbf{Java}, \textbf{Spring Boot}, and \textbf{J2EE} technologies, improving service scalability.}
  \resumeItem{Designed and implemented RESTful APIs with \textbf{OpenAPI} standards, ensuring consistent validation and error handling.}
  \resumeItem{Built SOAP web services to support legacy integrations and external partner systems.}
  \resumeItem{Applied object-oriented design and design patterns to create reusable components and reduce code duplication.}
  \resumeItem{Optimized database performance using \textbf{SQL}, \textbf{PL/SQL}, and \textbf{Hibernate}, improving query response times by 25\%.}
  \resumeItem{Implemented asynchronous processing and messaging patterns to improve system throughput and reliability.}
  \resumeItem{Developed frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript} for rich user interfaces.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes} clusters for environment consistency.}
  \resumeItem{Automated builds and deployments using \textbf{Jenkins} and \textbf{Azure DevOps}, enhancing release cadence.}
  \resumeItem{Collaborated with cross-functional teams to ensure adherence to design principles and coding standards.}
  \resumeItem{Implemented security features using \textbf{Spring Security} and OAuth2 to protect sensitive data.}
  \resumeItem{\textit{Environment: Java, Spring Boot, J2EE, REST, SOAP, Hibernate, SQL, PL/SQL, Angular, React, Docker, Kubernetes, Jenkins, Azure DevOps, Spring Security, OAuth2.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{J2EE} components including \textbf{Servlets} and \textbf{JSP}, enhancing application modularity.}
  \resumeItem{Implemented RESTful APIs and SOAP web services adhering to enterprise SOA standards.}
  \resumeItem{Applied design patterns and object-oriented principles to improve code maintainability and extensibility.}
  \resumeItem{Optimized database interactions using \textbf{SQL}, \textbf{PL/SQL}, and \textbf{Hibernate}, reducing query execution times.}
  \resumeItem{Built frontend features using \textbf{Angular} and \textbf{React} frameworks for internal dashboards and admin tools.}
  \resumeItem{Managed application deployments on \textbf{WebSphere} and \textbf{Tomcat} servers, ensuring high availability.}
  \resumeItem{Automated build processes using \textbf{Maven} and integrated CI pipelines with \textbf{Jenkins}.}
  \resumeItem{Implemented scheduled batch jobs using \textbf{Quartz} and \textbf{Spring Scheduling} for periodic data processing.}
  \resumeItem{Containerized development environments with \textbf{Docker} to streamline testing and deployment workflows.}
  \resumeItem{Enhanced application security and compliance with enterprise policies.}
  \resumeItem{\textit{Environment: Java, J2EE, Servlets, JSP, REST, SOAP, Hibernate, SQL, PL/SQL, Angular, React, WebSphere, Tomcat, Maven, Jenkins, Docker, Quartz, Spring Scheduling.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}