\documentclass[a4paper,10pt]{article}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{margin=1in}

\begin{document}

\begin{center}
    {\LARGE \textbf{John Doe}}\\
    \vspace{2mm}
    \href{mailto:johndoe@example.com}{johndoe@example.com} $|$ +1 234 567 8901 $|$ \href{https://linkedin.com/in/johndoe}{linkedin.com/in/johndoe} $|$ \href{https://github.com/johndoe}{github.com/johndoe}
\end{center}

\section*{Summary}
Innovative software engineer specializing in AI-driven chatbot development with expertise in natural language processing and automation. Delivered scalable customer support solutions resulting in 30\% faster response times. Skilled in machine learning and data analysis to optimize user experience and operational efficiency. Proven track record of designing NLP models that increased user engagement by 25\%.

\section*{Professional Experience}

\textbf{Software Engineer} \hfill San Francisco, CA \\
ABC Tech Solutions \hfill June 2020 -- Present
\begin{itemize}
    \item Designed and implemented \textbf{NLP}-based chatbot modules improving customer support efficiency by 35\% through enhanced automation and precise intent recognition.
    \item Developed data-driven algorithms using \textbf{Python, TensorFlow}, and \textbf{scikit-learn} to optimize chatbot responses, increasing user satisfaction by 20\%.
    \item Collaborated with cross-functional teams to integrate AI features in customer platforms resulting in 40\% reduction in manual queries handled.
\end{itemize}

\textbf{Junior Developer} \hfill Seattle, WA \\
Innovatech Inc. \hfill July 2018 -- May 2020
\begin{itemize}
    \item Automated data processing workflows using \textbf{Python} and \textbf{SQL}, achieving 50\% reduction in report generation time for business analytics.
    \item Implemented backend RESTful APIs in \textbf{Django} that supported client applications, improving data availability by 30\%.
    \item Conducted performance tuning and bug fixes improving overall application stability by 25\%.
\end{itemize}

\section*{Projects}

\textbf{AI-Powered Salary Chatbot} | NLP and Machine Learning Application \\
\begin{itemize}
    \item Engineered an intelligent chatbot using \textbf{Python}, \textbf{NLTK}, and \textbf{TensorFlow} that delivers personalized salary insights, boosting user engagement by 35\%.
    \item Integrated real-time data analysis features that provide automated career advice, increasing customer satisfaction scores by 20\%.
\end{itemize}

\textbf{Customer Support Automation Tool} \\
\begin{itemize}
    \item Developed an automated ticket classification system using \textbf{Python} and \textbf{scikit-learn}, reducing response time by 40\%.
    \item Streamlined support workflows with predictive analytics, resulting in 30\% higher first-contact resolution rates.
\end{itemize}

\textbf{Data Visualization Dashboard} \\
\begin{itemize}
    \item Created interactive dashboards using \textbf{JavaScript} and \textbf{D3.js}, providing actionable insights for business decision makers.
    \item Enhanced data accuracy and reporting speed by 25\% through efficient ETL pipeline integration.
\end{itemize}

\section*{Technical Skills}

\textbf{Programming Languages:} Python, JavaScript, SQL \\
\textbf{Machine Learning \& AI:} TensorFlow, scikit-learn, NLTK, Pandas \\
\textbf{Web Development:} Django, REST APIs, React \\
\textbf{Data Analysis:} Excel, Tableau, D3.js \\
\textbf{Tools \& Platforms:} Git, Docker, AWS \\
\textbf{Other Skills:} Agile Methodologies, Automated Testing

\end{document}