\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Deliver over 8 years of expertise in backend software engineering specializing in \textbf{Java} and \textbf{Spring Boot} to build scalable microservices and RESTful APIs.}
  \resumeItem{Drive client transformation initiatives with a consulting mindset, leveraging Agile methodologies and collaborative communication to align technical solutions with business goals.}
  \resumeItem{Implement robust application monitoring using tools like \textbf{Splunk} and \textbf{New Relic} to ensure system reliability and proactive incident management.}
  \resumeItem{Adapt quickly to evolving technologies and fast-paced environments, continuously enhancing skills to deliver high-quality, maintainable software solutions.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java (8/11/17+), Spring Boot, Spring Security, RESTful APIs, Microservices \\
\textbf{Application Monitoring:} & Splunk, New Relic, OpenTelemetry, CloudWatch \\
\textbf{Cloud \& DevOps:} & AWS (EKS, S3, RDS, IAM), Docker, Kubernetes, Jenkins, GitHub Actions, Terraform \\
\textbf{Databases:} & PostgreSQL, MySQL, Redis \\
\textbf{Methodologies:} & Agile, Scrum, CI/CD, Test-Driven Development \\
\textbf{Communication \& Collaboration:} & Jira, Confluence, Git, Strong verbal and written communication \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led development of \textbf{Java} microservices using \textbf{Spring Boot}, improving API response times by 30\% through optimized service design and caching.}
  \resumeItem{Designed and implemented secure RESTful APIs with \textbf{Spring Security}, \textbf{OAuth2}, and \textbf{JWT}, enhancing authentication and authorization workflows.}
  \resumeItem{Integrated application monitoring using \textbf{Splunk} and \textbf{New Relic}, reducing incident response times by 25\% through proactive alerting and dashboards.}
  \resumeItem{Collaborated with cross-functional teams in an \textbf{Agile} environment, facilitating sprint planning and retrospectives to improve delivery efficiency by 15\%.}
  \resumeItem{Containerized services with \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling scalable and reliable cloud-native application delivery.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, increasing deployment frequency by 40\% while maintaining quality standards.}
  \resumeItem{\textit{Environment: Java 17/21, Spring Boot 3, Spring Security, OAuth2, JWT, Splunk, New Relic, REST, Docker, Kubernetes, Jenkins, GitHub Actions, AWS (EKS, S3, RDS), Agile.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed scalable \textbf{Java} microservices with \textbf{Spring Boot}, delivering high-performance REST APIs for internal and external clients.}
  \resumeItem{Implemented robust authentication and authorization using \textbf{Spring Security} and \textbf{OAuth2}, securing microservice endpoints and data access.}
  \resumeItem{Monitored application health using \textbf{New Relic} and \textbf{CloudWatch}, improving system uptime by 20\% through early anomaly detection.}
  \resumeItem{Collaborated in Agile teams to deliver incremental features, enhancing sprint velocity by 18\% through effective communication and backlog refinement.}
  \resumeItem{Containerized and orchestrated services with \textbf{Docker} and \textbf{Kubernetes}, supporting zero-downtime deployments and scalability.}
  \resumeItem{Provisioned infrastructure using \textbf{Terraform} and \textbf{CloudFormation}, ensuring consistent and auditable environment setups.}
  \resumeItem{\textit{Environment: Java 17, Spring Boot, Spring Security, OAuth2, REST, New Relic, CloudWatch, Docker, Kubernetes, Terraform, CloudFormation, Agile.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Engineered backend services using \textbf{Java} and \textbf{Spring Boot}, delivering RESTful APIs with consistent validation and error handling.}
  \resumeItem{Implemented security protocols with \textbf{Spring Security}, \textbf{OAuth2}, and \textbf{JWT}, reducing unauthorized access incidents by 30\%.}
  \resumeItem{Enhanced application monitoring using \textbf{Splunk}, enabling faster root cause analysis and reducing mean time to recovery by 20\%.}
  \resumeItem{Worked in Agile teams to deliver features iteratively, improving team collaboration and sprint completion rates by 15\%.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed using \textbf{Kubernetes}, improving deployment reliability and scalability.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Azure DevOps}, increasing deployment frequency and reducing manual errors.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, Spring Security, OAuth2, JWT, REST, Splunk, Docker, Kubernetes, Jenkins, Azure DevOps, Agile.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, delivering RESTful APIs with clear documentation and versioning.}
  \resumeItem{Collaborated in Agile teams to deliver features on schedule, improving sprint delivery consistency by 12\%.}
  \resumeItem{Implemented application monitoring using \textbf{Splunk}, reducing downtime by enabling proactive issue detection.}
  \resumeItem{Built containerized environments with \textbf{Docker}, improving development and testing efficiency by 25\%.}
  \resumeItem{Automated build and deployment pipelines using \textbf{Jenkins}, reducing manual deployment errors and accelerating release cycles.}
  \resumeItem{\textit{Environment: Java 8, Spring Boot 2, REST, Splunk, Docker, Jenkins, AWS (EC2, S3, RDS), Agile.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

% ===== PROJECTS =====
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{AI-Powered Customer Support Chatbot} | Internal}{2024}
\resumeItemListStart
  \resumeItem{Developed an AI-driven chatbot using \textbf{Spring Boot} integrated with NLP services to automate customer queries, reducing response time by 40\%.}
  \resumeItem{Implemented secure REST APIs and monitored application health using \textbf{New Relic}, achieving 99.9\% uptime during peak usage.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Microservices-Based Payment Gateway} | Amazon}{2023}
\resumeItemListStart
  \resumeItem{Designed and developed scalable \textbf{Java} microservices with \textbf{Spring Boot} to handle 1M+ transactions daily with 99.99\% availability.}
  \resumeItem{Implemented API security using \textbf{OAuth2} and \textbf{JWT}, reducing fraudulent transactions by 25\% through enhanced authorization.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Application Monitoring Dashboard} | Paypal}{2021}
\resumeItemListStart
  \resumeItem{Built a centralized monitoring dashboard integrating \textbf{Splunk} and \textbf{New Relic} data, reducing incident detection time by 30\%.}
  \resumeItem{Developed RESTful APIs using \textbf{Spring Boot} to expose monitoring metrics and alerts for operational teams.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}