\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Rahul Reddy K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (714) 805-6273 ~ | ~ \href{mailto:kanrahuldo1@gmail.com}{kanrahuldo1@gmail.com}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{\textbf{Embedded Firmware Engineer} with \textbf{8+ years} of expertise in designing and developing robust embedded systems using \textbf{C/C++} on bare-metal and RTOS platforms, including FreeRTOS.}
    \resumeItem{Skilled in translating complex system requirements into modular architecture and efficient code, ensuring high reliability through rigorous unit and system-level testing.}
    \resumeItem{Experienced in debugging embedded firmware using \textbf{JTAG/BDM} and emulators, and proficient in Agile and Waterfall methodologies for product development lifecycle.}
    \resumeItem{Collaborated with global cross-functional teams and interfaced with customers across multiple time zones to gather requirements and provide technical support.}
    \resumeItem{Adept at investigating new embedded technologies and standards to enhance product capabilities and maintain compliance throughout validation and production phases.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & C, C++, Python, Shell Scripting \\
                \textbf{Embedded Platforms \& RTOS:} & Bare-metal, FreeRTOS, VxWorks, QNX, ARM Cortex-M/A, STM32, 8051, MSP430, PIC Microcontrollers \\
                \textbf{Debugging \& Tools:} & JTAG, BDM, Emulators, GDB, Valgrind, SonarQube, cppCheck, Coverity, Logic Analyzer, Oscilloscope \\
                \textbf{Protocols \& Communication:} & I2C, SPI, CAN, LIN, J1939, USART, TCP/IP, UDP/IP, MQTT \\
                \textbf{Version Control \& CI/CD:} & Git/GitHub, SVN, Jenkins, CMake, Ansible \\
                \textbf{Methodologies \& Design:} & Agile, Waterfall, Object-Oriented Analysis and Design (OOAD), Test Driven Development \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Toyota Motors}{Oct 2023 -- Present}
        {C++ Embedded / Application Developer}{TX}
      \resumeItemListStart
        \resumeItem{Designed and developed embedded firmware modules in \textbf{C/C++} for automotive systems, ensuring compliance with system requirements and architecture.}
        \resumeItem{Implemented unit and system-level tests to validate firmware robustness, reducing defect rates by 30\% through automated test suites.}
        \resumeItem{Collaborated with global hardware, software, QA, and project management teams to align firmware design with cross-functional requirements.}
        \resumeItem{Debugged embedded systems using \textbf{JTAG} and emulators, identifying root causes and delivering timely fixes for critical firmware issues.}
        \resumeItem{Integrated \textbf{CAN} and \textbf{I2C} communication protocols for peripheral device control, enhancing system reliability and performance.}
        \resumeItem{Managed source code using \textbf{Git/GitHub} and automated builds with \textbf{CMake}, streamlining development workflows and deployment.}
        \resumeItem{Supported product lifecycle phases including validation, verification, and production support, ensuring firmware compliance with industry standards.}
        \resumeItem{Interfaced with customers across multiple time zones to gather requirements and provide technical support, improving communication efficiency.}
        \resumeItem{Investigated emerging embedded technologies and standards, recommending improvements that increased firmware scalability and maintainability.}
        \resumeItem{Authored detailed technical documentation and test plans, facilitating knowledge transfer and compliance audits.}
      \resumeItemListEnd

    \resumeSubheading
        {Texas Instruments}{Aug 2022 -- Sep 2023}
        {C/C++ Embedded Developer}{Phoenix, AZ}
      \resumeItemListStart
        \resumeItem{Developed embedded firmware in \textbf{C/C++} on \textbf{FreeRTOS} and \textbf{VxWorks} platforms, translating system requirements into efficient code.}
        \resumeItem{Implemented multi-threaded state machines and synchronization mechanisms to maintain device operational integrity under real-time constraints.}
        \resumeItem{Debugged firmware using \textbf{JTAG} and \textbf{GDB}, performing root cause analysis and improving system stability by 25\%.}
        \resumeItem{Collaborated with QA and hardware teams to design and execute unit and system-level tests, enhancing firmware reliability.}
        \resumeItem{Integrated \textbf{CAN/J1939} and \textbf{I2C/SPI} protocols for sensor and peripheral communication, optimizing data throughput and latency.}
        \resumeItem{Authored and reviewed UML diagrams and technical documentation supporting \textbf{OOAD} principles for maintainable firmware architecture.}
        \resumeItem{Automated build and test pipelines using \textbf{Jenkins} and static analysis tools like \textbf{SonarQube}, increasing code quality and deployment speed.}
        \resumeItem{Designed and implemented embedded UI components using QT/QML on \textbf{QNX RTOS}, improving user interaction responsiveness.}
        \resumeItem{Performed peer code reviews and mentored junior engineers on embedded firmware best practices and debugging techniques.}
      \resumeItemListEnd

    \resumeSubheading
        {Texas Instruments}{May 2021 -- Jul 2022}
        {C/C++ Embedded Developer}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Developed embedded firmware in \textbf{C/C++} for microcontroller-based systems, focusing on modular design and efficient resource usage.}
        \resumeItem{Implemented AUTOSAR-compliant modules integrating \textbf{SPI}, \textbf{CAN}, and \textbf{PWM} peripherals, ensuring protocol compliance and system interoperability.}
        \resumeItem{Created backend communication components using Qt signals/slots, enabling seamless UI updates on \textbf{QNX RTOS} devices.}
        \resumeItem{Automated integration testing and reporting using \textbf{Python} and shell scripting, reducing manual effort by 40\%.}
      \resumeItemListEnd

    \resumeSubheading
        {Panasonic}{Feb 2020 -- Apr 2021}
        {C++ Developer}{Bengaluru, KA}
      \resumeItemListStart
        \resumeItem{Engineered real-time embedded \textbf{C++} firmware for print job management on \textbf{VxWorks RTOS}, improving throughput by 15\%.}
        \resumeItem{Developed low-level device drivers in \textbf{C} for \textbf{SPI}, \textbf{I2C}, and \textbf{USART} peripherals, enhancing hardware communication reliability.}
        \resumeItem{Implemented TCP/IP networking stacks to support remote monitoring and control via embedded REST APIs.}
        \resumeItem{Built HMI components using \textbf{QT/QML} on \textbf{QNX RTOS} with a \textbf{C++} backend, improving user experience and responsiveness.}
        \resumeItem{Created automated CI/CD pipelines with \textbf{Jenkins} and \textbf{CMake}, accelerating firmware build and regression testing cycles.}
        \resumeItem{Resolved critical firmware defects using \textbf{JTAG} debugging and memory profiling tools, reducing crash rates significantly.}
      \resumeItemListEnd

    \resumeSubheading
        {JSW Steel}{Aug 2017 -- Dec 2019}
        {C++ Embedded Developer}{India}
      \resumeItemListStart
        \resumeItem{Modernized legacy embedded systems by rewriting Fortran code into efficient, multi-threaded \textbf{C++} firmware, improving maintainability.}
        \resumeItem{Developed \textbf{C/C++} embedded communication interfaces for \textbf{I2C}, \textbf{SPI}, and \textbf{CAN} devices, ensuring seamless sensor integration.}
        \resumeItem{Designed and implemented IPC mechanisms and network communication using \textbf{TCP/IP} and \textbf{UDP/IP} protocols for distributed systems.}
        \resumeItem{Built embedded UI components with \textbf{Qt/QML} and managed backend logic using \textbf{C++} signals/slots, enhancing infotainment system responsiveness.}
        \resumeItem{Investigated bus traffic and protocol compliance using \textbf{Wireshark} and protocol analyzers, improving communication reliability.}
        \resumeItem{Managed source control migration from \textbf{SVN} to \textbf{Git}, preserving history and streamlining version management workflows.}
        \resumeItem{Automated reporting and monitoring tasks using \textbf{Python} scripts, increasing operational efficiency and data accuracy.}
        \resumeItem{Supported system testing, UAT, and production deployments, ensuring smooth firmware releases and post-deployment support.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\end{document}