\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small#2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Deliver over 8 years of full stack development expertise primarily focused on \textbf{C\#} and \textbf{.NET Core} with strong proficiency in \textbf{Angular} frontend and \textbf{AWS} cloud services.}
  \resumeItem{Design and implement scalable \textbf{microservices} and \textbf{REST APIs} with robust system design principles, ensuring high performance and maintainability.}
  \resumeItem{Integrate AI/ML and \textbf{Generative AI} capabilities into enterprise workflows, leveraging modern frameworks and cloud AI services for automation and productivity gains.}
  \resumeItem{Apply hands-on experience with \textbf{SQL} and \textbf{NoSQL} databases, optimizing data models and query performance to support complex distributed systems.}
  \resumeItem{Utilize containerization and orchestration tools like \textbf{Docker} and \textbf{Kubernetes} alongside CI/CD pipelines to enable efficient delivery and deployment.}
  \resumeItem{Collaborate in Agile environments to deliver enterprise-grade solutions, emphasizing security, observability, and cloud-native best practices.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & \textbf{C\#}, \textbf{.NET Core / .NET 6+}, \textbf{Angular}, TypeScript, JavaScript, SQL, NoSQL (MongoDB, DynamoDB) \\
\textbf{Cloud \& DevOps:} & AWS (EKS, ECS/Fargate, Lambda, API Gateway, S3, RDS/Aurora, DynamoDB, IAM, KMS, Secrets Manager, CloudWatch, Bedrock), Docker, Kubernetes, CI/CD (Jenkins, GitHub Actions, Azure DevOps) \\
\textbf{API \& Architecture:} & REST APIs, Microservices, System Design, OAuth2/OIDC, JWT, mTLS \\
\textbf{AI/ML \& Generative AI:} & AWS Bedrock, LangChain, Semantic Kernel, AutoGen, RAG architectures, Vector Databases (Pinecone, FAISS, OpenSearch) \\
\textbf{Databases:} & SQL (PostgreSQL, MySQL, Aurora), NoSQL (DynamoDB, MongoDB), Redis \\
\textbf{Testing \& Observability:} & JUnit, Mockito, Testcontainers, OpenTelemetry, CloudWatch, Prometheus, Grafana \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led design and development of \textbf{C\#/.NET 6} microservices, improving modularity and reducing release risks through clear service boundaries.}
  \resumeItem{Developed and maintained \textbf{REST APIs} with consistent validation and error handling, enhancing integration across enterprise platforms.}
  \resumeItem{Implemented \textbf{Angular} frontend modules using \textbf{TypeScript} and \textbf{NgRx}, delivering workflow-heavy UI with improved user experience.}
  \resumeItem{Integrated \textbf{Generative AI} capabilities using \textbf{AWS Bedrock} and \textbf{RAG} techniques, boosting internal productivity workflows.}
  \resumeItem{Built asynchronous event-driven processing pipelines leveraging \textbf{Kafka} and \textbf{AWS SQS/SNS}, increasing system reliability and scalability.}
  \resumeItem{Optimized database queries and caching with \textbf{Redis} and \textbf{JPA/Hibernate}, reducing latency by up to 40\% for critical paths.}
  \resumeItem{Containerized services with \textbf{Docker} and orchestrated deployments on \textbf{Kubernetes (EKS)} using \textbf{Helm}, enabling repeatable releases.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{GitHub Actions}, enforcing code quality and security via \textbf{SonarQube} and \textbf{Snyk}.}
  \resumeItem{Implemented observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, providing actionable metrics and alerting for production systems.}
  \resumeItem{\textit{Environment: \textbf{C\#}, \textbf{.NET 6}, \textbf{Angular}, \textbf{AWS Bedrock}, \textbf{Kafka}, \textbf{Redis}, \textbf{Docker}, \textbf{Kubernetes}, \textbf{Jenkins}, \textbf{GitHub Actions}, \textbf{OpenTelemetry}.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed scalable backend services using \textbf{Java} and \textbf{Kotlin}, focusing on API-first design and microservices architecture.}
  \resumeItem{Built \textbf{REST} and \textbf{gRPC} APIs, ensuring contract consistency and seamless integration across distributed systems.}
  \resumeItem{Implemented event-driven workflows with \textbf{Kafka}, improving throughput and decoupling service dependencies for better scalability.}
  \resumeItem{Designed and optimized access patterns for \textbf{DynamoDB} and \textbf{Aurora PostgreSQL}, improving query performance and reducing latency.}
  \resumeItem{Containerized and deployed microservices using \textbf{Docker} and \textbf{EKS/ECS}, enabling reliable cloud-native operations.}
  \resumeItem{Provisioned infrastructure with \textbf{Terraform} and \textbf{CloudFormation}, ensuring repeatable and auditable cloud environments.}
  \resumeItem{Implemented observability and monitoring using \textbf{OpenTelemetry} and \textbf{CloudWatch}, improving operational awareness and incident response.}
  \resumeItem{Developed frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, enhancing user interfaces for operational workflows.}
  \resumeItem{Built automated testing frameworks with \textbf{JUnit}, \textbf{Mockito}, and \textbf{Testcontainers}, increasing release stability and quality.}
  \resumeItem{\textit{Environment: \textbf{Java}, \textbf{Kotlin}, \textbf{Angular}, \textbf{React}, \textbf{Kafka}, \textbf{AWS}, \textbf{Docker}, \textbf{Kubernetes}, \textbf{Terraform}, \textbf{OpenTelemetry}.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{C\#} and \textbf{ASP.NET Core Web API}, enabling secure and scalable integration workflows.}
  \resumeItem{Built and maintained \textbf{REST APIs} with consistent validation, versioning, and error handling for enterprise applications.}
  \resumeItem{Delivered frontend components using \textbf{Angular} and \textbf{TypeScript}, implementing reusable modules and state management with \textbf{NgRx}.}
  \resumeItem{Implemented asynchronous messaging with \textbf{Kafka} to improve system resilience and throughput for critical processes.}
  \resumeItem{Optimized database performance on \textbf{PostgreSQL} and \textbf{MySQL} through query tuning and indexing, reducing response times by 25\%.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling environment-based configuration and scaling.}
  \resumeItem{Integrated multi-cloud platform services across \textbf{AWS}, \textbf{Azure}, and \textbf{GCP} for identity, storage, and messaging solutions.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing quality gates and security scans.}
  \resumeItem{Developed batch automation utilities in \textbf{Go} to streamline performance-sensitive workflows and reduce manual intervention.}
  \resumeItem{\textit{Environment: \textbf{C\#}, \textbf{ASP.NET Core}, \textbf{Angular}, \textbf{Kafka}, \textbf{PostgreSQL}, \textbf{Docker}, \textbf{Kubernetes}, \textbf{AWS}, \textbf{Azure}, \textbf{Go}, \textbf{Jenkins}.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, delivering reusable APIs and scalable components.}
  \resumeItem{Built \textbf{RESTful} APIs with documented endpoints, ensuring consistent standards and integration readiness.}
  \resumeItem{Delivered frontend features using \textbf{Angular} and \textbf{TypeScript}, creating reusable components and shared modules.}
  \resumeItem{Implemented scheduled processing using \textbf{Quartz} and \textbf{Spring Scheduling} for periodic workflows and batch jobs.}
  \resumeItem{Optimized database queries and indexing using \textbf{Hibernate/JPA}, improving performance and reducing contention.}
  \resumeItem{Standardized build and deployment pipelines using \textbf{Maven/Gradle} and \textbf{Jenkins} for continuous integration.}
  \resumeItem{Containerized development and test environments with \textbf{Docker}, enabling consistent and portable setups.}
  \resumeItem{Supported cloud deployments on \textbf{AWS}, leveraging EC2, S3, and RDS services for scalable infrastructure.}
  \resumeItem{Enhanced automated testing coverage using \textbf{JUnit} and \textbf{Mockito}, improving release stability.}
  \resumeItem{\textit{Environment: \textbf{Java}, \textbf{Spring Boot}, \textbf{Angular}, \textbf{Docker}, \textbf{AWS}, \textbf{Jenkins}, \textbf{Hibernate/JPA}.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}