\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered \textbf{8+ years} of full stack development expertise focusing on \textbf{C\#}, \textbf{.NET Core/.NET 6+}, and \textbf{Angular} to build scalable enterprise applications.}
  \resumeItem{Designed and implemented cloud-native solutions leveraging \textbf{Azure} services, microservices architecture, and RESTful APIs to enhance system reliability and scalability.}
  \resumeItem{Integrated AI/ML capabilities including \textbf{Generative AI} and vector search technologies, improving automation and user experience through intelligent features.}
  \resumeItem{Applied containerization and orchestration skills using \textbf{Docker} and \textbf{Kubernetes} alongside robust CI/CD pipelines for streamlined deployments.}
  \resumeItem{Expertise in SQL and NoSQL databases with a strong focus on system design and secure, high-performance backend services.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & \textbf{C\#}, \textbf{.NET Core / .NET 6+}, \textbf{Angular}, TypeScript, Java, Go \\
\textbf{Cloud \& DevOps:} & Azure (AKS, App Service, Azure AI Foundry, Azure Monitor, Key Vault), Docker, Kubernetes, CI/CD (Azure DevOps, Jenkins, GitHub Actions) \\
\textbf{Databases:} & SQL Server, PostgreSQL, MongoDB, NoSQL, Vector Databases (Pinecone, FAISS, OpenSearch) \\
\textbf{API \& Architecture:} & REST APIs, Microservices, System Design, RAG architectures, gRPC \\
\textbf{AI/ML \& Generative AI:} & LangChain, Semantic Kernel, AutoGen, OpenAI, Generative AI integration, AI copilots, Chatbots \\
\textbf{Tools \& Others:} & Terraform, Helm, SonarQube, Snyk, OpenTelemetry, Prometheus, Grafana \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led design and development of backend services using \textbf{C\#} and \textbf{.NET 6+}, improving API modularity and system scalability by 30\%.}
  \resumeItem{Developed and maintained \textbf{RESTful APIs} and microservices, enforcing secure authentication with \textbf{OAuth2/OIDC} and \textbf{JWT} tokens.}
  \resumeItem{Built dynamic frontend modules with \textbf{Angular} and \textbf{TypeScript}, enhancing user workflows and reducing UI bugs by 25\%.}
  \resumeItem{Integrated \textbf{Generative AI} capabilities using \textbf{Azure AI Foundry} and \textbf{OpenAI}, enabling intelligent automation and knowledge retrieval via \textbf{RAG} techniques.}
  \resumeItem{Implemented asynchronous processing using event-driven patterns, improving system throughput with \textbf{Kafka} and \textbf{Azure Service Bus}.}
  \resumeItem{Optimized database queries and caching strategies using \textbf{SQL Server} and \textbf{Redis}, reducing latency by 35\%.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed on \textbf{Azure Kubernetes Service (AKS)} using \textbf{Helm} charts for consistent releases.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Azure DevOps} and \textbf{GitHub Actions}, enforcing quality and security checks via \textbf{SonarQube} and \textbf{Snyk}.}
  \resumeItem{Implemented observability using \textbf{OpenTelemetry} and \textbf{Azure Monitor}, enabling proactive incident detection and resolution.}
  \resumeItem{\textit{Environment: C\#, .NET 6+, Angular, TypeScript, Azure (AKS, AI Foundry, Service Bus, Key Vault), Docker, Kubernetes, Helm, Redis, SQL Server, Kafka, Azure DevOps, GitHub Actions, SonarQube, Snyk, OpenTelemetry.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed scalable backend microservices using \textbf{C\#} and \textbf{.NET Core}, improving API response times by 25\%.}
  \resumeItem{Designed and implemented \textbf{RESTful APIs} and event-driven workflows using \textbf{Azure} messaging services and \textbf{Kafka} for high availability.}
  \resumeItem{Built frontend components with \textbf{Angular} and \textbf{TypeScript}, enhancing configuration and operational user interfaces.}
  \resumeItem{Integrated vector search and \textbf{RAG} architectures with \textbf{OpenSearch} to enable semantic search capabilities for internal tools.}
  \resumeItem{Automated deployments and infrastructure provisioning with \textbf{Terraform} and \textbf{Helm}, ensuring repeatable and auditable environments.}
  \resumeItem{Reduced backend latency using \textbf{Redis} caching and optimized \textbf{SQL} queries, improving throughput by 30\%.}
  \resumeItem{Containerized services using \textbf{Docker} and orchestrated with \textbf{Kubernetes} on \textbf{Azure AKS} and \textbf{EKS}, supporting blue-green deployments.}
  \resumeItem{Implemented CI/CD pipelines with \textbf{Jenkins} and \textbf{GitHub Actions}, integrating security scans and quality gates.}
  \resumeItem{Enhanced observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling detailed metrics and alerting.}
  \resumeItem{\textit{Environment: C\#, .NET Core, Angular, TypeScript, Azure (AKS, Service Bus), Docker, Kubernetes, Terraform, Helm, Redis, SQL Server, OpenSearch, Jenkins, GitHub Actions, OpenTelemetry.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{C\#} and \textbf{ASP.NET Core Web API}, delivering secure and scalable microservices for partner integrations.}
  \resumeItem{Built \textbf{RESTful APIs} with consistent validation, versioning, and error handling, improving client consumption by 20\%.}
  \resumeItem{Implemented frontend modules using \textbf{Angular} and \textbf{TypeScript}, creating reusable components and improving UI responsiveness.}
  \resumeItem{Applied \textbf{NgRx} for state management in complex workflows, enhancing maintainability and reducing bugs.}
  \resumeItem{Integrated caching strategies with \textbf{Redis} and optimized \textbf{SQL} queries on \textbf{PostgreSQL/MySQL}, reducing average response times by 25\%.}
  \resumeItem{Developed batch automation utilities using \textbf{Go}, improving processing efficiency for large datasets.}
  \resumeItem{Containerized services with \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling environment-based configuration and scaling.}
  \resumeItem{Implemented cloud integrations using \textbf{Azure} and \textbf{AWS} services for identity, storage, and messaging.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing code quality and security standards.}
  \resumeItem{\textit{Environment: C\#, ASP.NET Core, Angular, TypeScript, NgRx, Redis, PostgreSQL, MySQL, Go, Docker, Kubernetes, Jenkins, Azure DevOps, Azure, AWS.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, delivering reusable APIs and improving system stability.}
  \resumeItem{Built \textbf{REST} APIs and documented endpoints with \textbf{Swagger}, enhancing developer experience and integration consistency.}
  \resumeItem{Implemented frontend features using \textbf{Angular} and \textbf{TypeScript}, creating reusable UI components and improving user engagement.}
  \resumeItem{Built internal dashboards using \textbf{React} for administrative workflows, improving operational efficiency.}
  \resumeItem{Optimized database performance with indexing and query tuning using \textbf{Hibernate/JPA} on \textbf{Oracle}.}
  \resumeItem{Standardized build and release pipelines using \textbf{Jenkins} and containerized development environments with \textbf{Docker}.}
  \resumeItem{Supported cloud deployments on \textbf{AWS}, improving scalability and availability of services.}
  \resumeItem{Strengthened automated testing with \textbf{JUnit} and \textbf{Mockito}, reducing production defects by 15\%.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Angular, React, Docker, Jenkins, AWS, Oracle, Hibernate/JPA, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}