\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8+ years} of expertise architecting and developing scalable \textbf{Java} applications with \textbf{Spring Boot} and microservices for high-availability enterprise systems.}
  \resumeItem{Specialized in building event-driven architectures using \textbf{Kafka} to enable reliable asynchronous processing and seamless service integration.}
  \resumeItem{Experienced in frontend development with \textbf{ReactJS}, delivering modular and performant UI components for complex workflows.}
  \resumeItem{Implemented secure, API-first backend services with strong adherence to best practices in design, testing, and deployment in cloud environments.}
  \resumeItem{Proficient in containerization and orchestration technologies to support continuous delivery and scalable microservices infrastructure.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java, Spring Boot, Kafka, ReactJS, REST, Microservices \\
\textbf{Messaging \& Streaming:} & Kafka, AWS SQS, AWS SNS \\
\textbf{Frontend:} & ReactJS, TypeScript, Angular, RxJS \\
\textbf{Cloud \& Containerization:} & AWS (EKS, S3, RDS, DynamoDB), Docker, Kubernetes, Helm \\
\textbf{Databases \& Caching:} & PostgreSQL, MySQL, Redis \\
\textbf{CI/CD \& DevOps:} & Jenkins, GitHub Actions, Terraform, SonarQube, Snyk \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led development of microservices using \textbf{Java} and \textbf{Spring Boot}, improving system modularity and deployment efficiency by 30\%.}
  \resumeItem{Engineered asynchronous data pipelines with \textbf{Kafka}, enhancing message reliability and reducing processing delays by 25\%.}
  \resumeItem{Designed and maintained secure REST APIs with \textbf{Spring Security} and \textbf{OAuth2}, ensuring compliance with enterprise security standards.}
  \resumeItem{Developed interactive \textbf{ReactJS} dashboard modules, accelerating UI delivery and improving user experience for internal teams.}
  \resumeItem{Implemented containerized microservices using \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling scalable and repeatable releases.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{GitHub Actions}, reducing deployment times and improving code quality.}
  \resumeItem{Optimized database queries and caching strategies using \textbf{Redis}, reducing latency by 25\% on critical read paths.}
  \resumeItem{Applied observability best practices using \textbf{OpenTelemetry} and \textbf{CloudWatch} to monitor system health and alert on anomalies.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Kafka, ReactJS, REST, OAuth2, Docker, Kubernetes, Jenkins, GitHub Actions, Redis, OpenTelemetry, AWS.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed scalable microservices with \textbf{Java} and \textbf{Spring Boot}, improving API reliability and throughput by 20\%.}
  \resumeItem{Implemented event-driven workflows using \textbf{Kafka}, increasing system decoupling and fault tolerance.}
  \resumeItem{Built and maintained RESTful APIs adhering to OpenAPI standards, enhancing integration consistency across teams.}
  \resumeItem{Delivered frontend features using \textbf{ReactJS} and \textbf{TypeScript}, improving operational UI responsiveness and maintainability.}
  \resumeItem{Containerized applications with \textbf{Docker} and orchestrated deployments on \textbf{Kubernetes}, ensuring high availability.}
  \resumeItem{Provisioned infrastructure using \textbf{Terraform} and \textbf{CloudFormation}, enabling reproducible and auditable environments.}
  \resumeItem{Enhanced caching layers with \textbf{Redis}, reducing backend latency by 30\% for high-traffic services.}
  \resumeItem{Implemented automated testing and contract verification using \textbf{JUnit}, \textbf{Mockito}, and \textbf{Pact} to improve release stability.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Kafka, ReactJS, REST, Docker, Kubernetes, Terraform, OpenTelemetry, AWS, JUnit, Mockito, Pact.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend microservices using \textbf{Java} and \textbf{Spring Boot}, delivering scalable and reusable API modules.}
  \resumeItem{Implemented asynchronous processing with \textbf{Kafka}, improving message throughput and system resilience.}
  \resumeItem{Built secure REST APIs with \textbf{Spring Security} and \textbf{OAuth2}, enforcing enterprise-grade access controls.}
  \resumeItem{Delivered frontend components using \textbf{ReactJS} and \textbf{TypeScript}, enhancing modularity and user interaction.}
  \resumeItem{Optimized database performance using indexing and \textbf{Redis} caching, reducing response times by 25\%.}
  \resumeItem{Containerized services using \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling environment consistency and scalability.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Azure DevOps}, ensuring code quality and faster releases.}
  \resumeItem{Integrated cross-cloud platform services using AWS, Azure, and GCP for messaging, storage, and identity management.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Kafka, ReactJS, REST, OAuth2, Redis, Docker, Kubernetes, Jenkins, Azure DevOps, AWS, Azure, GCP.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, delivering clean APIs and reusable components.}
  \resumeItem{Built REST APIs following Swagger standards to improve documentation and integration consistency.}
  \resumeItem{Implemented frontend features with \textbf{ReactJS} and \textbf{Angular}, enhancing user interfaces and workflow efficiency.}
  \resumeItem{Enhanced database access performance using query optimization and indexing strategies.}
  \resumeItem{Containerized development environments with \textbf{Docker} to streamline testing and deployment processes.}
  \resumeItem{Supported cloud deployments on AWS, improving application availability and scalability.}
  \resumeItem{Strengthened automated testing using \textbf{JUnit} and \textbf{Mockito}, improving software quality and release confidence.}
  \resumeItem{\textit{Environment: Java, Spring Boot, REST, ReactJS, Angular, Docker, AWS, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}