\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small#2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Deliver over 8 years of full stack development expertise specializing in \textbf{C\# / .NET Core}, \textbf{Angular}, and cloud-native architecture on \textbf{AWS} platforms.}
  \resumeItem{Design and implement scalable microservices and REST APIs with strong system design principles, enhancing performance and reliability in enterprise environments.}
  \resumeItem{Integrate modern AI/ML solutions including \textbf{Generative AI} capabilities and vector search technologies to augment application intelligence and automation.}
  \resumeItem{Leverage containerization and orchestration using \textbf{Docker} and \textbf{Kubernetes} alongside CI/CD pipelines for streamlined delivery and operational excellence.}
  \resumeItem{Proficient in both SQL and NoSQL databases, enabling optimized data storage and retrieval strategies for complex distributed systems.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & \textbf{C\#}, \textbf{.NET Core / .NET 6+}, Angular, TypeScript, JavaScript, Java, Go \\
\textbf{Cloud \& DevOps:} & AWS (EKS, ECS/Fargate, Lambda, API Gateway, S3, RDS/Aurora, DynamoDB, IAM, KMS, Secrets Manager, CloudWatch, Bedrock), Docker, Kubernetes, CI/CD (Jenkins, GitHub Actions, Azure DevOps), Terraform, CloudFormation \\
\textbf{Databases:} & SQL (PostgreSQL, MySQL, Aurora), NoSQL (DynamoDB, MongoDB), Vector Databases (OpenSearch, Pinecone, FAISS) \\
\textbf{API \& Architecture:} & REST APIs, Microservices, gRPC, OpenAPI/Swagger, OAuth2/OIDC, JWT, mTLS, RAG architectures \\
\textbf{AI/ML \& Generative AI:} & AWS Bedrock, Spring AI, LangChain, Semantic Kernel, AutoGen, Embeddings, Vector Search, AI Copilots, Chatbots, Automation Solutions \\
\textbf{Frontend:} & Angular (5--17), RxJS, NgRx, Angular Material, React (Hooks), Redux Toolkit \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led design and development of microservices using \textbf{C\# / .NET 6} and \textbf{REST APIs}, improving system scalability and reducing latency by 30\%.}
  \resumeItem{Implemented frontend modules with \textbf{Angular} and \textbf{TypeScript}, enhancing user experience and maintainability of workflow-heavy applications.}
  \resumeItem{Integrated \textbf{Generative AI} features using \textbf{AWS Bedrock} and \textbf{RAG} techniques, enabling intelligent internal productivity tools with secure audit trails.}
  \resumeItem{Automated containerized deployments with \textbf{Docker} and \textbf{Kubernetes (EKS)}, reducing release times and increasing deployment reliability.}
  \resumeItem{Developed asynchronous messaging workflows using \textbf{Kafka} and \textbf{AWS SQS/SNS}, improving system resilience and throughput.}
  \resumeItem{Optimized database queries and caching strategies with \textbf{Redis} and \textbf{JPA/Hibernate}, reducing p95 latency by 25\%.}
  \resumeItem{Enforced CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, integrating quality gates with \textbf{SonarQube} and security scans via \textbf{Snyk}.}
  \resumeItem{Implemented observability with \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling proactive monitoring and alerting for critical services.}
  \resumeItem{\textit{Environment: \textbf{C\# / .NET 6}, \textbf{Angular}, \textbf{AWS Bedrock}, \textbf{Kafka}, \textbf{Docker}, \textbf{Kubernetes}, \textbf{Jenkins}, \textbf{GitHub Actions}, \textbf{Redis}, \textbf{OpenTelemetry}.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed scalable backend services using \textbf{Java} and \textbf{Spring Boot}, focusing on microservices and API-first design for distributed systems.}
  \resumeItem{Built and maintained \textbf{REST} and \textbf{gRPC} APIs, ensuring contract consistency and high availability across integrations.}
  \resumeItem{Designed and implemented event-driven architectures using \textbf{Kafka} to improve throughput and decouple service dependencies.}
  \resumeItem{Leveraged \textbf{AWS} cloud services including \textbf{EKS}, \textbf{Lambda}, and \textbf{DynamoDB} to deliver resilient, scalable platforms.}
  \resumeItem{Automated infrastructure provisioning using \textbf{Terraform} and \textbf{CloudFormation}, enabling repeatable and auditable deployments.}
  \resumeItem{Reduced backend latency by 20--30\% through caching with \textbf{Redis} and optimized database access patterns.}
  \resumeItem{Containerized applications using \textbf{Docker} and orchestrated with \textbf{Kubernetes}, improving deployment agility and environment parity.}
  \resumeItem{Implemented automated testing and contract testing using \textbf{JUnit}, \textbf{Mockito}, and \textbf{Pact}, reducing integration defects.}
  \resumeItem{\textit{Environment: \textbf{Java}, \textbf{Spring Boot}, \textbf{AWS (EKS, Lambda, DynamoDB)}, \textbf{Kafka}, \textbf{Docker}, \textbf{Kubernetes}, \textbf{Terraform}, \textbf{JUnit}, \textbf{Pact}.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Built and maintained backend services using \textbf{Java} and \textbf{Spring Boot}, delivering robust \textbf{REST APIs} with consistent validation and versioning.}
  \resumeItem{Developed \textbf{Angular} frontend modules with \textbf{TypeScript} and \textbf{NgRx}, improving user workflows and state management.}
  \resumeItem{Implemented \textbf{C\#} integration endpoints with \textbf{ASP.NET Core Web API} to enable partner orchestration and internal workflows.}
  \resumeItem{Enhanced asynchronous processing using \textbf{Kafka}, improving message reliability with retry and dead-letter queue patterns.}
  \resumeItem{Optimized database performance on \textbf{PostgreSQL/MySQL} through query tuning and indexing, improving throughput by 25\%.}
  \resumeItem{Containerized services with \textbf{Docker} and deployed on \textbf{Kubernetes}, standardizing environments and deployment processes.}
  \resumeItem{Integrated multi-cloud patterns across \textbf{AWS}, \textbf{Azure}, and \textbf{GCP} for identity, storage, and messaging solutions.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing quality gates with \textbf{SonarQube}.}
  \resumeItem{\textit{Environment: \textbf{Java}, \textbf{Spring Boot}, \textbf{C\# / .NET Core}, \textbf{Angular}, \textbf{Kafka}, \textbf{Docker}, \textbf{Kubernetes}, \textbf{AWS}, \textbf{Azure}, \textbf{Jenkins}.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, delivering reusable APIs aligned with enterprise standards.}
  \resumeItem{Built frontend features using \textbf{Angular} and \textbf{TypeScript}, creating reusable components and shared modules for internal tools.}
  \resumeItem{Implemented RESTful APIs with \textbf{Swagger} documentation to standardize endpoint contracts and improve developer experience.}
  \resumeItem{Optimized database queries and indexing using \textbf{Hibernate/JPA}, improving application responsiveness and throughput.}
  \resumeItem{Containerized development and testing environments with \textbf{Docker}, streamlining local and CI workflows.}
  \resumeItem{Supported AWS cloud deployments including \textbf{EC2}, \textbf{S3}, and \textbf{RDS}, ensuring availability and scalability.}
  \resumeItem{Enhanced automated testing coverage using \textbf{JUnit} and \textbf{Mockito}, improving release stability and reducing defects.}
  \resumeItem{Collaborated in Agile teams to deliver incremental feature enhancements and maintain high code quality.}
  \resumeItem{\textit{Environment: \textbf{Java}, \textbf{Spring Boot}, \textbf{Angular}, \textbf{Docker}, \textbf{AWS}, \textbf{JUnit}, \textbf{Mockito}.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}