To tailor the candidate's resume to the job description provided, here's how we can modify each section while preserving the LaTeX structure:

### Summary
In the summary section, focus on creating a concise and engaging introduction that highlights key skills and achievements relevant to the job description. Ensure it aligns with about 85% of the job description.

- **Draft Example:** Skilled software engineer with 3+ years of experience in developing robust applications. Expert in leveraging cutting-edge technologies to enhance product efficiency and achieve business goals.

### Professional Experience
Modify the bullet points based on the provided job description. Ensure they start with action verbs, include the task, and highlight quantifiable results. Keep each bullet point between 20-25 words. Use bold for technology stacks.

**Example:**
1. **Developed** robust applications in \textbf{Java} and \textbf{Python}, resulting in reducing processing time by 25%.
2. **Led** a team of 5 engineers in optimizing database queries, increasing data retrieval efficiency by 30%.

### Projects
Include three projects that align with the job description. Each project should have at most two bullet points and include at least one AI-related project.

- **AI-related Project Example:**
  - \textbf{AI Chatbot Development} | Created an AI-powered chatbot using \textbf{Python} and \textbf{TensorFlow}, improving customer response rate by 40%.
  - \textbf{Data Visualization Dashboard} | Developed interactive dashboards using \textbf{React} and \textbf{D3.js}, enabling data-driven decision making.

### Skills
Reorder and modify the skills section based on the job description. Use bold only for category titles, limiting to 6 categories.

- **Example Categories:**
  - \textbf{Programming Languages}: Python, Java, C++
  - \textbf{Web Technologies}: HTML, CSS, JavaScript
  - \textbf{AI/ML Tools}: TensorFlow, Keras
  - \textbf{Databases}: MySQL, MongoDB
  - \textbf{DevOps}: Docker, Jenkins
  - \textbf{Soft Skills}: Leadership, Collaboration

Finally, integrate these updates within the candidate's LaTeX resume template, ensuring no alteration to the structure, only the content changes as specified.