\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8+ years} of full stack development experience, specializing in \textbf{C\#/.NET} backend and \textbf{Angular} frontend for scalable enterprise applications.}
  \resumeItem{Designed and integrated AI-powered solutions including Generative AI and Retrieval Augmented Generation (RAG) workflows to automate complex business processes.}
  \resumeItem{Developed cloud-native applications leveraging \textbf{AWS} services such as Lambda, API Gateway, S3, DynamoDB, and ECS/EKS with strong emphasis on security and scalability.}
  \resumeItem{Built RESTful APIs and microservices architectures with secure authentication, enabling seamless integration of AI agents and intelligent assistants.}
  \resumeItem{Implemented CI/CD pipelines and DevOps best practices using Docker, Kubernetes, Jenkins, and GitHub Actions to streamline deployments and improve reliability.}
  \resumeItem{Experienced in vector databases and AI orchestration frameworks, enhancing enterprise data retrieval and AI service integration for improved decision-making.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & C\#, .NET Core / .NET 6+, Angular (5--17), TypeScript, JavaScript, Java, Go \\
\textbf{AI \& Cloud Services:} & AWS (Lambda, API Gateway, S3, DynamoDB, RDS, ECS/EKS, Bedrock, OpenAI), Generative AI, RAG, LLM integration, LangChain, Semantic Kernel, AutoGen, Pinecone, OpenSearch \\
\textbf{API \& Integration:} & REST, Microservices, OAuth2/OIDC, JWT, Secure Authentication, API Gateway \\
\textbf{Databases \& Caching:} & SQL (PostgreSQL, MySQL, Aurora), NoSQL (DynamoDB, MongoDB), Redis, Vector Databases (Pinecone, OpenSearch) \\
\textbf{DevOps \& Containerization:} & Docker, Kubernetes, Helm, CI/CD (Jenkins, GitHub Actions, Azure DevOps), Terraform, CloudFormation \\
\textbf{Observability \& Testing:} & OpenTelemetry, CloudWatch, Prometheus, Grafana, JUnit, Mockito, Testcontainers, SonarQube, Snyk \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led design and development of scalable backend services using \textbf{C\#} and \textbf{.NET 6+}, improving system modularity and API performance by 30\%.}
  \resumeItem{Integrated Generative AI solutions with \textbf{AWS Bedrock} and \textbf{Spring AI}, implementing RAG over enterprise data to enhance internal productivity workflows.}
  \resumeItem{Developed and maintained RESTful APIs and microservices architectures with secure authentication using \textbf{OAuth2/OIDC} and \textbf{JWT}, reducing security incidents.}
  \resumeItem{Built responsive frontend modules using \textbf{Angular} with \textbf{TypeScript} and \textbf{RxJS}, improving user experience and workflow efficiency.}
  \resumeItem{Implemented AI agents and autonomous workflows to automate business processes, increasing operational efficiency by 25\%.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes (EKS)} with Helm charts, enabling consistent and repeatable releases.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, enforcing quality and security gates with \textbf{SonarQube} and \textbf{Snyk}.}
  \resumeItem{Enhanced observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling proactive monitoring and faster incident resolution.}
  \resumeItem{\textit{Environment: C\#, .NET 6, Angular, TypeScript, AWS (EKS, Lambda, API Gateway, S3, DynamoDB, Bedrock), Docker, Kubernetes, Jenkins, GitHub Actions, OpenTelemetry, SonarQube, Snyk.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and implemented cloud-native microservices using \textbf{C\#/.NET Core} and \textbf{Java}, improving API scalability and reliability.}
  \resumeItem{Developed AI-driven automation tooling using \textbf{Go} and integrated LLM services with \textbf{AWS OpenAI} APIs to enhance operational workflows.}
  \resumeItem{Built RESTful APIs and event-driven services leveraging \textbf{AWS Lambda}, \textbf{API Gateway}, \textbf{SQS/SNS}, and \textbf{DynamoDB}, reducing latency by 20\%.}
  \resumeItem{Implemented frontend components using \textbf{Angular} and \textbf{React} with \textbf{TypeScript} for internal tools, improving user productivity.}
  \resumeItem{Provisioned infrastructure using \textbf{Terraform} and \textbf{CloudFormation}, ensuring secure and repeatable cloud deployments.}
  \resumeItem{Containerized microservices using \textbf{Docker} and deployed on \textbf{EKS/ECS}, enabling scalable and resilient application hosting.}
  \resumeItem{Enhanced observability with \textbf{OpenTelemetry} and \textbf{CloudWatch}, improving monitoring and alerting capabilities.}
  \resumeItem{Implemented contract testing with \textbf{Pact} and automated integration tests, reducing cross-service regressions by 30\%.}
  \resumeItem{\textit{Environment: C\#, .NET Core, Java, Go, Angular, React, AWS (Lambda, API Gateway, DynamoDB, SQS/SNS, OpenAI), Docker, Kubernetes, Terraform, CloudFormation, OpenTelemetry, Pact.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{C\#} with \textbf{ASP.NET Core Web API}, delivering secure and scalable APIs for partner integrations.}
  \resumeItem{Built AI-enabled automation workflows integrating Generative AI capabilities to streamline customer support and internal processes.}
  \resumeItem{Implemented frontend modules using \textbf{Angular} with \textbf{TypeScript} and \textbf{NgRx}, improving state management and user interaction.}
  \resumeItem{Optimized database queries and caching strategies using \textbf{PostgreSQL} and \textbf{Redis}, reducing response times by 25\%.}
  \resumeItem{Containerized services using \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling environment consistency and scalability.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Azure DevOps}, improving deployment frequency and reducing errors.}
  \resumeItem{Integrated cloud services across \textbf{AWS}, \textbf{Azure}, and \textbf{GCP} for identity, storage, and messaging, enhancing platform interoperability.}
  \resumeItem{Implemented secure authentication using \textbf{OAuth2/OIDC} and \textbf{JWT}, aligning with enterprise RBAC policies.}
  \resumeItem{\textit{Environment: C\#, ASP.NET Core, Angular, TypeScript, PostgreSQL, Redis, Docker, Kubernetes, Jenkins, Azure DevOps, AWS, Azure, GCP.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{C\#} and \textbf{.NET Core} to deliver reusable APIs and improve system reliability.}
  \resumeItem{Built frontend features with \textbf{Angular} and \textbf{TypeScript}, creating reusable components and enhancing user experience.}
  \resumeItem{Implemented scheduled workflows and automation using .NET background services, improving operational efficiency.}
  \resumeItem{Optimized database performance using \textbf{SQL} tuning and indexing strategies, reducing query latency by 15\%.}
  \resumeItem{Standardized builds and deployments using \textbf{Docker} and \textbf{Jenkins}, enabling consistent development environments.}
  \resumeItem{Supported cloud deployments using \textbf{AWS} services such as EC2, S3, and RDS, improving system availability and scalability.}
  \resumeItem{Enhanced test coverage using \textbf{JUnit} and \textbf{Mockito}, improving release stability and reducing bugs.}
  \resumeItem{Collaborated in Agile teams to deliver features and maintain high-quality code standards.}
  \resumeItem{\textit{Environment: C\#, .NET Core, Angular, TypeScript, SQL, Docker, Jenkins, AWS (EC2, S3, RDS), Agile.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}