\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Deliver over 8 years of expertise in designing and developing scalable enterprise applications using \textbf{Core Java} and \textbf{Spring Framework}, focusing on microservices and distributed systems.}
  \resumeItem{Specialize in event-driven architectures with hands-on experience in \textbf{Apache Kafka} including producers, consumers, and stream processing for high-throughput systems.}
  \resumeItem{Leverage \textbf{AWS cloud services} such as \textbf{Lambda}, \textbf{API Gateway}, \textbf{S3}, \textbf{EC2}, and \textbf{CloudWatch} to build resilient and scalable cloud-native applications.}
  \resumeItem{Design and document robust \textbf{RESTful APIs} using \textbf{OpenAPI/Swagger} standards, ensuring secure and maintainable integration layers.}
  \resumeItem{Apply strong knowledge of \textbf{SQL/NoSQL} databases and ORM frameworks like \textbf{Hibernate} to optimize data access and persistence.}
  \resumeItem{Implement CI/CD pipelines and version control workflows using \textbf{Git}, \textbf{Maven}, and \textbf{Gradle} to ensure automated and reliable deployments.}
  \resumeItem{Employ containerization and orchestration with \textbf{Docker} and \textbf{Kubernetes} to enable scalable service deployments and infrastructure automation.}
  \resumeItem{Integrate security best practices including \textbf{OAuth2}, \textbf{JWT}, and API key management for secure API development and access control.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Programming Languages \& Frameworks:} & Java (8/11/17), Spring Boot, Spring Cloud, Spring Data, Hibernate, Apache Kafka (producers, consumers, streams), C\#, Go, TypeScript \\
\textbf{Cloud \& Infrastructure:} & AWS Lambda, API Gateway, S3, EC2, CloudWatch, EKS, Terraform, CloudFormation, Docker, Kubernetes \\
\textbf{API Design \& Security:} & RESTful APIs, OpenAPI/Swagger, OAuth2, JWT, API Keys, Spring Security \\
\textbf{Databases \& Messaging:} & SQL (PostgreSQL, MySQL), NoSQL (DynamoDB, MongoDB), Kafka Connect, Redis \\
\textbf{CI/CD \& DevOps:} & Git, Maven, Gradle, Jenkins, GitHub Actions, Azure DevOps, SonarQube, Snyk \\
\textbf{Observability \& Testing:} & OpenTelemetry, CloudWatch, Prometheus, Grafana, JUnit, Mockito, Testcontainers, WireMock \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led design and development of microservices using \textbf{Java} and \textbf{Spring Boot}, improving modularity and reducing deployment risks.}
  \resumeItem{Developed and maintained \textbf{RESTful APIs} with \textbf{OpenAPI} specifications, ensuring consistent validation and error handling.}
  \resumeItem{Implemented secure authentication and authorization using \textbf{Spring Security}, \textbf{OAuth2}, and \textbf{JWT}, enhancing compliance and access control.}
  \resumeItem{Built event-driven workflows with \textbf{Apache Kafka} producers and consumers, increasing system reliability and scalability.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes (EKS)} clusters, enabling scalable cloud-native operations.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, improving release velocity and quality through automated testing and security scans.}
  \resumeItem{Optimized data access using \textbf{Hibernate} and implemented caching strategies with \textbf{Redis}, reducing latency by 25\%.}
  \resumeItem{Monitored production systems using \textbf{OpenTelemetry} and \textbf{CloudWatch}, setting up alerts to proactively address issues.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Spring Security, OAuth2, JWT, Kafka, AWS Lambda, API Gateway, S3, EC2, CloudWatch, Docker, Kubernetes, Helm, Terraform, Jenkins, GitHub Actions, Redis, Hibernate.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and implemented scalable microservices using \textbf{Java} and \textbf{Spring Boot}, improving API reliability and throughput.}
  \resumeItem{Built asynchronous event-driven pipelines leveraging \textbf{Apache Kafka} streams and \textbf{Kafka Connect} for seamless data integration.}
  \resumeItem{Developed \textbf{RESTful APIs} documented with \textbf{OpenAPI}, ensuring consistent interface contracts across teams.}
  \resumeItem{Automated infrastructure provisioning using \textbf{Terraform} and \textbf{CloudFormation}, enabling repeatable and auditable deployments.}
  \resumeItem{Implemented containerized services with \textbf{Docker} and orchestrated using \textbf{Kubernetes}, improving deployment scalability and resilience.}
  \resumeItem{Enhanced security posture by integrating \textbf{OAuth2} and \textbf{JWT} for API authentication and authorization.}
  \resumeItem{Improved system observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, reducing incident response times by 30\%.}
  \resumeItem{Built automated unit and integration tests using \textbf{JUnit} and \textbf{Mockito}, ensuring high code quality and reliability.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Kafka, AWS Lambda, API Gateway, DynamoDB, Aurora, S3, Terraform, CloudFormation, Docker, Kubernetes, OpenTelemetry, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend microservices using \textbf{Java} and \textbf{Spring Boot}, delivering scalable and maintainable APIs.}
  \resumeItem{Designed and documented \textbf{RESTful APIs} with \textbf{OpenAPI/Swagger}, ensuring consistent versioning and validation standards.}
  \resumeItem{Implemented secure API access using \textbf{Spring Security}, \textbf{OAuth2}, and \textbf{JWT}, aligning with enterprise security policies.}
  \resumeItem{Built asynchronous processing pipelines using \textbf{Apache Kafka}, improving message reliability and throughput.}
  \resumeItem{Optimized database interactions using \textbf{Hibernate/JPA} with \textbf{PostgreSQL/MySQL}, improving query performance by 25\%.}
  \resumeItem{Implemented caching strategies with \textbf{Redis} to reduce backend latency and improve response times.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling environment-based configuration management.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing quality gates and security scans.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Spring Security, OAuth2, JWT, Kafka, Hibernate, PostgreSQL, MySQL, Redis, Docker, Kubernetes, Jenkins, Azure DevOps.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, delivering reusable and well-layered components.}
  \resumeItem{Built and documented \textbf{RESTful APIs} using \textbf{Swagger}, improving API discoverability and client integration.}
  \resumeItem{Implemented database optimizations using \textbf{Hibernate/JPA} and indexing strategies to improve query efficiency.}
  \resumeItem{Containerized development and test environments using \textbf{Docker}, enhancing developer productivity and environment consistency.}
  \resumeItem{Supported cloud deployments on \textbf{AWS EC2}, \textbf{S3}, and \textbf{RDS}, enabling scalable infrastructure for applications.}
  \resumeItem{Standardized build and CI processes using \textbf{Maven}, \textbf{Gradle}, and \textbf{Jenkins}, improving release stability.}
  \resumeItem{Strengthened automated testing with \textbf{JUnit} and \textbf{Mockito}, reducing production defects.}
  \resumeItem{Implemented scheduled workflows using \textbf{Spring Scheduling} and \textbf{Quartz} for periodic task automation.}
  \resumeItem{\textit{Environment: Java, Spring Boot, REST, Swagger, Hibernate, AWS EC2, S3, RDS, Docker, Maven, Gradle, Jenkins, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}