\documentclass[a4paper]{article}
\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{margin=0.75in}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}

\titleformat{\section}{
  \large\bfseries
}{}{0em}{}[\titlerule]

\newcommand{\header}[1]{
  \large\textbf{#1}
}

\begin{document}

\begin{center}
  {\huge \textbf{Candidate Name}}\\
  City, State, ZIP Code \\
  Phone Number \textbullet{} Email Address \textbullet{} LinkedIn URL \textbullet{} GitHub URL
\end{center}

\section*{Summary}
\begin{itemize}[leftmargin=*,label={}]
\item Delivered expert software development and system design with strong focus on scalable, efficient \textbf{Java}, \textbf{Kotlin}, and \textbf{Python} applications in cloud environments.
\item Led complex software projects enhancing functionality and performance, achieving improved system reliability and user engagement by 20\%+.
\item Applied cutting-edge technologies including \textbf{TensorFlow}, \textbf{AI/ML} frameworks, and container orchestration to support innovative product development.
\item Collaborated with cross-functional teams to translate business needs into robust technical solutions, driving project success and continuous integration practices.
\end{itemize}

\section*{Professional Experience}

\textbf{Software Developer} \hfill City, State \\
Company ABC \hfill Jan 2020 -- Present
\begin{itemize}
\item Developed high-performance backend components using \textbf{Java Spring Boot} and \textbf{Kotlin} improving application response time by 30\%.
\item Implemented \textbf{RESTful APIs} and integrated third-party services, increasing data processing efficiency by 25\%.
\item Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker}, reducing deployment time by 40\% for multiple releases.
\item Enhanced application monitoring using \textbf{Prometheus} and \textbf{Grafana}, decreasing system downtime incidents by 15\%.
\end{itemize}

\textbf{Junior Software Engineer} \hfill City, State \\
Company XYZ \hfill Jun 2017 -- Dec 2019
\begin{itemize}
\item Designed and maintained scalable microservices in \textbf{Node.js} and \textbf{Express}, improving user request handling capacity by 35\%.
\item Developed automated test suites using \textbf{JUnit} and \textbf{Selenium} ensuring 98\% test coverage and higher code reliability.
\item Collaborated on cloud migration projects utilizing \textbf{AWS} services which led to 20\% reduction in infrastructure costs.
\item Streamlined database queries with \textbf{MySQL} optimizations, increasing data retrieval speed by 22\% in critical workflows.
\end{itemize}

\section*{Projects}

\textbf{AI-Powered Sentiment Analysis System |} 
\begin{itemize}
\item Built an AI-based sentiment classification engine with \textbf{Python} and \textbf{TensorFlow}, achieving 90\% accuracy on social media data.
\item Integrated real-time data pipelines to process 100K+ messages daily, enhancing analytics and decision-making speed by 25\%.
\end{itemize}

\textbf{Cloud-Based Inventory Management Platform |} 
\begin{itemize}
\item Developed scalable microservices architecture using \textbf{Kubernetes} and \textbf{Docker} to handle 50\% more concurrent users seamlessly.
\item Implemented automated deployment workflows reducing release time by 35\%, improving product delivery frequency and reliability.
\end{itemize}

\textbf{Smart Recommendation Engine |} 
\begin{itemize}
\item Engineered personalized recommendation algorithms with \textbf{Python} and \textbf{Scikit-learn}, increasing user engagement metrics by 18\%.
\item Applied data preprocessing and feature engineering to optimize model training time by 20\% while maintaining accuracy.
\end{itemize}

\section*{Technical Skills}

\textbf{Programming Languages:} Java, Kotlin, Python, JavaScript, SQL \\
\textbf{Frameworks \& Libraries:} Spring Boot, TensorFlow, Scikit-learn, Node.js, Express \\
\textbf{Cloud \& DevOps:} AWS, Jenkins, Docker, Kubernetes, Prometheus, Grafana \\
\textbf{Databases:} MySQL, MongoDB, PostgreSQL \\
\textbf{Testing:} JUnit, Selenium, Mockito \\
\textbf{Tools:} Git, Maven, Gradle, IntelliJ IDEA

\end{document}