\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Dynamic Full-Stack Developer with 5+ years of experience designing, developing, and deploying scalable web applications using Java, Python, Ruby, and Node.js.}
    \resumeItem{Proficient in building RESTful APIs with Spring Boot, Ruby on Rails, and Express.js, ensuring robust integration and 25\% performance improvements.}
    \resumeItem{Skilled in database design and optimization using PostgreSQL, MySQL, and MongoDB, resulting in 20\% faster query execution and data integrity.}
    \resumeItem{Experienced in automated testing using JUnit, Selenium, and Postman to maintain 95\% service reliability and stability in production environments.}
    \resumeItem{Adept at configuring CI/CD pipelines with Jenkins and GitHub Actions, improving deployment frequency by 50\% and reducing failures by 25\%.}
    \resumeItem{Communicates complex technical concepts clearly across global teams, with strong written skills and a bias for action to resolve issues swiftly.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java, Python, Ruby, JavaScript, TypeScript, SQL \\
                \textbf{Frameworks \& Backend:} & Spring Boot, Ruby on Rails, Node.js, Express.js, API Development \\
                \textbf{Frontend:} & React.js, Angular, Redux \\
                \textbf{Databases:} & PostgreSQL, MySQL, MongoDB, Oracle \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, API Gateway), Docker, Kubernetes, Jenkins, GitHub Actions \\
                \textbf{Testing \& Tools:} & JUnit, Selenium, Postman, Mockito \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Spring Boot} microservices on \textbf{AWS ECS} resulting in 25\% improvement in uptime and 30\% reduction in latency for client-facing applications.}
        \resumeItem{Developed responsive user interfaces with \textbf{React.js} boosting user engagement by 40\% and decreasing page load times by 25\% across e-commerce modules.}
        \resumeItem{Led migration from monolithic to microservices architecture using \textbf{Spring Cloud} and \textbf{Docker}, reducing deployment duration by 30\% for insurance applications.}
        \resumeItem{Implemented \textbf{GraphQL} APIs via \textbf{AWS API Gateway} achieving 35\% decrease in response times and lowering server load by 20\% during peak traffic.}
        \resumeItem{Established automated testing framework using \textbf{JUnit} and \textbf{Mockito}, increasing test coverage to 98\% and improving bug detection rate by 45\% pre-release.}
        \resumeItem{Optimized complex \textbf{PostgreSQL} queries outperforming prior benchmarks by 20\%, resulting in 15\% faster data retrieval for mission-critical high-load reporting systems.}
        \resumeItem{Orchestrated CI/CD pipelines with \textbf{Jenkins}, \textbf{Docker}, and \textbf{AWS CodePipeline}, increasing deployment frequency by 50\% and reducing rollback incidents by 30\%, improving overall release stability.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Delivered core banking microservices using \textbf{Java} and \textbf{Spring Boot}, improving transaction throughput by 30\% and reducing error rates by 15\% within account management systems.}
        \resumeItem{Designed responsive front end with \textbf{React.js} and \textbf{Redux} for loan application platform, increasing user satisfaction by 25\% and reducing load times by 35\%.}
        \resumeItem{Automated configuration processes using \textbf{Python} scripts, saving 20 hours per week and reducing manual errors by 40\% across deployment environments.}
        \resumeItem{Developed \textbf{Node.js} middleware for real-time transactions within event-driven architecture, improving cash position processing speed by 30\% and enhancing system reliability.}
        \resumeItem{Implemented \textbf{Kafka}-based event processing through asynchronous microservices design supporting 10,000 TPS, resulting in zero message loss and 99.9\% service availability during peak loads.}
        \resumeItem{Created \textbf{Grafana} dashboards with \textbf{Prometheus} metrics for core banking services, improving system observability and reducing incident response time by 35\%.}
        \resumeItem{Integrated \textbf{OAuth2} and \textbf{JWT} authentication leveraging Spring Security, reducing security breaches by 40\% and ensuring compliance with industry standards for user identity management.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed high-performance \textbf{Java} applications using Spring MVC for supply chain management, reducing data processing time by 25\% and improving throughput by 30\%.}
        \resumeItem{Built RESTful APIs with \textbf{Node.js} and \textbf{Express.js} for third-party services, increasing integration capabilities by 30\% and reducing response times by 25\%.}
        \resumeItem{Conducted automated testing with \textbf{JUnit} and \textbf{Postman} pre-deployment, improving code coverage to 95\% and reducing critical defects by 50\%.}
        \resumeItem{Migrated legacy systems to \textbf{AWS} Cloud leveraging Docker, cutting operational costs by 20\% and improving scalability by 40\% for enterprise applications.}
        \resumeItem{Optimized \textbf{DynamoDB} schemas through global secondary index design, reducing data latency by 15\% and enhancing retrieval performance for high-throughput operations.}
        \resumeItem{Developed Linux shell scripts for real-time monitoring across distributed services, reducing incident detection time by 30\% and automating system health checks.}
        \resumeItem{Streamlined CI/CD across microservices projects using \textbf{GitHub Actions}, increasing deployment speed by 40\% and minimizing manual release tasks by 50\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI Chatbot Assistant} $|$ Python, LangChain, OpenAI API, Redis, Docker}{}
        \resumeItemListStart
            \resumeItem{Designed an AI-powered chatbot using LangChain and OpenAI API, achieving 90\% accurate responses and reducing customer support load by 40\%.}
            \resumeItem{Deployed Dockerized service on AWS ECS via CI/CD pipelines, ensuring 99.5\% uptime and enabling auto-scaling to handle 200 concurrent user sessions seamlessly.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{E-commerce Platform} $|$ Ruby on Rails, React.js, PostgreSQL, AWS, Docker}{}
        \resumeItemListStart
            \resumeItem{Developed a full-stack e-commerce application using Ruby on Rails and React.js, improving checkout conversion rate by 30\% and reducing cart abandonment by 25\%.}
            \resumeItem{Integrated RESTful APIs with AWS Lambda and API Gateway, decreasing backend response times by 40\% and improving scalability during peak shopping events.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Internal Monitoring Dashboard} $|$ Node.js, Express.js, React.js, MongoDB, AWS ECS}{}
        \resumeItemListStart
            \resumeItem{Built a real-time operational dashboard using Node.js, Express.js, and React.js, achieving 50\% faster issue detection and streamlining incident management workflows.}
            \resumeItem{Implemented AWS CloudWatch and custom alerts, reducing mean time to resolution by 35\% and enhancing system reliability across microservices environments.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}