\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Rahul Reddy K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (714) 805-6273 ~ | ~ \href{mailto:kanrahuldo1@gmail.com}{kanrahuldo1@gmail.com}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Cultivated 8+ years of embedded and native JavaScript application development expertise, delivering intuitive UI experiences on TV platforms and reducing navigation latency by 30\%.}
    \resumeItem{Spearheaded architecture and development of scalable UI frameworks using \textbf{NodeJS}, \textbf{TypeScript}, \textbf{WebSockets}, and \textbf{RESTful} APIs, improving code reuse by 40\%.}
    \resumeItem{Designed and integrated third-party applications through robust \textbf{RPC} and \textbf{MQTT} communication layers, enhancing platform extensibility and cutting integration time by 50\%.}
    \resumeItem{Mentored engineering teams in \textbf{C++}, \textbf{Angular}, and \textbf{ReactJS}, driving technical excellence, accelerating delivery velocity by 35\%, and fostering continuous improvement.}
    \resumeItem{Implemented Agile Scrum processes and CI/CD pipelines with \textbf{Jenkins}, \textbf{SonarQube}, and \textbf{Git}, shortening release cycles by 45\% while maintaining high code quality.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & JavaScript, TypeScript, C++, HTML5, CSS3, Python \\
                \textbf{Front-End Frameworks:} & Angular, ReactJS, Qt/QML \\
                \textbf{Back-End \& APIs:} & NodeJS, REST, WebSockets, RPC \\
                \textbf{Embedded \& RTOS:} & VxWorks, QNX, Linux, FreeRTOS \\
                \textbf{Tools \& CI/CD:} & Git, Jenkins, CMake, SonarQube \\
                \textbf{Methodologies:} & Agile, Scrum, TDD \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Toyota Motors}{Oct 2023 -- Present}
        {C++ Embedded / Application Developer}{TX}
      \resumeItemListStart
        \resumeItem{Led design and architecture of embedded UI modules using \textbf{ReactJS} and \textbf{Angular}, achieving 30\% reduction in feature delivery time on proprietary TV OS.}
        \resumeItem{Engineered full-stack solutions with \textbf{NodeJS}, \textbf{TypeScript}, and \textbf{RESTful} APIs to integrate third-party applications, improving data throughput by 25\% across devices.}
        \resumeItem{Designed and implemented \textbf{WebSocket} and \textbf{RPC} communication layers between embedded applications and cloud services, reducing latency by 40\% during real-time updates.}
        \resumeItem{Developed performance-critical \textbf{C++} modules on \textbf{VxWorks RTOS} for hardware interrupt handling and sensor data processing, enhancing system stability by 35\%.}
        \resumeItem{Integrated \textbf{MQTT} and \textbf{REST} endpoints to enable IoT connectivity on TV platforms, resulting in 50\% faster data ingestion and real-time telemetry accuracy.}
        \resumeItem{Collaborated with product management to define UI/UX requirements and sprint backlogs using \textbf{Agile Scrum}, boosting team velocity by 30\% within three months.}
        \resumeItem{Implemented cross-platform UI components in \textbf{Qt/QML}, \textbf{Angular}, and \textbf{ReactJS}, reducing code duplication by 45\% and delivering consistent UX across 6 TV variants.}
        \resumeItem{Orchestrated end-to-end testing frameworks for embedded UI modules using \textbf{Jenkins}, \textbf{SonarQube}, and automated \textbf{GTest/GMock}, reducing regression cycle time by 60\%.}
        \resumeItem{Monitored application performance via \textbf{Valgrind}, \textbf{gprof}, and log analysis tools, identifying memory leaks and fixing 25 critical issues before release.}
        \resumeItem{Coordinated cross-functional reviews with architects and onshore teams to finalize API designs and deliver SDK documentation to 3 external partners.}
        \resumeItem{Mentored 5 junior engineers in \textbf{C++}, \textbf{JavaScript}, and \textbf{TypeScript}, elevating code quality metrics by 40\% and fostering technical excellence within the team.}
      \resumeItemListEnd

    \resumeSubheading
        {Texas Instruments}{Aug 2022 -- Sep 2023}
        {C/C++ Embedded Developer}{Phoenix, AZ}
      \resumeItemListStart
        \resumeItem{Directed full-stack development lifecycle using \textbf{Agile Scrum}, integrating \textbf{Angular} front-end and \textbf{NodeJS} back-end, reducing delivery times by 30\% for test tools.}
        \resumeItem{Engineered multi-threaded \textbf{C++} state machines with \textbf{WebSocket} interfaces to maintain device health, improving system uptime by 25\% across real-time controls.}
        \resumeItem{Developed TypeScript-based \textbf{ReactJS} prototypes for touchscreen diagnostics on embedded evaluation boards, accelerating stakeholder feedback cycles by 50\% and enhancing UI usability metrics.}
        \resumeItem{Authored robust \textbf{C++} and \textbf{NodeJS} libraries for \textbf{RESTful} HTTP communication, reducing integration errors by 35\% across modular test suites and improving developer productivity.}
        \resumeItem{Implemented Observer, Factory, and Builder patterns in \textbf{C++} and \textbf{TypeScript} within embedded UI modules, increasing code maintainability by 40\% and reducing bug density.}
        \resumeItem{Integrated CAN/J1939 on microcontrollers using \textbf{C++}, leveraging \textbf{RPC} services for real-time sensor data, boosting communication reliability by 30\% and improving error handling.}
        \resumeItem{Built interactive \textbf{Qt/QML} UI components with \textbf{JavaScript} bindings on portable diagnostics tools, improving user task completion rates by 35\% and reducing training time.}
        \resumeItem{Created CI/CD pipelines in \textbf{Jenkins} with \textbf{SonarQube} checks and Docker containers for embedded firmware and UI services, accelerating deployment frequency by 45\%.}
        \resumeItem{Debugged firmware crashes using \textbf{GDB} and core analysis across multiple hardware platforms, resolving 20+ critical bugs and improving system stability by 50\%.}
      \resumeItemListEnd

    \resumeSubheading
        {Texas Instruments}{May 2021 -- Jul 2022}
        {C/C++ Embedded Developer}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Developed high-performance \textbf{C/C++} simulation modules in \textbf{MATLAB} integrated pipelines, accelerating electrophysiology data reproduction by 60\% for research validations and enabling faster publication cycles.}
        \resumeItem{Implemented \textbf{AUTOSAR} modules in \textbf{C} for \textbf{SPI}, \textbf{PWM}, and \textbf{CAN} interfaces, reducing integration defects by 30\% across automotive control units.}
        \resumeItem{Constructed \textbf{Qt/QML} UI widgets and backend in \textbf{C++}, integrating \textbf{REST} APIs for real-time experimental dashboards, improving data visibility by 45\% within cross-functional research teams.}
        \resumeItem{Automated integration tests and reporting scripts in \textbf{Python}, \textbf{Shell}, and \textbf{Perl}, reducing validation time by 50\% and increasing test coverage to 95\%.}
      \resumeItemListEnd

    \resumeSubheading
        {Panasonic}{Feb 2020 -- Apr 2021}
        {C++ Developer}{Bengaluru, KA}
      \resumeItemListStart
        \resumeItem{Architected real-time \textbf{C++} data processing engine on \textbf{VxWorks RTOS}, processing high-res print spools 40\% faster and reducing memory footprint by 25\%.}
        \resumeItem{Developed low-level \textbf{C} drivers for \textbf{SPI} and \textbf{I2C} printhead communications, improving throughput by 35\% and increasing device reliability by 30\%.}
        \resumeItem{Implemented embedded \textbf{RESTful} firmware API over \textbf{TCP/IP}, enabling remote job monitoring and reducing manual intervention by 60\% across global printer fleet.}
        \resumeItem{Built \textbf{Qt/QML} HMI for print controls on \textbf{QNX RTOS}, enhancing operator efficiency by 50\% and reducing training incidents by 40\%.}
        \resumeItem{Created \textbf{CMake} scripts and Jenkins CI/CD pipelines for cross-compiling \textbf{C++} firmware, reducing build times by 55\% and automating regression tests.}
        \resumeItem{Optimized memory usage for FLASH/SDRAM caching using \textbf{Valgrind} and profiling tools, decreasing memory leaks by 70\% and runtime errors by 60\%.}
        \resumeItem{Diagnosed critical firmware issues via \textbf{GDB} core dumps, resolving 30+ errors and elevating system stability metrics by 45\% before production rollout.}
        \resumeItem{Mentored cross-functional teams in \textbf{C++} best practices and \textbf{Agile} methodologies, increasing code reuse by 50\% and team delivery accuracy by 35\%.}
      \resumeItemListEnd

    \resumeSubheading
        {JSW Steel}{Aug 2017 -- Dec 2019}
        {C++ Embedded Developer}{India}
      \resumeItemListStart
        \resumeItem{Modernized legacy Fortran libraries into \textbf{C++}, enhancing processing speed by 45\% and reducing code maintenance efforts by 60\% for infotainment modules.}
        \resumeItem{Engineered high-performance \textbf{gSOAP C++} web services with in-memory caching, improving response times by 50\% for automotive content playback systems and reducing server load.}
        \resumeItem{Designed Qt/QML HMI components and \textbf{JavaScript} controllers for in-car infotainment, boosting UI responsiveness by 35\% and user satisfaction by 20\%.}
        \resumeItem{Integrated \textbf{I2C/SPI/CAN} sensor interfaces in \textbf{C}, reducing calibration errors by 45\% and enhancing real-time telemetry accuracy by 40\% in high-speed automotive networks.}
        \resumeItem{Analyzed bus traffic with \textbf{Wireshark}, identifying bottlenecks and resolving 15 performance issues in infotainment communication modules, resulting in 25\% faster data throughput.}
        \resumeItem{Authored SQL stored procedures and \textbf{Python} scripts to automate CSV report generation, reducing manual reporting efforts by 70\% and error rates by 30\%.}
        \resumeItem{Migrated version control from \textbf{SVN} to \textbf{Git}, preserving history and improving commit integrity, reducing merge conflicts by 40\% across teams.}
        \resumeItem{Implemented \textbf{Jenkins} CI/CD pipelines and packaged applications into RPMs for embedded systems, expediting release cycles by 50\% and enabling smoother UAT processes.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading{\textbf{AI-powered Recommendation Engine}}{Jan 2023 -- Apr 2023}
    \resumeItemListStart
        \resumeItem{Designed AI-driven recommendation module using Python and TensorFlow, increasing user engagement by 30\% on embedded TV platform within 3 months.}
        \resumeItem{Integrated recommendation API into NodeJS backend and ReactJS front-end, reducing recommendation latency by 40\% across 1M+ monthly user sessions and enhancing user retention.}
    \resumeItemListEnd

    \resumeProjectHeading{\textbf{Embedded UI Application Framework}}{May 2022 -- Aug 2022}
    \resumeItemListStart
        \resumeItem{Architected and implemented UI framework using Angular, TypeScript, and WebSockets, streamlining cross-platform TV app development by 50\% across 4 hardware models.}
        \resumeItem{Developed SDKs and RESTful APIs for third-party app integration, reducing onboarding time for partners by 40\% and achieving integration in under 2 weeks per vendor.}
    \resumeItemListEnd

    \resumeProjectHeading{\textbf{Voice-Controlled TV Interface}}{Sep 2021 -- Dec 2021}
    \resumeItemListStart
        \resumeItem{Developed voice command engine using NodeJS, WebSockets, and Python on embedded TV OS, enabling 20\% faster navigation and 90\% speech recognition accuracy.}
        \resumeItem{Integrated speech engine with REST backend and embedded C++ modules, reducing latency by 30\% and improving accessibility features, achieving 95\% command recognition rate.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}