\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Rahul Reddy K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (714) 805-6273 ~ | ~ \href{mailto:kanrahuldo1@gmail.com}{kanrahuldo1@gmail.com}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Designed microservice architectures using Java and Spring Boot, processing 200K daily events and reducing data latency by 30\% while ensuring 99.9\% service uptime.}
    \resumeItem{Containerized applications with Docker and orchestrated Kubernetes deployments, improving deployment consistency by 70\% across environments and accelerating time-to-market by 40\%.}
    \resumeItem{Implemented CI/CD pipelines in Jenkins with Maven and Gradle, automating 85\% of build tests and reducing integration failures by 50\%.}
    \resumeItem{Integrated Kafka for high-throughput messaging and leveraged Redis caching, achieving 99.95\% message durability and reducing backend load by 35\% consistently.}
    \resumeItem{Architected resilient platforms on OpenShift, ensuring 99.9\% availability and implementing Drools rules for automated recovery, decreasing downtime by 45\% per release.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & Java, Python, C, C++, Shell Scripting \\
                \textbf{Frameworks \& Tools:} & Spring Boot, Drools, React, Envoy, gRPC, Spark, RPA \\
                \textbf{Containerization \& Orchestration:} & Docker, Kubernetes, OpenShift \\
                \textbf{Messaging \& Logging:} & Kafka, Elastic Stack, Redis, Consul \\
                \textbf{CI/CD \& Version Control:} & Jenkins, Maven, Gradle, Git \\
                \textbf{Databases:} & PostgreSQL, MongoDB \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Toyota Motors}{Oct 2023 -- Present}
        {C++ Embedded / Application Developer}{TX}
      \resumeItemListStart
        \resumeItem{Developed microservices using \textbf{Java} and \textbf{Spring Boot} to expose vehicle telemetry data through REST APIs, reducing data retrieval latency by 30\% in production.}
        \resumeItem{Containerized application components using \textbf{Docker} and built Helm charts for \textbf{Kubernetes}, improving deployment consistency and release frequency by 40\% across environments.}
        \resumeItem{Configured CI/CD pipelines in \textbf{Jenkins} with \textbf{Maven} and \textbf{Gradle}, automating 80\% of build and test processes and reducing integration failures by 50\%.}
        \resumeItem{Integrated \textbf{Kafka} streams to process sensor events in real time, achieving 99.9\% message delivery reliability and supporting 100K events per second.}
        \resumeItem{Leveraged \textbf{Redis} caching for frequent telemetry queries in Spring Boot services, reducing response time by 60\% and lowering backend load by 30\%.}
        \resumeItem{Designed high-availability platform architecture on \textbf{OpenShift}, ensuring 99.95\% uptime for critical automotive services and reducing mean time to recovery by 35\%.}
        \resumeItem{Implemented business rules with \textbf{Drools} engine to automate 120+ vehicle validation rules, decreasing manual quality checks by 80\% and accelerating releases.}
        \resumeItem{Developed RESTful services with \textbf{Spring Boot} supporting XML/JSON payloads, improving data interchange performance by 25\% and standardizing API contracts for compliance.}
        \resumeItem{Orchestrated \textbf{Docker} containers in CI/CD pipelines with Helm, reducing environment drift by 70\% and improving developer onboarding speed by 50\%.}
        \resumeItem{Integrated \textbf{Elastic Stack} for centralized logging and monitoring, enabling proactive issue detection and reducing mean time to detection by 45\%.}
        \resumeItem{Collaborated with cross-functional teams to analyze technical requirements and architect resilient scalable platforms, automating deployments and achieving 99.9\% availability across 5 services.}
      \resumeItemListEnd

    \resumeSubheading
        {Texas Instruments}{Aug 2022 -- Sep 2023}
        {C/C++ Embedded Developer}{Phoenix, AZ}
      \resumeItemListStart
        \resumeItem{Directed end-to-end SDLC for microservices using \textbf{Java}, \textbf{Spring Boot}, and \textbf{PostgreSQL}, reducing delivery cycle by 25\% and improving code quality with SonarQube.}
        \resumeItem{Built multi-threaded \textbf{Java} applications integrating \textbf{Kafka} streams, processing 200K messages daily and boosting data throughput by 35\% for device telemetry.}
        \resumeItem{Authored RESTful services in \textbf{Spring Boot} with \textbf{Docker} containers, achieving 99\% endpoint uptime and reducing deployment errors by 60\% across environments.}
        \resumeItem{Applied design patterns including Singleton and Factory to \textbf{Java} components, enhancing code modularity and reducing technical debt by 40\% across 3 modules.}
        \resumeItem{Implemented \textbf{Redis} caching for session data in Spring Boot services, reducing read latency by 55\% and cutting backend compute utilization by 30\%.}
        \resumeItem{Created \textbf{Jenkins} pipelines with \textbf{Maven} stages and \textbf{JUnit} test execution, integrating SonarQube analysis to efficiently reduce integration failures by 45\%.}
        \resumeItem{Debugged complex crashes using \textbf{GDB} and core-file analysis, resolving over 100 issues and improving system stability by 30\% within 6 months.}
        \resumeItem{Built QT/QML UI components on \textbf{QNX} RTOS, integrating RESTful clients for dashboard metrics and reducing UI latency by 40\% to enhance user experience.}
        \resumeItem{Performed peer code reviews and enforced \textbf{Git} workflows, improving code quality by 35\% and reducing merge conflicts by 50\% consistently.}
      \resumeItemListEnd

    \resumeSubheading
        {Texas Instruments}{May 2021 -- Jul 2022}
        {C/C++ Embedded Developer}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Developed scientific data pipelines in \textbf{Java} and \textbf{gRPC} to reproduce electrophysiology data, reducing data processing time by 50\% per experiment.}
        \resumeItem{Implemented AUTOSAR modules with microservices pattern using \textbf{Spring Boot}, enabling 30\% faster integration testing and improving software modularity and scalability.}
        \resumeItem{Built automation scripts in \textbf{Python} and Docker containers, orchestrating test environments on \textbf{Kubernetes} clusters to reduce setup time by 60\%.}
        \resumeItem{Developed RESTful backend services with \textbf{Spring Boot} integrating \textbf{PostgreSQL} and \textbf{Redis}, improving data reliability by 45\% and automating schema migrations.}
      \resumeItemListEnd

    \resumeSubheading
        {Panasonic}{Feb 2020 -- Apr 2021}
        {C++ Developer}{Bengaluru, KA}
      \resumeItemListStart
        \resumeItem{Designed real-time \textbf{C++} data engine, containerized with \textbf{Docker}, to spool print jobs, increasing throughput by 50\% and reducing latency by 40\%.}
        \resumeItem{Engineered device drivers in \textbf{C++} and \textbf{Java} bindings for printhead controllers over \textbf{SPI} and \textbf{I2C}, improving communication reliability by 30\%.}
        \resumeItem{Implemented embedded REST API using \textbf{Spring Boot} on RTOS to report real-time print metrics in \textbf{Docker} containers, improving remote diagnostics by 45\%.}
        \resumeItem{Significantly developed low-level \textbf{C} drivers for \textbf{USART} and memory-mapped I/O, optimizing FLASH and SDRAM usage, reducing memory footprint by 25\%.}
        \resumeItem{Built \textbf{Kafka} integration for print job streaming, processing 50K jobs daily through Java clients and achieving 99.9\% delivery success rate.}
        \resumeItem{Created CI pipelines with \textbf{Jenkins} and \textbf{Git}, orchestrating cross-compilation for ARM in \textbf{Docker} containers and reducing build time by 40\%.}
        \resumeItem{Resolved critical firmware bugs via \textbf{gdb} analysis and \textbf{Valgrind}, improving system stability by 35\% and preventing at least 100+ potential crashes.}
      \resumeItemListEnd

    \resumeSubheading
        {JSW Steel}{Aug 2017 -- Dec 2019}
        {C++ Embedded Developer}{India}
      \resumeItemListStart
        \resumeItem{Modernized legacy Fortran libraries by rewriting into Spring Boot microservices, improving performance by 60\% and decreasing maintenance overhead by 40\%.}
        \resumeItem{Developed high-performance gSOAP C++ web services with in-process caching, reducing response time by 45\% and supporting 150 concurrent clients with TLS security compliance.}
        \resumeItem{Implemented multi-threaded C++ modules handling XML/JSON messaging over TCP/IP, improving throughput by 50\% and reducing packet loss by 35\% in production.}
        \resumeItem{Developed Qt/QML HMI components for infotainment systems, integrating voice interactions in real-time and state machines, improving user responsiveness by 30\%.}
        \resumeItem{Built embedded C interfaces for I2C, SPI, and CAN sensor messaging, improving data consistency by 40\% and reducing retransmissions by 35\%.}
        \resumeItem{Investigated bus traffic using Wireshark and Elastic Stack, centralizing logs and reducing debugging time by 50\% across modules automatically per incident.}
        \resumeItem{Authored Oracle SQL queries and stored procedures, generating 100+ CSV reports daily and automating monitoring alerts across pipelines for operations.}
        \resumeItem{Integrated projects with \textbf{Jenkins} CI and migrated repositories from SVN to Git, preserving history and reducing release cycle by 20\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Smart Vehicle Telemetry Platform} | Java, Spring Boot, Kafka, Docker}{2023}
  \resumeItemListStart
    \resumeItem{Engineered microservice architecture with Java and Spring Boot, processing 100K telemetry events daily across regions with low latency and 99.9\% reliability.}
    \resumeItem{Containerized services in Docker, deployed on Kubernetes with Helm, reducing deployment time by 70\% and enabling horizontal scaling automatically and cost-effectively.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Intelligent Fault Prediction} | AI/ML, Kafka, Elastic Stack}{2022}
  \resumeItemListStart
    \resumeItem{Developed AI model using Python and TensorFlow to predict system faults, achieving 92\% accuracy and reducing unplanned downtime by 40\%.}
    \resumeItem{Streamed sensor data through Kafka topics into Elastic Stack, enabling real-time analytics and visualizing anomaly alerts with interactive Kibana dashboards.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Containerized CI/CD Framework} | Jenkins, Docker, Kubernetes}{2023}
  \resumeItemListStart
    \resumeItem{Designed CI/CD framework using Jenkins pipelines with Maven and Gradle, automating 90\% of build and test workflows and reducing failures by 55\%.}
    \resumeItem{Deployed build artifacts as Docker images and managed Kubernetes rollouts, achieving zero-downtime deployments and decreasing rollback incidents by 70\% consistently.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}