\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Deliver scalable, secure Generative AI applications and agentic AI workflows using \textbf{Java} and \textbf{Spring Boot} with expertise in RAG pipelines, LLM integration, and cloud-native architectures.}
  \resumeItem{Design and optimize AI systems for high-throughput enterprise workloads, incorporating prompt engineering, embeddings, vector search, and robust evaluation frameworks.}
  \resumeItem{Lead AI operations with CI/CD pipelines, model versioning, monitoring, and safety guardrails to ensure compliance with data privacy and governance standards.}
  \resumeItem{Collaborate cross-functionally to define AI solution architectures and mentor teams in scalable AI engineering best practices.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Programming \& Frameworks:} & Java (8/11/17/21), Spring Boot (1/2/3), Spring AI, Python, TypeScript, Go, C\# \\
\textbf{Generative AI \& ML:} & RAG pipelines, LLM integration, Prompt Engineering, Embeddings, Vector Search (OpenSearch), AI Copilots, Multimodal AI, Fine-tuning (LoRA, PEFT) \\
\textbf{Cloud Platforms:} & AWS (EKS, ECS/Fargate, Lambda, Bedrock, S3, RDS/Aurora, DynamoDB, IAM, KMS, Secrets Manager, CloudWatch, WAF), Azure (AKS, App Service, Azure AD, Key Vault, Azure Monitor), GCP (GKE, Cloud Storage, Pub/Sub, Cloud Logging) \\
\textbf{Containerization \& Orchestration:} & Docker, Kubernetes, Helm \\
\textbf{DevOps \& Observability:} & Jenkins, GitHub Actions, Azure DevOps, Terraform, CloudFormation, OpenTelemetry, Prometheus, Grafana, SonarQube, Snyk \\
\textbf{Databases \& Messaging:} & PostgreSQL, MySQL, Aurora, DynamoDB, MongoDB, Redis/ElastiCache, Kafka, AWS SQS/SNS, EventBridge, Kinesis, GCP Pub/Sub \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Designed and deployed production-grade Generative AI applications using \textbf{Java}, \textbf{Spring Boot 3}, and \textbf{Spring AI} integrated with \textbf{AWS Bedrock} for secure RAG workflows.}
  \resumeItem{Implemented agentic AI systems with tool calling, memory management, and verification loops, improving automation reliability and failure handling.}
  \resumeItem{Built scalable AI pipelines handling large enterprise workloads, optimizing latency and throughput with \textbf{Redis} caching and query tuning.}
  \resumeItem{Developed REST and gRPC APIs with OpenAPI standards, enforcing security via \textbf{Spring Security}, \textbf{OAuth2/OIDC}, \textbf{JWT}, and \textbf{mTLS}.}
  \resumeItem{Containerized microservices using \textbf{Docker} and deployed on \textbf{Kubernetes (EKS)} with \textbf{Helm} for consistent releases and scalability.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, integrating quality gates and security scans with \textbf{SonarQube} and \textbf{Snyk}.}
  \resumeItem{Implemented observability with \textbf{OpenTelemetry} and \textbf{CloudWatch}, establishing monitoring, alerting, and rollback strategies.}
  \resumeItem{Applied prompt engineering and embedding techniques to optimize retrieval accuracy and reduce hallucination rates in AI workflows.}
  \resumeItem{Developed asynchronous event-driven processing using \textbf{Kafka} and \textbf{AWS SQS/SNS}, improving throughput and fault tolerance.}
  \resumeItem{Enforced enterprise compliance with PII protection, audit logging, and content filtering aligned to governance frameworks.}
  \resumeItem{\textit{Environment: Java 17/21, Spring Boot 3, Spring Security, Spring AI, AWS Bedrock, REST, gRPC, Kafka, C\#, .NET 6, AWS (EKS, S3, RDS/Aurora, DynamoDB, SQS/SNS, IAM, KMS, Secrets Manager, CloudWatch, WAF), Docker, Kubernetes, Helm, Terraform, Angular 16/17, React, TypeScript, RxJS, NgRx, Redis, JUnit 5, Mockito, Testcontainers, Jenkins, GitHub Actions.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Architected and developed distributed AI services using \textbf{Java 17} and \textbf{Kotlin}, integrating LLMs and prompt frameworks for content intelligence tools.}
  \resumeItem{Built scalable RAG pipelines with optimized chunking and vector search using \textbf{OpenSearch}, enhancing retrieval efficiency by 30\%.}
  \resumeItem{Implemented multi-agent orchestration and planning workflows, improving automation accuracy and reducing manual interventions.}
  \resumeItem{Developed asynchronous event-driven systems with \textbf{Kafka}, increasing throughput and decoupling service dependencies.}
  \resumeItem{Designed and optimized data retrieval architectures using \textbf{DynamoDB} and \textbf{Aurora PostgreSQL} with indexing and caching strategies.}
  \resumeItem{Containerized services with \textbf{Docker} and deployed on \textbf{EKS/ECS}, ensuring secure rollouts and rollback capabilities.}
  \resumeItem{Provisioned infrastructure using \textbf{Terraform} and \textbf{CloudFormation} for scalable, auditable cloud environments.}
  \resumeItem{Implemented CI/CD pipelines with \textbf{GitHub Actions} and \textbf{Azure DevOps}, integrating automated testing and monitoring.}
  \resumeItem{Built evaluation frameworks measuring accuracy, relevancy, hallucination rates, and compliance using offline and A/B testing strategies.}
  \resumeItem{Applied fine-tuning techniques (LoRA, PEFT) to improve model performance on domain-specific tasks.}
  \resumeItem{\textit{Environment: Java 17, Kotlin, Go, REST, gRPC, Kafka, AWS (EKS/ECS, Lambda, API Gateway, DynamoDB, Aurora, S3, SQS/SNS, IAM, KMS, Secrets Manager, CloudWatch), Docker, Kubernetes, Terraform, CloudFormation, OpenTelemetry, Angular, React, TypeScript, JUnit 5, Mockito, Testcontainers, WireMock, Pact.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot 2}, integrating LLMs and embedding models for content intelligence and workflow automation.}
  \resumeItem{Built REST APIs with \textbf{OpenAPI/Swagger}, enforcing validation, versioning, and security with \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT}.}
  \resumeItem{Implemented RAG pipelines and vector search optimizations using \textbf{Redis} and \textbf{OpenSearch}, reducing query latency by 25\%.}
  \resumeItem{Delivered frontend modules using \textbf{Angular} and \textbf{React (Hooks)} with \textbf{TypeScript} for AI-assisted admin and dashboard workflows.}
  \resumeItem{Built asynchronous processing using \textbf{Kafka}, improving reliability with retry and dead-letter queue handling.}
  \resumeItem{Developed integration endpoints using \textbf{C\#} and \textbf{ASP.NET Core Web API} for multi-agent orchestration and automation workflows.}
  \resumeItem{Optimized database performance on \textbf{PostgreSQL/MySQL} with indexing and \textbf{Hibernate/JPA} tuning, improving throughput.}
  \resumeItem{Containerized services with \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling environment-based configurations.}
  \resumeItem{Implemented cloud integrations across \textbf{AWS}, \textbf{Azure}, and \textbf{GCP} for identity, storage, and messaging services.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing quality and security standards.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, Spring Security, REST, OpenAPI, Angular 8--12, React, TypeScript, RxJS, NgRx, Kafka, C\#, ASP.NET Core, Go, PostgreSQL/MySQL, Hibernate/JPA, Redis, Docker, Kubernetes, Jenkins, Azure DevOps, AWS/Azure/GCP.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8} and \textbf{Spring Boot 2}, building reusable components and scalable APIs for internal tooling.}
  \resumeItem{Built REST APIs with \textbf{Swagger} documentation and implemented secure access controls.}
  \resumeItem{Delivered UI features using \textbf{Angular} and \textbf{React 16} with \textbf{TypeScript} for admin dashboards and workflow modules.}
  \resumeItem{Implemented scheduled batch processing using \textbf{Quartz} and \textbf{Spring Scheduling} for automation workflows.}
  \resumeItem{Optimized database performance using \textbf{Hibernate/JPA} with query tuning and indexing strategies.}
  \resumeItem{Standardized builds and CI pipelines using \textbf{Maven/Gradle} and \textbf{Jenkins} for release stability.}
  \resumeItem{Containerized development and test environments using \textbf{Docker} to improve consistency.}
  \resumeItem{Supported cloud deployments on \textbf{AWS (EC2, S3, RDS)} with secure and scalable patterns.}
  \resumeItem{Enhanced automated testing coverage using \textbf{JUnit} and \textbf{Mockito} to reduce production defects.}
  \resumeItem{\textit{Environment: Java, Spring, JSF, JSP 2.0, AWS, Apache MyFaces, JMS, Hibernate, LDAP, JNDI, UDDI, WSDL, SOA, SOAP, UML, XML, HTML, Log4j, WebSphere 7.0, RAD 8.0, Oracle, SunOS UNIX, Shell Script, CVS, Ant, Windows XP.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}