\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8+ years} of full stack development expertise specializing in \textbf{Java}, \textbf{Spring Boot}, and \textbf{React.js} for scalable web applications.}
  \resumeItem{Designed and implemented RESTful services and user-facing features, converting wireframes and designs into performant, reusable front-end components.}
  \resumeItem{Applied strong knowledge of \textbf{HTML5}, \textbf{React}, \textbf{Node.js}, and \textbf{MongoDB} to build modular, maintainable codebases aligned with best practices.}
  \resumeItem{Collaborated effectively with technical leads and cross-functional teams to drive autonomous delivery of production-ready code with high test coverage.}
  \resumeItem{Optimized application performance and scalability through proactive debugging, code reviews, and adherence to design patterns and coding standards.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java (8/11/17/21), Spring Boot (1/2/3), React.js, Node.js, JavaScript, TypeScript, HTML5, CSS3/SCSS \\
\textbf{Frontend Technologies:} & React (Hooks), Angular (5--17), Redux Toolkit, RxJS, NgRx, Angular Material, UI binding patterns \\
\textbf{Backend \& APIs:} & RESTful services, Spring MVC, Spring Security, OAuth2/OIDC, JWT, Hibernate/JPA, MongoDB, PostgreSQL, MySQL \\
\textbf{Databases \& Caching:} & MongoDB, PostgreSQL, MySQL, Redis/ElastiCache \\
\textbf{Cloud \& DevOps:} & AWS (EKS, ECS/Fargate, Lambda, API Gateway, S3, RDS/Aurora, DynamoDB, IAM, KMS, Secrets Manager, CloudWatch), Docker, Kubernetes, Jenkins, GitHub Actions, Terraform \\
\textbf{Testing \& Observability:} & JUnit 5, Mockito, Testcontainers, Cypress, OpenTelemetry, Prometheus, Grafana \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Collaborated with technical leads to design and document sub-modules, delivering production-ready \textbf{Java} and \textbf{Spring Boot 3} backend components.}
  \resumeItem{Developed RESTful APIs and integrated \textbf{React.js} front-end features, converting wireframes into reusable UI components with optimized performance.}
  \resumeItem{Implemented authentication and authorization using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT}, ensuring secure service workflows.}
  \resumeItem{Built new user-facing features with \textbf{React (Hooks)} and \textbf{TypeScript}, improving modularity and maintainability of UI libraries.}
  \resumeItem{Created and maintained RESTful services using \textbf{Node.js} for internal integrations, enhancing service scalability and reliability.}
  \resumeItem{Produced unit and integration tests using \textbf{JUnit 5} and \textbf{Mockito}, increasing code quality and reducing defects by 30\%.}
  \resumeItem{Optimized application speed and scalability by tuning \textbf{MongoDB} queries and implementing \textbf{Redis} caching for high-read paths.}
  \resumeItem{Worked autonomously to debug and troubleshoot issues across front-end and backend layers, reducing incident resolution time by 25\%.}
  \resumeItem{Containerized microservices with \textbf{Docker} and deployed on \textbf{Kubernetes (EKS)} using \textbf{Helm} charts for repeatable releases.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, enforcing quality gates and security scans with \textbf{SonarQube} and \textbf{Snyk}.}
  \resumeItem{Implemented observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling proactive monitoring and alerting.}
  \resumeItem{\textit{Environment: Java 17/21, Spring Boot 3, Spring Security, React.js, Node.js, MongoDB, Redis, Docker, Kubernetes, Jenkins, GitHub Actions, OpenTelemetry, AWS (EKS, S3, RDS), JUnit 5, Mockito.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and implemented backend services using \textbf{Java 17} and \textbf{Spring Boot}, delivering scalable APIs aligned with enterprise standards.}
  \resumeItem{Developed RESTful endpoints and \textbf{Node.js} microservices, improving integration and data flow between distributed systems.}
  \resumeItem{Built front-end modules using \textbf{React.js} and \textbf{TypeScript}, converting wireframes into functional, reusable components.}
  \resumeItem{Created RESTful services with \textbf{Node.js} to support internal workflows, enhancing service responsiveness and maintainability.}
  \resumeItem{Implemented unit and integration tests with \textbf{JUnit 5} and \textbf{Mockito}, increasing test coverage and reducing bugs in production.}
  \resumeItem{Optimized database access patterns for \textbf{MongoDB} and \textbf{PostgreSQL}, improving query performance by 20\%.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{EKS/ECS}, enabling seamless cloud-native delivery.}
  \resumeItem{Provisioned infrastructure using \textbf{Terraform} and \textbf{CloudFormation}, ensuring consistent and auditable environments.}
  \resumeItem{Implemented observability using \textbf{OpenTelemetry} and monitored production with \textbf{CloudWatch} dashboards.}
  \resumeItem{Delivered front-end features using \textbf{Angular} and \textbf{React} with \textbf{TypeScript} for operational UI modules.}
  \resumeItem{\textit{Environment: Java 17, Spring Boot, Node.js, React.js, Angular, MongoDB, PostgreSQL, Docker, Kubernetes (EKS), Terraform, OpenTelemetry, JUnit 5, Mockito.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot 2}, implementing REST APIs with consistent validation and error handling.}
  \resumeItem{Built user-facing features with \textbf{React (Hooks)} and \textbf{TypeScript}, converting PSD designs into modular, reusable components.}
  \resumeItem{Implemented asynchronous processing and event-driven patterns using \textbf{Kafka}, improving system reliability and throughput.}
  \resumeItem{Created RESTful services using \textbf{Node.js} for integration endpoints, enhancing partner orchestration workflows.}
  \resumeItem{Improved database performance on \textbf{MongoDB} and \textbf{PostgreSQL} through query optimization and indexing strategies.}
  \resumeItem{Enhanced front-end state management using \textbf{NgRx} and \textbf{RxJS} for workflow-heavy Angular modules.}
  \resumeItem{Containerized services with \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling environment-based configuration and scaling.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing quality gates with \textbf{SonarQube}.}
  \resumeItem{Collaborated with teams to debug and resolve front-end and backend issues, improving release stability and user experience.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, React.js, Node.js, Angular, MongoDB, PostgreSQL, Kafka, Docker, Kubernetes, Jenkins, Azure DevOps.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8} and \textbf{Spring Boot 2}, delivering reusable components and clean API layers.}
  \resumeItem{Built front-end features using \textbf{Angular} and \textbf{React 16}, converting wireframes into functional UI components for internal dashboards.}
  \resumeItem{Implemented RESTful APIs documented with \textbf{Swagger}, improving service discoverability and integration.}
  \resumeItem{Optimized database queries and indexing using \textbf{Hibernate/JPA} for improved performance on \textbf{PostgreSQL}.}
  \resumeItem{Containerized development and test environments with \textbf{Docker}, enabling consistent builds and deployments.}
  \resumeItem{Supported cloud deployments on \textbf{AWS} with \textbf{EC2}, \textbf{S3}, and \textbf{RDS}, improving scalability and availability.}
  \resumeItem{Improved automated testing coverage using \textbf{JUnit} and \textbf{Mockito}, reducing post-release defects.}
  \resumeItem{Collaborated in Agile teams to deliver enhancements aligning with project timelines and quality standards.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Angular, React, Hibernate/JPA, PostgreSQL, AWS, Docker, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}