\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Leverage over \textbf{8+ years} of software engineering experience with a focus on backend development and advanced AI agent orchestration using \textbf{Python} and \textbf{LangGraph}.}
  \resumeItem{Specialize in designing scalable, stateful multi-agent workflows powered by \textbf{LLMs}, integrating prompt engineering and agentic system design for intelligent automation.}
  \resumeItem{Demonstrated expertise in \textbf{Generative AI fundamentals}, \textbf{LangChain}, and \textbf{LangGraph} orchestration with strong asynchronous programming skills in \textbf{Python}.}
  \resumeItem{Experienced in integrating with \textbf{OpenAI} and \textbf{Anthropic} platforms, implementing monitoring, debugging, and visualization for AI workflows within CI/CD pipelines.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Programming Languages:} & Python, Java (8/11/17/21), Kotlin, Go, C\# \\
\textbf{AI \& Agent Frameworks:} & LangGraph, LangChain, Spring AI, OpenAI API, Anthropic API, Prompt Engineering, Agentic Workflow Orchestration \\
\textbf{Backend Frameworks:} & Spring Boot (1/2/3), ASP.NET Core Web API (.NET 6+), Hibernate/JPA \\
\textbf{Cloud \& DevOps:} & AWS (EKS, ECS/Fargate, Lambda, Bedrock, S3, RDS/Aurora, DynamoDB, IAM, KMS, Secrets Manager, CloudWatch), Azure (AKS, App Service, Azure AD), GCP (GKE, Pub/Sub, Cloud Monitoring) \\
\textbf{Containerization \& Orchestration:} & Docker, Kubernetes, Helm \\
\textbf{CI/CD \& Observability:} & Jenkins, GitHub Actions, Azure DevOps, SonarQube, OpenTelemetry, Prometheus, Grafana \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Designed and implemented stateful multi-agent workflows using \textbf{Python} and \textbf{LangGraph}, enhancing automation and decision-making capabilities.}
  \resumeItem{Developed scalable backend services with \textbf{Java} and \textbf{Spring Boot 3}, improving modularity and reducing release risk through clean service boundaries.}
  \resumeItem{Integrated \textbf{OpenAI} and \textbf{Anthropic} APIs for generative AI capabilities, enabling advanced prompt engineering and agent orchestration.}
  \resumeItem{Built asynchronous processing pipelines using \textbf{Kafka} and \textbf{AWS SQS/SNS}, increasing system reliability with retry and dead-letter queue handling.}
  \resumeItem{Implemented secure authentication and authorization using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, \textbf{JWT}, and \textbf{mTLS} for enterprise-grade workflows.}
  \resumeItem{Developed AI workflow monitoring and debugging tools with graph visualization, improving observability and incident response times.}
  \resumeItem{Containerized microservices using \textbf{Docker} and deployed on \textbf{Kubernetes (EKS)} with \textbf{Helm} for repeatable and scalable releases.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, enforcing quality and security gates with \textbf{SonarQube} and \textbf{Snyk}.}
  \resumeItem{Enhanced API performance by \textbf{30--40\%} through \textbf{JPA/Hibernate} tuning and optimized caching strategies with \textbf{Redis}.}
  \resumeItem{\textit{Environment: Python, LangGraph, LangChain, Java 17/21, Spring Boot 3, Spring Security, OpenAI, Anthropic, Kafka, AWS Bedrock, REST, gRPC, C\#, .NET 6, Docker, Kubernetes, Helm, Jenkins, GitHub Actions, SonarQube, Redis, OpenTelemetry, CloudWatch.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Implemented distributed services using \textbf{Java 17} and \textbf{Kotlin}, focusing on scalable APIs and robust backend architecture.}
  \resumeItem{Developed asynchronous, event-driven workflows with \textbf{Kafka}, improving throughput and decoupling service dependencies.}
  \resumeItem{Built automation tools and performance-sensitive utilities using \textbf{Go}, reducing operational manual effort.}
  \resumeItem{Designed and optimized data access patterns for \textbf{DynamoDB} and \textbf{Aurora PostgreSQL}, improving query efficiency and latency.}
  \resumeItem{Integrated \textbf{OpenAI} APIs for internal AI-driven automation, applying prompt engineering and agent orchestration concepts.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{EKS/ECS}, following blue/green deployment strategies.}
  \resumeItem{Provisioned infrastructure using \textbf{Terraform} and \textbf{CloudFormation} for repeatable and auditable environments.}
  \resumeItem{Enhanced observability with \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling proactive monitoring and alerting.}
  \resumeItem{Delivered frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript} for configuration and operational workflows.}
  \resumeItem{\textit{Environment: Java 17, Kotlin, Go, OpenAI, Kafka, AWS (EKS/ECS, Lambda, DynamoDB, Aurora, S3, SQS/SNS, IAM, KMS, Secrets Manager, CloudWatch), Docker, Kubernetes, Terraform, CloudFormation, OpenTelemetry, Angular, React, TypeScript.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot 2}, delivering scalable APIs with clean architecture.}
  \resumeItem{Built secure REST APIs with \textbf{OpenAPI/Swagger}, enforcing validation, versioning, and error handling standards.}
  \resumeItem{Implemented authentication and authorization using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT} for enterprise RBAC compliance.}
  \resumeItem{Developed asynchronous processing pipelines with \textbf{Kafka}, improving reliability through retry and dead-letter queue mechanisms.}
  \resumeItem{Created integration endpoints using \textbf{C\#} and \textbf{ASP.NET Core Web API} to enable partner orchestration workflows.}
  \resumeItem{Improved database performance using \textbf{Hibernate/JPA} tuning and indexing on \textbf{PostgreSQL/MySQL}, reducing latency by 25\%.}
  \resumeItem{Built frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, applying \textbf{NgRx} for predictable state management.}
  \resumeItem{Containerized services using \textbf{Docker} and deployed on \textbf{Kubernetes} with environment-based configurations.}
  \resumeItem{Implemented CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing quality gates with \textbf{SonarQube}.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, Spring Security, REST, OpenAPI, Kafka, C\#, ASP.NET Core, Angular, React, TypeScript, NgRx, PostgreSQL/MySQL, Hibernate/JPA, Redis, Docker, Kubernetes, Jenkins, Azure DevOps.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Delivered backend services using \textbf{Java 8} and \textbf{Spring Boot 2}, focusing on reusable components and clean layering.}
  \resumeItem{Built RESTful APIs and documented endpoints using \textbf{Swagger}, improving API usability and standards compliance.}
  \resumeItem{Developed frontend features using \textbf{Angular} with \textbf{TypeScript} and reusable component libraries.}
  \resumeItem{Implemented internal dashboard modules using \textbf{React 16} with component-based architecture for admin workflows.}
  \resumeItem{Implemented scheduled workflows using \textbf{Quartz} and \textbf{Spring Scheduling}, automating periodic backend tasks.}
  \resumeItem{Optimized database performance with \textbf{Hibernate/JPA} tuning and indexing strategies.}
  \resumeItem{Standardized build processes using \textbf{Maven/Gradle} and CI pipelines with \textbf{Jenkins}.}
  \resumeItem{Containerized development and test environments using \textbf{Docker} for consistent deployments.}
  \resumeItem{Supported cloud deployments on \textbf{AWS EC2}, improving scalability and resilience.}
  \resumeItem{\textit{Environment: Java, Spring Boot 2, REST, Swagger, Angular, React 16, Quartz, Hibernate/JPA, Docker, Jenkins, AWS EC2.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}