\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Over \textbf{8+ years} of experience architecting and delivering scalable enterprise-grade telecom and web applications using \textbf{Java}, \textbf{Spring Boot}, and \textbf{React}.}
  \resumeItem{Expertise in designing resilient systems with \textbf{Java Reactive (Spring WebFlux)}, \textbf{Python}, and \textbf{MongoDB} to support complex telecom domains like \textbf{5G}, \textbf{Core Engineering}, and \textbf{Edge Networks}.}
  \resumeItem{Proven ability to translate telecom business requirements into robust architectures and enforce technical best practices across multiple projects.}
  \resumeItem{Strong leadership in agile environments, driving cross-team collaboration and ensuring technical quality and consistency in fast-paced settings.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java (8/11/17/21), Python, Spring Boot (1/2/3), Spring WebFlux, React (Hooks), Angular, TypeScript \\
\textbf{Databases \& Storage:} & MongoDB, Oracle, PostgreSQL, MySQL, Redis \\
\textbf{Cloud \& DevOps:} & AWS (EKS, S3, RDS, DynamoDB, SQS/SNS, IAM), Docker, Kubernetes, Terraform, Jenkins, GitHub Actions \\
\textbf{API \& Integration:} & REST, gRPC, OpenAPI/Swagger, OAuth2/OIDC, JWT, mTLS \\
\textbf{Messaging \& Streaming:} & Kafka, AWS SQS, AWS SNS \\
\textbf{Testing \& Observability:} & JUnit 5, Mockito, Testcontainers, OpenTelemetry, Prometheus, Grafana \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Architected and developed scalable backend services using \textbf{Java 17/21}, \textbf{Spring Boot 3}, and \textbf{Spring WebFlux}, improving system resilience by 30\%.}
  \resumeItem{Led design and implementation of telecom inventory APIs with \textbf{REST} and \textbf{OpenAPI}, ensuring compliance with enterprise architectural standards.}
  \resumeItem{Integrated \textbf{Python} scripts for data processing workflows, enhancing automation and reducing manual effort by 25\%.}
  \resumeItem{Developed frontend modules using \textbf{React (Hooks)} and \textbf{TypeScript}, accelerating UI delivery for telecom inventory management.}
  \resumeItem{Implemented secure authentication using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT}, aligning with enterprise security policies.}
  \resumeItem{Managed asynchronous messaging with \textbf{Kafka} and \textbf{AWS SQS/SNS}, improving event-driven processing reliability.}
  \resumeItem{Containerized microservices with \textbf{Docker} and deployed on \textbf{Kubernetes (EKS)} using \textbf{Helm}, ensuring scalable releases.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, enforcing quality gates with \textbf{SonarQube} and security scans.}
  \resumeItem{Enhanced observability through \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling proactive monitoring and alerting.}
  \resumeItem{\textit{Environment: Java 17/21, Spring Boot 3, Spring WebFlux, Spring Security, Python, React, Kafka, AWS (EKS, S3, RDS, SQS/SNS), Docker, Kubernetes, Jenkins, GitHub Actions.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and delivered enterprise-grade telecom solutions using \textbf{Java 17}, \textbf{Spring Boot}, and \textbf{MongoDB}, improving data scalability by 40\%.}
  \resumeItem{Implemented reactive APIs with \textbf{Spring WebFlux} to support high-throughput telecom inventory services.}
  \resumeItem{Developed frontend components using \textbf{React} and \textbf{TypeScript}, enhancing user experience for telecom network management tools.}
  \resumeItem{Automated backend workflows using \textbf{Python}, reducing operational overhead by 30\%.}
  \resumeItem{Built asynchronous event-driven systems using \textbf{Kafka}, improving message throughput and fault tolerance.}
  \resumeItem{Provisioned and managed cloud infrastructure with \textbf{Terraform} and \textbf{CloudFormation} on \textbf{AWS}, ensuring reliable deployments.}
  \resumeItem{Implemented secure API gateways with \textbf{OAuth2/OIDC} and \textbf{JWT}, safeguarding telecom data access.}
  \resumeItem{Containerized services with \textbf{Docker} and orchestrated deployments on \textbf{Kubernetes (EKS)}, enabling scalable microservices architecture.}
  \resumeItem{Enhanced monitoring using \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling rapid incident response.}
  \resumeItem{\textit{Environment: Java 17, Spring Boot, Spring WebFlux, Python, MongoDB, React, Kafka, AWS (EKS, S3, DynamoDB, SQS/SNS), Docker, Kubernetes, Terraform, CloudFormation.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend microservices using \textbf{Java 8/11} and \textbf{Spring Boot 2}, delivering scalable APIs for financial applications.}
  \resumeItem{Built reactive APIs with \textbf{Spring WebFlux} to improve system responsiveness and throughput by 25\%.}
  \resumeItem{Integrated \textbf{MongoDB} for flexible data storage, enhancing data retrieval performance for inventory systems.}
  \resumeItem{Implemented frontend features with \textbf{React} and \textbf{TypeScript}, improving user workflows and UI modularity.}
  \resumeItem{Automated asynchronous processing using \textbf{Kafka}, improving message reliability and system resilience.}
  \resumeItem{Implemented secure authentication mechanisms using \textbf{Spring Security}, \textbf{OAuth2}, and \textbf{JWT} for enterprise compliance.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling consistent environment management.}
  \resumeItem{Improved database query performance using indexing and \textbf{Hibernate/JPA} tuning on \textbf{PostgreSQL/MySQL}.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing quality and security standards.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2, Spring WebFlux, MongoDB, React, Kafka, PostgreSQL/MySQL, Docker, Kubernetes, Jenkins, Azure DevOps.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8} and \textbf{Spring Boot 2}, delivering reusable components for web applications.}
  \resumeItem{Built RESTful APIs documented with \textbf{Swagger}, supporting internal tooling and dashboards.}
  \resumeItem{Delivered UI features using \textbf{React 16} and \textbf{TypeScript}, enabling modular and maintainable admin workflows.}
  \resumeItem{Implemented scheduled batch processing using \textbf{Spring Scheduling} and \textbf{Quartz} to automate telecom-related workflows.}
  \resumeItem{Optimized database performance using \textbf{Hibernate/JPA} and indexing strategies on \textbf{Oracle} databases.}
  \resumeItem{Standardized builds and CI pipelines using \textbf{Maven}, \textbf{Gradle}, and \textbf{Jenkins} for consistent releases.}
  \resumeItem{Containerized development and test environments using \textbf{Docker} to improve developer productivity.}
  \resumeItem{Supported cloud deployments on \textbf{AWS (EC2, S3, RDS)}, enabling scalable infrastructure for applications.}
  \resumeItem{Strengthened automated testing using \textbf{JUnit} and \textbf{Mockito} to improve code quality and stability.}
  \resumeItem{\textit{Environment: Java 8, Spring Boot 2, React 16, Oracle, Docker, AWS (EC2, S3, RDS), Hibernate/JPA, Jenkins.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}