\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Leverage over \textbf{8+ years} of software engineering expertise with strong proficiency in \textbf{Python} and AI-assisted development tools to enhance workflows and customer solutions.}
  \resumeItem{Drive integration and evaluation of AI technologies, including hands-on experience with \textbf{LLMs}, \textbf{AI/ML} frameworks, and automation to improve engineering efficiency.}
  \resumeItem{Skilled in supporting and maintaining both \textbf{Linux} and \textbf{Windows} environments with network troubleshooting and infrastructure management.}
  \resumeItem{Lead project coordination and customer engagement to deliver tailored solutions while ensuring compliance with security and data privacy standards.}
  \resumeItem{Strong communicator adept at translating complex technical concepts to non-expert stakeholders, fostering collaboration and adoption of new tools.}
  \resumeItem{Proactive and adaptable professional committed to continuous learning and driving AI-powered innovation within engineering teams.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Operating Systems:} & Linux (CentOS, Fedora, Ubuntu), Windows \\
\textbf{Programming Languages:} & Python, Java, C\#, Go, TypeScript, JavaScript \\
\textbf{AI \& ML Tools:} & AI-assisted development tools (Claude Code), LLMs, TensorFlow, PyTorch, Spring AI \\
\textbf{DevOps \& Containerization:} & Docker, Kubernetes, Helm, Terraform, CloudFormation \\
\textbf{Networking \& Infrastructure:} & Basic network troubleshooting, network switch CLI commands, MCP servers, OpenCue, Slurm \\
\textbf{Project \& Collaboration Tools:} & Git, Jira, Confluence, Jenkins, GitHub Actions, Azure DevOps \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Coordinated project resources and client communications to deliver AI-enhanced software solutions aligned with business objectives.}
  \resumeItem{Leveraged \textbf{Python} and AI-assisted tools including \textbf{Claude Code} to automate repetitive tasks, improving code quality and delivery speed.}
  \resumeItem{Evaluated and integrated new AI-powered workflows into existing infrastructure, accelerating development and reducing manual effort by 30\%.}
  \resumeItem{Maintained and supported \textbf{Linux} and \textbf{Windows} environments, resolving network and system issues to ensure continuous operations.}
  \resumeItem{Developed documentation and training materials to promote AI tool adoption and best practices across engineering teams.}
  \resumeItem{Implemented secure coding and data handling practices complying with enterprise security and privacy standards.}
  \resumeItem{\textit{Environment: Python, Claude Code, AI/ML tools, Linux (Ubuntu), Windows, Docker, Kubernetes, Jenkins, GitHub Actions, Terraform, OpenTelemetry.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and delivered AI-assisted development pipelines using \textbf{Python} and integrated \textbf{LLMs} to enhance engineering workflows.}
  \resumeItem{Built and maintained containerized infrastructure with \textbf{Docker} and \textbf{Kubernetes}, improving deployment reliability and scalability.}
  \resumeItem{Developed automation tooling leveraging \textbf{AI/ML} frameworks such as \textbf{TensorFlow} and \textbf{PyTorch} to optimize operational processes.}
  \resumeItem{Supported \textbf{Linux} and \textbf{Windows} systems, performing network troubleshooting and infrastructure upgrades to reduce downtime.}
  \resumeItem{Led proof-of-concept projects integrating \textbf{MCP servers} and multi-agent workflows to enhance AI tool interoperability.}
  \resumeItem{Collaborated with cross-functional teams to ensure compliance with security and data privacy policies in AI-enabled environments.}
  \resumeItem{\textit{Environment: Python, TensorFlow, PyTorch, Claude Code, Docker, Kubernetes, MCP servers, Linux (CentOS), Windows, Jenkins, Terraform.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services primarily in \textbf{Python} to support scalable APIs and AI-assisted automation features.}
  \resumeItem{Integrated AI/ML tools and \textbf{LLMs} into development workflows, improving code quality and reducing manual testing efforts.}
  \resumeItem{Maintained \textbf{Linux} and \textbf{Windows} servers, performing routine network troubleshooting and infrastructure support.}
  \resumeItem{Created and updated technical documentation and training guides to facilitate AI tool adoption among engineering staff.}
  \resumeItem{Collaborated with customers and internal teams to define project scopes and deliver AI-powered solutions meeting business needs.}
  \resumeItem{Ensured adherence to security and privacy standards in all development and deployment activities.}
  \resumeItem{\textit{Environment: Python, AI/ML tools, Claude Code, Linux (Ubuntu), Windows, Docker, Kubernetes, Jenkins, GitHub.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Supported \textbf{Linux} and \textbf{Windows} environments by troubleshooting network and system issues to maintain operational stability.}
  \resumeItem{Developed backend components using \textbf{Python} and integrated automation scripts to streamline internal workflows.}
  \resumeItem{Assisted in evaluating new tools and technologies, contributing to proof-of-concept implementations for AI-assisted development.}
  \resumeItem{Created documentation and user guides to support team adoption of emerging AI and automation tools.}
  \resumeItem{Collaborated with cross-functional teams to ensure secure handling of data and compliance with company policies.}
  \resumeItem{Participated in project planning and delivery, supporting engineering teams from development through deployment.}
  \resumeItem{\textit{Environment: Python, Linux (Fedora), Windows, Docker, Jenkins, basic network troubleshooting.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}