\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Leveraged \textbf{Java} expertise over 8+ years to design scalable microservices and event-driven enterprise applications with strong experience in \textbf{Kafka}, \textbf{AWS SQS}, and \textbf{IBM MQ}.}
  \resumeItem{Integrated AI capabilities using Agentic IDEs like \textbf{Claude Code} and \textbf{Cursor}, with solid understanding of \textbf{AI agents}, \textbf{LLMs}, and tools such as \textbf{ChatGPT} for enterprise solutions.}
  \resumeItem{Delivered containerized cloud-native applications using \textbf{Docker}, \textbf{Kubernetes}, and automated CI/CD pipelines, ensuring robust DevOps practices across AWS and hybrid cloud environments.}
  \resumeItem{Applied proficiency in \textbf{Python} for AI integration and developed production-grade AI-powered applications, combining backend engineering with modern AI tooling.}
  \resumeItem{Strong background in building secure, high-performance distributed systems with deep knowledge of messaging queues, microservices, and cloud infrastructure.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java (8/11/17/21), Python, Spring Boot (1/2/3), Spring Security, Spring AI, Hibernate/JPA, C\# (.NET 6+), Go, Kotlin \\
\textbf{Messaging \& Event Streaming:} & Kafka, AWS SQS, IBM MQ, AWS SNS, EventBridge \\
\textbf{Cloud \& Containerization:} & AWS (EKS, ECS/Fargate, Lambda, SQS, SNS, Secrets Manager, IAM, KMS), Docker, Kubernetes, Helm \\
\textbf{AI \& GenAI Tools:} & Agentic IDEs (Claude Code, Cursor), ChatGPT, LLMs, AI agents, Spring AI, AWS Bedrock \\
\textbf{DevOps \& CI/CD:} & Jenkins, GitHub Actions, Azure DevOps Pipelines, Terraform, CloudFormation, SonarQube, Snyk \\
\textbf{Frontend \& API:} & REST, gRPC, OpenAPI/Swagger, Angular (5--17), React (Hooks), TypeScript, RxJS, NgRx \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Designed and developed microservices using \textbf{Java} and \textbf{Spring Boot 3}, improving modularity and reducing deployment risks across enterprise systems.}
  \resumeItem{Implemented event-driven workflows using \textbf{Kafka} and \textbf{AWS SQS}, enhancing system reliability with retry and dead-letter queue mechanisms.}
  \resumeItem{Integrated AI-powered features leveraging \textbf{Agentic IDEs} like \textbf{Claude Code} and \textbf{Cursor} to accelerate enterprise application development.}
  \resumeItem{Developed secure APIs with \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT}, ensuring compliance with enterprise security standards.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes (EKS)} with \textbf{Helm} charts for scalable cloud-native delivery.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, enforcing code quality via \textbf{SonarQube} and security scans with \textbf{Snyk}.}
  \resumeItem{Implemented observability with \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling proactive monitoring and alerting for production systems.}
  \resumeItem{Collaborated on AI integration using \textbf{Python} scripts and \textbf{Spring AI} to build GenAI workflows over enterprise data sources.}
  \resumeItem{Optimized backend performance by 30\% through \textbf{JPA/Hibernate} tuning and implemented caching strategies with \textbf{Redis}.}
  \resumeItem{Delivered frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript} and \textbf{RxJS}, improving user experience and maintainability.}
  \resumeItem{\textit{Environment: Java 17/21, Spring Boot 3, Kafka, AWS SQS, Agentic IDEs (Claude Code, Cursor), Python, Docker, Kubernetes (EKS), Jenkins, GitHub Actions, SonarQube, Snyk, OpenTelemetry, Angular, React, Redis.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed scalable microservices using \textbf{Java 17} and \textbf{Kotlin}, focusing on event-driven design with \textbf{Kafka} to improve throughput and decoupling.}
  \resumeItem{Built and maintained asynchronous messaging pipelines using \textbf{Kafka} and \textbf{AWS SQS}, enhancing reliability through DLQ and retry mechanisms.}
  \resumeItem{Provisioned cloud infrastructure using \textbf{Terraform} and \textbf{CloudFormation} to enable repeatable and auditable AWS deployments.}
  \resumeItem{Integrated AI components using \textbf{Python} for automation and data processing, supporting AI-powered internal tools.}
  \resumeItem{Containerized services with \textbf{Docker} and deployed on \textbf{EKS/ECS}, ensuring zero-downtime releases and scalable operations.}
  \resumeItem{Implemented API contracts using \textbf{gRPC} and \textbf{REST}, enforcing consistency and validation with \textbf{OpenAPI/Swagger}.}
  \resumeItem{Enhanced system observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, reducing incident response times by 25\%.}
  \resumeItem{Built frontend operational tools using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, improving usability for internal teams.}
  \resumeItem{Automated testing with \textbf{JUnit 5}, \textbf{Mockito}, and contract testing using \textbf{Pact} to ensure cross-service reliability.}
  \resumeItem{\textit{Environment: Java 17, Kotlin, Python, Kafka, AWS SQS, Terraform, CloudFormation, Docker, Kubernetes (EKS), OpenTelemetry, Angular, React, JUnit 5, Mockito, Pact.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed enterprise-grade backend services using \textbf{Java} and \textbf{Spring Boot 2}, delivering scalable APIs with robust security using \textbf{OAuth2/OIDC} and \textbf{JWT}.}
  \resumeItem{Implemented asynchronous processing with \textbf{Kafka}, improving message reliability through retry and dead-letter queue patterns.}
  \resumeItem{Built integration endpoints using \textbf{C\#} and \textbf{ASP.NET Core Web API} for partner orchestration and internal workflows.}
  \resumeItem{Optimized database queries and throughput using \textbf{Hibernate/JPA} with \textbf{PostgreSQL/MySQL} and improved response times by 25\% via \textbf{Redis} caching.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling environment-based configuration and scalable releases.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing quality via \textbf{SonarQube} scans.}
  \resumeItem{Delivered frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript} and \textbf{NgRx} for state management in complex workflows.}
  \resumeItem{Integrated cloud messaging and storage services across \textbf{AWS}, \textbf{Azure}, and \textbf{GCP} to support multi-cloud enterprise solutions.}
  \resumeItem{Supported AI integration efforts using \textbf{Python} scripts and tooling to enhance automation and data workflows.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, Kafka, C\#, ASP.NET Core, PostgreSQL/MySQL, Hibernate/JPA, Redis, Docker, Kubernetes, Jenkins, Azure DevOps, Angular, React, TypeScript, Python, AWS/Azure/GCP.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8} and \textbf{Spring Boot 2}, delivering reusable components and REST APIs with \textbf{Swagger} documentation.}
  \resumeItem{Implemented asynchronous messaging using \textbf{JMS} and \textbf{Kafka} to support event-driven workflows and improve system responsiveness.}
  \resumeItem{Built frontend features using \textbf{Angular} and \textbf{React 16} with \textbf{TypeScript}, focusing on reusable components for internal dashboards.}
  \resumeItem{Containerized development and testing environments using \textbf{Docker}, streamlining deployment and local testing workflows.}
  \resumeItem{Improved database performance through query optimization and indexing with \textbf{Hibernate/JPA} on \textbf{Oracle} and \textbf{MySQL}.}
  \resumeItem{Automated builds and CI pipelines using \textbf{Jenkins}, enhancing release stability and developer productivity.}
  \resumeItem{Supported cloud deployments on \textbf{AWS} (EC2, S3, RDS), improving scalability and availability of web applications.}
  \resumeItem{Implemented scheduled batch jobs using \textbf{Quartz} and \textbf{Spring Scheduling} for periodic data processing tasks.}
  \resumeItem{Enhanced system monitoring and logging using \textbf{Log4j} and custom metrics to improve operational visibility.}
  \resumeItem{\textit{Environment: Java 8, Spring Boot 2, JMS, Kafka, Angular, React, Docker, Jenkins, AWS (EC2, S3, RDS), Hibernate/JPA, Oracle, MySQL, Quartz, Log4j.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}