\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Deliver full stack solutions leveraging \textbf{C\#}, \textbf{ASP.NET Core}, \textbf{React}, and \textbf{Azure} cloud services to build scalable, secure, and maintainable applications.}
  \resumeItem{Design and optimize relational databases using \textbf{SQL Server} with complex queries and performance tuning for enterprise-grade applications.}
  \resumeItem{Develop and manage CI/CD pipelines using \textbf{Azure DevOps} and \textbf{GitHub Actions}, automating deployments and infrastructure provisioning.}
  \resumeItem{Implement responsive user interfaces with \textbf{React} and integrate RESTful APIs following microservices architecture principles.}
  \resumeItem{Apply unit testing practices using \textbf{xUnit} to ensure code quality, reliability, and maintainability in cloud-native environments.}
  \resumeItem{Collaborate effectively within Agile teams to deliver new features, troubleshoot issues, and enhance application security and scalability.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & \textbf{C\#}, \textbf{.NET Core}, ASP.NET Core, \textbf{React}, TypeScript, JavaScript, LINQ, Entity Framework Core \\
\textbf{Cloud \& DevOps:} & \textbf{Azure App Services}, Azure Functions, Azure Storage, Azure DevOps, GitHub Actions, Infrastructure as Code, CI/CD Pipelines \\
\textbf{Databases:} & \textbf{SQL Server}, T-SQL, Query Optimization, Relational Database Design \\
\textbf{Testing \& Quality:} & Unit Testing with \textbf{xUnit}, NUnit, Code Reviews, Test Automation \\
\textbf{Architecture \& APIs:} & RESTful APIs, Microservices, OAuth2, Security Best Practices, Containerization with Docker, Kubernetes (basic exposure) \\
\textbf{Methodologies \& Tools:} & Agile Scrum, Git, Jira, Visual Studio, VS Code, GitHub Copilot (AI-assisted development) \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Designed and developed backend services using \textbf{C\#} and \textbf{ASP.NET Core} to improve API reliability and maintainability by 30\%.}
  \resumeItem{Built responsive front-end components with \textbf{React} and integrated RESTful APIs to enhance user experience and reduce load times by 25\%.}
  \resumeItem{Implemented and optimized \textbf{SQL Server} databases with complex queries and indexing, improving data retrieval performance by 35\%.}
  \resumeItem{Developed and maintained \textbf{Azure} cloud services including App Services, Functions, and Storage to support scalable application deployment.}
  \resumeItem{Owned CI/CD pipelines using \textbf{Azure DevOps} and \textbf{GitHub Actions}, automating release management and infrastructure provisioning.}
  \resumeItem{Applied unit testing with \textbf{xUnit} to ensure code quality, reducing production bugs by 20\%.}
  \resumeItem{Collaborated in Agile teams to define features, conduct code reviews, and troubleshoot production issues, improving team velocity by 15\%.}
  \resumeItem{Implemented security best practices for cloud applications, enhancing application security and compliance with enterprise standards.}
  \resumeItem{\textit{Environment: C\#, ASP.NET Core, React, SQL Server, Azure App Services, Azure Functions, Azure DevOps, GitHub Actions, xUnit, Docker, Kubernetes, Agile Scrum.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed and maintained backend services using \textbf{C\#} and \textbf{ASP.NET Core Web API} to support scalable microservices architecture.}
  \resumeItem{Created interactive and responsive front-end features using \textbf{React} and \textbf{TypeScript}, improving user engagement metrics by 20\%.}
  \resumeItem{Optimized \textbf{SQL Server} databases with complex query tuning and schema design, reducing query latency by 25\%.}
  \resumeItem{Managed \textbf{Azure} cloud services including App Services, Functions, and Storage for reliable application hosting and scaling.}
  \resumeItem{Automated CI/CD workflows using \textbf{Azure DevOps} and \textbf{GitHub Actions}, enabling faster and safer deployments.}
  \resumeItem{Implemented unit tests with \textbf{xUnit} and integrated testing to improve overall test coverage by 40\%.}
  \resumeItem{Collaborated with cross-functional teams to design RESTful APIs and integrate microservices, enhancing system modularity and maintainability.}
  \resumeItem{Utilized containerization with \textbf{Docker} and orchestrated deployments on \textbf{Kubernetes} to improve environment consistency.}
  \resumeItem{\textit{Environment: C\#, ASP.NET Core Web API, React, TypeScript, SQL Server, Azure App Services, Azure Functions, Azure DevOps, GitHub Actions, Docker, Kubernetes, xUnit.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Designed and implemented backend APIs using \textbf{C\#} and \textbf{ASP.NET Core}, improving integration workflows with partners by 30\%.}
  \resumeItem{Developed dynamic front-end modules using \textbf{React} and \textbf{TypeScript}, enhancing UI responsiveness and user satisfaction.}
  \resumeItem{Optimized \textbf{SQL Server} databases with indexing and query tuning, reducing average response times by 20\%.}
  \resumeItem{Managed \textbf{Azure} cloud resources including App Services and Storage for scalable and secure application hosting.}
  \resumeItem{Built and maintained CI/CD pipelines using \textbf{Azure DevOps} and \textbf{Jenkins}, accelerating release cycles by 25\%.}
  \resumeItem{Applied unit testing with \textbf{xUnit} and \textbf{NUnit}, improving code reliability and reducing defects.}
  \resumeItem{Collaborated in Agile teams to deliver features, conduct code reviews, and ensure security compliance.}
  \resumeItem{Utilized containerization with \textbf{Docker} and deployed applications on \textbf{Kubernetes} clusters for environment consistency.}
  \resumeItem{\textit{Environment: C\#, ASP.NET Core, React, TypeScript, SQL Server, Azure App Services, Azure DevOps, Jenkins, Docker, Kubernetes, xUnit, NUnit.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{C\#} and \textbf{ASP.NET Core} to support internal tooling and web applications.}
  \resumeItem{Built front-end features using \textbf{React} and \textbf{JavaScript}, improving admin dashboard usability and performance.}
  \resumeItem{Optimized \textbf{SQL Server} database queries and schema design to enhance data processing efficiency by 15\%.}
  \resumeItem{Supported cloud deployments using \textbf{Azure} App Services and Storage for scalable application hosting.}
  \resumeItem{Implemented CI/CD pipelines with \textbf{Jenkins}, improving build automation and deployment reliability.}
  \resumeItem{Applied unit testing using \textbf{xUnit} and \textbf{NUnit} to improve code quality and reduce defects.}
  \resumeItem{Collaborated with Agile teams to deliver features, troubleshoot issues, and improve system stability.}
  \resumeItem{Containerized applications using \textbf{Docker} to streamline development and testing environments.}
  \resumeItem{\textit{Environment: C\#, ASP.NET Core, React, JavaScript, SQL Server, Azure App Services, Jenkins, Docker, xUnit, NUnit, Agile Scrum.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}