```latex
\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Experienced \textbf{software engineer} with 5+ years delivering robust data integration and application solutions, specializing in \textbf{Workday Integrations} and cloud-native architectures.}
    \resumeItem{Skilled in designing and implementing \textbf{data warehousing}, \textbf{ETL pipelines}, and \textbf{CI/CD} workflows using \textbf{Python}, \textbf{Shell scripting}, and \textbf{GitHub} to streamline deployments.}
    \resumeItem{Proficient in collaborating across cross-functional teams and managing \textbf{production support} while applying Agile methodologies like \textbf{Scrum} and \textbf{Kanban} for efficient delivery.}
    \resumeItem{Experienced with \textbf{SaaS data platforms} including \textbf{AWS} and \textbf{Snowflake}, and skilled in \textbf{Workday PRISM Analytics} and \textbf{Accounting Center} for enhanced reporting and data insights.}
    \resumeItem{Strong communicator adept at coordinating with upstream/downstream teams to identify dependencies, risks, and ensure comprehensive testing and deployment readiness.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, Shell Scripting, JavaScript, SQL, PL/SQL \\
                \textbf{Workday Integrations:} & EIB, API, Connectors, Studio, Orchestrate, Extend, PRISM Analytics, Accounting Center \\
                \textbf{Data Platforms \& Warehousing:} & AWS (S3, Lambda, Glue), Snowflake, Data Lakes, Data Modeling, ETL Pipelines \\
                \textbf{DevOps \& CI/CD:} & GitHub, Jenkins, UDeploy, Docker, CI/CD Pipelines \\
                \textbf{Tools \& Collaboration:} & Excel, PowerPoint, Visio, JIRA, Practitest, DragonBoat \\
                \textbf{Methodologies:} & Agile (Scrum, Kanban, XP), Production Support, On-Call Support \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Developed and maintained \textbf{Workday Integrations} using \textbf{EIB} and \textbf{API connectors}, improving data synchronization accuracy by 30\%.}
        \resumeItem{Automated deployment workflows with \textbf{GitHub} and \textbf{UDeploy}, reducing release cycle time by 40\% and enhancing pipeline reliability.}
        \resumeItem{Designed scalable \textbf{data integration} solutions leveraging \textbf{AWS} data lakes and \textbf{Snowflake}, increasing data processing speed by 35\%.}
        \resumeItem{Collaborated with cross-functional teams and \textbf{business SMEs} to identify testing dependencies, improving test coverage and reducing defects by 25\%.}
        \resumeItem{Implemented \textbf{Agile} practices using \textbf{JIRA} and \textbf{DragonBoat}, accelerating sprint delivery efficiency by 20\%.}
        \resumeItem{Provided \textbf{production support} and on-call incident resolution, decreasing critical downtime by 15\% through proactive monitoring and quick remediation.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{API-based data integration} modules using \textbf{Python} and \textbf{Shell scripting}, improving data pipeline efficiency by 30\%.}
        \resumeItem{Implemented \textbf{CI/CD pipelines} integrating \textbf{GitHub} and \textbf{Jenkins}, reducing deployment errors by 35\% and accelerating delivery.}
        \resumeItem{Designed and optimized \textbf{data models} for warehousing solutions, enhancing query performance by 25\% and data accuracy.}
        \resumeItem{Collaborated with upstream/downstream teams to coordinate testing scenarios, mitigating risks and ensuring smooth integration of new features.}
        \resumeItem{Adopted \textbf{Agile} methodologies including \textbf{Scrum} and \textbf{Kanban}, improving team velocity and sprint predictability by 18\%.}
        \resumeItem{Supported production environments with quick incident response, reducing average resolution time by 20\%.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed backend integration workflows using \textbf{Java} and \textbf{SQL}, improving data throughput by 22\% for supply chain applications.}
        \resumeItem{Automated build and deployment tasks with \textbf{Shell scripting} and \textbf{Jenkins}, cutting manual effort by 15 hours per month.}
        \resumeItem{Collaborated with third-party application teams to integrate APIs, reducing integration defects by 30\% and improving data consistency.}
        \resumeItem{Enhanced data indexing strategies in \textbf{DynamoDB}, increasing read efficiency by 14\% during peak loads.}
        \resumeItem{Assisted in cloud migration to \textbf{AWS EC2}, improving system uptime by 18\% and reducing hardware dependency.}
      \resumeItemListEnd


  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Workday Data Integration Automation} $|$ Python, Workday Studio, API, Jenkins}{ }
        \resumeItemListStart
            \resumeItem{Automated Workday data ingestion using \textbf{Workday Studio} and \textbf{APIs}, reducing manual processing time by 50\% and improving data accuracy.}
            \resumeItem{Implemented CI/CD pipelines with \textbf{Jenkins} to streamline deployment, cutting release time by 35\% and minimizing errors.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{AI-Powered Document Query System} $|$ Python, LangChain, OpenAI API, Docker}{ }
        \resumeItemListStart
            \resumeItem{Developed an AI-based natural language query system leveraging \textbf{LangChain} and \textbf{OpenAI API}, enabling 80\% faster document retrieval.}
            \resumeItem{Containerized the application with \textbf{Docker} and automated testing workflows, improving deployment consistency and scalability.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Cloud Data Warehouse Optimization} $|$ AWS, Snowflake, SQL, Python}{ }
        \resumeItemListStart
            \resumeItem{Optimized ETL pipelines on \textbf{AWS} and \textbf{Snowflake}, improving data load speed by 40\% and reducing storage costs by 20\%.}
            \resumeItem{Designed data models and automated data validation using \textbf{Python}, enhancing data quality and reporting accuracy.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}
```