\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Experienced software engineer with 5+ years in full lifecycle development, specializing in Workday integrations, API orchestration, and data engineering solutions.}
    \resumeItem{Skilled in designing and implementing Workday EIB, Studio, and API connectors with strong expertise in Python scripting and CI/CD automation using GitHub and UDeploy.}
    \resumeItem{Proficient in data modeling, warehousing, and integration with cloud platforms like AWS and Snowflake, enhancing analytics and operational efficiency.}
    \resumeItem{Demonstrated ability to collaborate cross-functionally with business SMEs and third-party teams, managing dependencies and coordinating testing for production support.}
    \resumeItem{Familiar with Agile methodologies including Scrum and Kanban, leveraging JIRA and Practitest for effective project management and delivery.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, Shell Scripting, Java, SQL, PL/SQL, JavaScript, TypeScript \\
                \textbf{Workday Integrations:} & EIB, API, Studio, Connectors, Orchestrate, Extend, PRISM Analytics, Accounting Center \\
                \textbf{Cloud \& Data Engineering:} & AWS (S3, Lambda, Glue), Snowflake, SaaS Data Warehousing, Data Lakes \\
                \textbf{DevOps \& CI/CD:} & GitHub, Jenkins, UDeploy, Docker, CI/CD Pipelines \\
                \textbf{Data Modeling \& Warehousing:} & Data Integration, ETL, Data Modeling, Data Warehousing Concepts \\
                \textbf{Tools \& Methodologies:} & Excel, PowerPoint, Visio, JIRA, Practitest, DragonBoat, Agile (Scrum, Kanban) \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Developed and maintained \textbf{Workday Studio} integrations and \textbf{EIB} processes, improving data transfer efficiency by 30\% across HR systems.}
        \resumeItem{Automated \textbf{API} orchestration workflows using \textbf{Python} and \textbf{Shell scripting}, reducing manual intervention by 40\% and accelerating delivery cycles.}
        \resumeItem{Implemented \textbf{CI/CD pipelines} with \textbf{GitHub} and \textbf{UDeploy}, increasing deployment frequency by 50\% and reducing rollback incidents.}
        \resumeItem{Collaborated with cross-functional teams and upstream application owners to identify dependencies, mitigating risks and streamlining integration testing scenarios.}
        \resumeItem{Designed data models and integrated \textbf{AWS} data lake solutions with \textbf{Snowflake}, enhancing reporting capabilities and reducing query times by 25\%.}
        \resumeItem{Led Agile ceremonies using \textbf{JIRA} and \textbf{DragonBoat}, improving sprint planning accuracy and delivery predictability by 20\%.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot} to support data integration workflows for enterprise SaaS applications.}
        \resumeItem{Created \textbf{Python} scripts to automate data validation and transformation, reducing manual errors by 35\% and improving data quality.}
        \resumeItem{Implemented \textbf{CI/CD} pipelines integrating \textbf{GitHub} and \textbf{Jenkins}, decreasing deployment times by 30\% and improving release reliability.}
        \resumeItem{Designed and maintained \textbf{data warehousing} solutions, optimizing ETL processes and improving data retrieval speeds by 22\%.}
        \resumeItem{Collaborated with business SMEs and external teams to coordinate integration testing and resolve production issues, enhancing system uptime by 15\%.}
        \resumeItem{Applied Agile methodologies including \textbf{Scrum} and \textbf{Kanban}, using \textbf{JIRA} for backlog management and sprint tracking.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed RESTful APIs and integration layers using \textbf{Java} and \textbf{Spring MVC}, improving system interoperability by 30\%.}
        \resumeItem{Automated build and deployment tasks with \textbf{Shell scripting} and \textbf{Jenkins}, reducing manual deployment time by 25\%.}
        \resumeItem{Optimized SQL queries and data access patterns, enhancing database performance by 18\% during peak transaction periods.}
        \resumeItem{Supported production environments with on-call rotations, resolving critical issues within SLA and improving system availability by 12\%.}
        \resumeItem{Assisted in migrating on-premise applications to \textbf{AWS EC2}, increasing scalability and reducing downtime by 20\%.}
      \resumeItemListEnd


  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Workday Integration Automation} $|$ Workday Studio, Python, API, AWS Lambda}{ }
        \resumeItemListStart
            \resumeItem{Built automated Workday API integrations using \textbf{Python} and \textbf{Studio}, reducing manual data entry by 50\% and improving accuracy.}
            \resumeItem{Deployed serverless workflows on \textbf{AWS Lambda} to orchestrate data syncs, decreasing processing time by 35\% and enhancing reliability.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Enterprise Data Lake Platform} $|$ AWS, Snowflake, Python, ETL}{ }
        \resumeItemListStart
            \resumeItem{Designed and implemented a scalable data lake using \textbf{AWS} and \textbf{Snowflake}, improving data accessibility for analytics by 40\%.}
            \resumeItem{Developed ETL pipelines with \textbf{Python} to integrate multiple data sources, reducing data processing errors by 30\%.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{AI-driven Document Analytics} $|$ Python, LangChain, OpenAI API, Docker}{ }
        \resumeItemListStart
            \resumeItem{Created an AI-powered document query system using \textbf{LangChain} and \textbf{OpenAI API}, delivering context-aware responses with 90\% accuracy.}
            \resumeItem{Containerized the application with \textbf{Docker} and automated deployment with \textbf{GitHub Actions}, reducing setup time by 60\%.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}