```latex
\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small#2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{\textbf{Full Stack Developer} with 5+ years of experience specializing in building scalable web applications using \textbf{Ruby on Rails} and \textbf{React.js}, delivering high-quality user experiences.} \vspace{-3pt}
    \resumeItem{Skilled in backend API development, efficient database design with \textbf{PostgreSQL}, and frontend rich UI creation using \textbf{React} and \textbf{Redux} for complex web dashboards.} \vspace{-3pt}
    \resumeItem{Experienced in designing distributed services and evolving large-scale systems with a strategic, product-oriented mindset focused on user needs and feature iteration.} \vspace{-3pt}
    \resumeItem{Passionate about networking and security domains, with proven ability to inspire teams and deliver sophisticated software solutions in agile environments.} \vspace{-3pt}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Ruby, JavaScript, TypeScript, Go, SQL, Python, Shell Scripting, Java \\
                \textbf{Frameworks \& Backend:} & Ruby on Rails, Node.js, Express.js, Go Gin, Spring Boot, RESTful APIs \\
                \textbf{Frontend:} & React.js, Redux, Material UI, Bootstrap, HTML5, CSS3 \\
                \textbf{Databases:} & PostgreSQL, MySQL, MongoDB, Redis \\
                \textbf{Testing \& Automation:} & RSpec, JUnit, Selenium, Jest, Postman, CI/CD (Jenkins, GitHub Actions) \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, S3, API Gateway), Docker, Kubernetes, Terraform, Jenkins \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Developed and maintained scalable backend services using \textbf{Ruby on Rails} and \textbf{PostgreSQL}, improving API response times by 30\%.}
        \resumeItem{Built dynamic user interfaces with \textbf{React.js} and \textbf{Redux}, enhancing user engagement by 40\% through improved dashboard features.}
        \resumeItem{Led migration of monolithic systems to microservices architecture with \textbf{Go} and \textbf{Ruby on Rails}, reducing deployment times by 25\%.}
        \resumeItem{Optimized complex \textbf{PostgreSQL} queries, increasing database efficiency and reducing latency by 20\%.}
        \resumeItem{Implemented real-time data updates on dashboards using WebSocket and React, improving live monitoring capabilities by 35\%.}
        \resumeItem{Integrated CI/CD pipelines with \textbf{Jenkins} and \textbf{Docker}, increasing deployment frequency by 50\% and reducing rollback incidents.}
        \resumeItem{Collaborated on security enhancements for backend services, applying best practices in authentication and authorization, reducing vulnerabilities by 40\%.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Designed and developed backend APIs using \textbf{Node.js} and \textbf{Express.js}, delivering core banking features with 99.9\% uptime.}
        \resumeItem{Created rich web interfaces using \textbf{React} and \textbf{Redux}, improving loan application usability and reducing user errors by 25\%.}
        \resumeItem{Implemented event-driven architecture with \textbf{Kafka}, handling over 10,000 transactions per second with high reliability.}
        \resumeItem{Built and monitored dashboards with \textbf{Grafana} and \textbf{Prometheus}, enhancing system observability and reducing incident response times by 30\%.}
        \resumeItem{Strengthened security frameworks using \textbf{OAuth2} and \textbf{JWT}, lowering security incidents by 40\%.}
        \resumeItem{Automated CI/CD workflows with \textbf{Jenkins} and \textbf{SVN}, reducing deployment times by 30\% and improving release cadence.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed backend modules with \textbf{Java} and \textbf{Spring MVC}, optimizing SQL queries to reduce order processing latency by 140ms.}
        \resumeItem{Integrated third-party logistics APIs using \textbf{Node.js} and \textbf{Express.js}, expanding vendor support by 12\% within the first quarter.}
        \resumeItem{Authored comprehensive unit tests with \textbf{JUnit} and \textbf{Mockito}, uncovering and fixing 20+ critical bugs pre-production.}
        \resumeItem{Improved system availability by migrating components to \textbf{AWS EC2}, reducing hardware downtime by 18\%.}
        \resumeItem{Enhanced DynamoDB access patterns, boosting read throughput by 14\% during peak usage windows.}
        \resumeItem{Automated build and deployment tasks using \textbf{Shell scripting} and \textbf{Jenkins}, saving 4 hours of manual work weekly.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{InsightPDF} | Python, Streamlit, LangChain, OpenAI API, FAISS, Docker, GitHub Actions}{ }
        \resumeItemListStart
            \resumeItem{Developed an AI-driven document query tool using a RAG pipeline, enabling contextual answers from PDFs with 95\% accuracy in natural language queries.}
            \resumeItem{Containerized the application with \textbf{Docker} and automated deployments using GitHub Actions, reducing deployment time by 40\%.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Meraki Dashboard Clone} | Ruby on Rails, React, PostgreSQL, WebSocket}{ }
        \resumeItemListStart
            \resumeItem{Built a real-time network device monitoring dashboard using \textbf{Ruby on Rails} backend and \textbf{React} frontend, improving update latency by 30\%.}
            \resumeItem{Implemented efficient \textbf{PostgreSQL} schema and queries, reducing data retrieval times by 25\% for large-scale device configurations.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{SecurBank} | Go, Gin, PostgreSQL, JWT, Docker, Redis}{ }
        \resumeItemListStart
            \resumeItem{Engineered secure backend services with \textbf{Go} and \textbf{Gin}, integrating JWT for authentication, enhancing system security by 30\%.}
            \resumeItem{Optimized caching with \textbf{Redis} and deployed using \textbf{Docker} containers, improving response times and scalability by 25\%.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}
```