\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Experienced \textbf{software engineer} with 5+ years delivering robust data integration and cloud-native solutions, specializing in \textbf{Workday} integrations and \textbf{Python} scripting.}
    \resumeItem{Skilled in developing and deploying scalable applications using \textbf{CI/CD pipelines}, GitHub, and \textbf{UDeploy} to streamline releases and improve operational efficiency.}
    \resumeItem{Proficient in data modeling, data warehousing, and integration with expertise in \textbf{AWS}, \textbf{Snowflake}, and \textbf{SaaS} platforms to optimize analytics workflows.}
    \resumeItem{Experienced in Agile methodologies including Scrum and Kanban, collaborating effectively with cross-functional teams and external stakeholders to manage dependencies and risks.}
    \resumeItem{Strong background in production and on-call support, ensuring high availability and quick resolution of issues in complex enterprise environments.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, Shell Scripting, Java, SQL, PL/SQL \\
                \textbf{Integration \& Middleware:} & Workday Integrations (EIB, API, Connectors, Studio, Orchestrate, Extend), REST APIs, Kafka \\
                \textbf{Cloud \& Data Engineering:} & AWS (S3, EC2, Lambda), Snowflake, SaaS Data Warehousing, Data Lakes \\
                \textbf{DevOps \& Automation:} & CI/CD Pipelines, GitHub, UDeploy, Jenkins, Docker \\
                \textbf{Data \& Analytics:} & Data Modeling, Data Warehousing, Workday PRISM Analytics, Accounting Center, Excel, PowerPoint, Visio \\
                \textbf{Methodologies \& Tools:} & Agile (Scrum, Kanban, XP), JIRA, Practitest, DragonBoat, Production Support \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Developed and maintained \textbf{Workday} integrations using \textbf{API} and \textbf{EIB}, improving data synchronization accuracy by 30\%.}
        \resumeItem{Automated deployment workflows with \textbf{GitHub} and \textbf{UDeploy}, reducing release cycle time by 40\% and enhancing deployment reliability.}
        \resumeItem{Collaborated with cross-functional teams to design data models and implement \textbf{SaaS} data warehousing solutions on \textbf{AWS} and \textbf{Snowflake}, improving query performance by 25\%.}
        \resumeItem{Created and maintained \textbf{Python} and \textbf{Shell} scripts for integration orchestration and data transformation, increasing automation coverage by 35\%.}
        \resumeItem{Led Agile ceremonies using \textbf{Scrum} and managed tasks through \textbf{JIRA}, ensuring timely delivery and effective risk mitigation across workstreams.}
        \resumeItem{Provided production and on-call support for critical \textbf{Workday} integration services, achieving 99.9\% uptime and rapid incident resolution.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{Workday Studio} integrations and \textbf{Connectors} to streamline HR data flows, reducing manual errors by 20\%.}
        \resumeItem{Developed \textbf{CI/CD} pipelines integrating \textbf{GitHub} and \textbf{Jenkins}, accelerating deployment frequency by 30\% and improving release stability.}
        \resumeItem{Designed and optimized data warehousing schemas and ETL pipelines on \textbf{AWS}, enhancing data processing throughput by 40\%.}
        \resumeItem{Authored \textbf{Python} scripts for automated testing and data validation, increasing test coverage by 25\% and reducing defects.}
        \resumeItem{Collaborated with upstream and downstream teams to identify dependencies and coordinate testing plans, reducing integration issues by 15\%.}
        \resumeItem{Supported production environments and participated in on-call rotations, maintaining system availability above 99.5\%.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring MVC}, improving data integration efficiency by 18\% through optimized SQL queries.}
        \resumeItem{Integrated third-party APIs and built middleware for data exchange, increasing vendor connectivity by 12\% within the first quarter.}
        \resumeItem{Automated build and deployment tasks with \textbf{Shell} scripting and \textbf{Jenkins}, reducing manual effort by 4 hours weekly.}
        \resumeItem{Assisted in migrating on-premise infrastructure to \textbf{AWS EC2}, improving system uptime by 15\% and reducing operational costs.}
        \resumeItem{Enhanced database performance by refining \textbf{DynamoDB} access patterns, achieving 14\% better read throughput during peak hours.}
      \resumeItemListEnd


  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Workday Integration Automation} | Workday Studio, Python, AWS Lambda, GitHub Actions}{}
        \resumeItemListStart
            \resumeItem{Developed automated \textbf{Workday} integration workflows using Studio and Python, reducing manual processing time by 40\%.}
            \resumeItem{Implemented CI/CD pipelines with \textbf{GitHub Actions} and AWS Lambda, improving deployment speed and reliability by 30\%.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{AI-Powered Data Analytics Platform} | Python, Snowflake, AWS, LangChain, OpenAI API}{}
        \resumeItemListStart
            \resumeItem{Built an AI-driven analytics platform leveraging \textbf{LangChain} and OpenAI API to deliver contextual insights from large datasets, increasing analysis speed by 50\%.}
            \resumeItem{Integrated \textbf{Snowflake} data warehousing on AWS to enable scalable and efficient data storage and querying for analytics workflows.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Enterprise Data Integration Framework} | Java, Spring Boot, Kafka, AWS, Jenkins}{}
        \resumeItemListStart
            \resumeItem{Designed a scalable data integration framework using \textbf{Spring Boot} and \textbf{Kafka}, improving data throughput by 35\% across enterprise systems.}
            \resumeItem{Automated deployment and testing with \textbf{Jenkins}, reducing release errors by 25\% and accelerating delivery cycles.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}