\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Rahul Reddy K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (714) 805-6273 ~ | ~ \href{mailto:kanrahuldo1@gmail.com}{kanrahuldo1@gmail.com}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{\textbf{Senior C/C++ Software Engineer} with 8+ years of expertise in systems-level programming, focusing on network protocols, VPN technologies, and Windows/Linux OS environments.}
    \resumeItem{Proficient in designing and debugging complex client/server applications, automating test suites, and enhancing network security protocols such as \textbf{IPSec} and \textbf{QUIC}.}
    \resumeItem{Experienced in scripting with \textbf{PowerShell} and \textbf{YAML} to streamline automation, and skilled in using tools like \textbf{Wireshark}, \textbf{gdb}, and \textbf{tcpdump} for system-level instrumentation.}
    \resumeItem{Strong background in troubleshooting legacy and new systems, analyzing WPP/ETW traces, and implementing secure VPN tunnels within software-defined networking frameworks.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & C, C++, Python, Shell Scripting, PowerShell \\
                \textbf{Operating Systems:} & Windows, Linux, Unix \\
                \textbf{Networking Protocols:} & IPSec, TCP/IP, UDP/IP, QUIC, VPN Technologies, SDN \\
                \textbf{Debugging \& Tracing Tools:} & Windows Debugger, gdb, Wireshark, tcpdump, WPP/ETW Trace Analysis \\
                \textbf{Build \& Automation Tools:} & CMake, Jenkins, Git/GitHub, YAML, SonarQube \\
                \textbf{Frameworks \& Libraries:} & Boost, Google Test, Google Mock \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Toyota Motors}{Oct 2023 -- Present}
        {C++ Embedded / Application Developer}{TX}
      \resumeItemListStart
        \resumeItem{Designed and implemented multi-threaded \textbf{C++} modules to enhance VPN and IPSec tunnel stability, reducing connection failures by 30\%.}
        \resumeItem{Developed and maintained test automation scripts using \textbf{PowerShell} and \textbf{YAML}, improving test pipeline efficiency across multiple network security projects.}
        \resumeItem{Troubleshot complex network protocol issues with \textbf{Wireshark} and \textbf{tcpdump}, accelerating root cause analysis and reducing bug resolution time by 25\%.}
        \resumeItem{Collaborated with cross-functional teams to customize Windows-based system software, ensuring compliance with client VPN and IPSec security requirements.}
        \resumeItem{Authored detailed design and test documentation for new \textbf{C++} features, enhancing maintainability and knowledge sharing within the engineering team.}
      \resumeItemListEnd

    \resumeSubheading
        {Texas Instruments}{Aug 2022 -- Sep 2023}
        {C/C++ Embedded Developer}{Phoenix, AZ}
      \resumeItemListStart
        \resumeItem{Led development of \textbf{C/C++} systems software integrating VPN and SDN features, improving secure communication throughput by 20\%.}
        \resumeItem{Enhanced automated test suites for network protocols including \textbf{IPSec} and \textbf{TCP}, increasing test coverage by 40\%.}
        \resumeItem{Utilized \textbf{gdb} and \textbf{Windows Debugger} to debug legacy software, resolving over 50 critical bugs and improving system stability.}
        \resumeItem{Implemented WPP/ETW trace analysis to diagnose complex system failures, reducing incident resolution time by 35\%.}
        \resumeItem{Developed \textbf{PowerShell} scripts to automate build and deployment processes, accelerating release cycles by 15\%.}
      \resumeItemListEnd

    \resumeSubheading
        {Texas Instruments}{May 2021 -- Jul 2022}
        {C/C++ Embedded Developer}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{C/C++} modules supporting Linux subsystems, enabling secure VPN connections and enhancing network protocol handling.}
        \resumeItem{Automated integration tests for \textbf{IPSec} tunnels using \textbf{Python} and shell scripts, improving regression testing efficiency by 30\%.}
        \resumeItem{Collaborated on cross-platform development between Windows and Linux environments, ensuring consistent VPN functionality across OSes.}
        \resumeItem{Analyzed network traffic with \textbf{Wireshark} to optimize \textbf{QUIC} protocol implementations, increasing data throughput by 18\%.}
      \resumeItemListEnd

    \resumeSubheading
        {Panasonic}{Feb 2020 -- Apr 2021}
        {C++ Developer}{Bengaluru, KA}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{C++} software for TCP/IP networking firmware, enabling secure VPN tunnels and remote device management over Ethernet.}
        \resumeItem{Performed manual and automated testing of \textbf{IPSec} and VPN connections on Windows and Linux platforms, reducing security tunnel failures by 22\%.}
        \resumeItem{Debugged system-level issues using \textbf{gdb} and \textbf{Wireshark}, accelerating bug fixes and improving firmware reliability.}
        \resumeItem{Created \textbf{YAML}-based configuration files for automated test pipelines, streamlining network protocol validation processes.}
      \resumeItemListEnd

    \resumeSubheading
        {JSW Steel}{Aug 2017 -- Dec 2019}
        {C++ Embedded Developer}{India}
      \resumeItemListStart
        \resumeItem{Modernized legacy \textbf{C++} codebase to support IPSec and VPN protocol enhancements, improving secure communication by 25\%.}
        \resumeItem{Developed client/server modules with \textbf{C++} for network security applications, increasing system throughput and reliability.}
        \resumeItem{Utilized \textbf{Wireshark} and protocol analyzers to investigate network traffic, identifying and resolving protocol inefficiencies.}
        \resumeItem{Authored PowerShell scripts to automate test execution and log analysis, reducing manual effort by 40\%.}
        \resumeItem{Migrated repositories from SVN to \textbf{Git} and integrated CI/CD pipelines, improving development workflow and deployment speed.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Secure VPN Automation Framework} | Windows/Linux}{2023}
    \resumeItemListStart
      \resumeItem{Designed an automated test framework using \textbf{PowerShell} and \textbf{YAML} to validate IPSec VPN tunnels, improving test coverage by 40\%.}
      \resumeItem{Integrated \textbf{Wireshark} and \textbf{gdb} tools for real-time debugging and traffic analysis, reducing manual troubleshooting time by 30\%.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{QUIC Protocol Optimization} | Linux}{2022}
    \resumeItemListStart
      \resumeItem{Enhanced \textbf{C++} implementation of \textbf{QUIC} to improve throughput by 18\% through packet handling optimizations and reduced latency.}
      \resumeItem{Analyzed network traffic using \textbf{tcpdump} and \textbf{Wireshark} to identify bottlenecks and validate protocol compliance.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{AI-driven Network Anomaly Detection} | Cross-platform}{2021}
    \resumeItemListStart
      \resumeItem{Developed a \textbf{Python}-based AI model to detect anomalies in IPSec VPN traffic, achieving 95\% accuracy in identifying security threats.}
      \resumeItem{Automated data collection and preprocessing pipelines, integrating with existing C/C++ network monitoring tools for seamless deployment.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}