\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Experienced full stack developer specializing in \textbf{JavaScript/TypeScript} and \textbf{PHP}, building scalable, secure, and resilient web applications with modern frameworks.}
    \resumeItem{Proficient in \textbf{React}, \textbf{Node.js}, and \textbf{Symfony}, with a strong focus on performance optimization, automated testing, and CI/CD pipelines using Docker and Kubernetes.}
    \resumeItem{Skilled in cloud-native development leveraging \textbf{AWS}, infrastructure as code tools like \textbf{Terraform}, and container orchestration for highly available production environments.}
    \resumeItem{Collaborative team player experienced in Agile methodologies, mentoring developers, and driving continuous improvement in engineering practices and developer workflows.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & JavaScript, TypeScript, PHP, SQL, Python, Java \\
                \textbf{Frameworks \& Backend:} & React, Node.js, Symfony, Express.js, Spring Boot \\
                \textbf{Testing \& Automation:} & Playwright, Jest, JUnit, Mockito, Selenium, CircleCI, Jenkins \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, ECS, S3), Terraform, Docker, Kubernetes, Octopus Deploy, CircleCI \\
                \textbf{Databases:} & PostgreSQL, MySQL, MongoDB, Redis \\
                \textbf{Methodologies \& Tools:} & Agile (Scrum, Kanban), CI/CD, Git, OAuth2, JWT, CDN (Akamai) \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Developed scalable microservices using \textbf{PHP} and \textbf{Symfony}, improving system resilience and reducing downtime by 25\% in production environments.}
        \resumeItem{Implemented responsive front-end features with \textbf{React} and \textbf{TypeScript}, increasing user engagement by 35\% through enhanced UI performance.}
        \resumeItem{Built containerized applications with \textbf{Docker} and orchestrated deployments using \textbf{Kubernetes}, improving deployment speed by 40\%.}
        \resumeItem{Automated end-to-end testing using \textbf{Playwright} and \textbf{Jest}, achieving 95\% test coverage and reducing production bugs by 30\%.}
        \resumeItem{Optimized PostgreSQL queries and database indexing, resulting in 20\% faster data retrieval and improved application scalability.}
        \resumeItem{Designed and maintained CI/CD pipelines with \textbf{CircleCI} and \textbf{Octopus Deploy}, accelerating release cycles by 50\%.}
        \resumeItem{Collaborated with stakeholders to define requirements and break down tasks, ensuring timely delivery of prioritized features in Agile sprints.}
        \resumeItem{Mentored junior developers and promoted pair programming, elevating team code quality and engineering standards.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Developed backend services in \textbf{Java} and \textbf{Spring Boot} following OOP principles, improving system modularity and maintainability.}
        \resumeItem{Created front-end components with \textbf{React} and \textbf{Redux}, enhancing user experience and reducing page load times by 25\%.}
        \resumeItem{Implemented event-driven architecture using \textbf{Kafka}, handling over 10,000 transactions per second with high reliability.}
        \resumeItem{Automated CI/CD workflows integrating \textbf{Jenkins} and \textbf{SVN}, reducing deployment times by 30\% and minimizing manual errors.}
        \resumeItem{Built observability dashboards with \textbf{Grafana} and \textbf{Prometheus}, enabling proactive system monitoring and faster incident resolution.}
        \resumeItem{Enhanced security by integrating \textbf{OAuth2} and \textbf{JWT}, reducing security incidents by 40\% through robust authentication mechanisms.}
        \resumeItem{Developed Node.js middleware for real-time transaction processing, improving throughput by 30\% in cash management systems.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Built backend modules using \textbf{PHP} and \textbf{Symfony}, reducing order processing latency by 140ms through optimized SQL queries.}
        \resumeItem{Integrated third-party logistics APIs with \textbf{Node.js} and \textbf{Express.js}, expanding vendor support coverage by 12\% within one quarter.}
        \resumeItem{Authored unit and integration tests with \textbf{JUnit} and \textbf{Mockito}, identifying 20+ critical bugs prior to production deployment.}
        \resumeItem{Migrated on-premise services to \textbf{AWS EC2}, improving availability and reducing downtime by 18\%.}
        \resumeItem{Optimized \textbf{DynamoDB} access patterns for inventory tracking, increasing read throughput by 14\% during peak hours.}
        \resumeItem{Automated build and deployment tasks using \textbf{Linux Shell} scripts and \textbf{Jenkins}, saving 4 hours of manual work weekly.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-Powered Document Query System} $|$ Python, LangChain, OpenAI API, FAISS, Docker}{}
        \resumeItemListStart
            \resumeItem{Developed an AI-driven document search tool using \textbf{RAG} techniques, delivering precise answers from PDFs with 90\% accuracy.}
            \resumeItem{Containerized the application with \textbf{Docker} and automated deployment using GitHub Actions, reducing setup time by 60\%.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Scalable Web Application with Container Orchestration} $|$ React, Node.js, Docker, Kubernetes, AWS}{}
        \resumeItemListStart
            \resumeItem{Engineered a full stack web app using \textbf{React} and \textbf{Node.js}, deploying on \textbf{Kubernetes} clusters to support 1000+ concurrent users.}
            \resumeItem{Implemented CI/CD pipelines with \textbf{CircleCI} and \textbf{Octopus Deploy}, reducing deployment time by 45\% and improving reliability.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Secure Banking Backend Service} $|$ PHP, Symfony, PostgreSQL, Docker, AWS}{}
        \resumeItemListStart
            \resumeItem{Built a secure backend with \textbf{Symfony} and \textbf{PostgreSQL}, integrating JWT authentication and deploying via Docker on AWS.}
            \resumeItem{Optimized database queries and caching with \textbf{Redis}, improving response times by 25\% and enhancing user experience.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}