\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Deliver over 8 years of expertise in full stack development with a focus on \textbf{Java}, \textbf{Spring Boot}, and modern JavaScript frameworks like \textbf{React} and \textbf{Angular}, driving scalable enterprise solutions.}
  \resumeItem{Architect and implement microservices-based applications leveraging \textbf{REST} and \textbf{GraphQL} APIs, ensuring high performance and maintainability.}
  \resumeItem{Design intuitive front-end interfaces using \textbf{React} and \textbf{Angular} with \textbf{HTML5} and \textbf{CSS}, enhancing user experience and responsiveness.}
  \resumeItem{Apply strong knowledge of \textbf{Oracle} and relational databases with advanced \textbf{SQL} and \textbf{PL/SQL} skills to optimize data access and integrity.}
  \resumeItem{Integrate AI tools and cloud-native technologies to streamline development workflows and enable event-driven, scalable systems.}
  \resumeItem{Lead CI/CD and DevOps initiatives using \textbf{Maven}, \textbf{Docker}, \textbf{Jenkins}, and \textbf{OpenShift}, with practical experience deploying on \textbf{AWS} cloud environments.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java, Spring Boot, React, Angular, JavaScript, TypeScript, SQL, PL/SQL \\
\textbf{Backend \& API:} & Microservices, REST, GraphQL, Spring Security, OAuth2/OIDC, JWT, Event-Driven Architecture \\
\textbf{Databases:} & Oracle, PostgreSQL, MySQL, Hibernate/JPA \\
\textbf{DevOps \& CI/CD:} & Maven, Gradle, Docker, Jenkins, OpenShift, GitHub Actions \\
\textbf{Cloud Platforms:} & AWS (EKS, ECS, Lambda, S3, RDS, IAM), Azure, GCP \\
\textbf{Frontend \& UI:} & React (Hooks), Angular, HTML5, CSS3/SCSS, RxJS, NgRx \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Designed and developed backend microservices using \textbf{Java} and \textbf{Spring Boot}, improving modularity and reducing deployment risk.}
  \resumeItem{Implemented and maintained \textbf{RESTful} APIs with consistent validation and error handling, enhancing integration reliability.}
  \resumeItem{Secured applications with \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT}, ensuring compliance with enterprise security standards.}
  \resumeItem{Built dynamic UI components using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, improving user engagement and modularity.}
  \resumeItem{Developed event-driven services using \textbf{Kafka} and \textbf{AWS SQS/SNS}, increasing system resilience and throughput.}
  \resumeItem{Optimized database queries and caching strategies with \textbf{Redis}, reducing latency by 25\% on critical paths.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes} with \textbf{Helm}, enabling scalable releases.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, enforcing quality and security gates.}
  \resumeItem{Integrated AI capabilities leveraging \textbf{Spring AI} and \textbf{AWS Bedrock}, enhancing internal productivity workflows.}
  \resumeItem{\textit{Environment: Java, Spring Boot, REST, Kafka, Spring Security, OAuth2/OIDC, JWT, React, Angular, TypeScript, Redis, Docker, Kubernetes, Jenkins, GitHub Actions, AWS (EKS, S3, RDS, SQS/SNS).}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed scalable backend services using \textbf{Java} and \textbf{Kotlin}, improving API reliability and operational efficiency.}
  \resumeItem{Implemented \textbf{REST} and \textbf{gRPC} APIs for internal and external integrations, ensuring consistent contract adherence.}
  \resumeItem{Built event-driven architectures using \textbf{Kafka}, improving decoupling and throughput of distributed systems.}
  \resumeItem{Optimized data storage and retrieval with \textbf{DynamoDB} and \textbf{Aurora PostgreSQL}, enhancing query performance.}
  \resumeItem{Reduced latency by 30\% using \textbf{Redis} caching for high-demand data access patterns.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed on \textbf{EKS/ECS}, improving deployment agility.}
  \resumeItem{Provisioned infrastructure using \textbf{Terraform} and \textbf{CloudFormation}, ensuring consistent environment setups.}
  \resumeItem{Implemented observability with \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling proactive monitoring and alerting.}
  \resumeItem{Delivered frontend modules with \textbf{Angular} and \textbf{React}, enhancing operational UI responsiveness.}
  \resumeItem{\textit{Environment: Java, Kotlin, REST, gRPC, Kafka, AWS (EKS, ECS, Lambda, DynamoDB, Aurora, S3), Docker, Kubernetes, Terraform, CloudFormation, Angular, React, TypeScript, OpenTelemetry.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services with \textbf{Java} and \textbf{Spring Boot}, delivering scalable and reusable API modules.}
  \resumeItem{Designed and maintained \textbf{RESTful} APIs with \textbf{OpenAPI} specifications, ensuring consistent validation and versioning.}
  \resumeItem{Implemented secure access controls using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT} for enterprise compliance.}
  \resumeItem{Built frontend components using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, improving user experience and modularity.}
  \resumeItem{Managed asynchronous processing with \textbf{Kafka}, improving system reliability through retry and dead-letter queue patterns.}
  \resumeItem{Optimized database performance using \textbf{Hibernate/JPA} and indexing on \textbf{PostgreSQL} and \textbf{MySQL}.}
  \resumeItem{Improved response times by 25\% through \textbf{Redis} caching and efficient data access patterns.}
  \resumeItem{Containerized microservices using \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling environment-based configuration.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing code quality standards.}
  \resumeItem{\textit{Environment: Java, Spring Boot, REST, OpenAPI, Spring Security, OAuth2/OIDC, JWT, Angular, React, TypeScript, Kafka, Hibernate/JPA, PostgreSQL, MySQL, Redis, Docker, Kubernetes, Jenkins, Azure DevOps.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, delivering clean, reusable components for web applications.}
  \resumeItem{Built \textbf{RESTful} APIs and documented endpoints using \textbf{Swagger} to standardize integration interfaces.}
  \resumeItem{Created frontend features with \textbf{Angular} and \textbf{React}, enhancing usability and modular design.}
  \resumeItem{Implemented scheduled workflows using \textbf{Spring Scheduling} and \textbf{Quartz}, improving operational automation.}
  \resumeItem{Optimized database queries and indexing using \textbf{Hibernate/JPA} to improve performance.}
  \resumeItem{Standardized build processes with \textbf{Maven} and \textbf{Gradle}, and managed CI pipelines using \textbf{Jenkins}.}
  \resumeItem{Containerized development and test environments with \textbf{Docker}, streamlining deployment cycles.}
  \resumeItem{Supported cloud deployments on \textbf{AWS} infrastructure, ensuring scalable and reliable hosting.}
  \resumeItem{Enhanced test coverage using \textbf{JUnit} and \textbf{Mockito}, improving release stability.}
  \resumeItem{\textit{Environment: Java, Spring Boot, REST, Swagger, Angular, React, Hibernate/JPA, Maven, Gradle, Jenkins, Docker, AWS (EC2, S3, RDS).}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}