\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Deliver robust full stack solutions leveraging \textbf{TypeScript} with modern \textbf{React} and \textbf{Angular} frameworks, focusing on modular architecture and performance optimization.}
  \resumeItem{Design scalable backend services with API-driven patterns, integrating ERP systems using synchronous and asynchronous data processing strategies.}
  \resumeItem{Optimize large datasets through pagination, filtering, caching, and query tuning on \textbf{PostgreSQL}, ensuring high performance and reliability.}
  \resumeItem{Drive integration efforts using Apache NiFi and explore event-driven alternatives to enhance data flow and system responsiveness.}
  \resumeItem{Apply strict code review discipline alongside \textbf{GitHub Copilot} to maintain secure, clean, and maintainable architecture with high-quality automated testing coverage.}
  \resumeItem{Own end-to-end quality in fast-paced environments, emphasizing scalable system design, performance tuning, and continuous integration/deployment practices.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Frontend:} & TypeScript, React (Hooks), Angular, Modular architecture, Performance optimization (LCP, FCP), RxJS, NgRx \\
\textbf{Backend \& API:} & API-driven architecture, ERP integrations, Synchronous and asynchronous processing, REST, gRPC, ASP.NET Core Web API \\
\textbf{Databases:} & PostgreSQL, Query optimization, Indexing strategies, Redis caching \\
\textbf{Integration \& Messaging:} & Apache NiFi, Kafka, AWS SQS/SNS, Event-driven architectures, Asynchronous workflows \\
\textbf{DevOps \& CI/CD:} & GitHub Copilot, Automated testing (unit, integration, regression), Jenkins, GitHub Actions, SonarQube, Docker, Kubernetes \\
\textbf{Security \& Quality:} & Secure coding practices, Code reviews, OAuth2/OIDC, JWT, Spring Security, mTLS \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led development of scalable backend services with \textbf{API-driven} design and ERP integration patterns, improving system modularity and maintainability.}
  \resumeItem{Implemented synchronous and asynchronous data processing workflows, enhancing throughput and reliability across distributed systems.}
  \resumeItem{Optimized large dataset handling using pagination, filtering, caching with \textbf{Redis}, and query tuning on \textbf{PostgreSQL}, reducing latency by 30\%.}
  \resumeItem{Developed performant frontend modules using \textbf{TypeScript}, \textbf{React (Hooks)}, and \textbf{Angular} with modular architecture and state management.}
  \resumeItem{Integrated \textbf{Apache NiFi} for data ingestion and explored event-driven alternatives to streamline integration layers.}
  \resumeItem{Enforced strict code review discipline combined with \textbf{GitHub Copilot} assistance to ensure secure, clean, and maintainable codebases.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{GitHub Actions}, achieving 85\% automated test coverage and reducing deployment errors.}
  \resumeItem{Implemented observability using \textbf{OpenTelemetry} and monitoring with \textbf{CloudWatch} to proactively diagnose and resolve performance bottlenecks.}
  \resumeItem{\textit{Environment: Java, Spring Boot, REST, gRPC, C\#, ASP.NET Core Web API, Apache NiFi, Kafka, AWS (EKS, S3, RDS, SQS/SNS), Docker, Kubernetes, Helm, Jenkins, GitHub Actions, Angular, React, TypeScript, Redis, PostgreSQL.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and implemented API-first backend services with ERP integration capabilities, ensuring consistent synchronous and asynchronous data flows.}
  \resumeItem{Improved data processing efficiency by applying query optimization and indexing strategies on \textbf{PostgreSQL} and caching hot data with \textbf{Redis}.}
  \resumeItem{Developed frontend components using \textbf{TypeScript} with \textbf{Angular} and \textbf{React}, focusing on modular design and performance metrics such as LCP and FCP.}
  \resumeItem{Built event-driven processing pipelines using \textbf{Kafka} and AWS messaging services to decouple system components and enhance scalability.}
  \resumeItem{Integrated secure authentication and authorization mechanisms using OAuth2/OIDC and JWT to protect APIs and data flows.}
  \resumeItem{Automated testing and CI/CD pipelines with \textbf{JUnit}, \textbf{Mockito}, and \textbf{GitHub Actions}, improving deployment reliability and functional coverage.}
  \resumeItem{Containerized applications using \textbf{Docker} and orchestrated deployments with \textbf{Kubernetes}, enabling repeatable and scalable releases.}
  \resumeItem{Monitored system health and performance using \textbf{OpenTelemetry} and \textbf{CloudWatch}, reducing incident response times by 20\%.}
  \resumeItem{\textit{Environment: Java, Kotlin, Go, REST, gRPC, Kafka, AWS (EKS, S3, RDS, DynamoDB, SQS/SNS), Docker, Kubernetes, Terraform, Angular, React, TypeScript, PostgreSQL, Redis.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services with \textbf{Java} and \textbf{Spring Boot} focusing on API-driven ERP integrations and modular architecture for scalability.}
  \resumeItem{Implemented synchronous and asynchronous processing using \textbf{Kafka} to improve reliability and throughput of enterprise workflows.}
  \resumeItem{Optimized database queries and applied indexing strategies on \textbf{PostgreSQL} and \textbf{MySQL}, enhancing response times by 25\%.}
  \resumeItem{Built frontend modules with \textbf{TypeScript}, \textbf{Angular}, and \textbf{React (Hooks)}, emphasizing performance optimization and modular UI components.}
  \resumeItem{Created integration endpoints using \textbf{C\#} and \textbf{ASP.NET Core Web API} to enable seamless partner and internal orchestration.}
  \resumeItem{Implemented caching strategies using \textbf{Redis} to reduce database load and improve p95 latency on critical paths.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing quality gates and automated test execution for high reliability.}
  \resumeItem{Applied secure coding standards with OAuth2/OIDC and JWT, aligning with enterprise RBAC and compliance requirements.}
  \resumeItem{\textit{Environment: Java, Spring Boot, REST, OpenAPI, Angular, React, TypeScript, Kafka, C\#, ASP.NET Core, PostgreSQL, MySQL, Redis, Docker, Kubernetes, Jenkins, Azure DevOps.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Delivered backend services using \textbf{Java} and \textbf{Spring Boot} with modular design and API-first principles for internal tooling applications.}
  \resumeItem{Built frontend features using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, focusing on reusable components and UI performance improvements.}
  \resumeItem{Optimized database access with query tuning and indexing strategies on \textbf{PostgreSQL}, improving throughput and reducing contention.}
  \resumeItem{Implemented scheduled and asynchronous processing using \textbf{Spring Scheduling} and message-driven patterns to improve workflow efficiency.}
  \resumeItem{Standardized builds and deployments using \textbf{Maven}, \textbf{Jenkins}, and containerized environments with \textbf{Docker} for consistent releases.}
  \resumeItem{Enhanced automated testing coverage using \textbf{JUnit} and \textbf{Mockito}, improving release stability and defect detection.}
  \resumeItem{Supported cloud deployments on \textbf{AWS} with secure and scalable infrastructure for application hosting and storage.}
  \resumeItem{Collaborated in Agile teams to deliver high-quality features with focus on clean architecture and maintainability.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Angular, React, TypeScript, PostgreSQL, Docker, Jenkins, AWS, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}