\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Experienced \textbf{Senior Software Engineer} skilled in designing, developing, testing, and deploying end-to-end \textbf{web applications} with strong expertise in \textbf{Ruby on Rails, Java}, and database systems.}
    \resumeItem{Proficient in application architecture, \textbf{Object-Oriented Design} patterns, and integrating complex systems using \textbf{GQL/REST APIs}, messaging, and ETL pipelines for reliable data flow.}
    \resumeItem{Skilled in analyzing and solving cross-functional business problems by crafting alternative technical solutions ensuring scalability and maintainability.}
    \resumeItem{Experienced in implementing \textbf{automated testing frameworks} to uphold quality and reduce defects, improving software reliability and performance.}
    \resumeItem{Strong ability to integrate applications with \textbf{third-party platforms}, internal services, and developed reusable components across technology stacks, ensuring seamless interoperability.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Frameworks:} & Ruby on Rails, Java, Spring Boot, JavaScript, TypeScript, Python, Node.js \\
                \textbf{Web Technologies \& APIs:} & RESTful APIs, GraphQL, ETL pipelines, Messaging (Kafka, RabbitMQ), GQL \\
                \textbf{Databases:} & MySQL, PostgreSQL, MongoDB, Oracle, Redis \\
                \textbf{Testing \& Automation:} & JUnit, Mockito, Selenium, Postman, Automated Testing Frameworks \\
                \textbf{Cloud \& Deployment:} & AWS (EC2, ECS, S3, API Gateway), Docker, Kubernetes, Jenkins, CI/CD Pipelines \\
                \textbf{Architectures \& Patterns:} & Microservices Architecture, Object-Oriented Design, Event-Driven Systems \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Developed scalable microservices with \textbf{Java} and \textbf{Spring Boot}, reducing downtime by 25\% and improving application reliability in cloud environments.}
        \resumeItem{Integrated \textbf{GraphQL} APIs via \textbf{AWS API Gateway}, decreasing client response times by 35\% and enhancing server efficiency under high traffic.}
        \resumeItem{Engineered asynchronous message-driven workflows using messaging frameworks, enhancing data processing speed by 30\% within distributed systems.}
        \resumeItem{Automated unit and integration tests using \textbf{JUnit} and \textbf{Mockito}, increasing code coverage beyond 98\% and improving release stability.}
        \resumeItem{Optimized complex \textbf{PostgreSQL} queries achieving a 20\% boost in database response and data retrieval efficiency.}
        \resumeItem{Implemented \textbf{CI/CD} pipelines with \textbf{Jenkins, Docker}, and AWS services, doubling deployment frequency and reducing manual release errors.}
        \resumeItem{Adapted \textbf{Object-Oriented Design} principles to error handling and architectural guidelines, ensuring maintainable and scalable application codebases.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Designed and delivered core banking services with \textbf{Java Spring Boot} in a microservices setup, improving transaction throughput by 25\%.}
        \resumeItem{Developed frontend components using \textbf{React} and integrated with backend microservices, elevating user satisfaction and platform responsiveness.}
        \resumeItem{Engineered real-time cash position system middleware in \textbf{Node.js}, increasing processing speed by 30\% with robust asynchronous event handling.}
        \resumeItem{Implemented \textbf{Kafka}-based event-driven architecture managing over 10,000 transactions per second, improving system scalability and fault tolerance.}
        \resumeItem{Created Grafana dashboards using \textbf{Prometheus} metrics, enhancing system monitoring and proactive issue detection.}
        \resumeItem{Implemented OAuth2 and JWT for secure authentication frameworks, reducing security incidents by 40\% and enhancing data protection.}
        \resumeItem{Configured Jenkins pipelines integrating \textbf{SVN} for continuous delivery, reducing build and deploy time by 30\%.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed high-performance \textbf{Java Spring MVC} applications for supply chain management, increasing data processing speed by 20\%.}
        \resumeItem{Built and maintained \textbf{RESTful APIs} using \textbf{Node.js} and \textbf{Express.js}, improving external integrations and platform extensibility by 30\%.}
        \resumeItem{Implemented automated testing with \textbf{JUnit} and \textbf{Postman}, achieving application reliability metrics exceeding 95\% in production.}
        \resumeItem{Migrated legacy systems to \textbf{AWS}, reducing operating costs by 20\% and improving cloud service scalability.}
        \resumeItem{Optimized \textbf{DynamoDB} queries, reducing data access latency by 15\%, enhancing overall application responsiveness.}
        \resumeItem{Developed Linux shell scripts to monitor system performance, reducing incident response time by 30\%.}
        \resumeItem{Enhanced CI/CD workflows using \textbf{GitHub Actions}, accelerating deployment time by 40\% and improving software delivery.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-driven Document Query System} | Python, LangChain, OpenAI API, Docker}{ }
        \resumeItemListStart
            \resumeItem{Implemented a multi-document NLP querying system using \textbf{RAG} architecture, improving response accuracy by 40\% with contextual AI insights.}
            \resumeItem{Containerized the application using \textbf{Docker} for easy deployment and scalability, reducing deployment time by 50\%.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Microservices based ETL Pipeline} | Java, Spring Boot, Kafka, MySQL}{ }
        \resumeItemListStart
            \resumeItem{Designed a robust ETL pipeline using \textbf{Java Spring Boot} and \textbf{Kafka} for messaging, improving data ingestion speed by 35\%.}
            \resumeItem{Integrated \textbf{MySQL} for persistence and implemented automated tests, increasing data integrity and testing coverage by 30\%.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{GraphQL API Gateway} | AWS API Gateway, GraphQL, JavaScript}{ }
        \resumeItemListStart
            \resumeItem{Developed a \textbf{GraphQL} API gateway on \textbf{AWS}, reducing server loads by 30\% and improving frontend query efficiency by 25\%.}
            \resumeItem{Implemented caching and optimized resolvers, cutting average API response times by 35\% and enhancing user experience during peak loads.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}