\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{\textbf{Software engineer} with \textbf{5+ years} in designing, developing, and deploying scalable, secure software solutions leveraging \textbf{Java}, \textbf{SQL}, and \textbf{cloud environments}.}
    \resumeItem{Experienced in integrating automation and monitoring within cloud systems, working efficiently in fast-paced Agile and DevOps teams across global locations.}
    \resumeItem{Proficient in end-to-end system ownership from architecture design to deployment, including embedding AI technologies to optimize execution and impact.}
    \resumeItem{Skilled in relational and NoSQL database management, advanced data structures, and algorithms, with a strong focus on secure application development and performance tuning.}
    \resumeItem{Familiar with enterprise software landscapes, including \textbf{Oracle ERP} and \textbf{OCI}, and streaming platforms like \textbf{Apache Kafka} for large-scale data processing.}
    \resumeItem{Effective communicator and self-starter, committed to delivering high-quality software solutions with minimal supervision in flexible, remote, and onsite settings.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Frameworks:} & Java (17 \& 21), Object-Oriented Programming, Spring Boot, Spring Cloud, Node.js, Express.js, React.js, Angular \\
                \textbf{Databases \& Querying:} & SQL, PL/SQL, Oracle Database, MongoDB, NoSQL concepts, Elasticsearch, DynamoDB \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, ECS, S3, API Gateway, CodePipeline), Oracle Cloud Infrastructure (OCI), Docker, Kubernetes, Jenkins, Terraform, GitHub Actions \\
                \textbf{Streaming \& Monitoring:} & Apache Kafka, ELK Stack (Elasticsearch, Logstash, Kibana), Prometheus, Grafana, Splunk \\
                \textbf{Testing \& Automation:} & JUnit, Mockito, Selenium, Postman, Cucumber, Karate, Rest Assured \\
                \textbf{Enterprise \& Security:} & Oracle ERP, OAuth2, JWT, Secure software design principles, Agile \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Developed scalable microservices using \textbf{Java}, \textbf{Spring Boot}, and \textbf{Oracle Cloud Infrastructure}, improving uptime by 25\% under Agile processes.}
        \resumeItem{Implemented secure REST APIs integrating with \textbf{Oracle ERP}, reducing response latency by 30\% and improving transaction throughput.}
        \resumeItem{Contributed to automated testing pipelines with \textbf{JUnit} and \textbf{Mockito}, achieving over 98\% test coverage and enhancing software reliability.}
        \resumeItem{Constructed comprehensive \textbf{ELK Stack} dashboards to visualize logs, enabling faster debugging and performance monitoring across distributed systems.}
        \resumeItem{Optimized SQL and \textbf{PL/SQL} queries for enterprise application databases, increasing query efficiency by 20\% and lowering system load.}
        \resumeItem{Led migration to microservices architecture deploying on \textbf{Kubernetes}, enabling 30\% faster deployments and improved scalability.}
        \resumeItem{Integrated \textbf{Apache Kafka} for real-time data streaming, improving event processing capacity by 40\% and reducing data latency.}
        \resumeItem{Automated CI/CD workflows using \textbf{Jenkins} and \textbf{Docker}, increasing deployment frequency by 50\% and reducing manual intervention.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented core banking microservices using \textbf{Java}, \textbf{Spring Boot}, and \textbf{Oracle Database}, improving transaction reliability by 35\%.}
        \resumeItem{Built frontend components with \textbf{Angular} and integrated backends, enhancing user experience and reducing page load times by 25\%.}
        \resumeItem{Developed real-time data pipelines with \textbf{Apache Kafka}, handling over 10,000 transactions per second with high availability.}
        \resumeItem{Created detailed system monitoring using \textbf{Grafana} and \textbf{Prometheus}, enabling proactive performance tuning and reducing downtime by 20\%.}
        \resumeItem{Strengthened security by integrating \textbf{OAuth2} and \textbf{JWT} authentication, decreasing security incidents by 40\%.}
        \resumeItem{Enhanced database access via optimized \textbf{PL/SQL} queries and batch processes, raising throughput by 18\%.}
        \resumeItem{Improved CI/CD efficiencies by integrating \textbf{SVN} and \textbf{Jenkins}, decreasing deployment time by 30\% and elevating release cadence.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring MVC}, improving supply chain data processing speed by 25\%.}
        \resumeItem{Built and secured REST APIs with \textbf{Node.js} supporting NoSQL databases like \textbf{MongoDB}, increasing integration capabilities by 30\%.}
        \resumeItem{Implemented \textbf{PL/SQL} based data procedures and optimized queries for enhanced Oracle DB performance, reducing latency by 15\%.}
        \resumeItem{Scripted Linux Shell tools for real-time system monitoring, accelerating issue detection and resolution by 30\%.}
        \resumeItem{Migrated legacy systems to \textbf{AWS} cloud infrastructure, cutting operational costs by 20\% and improving scalability.}
        \resumeItem{Enhanced CI/CD pipelines using \textbf{GitHub Actions}, increasing deployment speed by 40\% and ensuring reliable rollouts.}
        \resumeItem{Supported Agile team practices to deliver incremental features faster, improving project delivery speed by 25\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-powered Document Query System} $|$ Java, Spring Boot, Elasticsearch, Redis, Docker}{}
        \resumeItemListStart
            \resumeItem{Developed a natural language querying tool using AI embeddings and vector search with Redis, enabling dynamic retrieval from large document sets.}
            \resumeItem{Integrated \textbf{Elasticsearch} for advanced indexing and search capabilities, improving query response times by 35\% in a scalable architecture.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Real-time Streaming Data Platform} $|$ Apache Kafka, Kubernetes, Java, MongoDB, ELK Stack}{}
        \resumeItemListStart
            \resumeItem{Engineered an end-to-end streaming data pipeline with \textbf{Kafka} and \textbf{MongoDB}, achieving reliable data ingestion at 10,000+ TPS.}
            \resumeItem{Built monitoring dashboards with \textbf{Kibana} and \textbf{Logstash}, enabling comprehensive observability and lowering incident resolution times by 25\%.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Secure Cloud-native Banking Backend} $|$ Java, Spring Boot, Oracle DB, OCI, Jenkins}{}
        \resumeItemListStart
            \resumeItem{Created a secure banking backend utilizing \textbf{Oracle Cloud Infrastructure}, implementing PL/SQL procedures for high transaction throughput with 99.9\% uptime.}
            \resumeItem{Automated build and deployment via \textbf{Jenkins} and Docker containers, reducing deployment time by 40\% in a cloud-native environment.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}