\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Software engineer with 5+ years of expertise delivering scalable, high-quality software incorporating advanced data structures, algorithms, and cloud technologies.}
    \resumeItem{Proficient in \textbf{Java} development, deep knowledge of SQL and NoSQL databases including \textbf{MongoDB}, and hands-on experience with \textbf{Kafka} for streaming data pipelines.}
    \resumeItem{Experienced in building and deploying cloud-native applications with monitoring tools, \textbf{ELK Stack}, and Agile DevOps practices, optimizing system performance and automation.}
    \resumeItem{Strong collaborator with excellent written and verbal communication skills, capable of managing end-to-end software delivery in global, hybrid team environments.}
    \resumeItem{Skilled with enterprise-grade software, including Oracle ERP and \textbf{cloud infrastructure}, delivering secure, maintainable, and robust solutions across varying domains.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Java (17 \& 21), Python, SQL, PL/SQL, JavaScript, TypeScript, Shell Scripting, Kotlin, Go \\
                \textbf{Frameworks \& Backend:} & Spring Boot, Spring Cloud, Node.js, Express.js, Hibernate, JPA, GraphQL, RESTful APIs \\
                \textbf{Databases \& Streaming:} & Oracle Database, MongoDB, PostgreSQL, DynamoDB, Kafka, Redis, Cassandra \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, ECS, S3, API Gateway, CodePipeline), Azure, Docker, Kubernetes, Jenkins, Terraform \\
                \textbf{Monitoring \& Analytics:} & ELK Stack (Elasticsearch, Logstash, Kibana), Grafana, Prometheus, AppDynamics, Splunk \\
                \textbf{Testing \& Methodologies:} & JUnit, Mockito, Selenium, Postman, Agile (Scrum/Kanban), CI/CD pipelines \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Developed microservices using \textbf{Java}, \textbf{Spring Boot}, deployed on \textbf{AWS ECS}, improving system scalability by 30\%.}
        \resumeItem{Integrated \textbf{Kafka} event streams to build robust data pipelines, handling over 10,000 events per second with high reliability.}
        \resumeItem{Implemented monitoring solutions with \textbf{ELK Stack}, enhancing issue detection and system visibility, reducing incident response time by 40\%.}
        \resumeItem{Optimized \textbf{MongoDB} queries and schema design, accelerating data retrievals by 25\% for high-throughput applications.}
        \resumeItem{Collaborated on Agile teams delivering full software lifecycle from design to deployment using CI/CD on \textbf{Jenkins} and \textbf{Docker}.}
        \resumeItem{Developed automated unit and integration tests with \textbf{JUnit} and \textbf{Mockito}, achieving over 95\% code coverage and stable releases.}
        \resumeItem{Enhanced enterprise application features by integrating \textbf{Oracle ERP} modules, improving core transactional data accuracy by 20\%.}
        \resumeItem{Reduced server response times by 35\% through GraphQL API integration on \textbf{AWS API Gateway} for optimized client-server communication.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Built core banking services using \textbf{Java}, \textbf{Spring Boot} within a microservices architecture enhancing transaction throughput by 30\%.}
        \resumeItem{Designed and implemented \textbf{Kafka}-powered event-driven architecture, managing 10,000+ transactions per second reliably and securely.}
        \resumeItem{Developed real-time monitoring dashboards with \textbf{Grafana} and \textbf{Prometheus}, improving system observability and reducing downtime by 25\%.}
        \resumeItem{Enhanced security via \textbf{OAuth2} and \textbf{JWT} integrations, decreasing vulnerability errors by 40\% across enterprise applications.}
        \resumeItem{Automated deployment pipelines using \textbf{Jenkins} integrated with \textbf{SVN}, accelerating release cycles by 30\%.}
        \resumeItem{Improved database efficiency by optimizing \textbf{Oracle PL/SQL} procedures and queries with a focus on transactional integrity and speed.}
        \resumeItem{Led transition to Agile DevOps practices, increasing team productivity and delivering iterative features with higher reliability.}
        \resumeItem{Orchestrated \textbf{ELK Stack} logging solutions, significantly enhancing fault diagnosis and troubleshooting effectiveness.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Java} and \textbf{Spring MVC} based supply chain applications enhancing data processing efficiency by 20\%.}
        \resumeItem{Developed scalable \textbf{Node.js} \textbf{RESTful APIs}, enabling 30\% more integrations with third-party platforms efficiently.}
        \resumeItem{Migrated legacy systems to \textbf{AWS} with cloud-native solutions, achieving 20\% cost reductions and enhanced scalability.}
        \resumeItem{Optimized \textbf{DynamoDB} NoSQL storage to reduce data latency by 15\%, improving user experience and system responsiveness.}
        \resumeItem{Implemented Linux shell scripting tools for real-time system monitoring, decreasing system downtime reaction times by 30\%.}
        \resumeItem{Structured CI/CD workflows with \textbf{GitHub Actions}, resulting in a 40\% faster product delivery cycle.}
        \resumeItem{Contributed to Agile team practices, improving project delivery efficiency by 25\% with iterative development and continuous feedback.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-Powered Document Search} $|$ Python, LangChain, Elasticsearch, OpenAI API, Docker}{ }
        \resumeItemListStart
            \resumeItem{Developed an AI-driven search engine utilizing RAG, embedding semantic vectors in \textbf{Elasticsearch} for precise PDF content query results.}
            \resumeItem{Containerized with \textbf{Docker}; automated CI/CD pipelines via GitHub Actions to ensure reliable and scalable deployment.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Streaming Data Processing Platform} $|$ Apache Kafka, Kubernetes, Neo4j, Docker}{ }
        \resumeItemListStart
            \resumeItem{Implemented a distributed graph data analytics system using \textbf{Kafka} streams with \textbf{Neo4j} for real-time insights handling 1,000+ concurrent events.}
            \resumeItem{Orchestrated deployment on \textbf{Kubernetes} clusters with load balancing, ensuring high availability and fault tolerance.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Cloud-Native Banking APIs} $|$ Java, Spring Boot, MongoDB, AWS, ELK Stack}{ }
        \resumeItemListStart
            \resumeItem{Created secure, scalable microservices for banking APIs leveraging \textbf{Spring Boot} and \textbf{MongoDB}, improving transaction reliability by 30\%.}
            \resumeItem{Integrated monitoring with \textbf{ELK Stack}, enhancing operational insights and reducing mean time to recovery by 40\%.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}