\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Experienced software engineer with 5+ years developing scalable backend systems primarily in \textbf{Python} and \textbf{Java}, focusing on REST API design and optimization.} \vspace{-3pt}
    \resumeItem{Skilled in full-stack development using \textbf{React} and \textbf{TypeScript}, crafting intuitive UIs to simplify complex AI and data workflows for users.} \vspace{-3pt}
    \resumeItem{Proficient in designing no-code platforms and developer APIs enabling efficient automation of enterprise processes and dialogue systems.} \vspace{-3pt}
    \resumeItem{Adept at Agile methodologies, test-driven development, and implementing secure communication protocols to ensure system reliability and safety.} \vspace{-3pt}
    \resumeItem{Strong collaborator and mentor with experience guiding junior engineers and driving technical best practices across teams for maintainable codebases.} \vspace{-3pt}
    \resumeItem{Passionate about AI integration, performance optimization, and delivering high-quality software for evolving customer service automation platforms.} \vspace{-3pt}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, Java, JavaScript, TypeScript, Go, SQL, Shell Scripting, C++, Kotlin, HTML, CSS \\
                \textbf{Frameworks \& Backend:} & Django, Flask, Spring Boot, Node.js, Express.js, React.js, Next.js, Gin, REST APIs, WebSockets \\
                \textbf{Frontend \& Styling:} & React.js, Next.js, Redux, Tailwind CSS, styled-components, Material UI \\
                \textbf{Testing \& Automation:} & Pytest, JUnit, Mockito, Jest, React Testing Library, Playwright, Postman \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, ECS, API Gateway, CodePipeline), Docker, Kubernetes, Jenkins, GitHub Actions, Terraform \\
                \textbf{Databases \& Messaging:} & PostgreSQL, MongoDB, Redis, Kafka, DynamoDB, Neo4j \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Designed and developed scalable RESTful APIs using \textbf{Python} and \textbf{Spring Boot}, improving service response times by 30\% for client-facing applications.}
        \resumeItem{Implemented \textbf{React} and \textbf{Next.js}-based UIs for complex data visualization, enhancing user interactions and reducing query time by 35\%.}
        \resumeItem{Led migration to low-code platforms enabling non-technical users to configure dialogue systems, boosting client setup efficiency by over 25\%.}
        \resumeItem{Authored reusable API components with secure \textbf{WebSocket} integration, achieving real-time communication enhancements and 20\% performance gains.}
        \resumeItem{Collaborated with cross-functional teams to define technical standards, increasing adherence to coding best practices and reducing bugs by 40\%.}
        \resumeItem{Mentored junior engineers on \textbf{API design} and \textbf{React} best practices, accelerating onboarding and improving overall code quality.}
        \resumeItem{Optimized backend workflows and database queries in \textbf{PostgreSQL} and \textbf{Redis}, improving system throughput by 25\% during peak loads.}
        \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{AWS CodePipeline}, increasing deployment frequency by 50\% and reducing rollback incidents.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Developed backend services with \textbf{Python} and \textbf{Java Spring Boot}, delivering secure, scalable customer service APIs improving uptime by 20\%.}
        \resumeItem{Created frontend customer tools using \textbf{React} and \textbf{Tailwind CSS}, simplifying UI complexity and raising usability scores by 30\%.}
        \resumeItem{Automated repetitive tasks with \textbf{Python}, saving 20+ hours weekly and accelerating development cycles.}
        \resumeItem{Built event-driven microservices using \textbf{Kafka} securing transaction performance over 10,000 TPS, ensuring consistent service delivery.}
        \resumeItem{Implemented OAuth2 and JWT-based security protocols, reducing authentication-related issues by 40\% and enhancing user data protection.}
        \resumeItem{Enhanced monitoring through \textbf{Grafana} dashboards and \textbf{Prometheus}, increasing observability and reducing incident response time by 25\%.}
        \resumeItem{Streamlined CI/CD with \textbf{Jenkins} and SVN integration, decreasing release time by 30\% and increasing build success rates.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Python} and \textbf{Node.js}-based REST APIs, improving third-party API integration and expanding functionality by 30\%.}
        \resumeItem{Led migration of legacy systems to \textbf{AWS}, reducing infrastructure costs by 20\% and improving scalability.}
        \resumeItem{Optimized \textbf{DynamoDB} queries, reducing latency by 15\% and enhancing user data retrieval speeds.}
        \resumeItem{Automated monitoring using \textbf{Shell scripting} for system metrics, cutting response times to failures by 30\%.}
        \resumeItem{Pioneered Agile Scrum adoption, increasing team productivity by 25\% and improving project delivery cadence.}
        \resumeItem{Implemented testing automation with \textbf{JUnit} and \textbf{Postman}, raising application stability to above 95\%.}
        \resumeItem{Accelerated deployment workflows with \textbf{GitHub Actions}, raising deployment frequency by 40\% and minimizing errors.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-Powered Dialogue Configuration Platform} $|$ Python, React, Next.js, Tailwind CSS, WebSockets}{ }
        \resumeItemListStart
            \resumeItem{Engineered a low-code platform enabling non-technical users to visually configure dialogue agents, increasing setup speed by 30\%.}
            \resumeItem{Integrated real-time interaction APIs with \textbf{WebSocket} support to enhance user experience and responsiveness by 25\%.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Retrieval-Augmented Generation Chatbot} $|$ Python, LangChain, OpenAI API, FAISS, Streamlit}{ }
        \resumeItemListStart
            \resumeItem{Designed an AI chatbot leveraging \textbf{RAG} techniques with document indexing for contextual answers, improving query accuracy by 40\%.}
            \resumeItem{Containerized and deployed the solution using \textbf{Docker} with automated CI/CD pipelines via \textbf{GitHub Actions} to streamline releases.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Scalable Customer Support Portal} $|$ React, TypeScript, Python, Django, REST API}{ }
        \resumeItemListStart
            \resumeItem{Built a customer support portal with intuitive React interfaces and Python backend APIs, increasing customer satisfaction scores by 20\%.}
            \resumeItem{Implemented comprehensive unit and integration tests using \textbf{Jest} and \textbf{Pytest}, raising code coverage to 95\%.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}