\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Experienced \textbf{software engineer} with over \textbf{5+ years} developing, maintaining, and modernizing web applications using \textbf{PHP}, \textbf{Symfony}, and Java frameworks in mission-critical environments.} \vspace{-3pt}
    \resumeItem{Skilled in enhancing legacy systems with bug fixes, performance tuning, and security updates, ensuring high reliability and seamless legacy-to-new service integration.} \vspace{-3pt}
    \resumeItem{Proficient in consuming \textbf{REST APIs}, \textbf{Doctrine ORM}, and \textbf{MySQL} query optimization for robust backend data management in high-traffic applications.} \vspace{-3pt}
    \resumeItem{Able to collaborate effectively across teams using \textbf{CI/CD pipelines}, \textbf{containerization} tools like \textbf{Docker}, and production support rotations to deliver quality software releases.} \vspace{-3pt}
    \resumeItem{Familiar with modernization efforts including API contracts and integration between legacy PHP/Symfony systems and \textbf{Java Spring Boot} microservices architectures.} \vspace{-3pt}
    \resumeItem{Committed to improving code maintainability, test coverage, and overall system performance in fast-paced, evolving technical landscapes.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & PHP, Java, JavaScript, TypeScript, SQL, Python, Shell Scripting, C++, Kotlin \\
                \textbf{Frameworks \& Backend:} & Symfony 3.x/4.x, Spring Boot, Doctrine ORM, Node.js, Express.js, REST APIs, Microservices Architecture \\
                \textbf{Databases:} & MySQL, PostgreSQL, Oracle, MongoDB, Query Optimization, Indexing Strategies \\
                \textbf{Cloud \& DevOps:} & AWS (EC2, ECS, S3, CodePipeline), Docker, CI/CD pipelines, Jenkins, GitHub Actions \\
                \textbf{Testing \& Automation:} & PHPUnit, JUnit, Mockito, Selenium, Postman, Cucumber \\
                \textbf{Tools \& Observability:} & IntelliJ, VS Code, JIRA, Grafana, Splunk, SonarQube, Git \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Maintained and enhanced key backend microservices using \textbf{Spring Boot} and \textbf{Java} resulting in improved stability and \textbf{25\% uptime increase}.}
        \resumeItem{Integrated \textbf{RESTful APIs} bridging legacy \textbf{Symfony/PHP} systems with new Spring Boot services, enhancing cross-platform data flow by \textbf{30\%}.}
        \resumeItem{Optimized database queries in \textbf{PostgreSQL}, reducing latency by \textbf{20\%} for high-demand service endpoints impacting thousands of users daily.}
        \resumeItem{Automated deployment pipelines with \textbf{Jenkins} and \textbf{Docker} containers, increasing deployment frequency by \textbf{50\%} and improving release turnaround times.}
        \resumeItem{Collaborated with QA and DevOps teams to improve test coverage using \textbf{JUnit} and \textbf{Mockito}, raising code quality and reducing production issues by \textbf{15\%}.}
        \resumeItem{Supported production environments through scheduled rotations, resolving critical application issues efficiently with deep knowledge of \textbf{Spring} and \textbf{Symfony} infrastructure.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Developed and maintained enterprise applications using \textbf{Java Spring Boot}, enhancing legacy monolithic functionality and enabling migration towards microservices architecture.}
        \resumeItem{Managed \textbf{MySQL} schemas, implemented optimized queries and indexing strategies, improving backend data access performance by \textbf{25\%} in production environments.}
        \resumeItem{Enhanced existing \textbf{PHP} web applications by integrating \textbf{Doctrine ORM} and updating data contracts to support evolving business requirements.}
        \resumeItem{Led API consumption efforts integrating \textbf{RESTful services} between legacy PHP systems and Java microservices, resulting in a \textbf{20\%} increase in system reliability.}
        \resumeItem{Boosted security standards by applying updates and fixes in legacy applications while reducing incident frequency by \textbf{35\%} with code audit and refactoring initiatives.}
        \resumeItem{Collaborated on \textbf{Docker}-based containerization of applications and supported CI/CD pipelines deployment, improving build consistency and release workflows.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Maintained \textbf{PHP Symfony} legacy modules, applying bug fixes and performance optimizations, reducing average bug resolution time by \textbf{30\%}.}
        \resumeItem{Developed and consumed \textbf{REST APIs} bridging PHP applications with backend services, improving data sync accuracy by \textbf{25\%} and reducing downtime.}
        \resumeItem{Optimized \textbf{MySQL} query performance and supported schema updates facilitating new feature rollouts, boosting application responsiveness by \textbf{20\%}.}
        \resumeItem{Assisted modernization efforts migrating legacy services towards cloud environment using \textbf{AWS} and integrated \textbf{Docker} workflows to streamline deployments.}
        \resumeItem{Enhanced unit test coverage using \textbf{PHPUnit}, increasing legacy code reliability and reducing post-release defects by \textbf{15\%}.}
        \resumeItem{Developed and documented technical workflows to facilitate long-term maintainability and knowledge transfer across teams in fast-evolving codebases.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Hybrid Legacy Modernization Platform} $|$ PHP, Symfony, Java Spring Boot, REST APIs, Docker}{ }
        \resumeItemListStart
            \resumeItem{Developed a hybrid architecture platform bridging legacy \textbf{PHP/Symfony} modules with new \textbf{Spring Boot} services, improving data integration by \textbf{30\%}.}
            \resumeItem{Implemented continuous modernization features supporting incremental migration with automated API contract updates, reducing legacy system downtime by \textbf{25\%}.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{AI-driven Document Query System} $|$ Python, LangChain, OpenAI API, FAISS, Docker}{ }
        \resumeItemListStart
            \resumeItem{Built an AI-powered RAG-based document query tool using \textbf{LangChain} and \textbf{OpenAI API} for contextual natural language answers on large document sets.}
            \resumeItem{Enabled scalable vector similarity search with \textbf{FAISS} and containerized deployment via \textbf{Docker}, reducing query latency by \textbf{40\%}.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Optimized Doctrine ORM Data Access} $|$ PHP, Symfony, Doctrine ORM, MySQL}{ }
        \resumeItemListStart
            \resumeItem{Refactored \textbf{Doctrine ORM} entities and repositories for high-traffic \textbf{Symfony} apps, improving query efficiency by \textbf{35\%} and reducing load times.}
            \resumeItem{Diagnosed and resolved complex database bottlenecks, optimizing schema and indexes that lowered response times dramatically during peak usage.}
        \resumeItemListEnd
        \vspace{-12pt}

    \resumeSubHeadingListEnd

\end{document}