\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{\textbf{Software engineer} with \textbf{5+ years} of experience in enterprise application development, integration, and reporting using \textbf{C\#}, \textbf{.NET}, \textbf{Java}, and middleware solutions.} \vspace{-3pt}
    \resumeItem{Skilled in designing, developing, and supporting enterprise interfaces and ETL processes leveraging \textbf{SSIS}, \textbf{BizTalk}, and robust SQL scripting for data integration.} \vspace{-3pt}
    \resumeItem{Experienced with \textbf{Primavera P6} and \textbf{Unifier} applications, supporting scheduling, project management, and asset management workflows across diverse business units.} \vspace{-3pt}
    \resumeItem{Proficient in creating dynamic reporting dashboards and analytics using \textbf{Power BI}, \textbf{Oracle Business Intelligence}, and \textbf{SQL Server Reporting Services} for decision support.} \vspace{-3pt}
    \resumeItem{Strong collaborator with an ability to gather requirements and lead cross-functional teams including vendors and technology partners for successful project delivery.} \vspace{-3pt}
    \resumeItem{Possess excellent problem-solving, communication, and project management skills with a focus on quality, safety, and integrity in enterprise technology solutions.} \vspace{-3pt}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Frameworks:} & C\#, .NET, Java, Spring Boot, SSIS, BizTalk, SQL, PL/SQL, Oracle SQL, PowerShell, JavaScript \\
                \textbf{Middleware \& Integration:} & SSIS (SQL Server Integration Services), BizTalk Server, Oracle Data Integrator, RESTful APIs, SOAP Web Services \\
                \textbf{Enterprise Applications:} & Primavera P6, Primavera Unifier, Maximo, ScheduleAnywhere, TEAMS, Oracle Business Intelligence, Microsoft Reporting Services, Power BI \\
                \textbf{Databases:} & Oracle Database, Microsoft SQL Server, PostgreSQL, MySQL \\
                \textbf{Reporting \& Analytics:} & Power BI, Oracle Business Intelligence, SQL Server Reporting Services (SSRS), Data Analytics, SQL queries and optimization \\
                \textbf{Tools \& Environments:} & WebLogic Server, Citrix, Visual Studio, IntelliJ IDEA, Azure DevOps, JIRA, Git, Agile Methodologies \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Developed enterprise interfaces using \textbf{C\#} and \textbf{.NET}, improving data transfer efficiency between Primavera P6 and internal systems by 30\%.}
        \resumeItem{Implemented \textbf{SSIS} packages to automate complex data workflows, reducing manual errors by 25\% in project scheduling data feeds.}
        \resumeItem{Configured reporting dashboards with \textbf{Power BI} to visualize project progress, enhancing stakeholder insights and decision making by 40\%.}
        \resumeItem{Integrated Primavera Unifier with Maximo and ScheduleAnywhere applications via reliable APIs, enabling seamless cross-application data synchronization.}
        \resumeItem{Collaborated with database administrators to optimize \textbf{SQL} queries and implement automated reporting, improving report generation time by 35\%.}
        \resumeItem{Supported deployment and maintenance of applications on \textbf{WebLogic} servers in a Citrix environment, enhancing application reliability and availability.}
        \resumeItem{Coordinated with security teams on access controls and compliance requirements, reducing vulnerabilities and improving audit readiness by 20\%.}
        \resumeItem{Assisted project managers with progress tracking and status reporting for Primavera-related projects to ensure on-time, on-budget delivery.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Java}-based integration solutions for enterprise scheduling systems, improving synchronization accuracy by 30\%.}
        \resumeItem{Built \textbf{BizTalk} orchestrations to facilitate data interchange between scheduling and asset management systems, reducing latency by 25\%.}
        \resumeItem{Designed and implemented SQL Server-based reporting services (SSRS) for project and operational data, improving reporting efficiency by 35\%.}
        \resumeItem{Automated data export/import processes applying \textbf{SSIS} to support Primavera application lifecycle and external vendor data transfers.}
        \resumeItem{Configured application parameters supporting business requirements across multiple deployments, increasing flexibility and reducing configuration errors.}
        \resumeItem{Collaborated with infrastructure and database teams ensuring high availability of applications on Citrix and WebLogic platforms.}
        \resumeItem{Engaged in software change management and version control using Agile methodologies to deliver reliable software changes on schedule.}
        \resumeItem{Maintained strong communication with client teams to clarify user requirements and improve application functionality and support processes.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed core modules in \textbf{Java} and \textbf{Spring MVC} supporting enterprise asset scheduling and project management workflows.}
        \resumeItem{Created RESTful APIs integrating enterprise applications, enhancing data accessibility and reducing manual updates by 30\%.}
        \resumeItem{Implemented SQL and PL/SQL enhancements for reporting and complex analytics covering project schedules and resources utilization.}
        \resumeItem{Participated in migrating legacy scheduling data and interfaces to modern platforms with improved security and performance.}
        \resumeItem{Developed automation scripts reducing manual report generation time by 20\%, improving operational efficiency for business users.}
        \resumeItem{Supported the deployment and testing of application interfaces in Citrix and WebLogic server environments to ensure stability.}
        \resumeItem{Collaborated with QA to implement testing strategies improving software quality and reducing defects by 25\%.}
        \resumeItem{Adopted Agile project methodologies to enhance teamwork efficiency and timely delivery of software components for clients.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-Powered Project Schedule Analysis} $|$ Python, LangChain, OpenAI API, Power BI}{ }
        \resumeItemListStart
            \resumeItem{Developed an AI system analyzing Primavera P6 schedule data via natural language, providing intelligent insights and forecasting project bottlenecks.}
            \resumeItem{Created dynamic visualizations in \textbf{Power BI} combining AI-generated data summaries for enhanced stakeholder decision-making and schedule optimization.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Enterprise Middleware Integration Platform} $|$ C\#, BizTalk, SSIS, SQL Server}{ }
        \resumeItemListStart
            \resumeItem{Designed and implemented middleware using \textbf{BizTalk} and \textbf{SSIS} to integrate Primavera, Maximo, and ScheduleAnywhere systems seamlessly, improving data interchange by 30\%.}
            \resumeItem{Automated ETL workflows supporting enterprise application lifecycle management, reducing manual intervention and data errors by 25\%.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Automated Reporting Suite for Project Management} $|$ Oracle BI, SSRS, SQL, Java}{ }
        \resumeItemListStart
            \resumeItem{Developed custom reports and dashboards leveraging \textbf{Oracle Business Intelligence} and \textbf{SQL} to provide real-time project performance metrics.}
            \resumeItem{Enhanced reporting accuracy and shortened report generation time by 40\% through optimized SQL queries and automated report scheduling.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}