\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8+ years} of backend development expertise specializing in \textbf{Java} with \textbf{Spring Boot} and reactive programming for scalable microservices.}
  \resumeItem{Applied \textbf{Python} extensively for backend automation and data-driven workflows, enhancing system reliability and performance.}
  \resumeItem{Engineered event-driven architectures using \textbf{Apache Kafka} and stream processing pipelines leveraging \textbf{Flink} to improve data throughput and real-time analytics.}
  \resumeItem{Optimized caching strategies with \textbf{Redis} and managed data persistence using \textbf{MongoDB} and \textbf{Oracle} databases for high availability.}
  \resumeItem{Designed and consumed \textbf{RESTful APIs} with strong security via \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and JWT, supporting cloud-native deployments on Kubernetes platforms.}
  \resumeItem{Gained foundational experience with conversational AI frameworks including \textbf{Dialogflow CX} and LLM concepts, supporting agentic architectures and prompt engineering.}
  \resumeItem{Collaborated effectively across teams, driving CI/CD automation, observability, and microservices best practices in fintech and digital assistant environments.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java (8/11/17/21), Python (backend/data-driven), Spring Boot (1/2/3), Spring WebFlux, Spring Security, Apache Flink, Hibernate/JPA \\
\textbf{Messaging \& Streaming:} & Apache Kafka, AWS SQS, AWS SNS, EventBridge, Kinesis, GCP Pub/Sub \\
\textbf{Databases \& Caching:} & MongoDB, Oracle, PostgreSQL, MySQL, Redis/ElastiCache \\
\textbf{API \& Integration:} & REST, gRPC, OpenAPI/Swagger, OAuth2/OIDC, JWT, mTLS, GraphQL (familiar) \\
\textbf{Cloud \& DevOps:} & AWS (EKS, ECS/Fargate, Lambda), Azure (AKS), GCP (GKE), Docker, Kubernetes, Helm, Terraform, CloudFormation \\
\textbf{AI \& Conversational Platforms:} & Google Dialogflow CX, LLM concepts, Agent Development Kit (ADK), Prompt Engineering, Spring AI \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led design and development of backend microservices using \textbf{Java 17/21} and \textbf{Spring Boot 3}, improving modularity and release agility by 30\%.}
  \resumeItem{Engineered reactive APIs with \textbf{Spring WebFlux} and \textbf{REST}, ensuring scalable, non-blocking request handling with consistent error models.}
  \resumeItem{Implemented secure authentication and authorization using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, \textbf{JWT}, and \textbf{mTLS}, enhancing compliance and RBAC enforcement.}
  \resumeItem{Developed event-driven workflows leveraging \textbf{Apache Kafka} for asynchronous processing, increasing system throughput by 25\%.}
  \resumeItem{Built streaming data pipelines using \textbf{Apache Flink}, enabling real-time analytics and reducing latency in data processing by 20\%.}
  \resumeItem{Optimized caching layers with \textbf{Redis}, reducing backend read latency by 25\% for critical high-traffic APIs.}
  \resumeItem{Managed data persistence with \textbf{MongoDB} and \textbf{Oracle}, tuning queries and indexes to improve performance by 30\%.}
  \resumeItem{Containerized microservices with \textbf{Docker} and deployed on \textbf{Kubernetes (EKS)} using \textbf{Helm}, enabling scalable cloud-native operations.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, enforcing quality gates with \textbf{SonarQube} and security scans via \textbf{Snyk}.}
  \resumeItem{Integrated foundational conversational AI concepts using \textbf{Spring AI} and \textbf{AWS Bedrock}, supporting enterprise GenAI workflows with secure prompt management.}
  \resumeItem{Implemented observability with \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling proactive monitoring and alerting for production systems.}
  \resumeItem{\textit{Environment: Java 17/21, Spring Boot 3, Spring WebFlux, Spring Security, Apache Kafka, Apache Flink, Redis, MongoDB, Oracle, Docker, Kubernetes (EKS), Jenkins, GitHub Actions, AWS (EKS, S3, RDS, SQS/SNS), Spring AI, AWS Bedrock.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed backend microservices using \textbf{Java 17} and \textbf{Kotlin}, focusing on reactive programming and scalable API design.}
  \resumeItem{Implemented event-driven architectures with \textbf{Apache Kafka}, improving decoupling and throughput across distributed services by 30\%.}
  \resumeItem{Built stream processing pipelines using \textbf{Apache Flink}, enabling real-time data transformation and analytics with 99.9\% uptime.}
  \resumeItem{Optimized caching strategies using \textbf{Redis/ElastiCache}, reducing latency on hot data paths by 20\%.}
  \resumeItem{Designed and maintained data models in \textbf{MongoDB} and \textbf{Aurora PostgreSQL}, improving query efficiency through indexing and schema tuning.}
  \resumeItem{Containerized applications using \textbf{Docker} and orchestrated deployments on \textbf{Kubernetes (EKS/ECS)}, ensuring robust scaling and fault tolerance.}
  \resumeItem{Automated infrastructure provisioning with \textbf{Terraform} and \textbf{CloudFormation} for consistent, auditable cloud environments.}
  \resumeItem{Implemented secure API access using \textbf{OAuth2/OIDC} and JWT tokens, aligning with enterprise security policies.}
  \resumeItem{Developed integration and operational UI components using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, enhancing user experience for internal tools.}
  \resumeItem{Established observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling actionable metrics and alerting for service health.}
  \resumeItem{\textit{Environment: Java 17, Kotlin, Apache Kafka, Apache Flink, Redis, MongoDB, PostgreSQL, Docker, Kubernetes (EKS/ECS), Terraform, CloudFormation, Angular, React, TypeScript, OpenTelemetry, AWS (S3, Lambda, API Gateway).}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8/11} and \textbf{Spring Boot 2.x}, delivering scalable RESTful APIs with robust validation and versioning.}
  \resumeItem{Implemented asynchronous processing with \textbf{Apache Kafka}, improving system resilience and throughput by 25\%.}
  \resumeItem{Optimized caching using \textbf{Redis}, reducing API response times by 25\% and minimizing database load.}
  \resumeItem{Managed data persistence in \textbf{MongoDB} and relational databases (\textbf{PostgreSQL/MySQL}), tuning queries and indexes for performance.}
  \resumeItem{Built secure API endpoints with \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT}, enforcing enterprise RBAC policies.}
  \resumeItem{Delivered frontend modules using \textbf{Angular} and \textbf{React (Hooks)} with \textbf{TypeScript} and \textbf{RxJS}, supporting workflow-heavy user experiences.}
  \resumeItem{Containerized services with \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling environment-based configuration and scaling.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, improving release velocity and quality.}
  \resumeItem{Integrated cloud platform services across \textbf{AWS}, \textbf{Azure}, and \textbf{GCP} for identity, storage, and messaging needs.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, Apache Kafka, Redis, MongoDB, PostgreSQL/MySQL, Docker, Kubernetes, Jenkins, Azure DevOps, Angular, React, TypeScript, AWS, Azure, GCP.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8} and \textbf{Spring Boot 2}, delivering modular APIs and reusable components.}
  \resumeItem{Built RESTful APIs documented with \textbf{Swagger}, ensuring consistent validation and error handling.}
  \resumeItem{Implemented caching and performance tuning using \textbf{Hibernate/JPA} and query optimization techniques.}
  \resumeItem{Delivered UI features using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, supporting admin and user workflows.}
  \resumeItem{Implemented scheduled batch jobs using \textbf{Spring Scheduling} and \textbf{Quartz} for periodic data processing.}
  \resumeItem{Containerized development and test environments using \textbf{Docker}, improving developer productivity.}
  \resumeItem{Supported cloud deployments on \textbf{AWS EC2} and \textbf{S3}, enabling scalable infrastructure.}
  \resumeItem{Strengthened automated testing with \textbf{JUnit} and \textbf{Mockito}, improving release stability.}
  \resumeItem{\textit{Environment: Java 8, Spring Boot 2, REST, Swagger, Hibernate/JPA, Angular, React, TypeScript, Docker, AWS (EC2, S3), JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}