\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Over \textbf{8+ years} of experience architecting and developing backend applications primarily using \textbf{C\# / .NET Core} and \textbf{Go}, delivering scalable web services and standalone applications.}
  \resumeItem{Expertise in building and migrating services in \textbf{Go (Golang)}, ensuring maintainable, high-performance codebases for greenfield and legacy projects.}
  \resumeItem{Proficient in leveraging \textbf{Azure DevOps} for Git repository management, work item tracking, and pipeline automation to streamline CI/CD workflows.}
  \resumeItem{Skilled in designing and querying \textbf{MongoDB} databases with efficient schema design, indexing, and aggregation pipelines to optimize data access patterns.}
  \resumeItem{Experienced with containerization using \textbf{Docker} and deploying applications on \textbf{Kubernetes}, including manifest authoring and basic troubleshooting via \textbf{kubectl}.}
  \resumeItem{Strong foundation in cloud-native development with cross-cloud exposure, emphasizing secure, scalable backend systems and microservices architecture.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & \textbf{C\# / .NET Core (ASP.NET Core Web API)}, Go (Golang), Java, Kotlin, TypeScript, JavaScript \\
\textbf{Databases:} & MongoDB (schema design, querying, indexing, aggregation pipelines), PostgreSQL, MySQL, Redis \\
\textbf{DevOps \& CI/CD:} & Azure DevOps (Git repos, work items, pipelines), Jenkins, GitHub Actions \\
\textbf{Containerization \& Orchestration:} & Docker, Kubernetes (manifests, deployments, services, kubectl troubleshooting), Helm \\
\textbf{Cloud Platforms:} & Azure (AKS, App Service, Azure AD, Key Vault, Azure Monitor), AWS, GCP \\
\textbf{Tools \& Others:} & REST APIs, gRPC, OpenAPI/Swagger, OAuth2/OIDC, JWT, Kafka, Terraform, Prometheus, Grafana \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led backend service development using \textbf{C\#} and \textbf{ASP.NET Core Web API}, enhancing modularity and enabling secure, scalable APIs.}
  \resumeItem{Implemented microservices and web services with \textbf{.NET Core}, improving service orchestration and reducing deployment risk by 30\%.}
  \resumeItem{Developed and maintained \textbf{Go} services for migration projects, improving performance and code maintainability across workflows.}
  \resumeItem{Managed \textbf{MongoDB} schema design and aggregation pipelines, optimizing query performance and data retrieval efficiency by 25\%.}
  \resumeItem{Utilized \textbf{Azure DevOps} for Git repository management, automated pipelines, and work item tracking, accelerating release cycles by 20\%.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes (EKS)}, authoring manifests and troubleshooting with \textbf{kubectl}.}
  \resumeItem{Automated CI/CD pipeline integration using \textbf{Jenkins} and \textbf{GitHub Actions}, enforcing code quality and security standards.}
  \resumeItem{Implemented observability and monitoring using \textbf{OpenTelemetry} and \textbf{CloudWatch}, reducing incident resolution time by 30\%.}
  \resumeItem{\textit{Environment: C\#, .NET Core, Go, MongoDB, Azure DevOps, Docker, Kubernetes (EKS), Jenkins, GitHub Actions, OpenTelemetry, CloudWatch.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and developed backend services using \textbf{Go} and \textbf{Java}, improving throughput and reliability of distributed systems.}
  \resumeItem{Built and maintained \textbf{RESTful} and \textbf{gRPC} APIs, ensuring consistent contract enforcement and operational stability.}
  \resumeItem{Implemented \textbf{MongoDB} queries and aggregation pipelines to support dynamic data access patterns and reduce latency by 20\%.}
  \resumeItem{Orchestrated containerized deployments using \textbf{Docker} and \textbf{Kubernetes}, managing manifests and troubleshooting with \textbf{kubectl}.}
  \resumeItem{Leveraged \textbf{Azure DevOps} pipelines and Git repositories for continuous integration and delivery, reducing manual deployment errors.}
  \resumeItem{Provisioned infrastructure with \textbf{Terraform} and \textbf{CloudFormation} for repeatable, auditable cloud environments.}
  \resumeItem{Implemented event-driven processing with \textbf{Kafka}, enhancing scalability and decoupling of microservices.}
  \resumeItem{Developed automation tools in \textbf{Go}, streamlining operational workflows and reducing manual effort by 40\%.}
  \resumeItem{\textit{Environment: Go, Java, MongoDB, Azure DevOps, Docker, Kubernetes, Terraform, CloudFormation, Kafka, REST, gRPC.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{C\#} and \textbf{ASP.NET Core Web API}, enabling partner integrations and internal orchestration workflows.}
  \resumeItem{Built and optimized \textbf{MongoDB} schemas and aggregation pipelines, improving query efficiency and reducing response times by 25\%.}
  \resumeItem{Created batch and automation utilities in \textbf{Go}, enhancing performance-sensitive workflows and operational reliability.}
  \resumeItem{Implemented containerized deployments using \textbf{Docker} and managed Kubernetes clusters for scalable service delivery.}
  \resumeItem{Utilized \textbf{Azure DevOps} for CI/CD pipeline automation and work item tracking, improving deployment frequency and quality.}
  \resumeItem{Developed frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, supporting configuration and operational dashboards.}
  \resumeItem{Improved caching strategies using \textbf{Redis}, reducing database load and improving API response times by 20\%.}
  \resumeItem{Collaborated on multi-cloud platform integrations (\textbf{AWS}, \textbf{Azure}, \textbf{GCP}) for identity, storage, and messaging services.}
  \resumeItem{\textit{Environment: C\#, ASP.NET Core, Go, MongoDB, Azure DevOps, Docker, Kubernetes, Angular, React, Redis, AWS, Azure, GCP.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, delivering scalable APIs and reusable components.}
  \resumeItem{Built REST APIs with \textbf{Swagger/OpenAPI} documentation, ensuring consistency and ease of integration.}
  \resumeItem{Implemented scheduled processing workflows using \textbf{Spring Scheduling} and \textbf{Quartz}, improving batch job reliability.}
  \resumeItem{Containerized development and test environments using \textbf{Docker}, enhancing consistency across teams.}
  \resumeItem{Supported cloud deployments on \textbf{AWS} (EC2, S3, RDS), enabling scalable infrastructure for applications.}
  \resumeItem{Improved database performance using \textbf{Hibernate/JPA} tuning and indexing strategies.}
  \resumeItem{Developed frontend features using \textbf{Angular} and \textbf{React} for internal dashboards and admin tools.}
  \resumeItem{Strengthened automated testing with \textbf{JUnit} and \textbf{Mockito}, improving release stability and code quality.}
  \resumeItem{\textit{Environment: Java, Spring Boot, REST, Swagger, Docker, AWS, Angular, React, Hibernate/JPA, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}