\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8 years} of backend development expertise specializing in \textbf{Java} and \textbf{Spring Boot} microservices with strong proficiency in reactive programming and event-driven systems.}
  \resumeItem{Applied \textbf{Python} for backend automation and data-driven workflows, integrating stream processing and caching solutions to optimize performance and scalability.}
  \resumeItem{Engineered robust event-driven architectures using \textbf{Apache Kafka} and \textbf{Flink} for real-time data pipelines, enhancing throughput and fault tolerance.}
  \resumeItem{Designed and maintained APIs with \textbf{RESTful} principles and incorporated \textbf{GraphQL} knowledge to support flexible client interactions.}
  \resumeItem{Implemented caching strategies leveraging \textbf{Redis} and managed data persistence across \textbf{MongoDB} and \textbf{Oracle} databases for mixed workload efficiency.}
  \resumeItem{Collaborated on conversational AI projects with exposure to \textbf{Google Dialogflow CX} and foundational \textbf{LLM} concepts, contributing to intelligent agent frameworks and prompt engineering.}
  \resumeItem{Led cloud-native deployments using container orchestration with \textbf{Kubernetes} and CI/CD pipelines, ensuring scalable and secure delivery in fintech environments.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java, Spring Boot, Spring WebFlux, Python, REST, GraphQL, Apache Kafka, Flink, Redis \\
\textbf{Databases \& Caching:} & MongoDB, Oracle, Redis, PostgreSQL, MySQL \\
\textbf{Cloud \& DevOps:} & Kubernetes, Docker, OpenShift Container Platform (OCP), Jenkins, GitHub Actions, Terraform, Helm \\
\textbf{Conversational AI \& AI/ML:} & Google Dialogflow CX, LLM concepts, Agent Development Kit (ADK), Prompt Engineering, Spring AI \\
\textbf{Microservices \& Integration:} & Microservices architecture, API-first design, OAuth2/OIDC, JWT, mTLS, gRPC \\
\textbf{Observability \& Testing:} & OpenTelemetry, Prometheus, Grafana, JUnit, Mockito, Testcontainers \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Delivered backend microservices using \textbf{Java} and \textbf{Spring Boot}, incorporating reactive programming with \textbf{Spring WebFlux} to improve system responsiveness by 30\%.}
  \resumeItem{Engineered event-driven workflows utilizing \textbf{Apache Kafka} for asynchronous processing, enhancing system reliability and throughput.}
  \resumeItem{Developed and maintained \textbf{RESTful APIs} with consistent versioning and validation, improving client integration stability.}
  \resumeItem{Implemented caching layers using \textbf{Redis}, reducing read latency by 25\% for high-demand data paths.}
  \resumeItem{Collaborated on conversational AI components integrating \textbf{Google Dialogflow CX} and foundational \textbf{LLM} concepts to enhance digital assistant capabilities.}
  \resumeItem{Containerized services with \textbf{Docker} and deployed on \textbf{Kubernetes (OCP)}, enabling scalable cloud-native delivery.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, enforcing quality gates and security scans.}
  \resumeItem{Monitored production systems using \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling proactive issue detection and alerting.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Spring WebFlux, Apache Kafka, Redis, Google Dialogflow CX, Docker, Kubernetes, Jenkins, GitHub Actions, OpenTelemetry, REST APIs, OAuth2/OIDC, JWT.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed backend services primarily in \textbf{Java} and \textbf{Spring Boot}, applying reactive programming to enhance scalability and responsiveness.}
  \resumeItem{Designed and implemented \textbf{Apache Kafka} event-driven pipelines, improving message throughput and decoupling service dependencies.}
  \resumeItem{Built \textbf{RESTful APIs} and integrated \textbf{GraphQL} endpoints to support flexible client data requirements.}
  \resumeItem{Applied \textbf{Python} for backend automation and data-driven tooling, streamlining operational workflows.}
  \resumeItem{Optimized caching strategies using \textbf{Redis}, reducing response times by 20--30\% for critical services.}
  \resumeItem{Managed data persistence with \textbf{MongoDB} and relational databases, improving query performance through indexing and tuning.}
  \resumeItem{Containerized applications with \textbf{Docker} and orchestrated deployments on \textbf{Kubernetes}, ensuring high availability.}
  \resumeItem{Provisioned infrastructure with \textbf{Terraform} and \textbf{CloudFormation} for repeatable cloud environments.}
  \resumeItem{Implemented observability using \textbf{OpenTelemetry} and monitored systems with \textbf{CloudWatch} dashboards and alerts.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Python, Apache Kafka, Redis, MongoDB, REST, GraphQL, Docker, Kubernetes, Terraform, OpenTelemetry.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Built scalable backend services using \textbf{Java} and \textbf{Spring Boot}, focusing on microservices and reactive programming paradigms.}
  \resumeItem{Developed secure \textbf{RESTful APIs} with \textbf{OAuth2/OIDC} and \textbf{JWT} authentication, enhancing platform security compliance.}
  \resumeItem{Implemented asynchronous processing with \textbf{Apache Kafka}, improving system reliability and throughput.}
  \resumeItem{Enhanced caching with \textbf{Redis}, reducing database load and improving response times by 25\%.}
  \resumeItem{Managed data storage across \textbf{MongoDB} and \textbf{Oracle} databases, optimizing queries and indexing strategies.}
  \resumeItem{Contributed to conversational AI initiatives by collaborating on \textbf{agentic frameworks} and foundational \textbf{LLM} concepts.}
  \resumeItem{Containerized and deployed services using \textbf{Docker} and \textbf{Kubernetes}, supporting cloud-native architecture.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Azure DevOps}, improving deployment frequency and quality.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Apache Kafka, Redis, MongoDB, Oracle, REST, OAuth2/OIDC, JWT, Docker, Kubernetes, Jenkins, Azure DevOps.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, delivering modular APIs and reusable components.}
  \resumeItem{Built \textbf{RESTful APIs} following \textbf{OpenAPI} standards, improving integration consistency.}
  \resumeItem{Implemented caching solutions using \textbf{Redis} to optimize read-heavy operations and reduce latency.}
  \resumeItem{Enhanced database performance with indexing and query tuning on \textbf{Oracle} and \textbf{MongoDB} systems.}
  \resumeItem{Supported microservices deployments using \textbf{Docker} containers and \textbf{Kubernetes} orchestration.}
  \resumeItem{Strengthened automated testing with \textbf{JUnit} and \textbf{Mockito}, improving release stability.}
  \resumeItem{Collaborated with cross-functional teams on cloud deployments and CI pipelines using \textbf{Jenkins}.}
  \resumeItem{\textit{Environment: Java, Spring Boot, REST, Redis, Oracle, MongoDB, Docker, Kubernetes, Jenkins, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}