\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Deliver over \textbf{8+ years} of backend expertise specializing in \textbf{Java} and \textbf{Spring Boot} microservices, with strong proficiency in \textbf{Python} for data-driven backend solutions.}
  \resumeItem{Architect and implement event-driven systems leveraging \textbf{Apache Kafka} and stream processing using \textbf{Flink}, optimizing real-time data pipelines and workflows.}
  \resumeItem{Apply advanced \textbf{Reactive Programming} techniques using \textbf{Spring WebFlux} to build scalable, non-blocking APIs and services.}
  \resumeItem{Utilize \textbf{Redis} caching and hybrid \textbf{MongoDB} and \textbf{Oracle} database expertise to enhance performance and data reliability.}
  \resumeItem{Familiar with conversational AI frameworks including \textbf{Google Dialogflow CX} and foundational knowledge of \textbf{LLM}, prompt engineering, and agentic architectures.}
  \resumeItem{Drive cloud-native deployments with container orchestration on \textbf{Kubernetes}, CI/CD automation, and observability using modern telemetry tools.}
  \resumeItem{Collaborate effectively across teams, leveraging strong communication skills and domain experience in \textbf{FinTech} and digital assistant platforms.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java (8/11/17/21), Python (backend/data-driven), Spring Boot (1/2/3), Spring WebFlux, Spring Security, Hibernate/JPA \\
\textbf{Event Streaming \& Processing:} & Apache Kafka, Flink, Redis, Reactive Programming (WebFlux) \\
\textbf{Databases \& Caching:} & MongoDB, Oracle, Redis/ElastiCache \\
\textbf{API \& Integration:} & RESTful APIs, gRPC, OpenAPI/Swagger, OAuth2/OIDC, JWT, mTLS, GraphQL (familiar) \\
\textbf{AI \& Conversational Platforms:} & Google Dialogflow CX, LLM concepts, prompt engineering, Agent Development Kit (ADK) familiarity \\
\textbf{Cloud \& DevOps:} & Kubernetes (OCP, EKS), Docker, CI/CD (Jenkins, GitHub Actions, Azure DevOps), Terraform, CloudFormation, OpenTelemetry \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led design and development of scalable backend services using \textbf{Java 17/21} and \textbf{Spring Boot 3}, improving modularity and deployment efficiency.}
  \resumeItem{Implemented reactive APIs with \textbf{Spring WebFlux}, reducing latency and enhancing throughput for critical financial workflows.}
  \resumeItem{Developed event-driven pipelines using \textbf{Apache Kafka} and integrated stream processing with \textbf{Flink}, boosting real-time data processing by 35\%.}
  \resumeItem{Optimized caching layers with \textbf{Redis}, decreasing p95 latency by 25\% for high-traffic API endpoints.}
  \resumeItem{Built and consumed RESTful APIs with strict adherence to \textbf{OpenAPI} standards, ensuring consistency across microservices.}
  \resumeItem{Applied \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT} to enforce secure access controls and enterprise compliance.}
  \resumeItem{Integrated conversational AI features using \textbf{Google Dialogflow CX}, enhancing internal productivity workflows with AI-driven automation.}
  \resumeItem{Containerized microservices using \textbf{Docker} and deployed on \textbf{Kubernetes (EKS)} with Helm, enabling streamlined CI/CD pipelines.}
  \resumeItem{Automated build and release processes using \textbf{Jenkins} and \textbf{GitHub Actions}, improving deployment frequency by 40\%.}
  \resumeItem{Implemented observability with \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling proactive monitoring and alerting for critical services.}
  \resumeItem{\textit{Environment: Java 17/21, Spring Boot 3, Spring WebFlux, Kafka, Flink, Redis, MongoDB, Oracle, REST, OpenAPI, OAuth2/OIDC, JWT, Google Dialogflow CX, Docker, Kubernetes (EKS), Jenkins, GitHub Actions, OpenTelemetry, AWS.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and implemented backend services using \textbf{Java 17} and \textbf{Kotlin}, focusing on scalable microservices and reactive programming patterns.}
  \resumeItem{Built event-driven architectures leveraging \textbf{Apache Kafka} for asynchronous processing and data streaming workflows.}
  \resumeItem{Developed stream processing applications using \textbf{Flink}, enhancing data pipeline throughput and fault tolerance.}
  \resumeItem{Improved data caching strategies with \textbf{Redis}, reducing backend read latency by 30\% for hot data paths.}
  \resumeItem{Implemented RESTful APIs and \textbf{gRPC} services with robust versioning and validation, supporting multi-team integrations.}
  \resumeItem{Applied security best practices using \textbf{OAuth2/OIDC}, \textbf{JWT}, and \textbf{mTLS} for service authentication and authorization.}
  \resumeItem{Containerized applications with \textbf{Docker} and orchestrated deployments on \textbf{Kubernetes (EKS/ECS)}, ensuring high availability.}
  \resumeItem{Provisioned infrastructure using \textbf{Terraform} and \textbf{CloudFormation}, enabling consistent and auditable cloud environments.}
  \resumeItem{Implemented observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, improving incident response times by 25\%.}
  \resumeItem{Delivered internal operational UIs using \textbf{Angular} and \textbf{React} with \textbf{TypeScript} for configuration workflows.}
  \resumeItem{\textit{Environment: Java 17, Kotlin, Spring Boot, Kafka, Flink, Redis, MongoDB, Oracle, REST, gRPC, OAuth2/OIDC, JWT, mTLS, Docker, Kubernetes (EKS/ECS), Terraform, CloudFormation, OpenTelemetry, Angular, React, TypeScript.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend microservices using \textbf{Java 8/11} and \textbf{Spring Boot 2}, focusing on modular and reusable API components.}
  \resumeItem{Built and consumed RESTful APIs with \textbf{OpenAPI/Swagger}, ensuring consistent validation, versioning, and error handling.}
  \resumeItem{Integrated \textbf{Apache Kafka} for asynchronous event processing, improving system reliability and throughput.}
  \resumeItem{Enhanced caching with \textbf{Redis}, reducing database contention and improving response times by 25\%.}
  \resumeItem{Implemented secure authentication and authorization using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT} aligned with RBAC policies.}
  \resumeItem{Worked with \textbf{MongoDB} and \textbf{Oracle} databases, optimizing queries and indexing strategies for performance gains.}
  \resumeItem{Delivered frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript} for workflow-heavy and dashboard interfaces.}
  \resumeItem{Containerized services with \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling environment-based configuration management.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing quality gates and security scans.}
  \resumeItem{Collaborated on cloud platform integrations across \textbf{AWS}, \textbf{Azure}, and \textbf{GCP}, enhancing identity and messaging services.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2, Kafka, Redis, MongoDB, Oracle, REST, OpenAPI, OAuth2/OIDC, JWT, Angular, React, TypeScript, Docker, Kubernetes, Jenkins, Azure DevOps, AWS, Azure, GCP.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8} and \textbf{Spring Boot 2} with clean layering and reusable components for web applications.}
  \resumeItem{Built RESTful APIs documented with \textbf{Swagger}, supporting internal and external integrations.}
  \resumeItem{Implemented caching and query optimizations with \textbf{Hibernate/JPA} and \textbf{Oracle} database, improving data access speeds.}
  \resumeItem{Delivered frontend features using \textbf{Angular} and \textbf{React} with \textbf{TypeScript} for admin and dashboard modules.}
  \resumeItem{Implemented scheduled workflows using \textbf{Spring Scheduling} and \textbf{Quartz} for periodic batch processing.}
  \resumeItem{Standardized build and deployment pipelines using \textbf{Maven}, \textbf{Gradle}, and \textbf{Jenkins}, improving release stability.}
  \resumeItem{Containerized development and test environments with \textbf{Docker} to streamline local setups.}
  \resumeItem{Supported cloud deployments on \textbf{AWS EC2} and \textbf{S3}, aligning with enterprise cloud strategies.}
  \resumeItem{Enhanced automated testing using \textbf{JUnit} and \textbf{Mockito}, increasing code coverage and reducing defects.}
  \resumeItem{\textit{Environment: Java 8, Spring Boot 2, REST, Swagger, Hibernate/JPA, Oracle, Angular, React, TypeScript, Docker, Jenkins, AWS EC2, S3, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}