\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8+ years} of backend development expertise specializing in \textbf{Java} and \textbf{Spring Boot}, focusing on modernizing legacy systems to \textbf{AWS} cloud environments.}
  \resumeItem{Designed and implemented robust \textbf{ETL} pipelines, \textbf{data modeling}, and \textbf{SQL} optimization to support scalable data modernization initiatives.}
  \resumeItem{Led cloud migration and modernization projects using \textbf{AWS} services including \textbf{Lambda}, \textbf{S3}, \textbf{RDS}, and \textbf{DynamoDB} with strong DevOps practices.}
  \resumeItem{Applied Agile methodologies and a testing mindset to deliver high-quality, maintainable backend services with continuous integration and deployment pipelines.}
  \resumeItem{Skilled in containerization and orchestration using \textbf{Docker} and \textbf{Kubernetes}, enabling scalable and resilient cloud-native architectures.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java (8/11/17/21), Spring Boot (1.5/2.x/3.x), SQL, Hibernate/JPA, C\# \\
\textbf{Cloud \& Data Modernization:} & AWS (Lambda, S3, RDS/Aurora, DynamoDB, IAM, KMS, Secrets Manager, CloudWatch), Data Modeling, ETL Pipelines \\
\textbf{DevOps \& Containerization:} & Docker, Kubernetes (EKS), Helm, Terraform, CloudFormation, Jenkins, GitHub Actions \\
\textbf{Databases \& Caching:} & PostgreSQL, MySQL, Aurora, DynamoDB, Redis/ElastiCache \\
\textbf{Messaging \& Streaming:} & Kafka, AWS SQS, AWS SNS \\
\textbf{Testing \& Observability:} & JUnit 5, Mockito, Testcontainers, OpenTelemetry, CloudWatch, SonarQube, Snyk \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Java Developer}{USA}
\resumeItemListStart
  \resumeItem{Led modernization of legacy applications to \textbf{AWS} cloud using \textbf{Java 17/21} and \textbf{Spring Boot 3}, improving scalability and maintainability.}
  \resumeItem{Developed and optimized \textbf{ETL} pipelines and \textbf{data models} to support enterprise data workflows, improving data processing efficiency by 30\%.}
  \resumeItem{Implemented secure backend services with \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT}, ensuring compliance with enterprise security standards.}
  \resumeItem{Built RESTful and gRPC APIs with \textbf{OpenAPI} specifications, enabling consistent integration and versioning across microservices.}
  \resumeItem{Containerized microservices using \textbf{Docker} and deployed on \textbf{Kubernetes (EKS)} with \textbf{Helm}, enabling automated and repeatable releases.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, enforcing quality and security gates with \textbf{SonarQube} and \textbf{Snyk}.}
  \resumeItem{Improved observability by integrating \textbf{OpenTelemetry} metrics and alerts via \textbf{CloudWatch}, reducing incident response times by 25\%.}
  \resumeItem{Collaborated in Agile teams to deliver high-quality features with a strong testing mindset using \textbf{JUnit 5} and \textbf{Mockito}.}
  \resumeItem{\textit{Environment: Java 17/21, Spring Boot 3, Spring Security, AWS (Lambda, S3, RDS/Aurora, DynamoDB, SQS/SNS, IAM, KMS, Secrets Manager, CloudWatch), Docker, Kubernetes (EKS), Helm, Jenkins, GitHub Actions, SonarQube, Snyk, OpenTelemetry, JUnit 5, Mockito.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Engineered backend services using \textbf{Java 17} and \textbf{Kotlin}, focusing on scalable data processing and cloud-native application design.}
  \resumeItem{Designed and implemented \textbf{ETL} workflows and \textbf{data modeling} strategies for efficient data ingestion and transformation.}
  \resumeItem{Migrated legacy components to \textbf{AWS} services including \textbf{Lambda}, \textbf{S3}, and \textbf{Aurora PostgreSQL}, improving system reliability and cost efficiency.}
  \resumeItem{Built event-driven architectures leveraging \textbf{Kafka} and \textbf{AWS SQS/SNS} to decouple services and increase throughput by 40\%.}
  \resumeItem{Provisioned and managed infrastructure using \textbf{Terraform} and \textbf{CloudFormation} for consistent and auditable deployments.}
  \resumeItem{Implemented containerized deployments using \textbf{Docker} and orchestrated with \textbf{Kubernetes (EKS/ECS)}, ensuring high availability and scalability.}
  \resumeItem{Enhanced backend performance by optimizing \textbf{SQL} queries and leveraging \textbf{Redis} caching, reducing latency by 20\%.}
  \resumeItem{Applied automated testing with \textbf{JUnit 5}, \textbf{Mockito}, and contract testing using \textbf{Pact} to maintain code quality and prevent regressions.}
  \resumeItem{\textit{Environment: Java 17, Kotlin, AWS (Lambda, S3, Aurora, DynamoDB, SQS/SNS, IAM, KMS, Secrets Manager, CloudWatch), Kafka, Docker, Kubernetes (EKS/ECS), Terraform, CloudFormation, JUnit 5, Mockito, Pact.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend microservices using \textbf{Java 8/11} and \textbf{Spring Boot 2.x} with a focus on \textbf{ETL}, \textbf{data modeling}, and \textbf{SQL} query optimization.}
  \resumeItem{Modernized legacy systems by integrating \textbf{AWS} cloud services such as \textbf{S3}, \textbf{RDS}, and \textbf{DynamoDB}, improving scalability and fault tolerance.}
  \resumeItem{Implemented secure APIs with \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT} for enterprise-grade access control.}
  \resumeItem{Built asynchronous processing pipelines using \textbf{Kafka}, improving throughput and reliability with retry and dead-letter queue patterns.}
  \resumeItem{Optimized database performance through indexing and query tuning on \textbf{PostgreSQL} and \textbf{MySQL}, reducing response times by 25\%.}
  \resumeItem{Containerized services with \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling environment-based configuration and scaling.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, ensuring consistent quality with \textbf{SonarQube} scans.}
  \resumeItem{Collaborated in Agile teams with a strong testing mindset, using \textbf{JUnit 5} and \textbf{Mockito} for unit and integration testing.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, AWS (S3, RDS, DynamoDB), Kafka, PostgreSQL, MySQL, Docker, Kubernetes, Jenkins, Azure DevOps, SonarQube, JUnit 5, Mockito.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8} and \textbf{Spring Boot (1.5/2.0)} focusing on modular design and reusable components.}
  \resumeItem{Built and maintained RESTful APIs with \textbf{Swagger} documentation to standardize service contracts and improve integration.}
  \resumeItem{Implemented batch processing and scheduled workflows using \textbf{Spring Scheduling} and \textbf{Quartz} for data transformation tasks.}
  \resumeItem{Optimized database queries and indexing strategies using \textbf{Hibernate/JPA} to improve performance on \textbf{Oracle} and \textbf{MySQL} databases.}
  \resumeItem{Containerized development and test environments using \textbf{Docker}, facilitating faster feedback cycles and environment parity.}
  \resumeItem{Supported cloud deployments on \textbf{AWS EC2}, \textbf{S3}, and \textbf{RDS}, enhancing system availability and scalability.}
  \resumeItem{Strengthened automated testing practices using \textbf{JUnit} and \textbf{Mockito} to increase release stability and reduce defects.}
  \resumeItem{Collaborated in Agile teams delivering incremental improvements aligned with business priorities and technical roadmaps.}
  \resumeItem{\textit{Environment: Java 8, Spring Boot 1.5/2.0, REST, Swagger, Hibernate/JPA, Oracle, MySQL, Docker, AWS (EC2, S3, RDS), JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}