\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8+ years} of experience architecting and developing robust \textbf{Java} applications with \textbf{Spring Boot} and microservices for scalable enterprise solutions.}
  \resumeItem{Implemented event-driven architectures using \textbf{Kafka} and \textbf{Cassandra} for high-throughput, fault-tolerant distributed systems in financial and consumer domains.}
  \resumeItem{Designed and maintained RESTful APIs and microservices, ensuring clean code, modularity, and adherence to best practices in Agile environments.}
  \resumeItem{Collaborated effectively with cross-functional teams to translate business requirements into scalable technical solutions and optimized performance.}
  \resumeItem{Applied containerization and orchestration using \textbf{Docker} and \textbf{Kubernetes}, with CI/CD pipelines for automated deployments and quality assurance.}
  \resumeItem{Familiar with \textbf{Azure} cloud services and \textbf{Redis} caching, enhancing system responsiveness and scalability in distributed applications.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java (8/11/17/21), Spring Boot (1.5/2.x/3.x), Kafka, Cassandra, Microservices Architecture, REST APIs \\
\textbf{Databases \& Caching:} & Cassandra, PostgreSQL, MySQL, Redis, DynamoDB \\
\textbf{Cloud \& DevOps:} & AWS (EKS, S3, RDS, SQS/SNS), Azure (AKS, App Service), Docker, Kubernetes, Helm, Terraform, Jenkins, GitHub Actions \\
\textbf{Frontend:} & Angular (5--17), React (Hooks), TypeScript, RxJS, NgRx \\
\textbf{Testing \& Quality:} & JUnit 5, Mockito, Testcontainers, WireMock, Pact, SonarQube \\
\textbf{Observability \& Messaging:} & OpenTelemetry, CloudWatch, Prometheus, Grafana, Kafka, AWS SQS/SNS \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Java Developer}{USA}
\resumeItemListStart
  \resumeItem{Designed and developed \textbf{Java 17/21} microservices using \textbf{Spring Boot 3}, improving modularity and reducing deployment risks by 30\%.}
  \resumeItem{Implemented event-driven processing with \textbf{Kafka}, enabling asynchronous workflows and improving system throughput by 25\%.}
  \resumeItem{Developed and maintained APIs using \textbf{REST} and \textbf{gRPC}, ensuring compliance with \textbf{OpenAPI} standards and versioning policies.}
  \resumeItem{Applied \textbf{Spring Security} with \textbf{OAuth2/OIDC} and \textbf{JWT} to secure services and enforce RBAC policies across microservices.}
  \resumeItem{Integrated \textbf{Cassandra} for scalable, high-availability data storage supporting event-driven architectures.}
  \resumeItem{Optimized caching strategies using \textbf{Redis}, reducing data access latency by 25\% in critical read paths.}
  \resumeItem{Containerized microservices with \textbf{Docker} and deployed on \textbf{Kubernetes (EKS)} using \textbf{Helm}, enabling automated rollouts and rollbacks.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{GitHub Actions}, incorporating \textbf{SonarQube} quality gates and security scans.}
  \resumeItem{Monitored applications using \textbf{OpenTelemetry} and \textbf{CloudWatch}, reducing incident response times by 20\%.}
  \resumeItem{\textit{Environment: Java 17/21, Spring Boot 3, Kafka, Cassandra, Spring Security, OAuth2/OIDC, JWT, Redis, Docker, Kubernetes (EKS), Helm, Jenkins, GitHub Actions, SonarQube, OpenTelemetry, CloudWatch.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed scalable \textbf{Java 17} microservices using \textbf{Spring Boot}, improving system reliability and API consistency.}
  \resumeItem{Implemented event-driven solutions using \textbf{Kafka} to decouple services and increase throughput by 30\%.}
  \resumeItem{Designed and optimized data models with \textbf{Cassandra} and \textbf{DynamoDB}, enhancing query performance and scalability.}
  \resumeItem{Built RESTful APIs with \textbf{OpenAPI} specifications, ensuring backward compatibility and robust validation.}
  \resumeItem{Leveraged \textbf{Redis} caching to reduce backend latency by 20\% for high-traffic endpoints.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed on \textbf{EKS/ECS}, supporting zero-downtime deployments.}
  \resumeItem{Provisioned infrastructure using \textbf{Terraform} and \textbf{CloudFormation}, enabling repeatable and auditable environment setups.}
  \resumeItem{Implemented observability using \textbf{OpenTelemetry} and \textbf{CloudWatch} dashboards, improving monitoring coverage.}
  \resumeItem{Developed automated tests using \textbf{JUnit 5} and \textbf{Mockito}, ensuring 90\%+ code coverage and reducing defects.}
  \resumeItem{\textit{Environment: Java 17, Spring Boot, Kafka, Cassandra, Redis, DynamoDB, Docker, Kubernetes (EKS/ECS), Terraform, CloudFormation, OpenTelemetry, CloudWatch, JUnit 5, Mockito.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend microservices using \textbf{Java 8/11} and \textbf{Spring Boot 2.x}, improving modularity and scalability of payment platforms.}
  \resumeItem{Implemented asynchronous event processing with \textbf{Kafka}, enhancing system resilience and throughput by 20\%.}
  \resumeItem{Designed data storage solutions using \textbf{Cassandra} and relational databases, improving query efficiency by 15\%.}
  \resumeItem{Built secure APIs with \textbf{Spring Security}, \textbf{OAuth2}, and \textbf{JWT}, enforcing enterprise-grade access controls.}
  \resumeItem{Enhanced caching layers using \textbf{Redis}, reducing database load and improving response times by 25\%.}
  \resumeItem{Delivered frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, improving user experience and maintainability.}
  \resumeItem{Containerized services with \textbf{Docker} and orchestrated deployments using \textbf{Kubernetes}, streamlining release cycles.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Azure DevOps}, maintaining high code quality and deployment reliability.}
  \resumeItem{Integrated cloud services across \textbf{AWS}, \textbf{Azure}, and \textbf{GCP} for identity, storage, and messaging capabilities.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, Kafka, Cassandra, Redis, Spring Security, OAuth2, JWT, Angular, React, Docker, Kubernetes, Jenkins, Azure DevOps, AWS, Azure, GCP.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8} and \textbf{Spring Boot (1.5/2.0)}, delivering reusable components and clean API layers.}
  \resumeItem{Built REST APIs and documented with \textbf{Swagger}, ensuring consistency and ease of integration.}
  \resumeItem{Implemented internal service orchestration using \textbf{C\#} with \textbf{.NET Framework}, enabling partner workflows and data exchange.}
  \resumeItem{Delivered frontend features using \textbf{Angular 5/6/7} and \textbf{React 16} with \textbf{TypeScript}, improving UI modularity and performance.}
  \resumeItem{Optimized database queries and indexing using \textbf{Hibernate/JPA}, improving data retrieval times by 15\%.}
  \resumeItem{Standardized builds and CI pipelines using \textbf{Maven} and \textbf{Jenkins}, improving release stability.}
  \resumeItem{Containerized development environments using \textbf{Docker}, accelerating testing and deployment workflows.}
  \resumeItem{Supported cloud deployments on \textbf{AWS (EC2, S3, RDS)}, enabling scalable infrastructure for web applications.}
  \resumeItem{Enhanced automated testing with \textbf{JUnit} and \textbf{Mockito}, increasing code coverage and reducing bugs.}
  \resumeItem{\textit{Environment: Java 8, Spring Boot 1.5/2.0, REST, Swagger, C\#, .NET Framework, Angular 5/6/7, React 16, Hibernate/JPA, Docker, Jenkins, AWS (EC2, S3, RDS), JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}