\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8+ years} of expertise in backend-focused \textbf{Java/J2EE} development, specializing in scalable microservices and cloud-native architectures.}
  \resumeItem{Designed and implemented event-driven systems leveraging \textbf{Kafka} and asynchronous messaging to enhance throughput and decouple services efficiently.}
  \resumeItem{Built and maintained containerized applications using \textbf{Spring Boot}, \textbf{Docker}, and \textbf{Kubernetes}, achieving high availability and streamlined deployments on \textbf{AWS}.}
  \resumeItem{Optimized database solutions across \textbf{SQL} and \textbf{NoSQL} platforms including \textbf{MongoDB}, improving query performance and data consistency.}
  \resumeItem{Led technical design, code reviews, and production troubleshooting using observability tools such as \textbf{Splunk} and \textbf{Grafana}, ensuring robust system reliability.}
  \resumeItem{Collaborated with cross-functional teams to mentor engineers and align technical solutions with business goals in fast-paced Agile environments.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java (8/11/17/21), Spring Boot (1.5/2.x/3.x), J2EE, JavaScript, Angular, React \\
\textbf{Cloud \& Containerization:} & AWS (EKS, ECS, Lambda, S3, RDS, DynamoDB), Docker, Kubernetes, Helm \\
\textbf{Databases:} & SQL (PostgreSQL, MySQL, Aurora), NoSQL (MongoDB, DynamoDB), Redis \\
\textbf{Messaging \& Streaming:} & Kafka, AWS SQS, SNS, Pub/Sub \\
\textbf{CI/CD \& DevOps:} & Jenkins, Maven, Git, Bitbucket, Jira, Confluence, Terraform, CloudFormation \\
\textbf{Monitoring \& Logging:} & Splunk, Grafana, Dynatrace, Prometheus, OpenTelemetry \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Java Developer}{USA}
\resumeItemListStart
  \resumeItem{Architected and developed scalable backend services using \textbf{Java 17/21} and \textbf{Spring Boot 3}, improving modularity and reducing deployment risk.}
  \resumeItem{Designed and implemented event-driven microservices with \textbf{Kafka}, enhancing system throughput and fault tolerance by decoupling service dependencies.}
  \resumeItem{Built and maintained containerized applications deployed on \textbf{Kubernetes (EKS)} using \textbf{Docker} and \textbf{Helm} for consistent environment management.}
  \resumeItem{Optimized SQL and NoSQL database queries, including \textbf{MongoDB}, achieving 30--40\% performance improvements through indexing and caching strategies.}
  \resumeItem{Led troubleshooting and production support using \textbf{Splunk} and monitoring tools, reducing incident resolution time by 25\%.}
  \resumeItem{Implemented secure authentication and authorization using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT}, ensuring enterprise compliance.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{GitHub Actions}, enforcing quality gates using \textbf{SonarQube} and vulnerability scans with \textbf{Snyk}.}
  \resumeItem{Collaborated in Agile teams, participating in code reviews and mentoring junior engineers to elevate code quality and team productivity.}
  \resumeItem{\textit{Environment: Java 17/21, Spring Boot 3, Kafka, Docker, Kubernetes (EKS), Helm, MongoDB, SQL, Splunk, Jenkins, GitHub Actions, OAuth2, JWT, SonarQube, Snyk.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed backend microservices using \textbf{Java 17} and \textbf{Spring Boot}, improving API scalability and robustness across distributed systems.}
  \resumeItem{Implemented asynchronous event processing with \textbf{Kafka}, increasing system resilience and decoupling service workflows effectively.}
  \resumeItem{Designed and optimized data models for \textbf{SQL} and \textbf{NoSQL} databases including \textbf{DynamoDB} and \textbf{Aurora}, enhancing query performance by 20--30\%.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{EKS/ECS}, ensuring reliable and repeatable production releases.}
  \resumeItem{Provisioned infrastructure using \textbf{Terraform} and \textbf{CloudFormation} for consistent and auditable cloud environments.}
  \resumeItem{Implemented observability with \textbf{OpenTelemetry} and \textbf{CloudWatch}, reducing mean time to detect issues by 30\%.}
  \resumeItem{Built frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript} to support operational workflows and dashboards.}
  \resumeItem{Developed automated tests using \textbf{JUnit 5} and \textbf{Mockito}, improving code coverage and reducing defects in production.}
  \resumeItem{\textit{Environment: Java 17, Spring Boot, Kafka, AWS (EKS, ECS, DynamoDB, Aurora), Docker, Terraform, CloudFormation, Angular, React, JUnit 5, Mockito.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8/11} and \textbf{Spring Boot 2.x}, delivering scalable APIs and reusable microservices.}
  \resumeItem{Built event-driven systems with \textbf{Kafka}, improving asynchronous processing and system reliability through retry and DLQ patterns.}
  \resumeItem{Optimized relational and NoSQL databases including \textbf{PostgreSQL}, \textbf{MySQL}, and \textbf{MongoDB}, increasing query efficiency by 25\%.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling consistent environments and streamlined releases.}
  \resumeItem{Implemented secure access controls using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT} for enterprise-grade authorization.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing code quality through \textbf{SonarQube} scans.}
  \resumeItem{Delivered frontend features using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, supporting complex workflows and dashboard interfaces.}
  \resumeItem{Collaborated with cross-functional teams to troubleshoot production issues and mentor junior engineers, improving team efficiency.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, Kafka, PostgreSQL, MySQL, MongoDB, Docker, Kubernetes, Jenkins, Azure DevOps, Angular, React, Spring Security.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8} and \textbf{Spring Boot (1.5/2.0)}, delivering reusable components and clean API layers.}
  \resumeItem{Built RESTful APIs following \textbf{Swagger/OpenAPI} standards, improving endpoint consistency and documentation quality.}
  \resumeItem{Implemented internal integration endpoints using \textbf{C\#} with \textbf{.NET Framework}, supporting partner workflows and service orchestration.}
  \resumeItem{Delivered frontend features using \textbf{Angular 5/6/7} and \textbf{React 16} with \textbf{TypeScript}, building reusable UI components and dashboards.}
  \resumeItem{Optimized database queries using \textbf{Hibernate/JPA} and indexing, improving data retrieval times significantly.}
  \resumeItem{Standardized builds and CI pipelines using \textbf{Maven} and \textbf{Jenkins}, enhancing release stability and automation.}
  \resumeItem{Containerized development environments using \textbf{Docker}, enabling consistent testing and deployment workflows.}
  \resumeItem{Supported cloud deployments on \textbf{AWS EC2, S3, and RDS}, integrating cloud services with on-premise applications.}
  \resumeItem{\textit{Environment: Java 8, Spring Boot, REST, Swagger, C\#, .NET Framework, Angular, React, Hibernate/JPA, Docker, Jenkins, AWS EC2/S3/RDS.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}