\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8+ years} of expertise in designing and maintaining complex Java/JEE enterprise applications with strong focus on \textbf{Spring Boot}, \textbf{Hibernate/JPA}, and \textbf{Struts} frameworks.}
  \resumeItem{Led development of scalable web applications using \textbf{Angular} and \textbf{React.js} with modern JavaScript (ES6+), including state management with \textbf{Redux} and routing via \textbf{React Router}.}
  \resumeItem{Implemented robust backend services with \textbf{Java 8+}, \textbf{Spring MVC}, and \textbf{RESTful APIs}, ensuring high data integrity and compliance with enterprise standards.}
  \resumeItem{Applied advanced SQL and PL/SQL skills for database design, stored procedures, and performance optimization on Oracle and SQL Server platforms.}
  \resumeItem{Experienced in \textbf{JBOSS Enterprise SOA} environment, including workflow automation and integration, with strong adherence to \textbf{CMMI Level 3} and \textbf{Agile} methodologies.}
  \resumeItem{Integrated AI-driven tools to accelerate coding tasks, improve code quality, and streamline development workflows, enhancing team productivity and collaboration.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java (8/11/17), Java EE, Spring Boot (2.x/3.x), Spring MVC, Hibernate/JPA, Apache Struts, Angular (5--17), React.js (ES6+), Redux, React Router, JavaScript, TypeScript \\
\textbf{Databases \& SQL:} & Oracle, SQL Server, PL/SQL, SQL, Stored Procedures, Functions, Database Design, Query Optimization \\
\textbf{Application Servers \& Middleware:} & JBOSS Enterprise SOA, JBOSS Workflow, Apache Tomcat, WebSphere, OpenShift Container Platform \\
\textbf{DevOps \& CI/CD:} & Azure DevOps Pipelines, Git, Maven, Jenkins, CI/CD Pipelines, Build Automation, Source Control \\
\textbf{Methodologies \& Practices:} & Agile, Test Driven Development (TDD), CMM/CMMI Level 3, Software Development Life Cycle (SDLC) \\
\textbf{Additional Technologies:} & RESTful Web Services, SOAP Web Services, JMS API, Apache Kafka, Apache Spark, ActiveMQ, AI-assisted Development Tools, Cloud Platforms (AWS, Azure) \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Java Developer}{USA}
\resumeItemListStart
  \resumeItem{Led design and development of complex \textbf{Java 17} backend services using \textbf{Spring Boot 3} and \textbf{Hibernate/JPA}, improving system stability and scalability.}
  \resumeItem{Developed and maintained \textbf{RESTful APIs} using \textbf{Spring MVC} and \textbf{Spring Security}, enhancing secure access and data integrity across critical applications.}
  \resumeItem{Implemented frontend modules with \textbf{Angular 16/17} and \textbf{React.js} using \textbf{Redux} and \textbf{React Router}, improving user experience and component lifecycle management.}
  \resumeItem{Managed \textbf{JBOSS} based SOA services and workflow automation, streamlining business processes and ensuring compliance with enterprise standards.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, resulting in faster releases and improved deployment reliability.}
  \resumeItem{Integrated AI-driven coding tools to accelerate development, enhance code quality, and facilitate team collaboration on complex projects.}
  \resumeItem{Optimized database queries and indexing on \textbf{Oracle} and \textbf{SQL Server} using advanced \textbf{PL/SQL} and \textbf{SQL} techniques, reducing latency by 30\%.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed on \textbf{Kubernetes (EKS)}, improving environment consistency and scalability.}
  \resumeItem{Enhanced asynchronous processing using \textbf{Apache Kafka} and \textbf{AWS SQS/SNS}, increasing system throughput and fault tolerance.}
  \resumeItem{\textit{Environment: Java 17, Spring Boot 3, Hibernate/JPA, Spring MVC, JBOSS SOA, Angular, React.js, Redux, REST, Jenkins, GitHub Actions, Oracle, SQL Server, Docker, Kubernetes, Kafka, AI-assisted development tools.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and implemented \textbf{Java 17} microservices using \textbf{Spring Boot} and \textbf{Hibernate}, improving modularity and maintainability of core systems.}
  \resumeItem{Developed \textbf{RESTful} and \textbf{SOAP} web services with robust validation and error handling, ensuring seamless integration with external systems.}
  \resumeItem{Built frontend features using \textbf{Angular} and \textbf{React.js} with modern JavaScript (ES6+), leveraging \textbf{Redux} for predictable state management.}
  \resumeItem{Implemented event-driven architecture using \textbf{Apache Kafka}, enhancing asynchronous processing and system resilience.}
  \resumeItem{Optimized database performance on \textbf{Oracle} and \textbf{SQL Server} through query tuning and stored procedure development using \textbf{PL/SQL}.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Azure DevOps}, reducing deployment times and improving release quality.}
  \resumeItem{Managed \textbf{JBOSS} middleware and workflow services, streamlining enterprise SOA processes and improving operational efficiency.}
  \resumeItem{Applied Agile and \textbf{Test Driven Development} practices, increasing code coverage and reducing production defects.}
  \resumeItem{Utilized AI-assisted development tools to accelerate coding tasks and improve documentation quality, enhancing team productivity.}
  \resumeItem{\textit{Environment: Java 17, Spring Boot, Hibernate, REST, SOAP, Angular, React.js, Redux, Kafka, Oracle, SQL Server, PL/SQL, Azure DevOps, JBOSS SOA, Agile, TDD, AI-assisted development.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed \textbf{Java 8/11} backend services using \textbf{Spring Boot 2.x} and \textbf{Hibernate/JPA}, improving API performance and reliability.}
  \resumeItem{Built and maintained \textbf{RESTful} web services and \textbf{SOAP} APIs, ensuring secure and compliant data exchange.}
  \resumeItem{Implemented frontend solutions with \textbf{Angular 8--12} and \textbf{React.js} using \textbf{Redux} for state management and enhanced user workflows.}
  \resumeItem{Optimized database operations on \textbf{Oracle} and \textbf{SQL Server} using advanced \textbf{PL/SQL} stored procedures and query tuning.}
  \resumeItem{Managed \textbf{JBOSS} Enterprise SOA environment and workflow services, improving integration and business process automation.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Azure DevOps}, accelerating release cycles and improving deployment stability.}
  \resumeItem{Adhered to \textbf{CMMI Level 3} and Agile methodologies, enhancing process maturity and team collaboration.}
  \resumeItem{Utilized AI-driven code generation and refactoring tools to improve development efficiency and code quality.}
  \resumeItem{Implemented asynchronous messaging using \textbf{Apache Kafka}, improving system scalability and fault tolerance.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, Hibernate/JPA, REST, SOAP, Angular, React.js, Redux, Oracle, SQL Server, PL/SQL, JBOSS SOA, Jenkins, Azure DevOps, Kafka, Agile, CMMI, AI-assisted development.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8} and \textbf{Spring Boot (1.5/2.0)}, improving modularity and maintainability of web applications.}
  \resumeItem{Built \textbf{RESTful} APIs and maintained \textbf{Apache Struts} based applications, enhancing system stability and user experience.}
  \resumeItem{Implemented frontend features with \textbf{Angular 5/6/7} and \textbf{React 16}, delivering reusable components and improved UI workflows.}
  \resumeItem{Optimized database queries and indexing using \textbf{Hibernate/JPA} and \textbf{PL/SQL} on \textbf{Oracle} databases, reducing response times by 20\%.}
  \resumeItem{Managed builds and deployments using \textbf{Maven} and \textbf{Jenkins}, standardizing release processes and improving automation.}
  \resumeItem{Supported \textbf{JBOSS} and \textbf{WebSphere} application servers, ensuring high availability and performance of enterprise applications.}
  \resumeItem{Applied Agile practices and implemented unit testing with \textbf{JUnit} and \textbf{Mockito}, increasing code quality and reducing defects.}
  \resumeItem{Containerized development environments using \textbf{Docker}, improving consistency across testing and production.}
  \resumeItem{Contributed to cloud deployments on \textbf{AWS EC2} and \textbf{S3}, enabling scalable and resilient infrastructure.}
  \resumeItem{\textit{Environment: Java 8, Spring Boot, Apache Struts, Hibernate/JPA, Angular, React, Oracle, PL/SQL, Maven, Jenkins, JBOSS, WebSphere, Docker, AWS, JUnit, Mockito, Agile.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}