\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8+ years} of experience architecting and developing scalable back-end solutions with \textbf{C\#}, \textbf{ASP.NET Core}, and \textbf{.NET Framework} for enterprise clients.}
  \resumeItem{Led design and implementation of secure RESTful APIs and microservices, optimizing database interactions with \textbf{SQL Server} and \textbf{Entity Framework Core}.}
  \resumeItem{Implemented cloud-native applications leveraging \textbf{Azure} and \textbf{AWS} platforms, integrating CI/CD pipelines using \textbf{Azure DevOps} and \textbf{GitHub}.}
  \resumeItem{Collaborated with cross-functional teams to deliver maintainable, high-quality codebases using asynchronous programming, dependency injection, and middleware in \textbf{.NET}.}
  \resumeItem{Mentored development teams and acted as primary technical liaison for stakeholders, ensuring alignment on functional and technical requirements.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & C\#, ASP.NET Core, .NET Framework, Entity Framework Core, SQL, RESTful APIs, Microservices \\
\textbf{Databases:} & SQL Server, NoSQL, Query Optimization, Relational Databases \\
\textbf{Cloud \& DevOps:} & Azure, AWS, Azure DevOps, GitHub, CI/CD Pipelines, Docker, Kubernetes \\
\textbf{Programming Concepts:} & Asynchronous Programming, Dependency Injection, Middleware, Secure Coding Practices \\
\textbf{Version Control \& Tools:} & Git, Azure DevOps, GitHub, Jenkins \\
\textbf{Collaboration \& Documentation:} & Agile/Scrum, Technical Documentation, Cross-functional Teamwork \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Java Developer}{USA}
\resumeItemListStart
  \resumeItem{Led backend development using \textbf{C\#} and \textbf{ASP.NET Core Web API}, designing scalable microservices aligned with client requirements.}
  \resumeItem{Developed and optimized RESTful APIs with \textbf{Entity Framework Core}, improving database query performance by 30\%.}
  \resumeItem{Architected secure service-to-service communication using dependency injection and middleware patterns in \textbf{.NET}.}
  \resumeItem{Implemented asynchronous programming models to enhance throughput and reduce latency in high-load workflows.}
  \resumeItem{Collaborated with cross-functional teams including DevOps and QA to deploy services on \textbf{Azure} and \textbf{AWS} cloud platforms.}
  \resumeItem{Mentored junior developers and conducted code reviews to ensure adherence to best practices and maintainability.}
  \resumeItem{Prepared detailed technical documentation covering system design, API specifications, and deployment processes.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Azure DevOps} and \textbf{GitHub Actions}, reducing deployment times by 25\%.}
  \resumeItem{Acted as primary technical contact for stakeholders, facilitating requirement gathering and onsite client meetings.}
  \resumeItem{Optimized SQL Server queries and indexing strategies, reducing p95 latency by 20\% for critical application paths.}
  \resumeItem{Containerized microservices with \textbf{Docker} and orchestrated deployments using \textbf{Kubernetes} on cloud environments.}
  \resumeItem{Implemented observability using OpenTelemetry integrated with cloud monitoring tools to proactively identify issues.}
  \resumeItem{\textit{Environment: C\#, ASP.NET Core, .NET Framework, Entity Framework Core, SQL Server, Azure, AWS, Docker, Kubernetes, Azure DevOps, GitHub, OpenTelemetry.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and developed RESTful APIs and microservices using \textbf{C\#} and \textbf{ASP.NET Core}, improving integration with front-end applications.}
  \resumeItem{Optimized database schemas and queries in \textbf{SQL Server}, enhancing data retrieval efficiency by 25\%.}
  \resumeItem{Implemented asynchronous processing and middleware to improve scalability and maintainability of backend services.}
  \resumeItem{Leveraged \textbf{AWS} cloud services for deployment and infrastructure automation, ensuring high availability and security.}
  \resumeItem{Built and maintained CI/CD pipelines using \textbf{GitHub Actions} and \textbf{Azure DevOps}, accelerating release cycles.}
  \resumeItem{Collaborated with cross-functional teams to gather requirements and translate them into technical solutions.}
  \resumeItem{Applied dependency injection and secure coding standards to enhance code modularity and security posture.}
  \resumeItem{Containerized applications using \textbf{Docker} and managed orchestration with \textbf{Kubernetes}, enabling consistent deployments.}
  \resumeItem{Prepared comprehensive technical documentation and conducted knowledge transfer sessions for team members.}
  \resumeItem{Acted as liaison for client communication during project phases, ensuring alignment on deliverables and timelines.}
  \resumeItem{Enhanced API security and performance through middleware optimizations and asynchronous programming models.}
  \resumeItem{Implemented monitoring solutions using OpenTelemetry and AWS CloudWatch for proactive incident detection.}
  \resumeItem{\textit{Environment: C\#, ASP.NET Core, SQL Server, AWS, Docker, Kubernetes, GitHub Actions, Azure DevOps, OpenTelemetry.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed scalable backend services using \textbf{C\#} and \textbf{ASP.NET Core Web API}, delivering secure and maintainable APIs.}
  \resumeItem{Optimized \textbf{SQL Server} queries and indexes, achieving 25\% faster response times for critical data operations.}
  \resumeItem{Implemented asynchronous programming and dependency injection to improve application performance and testability.}
  \resumeItem{Collaborated with frontend teams to integrate RESTful APIs with Angular and React applications.}
  \resumeItem{Built and maintained CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, increasing deployment reliability.}
  \resumeItem{Containerized services with \textbf{Docker} and deployed on Kubernetes clusters to support scalable environments.}
  \resumeItem{Applied secure authentication and authorization mechanisms aligned with enterprise security standards.}
  \resumeItem{Prepared and updated technical documentation, including API specifications and architecture diagrams.}
  \resumeItem{Participated in Agile ceremonies and worked closely with product owners to refine requirements.}
  \resumeItem{Mentored junior developers on best practices in \textbf{.NET} development and cloud deployment strategies.}
  \resumeItem{Improved system observability using OpenTelemetry and cloud monitoring tools across multi-cloud environments.}
  \resumeItem{Acted as a key technical resource for internal and partner integrations using \textbf{C\#} microservices.}
  \resumeItem{\textit{Environment: C\#, ASP.NET Core, SQL Server, Azure, AWS, Docker, Kubernetes, Jenkins, Azure DevOps, Angular, React, OpenTelemetry.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{C\#} with \textbf{.NET Framework} and \textbf{ASP.NET Core}, enhancing integration workflows.}
  \resumeItem{Built RESTful APIs and documented endpoints using Swagger to standardize service communication.}
  \resumeItem{Optimized database queries and implemented indexing strategies to improve performance on relational databases.}
  \resumeItem{Collaborated with frontend teams using Angular and React to deliver reusable UI components.}
  \resumeItem{Implemented asynchronous processing and middleware to support scalable backend operations.}
  \resumeItem{Containerized development and testing environments using \textbf{Docker} to streamline workflows.}
  \resumeItem{Supported cloud deployments on \textbf{AWS} with EC2, S3, and RDS services.}
  \resumeItem{Automated build and deployment pipelines using \textbf{Jenkins}, improving release efficiency.}
  \resumeItem{Enhanced code quality through unit testing and continuous integration practices.}
  \resumeItem{Participated in Agile teams to deliver incremental product enhancements and technical improvements.}
  \resumeItem{\textit{Environment: C\#, .NET Framework, ASP.NET Core, SQL Server, AWS, Docker, Jenkins, Angular, React, Swagger.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}