\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Engineered scalable backend systems with \textbf{Python} automation, infrastructure as code, and container orchestration, delivering robust platform solutions.}
  \resumeItem{Designed and maintained CI/CD pipelines with \textbf{Terraform}, \textbf{Ansible}, and \textbf{Docker}, improving deployment automation and operational efficiency.}
  \resumeItem{Automated infrastructure provisioning and configuration management using \textbf{Infrastructure as Code} tools, enhancing system reliability and scalability.}
  \resumeItem{Developed distributed microservices and internal tooling, leveraging \textbf{Kubernetes} and \textbf{Prometheus/Grafana} for monitoring and performance optimization.}
  \resumeItem{Collaborated in Agile environments to deliver high-quality software, focusing on problem solving and platform engineering best practices.}
  \resumeItem{Experienced in cloud platforms including \textbf{AWS} and \textbf{Azure}, integrating NoSQL and SQL databases with secure, automated deployment pipelines.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Scripting:} & Python, Shell Scripting, Java (8/11/17/21), Go, C\#, TypeScript \\
\textbf{Platform \& Automation:} & Ansible, Terraform, Docker, Kubernetes, Helm, CI/CD Pipelines (Jenkins, GitHub Actions, Azure DevOps) \\
\textbf{Cloud \& Infrastructure:} & AWS (EKS, ECS, Lambda, S3, RDS, DynamoDB), Azure (AKS, App Service, Key Vault), Infrastructure as Code (Terraform, CloudFormation) \\
\textbf{Databases:} & PostgreSQL, MySQL, Aurora, DynamoDB, MongoDB, Redis, NoSQL and SQL administration and architecture \\
\textbf{Monitoring \& Observability:} & Prometheus, Grafana, OpenTelemetry, CloudWatch, Azure Monitor \\
\textbf{Development \& Testing:} & REST, gRPC, Microservices, Agile/Scrum, JUnit 5, Mockito, Testcontainers, Pact \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Developed and automated deployment pipelines using \textbf{Terraform} and \textbf{Ansible}, reducing release times by 30\% and improving reliability.}
  \resumeItem{Engineered backend services with \textbf{Java 17} and \textbf{Spring Boot 3}, integrating microservices architectures and containerized deployments on \textbf{Kubernetes}.}
  \resumeItem{Implemented monitoring solutions using \textbf{Prometheus} and \textbf{Grafana}, enhancing system observability and reducing incident response times by 25\%.}
  \resumeItem{Automated infrastructure provisioning and configuration management using \textbf{Terraform} and \textbf{Ansible}, improving environment consistency and scalability.}
  \resumeItem{Built internal tooling with \textbf{Python} scripts to automate operational workflows, increasing team productivity and reducing manual errors.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{EKS}, enabling smooth rollout and rollback strategies.}
  \resumeItem{Collaborated in Agile teams to deliver secure, scalable services with \textbf{REST} and \textbf{gRPC} APIs, following best practices for CI/CD and source control.}
  \resumeItem{Implemented security and authentication using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT} to meet enterprise compliance requirements.}
  \resumeItem{Optimized database access patterns on \textbf{PostgreSQL} and \textbf{Redis}, improving query performance and reducing latency by 20\%.}
  \resumeItem{Led code reviews and knowledge sharing to maintain high-quality code standards and promote problem-solving culture.}
  \resumeItem{\textit{Environment: Java 17/21, Spring Boot 3, Python, Terraform, Ansible, Docker, Kubernetes (EKS), Prometheus, Grafana, AWS (EKS, S3, RDS, DynamoDB), REST, gRPC, Spring Security, OAuth2, JWT, PostgreSQL, Redis, Jenkins, GitHub Actions.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and maintained CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, automating deployments and reducing manual intervention by 40\%.}
  \resumeItem{Developed distributed microservices in \textbf{Java 17} and \textbf{Kotlin}, leveraging \textbf{Docker} containers orchestrated with \textbf{Kubernetes} for scalability.}
  \resumeItem{Automated infrastructure provisioning with \textbf{Terraform} and \textbf{CloudFormation}, ensuring consistent and auditable cloud environments on \textbf{AWS}.}
  \resumeItem{Built automation tooling using \textbf{Python} and \textbf{Go} scripts to streamline operational tasks and improve system reliability.}
  \resumeItem{Implemented event-driven architecture using \textbf{Kafka} and \textbf{AWS SQS/SNS}, enhancing throughput and decoupling services.}
  \resumeItem{Monitored production systems with \textbf{OpenTelemetry} and \textbf{CloudWatch}, reducing mean time to detection for incidents.}
  \resumeItem{Optimized database schemas and access for \textbf{DynamoDB} and \textbf{Aurora PostgreSQL}, improving query efficiency by 25\%.}
  \resumeItem{Developed RESTful and gRPC APIs adhering to best practices for versioning, validation, and error handling.}
  \resumeItem{Containerized and deployed services on \textbf{EKS} and \textbf{ECS}, supporting blue-green and canary deployment strategies.}
  \resumeItem{Collaborated in Agile teams to deliver reliable software, participating in code reviews and sprint planning.}
  \resumeItem{\textit{Environment: Java 17, Kotlin, Python, Go, Docker, Kubernetes, Terraform, CloudFormation, AWS (EKS, ECS, Lambda, DynamoDB, Aurora, S3, SQS/SNS), Kafka, OpenTelemetry, Jenkins, GitHub Actions.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8/11} and \textbf{Spring Boot 2.x}, focusing on microservices architecture and scalable API design.}
  \resumeItem{Implemented automation scripts in \textbf{Python} and shell scripting to support deployment and operational tasks, reducing manual workload by 30\%.}
  \resumeItem{Built and maintained CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, improving release frequency and stability.}
  \resumeItem{Containerized services with \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling environment consistency and scalable deployments.}
  \resumeItem{Integrated monitoring and alerting using \textbf{Prometheus} and \textbf{Grafana}, enhancing system reliability and reducing downtime.}
  \resumeItem{Managed SQL and NoSQL databases (\textbf{PostgreSQL}, \textbf{MySQL}, \textbf{MongoDB}), optimizing queries and indexing for better performance.}
  \resumeItem{Collaborated in Agile teams, delivering features with \textbf{REST} APIs and ensuring code quality through peer reviews and automated testing.}
  \resumeItem{Implemented asynchronous processing using \textbf{Kafka}, improving system throughput and fault tolerance.}
  \resumeItem{Developed internal tooling and automation utilities to improve developer productivity and operational efficiency.}
  \resumeItem{Ensured secure access and authorization using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT}.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, Python, Docker, Kubernetes, Jenkins, Azure DevOps, Prometheus, Grafana, Kafka, PostgreSQL, MySQL, MongoDB, REST, OAuth2, JWT.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8} and \textbf{Spring Boot (1.5/2.0)}, delivering reusable components and RESTful APIs.}
  \resumeItem{Automated deployment and environment setup using \textbf{Docker} containers, improving development and testing workflows.}
  \resumeItem{Built internal dashboards and tooling with \textbf{React} and \textbf{Angular}, enhancing operational visibility and user experience.}
  \resumeItem{Implemented scheduled batch processing using \textbf{Spring Scheduling} and \textbf{Quartz}, improving task automation and reliability.}
  \resumeItem{Optimized database performance using \textbf{Hibernate/JPA} with indexing and query tuning on \textbf{Oracle} databases.}
  \resumeItem{Supported cloud deployments on \textbf{AWS EC2} and \textbf{S3}, integrating infrastructure with application services.}
  \resumeItem{Strengthened automated testing using \textbf{JUnit} and \textbf{Mockito}, improving code quality and release stability.}
  \resumeItem{Collaborated in Agile teams to deliver enhancements and maintain internal tooling, focusing on platform engineering principles.}
  \resumeItem{Developed internal integration endpoints using \textbf{C\#} with \textbf{.NET Framework}, supporting partner workflows.}
  \resumeItem{Maintained source control and build automation using \textbf{Jenkins} and \textbf{Maven/Gradle}, ensuring consistent releases.}
  \resumeItem{\textit{Environment: Java 8, Spring Boot 1.5/2.0, Docker, React, Angular, Hibernate/JPA, Oracle, AWS EC2/S3, JUnit, Mockito, Jenkins, C\#, .NET Framework.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}