\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8+ years} of full stack development focusing on \textbf{C\#/.NET} and \textbf{ReactJS} to build scalable, responsive applications with cloud-native architecture.}
  \resumeItem{Designed and developed backend APIs and serverless components using \textbf{Azure Functions} and \textbf{ASP.NET Core Web API} for robust service orchestration.}
  \resumeItem{Implemented CI/CD pipelines and observability frameworks to enable rapid deployments and proactive system monitoring using telemetry and alerting tools.}
  \resumeItem{Collaborated with cross-functional teams to deliver end-to-end solutions, ensuring clear communication between technical and business stakeholders.}
  \resumeItem{Integrated Generative AI and LLMs into enterprise workflows, designing AI-driven services aligned with security and operational excellence.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & \textbf{C\#}, \textbf{ASP.NET Core Web API}, \textbf{ReactJS (Hooks)}, \textbf{TypeScript}, \textbf{Java}, \textbf{Go}, \textbf{Spring Boot}, \textbf{Angular} \\
\textbf{Cloud \& Serverless:} & \textbf{Azure Functions}, \textbf{Azure Monitor}, \textbf{AWS (EKS, Lambda, S3)}, \textbf{GCP}, \textbf{Azure DevOps} \\
\textbf{Databases:} & \textbf{SQL Server}, \textbf{PostgreSQL}, \textbf{MongoDB}, \textbf{Redis}, \textbf{NoSQL} \\
\textbf{DevOps \& CI/CD:} & \textbf{Jenkins}, \textbf{GitHub Actions}, \textbf{Azure DevOps Pipelines}, \textbf{Terraform}, \textbf{Docker}, \textbf{Kubernetes}, \textbf{Helm} \\
\textbf{Observability \& Monitoring:} & \textbf{OpenTelemetry}, \textbf{Azure Monitor}, \textbf{CloudWatch}, \textbf{Prometheus}, \textbf{Grafana}, \textbf{Logging \& Alerting} \\
\textbf{AI \& Integration:} & \textbf{Generative AI}, \textbf{LLMs}, \textbf{Spring AI}, \textbf{AI Agents (MCP, A2A frameworks)} \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led design and development of scalable backend services using \textbf{C\#} and \textbf{ASP.NET Core Web API}, improving modularity and deployment speed.}
  \resumeItem{Built responsive web interfaces with \textbf{ReactJS (Hooks)} and \textbf{TypeScript}, enhancing user experience and maintainability of dashboard modules.}
  \resumeItem{Developed robust APIs and serverless components leveraging \textbf{Azure Functions}, improving system scalability and reducing latency by 30\%.}
  \resumeItem{Implemented CI/CD pipelines using \textbf{Azure DevOps} and \textbf{GitHub Actions}, accelerating release cycles and enforcing quality gates with \textbf{SonarQube}.}
  \resumeItem{Configured observability using \textbf{OpenTelemetry} and \textbf{Azure Monitor}, enabling proactive alerting and reducing incident response times by 40\%.}
  \resumeItem{Collaborated with cross-functional teams to integrate \textbf{Generative AI} and \textbf{LLMs} into internal workflows, ensuring secure and compliant AI service design.}
  \resumeItem{Optimized data storage and retrieval using \textbf{SQL Server} and \textbf{Redis} caching, improving API response times by 25\%.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed on \textbf{Kubernetes (EKS)} using \textbf{Helm} charts for consistent environment management.}
  \resumeItem{Enhanced asynchronous processing using \textbf{Kafka} and \textbf{Azure Service Bus}, improving system reliability and message throughput.}
  \resumeItem{\textit{Environment: C\#, ASP.NET Core Web API, ReactJS, TypeScript, Azure Functions, Azure Monitor, OpenTelemetry, Kafka, Redis, SQL Server, Docker, Kubernetes, Helm, Azure DevOps, GitHub Actions, SonarQube, Generative AI, LLMs.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and implemented backend services using \textbf{Java 17} and \textbf{Spring Boot}, delivering scalable APIs aligned with microservices architecture.}
  \resumeItem{Developed frontend modules using \textbf{ReactJS} and \textbf{TypeScript}, improving UI responsiveness and modularity for internal operational tools.}
  \resumeItem{Built serverless components on \textbf{AWS Lambda} and integrated APIs with \textbf{REST} and \textbf{gRPC}, enhancing service interoperability.}
  \resumeItem{Implemented CI/CD pipelines with \textbf{Jenkins} and \textbf{GitHub Actions}, enabling automated deployments and quality checks.}
  \resumeItem{Configured observability via \textbf{OpenTelemetry} and \textbf{CloudWatch}, improving monitoring and alerting for production systems.}
  \resumeItem{Optimized database access patterns using \textbf{DynamoDB} and \textbf{Aurora PostgreSQL}, reducing latency by 20\% through indexing and caching.}
  \resumeItem{Developed asynchronous event-driven workflows using \textbf{Kafka} and \textbf{AWS SQS/SNS}, increasing throughput and fault tolerance.}
  \resumeItem{Containerized services with \textbf{Docker} and orchestrated deployments on \textbf{EKS/ECS}, ensuring high availability and scalability.}
  \resumeItem{Implemented contract testing with \textbf{Pact} to maintain API compatibility and prevent regressions across services.}
  \resumeItem{\textit{Environment: Java 17, Spring Boot, ReactJS, TypeScript, AWS Lambda, REST, gRPC, Kafka, DynamoDB, Aurora PostgreSQL, Docker, Kubernetes (EKS), Jenkins, GitHub Actions, OpenTelemetry, CloudWatch, Pact.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8/11} and \textbf{Spring Boot 2.x}, delivering secure and scalable APIs with OAuth2 and JWT authentication.}
  \resumeItem{Built frontend components using \textbf{Angular (8--12)} and \textbf{ReactJS (Hooks)} with \textbf{TypeScript}, improving modularity and user experience.}
  \resumeItem{Implemented integration endpoints using \textbf{C\#} and \textbf{ASP.NET Core Web API}, enabling partner orchestration and internal workflows.}
  \resumeItem{Enhanced asynchronous processing pipelines with \textbf{Kafka}, improving reliability through retry and dead-letter queue handling.}
  \resumeItem{Optimized database queries and indexing on \textbf{PostgreSQL} and \textbf{MySQL}, improving throughput and reducing latency by 25\%.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling environment-based configuration and scalability.}
  \resumeItem{Implemented CI/CD automation with \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing code quality standards with \textbf{SonarQube}.}
  \resumeItem{Integrated cloud services across \textbf{AWS}, \textbf{Azure}, and \textbf{GCP} for identity management, storage, and messaging solutions.}
  \resumeItem{Developed batch automation utilities using \textbf{Go}, improving performance for data processing workflows.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, C\#, ASP.NET Core Web API, Angular, ReactJS, TypeScript, Kafka, PostgreSQL, MySQL, Docker, Kubernetes, Jenkins, Azure DevOps, AWS, Azure, GCP, Go.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8} and \textbf{Spring Boot (1.5/2.0)}, delivering reusable components and RESTful APIs.}
  \resumeItem{Built frontend features using \textbf{Angular (5--7)} and \textbf{React 16} with \textbf{TypeScript}, enabling modular UI for internal dashboards.}
  \resumeItem{Implemented integration services using \textbf{C\#} with \textbf{.NET Framework / .NET Core}, supporting internal workflows and partner APIs.}
  \resumeItem{Improved database performance with \textbf{Hibernate/JPA} tuning and indexing strategies on \textbf{Oracle} and \textbf{MySQL}.}
  \resumeItem{Automated builds and CI pipelines using \textbf{Jenkins}, standardizing deployment and testing processes.}
  \resumeItem{Containerized development and test environments using \textbf{Docker}, improving consistency and developer productivity.}
  \resumeItem{Implemented scheduled workflows using \textbf{Quartz} and \textbf{Spring Scheduling} to automate periodic tasks.}
  \resumeItem{Supported cloud deployments on \textbf{AWS EC2} and \textbf{S3}, enabling scalable infrastructure for web applications.}
  \resumeItem{Strengthened unit and integration testing using \textbf{JUnit} and \textbf{Mockito}, improving release stability.}
  \resumeItem{\textit{Environment: Java 8, Spring Boot, C\#, .NET Framework/Core, Angular, React, Hibernate/JPA, Oracle, MySQL, Jenkins, Docker, AWS EC2, Quartz, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}