\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Experienced \textbf{full stack developer} specializing in \textbf{C\#} and \textbf{React.js} with 5+ years delivering scalable, cloud-native applications and APIs.}
    \resumeItem{Skilled in designing and deploying \textbf{microservices} and \textbf{serverless functions} on \textbf{Azure} and \textbf{AWS}, improving system reliability and performance.}
    \resumeItem{Proficient in building robust \textbf{CI/CD pipelines} and implementing observability with monitoring and alerting tools to ensure operational excellence.}
    \resumeItem{Experienced in integrating \textbf{Generative AI} and \textbf{LLMs} into applications, enhancing user experience through intelligent automation and AI agents.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & C\# (8.0+), Java, TypeScript, JavaScript, SQL, Python, Shell Scripting \\
                \textbf{Frameworks \& Backend:} & .NET Core, ASP.NET MVC, Azure Functions, Spring Boot, Node.js, Express.js, React.js, Redux \\
                \textbf{Cloud \& DevOps:} & Azure (Functions, DevOps, Monitor), AWS (EC2, ECS, S3, API Gateway), Docker, Kubernetes, Jenkins, GitHub Actions, CI/CD Pipelines \\
                \textbf{Databases:} & SQL Server, PostgreSQL, MongoDB, Redis, DynamoDB \\
                \textbf{AI \& Machine Learning:} & Generative AI, LLM Integration, LangChain, MCP, RAG, TensorFlow \\
                \textbf{Monitoring \& Observability:} & Azure Monitor, Grafana, Prometheus, Splunk, Application Insights, Logging, Telemetry, Alerting \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{C\#} microservices and \textbf{Azure Functions} improving system uptime by 25\% and reducing latency in cloud-native applications.}
        \resumeItem{Engineered responsive web interfaces with \textbf{React.js} and \textbf{Redux}, increasing user engagement by 40\% and enhancing customer satisfaction.}
        \resumeItem{Implemented \textbf{CI/CD pipelines} using \textbf{Azure DevOps} and \textbf{Jenkins}, accelerating deployment frequency by 50\% and reducing release errors.}
        \resumeItem{Integrated \textbf{Generative AI} models and \textbf{LLMs} into existing services, improving query accuracy and reducing manual support tickets by 30\%.}
        \resumeItem{Optimized \textbf{PostgreSQL} queries and managed \textbf{Redis} caching, improving database response times by 20\% under peak loads.}
        \resumeItem{Set up observability with \textbf{Azure Monitor} and \textbf{Grafana}, enabling proactive alerting and reducing incident resolution times by 35\%.}
        \resumeItem{Designed and deployed \textbf{GraphQL} APIs via \textbf{AWS API Gateway}, decreasing client response times by 35\% and lowering backend load.}
        \resumeItem{Led migration from monolithic to microservices architecture using \textbf{ASP.NET Core}, enhancing scalability and maintainability by 30\%.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Developed core banking microservices using \textbf{C\#} and \textbf{.NET Core}, improving transaction throughput by 25\% and system reliability.}
        \resumeItem{Built front-end components with \textbf{React.js} and \textbf{Redux}, enhancing loan application user experience and reducing form errors by 15\%.}
        \resumeItem{Automated deployment pipelines with \textbf{Jenkins} and integrated \textbf{CI/CD} workflows, reducing deployment times by 30\%.}
        \resumeItem{Implemented event-driven architecture using \textbf{Kafka}, handling over 10,000 transactions per second with 99.9\% uptime.}
        \resumeItem{Configured monitoring dashboards with \textbf{Grafana} and \textbf{Prometheus}, improving system observability and reducing downtime by 20\%.}
        \resumeItem{Strengthened security with \textbf{OAuth2} and \textbf{JWT}, decreasing security incidents by 40\% through improved authentication flows.}
        \resumeItem{Developed middleware with \textbf{Node.js} to manage real-time cash position transactions, increasing processing speed by 30\%.}
        \resumeItem{Enhanced database performance by optimizing \textbf{SQL Server} queries, improving data retrieval speeds by 18\%.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Developed backend services in \textbf{C\#} and \textbf{ASP.NET MVC} for supply chain management, reducing order latency by 140ms via query optimization.}
        \resumeItem{Integrated third-party logistics APIs using \textbf{Node.js} and \textbf{Express.js}, expanding vendor support by 12\% within the first quarter.}
        \resumeItem{Authored unit tests with \textbf{xUnit} and \textbf{Moq}, identifying 20+ critical bugs before production deployment.}
        \resumeItem{Assisted migration of on-premise services to \textbf{Azure} cloud, improving system availability by 18\% through infrastructure modernization.}
        \resumeItem{Optimized \textbf{MongoDB} indexing and access patterns, increasing read throughput by 14\% during peak usage.}
        \resumeItem{Automated builds and deployments using \textbf{Jenkins} and \textbf{Shell scripts}, reducing manual effort by 4 hours weekly.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI-Powered Document Query System} $|$ C\#, React.js, LangChain, Azure Functions, OpenAI API}{}
        \resumeItemListStart
            \resumeItem{Developed an AI-driven document query app using \textbf{Generative AI} and \textbf{LLMs} to provide context-aware answers from PDF content.}
            \resumeItem{Implemented serverless \textbf{Azure Functions} and \textbf{React.js} frontend, improving query response accuracy by 40\% and user satisfaction.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Cloud-Native Microservices Platform} $|$ .NET Core, Azure, Docker, Kubernetes, SQL Server}{}
        \resumeItemListStart
            \resumeItem{Designed and deployed scalable microservices with \textbf{.NET Core} and \textbf{Azure Kubernetes Service}, enhancing system scalability by 30\%.}
            \resumeItem{Integrated \textbf{CI/CD pipelines} with \textbf{Azure DevOps}, reducing deployment time by 40\% and minimizing downtime during releases.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Real-Time API Gateway} $|$ AWS API Gateway, GraphQL, C\#, Redis, Jenkins}{}
        \resumeItemListStart
            \resumeItem{Developed a \textbf{GraphQL} API gateway using \textbf{AWS API Gateway} and \textbf{C\#}, reducing backend response times by 35\%.}
            \resumeItem{Implemented caching with \textbf{Redis} and automated deployments using \textbf{Jenkins}, improving throughput by 25\% during peak loads.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}