\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Architected and delivered scalable, modular \textbf{.NET} and \textbf{Angular} applications with microservices and cloud-native designs, driving banking digital transformations.}
  \resumeItem{Led cross-functional teams in designing reusable components and API-first platforms, enabling maintainable and extensible enterprise banking solutions on \textbf{Azure Cloud}.}
  \resumeItem{Specialized in lending, loan servicing, and financial workflows with strong expertise in \textbf{API development}, \textbf{microservices}, and \textbf{enterprise integrations} ensuring regulatory compliance.}
  \resumeItem{Implemented cloud migration, workflow automation, and performance optimizations leveraging \textbf{Azure Services}, \textbf{Cloudflare}, and modern architectural patterns for scalability.}
  \resumeItem{Demonstrated leadership in sprint planning, offshore team coordination, and governance adherence, fostering innovation and quality across distributed delivery environments.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & \textbf{C\# / .NET} (ASP.NET Core Web API), \textbf{Angular} (latest versions), TypeScript, Java, Go \\
\textbf{Cloud \& DevOps:} & \textbf{Azure Services} (App Services, Functions, API Gateway, Front Door, Traffic Manager, SQL), \textbf{Cloudflare}, Docker, Kubernetes, Terraform, CI/CD (Jenkins, GitHub Actions, Azure DevOps) \\
\textbf{API \& Architecture:} & RESTful APIs, Microservices, Event-driven architecture, Enterprise integration patterns, API Gateway, OAuth2/OIDC, JWT \\
\textbf{Databases \& Caching:} & SQL Server, PostgreSQL, Redis, Azure SQL, NoSQL Databases \\
\textbf{Testing \& Quality:} & Unit testing frameworks, SonarQube, Snyk, JUnit, Mockito \\
\textbf{Tools \& Other:} & Agile/Scrum, Jira, Confluence, Git, OpenTelemetry, Monitoring (Azure Monitor, CloudWatch) \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Designed and developed modular \textbf{.NET 6} microservices and \textbf{Angular 16/17} frontends, improving scalability and maintainability of banking workflows.}
  \resumeItem{Led API-first design and implementation using \textbf{REST} and \textbf{OpenAPI}, ensuring consistent validation, versioning, and security compliance across services.}
  \resumeItem{Implemented \textbf{Azure Functions} and \textbf{App Services} to enable cloud-native workflows, reducing operational overhead and improving deployment agility.}
  \resumeItem{Collaborated with business stakeholders to translate lending and loan servicing requirements into robust technical solutions, enhancing loan processing efficiency.}
  \resumeItem{Guided offshore teams on \textbf{coding standards} and architectural best practices, improving code quality and delivery velocity by 25\%.}
  \resumeItem{Optimized API performance and scalability using \textbf{Azure API Gateway} and \textbf{Cloudflare} for enhanced security and traffic management.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Azure DevOps} and \textbf{GitHub Actions}, reducing release cycle time by 30\%.}
  \resumeItem{Implemented observability with \textbf{OpenTelemetry} and \textbf{Azure Monitor}, enabling proactive issue detection and resolution.}
  \resumeItem{Managed sprint planning, estimation, and release coordination across distributed onsite and offshore teams, ensuring timely delivery of features.}
  \resumeItem{\textit{Environment: .NET 6, ASP.NET Core Web API, Angular 16/17, Azure App Services, Azure Functions, Azure API Gateway, Cloudflare, REST, OpenAPI, OAuth2, JWT, OpenTelemetry, Azure Monitor, GitHub Actions, Azure DevOps.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed backend microservices using \textbf{Java 17} and \textbf{Spring Boot 3}, enhancing modularity and API-first design for financial data processing.}
  \resumeItem{Built and maintained \textbf{RESTful APIs} and \textbf{gRPC} endpoints to support high-throughput financial workflows and integrations.}
  \resumeItem{Designed and implemented event-driven architectures using \textbf{Kafka} to decouple services and improve system resilience.}
  \resumeItem{Provisioned and managed infrastructure with \textbf{Terraform}, enabling consistent and auditable cloud environments on AWS and Azure.}
  \resumeItem{Containerized services using \textbf{Docker} and orchestrated deployments with \textbf{Kubernetes (EKS)}, improving scalability and reliability.}
  \resumeItem{Implemented security controls with \textbf{IAM}, \textbf{KMS}, and secrets management, ensuring compliance with financial regulatory standards.}
  \resumeItem{Enhanced API security and performance using \textbf{API Gateway} and caching strategies, reducing latency by 20\%.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{GitHub Actions}, improving deployment frequency and reducing errors.}
  \resumeItem{Delivered frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript} for financial operations dashboards.}
  \resumeItem{\textit{Environment: Java 17, Spring Boot 3, REST, gRPC, Kafka, AWS (EKS, Lambda, API Gateway), Docker, Kubernetes, Terraform, Jenkins, GitHub Actions, Angular, React, TypeScript.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Engineered reusable \textbf{Java 8/11} microservices with \textbf{Spring Boot 2.x}, supporting lending and payment workflows with high availability.}
  \resumeItem{Developed secure \textbf{REST APIs} with \textbf{OAuth2/OIDC} and \textbf{JWT} for enterprise-level authentication and authorization.}
  \resumeItem{Built frontend applications using \textbf{Angular 8--12} and \textbf{TypeScript}, delivering modular UI components for financial services.}
  \resumeItem{Implemented asynchronous processing with \textbf{Kafka}, improving reliability and throughput of transaction workflows.}
  \resumeItem{Developed integration endpoints using \textbf{C\#} and \textbf{ASP.NET Core Web API} for internal and partner system orchestration.}
  \resumeItem{Optimized database performance using \textbf{Hibernate/JPA} on \textbf{PostgreSQL/MySQL} with indexing and query tuning, improving response times by 25\%.}
  \resumeItem{Containerized microservices with \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling environment-based configurations and scalability.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing code quality and security standards.}
  \resumeItem{Implemented cross-cloud integrations leveraging \textbf{AWS}, \textbf{Azure}, and \textbf{GCP} services for identity and messaging workflows.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, REST, OAuth2, JWT, Angular 8--12, TypeScript, Kafka, C\#, ASP.NET Core, PostgreSQL, MySQL, Hibernate, Docker, Kubernetes, Jenkins, Azure DevOps, AWS, Azure, GCP.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8} and \textbf{Spring Boot 1.5/2.0}, delivering reusable components for internal banking-related tooling.}
  \resumeItem{Built \textbf{RESTful APIs} and documented endpoints with \textbf{Swagger}, enabling consistent integration and maintainability.}
  \resumeItem{Implemented internal service endpoints using \textbf{C\#} with \textbf{.NET Framework} and \textbf{.NET Core}, supporting financial workflow orchestration.}
  \resumeItem{Delivered frontend features using \textbf{Angular 5/6/7} with \textbf{TypeScript}, creating reusable modules for administrative dashboards.}
  \resumeItem{Built internal dashboards using \textbf{React 16} with component-based architecture to improve user experience and modularity.}
  \resumeItem{Implemented scheduled batch processing using \textbf{Quartz} and \textbf{Spring Scheduling}, automating periodic financial workflows.}
  \resumeItem{Improved database query performance using \textbf{Hibernate/JPA} and indexing strategies, reducing latency by 15\%.}
  \resumeItem{Standardized build and deployment pipelines with \textbf{Maven/Gradle} and \textbf{Jenkins}, improving release stability.}
  \resumeItem{Containerized development and testing environments using \textbf{Docker}, enabling consistent developer workflows.}
  \resumeItem{\textit{Environment: Java 8, Spring Boot 1.5/2.0, REST, Swagger, C\#, .NET Framework/Core, Angular 5--7, React 16, Quartz, Hibernate/JPA, Maven, Gradle, Jenkins, Docker, AWS EC2, S3, RDS.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}