```latex
\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8+ years} of enterprise software solutions specializing in \textbf{C\# / .NET Core} backend systems and cloud-native Azure platform modernization.}
  \resumeItem{Expert in migrating legacy applications into modular, plug-in driven architectures leveraging \textbf{Azure App Services}, \textbf{Functions}, and \textbf{Service Bus} for scalable integrations.}
  \resumeItem{Skilled in designing and implementing CI/CD pipelines with \textbf{Azure DevOps} and infrastructure as code using \textbf{ARM} and \textbf{Terraform} to enable automated cloud deployments.}
  \resumeItem{Proficient in REST API development, asynchronous programming, and dependency injection to ensure maintainable, loosely coupled systems.}
  \resumeItem{Strong collaborator with architects and DevOps teams to troubleshoot and optimize performance in hybrid cloud environments.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & C\#, .NET Framework/Core (ASP.NET Core Web API), REST API, Dependency Injection, Asynchronous Programming \\
\textbf{Cloud \& Azure Services:} & Azure App Services, Azure Functions, Azure Storage, Azure Service Bus, Azure Key Vault, Azure DevOps Pipelines \\
\textbf{Architecture \& Patterns:} & Modular Architecture, Plug-in Driven Design, Microservices, Event-Driven Architecture \\
\textbf{DevOps \& IaC:} & CI/CD (Azure DevOps, GitHub Actions), Infrastructure as Code (ARM, Bicep, Terraform), Docker, Kubernetes \\
\textbf{Testing \& Quality:} & Unit Testing, Code Reviews, SonarQube, Automated Testing \\
\textbf{Tools \& Others:} & Git, Jira, Confluence, Visual Studio, Postman \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Refactored legacy \textbf{C\# / .NET 6} applications into modular Azure services, improving scalability and reducing coupling by 35\%.}
  \resumeItem{Developed and integrated REST APIs using \textbf{ASP.NET Core Web API} to enable seamless communication across distributed systems.}
  \resumeItem{Implemented asynchronous messaging with \textbf{Azure Service Bus}, enhancing reliability and throughput of event-driven workflows by 40\%.}
  \resumeItem{Collaborated with DevOps to build CI/CD pipelines using \textbf{Azure DevOps}, reducing deployment time by 50\%.}
  \resumeItem{Utilized \textbf{Azure Functions} and \textbf{App Services} to modernize application components, achieving 25\% improvement in resource utilization.}
  \resumeItem{Applied infrastructure as code with \textbf{Terraform} to provision cloud environments, ensuring consistency and auditability.}
  \resumeItem{Conducted unit testing and code reviews, increasing code coverage by 30\% and reducing defects in production.}
  \resumeItem{Troubleshot integration and performance issues in hybrid cloud environments, improving system uptime to 99.9\%.}
  \resumeItem{\textit{Environment: C\#, .NET 6, Azure App Services, Azure Functions, Azure Service Bus, Azure Storage, Azure Key Vault, Azure DevOps, Terraform, REST API, Docker, Kubernetes.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Migrated monolithic services to modular \textbf{C\# / .NET Core} microservices, improving maintainability and deployment frequency by 40\%.}
  \resumeItem{Designed and implemented RESTful APIs with \textbf{ASP.NET Core Web API} for internal platform integrations, reducing latency by 20\%.}
  \resumeItem{Leveraged \textbf{Azure Functions} for serverless compute, automating workflows and cutting operational costs by 30\%.}
  \resumeItem{Built asynchronous event processing using \textbf{Azure Service Bus}, enhancing message throughput and fault tolerance.}
  \resumeItem{Developed and maintained CI/CD pipelines with \textbf{GitHub Actions} and \textbf{Azure DevOps}, accelerating release cycles by 35\%.}
  \resumeItem{Implemented infrastructure as code using \textbf{ARM} templates and \textbf{Terraform} for consistent environment provisioning.}
  \resumeItem{Enhanced security by integrating \textbf{Azure Key Vault} for secrets management, reducing credential exposure risks.}
  \resumeItem{Performed code reviews and unit testing, increasing code quality and reducing post-release bugs by 25\%.}
  \resumeItem{\textit{Environment: C\#, .NET Core, Azure Functions, Azure Service Bus, Azure Storage, Azure Key Vault, GitHub Actions, Azure DevOps, ARM, Terraform, REST API, Docker, Kubernetes.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Refactored legacy \textbf{C\# / ASP.NET Core} services to cloud-ready architectures, improving modularity and deployment speed by 30\%.}
  \resumeItem{Developed REST APIs with \textbf{ASP.NET Core Web API}, enforcing robust validation and versioning standards to support partner integrations.}
  \resumeItem{Implemented asynchronous messaging patterns using \textbf{Azure Service Bus} to enhance reliability of distributed workflows.}
  \resumeItem{Collaborated with DevOps teams to automate CI/CD pipelines using \textbf{Azure DevOps}, reducing manual deployment errors by 40\%.}
  \resumeItem{Integrated \textbf{Azure Key Vault} for secure secrets management, improving compliance with enterprise security policies.}
  \resumeItem{Optimized service performance through profiling and refactoring, reducing API response times by 25\%.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling scalable cloud deployments.}
  \resumeItem{Conducted unit testing and enforced code quality standards, increasing maintainability and reducing technical debt.}
  \resumeItem{\textit{Environment: C\#, ASP.NET Core, Azure Service Bus, Azure Key Vault, Azure DevOps, Docker, Kubernetes, REST API, Terraform.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed integration services using \textbf{C\# / .NET Framework} to support legacy application workflows and partner systems.}
  \resumeItem{Built RESTful APIs and internal tools, improving data exchange and reducing manual processing by 30\%.}
  \resumeItem{Implemented scheduled processing with \textbf{Quartz} and \textbf{Spring Scheduling} to automate batch jobs and reporting.}
  \resumeItem{Containerized development environments using \textbf{Docker}, enhancing developer productivity and consistency.}
  \resumeItem{Supported cloud deployments on \textbf{AWS EC2} and storage services, facilitating hybrid cloud migration efforts.}
  \resumeItem{Improved database performance through query optimization and indexing, reducing latency by 20\%.}
  \resumeItem{Maintained code quality with unit testing and continuous integration using \textbf{Jenkins}.}
  \resumeItem{\textit{Environment: C\#, .NET Framework, REST, Quartz, Docker, AWS EC2, Jenkins, SQL Server.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

% ===== PROJECTS =====
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Azure Modular Platform Migration} | Enterprise Cloud Modernization}{2024}
\resumeItemListStart
  \resumeItem{Led migration of legacy \textbf{C\# / .NET} monolith to modular Azure platform using \textbf{Azure App Services} and \textbf{Azure Functions}, improving scalability by 40\%.}
  \resumeItem{Implemented asynchronous messaging with \textbf{Azure Service Bus}, enhancing system responsiveness and fault tolerance across distributed modules.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{CI/CD Pipeline Automation} | Cloud Infrastructure}{2023}
\resumeItemListStart
  \resumeItem{Designed and implemented automated CI/CD pipelines using \textbf{Azure DevOps} and \textbf{Terraform}, reducing deployment time by 50\% and increasing release reliability.}
  \resumeItem{Integrated infrastructure as code with \textbf{ARM} templates to provision consistent Azure environments, improving auditability and scalability.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{AI-Driven Workflow Enhancement} | Internal Productivity Tool}{2022}
\resumeItemListStart
  \resumeItem{Developed an AI-enabled workflow automation tool integrating \textbf{Azure Cognitive Services} to streamline internal processes, reducing manual effort by 35\%.}
  \resumeItem{Implemented secure API endpoints with \textbf{ASP.NET Core Web API} and integrated \textbf{Azure Key Vault} for managing sensitive credentials securely.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}
```