```latex
\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Kafka Administrator\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Designed and maintained highly available \textbf{Kafka} clusters with robust security and monitoring, improving platform reliability by 30\% in critical environments.}
  \resumeItem{Automated Kafka provisioning and configuration using \textbf{Ansible} and \textbf{Terraform}, reducing manual deployment time by 40\% and minimizing downtime.}
  \resumeItem{Monitored and troubleshot Kafka clusters using \textbf{Prometheus} and \textbf{Grafana}, resolving broker outages and replication lag to ensure 99.9\% uptime.}
  \resumeItem{Managed Linux infrastructure (\textbf{RHEL}, \textbf{Ubuntu}) supporting Kafka ecosystem, enhancing system stability and performance in real-time data platforms.}
  \resumeItem{Implemented Kafka security protocols including ACLs and schema registry, ensuring compliance and secure data streaming across enterprise pipelines.}
  \resumeItem{Experienced in Kafka ecosystem components like \textbf{ZooKeeper}, \textbf{Kafka Connect}, \textbf{MirrorMaker}, and \textbf{KRaft}, enabling scalable and resilient data pipelines.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Messaging \& Streaming:} & Kafka, Kafka Connect, Kafka Streams, MirrorMaker, Schema Registry, ZooKeeper, KRaft \\
\textbf{Operating Systems:} & Linux (RHEL, Ubuntu), Shell Scripting (Bash) \\
\textbf{Infrastructure \& Automation:} & Ansible, Terraform, OpenShift Kubernetes, Docker, Helm \\
\textbf{Monitoring \& Observability:} & Prometheus, Grafana, OpenTelemetry \\
\textbf{Programming \& Scripting:} & Python, Bash \\
\textbf{Security \& Access Control:} & Kafka ACLs, RBAC, Authentication, Authorization \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Java Developer}{USA}
\resumeItemListStart
  \resumeItem{Designed and maintained \textbf{Kafka} clusters with automated provisioning using \textbf{Terraform} and \textbf{Ansible}, improving deployment efficiency by 35\%.}
  \resumeItem{Monitored cluster health using \textbf{Prometheus} and \textbf{Grafana}, reducing incident response time by 40\% through proactive alerting and dashboards.}
  \resumeItem{Implemented Kafka security protocols including ACLs and schema registry, enhancing data protection and compliance across multiple teams.}
  \resumeItem{Automated Linux infrastructure management on \textbf{RHEL} and \textbf{Ubuntu} servers, improving platform stability and reducing manual errors by 25\%.}
  \resumeItem{Troubleshot Kafka broker outages and replication lag, restoring cluster performance and ensuring 99.9\% uptime for mission-critical data streams.}
  \resumeItem{Collaborated with engineering teams to onboard Kafka use cases, optimizing throughput and reliability for real-time data pipelines.}
  \resumeItem{Developed Python and Bash scripts to automate Kafka maintenance tasks, reducing manual intervention by over 50\%.}
  \resumeItem{\textit{Environment: Kafka, Terraform, Ansible, Prometheus, Grafana, Python, Bash, RHEL, Ubuntu, Kafka Connect, Schema Registry, ACLs.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Deployed and managed highly available \textbf{Kafka} clusters on \textbf{OpenShift Kubernetes} using helm charts, improving scalability by 30\%.}
  \resumeItem{Implemented Kafka resiliency and disaster recovery setups, reducing data loss risk and improving recovery speed by 50\%.}
  \resumeItem{Built and maintained data ingestion pipelines integrating \textbf{Kafka} with external platforms like \textbf{Solr}, enhancing cross-platform data availability.}
  \resumeItem{Automated Kafka provisioning and monitoring using \textbf{Ansible} and \textbf{Terraform}, cutting deployment times by 45\%.}
  \resumeItem{Monitored cluster performance and health using \textbf{Prometheus} and \textbf{Grafana}, enabling early detection of broker issues and replication lag.}
  \resumeItem{Developed and maintained Kafka Connect and MirrorMaker pipelines, ensuring reliable data replication across data centers.}
  \resumeItem{Managed Linux-based Kafka infrastructure on \textbf{Ubuntu} servers, improving system uptime and performance tuning.}
  \resumeItem{\textit{Environment: Kafka, OpenShift Kubernetes, Helm, Terraform, Ansible, Prometheus, Grafana, Kafka Connect, MirrorMaker, Python, Ubuntu.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Administered \textbf{Kafka} clusters ensuring high availability and security using ACLs, improving data pipeline reliability by 30\%.}
  \resumeItem{Automated Kafka upgrades and patching with minimal downtime, reducing maintenance windows by 40\%.}
  \resumeItem{Monitored Kafka cluster health via \textbf{Prometheus} and \textbf{Grafana}, proactively resolving replication lag and broker outages.}
  \resumeItem{Developed and optimized Kafka topics, partitions, and schema registry configurations to maximize throughput and reliability.}
  \resumeItem{Built Bash and Python automation scripts to streamline Kafka operational tasks, decreasing manual effort by 50\%.}
  \resumeItem{Supported Kafka Connect and Kafka Streams for real-time data processing, enhancing streaming pipeline efficiency.}
  \resumeItem{Managed Linux infrastructure (\textbf{RHEL}, \textbf{Ubuntu}) supporting Kafka clusters, improving system stability and performance.}
  \resumeItem{\textit{Environment: Kafka, ACLs, Prometheus, Grafana, Bash, Python, Kafka Connect, Kafka Streams, RHEL, Ubuntu.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Supported Linux-based infrastructure and containerized environments using \textbf{Docker} for backend services, improving deployment consistency by 30\%.}
  \resumeItem{Developed backend microservices with \textbf{Java} and \textbf{Spring Boot}, improving modularity and maintainability of internal tools.}
  \resumeItem{Implemented REST APIs and automated batch processing workflows, reducing manual processing time by 25\%.}
  \resumeItem{Built monitoring dashboards with \textbf{Grafana} for internal services, improving incident detection and resolution speed.}
  \resumeItem{Automated deployment pipelines using \textbf{Jenkins} and container orchestration with Kubernetes, enhancing release reliability.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Docker, Kubernetes, Jenkins, Grafana, Linux, Bash.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

% ===== PROJECTS =====
\section{Projects}
\resumeItemListStart

\resumeProjectHeading
{\textbf{Kafka Cluster Automation and Monitoring}}{2023}
\resumeItemListStart
  \resumeItem{Designed automated Kafka cluster provisioning using \textbf{Terraform} and \textbf{Ansible}, reducing deployment time by 40\%.}
  \resumeItem{Built custom monitoring dashboards with \textbf{Prometheus} and \textbf{Grafana} to track broker health and replication lag in real time.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Real-Time Data Pipeline with Kafka Connect and MirrorMaker}}{2022}
\resumeItemListStart
  \resumeItem{Developed and maintained Kafka Connect pipelines to ingest data from multiple sources, improving data availability by 35\%.}
  \resumeItem{Implemented MirrorMaker for cross-datacenter replication, enhancing disaster recovery capabilities and reducing data loss risk.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{AI-Enabled Kafka Security Compliance Tool}}{2024}
\resumeItemListStart
  \resumeItem{Built a Python-based tool leveraging AI to analyze Kafka ACLs and schema registry configurations, identifying potential security risks automatically.}
  \resumeItem{Integrated the tool with Kafka monitoring stack, reducing manual security audits by 50\% and improving compliance adherence.}
\resumeItemListEnd

\resumeItemListEnd

\end{document}
```