\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Architected and developed scalable, secure enterprise applications using \textbf{C\#}, \textbf{ASP.NET Core}, and \textbf{AWS} cloud services in the Financial Services domain.}
  \resumeItem{Led design and implementation of microservices and API-driven systems ensuring compliance with financial industry security and performance standards.}
  \resumeItem{Delivered cloud-native solutions leveraging \textbf{AWS Lambda}, \textbf{API Gateway}, \textbf{EC2}, and infrastructure as code with \textbf{Terraform} and \textbf{CloudFormation}.}
  \resumeItem{Guided teams on best practices in software architecture, DevOps pipelines, containerization with \textbf{Docker} and \textbf{Kubernetes}, and CI/CD automation.}
  \resumeItem{Extensive experience in system design, distributed systems, and secure financial application development with strong leadership in Agile environments.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & C\#, \textbf{.NET Core / .NET Framework}, ASP.NET Core Web API, Java, Spring Boot \\
\textbf{Cloud \& Infrastructure:} & AWS (EC2, S3, Lambda, API Gateway, RDS, DynamoDB, IAM, KMS, Secrets Manager, CloudFormation, Terraform), Azure, GCP \\
\textbf{Architecture \& Design:} & Microservices, RESTful APIs, Event-Driven Architecture, Messaging (Kafka, RabbitMQ), System Design, Scalability, Security Compliance \\
\textbf{Containerization \& Orchestration:} & Docker, Kubernetes (EKS), Helm \\
\textbf{DevOps \& CI/CD:} & Jenkins, GitHub Actions, Azure DevOps, SonarQube, Snyk, Infrastructure as Code (Terraform, CloudFormation) \\
\textbf{Databases \& Caching:} & SQL Server, PostgreSQL, MySQL, Aurora, DynamoDB, Redis \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Designed and developed secure, scalable backend services using \textbf{C\#} and \textbf{ASP.NET Core Web API}, improving modularity and deployment efficiency.}
  \resumeItem{Led architecture discussions and implemented microservices leveraging \textbf{AWS Lambda}, \textbf{API Gateway}, and \textbf{EC2}, enhancing system scalability by 35\%.}
  \resumeItem{Implemented secure authentication and authorization using industry standards, ensuring compliance with financial security regulations.}
  \resumeItem{Built and optimized RESTful APIs with \textbf{OpenAPI} specifications, improving integration consistency across platforms.}
  \resumeItem{Automated infrastructure provisioning using \textbf{Terraform} and \textbf{CloudFormation}, reducing deployment errors by 40\%.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed on \textbf{Kubernetes (EKS)} clusters using \textbf{Helm} charts for consistent environments.}
  \resumeItem{Established CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, integrating quality gates with \textbf{SonarQube} and security scans via \textbf{Snyk}.}
  \resumeItem{Implemented event-driven processing using \textbf{Kafka} and \textbf{AWS SQS/SNS}, improving asynchronous workflows and fault tolerance.}
  \resumeItem{Mentored developers on best practices in \textbf{cloud architecture}, microservices design, and secure coding standards.}
  \resumeItem{Monitored production systems with \textbf{OpenTelemetry} and \textbf{CloudWatch}, proactively identifying and resolving performance bottlenecks.}
  \resumeItem{\textit{Environment: C\#, ASP.NET Core, AWS (Lambda, API Gateway, EC2, S3, RDS, DynamoDB, SQS, SNS, IAM, KMS, Secrets Manager, CloudFormation, CloudWatch), Docker, Kubernetes (EKS), Helm, Terraform, Jenkins, GitHub Actions, SonarQube, Snyk, Kafka, OpenTelemetry.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed cloud-native microservices using \textbf{Java} and \textbf{Spring Boot}, aligning with AWS best practices for scalability and security.}
  \resumeItem{Designed and implemented RESTful and gRPC APIs, ensuring robust contract definitions and backward compatibility.}
  \resumeItem{Provisioned and managed AWS infrastructure with \textbf{Terraform} and \textbf{CloudFormation}, enabling automated, repeatable deployments.}
  \resumeItem{Integrated \textbf{AWS Lambda} and \textbf{API Gateway} for serverless components, reducing operational overhead by 25\%.}
  \resumeItem{Implemented asynchronous event-driven architecture using \textbf{Kafka} and AWS messaging services, improving throughput and decoupling.}
  \resumeItem{Optimized database access patterns for \textbf{DynamoDB} and \textbf{Aurora PostgreSQL}, improving query performance by 30\%.}
  \resumeItem{Containerized services with \textbf{Docker} and deployed on \textbf{EKS/ECS}, following blue-green deployment strategies for zero downtime.}
  \resumeItem{Built CI/CD pipelines using \textbf{GitHub Actions}, incorporating automated tests and security scans for release quality.}
  \resumeItem{Monitored distributed systems using \textbf{OpenTelemetry} and \textbf{CloudWatch} dashboards, enabling proactive incident response.}
  \resumeItem{Collaborated on event-driven system design using \textbf{Kafka}, enhancing system resilience and scalability.}
  \resumeItem{\textit{Environment: Java, Spring Boot, AWS (Lambda, API Gateway, DynamoDB, Aurora, S3, SQS, SNS, IAM, KMS, Secrets Manager, CloudFormation, CloudWatch), Docker, Kubernetes (EKS), Terraform, GitHub Actions, OpenTelemetry, Kafka.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed secure backend APIs using \textbf{C\#} with \textbf{ASP.NET Core Web API}, improving service reliability and maintainability.}
  \resumeItem{Designed and implemented RESTful services adhering to financial compliance and security standards using \textbf{OAuth2} and \textbf{JWT}.}
  \resumeItem{Built frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, enhancing user experience for financial workflows.}
  \resumeItem{Implemented asynchronous processing using \textbf{Kafka}, improving message reliability and throughput by 20\%.}
  \resumeItem{Optimized database queries and indexing strategies on \textbf{PostgreSQL} and \textbf{MySQL}, reducing latency by 25\%.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed on \textbf{Kubernetes}, improving environment consistency and deployment speed.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, integrating static code analysis and security checks.}
  \resumeItem{Collaborated with cross-functional teams to translate business requirements into secure, scalable technical solutions.}
  \resumeItem{Implemented cloud integrations using \textbf{AWS}, \textbf{Azure}, and \textbf{GCP} for identity management, storage, and messaging services.}
  \resumeItem{Enhanced system security and compliance by enforcing RBAC and audit logging aligned with financial regulations.}
  \resumeItem{\textit{Environment: C\#, ASP.NET Core, Angular, React, Kafka, PostgreSQL, MySQL, Docker, Kubernetes, Jenkins, Azure DevOps, AWS, Azure, GCP, OAuth2, JWT.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{C\#} with \textbf{.NET Framework} and \textbf{.NET Core}, supporting internal integrations and workflows.}
  \resumeItem{Built REST APIs and documented endpoints using \textbf{Swagger}, improving service discoverability and client integration.}
  \resumeItem{Delivered frontend features using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, enhancing internal dashboard usability.}
  \resumeItem{Implemented scheduled batch processing using \textbf{Quartz} and \textbf{Spring Scheduling}, improving operational efficiency.}
  \resumeItem{Optimized database performance with \textbf{Hibernate/JPA} and indexing strategies, reducing query times by 15\%.}
  \resumeItem{Standardized build and deployment pipelines using \textbf{Jenkins} and containerized environments with \textbf{Docker}.}
  \resumeItem{Supported cloud deployments on \textbf{AWS EC2}, \textbf{S3}, and \textbf{RDS}, improving infrastructure scalability.}
  \resumeItem{Enhanced automated testing coverage using \textbf{JUnit} and \textbf{Mockito}, improving release stability.}
  \resumeItem{Collaborated in Agile teams to deliver iterative enhancements aligned with business priorities.}
  \resumeItem{Maintained secure coding practices and compliance with internal policies for enterprise applications.}
  \resumeItem{\textit{Environment: C\#, .NET Framework, .NET Core, Angular, React, Quartz, Hibernate/JPA, Docker, Jenkins, AWS (EC2, S3, RDS), JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}