\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Kafka Administrator\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Designed, deployed, and maintained scalable \textbf{Kafka} clusters in production environments, ensuring high availability and security compliance.}
  \resumeItem{Automated Kafka provisioning and monitoring using \textbf{Ansible}, \textbf{Terraform}, and Linux shell scripting to reduce manual operational overhead.}
  \resumeItem{Monitored cluster health and performance using \textbf{Prometheus} and \textbf{Grafana}, troubleshooting broker outages and replication lag effectively.}
  \resumeItem{Managed Kafka ecosystem components including \textbf{ZooKeeper}, \textbf{Kafka Connect}, \textbf{Schema Registry}, and \textbf{MirrorMaker} to support data pipeline reliability.}
  \resumeItem{Implemented security protocols and access control lists (ACLs) on \textbf{Kafka} clusters running on \textbf{RHEL} and \textbf{Ubuntu} Linux platforms.}
  \resumeItem{Supported containerized Kafka deployments using \textbf{OpenShift Kubernetes} and helm charts, enabling resilient and scalable infrastructure.}
  \resumeItem{Developed automation scripts in \textbf{Python} and \textbf{Bash} to streamline Kafka cluster upgrades, patching, and incident response.}
  \resumeItem{Collaborated with engineering teams to onboard new Kafka use cases, ensuring platform reliability and compliance with enterprise standards.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Operating Systems:} & Linux (RHEL, Ubuntu), OpenShift Kubernetes \\
\textbf{Messaging \& Streaming:} & Kafka, Kafka Connect, Kafka Streams, MirrorMaker, Schema Registry, ZooKeeper, KRaft \\
\textbf{Infrastructure \& Automation:} & Ansible, Terraform, Bash, Python, Helm, Docker \\
\textbf{Monitoring \& Observability:} & Prometheus, Grafana \\
\textbf{Security:} & Kafka ACLs, Security Protocols, RBAC, Authentication and Authorization \\
\textbf{Cloud \& Container Orchestration:} & OpenShift Kubernetes, Docker \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Kafka Administrator}{USA}
\resumeItemListStart
  \resumeItem{Designed and maintained highly available \textbf{Kafka} clusters on \textbf{RHEL} and \textbf{Ubuntu}, ensuring zero downtime during upgrades and patching.}
  \resumeItem{Automated Kafka provisioning and configuration using \textbf{Terraform} and \textbf{Ansible}, reducing manual setup time by 40\%.}
  \resumeItem{Monitored cluster health and performance using \textbf{Prometheus} and \textbf{Grafana}, enabling proactive incident detection and resolution.}
  \resumeItem{Managed Kafka security by implementing \textbf{ACLs} and authentication protocols, ensuring compliance with enterprise security policies.}
  \resumeItem{Supported \textbf{Kafka Connect}, \textbf{Schema Registry}, and \textbf{MirrorMaker} for reliable data pipeline integrations and replication.}
  \resumeItem{Developed \textbf{Python} and \textbf{Bash} scripts to automate cluster maintenance and incident response workflows.}
  \resumeItem{Collaborated with engineering teams to onboard new Kafka use cases, optimizing throughput and cluster resource allocation.}
  \resumeItem{\textit{Environment: Kafka, Kafka Connect, Schema Registry, MirrorMaker, RHEL, Ubuntu, Ansible, Terraform, Prometheus, Grafana, Python, Bash, OpenShift Kubernetes.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Kafka Administrator}{USA}
\resumeItemListStart
  \resumeItem{Deployed and managed \textbf{Kafka} clusters using vendor-provided helm charts on \textbf{OpenShift Kubernetes}, improving cluster resiliency.}
  \resumeItem{Implemented Kafka disaster recovery (dc/dr) setups and observability, reducing recovery time by 30\%.}
  \resumeItem{Configured secure Kafka access controls and monitored cluster health with \textbf{Prometheus} and \textbf{Grafana}, ensuring SLA adherence.}
  \resumeItem{Automated Kafka upgrades and patching with minimal downtime using \textbf{Bash} and \textbf{Python} scripts.}
  \resumeItem{Managed data ingestion pipelines from external sources to Kafka and Kafka to Solr, enhancing data streaming reliability.}
  \resumeItem{Maintained Kafka ecosystem components including \textbf{ZooKeeper}, \textbf{Kafka Connect}, and \textbf{Schema Registry} for seamless integration.}
  \resumeItem{Provisioned and managed infrastructure using \textbf{Terraform} and \textbf{Ansible}, ensuring consistent and auditable deployments.}
  \resumeItem{\textit{Environment: Kafka, OpenShift Kubernetes, Helm, ZooKeeper, Kafka Connect, Schema Registry, Prometheus, Grafana, Terraform, Ansible, Python, Bash.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Kafka Administrator}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Designed and maintained \textbf{Kafka} clusters supporting mission-critical financial data streams on \textbf{Linux} platforms.}
  \resumeItem{Implemented Kafka security protocols and ACLs, ensuring secure data access and compliance with internal policies.}
  \resumeItem{Monitored Kafka cluster health and performance using \textbf{Prometheus} and \textbf{Grafana}, reducing incident response times by 25\%.}
  \resumeItem{Automated Kafka topic creation, partition management, and configuration using \textbf{Bash} scripts, improving operational efficiency.}
  \resumeItem{Managed Kafka Connect and MirrorMaker pipelines to support data replication and integration with external systems.}
  \resumeItem{Collaborated with cross-functional teams to onboard new Kafka use cases and optimize cluster resource utilization.}
  \resumeItem{Supported Kafka upgrades and patching with minimal service disruption through scripted automation.}
  \resumeItem{\textit{Environment: Kafka, Linux (RHEL/Ubuntu), Kafka Connect, MirrorMaker, Prometheus, Grafana, Bash, Python, ACLs.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Supported backend services and data streaming infrastructure using \textbf{Kafka} and \textbf{Linux} environments.}
  \resumeItem{Developed automation scripts in \textbf{Bash} to streamline deployments and monitoring of Kafka clusters.}
  \resumeItem{Monitored cluster performance and addressed broker outages to maintain high availability.}
  \resumeItem{Assisted in Kafka topic management and implemented security controls to safeguard data pipelines.}
  \resumeItem{Collaborated with teams to integrate Kafka with internal data platforms, improving data flow reliability.}
  \resumeItem{Contributed to containerization efforts using \textbf{Docker} for development and testing environments.}
  \resumeItem{Participated in Kafka upgrade planning and execution to minimize downtime and ensure stability.}
  \resumeItem{\textit{Environment: Kafka, Linux, Bash, Docker, Kafka topic management, monitoring.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}