\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Kafka Administrator \& Automation Specialist\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Led Kafka administration and automation initiatives with over \textbf{8 years} of experience managing scalable, secure, and highly available Apache Kafka and Confluent Kafka clusters.}
  \resumeItem{Automated Kafka deployment, configuration, and upgrades using \textbf{Ansible}, \textbf{Terraform}, \textbf{Python}, and \textbf{Shell scripting}, improving operational efficiency by 40\%.}
  \resumeItem{Deployed and managed Kafka clusters on \textbf{Kubernetes/OpenShift} using \textbf{Confluent for Kubernetes (CFK)}, enabling seamless cloud and on-premises integration.}
  \resumeItem{Implemented GitOps-based CI/CD pipelines with \textbf{ArgoCD} and \textbf{Jenkins}, streamlining Kafka infrastructure delivery and reducing deployment errors.}
  \resumeItem{Monitored Kafka performance using \textbf{Prometheus}, \textbf{Grafana}, \textbf{JMX}, and \textbf{Confluent Control Center} to ensure cluster health and availability.}
  \resumeItem{Configured Kafka Connectors (S3, JDBC, Snowflake) and managed \textbf{Confluent Schema Registry} to support data integration and schema evolution.}
  \resumeItem{Secured Kafka environments with \textbf{SASL}, \textbf{SSL/TLS}, \textbf{RBAC}, \textbf{ACLs}, and automated certificate management, enhancing data protection and compliance.}
  \resumeItem{Supported disaster recovery through multi-region replication and \textbf{Cluster Linking}, ensuring business continuity and data resiliency.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Messaging \& Streaming:} & Kafka, Confluent Kafka, Kafka Connect (S3, JDBC, Snowflake), Confluent Schema Registry, KRaft mode, Cluster Linking \\
\textbf{Automation \& IaC:} & Ansible, Terraform, Python, Shell scripting, GitOps (ArgoCD, Jenkins) \\
\textbf{Containerization \& Orchestration:} & Kubernetes, OpenShift, Confluent for Kubernetes (CFK), Docker, Helm \\
\textbf{Monitoring \& Observability:} & Prometheus, Grafana, JMX, Confluent Control Center \\
\textbf{Security \& Networking:} & SASL, SSL/TLS, RBAC, ACLs, Certificate Management, Kerberos, TLS \\
\textbf{Operating Systems \& Tools:} & Linux, Git, Jenkins, Bash, Python scripting \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Kafka Administrator \& Automation Lead}{USA}
\resumeItemListStart
  \resumeItem{Automated Kafka cluster installation, configuration, and patching using \textbf{Ansible}, \textbf{Terraform}, and \textbf{Python}, reducing manual deployment time by 50\%.}
  \resumeItem{Managed Kafka topics, partitions, and replication in \textbf{KRaft mode}, ensuring high availability and optimized throughput for critical financial data streams.}
  \resumeItem{Deployed and maintained \textbf{Confluent Platform} on \textbf{Kubernetes} using \textbf{Confluent for Kubernetes (CFK)}, enabling scalable multi-environment Kafka infrastructure.}
  \resumeItem{Implemented GitOps workflows with \textbf{ArgoCD} and \textbf{Jenkins} for Kafka infrastructure CI/CD, improving deployment reliability and traceability.}
  \resumeItem{Monitored Kafka clusters using \textbf{Prometheus}, \textbf{Grafana}, and \textbf{Confluent Control Center}, proactively resolving performance bottlenecks and outages.}
  \resumeItem{Configured and managed Kafka Connectors including \textbf{S3}, \textbf{JDBC}, and \textbf{Snowflake}, facilitating seamless data integration across platforms.}
  \resumeItem{Enforced Kafka security using \textbf{SASL}, \textbf{SSL/TLS}, \textbf{RBAC}, and \textbf{ACLs}, automating certificate renewals to maintain compliance.}
  \resumeItem{\textit{Environment: Kafka, Confluent Kafka, Kubernetes, CFK, Ansible, Terraform, Python, Shell scripting, ArgoCD, Jenkins, Prometheus, Grafana, JMX, Confluent Control Center, SASL, SSL/TLS, RBAC, ACLs.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Kafka Infrastructure Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and automated Kafka cluster provisioning and upgrades using \textbf{Terraform} and \textbf{Ansible}, achieving 99.9\% uptime across multi-region deployments.}
  \resumeItem{Managed Kafka cluster configurations, topics, and replication strategies, optimizing for fault tolerance and high throughput in cloud environments.}
  \resumeItem{Deployed \textbf{Confluent Kafka} on \textbf{OpenShift} with \textbf{CFK}, enabling containerized Kafka services with seamless scaling and management.}
  \resumeItem{Built CI/CD pipelines using \textbf{Jenkins} and GitOps principles, automating Kafka infrastructure changes and reducing deployment lead time by 35\%.}
  \resumeItem{Monitored cluster health with \textbf{Prometheus}, \textbf{Grafana}, and \textbf{JMX}, implementing alerts and dashboards for operational visibility.}
  \resumeItem{Configured Kafka Connectors for \textbf{S3}, \textbf{JDBC}, and \textbf{Snowflake}, automating data ingestion and export workflows.}
  \resumeItem{Implemented Kafka security protocols including \textbf{Kerberos}, \textbf{SASL}, and \textbf{SSL/TLS}, enhancing access control and data encryption.}
  \resumeItem{\textit{Environment: Kafka, Confluent Kafka, OpenShift, CFK, Terraform, Ansible, Jenkins, Prometheus, Grafana, JMX, Kafka Connect, Kerberos, SASL, SSL/TLS.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer - Kafka \& Automation}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Managed Kafka clusters supporting payment processing pipelines, ensuring high availability and low latency through partition and replication tuning.}
  \resumeItem{Automated Kafka deployment and configuration using \textbf{Shell scripting} and \textbf{Python}, improving consistency and reducing manual errors.}
  \resumeItem{Configured and maintained \textbf{Kafka Connect} with \textbf{JDBC} and \textbf{S3} connectors, enabling reliable data movement between Kafka and external systems.}
  \resumeItem{Monitored Kafka performance with \textbf{Prometheus} and \textbf{Grafana}, identifying and resolving bottlenecks to improve throughput by 20\%.}
  \resumeItem{Implemented security features including \textbf{SASL}, \textbf{SSL/TLS}, and \textbf{ACLs}, automating certificate management to meet compliance standards.}
  \resumeItem{Supported disaster recovery by configuring multi-region replication with \textbf{Cluster Linking}, ensuring data availability during outages.}
  \resumeItem{Collaborated with DevOps teams to integrate Kafka infrastructure into CI/CD pipelines using \textbf{Jenkins} and \textbf{GitOps} practices.}
  \resumeItem{\textit{Environment: Kafka, Kafka Connect, Shell scripting, Python, Prometheus, Grafana, SASL, SSL/TLS, ACLs, Cluster Linking, Jenkins, GitOps.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer - Middleware \& Automation}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Supported middleware services integrating Kafka messaging for game telemetry and analytics pipelines, improving data reliability.}
  \resumeItem{Automated deployment scripts using \textbf{Shell scripting} to provision Kafka clusters and related infrastructure components.}
  \resumeItem{Assisted in configuring Kafka topics, partitions, and replication to optimize message delivery and fault tolerance.}
  \resumeItem{Monitored Kafka cluster health using \textbf{JMX} and custom scripts, reducing incident response times by 30\%.}
  \resumeItem{Implemented basic security controls including \textbf{SSL/TLS} encryption and access control lists for Kafka clusters.}
  \resumeItem{Collaborated with development teams to integrate Kafka-based event streams into microservices architecture.}
  \resumeItem{Maintained CI/CD pipelines using \textbf{Jenkins} and containerized deployments with \textbf{Docker}.}
  \resumeItem{\textit{Environment: Kafka, Shell scripting, JMX, SSL/TLS, ACLs, Jenkins, Docker, Middleware services.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}