\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Led design and development of full-stack enterprise GIS applications using \textbf{C\# / .NET Core}, \textbf{ArcGIS Enterprise}, and \textbf{SQL Server}, improving spatial data integration.}
  \resumeItem{Architected scalable REST APIs and integrated geospatial data with enterprise systems leveraging \textbf{Azure cloud services} and \textbf{ESRI ArcGIS Pro} tools.}
  \resumeItem{Mentored development teams in Agile environments, driving adoption of best practices in \textbf{GIS technologies}, \textbf{.NET Core}, and frontend frameworks like \textbf{Angular} and \textbf{React}.}
  \resumeItem{Delivered high-performance backend services and spatial data management solutions, enhancing application responsiveness and maintainability.}
  \resumeItem{Experienced in hybrid cloud deployments, leveraging \textbf{Azure} and container orchestration for reliable, scalable GIS-enabled enterprise applications.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & C\#, ASP.NET Core (.NET 6+), Java, TypeScript, Angular, React \\
\textbf{GIS Technologies:} & ESRI ArcGIS Pro, ArcGIS Enterprise, ArcMap, Spatial Data Management, Geospatial Databases \\
\textbf{Databases:} & SQL Server, PostgreSQL, MySQL, Geospatial Databases, Hibernate/JPA \\
\textbf{Cloud \& DevOps:} & Microsoft Azure (App Service, Azure AD, Key Vault, Azure Monitor), Docker, Kubernetes, Terraform, Azure DevOps, Jenkins \\
\textbf{API \& Integration:} & REST APIs, OpenAPI/Swagger, OAuth2/OIDC, JWT, Microservices Architecture \\
\textbf{Tools \& Others:} & Git, Jira, Confluence, Postman, SonarQube, Snyk \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led design and development of \textbf{C\#} backend services using \textbf{ASP.NET Core Web API}, improving integration with spatial data and enterprise workflows.}
  \resumeItem{Architected and implemented RESTful APIs to expose GIS-enabled services, enhancing interoperability with \textbf{ArcGIS Enterprise} and internal systems.}
  \resumeItem{Developed spatial data management solutions leveraging \textbf{SQL Server} geospatial features, improving query efficiency by 30\%.}
  \resumeItem{Integrated \textbf{Azure cloud} services for scalable deployment of GIS applications, enabling hybrid cloud architecture and secure access management.}
  \resumeItem{Mentored a team of developers on best practices for \textbf{GIS application development} and \textbf{full-stack .NET} technologies, improving code quality and delivery speed.}
  \resumeItem{Delivered frontend modules using \textbf{Angular 16/17} and \textbf{React (Hooks)} with \textbf{TypeScript}, enhancing user experience for spatial data visualization.}
  \resumeItem{Implemented CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, automating deployments with quality and security gates.}
  \resumeItem{Improved API performance and reliability by optimizing \textbf{SQL Server} spatial queries and caching strategies, reducing latency by 25\%.}
  \resumeItem{Containerized microservices using \textbf{Docker} and deployed on \textbf{Kubernetes (EKS)}, ensuring scalable and resilient GIS platform components.}
  \resumeItem{Applied security best practices with \textbf{OAuth2/OIDC} and \textbf{JWT} for secure API access and enterprise compliance.}
  \resumeItem{Collaborated closely with GIS analysts to integrate \textbf{ArcGIS Pro} workflows into enterprise applications, streamlining spatial data processing.}
  \resumeItem{Utilized \textbf{OpenTelemetry} and \textbf{CloudWatch} for observability, enabling proactive monitoring of GIS services.}
  \resumeItem{\textit{Environment: C\#, ASP.NET Core, ArcGIS Enterprise, ArcGIS Pro, SQL Server, Azure (App Service, AD, Key Vault, Monitor), Docker, Kubernetes, Jenkins, GitHub Actions, Angular, React, TypeScript, OAuth2, JWT, OpenTelemetry, CloudWatch.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 17} and \textbf{Spring Boot}, integrating geospatial data with enterprise APIs for improved spatial analytics.}
  \resumeItem{Built and maintained RESTful APIs with \textbf{OpenAPI} specifications, facilitating GIS data exchange and service orchestration.}
  \resumeItem{Implemented event-driven processing using \textbf{Kafka}, improving asynchronous handling of spatial data updates and notifications.}
  \resumeItem{Designed and optimized data storage using \textbf{PostgreSQL} with geospatial extensions, enhancing query performance by 20\%.}
  \resumeItem{Delivered frontend features using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, improving spatial data visualization and user interaction.}
  \resumeItem{Provisioned and managed infrastructure using \textbf{Terraform} and \textbf{CloudFormation} for consistent GIS service deployments on \textbf{AWS}.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed on \textbf{EKS/ECS}, ensuring scalability and high availability of GIS services.}
  \resumeItem{Implemented security controls using \textbf{IAM}, \textbf{KMS}, and \textbf{Secrets Manager} to protect sensitive geospatial data and APIs.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins}, enforcing quality and security standards for GIS-related microservices.}
  \resumeItem{Monitored system health and performance using \textbf{OpenTelemetry} and \textbf{CloudWatch}, improving incident response times.}
  \resumeItem{\textit{Environment: Java 17, Spring Boot, REST, Kafka, PostgreSQL (PostGIS), AWS (EKS, ECS, IAM, KMS, Secrets Manager, CloudWatch), Docker, Terraform, Jenkins, Angular, React, TypeScript.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8/11} and \textbf{Spring Boot 2.x}, integrating enterprise GIS data into payment processing workflows.}
  \resumeItem{Built and maintained REST APIs with \textbf{OpenAPI/Swagger}, enabling secure access to spatial data services within the enterprise.}
  \resumeItem{Implemented \textbf{C\#} microservices with \textbf{ASP.NET Core Web API} to support partner integrations and spatial data orchestration.}
  \resumeItem{Delivered frontend modules using \textbf{Angular 8--12} and \textbf{React (Hooks)} with \textbf{TypeScript}, enhancing geospatial data visualization for internal tools.}
  \resumeItem{Optimized database queries and indexing strategies on \textbf{PostgreSQL/MySQL}, improving spatial data retrieval times by 25\%.}
  \resumeItem{Implemented asynchronous processing using \textbf{Kafka}, enhancing reliability of spatial data updates and event handling.}
  \resumeItem{Containerized services with \textbf{Docker} and deployed using \textbf{Kubernetes}, enabling consistent GIS application environments.}
  \resumeItem{Integrated cloud platforms \textbf{AWS}, \textbf{Azure}, and \textbf{GCP} for identity, storage, and messaging services supporting GIS workflows.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing quality gates and security compliance.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, C\#, ASP.NET Core, REST, OpenAPI, Angular, React, TypeScript, Kafka, PostgreSQL/MySQL, Docker, Kubernetes, Jenkins, Azure DevOps, AWS, Azure, GCP.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8} and \textbf{Spring Boot}, supporting enterprise GIS data processing and integration.}
  \resumeItem{Built REST APIs and internal service endpoints using \textbf{C\#} with \textbf{.NET Framework / .NET Core} for spatial data workflows.}
  \resumeItem{Delivered frontend components using \textbf{Angular 5/6/7} and \textbf{React 16} with \textbf{TypeScript}, improving spatial data visualization and user interactions.}
  \resumeItem{Optimized database queries using \textbf{Hibernate/JPA} and indexing, improving spatial data retrieval efficiency.}
  \resumeItem{Implemented scheduled processing using \textbf{Quartz} and \textbf{Spring Scheduling} for periodic GIS data updates.}
  \resumeItem{Containerized development and test environments using \textbf{Docker}, enabling consistent builds and deployments.}
  \resumeItem{Supported cloud deployments on \textbf{AWS (EC2, S3, RDS)}, integrating GIS data storage and processing solutions.}
  \resumeItem{Improved release stability by implementing automated testing with \textbf{JUnit} and \textbf{Mockito}.}
  \resumeItem{\textit{Environment: Java 8, Spring Boot, C\#, .NET Framework/Core, REST, Angular, React, TypeScript, Hibernate/JPA, Docker, AWS (EC2, S3, RDS), JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}