\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Innovative \textbf{Software Developer} with 8+ years designing scalable \textbf{Java} microservices and integrations, specializing in \textbf{Spring Boot} and API-driven architectures.}
  \resumeItem{Experienced in building robust event-driven systems using \textbf{Kafka} and seamless API integrations with \textbf{SOAP} and \textbf{REST}, emphasizing maintainability and scalability.}
  \resumeItem{Proficient in leveraging cloud platforms, particularly \textbf{Google Cloud Platform} and relational databases such as \textbf{Oracle} and \textbf{Postgres}, to deliver high-availability solutions.}
  \resumeItem{Strong technical leadership and mentorship skills, driving best practices in CI/CD pipelines, code quality, and incident management within agile, collaborative teams.}
  \resumeItem{Passionate about advancing Product Information Management (PIM) platforms and integrating innovative data solutions to streamline business workflows.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java (8/11/17/21), Spring Boot (1.5/2.x/3.x), Kafka, REST, SOAP, C\#, Go, TypeScript, Angular, React \\
\textbf{Cloud Platforms:} & Google Cloud Platform (Pub/Sub, Cloud SQL), AWS, Azure \\
\textbf{Databases:} & Oracle, PostgreSQL, MySQL, DynamoDB, Redis \\
\textbf{CI/CD \& DevOps:} & Bamboo, Bitbucket, Jenkins, GitHub Actions, Docker, Kubernetes, Terraform, Helm \\
\textbf{Testing \& Quality:} & JUnit 5, Mockito, SonarQube, Pact, Testcontainers, WireMock \\
\textbf{Observability \& Monitoring:} & Grafana, Newrelic, OpenTelemetry, CloudWatch, Prometheus \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led design and development of scalable \textbf{Java 17/21} microservices using \textbf{Spring Boot 3}, enhancing modularity and system reliability.}
  \resumeItem{Developed and integrated \textbf{REST} and \textbf{gRPC} APIs, ensuring compliance with \textbf{OpenAPI} standards and seamless cross-platform communication.}
  \resumeItem{Implemented robust security using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT}, enforcing enterprise-grade access controls and compliance.}
  \resumeItem{Architected event-driven workflows with \textbf{Kafka}, improving asynchronous processing and data streaming reliability.}
  \resumeItem{Optimized CI/CD pipelines using \textbf{Bamboo} and \textbf{Bitbucket}, enforcing code quality through \textbf{SonarQube} and automated security scans.}
  \resumeItem{Monitored application health and performance using \textbf{Grafana} and \textbf{Newrelic}, reducing incident resolution times by 30\%.}
  \resumeItem{Mentored engineering teams on best practices for scalable API design, microservice architecture, and cloud-native development.}
  \resumeItem{Led incident management and root cause analysis in a 24/7 on-call environment, ensuring minimal downtime and rapid recovery.}
  \resumeItem{Collaborated with stakeholders to define strategic vision for product data platforms, aligning technical roadmaps with business goals.}
  \resumeItem{Built proof of concepts leveraging \textbf{Google Cloud Platform} services such as \textbf{Pub/Sub} and \textbf{Cloud SQL} to validate new integration approaches.}
  \resumeItem{\textit{Environment: Java 17/21, Spring Boot 3, Kafka, REST, SOAP, OAuth2/OIDC, JWT, Bamboo, Bitbucket, SonarQube, Grafana, Newrelic, Google Cloud Platform (Pub/Sub, Cloud SQL), Oracle, PostgreSQL.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and developed scalable \textbf{Java 17} microservices with \textbf{Spring Boot}, improving service modularity and API consistency.}
  \resumeItem{Implemented \textbf{Kafka}-based event streaming to decouple services and enhance throughput for high-volume data pipelines.}
  \resumeItem{Built and maintained \textbf{REST} and \textbf{gRPC} APIs, ensuring robust contract adherence and seamless internal integrations.}
  \resumeItem{Developed automation tools in \textbf{Go} to streamline operational workflows and reduce manual intervention.}
  \resumeItem{Optimized database access patterns on \textbf{PostgreSQL} and \textbf{DynamoDB}, improving query performance and reducing latency by 25\%.}
  \resumeItem{Containerized microservices using \textbf{Docker} and deployed on \textbf{Kubernetes (EKS/ECS)}, enabling repeatable and scalable releases.}
  \resumeItem{Provisioned infrastructure with \textbf{Terraform} and \textbf{CloudFormation} for consistent and auditable cloud environments.}
  \resumeItem{Implemented observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling proactive monitoring and alerting.}
  \resumeItem{Executed contract testing with \textbf{Pact} to prevent cross-service regressions and improve integration reliability.}
  \resumeItem{Delivered frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, enhancing user experience for internal tools.}
  \resumeItem{\textit{Environment: Java 17, Spring Boot, Kafka, REST, gRPC, Go, PostgreSQL, DynamoDB, Docker, Kubernetes (EKS/ECS), Terraform, CloudFormation, OpenTelemetry, Angular, React, TypeScript, Pact.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed \textbf{Java 8/11} microservices using \textbf{Spring Boot 2.x}, focusing on reusable APIs and scalable backend components.}
  \resumeItem{Built and maintained \textbf{REST} APIs with \textbf{OpenAPI/Swagger}, enforcing validation, versioning, and error handling standards.}
  \resumeItem{Implemented secure authentication and authorization using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT} aligned with RBAC policies.}
  \resumeItem{Integrated asynchronous processing using \textbf{Kafka}, improving system reliability with retry and dead-letter queue patterns.}
  \resumeItem{Constructed integration endpoints in \textbf{C\#} with \textbf{ASP.NET Core Web API}, enabling partner and internal orchestration workflows.}
  \resumeItem{Improved database performance on \textbf{PostgreSQL} and \textbf{MySQL} through query optimization and indexing, reducing response times by 25\%.}
  \resumeItem{Developed frontend modules using \textbf{Angular 8--12} and \textbf{React (Hooks)} with \textbf{TypeScript} for workflow-heavy and dashboard experiences.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling environment-based configuration management.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing quality gates with \textbf{SonarQube}.}
  \resumeItem{Collaborated on multi-cloud platform integrations including \textbf{AWS}, \textbf{Azure}, and \textbf{GCP} for identity, storage, and messaging solutions.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, Kafka, REST, OpenAPI, Spring Security, OAuth2/OIDC, JWT, C\#, ASP.NET Core, PostgreSQL, MySQL, Angular, React, Docker, Kubernetes, Jenkins, Azure DevOps, AWS, Azure, GCP.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8} and \textbf{Spring Boot (1.5/2.0)}, delivering scalable APIs and reusable components.}
  \resumeItem{Built \textbf{REST} APIs and documented endpoints using \textbf{Swagger}, supporting internal and external integrations.}
  \resumeItem{Implemented service endpoints using \textbf{C\#} with \textbf{.NET Framework / .NET Core}, enabling cross-platform orchestration workflows.}
  \resumeItem{Delivered frontend features using \textbf{Angular 5/6/7} and \textbf{React 16} with \textbf{TypeScript}, building reusable UI components and dashboards.}
  \resumeItem{Implemented scheduled batch processing using \textbf{Quartz} and \textbf{Spring Scheduling} for periodic data workflows.}
  \resumeItem{Optimized database queries and indexing with \textbf{Hibernate/JPA}, improving performance on \textbf{Oracle} databases.}
  \resumeItem{Standardized builds and CI pipelines using \textbf{Maven/Gradle} and \textbf{Jenkins}, improving release consistency.}
  \resumeItem{Containerized development and testing environments using \textbf{Docker}, enabling reproducible builds.}
  \resumeItem{Supported deployments on \textbf{AWS (EC2, S3, RDS)}, ensuring cloud readiness and scalability.}
  \resumeItem{Enhanced automated testing coverage using \textbf{JUnit} and \textbf{Mockito}, improving code reliability and stability.}
  \resumeItem{\textit{Environment: Java 8, Spring Boot, REST, Swagger, C\#, .NET Framework/Core, Angular, React, Hibernate/JPA, Oracle, Docker, Jenkins, AWS EC2/S3/RDS, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}