\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Designed, deployed, and maintained scalable \textbf{Kafka} clusters and Linux infrastructure supporting real-time data pipelines and enterprise-grade environments.}
  \resumeItem{Automated Kafka provisioning, configuration, and monitoring using \textbf{Ansible}, \textbf{Terraform}, and shell scripting, improving operational efficiency and reliability.}
  \resumeItem{Monitored cluster health and performance using \textbf{Prometheus} and \textbf{Grafana}, reducing incident response times and ensuring high availability.}
  \resumeItem{Implemented security protocols and access controls including \textbf{ACLs} and schema registry management to ensure platform compliance and data integrity.}
  \resumeItem{Experienced in \textbf{Linux} administration (\textbf{RHEL}, \textbf{Ubuntu}) and container orchestration with \textbf{OpenShift Kubernetes} for Kafka deployments.}
  \resumeItem{Developed automation scripts in \textbf{Python} and \textbf{Bash} to streamline Kafka cluster maintenance and incident resolution.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Messaging \& Streaming:} & Kafka, Kafka Connect, Kafka Streams, MirrorMaker, Schema Registry, ZooKeeper, KRaft \\
\textbf{Operating Systems \& Infrastructure:} & Linux (RHEL, Ubuntu), OpenShift Kubernetes, Docker, Ansible, Terraform \\
\textbf{Monitoring \& Observability:} & Prometheus, Grafana, OpenTelemetry \\
\textbf{Scripting \& Automation:} & Python, Bash, Shell scripting \\
\textbf{Security \& Access Control:} & Kafka ACLs, Security Protocols, RBAC, OAuth2/OIDC, JWT \\
\textbf{Cloud \& DevOps:} & Infrastructure as Code (IaC), CI/CD pipelines, Helm charts, Kubernetes \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Java Developer}{USA}
\resumeItemListStart
  \resumeItem{Designed and maintained \textbf{Kafka} clusters with high availability, automating deployments and upgrades using \textbf{Terraform} and \textbf{Ansible}, reducing downtime by 30\%.}
  \resumeItem{Monitored Kafka cluster health and performance using \textbf{Prometheus} and \textbf{Grafana}, enabling proactive incident detection and reducing replication lag.}
  \resumeItem{Implemented Kafka security policies including \textbf{ACLs} and schema registry management to enforce data access controls and compliance.}
  \resumeItem{Developed automation scripts in \textbf{Python} and \textbf{Bash} for cluster provisioning, patching, and incident resolution, improving operational efficiency.}
  \resumeItem{Supported Linux infrastructure (\textbf{RHEL}, \textbf{Ubuntu}) hosting Kafka clusters, ensuring platform reliability and performance.}
  \resumeItem{Collaborated with engineering teams to onboard new Kafka use cases, integrating with \textbf{Kafka Connect} and \textbf{MirrorMaker} for data pipeline expansion.}
  \resumeItem{Containerized Kafka components and deployed on \textbf{OpenShift Kubernetes} using vendor-provided Helm charts and Docker images.}
  \resumeItem{Automated CI/CD pipelines and enforced quality gates using Jenkins and GitHub Actions for Kafka-related deployments.}
  \resumeItem{Implemented observability enhancements using \textbf{OpenTelemetry} and CloudWatch for end-to-end Kafka monitoring.}
  \resumeItem{Performed root cause analysis on Kafka outages and replication issues, reducing incident recurrence by 25\%.}
  \resumeItem{Optimized Kafka throughput and reliability by tuning topics, partitions, and broker configurations.}
  \resumeItem{Managed Kafka Streams applications to support real-time data processing with minimal latency.}
  \resumeItem{Ensured security compliance by integrating enterprise authentication and authorization frameworks with Kafka clusters.}
  \resumeItem{Environment: \textbf{Kafka}, \textbf{Prometheus}, \textbf{Grafana}, \textbf{Ansible}, \textbf{Terraform}, \textbf{Python}, \textbf{Bash}, \textbf{RHEL}, \textbf{Ubuntu}, \textbf{OpenShift Kubernetes}, \textbf{Docker}, Jenkins, GitHub Actions.}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Deployed and maintained highly available \textbf{Kafka} clusters, performing upgrades and patching with minimal downtime in production environments.}
  \resumeItem{Automated Kafka provisioning and configuration using \textbf{Terraform} and \textbf{Ansible}, reducing manual intervention by 40\%.}
  \resumeItem{Monitored Kafka cluster health using \textbf{Prometheus} and \textbf{Grafana}, identifying and resolving broker outages and replication lag.}
  \resumeItem{Implemented Kafka security protocols and access controls including \textbf{ACLs} to protect sensitive data streams.}
  \resumeItem{Developed and maintained \textbf{Python} and \textbf{Bash} scripts for Kafka cluster automation and incident management.}
  \resumeItem{Supported Linux-based Kafka infrastructure (\textbf{RHEL}, \textbf{Ubuntu}) ensuring platform stability and performance.}
  \resumeItem{Managed Kafka Connect and MirrorMaker pipelines for data ingestion and replication across data centers.}
  \resumeItem{Containerized Kafka components and deployed on Kubernetes clusters using Helm charts and Docker images.}
  \resumeItem{Collaborated with cross-functional teams to onboard new Kafka use cases, ensuring compliance with security standards.}
  \resumeItem{Performed root cause analysis for platform-level incidents, reducing downtime and improving cluster resiliency.}
  \resumeItem{Integrated Kafka monitoring with \textbf{OpenTelemetry} and AWS CloudWatch for enhanced observability.}
  \resumeItem{Environment: \textbf{Kafka}, \textbf{Prometheus}, \textbf{Grafana}, \textbf{Terraform}, \textbf{Ansible}, \textbf{Python}, \textbf{Bash}, \textbf{RHEL}, \textbf{Ubuntu}, Kubernetes, Docker, Helm.}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Administered and scaled \textbf{Kafka} clusters supporting asynchronous processing and real-time event streaming.}
  \resumeItem{Implemented Kafka topic management, partitioning, and ACLs to optimize throughput and secure data access.}
  \resumeItem{Developed \textbf{Bash} and \textbf{Python} automation scripts to streamline Kafka cluster maintenance and monitoring tasks.}
  \resumeItem{Monitored cluster health and performance using \textbf{Prometheus} and \textbf{Grafana}, reducing replication lag and broker outages.}
  \resumeItem{Supported Linux environments (\textbf{Ubuntu}, \textbf{RHEL}) hosting Kafka brokers, ensuring high availability and fault tolerance.}
  \resumeItem{Managed Kafka Connectors for data ingestion pipelines and ensured data consistency across systems.}
  \resumeItem{Collaborated with security teams to implement Kafka security best practices including ACLs and encryption.}
  \resumeItem{Containerized Kafka components using Docker and deployed on Kubernetes clusters for scalable environments.}
  \resumeItem{Automated CI/CD workflows for Kafka deployments using Jenkins and Azure DevOps.}
  \resumeItem{Performed root cause analysis and incident resolution to maintain platform reliability.}
  \resumeItem{Environment: \textbf{Kafka}, \textbf{Prometheus}, \textbf{Grafana}, \textbf{Python}, \textbf{Bash}, \textbf{Ubuntu}, \textbf{RHEL}, Docker, Kubernetes, Jenkins, Azure DevOps.}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Supported backend services and asynchronous event processing using \textbf{Kafka} for internal tooling and web applications.}
  \resumeItem{Developed and maintained Kafka topics, partitions, and broker configurations to improve message throughput and reliability.}
  \resumeItem{Automated Kafka deployment and monitoring tasks using \textbf{Bash} scripts and Linux shell commands.}
  \resumeItem{Monitored Kafka cluster health using open-source tools, reducing downtime and improving alerting.}
  \resumeItem{Managed Linux-based Kafka infrastructure (\textbf{RHEL}, \textbf{Ubuntu}) ensuring stable production environments.}
  \resumeItem{Collaborated with teams to integrate Kafka with other messaging systems and data platforms.}
  \resumeItem{Containerized Kafka components using Docker for consistent development and testing environments.}
  \resumeItem{Assisted in Kafka upgrades and patching, ensuring minimal disruption to services.}
  \resumeItem{Environment: \textbf{Kafka}, \textbf{Bash}, \textbf{RHEL}, \textbf{Ubuntu}, Docker, Linux Shell Scripting.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}