\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8+ years} of hands-on experience in \textbf{GIS application development} and \textbf{.NET (C\#)} backend services with strong focus on \textbf{Hexagon Intergraph technologies} and \textbf{Oracle SQL/PL\_SQL} performance tuning.}
  \resumeItem{Specialized in \textbf{Energy \& Utilities} domain, developing scalable GIS solutions integrating \textbf{G/Technology} and \textbf{G/Net Viewer} platforms with enterprise systems.}
  \resumeItem{Implemented robust \textbf{Windows Server} based deployments and maintained high availability environments using Agile methodologies and \textbf{Jira} for efficient project delivery.}
  \resumeItem{Applied strong analytical skills to troubleshoot complex database and application performance issues, enhancing system reliability and user experience.}
  \resumeItem{Collaborated effectively across teams, demonstrating excellent communication and teamwork to deliver integrated GIS and enterprise applications.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & C\#, \textbf{.NET Framework}, ASP.NET Core, Oracle SQL, PL\_SQL, Hexagon Intergraph (G/Technology, G/Net Viewer) \\
\textbf{Databases:} & Oracle, SQL Server, performance tuning, query optimization \\
\textbf{GIS \& Geospatial Tools:} & Hexagon Intergraph, FME, ESRI ArcGIS (basic familiarity) \\
\textbf{Operating Systems \& Servers:} & Windows Server environments, Windows 10/11 \\
\textbf{Development \& Integration:} & Agile methodologies, Jira, API integrations, enterprise integration patterns, API management \\
\textbf{DevOps \& CI/CD:} & Familiarity with CI/CD pipelines, DevOps workflows, Git, Jenkins, Azure DevOps \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Designed and developed \textbf{GIS-integrated enterprise applications} using \textbf{C\#} and \textbf{.NET Framework}, improving data accuracy and system responsiveness by 30\%.}
  \resumeItem{Led performance tuning of \textbf{Oracle SQL} and \textbf{PL\_SQL} queries, reducing database latency by 25\% in critical energy data workflows.}
  \resumeItem{Implemented \textbf{Hexagon Intergraph G/Technology} integration modules, enhancing GIS data visualization and editing capabilities for utility asset management.}
  \resumeItem{Managed deployments and maintenance on \textbf{Windows Server} environments, ensuring 99.9\% uptime for GIS applications supporting field operations.}
  \resumeItem{Collaborated in Agile teams using \textbf{Jira} to deliver iterative releases, improving cross-team communication and project transparency.}
  \resumeItem{Developed API integrations between GIS platforms and enterprise systems, streamlining data exchange and reducing manual data entry errors.}
  \resumeItem{Applied strong problem-solving skills to troubleshoot complex system issues, achieving 20\% faster incident resolution times.}
  \resumeItem{Supported CI/CD pipelines using \textbf{Jenkins} and \textbf{Git}, automating build and deployment processes for GIS applications.}
  \resumeItem{Enhanced security and access control for GIS services by integrating enterprise authentication mechanisms and role-based access controls.}
  \resumeItem{Conducted knowledge transfer sessions on \textbf{Hexagon Intergraph} technologies and Oracle performance tuning for junior developers.}
  \resumeItem{\textit{Environment: C\#, .NET Framework, Oracle SQL, PL\_SQL, Hexagon Intergraph (G/Technology, G/Net Viewer), Windows Server, Agile, Jira, Jenkins, Git.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{C\#} and \textbf{.NET Core}, integrating geospatial data for enterprise utility applications with improved performance.}
  \resumeItem{Optimized \textbf{Oracle SQL} queries and \textbf{PL\_SQL} procedures, enhancing data retrieval speeds by 30\% for large-scale GIS datasets.}
  \resumeItem{Implemented \textbf{Hexagon Intergraph G/Net Viewer} customizations, improving user interaction with spatial data in utility asset management.}
  \resumeItem{Maintained and configured \textbf{Windows Server} environments to support high availability GIS applications used in energy sector operations.}
  \resumeItem{Collaborated in Agile teams using \textbf{Jira} to manage sprints and deliverables, ensuring timely completion of GIS-related features.}
  \resumeItem{Built automated deployment pipelines using \textbf{Azure DevOps} and \textbf{GitHub Actions}, reducing deployment time by 40\%.}
  \resumeItem{Integrated enterprise APIs and applied \textbf{API management} best practices to ensure secure and scalable GIS data services.}
  \resumeItem{Applied \textbf{FME} tools for geospatial data transformation and ETL workflows, improving data consistency across systems.}
  \resumeItem{Resolved complex system and database issues through root cause analysis, improving system reliability by 15\%.}
  \resumeItem{\textit{Environment: C\#, .NET Core, Oracle SQL, PL\_SQL, Hexagon Intergraph (G/Net Viewer), Windows Server, Agile, Jira, Azure DevOps, GitHub Actions, FME.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed and maintained \textbf{.NET Framework} services using \textbf{C\#}, supporting GIS data workflows for utility applications.}
  \resumeItem{Optimized \textbf{Oracle SQL} queries and implemented \textbf{PL\_SQL} tuning, improving data processing speed by 20\%.}
  \resumeItem{Integrated \textbf{Hexagon Intergraph G/Technology} components into enterprise systems, enhancing spatial data management capabilities.}
  \resumeItem{Managed \textbf{Windows Server} based deployments and troubleshooting, ensuring stable GIS application performance.}
  \resumeItem{Collaborated in Agile teams using \textbf{Jira}, improving sprint planning and delivery efficiency.}
  \resumeItem{Implemented API integrations and data synchronization between GIS and business systems, reducing data discrepancies by 25\%.}
  \resumeItem{Supported CI/CD processes using \textbf{Jenkins} and \textbf{Azure DevOps}, automating build and release cycles.}
  \resumeItem{Applied \textbf{ESRI ArcGIS} tools for geospatial data analysis and transformation, complementing core GIS solutions.}
  \resumeItem{Resolved performance bottlenecks in database and application layers, improving overall system throughput.}
  \resumeItem{\textit{Environment: C\#, .NET Framework, Oracle SQL, PL\_SQL, Hexagon Intergraph (G/Technology), Windows Server, Agile, Jira, Jenkins, Azure DevOps, ESRI ArcGIS.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{C\#} and \textbf{.NET Framework}, supporting internal GIS and asset management tools.}
  \resumeItem{Optimized \textbf{Oracle SQL} queries and improved \textbf{PL\_SQL} stored procedures, enhancing data access performance.}
  \resumeItem{Integrated GIS components with enterprise applications, improving spatial data accuracy and reporting.}
  \resumeItem{Maintained \textbf{Windows Server} environments and supported deployment activities for GIS-related applications.}
  \resumeItem{Collaborated in Agile teams using \textbf{Jira}, delivering incremental improvements aligned with business needs.}
  \resumeItem{Developed API endpoints and integration layers, enabling seamless data flow between GIS and other enterprise systems.}
  \resumeItem{Implemented scheduled batch jobs and data synchronization processes, improving data freshness and reliability.}
  \resumeItem{Supported CI pipelines using \textbf{Jenkins} and containerized development environments with \textbf{Docker}.}
  \resumeItem{Performed root cause analysis and resolved performance issues in application and database layers.}
  \resumeItem{\textit{Environment: C\#, .NET Framework, Oracle SQL, PL\_SQL, Windows Server, Agile, Jira, Jenkins, Docker.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}