\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small#2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Deliver over \textbf{8+ years} of experience architecting and developing scalable web applications with a focus on \textbf{.NET Core} and \textbf{C\#}, ensuring robust backend solutions.}
  \resumeItem{Expertise in designing and maintaining RESTful APIs, optimizing database interactions with \textbf{SQL Server} and \textbf{PostgreSQL}, and integrating front-end components using \textbf{JavaScript} frameworks.}
  \resumeItem{Collaborate effectively with cross-functional teams including front-end developers and UX designers to deliver seamless user experiences and high-quality software products.}
  \resumeItem{Proficient in version control using \textbf{Git} and implementing CI/CD pipelines to automate deployments and maintain code quality in agile environments.}
  \resumeItem{Experienced with cloud platforms such as \textbf{Azure} and \textbf{AWS}, leveraging cloud services for scalable and secure application deployments.}
  \resumeItem{Committed to writing clean, maintainable, and well-documented code while staying current with emerging \textbf{.NET Core} technologies and best practices.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & \textbf{C\#}, \textbf{.NET Core} (ASP.NET Core Web API), JavaScript, TypeScript, SQL \\
\textbf{Databases:} & SQL Server, PostgreSQL, MySQL \\
\textbf{Frontend Technologies:} & HTML5, CSS3, JavaScript, React, Angular \\
\textbf{API \& Integration:} & RESTful APIs, OpenAPI/Swagger, OAuth2/OIDC, JWT \\
\textbf{Cloud \& DevOps:} & Azure, AWS, Docker, Kubernetes, CI/CD (GitHub Actions, Azure DevOps) \\
\textbf{Version Control \& Tools:} & Git, Jenkins, SonarQube, Snyk \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Java Developer}{USA}
\resumeItemListStart
  \resumeItem{Designed and developed backend services using \textbf{C\#} with \textbf{ASP.NET Core Web API}, improving system modularity and maintainability.}
  \resumeItem{Implemented and optimized RESTful APIs conforming to \textbf{OpenAPI} standards, enhancing integration consistency across platforms.}
  \resumeItem{Collaborated with front-end teams to integrate user-facing elements using \textbf{React} and \textbf{Angular}, improving application responsiveness.}
  \resumeItem{Conducted code reviews and enforced coding standards to ensure clean, maintainable, and well-documented \textbf{.NET Core} codebases.}
  \resumeItem{Troubleshot complex technical issues in production systems, reducing incident resolution time by 30\%.}
  \resumeItem{Automated CI/CD pipelines using \textbf{GitHub Actions} and \textbf{Jenkins}, improving deployment frequency and reliability.}
  \resumeItem{Leveraged \textbf{Azure} cloud services for scalable application hosting and secure data storage, enhancing system availability.}
  \resumeItem{Implemented caching strategies using \textbf{Redis} to reduce backend latency by 25\% for high-traffic endpoints.}
  \resumeItem{Enhanced security by integrating \textbf{OAuth2/OIDC} and \textbf{JWT} authentication mechanisms in backend services.}
  \resumeItem{Containerized microservices with \textbf{Docker} and orchestrated deployments using \textbf{Kubernetes}, enabling efficient scaling.}
  \resumeItem{Monitored application performance and health using \textbf{OpenTelemetry} and \textbf{CloudWatch}, proactively identifying bottlenecks.}
  \resumeItem{Worked in Agile teams to deliver iterative product enhancements aligned with business priorities and customer needs.}
  \resumeItem{\textit{Environment: C\#, .NET Core, ASP.NET Core Web API, REST, OpenAPI, OAuth2/OIDC, JWT, React, Angular, Azure, AWS, Docker, Kubernetes, Redis, Git, Jenkins, GitHub Actions, SonarQube, Snyk, OpenTelemetry, CloudWatch.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed scalable backend services using \textbf{C\#} and \textbf{.NET Core}, improving API performance and reliability.}
  \resumeItem{Built and maintained RESTful APIs to support front-end applications and internal integrations, enhancing system interoperability.}
  \resumeItem{Collaborated with front-end developers using \textbf{React} and \textbf{Angular} to deliver seamless user experiences.}
  \resumeItem{Optimized database queries and schema design in \textbf{PostgreSQL} and \textbf{SQL Server}, reducing query latency by 20\%.}
  \resumeItem{Implemented CI/CD pipelines with \textbf{Azure DevOps} and \textbf{GitHub Actions}, accelerating delivery cycles and improving quality.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes} clusters to enhance scalability and fault tolerance.}
  \resumeItem{Integrated cloud services from \textbf{AWS} and \textbf{Azure} to support application hosting, storage, and messaging needs.}
  \resumeItem{Applied security best practices using \textbf{OAuth2}, \textbf{JWT}, and role-based access controls to protect APIs.}
  \resumeItem{Implemented caching solutions using \textbf{Redis} to improve data retrieval times for frequently accessed endpoints.}
  \resumeItem{Participated in Agile ceremonies and collaborated with cross-functional teams to meet sprint goals effectively.}
  \resumeItem{Utilized monitoring tools such as \textbf{CloudWatch} and \textbf{OpenTelemetry} to maintain system health and performance.}
  \resumeItem{Developed automation tools and performance improvements, reducing manual operational overhead by 30\%.}
  \resumeItem{\textit{Environment: C\#, .NET Core, REST, PostgreSQL, SQL Server, React, Angular, Docker, Kubernetes, AWS, Azure, Redis, OAuth2, JWT, Git, Azure DevOps, GitHub Actions, CloudWatch, OpenTelemetry.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Designed and implemented backend services using \textbf{C\#} and \textbf{ASP.NET Core Web API}, supporting high-availability payment workflows.}
  \resumeItem{Developed RESTful APIs with consistent validation and error handling, improving integration stability with partner systems.}
  \resumeItem{Collaborated with front-end teams using \textbf{Angular} and \textbf{React} to deliver user-centric web applications.}
  \resumeItem{Optimized database performance on \textbf{PostgreSQL} and \textbf{MySQL} through query tuning and indexing, boosting throughput by 25\%.}
  \resumeItem{Implemented secure authentication and authorization using \textbf{OAuth2} and \textbf{JWT}, aligning with enterprise security policies.}
  \resumeItem{Containerized microservices with \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling rapid scaling and environment consistency.}
  \resumeItem{Automated build and deployment pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, reducing manual errors and deployment time.}
  \resumeItem{Integrated cloud solutions from \textbf{AWS}, \textbf{Azure}, and \textbf{GCP} for identity management, storage, and messaging services.}
  \resumeItem{Implemented asynchronous processing using message brokers to improve system reliability and throughput.}
  \resumeItem{Participated in code reviews and knowledge sharing sessions to maintain high code quality and team collaboration.}
  \resumeItem{Monitored application health and performance using observability tools to proactively address issues.}
  \resumeItem{Worked within Agile teams to deliver iterative feature enhancements aligned with business objectives.}
  \resumeItem{\textit{Environment: C\#, ASP.NET Core Web API, REST, OAuth2, JWT, Angular, React, PostgreSQL, MySQL, Docker, Kubernetes, Jenkins, Azure DevOps, AWS, Azure, GCP.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend components using \textbf{C\#} and \textbf{.NET Framework/.NET Core}, supporting integration workflows and internal tooling.}
  \resumeItem{Built RESTful APIs and documented endpoints with \textbf{Swagger}, enabling standardized communication across services.}
  \resumeItem{Collaborated with front-end developers using \textbf{Angular} and \textbf{React} to deliver modular UI components.}
  \resumeItem{Improved database efficiency using \textbf{Hibernate/JPA} and query optimization techniques, reducing response times.}
  \resumeItem{Implemented scheduled batch processing using \textbf{Quartz} and \textbf{Spring Scheduling} to automate periodic tasks.}
  \resumeItem{Standardized build processes with \textbf{Maven/Gradle} and automated CI pipelines using \textbf{Jenkins} for consistent releases.}
  \resumeItem{Containerized development and testing environments using \textbf{Docker}, enhancing developer productivity and environment parity.}
  \resumeItem{Supported cloud deployments on \textbf{AWS} (EC2, S3, RDS), improving application scalability and availability.}
  \resumeItem{Enhanced automated testing with \textbf{JUnit} and \textbf{Mockito}, increasing code coverage and release stability.}
  \resumeItem{Participated in Agile ceremonies and contributed to continuous improvement of development processes.}
  \resumeItem{Maintained legacy systems and facilitated migration efforts towards modern \textbf{.NET Core} architectures.}
  \resumeItem{Ensured code quality and security standards compliance through peer reviews and static analysis tools.}
  \resumeItem{\textit{Environment: C\#, .NET Framework, .NET Core, REST, Swagger, Angular, React, Hibernate/JPA, Docker, Jenkins, AWS, Quartz, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}