\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8 years} of professional experience in \textbf{.NET} and \textbf{C\#} development, specializing in both desktop (\textbf{WinForms}) and web applications.}
  \resumeItem{Designed and implemented scalable web services using \textbf{WCF} and \textbf{RESTful APIs}, ensuring robust integration and high performance.}
  \resumeItem{Developed rich UI experiences leveraging \textbf{Blazor} and \textbf{MVC} frameworks, driving enhanced user engagement and maintainability.}
  \resumeItem{Strong expertise in full software development lifecycle with a focus on enterprise-grade \textbf{C\#} and \textbf{VB.NET} applications across multiple platforms.}
  \resumeItem{Proven ability to deliver results in Agile environments, collaborating effectively to meet evolving business needs and technical challenges.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & C\#, VB.NET, .NET Framework, .NET Core, Blazor, ASP.NET MVC, WinForms \\
\textbf{Web Services \& APIs:} & WCF, REST, Web API, JSON, XML \\
\textbf{Frontend Technologies:} & Blazor, MVC, HTML5, CSS3, JavaScript \\
\textbf{Databases \& ORM:} & SQL Server, Entity Framework, ADO.NET \\
\textbf{Development Tools \& Practices:} & Visual Studio, Git, Azure DevOps, Agile/Scrum, Unit Testing \\
\textbf{Cloud \& DevOps:} & Azure App Service, Azure DevOps Pipelines, Docker, Kubernetes \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Java Developer}{USA}
\resumeItemListStart
  \resumeItem{Engineered \textbf{C\#} backend services using \textbf{ASP.NET Core Web API} to support internal integrations, enhancing service orchestration efficiency by 30\%.}
  \resumeItem{Developed and maintained \textbf{RESTful APIs} and \textbf{WCF} services to enable seamless communication across enterprise platforms.}
  \resumeItem{Implemented \textbf{Blazor} components for internal dashboards, improving UI responsiveness and reducing page load times by 25\%.}
  \resumeItem{Led migration of legacy \textbf{WinForms} applications to modern \textbf{Blazor} web apps, increasing maintainability and user satisfaction.}
  \resumeItem{Collaborated in Agile teams to deliver iterative enhancements, ensuring alignment with business requirements and technical standards.}
  \resumeItem{Optimized data access layers using \textbf{Entity Framework} and SQL tuning, reducing query latency by 20\%.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Azure DevOps}, improving deployment frequency and reducing rollback incidents.}
  \resumeItem{Applied unit testing and integration testing practices to \textbf{C\#} codebases, increasing code coverage to over 85\%.}
  \resumeItem{Utilized \textbf{Docker} containers for development and testing environments, streamlining deployment workflows.}
  \resumeItem{Implemented secure authentication and authorization using \textbf{OAuth2} and \textbf{JWT} tokens in web services.}
  \resumeItem{Monitored application performance and reliability using Azure Monitor and logging frameworks, proactively resolving issues.}
  \resumeItem{Contributed to architecture discussions, advocating for \textbf{Blazor} adoption to modernize frontend technology stack.}
  \resumeItem{\textit{Environment: C\#, VB.NET, .NET Core, Blazor, ASP.NET MVC, WCF, REST, SQL Server, Entity Framework, Azure DevOps, Docker, OAuth2, JWT, Agile/Scrum.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and implemented \textbf{C\#} services using \textbf{ASP.NET Core} to support scalable web applications and internal APIs.}
  \resumeItem{Developed \textbf{RESTful} and \textbf{WCF} web services to integrate with partner systems, improving data exchange reliability by 35\%.}
  \resumeItem{Built frontend modules using \textbf{Blazor} and \textbf{MVC} frameworks, enhancing user experience and reducing client-side errors.}
  \resumeItem{Maintained legacy \textbf{WinForms} applications and facilitated incremental migration to web-based UI using \textbf{Blazor}.}
  \resumeItem{Implemented asynchronous messaging patterns and service orchestration to improve throughput and fault tolerance.}
  \resumeItem{Optimized database interactions using \textbf{Entity Framework} and SQL tuning, reducing response times by 15\%.}
  \resumeItem{Automated build and deployment pipelines with \textbf{Azure DevOps} and \textbf{Docker}, increasing release velocity.}
  \resumeItem{Collaborated in cross-functional Agile teams to deliver features aligned with evolving business priorities.}
  \resumeItem{Applied secure coding practices and integrated \textbf{OAuth2} authentication in web services to ensure compliance.}
  \resumeItem{Participated in code reviews and knowledge sharing sessions to raise team proficiency in \textbf{Blazor} and \textbf{.NET} technologies.}
  \resumeItem{Monitored application health and performance, proactively addressing bottlenecks and incidents.}
  \resumeItem{\textit{Environment: C\#, VB.NET, .NET Core, Blazor, ASP.NET MVC, WCF, REST, SQL Server, Entity Framework, Azure DevOps, Docker, OAuth2, Agile/Scrum.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed \textbf{C\#} and \textbf{VB.NET} backend services supporting payment processing and partner integrations.}
  \resumeItem{Built and maintained \textbf{WCF} and \textbf{RESTful} web services to enable secure and scalable data exchange.}
  \resumeItem{Implemented rich UI components using \textbf{Blazor} and \textbf{MVC}, improving maintainability and user interaction.}
  \resumeItem{Maintained and enhanced legacy \textbf{WinForms} applications, ensuring stability and performance.}
  \resumeItem{Optimized database queries and implemented caching strategies, reducing latency by 25\%.}
  \resumeItem{Automated deployment workflows using \textbf{Azure DevOps}, improving release consistency and traceability.}
  \resumeItem{Collaborated with cross-functional teams in Agile environment to deliver quality software on schedule.}
  \resumeItem{Applied unit and integration testing to ensure robustness of \textbf{.NET} applications.}
  \resumeItem{Implemented security features including role-based access control and token-based authentication.}
  \resumeItem{Participated in code reviews and technical discussions to improve code quality and team knowledge.}
  \resumeItem{Monitored application health and performance, addressing issues proactively to minimize downtime.}
  \resumeItem{\textit{Environment: C\#, VB.NET, .NET Framework/Core, Blazor, ASP.NET MVC, WCF, REST, SQL Server, Entity Framework, Azure DevOps, Agile/Scrum.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed desktop applications using \textbf{WinForms} and backend services with \textbf{C\#} and \textbf{.NET Framework}.}
  \resumeItem{Built and maintained \textbf{WCF} and \textbf{REST} web services to support internal tooling and integrations.}
  \resumeItem{Contributed to frontend development using \textbf{ASP.NET MVC} and early \textbf{Blazor} prototypes for internal dashboards.}
  \resumeItem{Optimized database queries and improved data access layers, enhancing application responsiveness.}
  \resumeItem{Automated builds and deployments using \textbf{Jenkins} and \textbf{Docker} containers for consistent environments.}
  \resumeItem{Collaborated in Agile teams to deliver incremental improvements and maintain software quality.}
  \resumeItem{Implemented scheduled background processing using \textbf{Quartz} and \textbf{Spring Scheduling} for batch jobs.}
  \resumeItem{Enhanced application security by integrating authentication and authorization mechanisms.}
  \resumeItem{Performed unit testing and participated in peer code reviews to maintain high code standards.}
  \resumeItem{Supported cloud deployments on \textbf{AWS} for scalable infrastructure and storage solutions.}
  \resumeItem{Monitored application logs and performance metrics to identify and resolve issues promptly.}
  \resumeItem{\textit{Environment: C\#, VB.NET, .NET Framework, WinForms, ASP.NET MVC, WCF, REST, SQL Server, Jenkins, Docker, AWS, Agile.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}