\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Over \textbf{8+ years} of experience architecting and delivering scalable \textbf{.NET} and \textbf{C\#} cloud applications with strong expertise in \textbf{Azure AI} services and AI integration.}
  \resumeItem{Designed and deployed AI-powered solutions leveraging \textbf{Azure OpenAI}, \textbf{Cognitive Services}, and \textbf{Azure Functions}, enabling intelligent features like NLP and semantic search.}
  \resumeItem{Skilled in frontend development using \textbf{Angular} and \textbf{TypeScript}, building responsive UI modules aligned with enterprise workflows and security standards.}
  \resumeItem{Experienced in prompt engineering, model finetuning, and applying \textbf{Microsoft Responsible AI} frameworks to ensure ethical and secure AI deployments.}
  \resumeItem{Proficient in building cloud-native applications with \textbf{Azure App Services}, \textbf{Entra ID}, \textbf{Key Vault}, and implementing robust data pipelines and embedding-based search solutions.}
  \resumeItem{Strong background in SQL Server with additional experience in PostgreSQL, containerization using \textbf{Docker/Kubernetes}, and CI/CD automation with \textbf{Git} and Azure DevOps.}
  \resumeItem{Proven ability to lead cross-functional teams in Agile environments, translating complex business problems into AI-driven, scalable, and secure solutions.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & C\#, .NET (ASP.NET Core Web API), Python, Angular, TypeScript, SQL, PostgreSQL, SQL Server \\
\textbf{Cloud \& AI Services:} & Microsoft Azure (Azure AI, Azure OpenAI, Cognitive Services, Azure Functions, Azure App Services, Entra ID, Key Vault), Docker, Kubernetes \\
\textbf{AI \& Data Engineering:} & Natural Language Processing, Chatbots, Document Intelligence, Semantic Search, Predictive Analytics, Prompt Engineering, Model Finetuning, Vector Stores, Embeddings \\
\textbf{DevOps \& CI/CD:} & Git, Azure DevOps Pipelines, Jenkins, CI/CD best practices, Containerization (Docker, Kubernetes) \\
\textbf{Security \& Identity:} & OAuth2/OIDC, Azure Entra ID, Key Vault, Microsoft Responsible AI frameworks, RBAC, Secure API design \\
\textbf{Design \& Architecture:} & Domain-Driven Design (DDD), Event-Driven Architecture, REST APIs, Microservices, Agile/Scrum \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Architected and developed AI-powered backend services using \textbf{C\#}, \textbf{.NET 6}, and \textbf{Azure AI} services, enhancing natural language processing capabilities.}
  \resumeItem{Integrated \textbf{Azure OpenAI} and \textbf{Cognitive Services} into enterprise workflows via \textbf{Azure Functions} and REST APIs, improving automation and user experience.}
  \resumeItem{Led frontend development with \textbf{Angular 16/17} and \textbf{TypeScript}, delivering scalable UI components aligned with AI-driven features and secure access controls.}
  \resumeItem{Implemented secure authentication and authorization using \textbf{Azure Entra ID} and \textbf{Key Vault}, ensuring compliance with enterprise security policies.}
  \resumeItem{Built embedding-based semantic search and document intelligence pipelines leveraging \textbf{Azure AI} and vector stores, improving data retrieval accuracy by 30\%.}
  \resumeItem{Designed and deployed containerized microservices with \textbf{Docker} and \textbf{Kubernetes (EKS)}, enabling scalable and resilient AI application hosting.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, enforcing quality gates and security scanning with \textbf{SonarQube} and \textbf{Snyk}.}
  \resumeItem{Applied \textbf{Microsoft Responsible AI} frameworks for prompt engineering and model finetuning, ensuring ethical AI usage and compliance.}
  \resumeItem{Optimized API performance by 35\% through efficient data access patterns and caching strategies using \textbf{Redis}.}
  \resumeItem{Collaborated in Agile/Scrum teams to translate business requirements into AI-driven solutions, focusing on scalability, security, and maintainability.}
  \resumeItem{\textit{Environment: C\#, .NET 6, Azure AI, Azure OpenAI, Cognitive Services, Azure Functions, Azure App Services, Entra ID, Key Vault, Docker, Kubernetes (EKS), Jenkins, GitHub Actions, SonarQube, Snyk, Angular 16/17, TypeScript, Redis.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed scalable backend services using \textbf{C\#} and \textbf{ASP.NET Core Web API}, integrating AI capabilities with cloud-native Azure and AWS services.}
  \resumeItem{Implemented REST and gRPC APIs to support AI-powered features including chatbot integrations and predictive analytics workflows.}
  \resumeItem{Built automation tooling and performance-sensitive utilities using \textbf{Python} and \textbf{Go}, enhancing AI model data pipelines and operational efficiency.}
  \resumeItem{Designed and maintained containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes (EKS/ECS)}, ensuring high availability and scalability.}
  \resumeItem{Implemented data embedding and vector search solutions using cloud-native services, improving semantic search relevance by 25\%.}
  \resumeItem{Applied secure identity and access management using \textbf{AWS IAM} and \textbf{Azure Entra ID}, safeguarding sensitive AI data and APIs.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Azure DevOps} and \textbf{GitHub Actions}, improving deployment frequency and reducing errors.}
  \resumeItem{Collaborated in Agile teams to deliver AI-driven features aligned with business goals, ensuring robust performance and security.}
  \resumeItem{Enhanced observability using \textbf{OpenTelemetry} and cloud monitoring tools, enabling proactive issue detection and resolution.}
  \resumeItem{Developed frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, supporting AI-powered user interfaces.}
  \resumeItem{\textit{Environment: C\#, ASP.NET Core, Python, Go, Docker, Kubernetes (EKS/ECS), AWS (IAM, S3, DynamoDB), Azure Entra ID, Azure DevOps, GitHub Actions, Angular, React, TypeScript, OpenTelemetry.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{C\#} and \textbf{ASP.NET Core Web API}, integrating AI capabilities for document intelligence and predictive analytics.}
  \resumeItem{Built and maintained REST APIs using \textbf{OpenAPI/Swagger}, ensuring consistent validation, versioning, and error handling for AI-powered features.}
  \resumeItem{Implemented frontend UI modules using \textbf{Angular 8--12} and \textbf{TypeScript}, delivering chatbot and semantic search interfaces.}
  \resumeItem{Designed and optimized data pipelines and embedding-based search using \textbf{PostgreSQL} and \textbf{Redis}, improving query performance by 25\%.}
  \resumeItem{Integrated secure authentication using \textbf{OAuth2/OIDC} and \textbf{JWT}, aligning with enterprise RBAC and compliance requirements.}
  \resumeItem{Containerized microservices with \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling scalable AI application hosting.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing code quality with \textbf{SonarQube}.}
  \resumeItem{Collaborated with cross-functional teams in Agile environments to deliver AI-driven business solutions with focus on scalability and security.}
  \resumeItem{Improved system observability using cloud monitoring and logging tools, enabling faster incident response and resolution.}
  \resumeItem{Enhanced chatbot workflows and natural language processing features using prompt engineering and AI model tuning techniques.}
  \resumeItem{\textit{Environment: C\#, ASP.NET Core, Angular 8--12, TypeScript, PostgreSQL, Redis, Docker, Kubernetes, Jenkins, Azure DevOps, OAuth2/OIDC, JWT, SonarQube.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{C\#} and \textbf{.NET Framework/Core}, supporting integration workflows and internal tooling enhancements.}
  \resumeItem{Built REST APIs and documented endpoints using \textbf{Swagger}, enabling consistent service communication and integration.}
  \resumeItem{Delivered frontend features using \textbf{Angular 5/6/7} and \textbf{TypeScript}, focusing on reusable components and modular UI design.}
  \resumeItem{Implemented scheduled processing and batch jobs using \textbf{Quartz} and \textbf{Spring Scheduling}, improving operational efficiency.}
  \resumeItem{Optimized database performance using \textbf{Hibernate/JPA} and indexing strategies, reducing query latency by 20\%.}
  \resumeItem{Containerized development and testing environments using \textbf{Docker}, streamlining deployment and consistency across teams.}
  \resumeItem{Supported cloud deployments on \textbf{AWS} with focus on secure and scalable infrastructure.}
  \resumeItem{Improved automated testing coverage using \textbf{JUnit} and \textbf{Mockito}, enhancing release stability.}
  \resumeItem{Collaborated in Agile teams to deliver reliable software solutions aligned with business needs and technical standards.}
  \resumeItem{Contributed to internal integration endpoints using \textbf{C\#} and \textbf{.NET Core}, enabling partner workflows and service orchestration.}
  \resumeItem{\textit{Environment: C\#, .NET Framework/Core, Angular 5--7, TypeScript, Docker, AWS (EC2, S3, RDS), Hibernate/JPA, Quartz, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}