\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Deliver over \textbf{8+ years} of expertise designing scalable Java microservices with \textbf{Spring Boot}, API integrations, and event-driven systems using \textbf{Kafka} in cloud environments.}
  \resumeItem{Lead technical teams by mentoring engineers, translating business requirements into robust technical solutions, and driving CI/CD pipelines with quality and performance focus.}
  \resumeItem{Develop and optimize APIs (SOAP \& REST) and manage relational databases such as \textbf{Oracle} and \textbf{PostgreSQL} to build resilient product information management solutions.}
  \resumeItem{Leverage cloud platforms including \textbf{Google Cloud Platform} alongside observability tools like \textbf{Grafana} and \textbf{Newrelic} to monitor and troubleshoot production systems effectively.}
  \resumeItem{Passionate about building maintainable, scalable integrations and fostering collaborative environments to accelerate innovation in product data management.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java (8/11/17/21), Spring Boot (1.5/2.x/3.x), Kotlin, C\# (\textbf{ASP.NET Core Web API}), Go, TypeScript, JavaScript \\
\textbf{API \& Integration:} & REST, SOAP, gRPC, OpenAPI/Swagger, OAuth2/OIDC, JWT, mTLS, Kafka, Google Cloud Pub/Sub \\
\textbf{Databases:} & Oracle, PostgreSQL, MySQL, Aurora, DynamoDB, MongoDB, Redis/ElastiCache \\
\textbf{Cloud Platforms:} & Google Cloud Platform (Pub/Sub, Cloud SQL), AWS (EKS, S3, RDS/Aurora, DynamoDB), Azure (AKS, App Service) \\
\textbf{DevOps \& CI/CD:} & Bamboo, Bitbucket, Jenkins, GitHub Actions, Azure DevOps, Docker, Kubernetes, Helm, Terraform, CloudFormation, SonarQube \\
\textbf{Observability \& Testing:} & Grafana, Newrelic, OpenTelemetry, JUnit 5, Mockito, Testcontainers, WireMock, Pact \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led design and development of scalable \textbf{Java 17/21} microservices with \textbf{Spring Boot 3}, improving modularity and integration across product data platforms.}
  \resumeItem{Developed and integrated \textbf{REST} and \textbf{gRPC} APIs, ensuring seamless cross-platform communication and adherence to OpenAPI standards.}
  \resumeItem{Implemented secure authentication and authorization using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT}, enhancing enterprise compliance.}
  \resumeItem{Managed CI/CD pipelines using \textbf{Jenkins} and \textbf{GitHub Actions}, enforcing code quality with \textbf{SonarQube} and automating releases.}
  \resumeItem{Utilized \textbf{Kafka} for asynchronous event-driven processing, improving system reliability and throughput with retry and dead-letter queue patterns.}
  \resumeItem{Optimized database access and caching strategies using \textbf{Redis} and \textbf{JPA/Hibernate}, reducing latency by 30--40\%.}
  \resumeItem{Monitored system health and performance using \textbf{Grafana} and \textbf{Newrelic}, enabling proactive issue detection and resolution.}
  \resumeItem{Collaborated with stakeholders to translate business needs into technical requirements, providing estimations and managing project timelines effectively.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed on \textbf{Kubernetes (EKS)} using \textbf{Helm}, ensuring scalable and repeatable deployments.}
  \resumeItem{Implemented contract and unit testing using \textbf{JUnit 5} and \textbf{Mockito}, improving code reliability and reducing regressions.}
  \resumeItem{\textit{Environment: Java 17/21, Spring Boot 3, Spring Security, REST, gRPC, Kafka, Jenkins, GitHub Actions, SonarQube, Docker, Kubernetes (EKS), Helm, Redis, JPA/Hibernate, Grafana, Newrelic.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and implemented \textbf{Java 17} and \textbf{Kotlin} microservices using \textbf{Spring Boot}, supporting scalable product data integrations.}
  \resumeItem{Built and maintained \textbf{REST} and \textbf{gRPC} APIs, ensuring consistent versioning, validation, and error handling for external and internal clients.}
  \resumeItem{Developed event-driven solutions with \textbf{Kafka}, increasing throughput and decoupling service dependencies for improved scalability.}
  \resumeItem{Optimized database queries and access patterns for \textbf{Aurora PostgreSQL} and \textbf{DynamoDB}, improving read latency by 20--30\%.}
  \resumeItem{Implemented security best practices using AWS IAM, KMS encryption, and secrets management, securing sensitive product data workflows.}
  \resumeItem{Automated infrastructure provisioning with \textbf{Terraform} and \textbf{CloudFormation}, ensuring consistent and auditable environments.}
  \resumeItem{Containerized services using \textbf{Docker} and deployed on \textbf{EKS/ECS}, following best practices for rolling updates and rollbacks.}
  \resumeItem{Implemented observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling real-time monitoring and alerting.}
  \resumeItem{Built automated unit and integration tests using \textbf{JUnit 5}, \textbf{Mockito}, and contract tests with \textbf{Pact} to prevent regressions.}
  \resumeItem{Delivered frontend modules for internal tools using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, improving user experience and operational efficiency.}
  \resumeItem{\textit{Environment: Java 17, Kotlin, Spring Boot, REST, gRPC, Kafka, AWS (EKS, ECS, Aurora, DynamoDB, IAM, KMS), Docker, Terraform, CloudFormation, OpenTelemetry, Angular, React, JUnit 5, Mockito, Pact.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend microservices using \textbf{Java 8/11} and \textbf{Spring Boot 2.x}, delivering scalable APIs for product data management.}
  \resumeItem{Designed and integrated \textbf{REST} and \textbf{SOAP} APIs, ensuring interoperability across platforms and consistent error handling.}
  \resumeItem{Implemented secure access control using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT}, aligning with enterprise RBAC policies.}
  \resumeItem{Built asynchronous processing pipelines with \textbf{Kafka}, improving system resilience and throughput with retry and dead-letter queue mechanisms.}
  \resumeItem{Optimized database performance on \textbf{PostgreSQL} and \textbf{MySQL} through indexing and query tuning, reducing response times by 25\%.}
  \resumeItem{Developed integration endpoints using \textbf{C\#} and \textbf{ASP.NET Core Web API}, enabling partner and internal orchestration workflows.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes}, facilitating environment-based configuration and scalability.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing code quality via \textbf{SonarQube} scans.}
  \resumeItem{Delivered frontend modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, enhancing user workflows and dashboard capabilities.}
  \resumeItem{Implemented contract and integration testing using \textbf{JUnit 5}, \textbf{Mockito}, and \textbf{Testcontainers}, improving release stability.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, REST, SOAP, Spring Security, Angular, React, TypeScript, Kafka, C\#, ASP.NET Core, PostgreSQL, MySQL, Docker, Kubernetes, Jenkins, Azure DevOps, SonarQube.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8} and \textbf{Spring Boot (1.5/2.0)}, delivering reusable components and scalable APIs.}
  \resumeItem{Built and documented \textbf{REST} and \textbf{SOAP} APIs, ensuring compliance with enterprise integration standards.}
  \resumeItem{Implemented internal service endpoints using \textbf{C\#} with \textbf{.NET Framework / .NET Core} for system orchestration and data exchange.}
  \resumeItem{Delivered UI features using \textbf{Angular 5/6/7} and \textbf{React 16} with \textbf{TypeScript}, improving modularity and reusability.}
  \resumeItem{Implemented scheduled workflows using \textbf{Quartz} and \textbf{Spring Scheduling}, automating periodic data processing tasks.}
  \resumeItem{Optimized database queries and indexing with \textbf{Hibernate/JPA}, improving response times and throughput.}
  \resumeItem{Standardized builds and CI pipelines using \textbf{Maven/Gradle} and \textbf{Jenkins}, enhancing release automation.}
  \resumeItem{Containerized development and test environments using \textbf{Docker}, improving consistency and developer productivity.}
  \resumeItem{Supported cloud deployments on \textbf{AWS (EC2, S3, RDS)}, enabling scalable infrastructure for product services.}
  \resumeItem{Strengthened automated testing using \textbf{JUnit} and \textbf{Mockito}, increasing code coverage and reducing defects.}
  \resumeItem{\textit{Environment: Java 8, Spring Boot, REST, SOAP, C\#, .NET Framework/Core, Angular, React, Hibernate/JPA, Docker, Jenkins, AWS EC2, S3, RDS.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}