\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Leads development and delivery of scalable \textbf{.NET Core} applications with over \textbf{12 years} of experience, emphasizing strong backend architecture and AWS cloud integration.}
  \resumeItem{Expert in building robust APIs using \textbf{SOAP} and \textbf{REST}, with proven ability to manage teams and deliver financial domain solutions.}
  \resumeItem{Skilled in leveraging \textbf{AWS} services to enhance application performance, security, and scalability in enterprise environments.}
  \resumeItem{Demonstrates excellent communication and analytical skills, driving collaboration and innovation in agile teams.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & C\#, \textbf{.NET Core}, VB.NET, Angular, SOAP, REST APIs \\
\textbf{Cloud \& DevOps:} & AWS (Lambda, API Gateway, S3, RDS, DynamoDB, IAM, KMS, CloudWatch), Docker, Kubernetes, Terraform, CloudFormation \\
\textbf{API \& Integration:} & SOAP, REST, API Gateway, OAuth2, JWT, OpenAPI/Swagger \\
\textbf{Frontend:} & Angular (5--17), TypeScript, RxJS, NgRx \\
\textbf{Databases \& Caching:} & SQL Server, PostgreSQL, MySQL, Redis, DynamoDB \\
\textbf{Tools \& Methodologies:} & Agile/Scrum, Jenkins, GitHub Actions, SonarQube, Snyk, Jira, Confluence \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Led development of scalable backend services using \textbf{C\#} and \textbf{.NET Core}, improving system robustness and maintainability by 30\%.}
  \resumeItem{Designed and implemented secure \textbf{SOAP} and \textbf{REST} APIs, enhancing integration capabilities with internal and external financial systems.}
  \resumeItem{Managed AWS infrastructure including \textbf{Lambda}, \textbf{API Gateway}, and \textbf{S3}, resulting in 25\% improved deployment efficiency.}
  \resumeItem{Coordinated a team of developers to deliver high-quality solutions within Agile frameworks, improving sprint delivery success rate by 20\%.}
  \resumeItem{Optimized API performance and security using \textbf{OAuth2}, \textbf{JWT}, and \textbf{IAM}, reducing unauthorized access incidents by 40\%.}
  \resumeItem{Developed frontend modules using \textbf{Angular} and \textbf{TypeScript}, enhancing user experience and reducing load times by 15\%.}
  \resumeItem{Implemented CI/CD pipelines with \textbf{Jenkins} and \textbf{GitHub Actions}, decreasing deployment errors by 35\%.}
  \resumeItem{Utilized \textbf{Redis} caching and database indexing to reduce API response latency by 25\%.}
  \resumeItem{Integrated observability using \textbf{CloudWatch} and \textbf{OpenTelemetry}, improving system monitoring and incident response times.}
  \resumeItem{Applied \textbf{Terraform} for AWS infrastructure provisioning, ensuring consistent and auditable environment setups.}
  \resumeItem{Enhanced financial domain workflows by incorporating domain-specific validations and compliance checks, improving data accuracy by 30\%.}
  \resumeItem{Streamlined service orchestration using \textbf{ASP.NET Core Web API}, enabling seamless communication across microservices.}
  \resumeItem{\textit{Environment: C\#, .NET Core, Angular, AWS (Lambda, API Gateway, S3, RDS, IAM, CloudWatch), SOAP, REST, OAuth2, JWT, Jenkins, GitHub Actions, Terraform, Redis.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed and maintained backend services using \textbf{C\#} and \textbf{.NET Core}, supporting scalable cloud-native applications.}
  \resumeItem{Built and secured \textbf{SOAP} and \textbf{REST} APIs, improving partner integrations and reducing latency by 20\%.}
  \resumeItem{Implemented AWS services including \textbf{API Gateway}, \textbf{Lambda}, and \textbf{DynamoDB}, increasing system scalability and fault tolerance.}
  \resumeItem{Automated infrastructure provisioning with \textbf{Terraform} and \textbf{CloudFormation}, reducing environment setup time by 40\%.}
  \resumeItem{Collaborated with frontend teams using \textbf{Angular} and \textbf{TypeScript} to deliver responsive user interfaces.}
  \resumeItem{Enhanced API security using \textbf{OAuth2} and \textbf{JWT}, decreasing security vulnerabilities by 30\%.}
  \resumeItem{Containerized applications with \textbf{Docker} and orchestrated deployments on \textbf{Kubernetes}, improving release consistency.}
  \resumeItem{Improved system observability with \textbf{CloudWatch} and \textbf{OpenTelemetry}, enabling proactive incident management.}
  \resumeItem{Led code reviews and mentored junior developers, fostering knowledge sharing and improving team productivity.}
  \resumeItem{Optimized database queries and caching strategies using \textbf{Redis}, reducing data retrieval times by 25\%.}
  \resumeItem{Integrated CI/CD pipelines using \textbf{Jenkins}, ensuring automated testing and reliable deployments.}
  \resumeItem{Supported financial domain projects by implementing compliance-driven features and audit logging.}
  \resumeItem{\textit{Environment: C\#, .NET Core, Angular, AWS (API Gateway, Lambda, DynamoDB, CloudWatch), SOAP, REST, OAuth2, JWT, Docker, Kubernetes, Terraform, Jenkins, Redis.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{C\#} and \textbf{ASP.NET Core Web API}, improving service reliability by 30\%.}
  \resumeItem{Designed and maintained \textbf{SOAP} and \textbf{REST} APIs for payment processing, enhancing integration with external partners.}
  \resumeItem{Implemented secure authentication and authorization using \textbf{OAuth2} and \textbf{JWT}, reducing security incidents by 25\%.}
  \resumeItem{Built frontend components using \textbf{Angular} and \textbf{TypeScript}, improving user engagement and reducing bugs by 15\%.}
  \resumeItem{Optimized database performance on \textbf{SQL Server} and \textbf{PostgreSQL} through indexing and query tuning, improving throughput by 20\%.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed on \textbf{Kubernetes}, enhancing scalability and deployment speed.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, reducing deployment time by 35\%.}
  \resumeItem{Integrated AWS services such as \textbf{S3}, \textbf{RDS}, and \textbf{IAM} to support cloud-based financial applications.}
  \resumeItem{Collaborated with cross-functional teams to deliver features aligned with financial regulations and compliance.}
  \resumeItem{Implemented caching strategies using \textbf{Redis} to reduce database load and improve response times by 25\%.}
  \resumeItem{Led code quality initiatives using \textbf{SonarQube} and \textbf{Snyk}, improving code security and maintainability.}
  \resumeItem{Supported asynchronous processing using messaging queues, enhancing system reliability and throughput.}
  \resumeItem{\textit{Environment: C\#, ASP.NET Core, Angular, SQL Server, PostgreSQL, AWS (S3, RDS, IAM), Docker, Kubernetes, Jenkins, Azure DevOps, OAuth2, JWT, Redis, SOAP, REST.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{C\#} and \textbf{.NET Framework/Core}, supporting integration workflows and internal tools.}
  \resumeItem{Built and maintained \textbf{SOAP} and \textbf{REST} APIs, improving communication between distributed systems by 20\%.}
  \resumeItem{Implemented frontend features using \textbf{Angular} and \textbf{TypeScript}, enhancing usability and reducing UI defects by 15\%.}
  \resumeItem{Optimized database queries and indexing using \textbf{SQL Server} and \textbf{Hibernate/JPA}, improving data access speed by 25\%.}
  \resumeItem{Containerized development environments with \textbf{Docker}, streamlining testing and deployment processes.}
  \resumeItem{Supported AWS deployments using \textbf{EC2}, \textbf{S3}, and \textbf{RDS}, improving application availability.}
  \resumeItem{Automated builds and deployments using \textbf{Jenkins}, reducing manual errors and accelerating release cycles.}
  \resumeItem{Collaborated with teams to implement scheduled batch jobs using \textbf{Quartz} and \textbf{Spring Scheduling} for periodic tasks.}
  \resumeItem{Enhanced application security by integrating authentication and authorization mechanisms in line with enterprise standards.}
  \resumeItem{Improved SOAP service reliability through refactoring and enhanced error handling, reducing downtime by 15\%.}
  \resumeItem{Contributed to Agile ceremonies and sprint planning, supporting continuous delivery and team collaboration.}
  \resumeItem{Managed source control and versioning using \textbf{CVS} and \textbf{Git}, ensuring codebase integrity.}
  \resumeItem{\textit{Environment: C\#, .NET Framework/Core, Angular, SQL Server, SOAP, REST, AWS (EC2, S3, RDS), Docker, Jenkins, Quartz, Hibernate/JPA.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}