\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Kafka Tester\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8+ years} of expertise in Kafka-based data streaming, message validation, and API testing within enterprise environments.}
  \resumeItem{Specialized in verifying data integrity across Kafka topics, including serialization/deserialization using \textbf{JSON} and \textbf{Avro} formats, ensuring robust message flows.}
  \resumeItem{Proficient in designing and executing automated and manual test plans for Kafka clients, APIs, and database queries using \textbf{Postman}, \textbf{Swagger}, \textbf{SQL}, \textbf{Oracle}, and \textbf{MongoDB}.}
  \resumeItem{Experienced in Agile delivery with continuous integration pipelines and test automation using \textbf{Cucumber} and \textbf{Karate}, enhancing release quality and velocity.}
  \resumeItem{Skilled in troubleshooting Kafka client configurations, securing Kafka clusters, and collaborating with cross-functional teams to support data streaming initiatives.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Messaging \& Streaming:} & Kafka (topics, partitions, producers, consumers, security), Message testing (JSON, Avro), Kafka client troubleshooting \\
\textbf{Databases:} & SQL, Oracle, MongoDB, Data validation and query writing \\
\textbf{API Testing \& Tools:} & Postman, Swagger (API design and documentation), Git, API automation (Cucumber, Karate) \\
\textbf{Testing \& Automation:} & Continuous integration, Automated testing frameworks, Manual testing, X-ray, Jira, Confluence \\
\textbf{Methodologies:} & Agile ceremonies, Scrum, Test plan and scenario design, Performance and error handling validation \\
\textbf{Version Control \& Collaboration:} & Git, Jira, Confluence, Agile tools \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Senior Kafka Tester}{USA}
\resumeItemListStart
  \resumeItem{Designed and executed comprehensive test plans for Kafka streaming services, validating message integrity and serialization using \textbf{JSON} and \textbf{Avro} formats.}
  \resumeItem{Developed and maintained automated test scripts using \textbf{Cucumber} and \textbf{Karate}, improving test coverage and reducing manual validation efforts by 40\%.}
  \resumeItem{Configured and troubleshot Kafka client applications, resolving connectivity and security issues to ensure seamless data streaming across banking units.}
  \resumeItem{Authored SQL queries for \textbf{Oracle} and \textbf{MongoDB} databases to verify data accuracy against Kafka messages, supporting data validation and mapping logic.}
  \resumeItem{Collaborated with cross-functional Agile teams, participating in ceremonies and utilizing \textbf{Jira}, \textbf{Confluence}, and \textbf{X-ray} to track testing progress and defects.}
  \resumeItem{Executed API testing using \textbf{Postman} and \textbf{Swagger}, validating JSON responses, response codes, and error handling for microservices interacting with Kafka.}
  \resumeItem{Improved continuous integration pipelines by integrating automated Kafka message tests, accelerating feedback cycles and release readiness.}
  \resumeItem{\textit{Environment: Kafka, JSON, Avro, Oracle, MongoDB, Postman, Swagger, Cucumber, Karate, Git, Jira, Confluence, X-ray, Agile.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Kafka Integration Tester}{USA}
\resumeItemListStart
  \resumeItem{Implemented message testing strategies for Kafka topics, ensuring data serialization and deserialization integrity using \textbf{JSON} and \textbf{Avro} schemas.}
  \resumeItem{Developed and executed API test cases with \textbf{Postman} and \textbf{Swagger}, validating response codes, payloads, and error scenarios for streaming services.}
  \resumeItem{Wrote complex queries against \textbf{Oracle} and \textbf{MongoDB} databases to verify data correctness and consistency with Kafka message flows.}
  \resumeItem{Configured Kafka clients and resolved performance bottlenecks, boosting message throughput and reducing latency by 25\%.}
  \resumeItem{Automated testing workflows using \textbf{Karate} and integrated them into CI pipelines, enhancing regression test efficiency and reliability.}
  \resumeItem{Participated in Agile ceremonies and utilized \textbf{Jira} and \textbf{Confluence} for defect tracking and documentation of test scenarios.}
  \resumeItem{Collaborated with development teams to troubleshoot Kafka security configurations and ensure compliance with enterprise data policies.}
  \resumeItem{\textit{Environment: Kafka, JSON, Avro, Oracle, MongoDB, Postman, Swagger, Karate, Git, Jira, Confluence, Agile.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Tester - Kafka \& API}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Designed and executed manual and automated tests for Kafka message flows, validating data serialization and integrity using \textbf{JSON} and \textbf{Avro}.}
  \resumeItem{Developed API test cases using \textbf{Postman} and \textbf{Swagger}, verifying response correctness, performance, and error handling for microservices.}
  \resumeItem{Authored SQL queries for \textbf{Oracle} and \textbf{MongoDB} to validate data mapping and consistency with Kafka streaming outputs.}
  \resumeItem{Troubleshot Kafka client configuration issues, improving message reliability and reducing failure rates by 30\%.}
  \resumeItem{Integrated automated tests into CI pipelines using \textbf{Cucumber}, enhancing test repeatability and reducing manual effort.}
  \resumeItem{Participated actively in Agile ceremonies, managing test cases and defects using \textbf{Jira}, \textbf{Confluence}, and \textbf{X-ray}.}
  \resumeItem{Collaborated with developers to enhance Kafka security and data streaming capabilities aligned with enterprise standards.}
  \resumeItem{\textit{Environment: Kafka, JSON, Avro, Oracle, MongoDB, Postman, Swagger, Cucumber, Git, Jira, Confluence, Agile.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{QA Engineer - Messaging \& API}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Executed test scenarios for Kafka messaging systems, validating message processing and data serialization using \textbf{JSON} formats.}
  \resumeItem{Performed API testing using \textbf{Postman} and \textbf{Swagger}, ensuring accurate response codes and payload validation.}
  \resumeItem{Wrote and executed SQL queries against \textbf{Oracle} databases to verify data consistency with Kafka messages.}
  \resumeItem{Supported Kafka client troubleshooting and configuration, improving message delivery success rates by 20\%.}
  \resumeItem{Developed manual and automated test cases, contributing to continuous integration efforts and improving release quality.}
  \resumeItem{Collaborated with Agile teams, using \textbf{Jira} and \textbf{Confluence} to document test cases and track defects effectively.}
  \resumeItem{Validated message security configurations and compliance with organizational data streaming policies.}
  \resumeItem{\textit{Environment: Kafka, JSON, Oracle, Postman, Swagger, Jira, Confluence, Agile.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}