\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8+ years} of software development experience specializing in backend systems, API design, and scalable AI-driven platforms.}
  \resumeItem{Designed and implemented Generative AI solutions leveraging \textbf{RAG} techniques with strong proficiency in \textbf{Python}, \textbf{FastAPI}, and cloud platforms (\textbf{AWS}, \textbf{Azure}, \textbf{GCP}).}
  \resumeItem{Expert in architecting distributed applications with focus on scalable APIs, secure cloud deployments, and integration of AI models into enterprise workflows.}
  \resumeItem{Skilled in vector databases, embedding models, and retrieval pipelines, enabling efficient data ingestion and preprocessing for large knowledge bases.}
  \resumeItem{Experienced in containerization (\textbf{Docker}), orchestration (\textbf{Kubernetes}), and CI/CD pipelines to ensure robust and repeatable deployments.}
  \resumeItem{Strong communicator with proven ability to collaborate across teams and deliver high-quality AI and backend solutions in fast-paced environments.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Programming Languages:} & Python, Java (8/11/17/21), Kotlin, Go, C\# \\
\textbf{Backend Frameworks \& APIs:} & FastAPI, Spring Boot (1.5/2.x/3.x), ASP.NET Core Web API, REST, gRPC, OpenAPI/Swagger \\
\textbf{Generative AI \& Data:} & RAG, Embeddings, Vector Databases, LLM Fine-tuning, Prompt Engineering \\
\textbf{Cloud Platforms:} & AWS (EKS, ECS/Fargate, Lambda, API Gateway, S3, RDS/Aurora, DynamoDB, IAM, KMS, Secrets Manager, CloudWatch), Azure (AKS, App Service, Azure AD, Key Vault, Azure Monitor), GCP (GKE, Cloud Storage, Pub/Sub, Cloud Logging/Monitoring) \\
\textbf{Containerization \& Orchestration:} & Docker, Kubernetes, Helm \\
\textbf{CI/CD \& DevOps:} & Jenkins, GitHub Actions, Azure DevOps Pipelines, Terraform, CloudFormation \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Architected and developed scalable backend services using \textbf{Java 17/21} and \textbf{Spring Boot 3}, improving modularity and API performance by 30\%.}
  \resumeItem{Implemented secure authentication and authorization using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT} for enterprise-grade compliance.}
  \resumeItem{Designed and integrated Generative AI workflows leveraging \textbf{Spring AI} and \textbf{AWS Bedrock} with \textbf{RAG} over enterprise knowledge bases.}
  \resumeItem{Built and optimized REST APIs using \textbf{FastAPI} and \textbf{Spring Boot} for seamless AI model integration and data retrieval pipelines.}
  \resumeItem{Collaborated with cross-functional teams to deploy AI solutions on \textbf{AWS EKS} using \textbf{Docker} and \textbf{Kubernetes}, enhancing scalability and reliability.}
  \resumeItem{Implemented asynchronous event processing using \textbf{Kafka} and \textbf{AWS SQS/SNS}, improving system throughput and fault tolerance.}
  \resumeItem{Reduced backend latency by 25\% through \textbf{Redis} caching and query optimization using \textbf{JPA/Hibernate} tuning.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{GitHub Actions}, enforcing quality and security via \textbf{SonarQube} and \textbf{Snyk}.}
  \resumeItem{Established observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling proactive monitoring and alerting.}
  \resumeItem{\textit{Environment: Java 17/21, Spring Boot 3, Spring Security, Spring AI, AWS Bedrock, FastAPI, REST, Kafka, C\#, .NET 6, AWS (EKS, S3, RDS/Aurora, DynamoDB, SQS/SNS, IAM, KMS, Secrets Manager, CloudWatch), Docker, Kubernetes, Helm, Terraform, Angular 16/17, React, TypeScript, RxJS, NgRx, Redis, Jenkins, GitHub Actions.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Designed and delivered distributed backend services using \textbf{Java 17} and \textbf{Kotlin}, focusing on scalable APIs and cloud-native deployments.}
  \resumeItem{Implemented \textbf{FastAPI}-based microservices to support AI model serving and data ingestion pipelines for large-scale knowledge bases.}
  \resumeItem{Developed event-driven architectures using \textbf{Kafka}, improving system decoupling and throughput by 30\%.}
  \resumeItem{Optimized database access patterns on \textbf{DynamoDB} and \textbf{Aurora PostgreSQL}, reducing query latency by 20\%.}
  \resumeItem{Containerized applications with \textbf{Docker} and deployed on \textbf{AWS EKS/ECS}, enabling scalable and resilient service delivery.}
  \resumeItem{Provisioned infrastructure using \textbf{Terraform} and \textbf{CloudFormation} to ensure consistent and auditable cloud environments.}
  \resumeItem{Implemented observability and monitoring using \textbf{OpenTelemetry} and \textbf{CloudWatch} dashboards for proactive issue detection.}
  \resumeItem{Built automated testing suites with \textbf{JUnit 5}, \textbf{Mockito}, and integration tests using \textbf{Testcontainers} and \textbf{WireMock}.}
  \resumeItem{Applied container orchestration best practices with \textbf{Kubernetes}, improving deployment reliability and scalability.}
  \resumeItem{\textit{Environment: Java 17, Kotlin, FastAPI, REST, gRPC, Kafka, AWS (EKS/ECS, Lambda, API Gateway, DynamoDB, Aurora, S3, SQS/SNS, IAM, KMS, Secrets Manager, CloudWatch), Docker, Kubernetes, Terraform, CloudFormation, OpenTelemetry, Angular, React, TypeScript, JUnit 5, Mockito, Testcontainers, WireMock.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8/11} and \textbf{Spring Boot 2.x}, delivering scalable APIs and reusable modules for enterprise applications.}
  \resumeItem{Built and maintained REST APIs with \textbf{OpenAPI/Swagger}, ensuring consistent validation, versioning, and error handling standards.}
  \resumeItem{Implemented secure authentication and authorization using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT} aligned with RBAC policies.}
  \resumeItem{Integrated Generative AI components using \textbf{Python} and \textbf{FastAPI} to support AI-driven workflows and data retrieval pipelines.}
  \resumeItem{Improved data ingestion and preprocessing using embedding models and vector search techniques, enhancing knowledge base retrieval efficiency.}
  \resumeItem{Developed asynchronous processing workflows using \textbf{Kafka}, improving system reliability and throughput.}
  \resumeItem{Built integration endpoints using \textbf{C\#} with \textbf{ASP.NET Core Web API} for partner and internal orchestration workflows.}
  \resumeItem{Optimized database queries and improved performance by 25\% using \textbf{Hibernate/JPA} tuning and \textbf{Redis} caching.}
  \resumeItem{Containerized services using \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling environment-based configuration and scalability.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, Spring Security, REST, OpenAPI, Python, FastAPI, Angular 8--12, React, TypeScript, RxJS, NgRx, Kafka, C\#, ASP.NET Core, Hibernate/JPA, PostgreSQL/MySQL, Redis, Docker, Kubernetes, Jenkins, Azure DevOps, AWS/Azure/GCP.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8} and \textbf{Spring Boot (1.5/2.0)}, delivering reusable components and clean API layering.}
  \resumeItem{Built and documented REST APIs using \textbf{Swagger}, adhering to standards for consistent integration.}
  \resumeItem{Implemented integration endpoints using \textbf{C\#} with \textbf{.NET Framework / .NET Core}, supporting internal workflows.}
  \resumeItem{Delivered frontend features using \textbf{Angular 5/6/7} with \textbf{TypeScript}, creating reusable components and shared modules.}
  \resumeItem{Built internal dashboard modules using \textbf{React 16} with component-based patterns for admin workflows.}
  \resumeItem{Implemented scheduled processing and batch jobs using \textbf{Quartz} and \textbf{Spring Scheduling} for periodic workflows.}
  \resumeItem{Optimized database performance with query tuning and indexing using \textbf{Hibernate/JPA}.}
  \resumeItem{Standardized builds and CI pipelines using \textbf{Maven/Gradle} and \textbf{Jenkins} for improved release stability.}
  \resumeItem{Containerized development and test environments with \textbf{Docker}, supporting cloud deployment on \textbf{AWS EC2/S3/RDS}.}
  \resumeItem{\textit{Environment: Java, Spring Boot, REST, Swagger, C\#, .NET, Angular, React, Hibernate/JPA, Docker, Jenkins, AWS EC2/S3/RDS.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}