\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Kafka Tester\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Leveraged over \textbf{8+ years} of experience validating and testing distributed data streaming systems, specializing in \textbf{Kafka} message integrity and API testing.}
  \resumeItem{Expert in designing and executing automated and manual test plans for Kafka topics, producers, consumers, and message serialization formats including \textbf{JSON} and \textbf{Avro}.}
  \resumeItem{Proficient in querying and validating data across \textbf{Oracle} and \textbf{MongoDB} databases to ensure data consistency and integrity in streaming pipelines.}
  \resumeItem{Skilled in continuous integration and automated testing frameworks such as \textbf{Cucumber} and \textbf{Karate}, with strong command over \textbf{Postman}, \textbf{Git}, and \textbf{Jira/Confluence} for Agile delivery.}
  \resumeItem{Experienced in API testing and validation using \textbf{Swagger} and \textbf{Postman}, ensuring robust response handling, performance, and error management.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Messaging \& Streaming:} & Kafka, Kafka client configuration, message testing (JSON, Avro), data serialization/deserialization, troubleshooting Kafka issues \\
\textbf{Databases:} & Oracle, MongoDB, SQL, query writing, data validation \\
\textbf{Testing \& Automation:} & Continuous integration, automated testing (Cucumber, Karate), manual testing, API testing, Postman, Swagger, JSON validation \\
\textbf{Development \& Tools:} & Git, Jira, Confluence, Agile ceremonies, X-ray, API design and documentation \\
\textbf{API \& Integration:} & REST APIs, OpenAPI/Swagger, response code validation, error handling, performance testing \\
\textbf{Others:} & Agile methodologies, message processing, test plan design and execution \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Kafka Tester}{USA}
\resumeItemListStart
  \resumeItem{Designed and executed comprehensive test plans for \textbf{Kafka} topics, partitions, producers, and consumers, improving message reliability by 30\%.}
  \resumeItem{Validated data integrity and serialization formats including \textbf{JSON} and \textbf{Avro} across streaming pipelines, reducing data errors by 25\%.}
  \resumeItem{Developed and executed automated test cases using \textbf{Cucumber} and \textbf{Karate}, increasing test coverage and reducing manual testing effort by 40\%.}
  \resumeItem{Queried and verified data consistency in \textbf{Oracle} and \textbf{MongoDB} databases based on mapping logic, ensuring accurate data flow in Kafka streams.}
  \resumeItem{Configured and troubleshot \textbf{Kafka} clients and brokers, resolving connectivity and security issues to maintain stable data streaming.}
  \resumeItem{Performed API testing using \textbf{Postman} and \textbf{Swagger}, validating JSON responses, error codes, and performance metrics.}
  \resumeItem{Collaborated in Agile ceremonies, utilizing \textbf{Jira}, \textbf{Confluence}, and \textbf{X-ray} to track defects and document test cases effectively.}
  \resumeItem{\textit{Environment: Kafka, Oracle, MongoDB, JSON, Avro, Cucumber, Karate, Postman, Swagger, Git, Jira, Confluence, Agile, X-ray.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{QA Engineer - Kafka Streaming}{USA}
\resumeItemListStart
  \resumeItem{Executed message testing for \textbf{Kafka} streams, validating producer and consumer behavior with \textbf{JSON} and \textbf{Avro} serialization formats.}
  \resumeItem{Developed automated test scripts for continuous integration pipelines using \textbf{Karate}, improving regression testing efficiency by 35\%.}
  \resumeItem{Validated data integrity and consistency by writing complex queries in \textbf{Oracle} and \textbf{MongoDB}, supporting accurate streaming data verification.}
  \resumeItem{Configured and troubleshot \textbf{Kafka} client issues, enhancing streaming reliability and reducing downtime during peak loads.}
  \resumeItem{Performed API testing and validation using \textbf{Postman} and \textbf{Swagger}, ensuring robust error handling and response correctness.}
  \resumeItem{Participated in Agile ceremonies and defect management using \textbf{Jira} and \textbf{Confluence}, maintaining clear communication and documentation.}
  \resumeItem{Collaborated with development teams to enhance Kafka security configurations and message processing workflows.}
  \resumeItem{\textit{Environment: Kafka, Oracle, MongoDB, JSON, Avro, Karate, Postman, Swagger, Git, Jira, Confluence, Agile.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software QA Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Designed and executed manual and automated test cases for \textbf{Kafka} message streaming, improving message validation accuracy by 20\%.}
  \resumeItem{Validated data serialization and deserialization processes using \textbf{JSON} and \textbf{Avro} formats, ensuring message integrity across services.}
  \resumeItem{Wrote SQL queries and performed data validation on \textbf{Oracle} and \textbf{MongoDB} databases to verify streaming data correctness.}
  \resumeItem{Used \textbf{Postman} and \textbf{Swagger} to test APIs, validating response codes, payloads, and error handling scenarios.}
  \resumeItem{Configured \textbf{Kafka} clients and monitored message flows to identify and resolve streaming issues promptly.}
  \resumeItem{Collaborated in Agile teams using \textbf{Jira} and \textbf{Confluence}, contributing to sprint planning and defect tracking.}
  \resumeItem{Implemented continuous integration testing using \textbf{Cucumber}, reducing manual test cycles by 30\%.}
  \resumeItem{\textit{Environment: Kafka, Oracle, MongoDB, JSON, Avro, Cucumber, Postman, Swagger, Git, Jira, Confluence, Agile.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{QA Analyst}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed and executed test plans for message streaming using \textbf{Kafka}, validating data flow and message processing accuracy.}
  \resumeItem{Performed manual and automated API testing with \textbf{Postman} and \textbf{Swagger}, ensuring compliance with response and error standards.}
  \resumeItem{Queried \textbf{Oracle} and \textbf{MongoDB} databases to verify data integrity and consistency for streaming services.}
  \resumeItem{Assisted in troubleshooting \textbf{Kafka} client configuration and security issues, improving system stability.}
  \resumeItem{Participated in Agile ceremonies, maintaining documentation and defect logs in \textbf{Jira} and \textbf{Confluence}.}
  \resumeItem{Supported continuous integration testing efforts using \textbf{Cucumber}, increasing automation coverage by 25\%.}
  \resumeItem{Validated message serialization and deserialization processes using \textbf{JSON} and \textbf{Avro} formats.}
  \resumeItem{\textit{Environment: Kafka, Oracle, MongoDB, JSON, Avro, Cucumber, Postman, Swagger, Git, Jira, Confluence, Agile.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}