\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8+ years} of software development expertise, specializing in scalable backend systems and Generative AI solutions using \textbf{Python}, \textbf{FastAPI}, and cloud platforms.}
  \resumeItem{Designed and implemented enterprise-grade APIs and AI-driven architectures leveraging \textbf{RAG} frameworks and vector databases to enhance data retrieval and knowledge management.}
  \resumeItem{Experienced in deploying robust AI applications on \textbf{AWS}, \textbf{Azure}, and \textbf{GCP} with containerization and orchestration using \textbf{Docker} and \textbf{Kubernetes}.}
  \resumeItem{Skilled in collaborating with cross-functional teams to integrate AI models into existing workflows, ensuring security, scalability, and performance.}
  \resumeItem{Proficient in LLM fine-tuning, prompt engineering, and CI/CD automation to streamline AI model deployment and monitoring.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Programming \& Frameworks:} & Python, FastAPI, Java (8/11/17/21), Spring Boot (1.5/2.x/3.x), C\# (\textbf{ASP.NET Core Web API}), Go \\
\textbf{Cloud \& Deployment:} & AWS (EKS, ECS/Fargate, Lambda, API Gateway, S3, RDS/Aurora, DynamoDB, IAM, KMS, Secrets Manager, CloudWatch), Azure (AKS, App Service, Azure AD, Key Vault, Azure Monitor), GCP (GKE, Cloud Storage, Pub/Sub, Cloud Logging/Monitoring) \\
\textbf{Generative AI \& Data:} & RAG, Vector Databases, Embeddings, LLM Fine-tuning, Prompt Engineering, Spring AI, AWS Bedrock \\
\textbf{Containerization \& Orchestration:} & Docker, Kubernetes, Helm \\
\textbf{CI/CD \& DevOps:} & Jenkins, GitHub Actions, Azure DevOps Pipelines, Terraform, CloudFormation \\
\textbf{Frontend \& Integration:} & Angular (5--17), React (Hooks), TypeScript, RxJS, NgRx, REST, gRPC, OpenAPI/Swagger, OAuth2/OIDC, JWT \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Architected and developed scalable \textbf{Python} backend services using \textbf{FastAPI} to integrate Generative AI models with enterprise data pipelines.}
  \resumeItem{Designed and implemented \textbf{RAG}-based AI applications leveraging vector databases for enhanced knowledge retrieval and real-time responses.}
  \resumeItem{Built and optimized secure, high-performance APIs using \textbf{FastAPI} and \textbf{REST}, improving integration speed by 35\%.}
  \resumeItem{Collaborated with cross-functional teams to embed AI solutions into existing banking workflows, ensuring compliance with security and performance standards.}
  \resumeItem{Deployed AI-driven microservices on \textbf{AWS EKS} using \textbf{Docker} containers and \textbf{Kubernetes} orchestration for scalable production environments.}
  \resumeItem{Implemented authentication and authorization using \textbf{OAuth2/OIDC} and \textbf{JWT} to secure AI service endpoints.}
  \resumeItem{Enhanced data ingestion and preprocessing pipelines for large-scale knowledge bases, improving query throughput by 40\%.}
  \resumeItem{Conducted performance tuning of AI models and APIs, reducing latency by 25\% through optimized retrieval and caching strategies.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{GitHub Actions}, enabling faster and reliable AI model deployments.}
  \resumeItem{Monitored production systems using \textbf{OpenTelemetry} and \textbf{CloudWatch}, ensuring high availability and prompt incident response.}
  \resumeItem{\textit{Environment: Python, FastAPI, RAG, Vector Databases, AWS (EKS, S3, IAM, KMS, CloudWatch), Docker, Kubernetes, Jenkins, GitHub Actions, OAuth2/OIDC, JWT, OpenTelemetry.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed distributed backend services using \textbf{Java 17} and \textbf{Spring Boot}, focusing on scalable API-first design and microservices architecture.}
  \resumeItem{Implemented \textbf{RAG} frameworks and embedding models to enhance internal AI-driven search and recommendation systems.}
  \resumeItem{Built and maintained REST and gRPC APIs to integrate AI models with data pipelines, improving data accessibility by 30\%.}
  \resumeItem{Designed and optimized data retrieval pipelines with vector databases, reducing query latency by 20\%.}
  \resumeItem{Containerized services using \textbf{Docker} and deployed on \textbf{AWS EKS}, following best practices for cloud-native applications.}
  \resumeItem{Provisioned infrastructure using \textbf{Terraform} and \textbf{CloudFormation} to ensure consistent and auditable cloud deployments.}
  \resumeItem{Implemented observability with \textbf{OpenTelemetry} and \textbf{CloudWatch} dashboards for proactive monitoring of AI services.}
  \resumeItem{Collaborated with DevOps teams to integrate CI/CD pipelines using \textbf{GitHub Actions}, accelerating release cycles.}
  \resumeItem{Conducted prompt engineering and LLM fine-tuning experiments to improve model accuracy and response quality.}
  \resumeItem{Improved security posture by enforcing \textbf{IAM} roles, encryption with \textbf{KMS}, and secrets management using \textbf{Secrets Manager}.}
  \resumeItem{\textit{Environment: Java 17, Spring Boot, RAG, Vector Databases, AWS (EKS, S3, DynamoDB, IAM, KMS, Secrets Manager), Docker, Kubernetes, Terraform, CloudFormation, OpenTelemetry, GitHub Actions.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8/11} and \textbf{Spring Boot 2.x}, delivering scalable APIs aligned with enterprise security standards.}
  \resumeItem{Built RESTful APIs with \textbf{OpenAPI/Swagger}, ensuring consistent validation, versioning, and error handling across services.}
  \resumeItem{Implemented AI integration workflows embedding \textbf{RAG} techniques and vector search to enhance internal knowledge management.}
  \resumeItem{Optimized data retrieval and caching strategies using \textbf{Redis}, reducing response times by 25\%.}
  \resumeItem{Containerized applications using \textbf{Docker} and orchestrated deployments with \textbf{Kubernetes} for consistent multi-environment releases.}
  \resumeItem{Collaborated with cross-functional teams to embed AI-powered features into customer-facing applications, improving user engagement.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, improving deployment frequency and reliability.}
  \resumeItem{Implemented secure authentication and authorization using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT}.}
  \resumeItem{Developed batch automation utilities with \textbf{Go} to streamline data processing workflows.}
  \resumeItem{\textit{Environment: Java 8/11, Spring Boot 2.x, RAG, Redis, Docker, Kubernetes, Jenkins, Azure DevOps, Spring Security, OAuth2/OIDC, JWT, Go.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java 8} and \textbf{Spring Boot (1.5/2.0)}, focusing on modular design and scalable REST APIs.}
  \resumeItem{Built and documented APIs using \textbf{REST} and \textbf{Swagger}, ensuring clear integration contracts for internal teams.}
  \resumeItem{Implemented service endpoints using \textbf{C\#} with \textbf{.NET Framework / .NET Core} for partner integrations and orchestration.}
  \resumeItem{Delivered frontend features using \textbf{Angular 5/6/7} and \textbf{React 16} with \textbf{TypeScript} for admin dashboards and user workflows.}
  \resumeItem{Improved database performance using \textbf{Hibernate/JPA} tuning and indexing strategies on \textbf{Oracle} and \textbf{MySQL}.}
  \resumeItem{Standardized builds and CI pipelines using \textbf{Maven/Gradle} and \textbf{Jenkins} to enhance release stability.}
  \resumeItem{Implemented containerized development environments using \textbf{Docker} to streamline testing and deployment.}
  \resumeItem{Supported cloud deployments on \textbf{AWS EC2} and \textbf{S3}, aligning with enterprise infrastructure standards.}
  \resumeItem{Enhanced automated testing coverage using \textbf{JUnit} and \textbf{Mockito}, improving code quality and reducing defects.}
  \resumeItem{\textit{Environment: Java 8, Spring Boot, REST, Swagger, C\#, .NET Framework/Core, Angular, React, Hibernate/JPA, Docker, Jenkins, AWS EC2/S3, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}