\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Kafka Administrator - Automation Specialist\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Led automation and administration of high-availability \textbf{Apache Kafka} clusters with strong expertise in \textbf{Ansible}, \textbf{Terraform}, and \textbf{GitOps}, reducing manual interventions by 40\%.}
  \resumeItem{Deployed and managed Kafka on \textbf{Kubernetes} (OpenShift) using \textbf{Confluent for Kubernetes (CFK)}, ensuring scalable, secure, and resilient streaming platforms.}
  \resumeItem{Implemented robust monitoring and alerting using \textbf{Prometheus}, \textbf{Grafana}, and \textbf{Confluent Control Center} to maintain optimal cluster health and performance.}
  \resumeItem{Automated security compliance with \textbf{SASL/SSL}, \textbf{RBAC}, \textbf{ACLs}, and certificate management, strengthening data governance and access controls.}
  \resumeItem{Managed Kafka Connectors and \textbf{Schema Registry} deployments, enabling seamless data integration and schema governance across multi-region environments.}
  \resumeItem{Configured disaster recovery with active-passive clusters and multi-region replication using \textbf{Cluster Link}, enhancing system availability and fault tolerance.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Infrastructure \& Automation:} & Kubernetes (OpenShift), Linux, Ansible, Terraform, GitOps (ArgoCD, Jenkins), Shell scripting, Python \\
\textbf{Messaging \& Streaming:} & Apache Kafka, Confluent Platform, Kafka Connect, Schema Registry, Kafka Raft (KRaft) mode, Cluster Link \\
\textbf{Monitoring \& Observability:} & Prometheus, Grafana, JMX, Confluent Control Center \\
\textbf{Security \& Networking:} & TLS/SSL, SASL, Kerberos, RBAC, ACLs, Certificate Management \\
\textbf{Cloud \& DevOps:} & Docker, Helm, Jenkins, CI/CD pipelines, AWS, Azure, GCP (basic familiarity) \\
\textbf{Programming \& Scripting:} & Python, Shell scripting, Java (for Kafka ecosystem understanding) \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Kafka Administrator - Automation Specialist}{USA}
\resumeItemListStart
  \resumeItem{Automated Kafka cluster provisioning and configuration using \textbf{Ansible} and \textbf{Terraform}, reducing deployment time by 50\%.}
  \resumeItem{Deployed and managed \textbf{Confluent for Kubernetes (CFK)} on \textbf{OpenShift}, ensuring seamless Kafka broker scaling and upgrades.}
  \resumeItem{Implemented Kafka security protocols including \textbf{SASL/SSL}, \textbf{RBAC}, and \textbf{ACLs}, enhancing cluster compliance and access control.}
  \resumeItem{Configured and automated Kafka topic partition management and replication settings, improving data availability and throughput.}
  \resumeItem{Monitored cluster health and performance using \textbf{Prometheus}, \textbf{Grafana}, and \textbf{Confluent Control Center}, reducing incident response times by 30\%.}
  \resumeItem{Managed Kafka Connectors and \textbf{Schema Registry} deployments for data integration pipelines, improving data governance and reliability.}
  \resumeItem{Implemented disaster recovery strategies using \textbf{Active-Passive clusters} and \textbf{Cluster Link} for multi-region replication, ensuring business continuity.}
  \resumeItem{\textit{Environment: Apache Kafka, Confluent Platform, Kubernetes (OpenShift), Ansible, Terraform, GitOps, Prometheus, Grafana, SASL/SSL, RBAC, ACLs, Python, Shell scripting.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed automation scripts in \textbf{Python} and \textbf{Shell} to streamline Kafka cluster maintenance and upgrades, reducing manual errors by 35\%.}
  \resumeItem{Provisioned and managed Kafka infrastructure on \textbf{Kubernetes} clusters, improving deployment consistency and scalability.}
  \resumeItem{Implemented Kafka security features including \textbf{TLS encryption} and \textbf{Kerberos} authentication, enhancing data protection.}
  \resumeItem{Monitored Kafka broker health and consumer lag using \textbf{Prometheus} and \textbf{Grafana}, enabling proactive issue resolution.}
  \resumeItem{Automated infrastructure deployment using \textbf{Terraform} and integrated continuous deployment pipelines with \textbf{Jenkins} and \textbf{GitOps} workflows.}
  \resumeItem{Configured Kafka Connectors for \textbf{S3}, \textbf{JDBC}, and \textbf{Snowflake}, improving data pipeline reliability and monitoring.}
  \resumeItem{Supported disaster recovery setups with multi-region replication using \textbf{Cluster Link}, ensuring high availability.}
  \resumeItem{\textit{Environment: Kafka, Kubernetes, Terraform, Ansible, Jenkins, GitOps, Prometheus, Grafana, TLS, Kerberos, Python, Shell scripting.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Managed Kafka clusters and automated topic and partition management using \textbf{Ansible} and custom \textbf{Python} scripts, improving operational efficiency.}
  \resumeItem{Implemented Kafka security with \textbf{SASL/SSL} and \textbf{ACLs}, enforcing strict access controls and compliance.}
  \resumeItem{Deployed and maintained Kafka Connectors and \textbf{Schema Registry}, enabling reliable data governance and integration.}
  \resumeItem{Monitored Kafka performance using \textbf{JMX}, \textbf{Prometheus}, and \textbf{Grafana}, reducing downtime by 25\%.}
  \resumeItem{Automated Kafka broker upgrades and patching using \textbf{Terraform} and \textbf{GitOps} pipelines, ensuring minimal disruption.}
  \resumeItem{Configured disaster recovery with active-passive Kafka clusters, improving fault tolerance and data replication.}
  \resumeItem{Supported containerized deployments using \textbf{Docker} and \textbf{Kubernetes}, enhancing cluster scalability and management.}
  \resumeItem{\textit{Environment: Apache Kafka, Ansible, Terraform, GitOps, Prometheus, Grafana, SASL/SSL, ACLs, Kafka Connect, Schema Registry, Docker, Kubernetes, Python.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Supported Kafka cluster operations and automation using \textbf{Shell scripting} and \textbf{Ansible}, improving deployment repeatability by 30\%.}
  \resumeItem{Implemented Kafka security configurations including \textbf{TLS} and basic \textbf{ACLs}, enhancing data protection.}
  \resumeItem{Monitored Kafka broker metrics using \textbf{JMX} and integrated alerts to reduce incident resolution times.}
  \resumeItem{Assisted in Kafka Connect deployments and basic \textbf{Schema Registry} management for data governance.}
  \resumeItem{Automated Kafka topic creation and partition adjustments to optimize throughput and availability.}
  \resumeItem{Containerized Kafka components using \textbf{Docker} and supported Kubernetes-based deployments for scalability.}
  \resumeItem{Collaborated on infrastructure automation using \textbf{Terraform} and \textbf{Jenkins} pipelines to streamline releases.}
  \resumeItem{\textit{Environment: Kafka, Ansible, Shell scripting, TLS, ACLs, JMX, Kafka Connect, Schema Registry, Docker, Kubernetes, Terraform, Jenkins.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}