\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Software engineer with \textbf{5+ years} focused on \textbf{Python} full-stack development, delivering resilient monoliths and microservices for web applications.}
    \resumeItem{Engineered CI/CD pipelines and automated testing with \textbf{Jenkins} and \textbf{GitHub Actions}, increasing deployment cadence while improving release reliability.}
    \resumeItem{Diagnosed and fixed performance bottlenecks by profiling services and optimizing queries, improving throughput and reducing end-to-end latency for users.}
    \resumeItem{Built RESTful and gRPC services adopting service-oriented patterns to improve scalability, observability and fault isolation across teams.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Scripting:} & Python, Java, JavaScript, TypeScript, SQL, Shell Scripting, Go, C++, Kotlin \\
                \textbf{Frameworks \& Backend:} & \textbf{Spring Boot}, \textbf{Spring Cloud}, \textbf{Node.js}, Express.js, gRPC, RESTful APIs, Flask, Gin \\
                \textbf{Cloud \& DevOps:} & AWS (ECS, EC2, S3, API Gateway, CodePipeline), Docker, Kubernetes, Jenkins, GitHub Actions, Terraform \\
                \textbf{Databases:} & PostgreSQL, Oracle Database, MongoDB, DynamoDB, Redis, Cassandra \\
                \textbf{Testing \& Observability:} & JUnit, Mockito, Postman, Selenium, Grafana, Prometheus, AppDynamics, Splunk \\
                \textbf{Methodologies:} & Microservices Architecture, CI/CD Automation, Service-Oriented Architecture, Agile (Scrum/Kanban), Performance Profiling \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Led development of microservices using \textbf{Java} and \textbf{Spring Boot}, improving system scalability and significantly reducing latency by 30\%.}
        \resumeItem{Implemented \textbf{GraphQL} and optimized APIs on \textbf{AWS API Gateway} to consistently reduce average response times by 35\% under peak traffic.}
        \resumeItem{Engineered CI/CD pipelines with \textbf{Jenkins}, \textbf{Docker}, and \textbf{AWS CodePipeline}, increasing deployment frequency by 50\% and improving release predictability.}
        \resumeItem{Optimized complex \textbf{PostgreSQL} queries and traced JVM hotspots with profilers, improving throughput by 20\% during peak loads.}
        \resumeItem{Migrated monolithic modules to \textbf{microservices} with \textbf{Spring Cloud}, significantly reducing deployment time by 30\% and improving fault isolation.}
        \resumeItem{Built responsive frontends using \textbf{React.js}, integrating backend services to increase user engagement by 40\% and decrease page load time.}
        \resumeItem{Implemented automated testing with \textbf{JUnit} and \textbf{Mockito}, raising test coverage to 98\% and reducing production defects by 45\% across core services.}
        \resumeItem{Architected an Agentic RAG pipeline using \textbf{Python} and \textbf{Redis} embeddings, improving FAQ accuracy by 28\% and substantially reducing support load.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Delivered core banking microservices using \textbf{Java} and \textbf{Spring Boot}, improving transaction throughput and reducing latency by 25\% across account services.}
        \resumeItem{Designed and implemented \textbf{React} frontends with \textbf{Redux}, increasing loan application completion rates by 18\% consistently across modules.}
        \resumeItem{Automated configuration tasks using \textbf{Python} scripts, saving the team 20 hours weekly and reducing manual deployment errors by 35\% consistently.}
        \resumeItem{Built a \textbf{Node.js} middleware handling real-time transactions, improving processing speed by 30\% during peak windows for cash position updates.}
        \resumeItem{Implemented a \textbf{Kafka}-based event-driven system, reliably processing over 10,000 transactions per second for settlement and reporting pipelines.}
        \resumeItem{Created \textbf{Grafana} dashboards with \textbf{Prometheus} metrics, reducing incident detection time by 40\% across payment and ledger services.}
        \resumeItem{Enhanced security frameworks integrating \textbf{OAuth2} and \textbf{JWT}, decreasing authentication incidents by 40\% and improving compliance consistently.}
        \resumeItem{Improved CI/CD by integrating \textbf{SVN} with \textbf{Jenkins}, reducing deployment times by 30\% for all core banking services.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Implemented high-performance supply chain services using \textbf{Java} and \textbf{Spring MVC}, improving data throughput and reducing processing time by 22\% consistently.}
        \resumeItem{Built and maintained \textbf{RESTful} APIs with \textbf{Node.js} and \textbf{Express.js}, enabling third-party integrations and increasing capabilities by 30\% across vendor systems.}
        \resumeItem{Implemented testing strategies using \textbf{JUnit} and \textbf{Postman}, raising reliability to 95\% during nightly and CI runs and decreasing regressions.}
        \resumeItem{Migrated legacy systems to \textbf{AWS}, lowering operational costs by 20\% through automation and monitoring while improving infrastructure reliability.}
        \resumeItem{Optimized \textbf{DynamoDB} schemas and queries, reducing data access latency by 15\% for real-time inventory services under load.}
        \resumeItem{Developed Linux \textbf{Shell} scripts for real-time performance monitoring, reducing detection-to-resolution time by 30\% during peak processing windows.}
        \resumeItem{Streamlined CI/CD using \textbf{GitHub Actions}, increasing deployment speed by 40\% and improving rollback mechanisms across microservices and APIs.}
        \resumeItem{Facilitated Agile practices and Scrum ceremonies, improving delivery predictability by 25\% through cross-functional coordination.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{InsightPDF} $|$ Python, Streamlit, LangChain, OpenAI API, FAISS, Docker, GitHub Actions}{ }
        \resumeItemListStart
            \resumeItem{Built a RAG pipeline using \textbf{Python}, \textbf{LangChain}, \textbf{FAISS}, and \textbf{OpenAI API} to answer PDF queries with 92\% contextual accuracy.}
            \resumeItem{Deployed containerized service with \textbf{Docker} and \textbf{GitHub Actions}, reducing model inference deployment time by 60\% during peak query loads.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Scalable Deep Learning Image Recognition Application} $|$ AWS, EC2, S3, SQS, IAM, Python}{ }
        \resumeItemListStart
            \resumeItem{Engineered scalable face recognition backend on \textbf{AWS EC2} with \textbf{SQS} decoupling, handling 200 requests under 120 seconds while ensuring reliability.}
            \resumeItem{Implemented \textbf{Redis} caching and profiling, reducing data retrieval times by 60\% for high-concurrency scenarios and consistent latency.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{SecurBank} $|$ Go, Gin, PostgreSQL, JWT, PASETO, Docker, Kubernetes, AWS, Redis, GitHub Actions}{ }
        \resumeItemListStart
            \resumeItem{Developed secure backend with \textbf{Go}, \textbf{Gin}, and \textbf{PostgreSQL}, implementing JWT/PASETO authentication and improving reliability by 30\% for transactional services.}
            \resumeItem{Deployed with \textbf{Docker} and \textbf{Kubernetes} on \textbf{AWS}, added \textbf{Redis} caching and background workers, increasing throughput by 25\% for peak workloads.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}