\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai Rahul K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (602) 492-8754 ~ | ~ \href{mailto:sairahulkan@gmail.com}{sairahulkan@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/rq123/}{\color{blue}\underline{LinkedIn}} ~ | ~
    \href{https://github.com/kanrahuldo}{\color{blue}\underline{GitHub}}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{Practical software engineer specializing in \textbf{C\# (.NET Core)} microservices, UI, and cloud-native deployments for resilient mission-critical systems.}
    \resumeItem{Delivered production systems combining \textbf{Blazor}/desktop UI, messaging, and container orchestration to improve reliability and maintainability.}
    \resumeItem{Experienced designing relational schemas and T-SQL for \textbf{Microsoft SQL Server}, and integrating asynchronous messaging like \textbf{Kafka} and \textbf{Azure Service Bus}.}
    \resumeItem{Skilled in containerization and orchestration with \textbf{Docker} and \textbf{Kubernetes}, plus CI/CD automation using \textbf{GitHub Actions} and \textbf{Azure DevOps}.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming \& Frameworks:} & C\# (.NET Core, ASP.NET Core), Java, Python, JavaScript, TypeScript \\
                \textbf{Backend \& Microservices:} & ASP.NET Core, .NET Core, Spring Boot, gRPC, RESTful Design, Microservices Architecture \\
                \textbf{Frontend \& UI:} & Blazor, WPF, React.js, Angular, JavaScript \\
                \textbf{Databases \& Messaging:} & Microsoft SQL Server (T-SQL), PostgreSQL, Redis, MongoDB, Kafka, RabbitMQ, Azure Service Bus \\
                \textbf{DevOps \& Cloud:} & Docker, Kubernetes, Azure (Azure DevOps), GitHub Actions, CI/CD, Terraform, Jenkins \\
                \textbf{Testing \& Security:} & xUnit, JUnit, Automated Testing, OAuth2, JWT, Secure Coding Practices \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Capgemini}{01/2024 -- Present}
        {Full Stack Developer}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Led design and implemented scalable microservices using \textbf{.NET Core (C\#)}, improving uptime and reducing latency by 25\% across distributed systems.}
        \resumeItem{Built responsive frontend features with \textbf{Blazor} and \textbf{JavaScript}, increasing user engagement by 40\% and reducing render times by 30\% while improving overall performance metrics.}
        \resumeItem{Implemented inter-service messaging using \textbf{Kafka} and \textbf{Azure Service Bus}, enabling reliable event-driven workflows and decreasing failures by 35\% during peak load periods.}
        \resumeItem{Containerized microservices with \textbf{Docker} and orchestrated deployments using \textbf{Kubernetes}, reducing release failures by 40\% and accelerating deployments by 50\% across clusters.}
        \resumeItem{Authored unit tests and integration suites using \textbf{xUnit}, raising automated test coverage to 98\% and reducing regressions in production by 60\%.}
        \resumeItem{Optimized database schemas and T-SQL procedures on \textbf{Microsoft SQL Server}, improving query performance and lowering average response times by 20\%.}
        \resumeItem{Collaborated in agile teams using \textbf{Azure DevOps} to produce documentation and led code reviews, improving delivery predictability and reducing defects by 30\%.}
        \resumeItem{Deployed CI/CD pipelines with \textbf{GitHub Actions} and \textbf{Docker}, enabling automated releases and increasing deployment frequency by 50\% with rollback safety.}
      \resumeItemListEnd

    \resumeSubheading
        {L\&T Technology Services Ltd}{08/2019 -- 06/2022}
        {Software Engineer}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Designed microservices for banking workflows using \textbf{Java} and \textbf{Spring Boot}, improving transaction throughput and reducing latency by 30\% during peak hours.}
        \resumeItem{Implemented real-time middleware with \textbf{Node.js} to manage cash position events for critical operations, increasing processing speed and reducing delays by 30\%.}
        \resumeItem{Built Kafka-based event streaming architecture handling 10,000 TPS, improving resilience and enabling scalable asynchronous processing across services by 40\% during peak periods.}
        \resumeItem{Integrated \textbf{OAuth2} and \textbf{JWT} for secure APIs across services, reducing unauthorized access incidents and improving security posture by 40\% with monitoring.}
        \resumeItem{Developed Grafana dashboards using Prometheus metrics, enhancing observability and decreasing incident MTTR by 35\% and enabling faster root-cause analysis across services.}
        \resumeItem{Improved CI/CD pipelines with \textbf{Jenkins}, reducing deployment time by 30\% and increasing release reliability for multiple teams across geographies.}
        \resumeItem{Piloted a \textbf{.NET Core (C\#)} proof-of-concept to integrate legacy services for compliance, reducing integration complexity and accelerating platform modernization by 25\%.}
        \resumeItem{Automated application configuration using \textbf{Python}, saving 20 hours weekly for operations and improving deployment consistency across environments by 60\%.}
      \resumeItemListEnd

    \resumeSubheading
        {Irusu Technologies Pvt Ltd}{01/2019 -- 07/2019}
        {Software Development Engineer}{Hyderabad, KA, India}
      \resumeItemListStart
        \resumeItem{Implemented supply chain modules using \textbf{Java} and \textbf{Spring MVC}, improving data throughput and reducing processing time by 15\% during monthly peaks.}
        \resumeItem{Built and maintained RESTful APIs with \textbf{Node.js}, enabling third-party integrations and increasing API adoption by 30\% within six months post-launch.}
        \resumeItem{Authored unit and integration tests using \textbf{JUnit} and \textbf{Postman}, raising reliability and reducing defects in production by 95\% quarterly consistently.}
        \resumeItem{Migrated legacy systems to \textbf{AWS}, reducing operational costs by 20\% and improving scalability for peak workloads by 30\% monthly traffic.}
        \resumeItem{Optimized DynamoDB access patterns, reducing latency by 15\% and improving application responsiveness for real-time operations in production environments.}
        \resumeItem{Developed Linux shell scripts for monitoring, decreasing incident detection time by 30\% and improving operational visibility across teams daily operations.}
        \resumeItem{Streamlined CI/CD with \textbf{GitHub Actions}, increasing deployment speed by 40\% and reducing manual release steps for multiple services in production.}
        \resumeItem{Facilitated Agile adoption and Scrum rituals, improving team delivery cadence by 25\% and reducing cycle time for features per sprint.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%% DON'T TOUCH THIS SECTION
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Arizona State University, Tempe, AZ, USA}{08/2022 -- 05/2024}
      {Master of Science in Computer Science}{CGPA: 4.0/4.0}
    \educationSubheading
      {Manipal Institute of Technology, Manipal, KA, India}{07/2015 -- 06/2019}
      {Bachelor of Technology, Computer Engineering}{}
  \resumeSubHeadingListEnd
%%%%%%

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{InsightPDF} | Python, Streamlit, LangChain, OpenAI API, FAISS, Docker, GitHub Actions}{ }
        \resumeItemListStart
            \resumeItem{Built RAG pipeline with \textbf{LangChain} and \textbf{OpenAI API}, enabling contextual retrieval from PDFs and improving answer relevance by 45\% on average.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{DispatcherUI} | .NET Core (C\#), Blazor, Microsoft SQL Server, Docker, Azure Service Bus}{ }
        \resumeItemListStart
            \resumeItem{Designed Blazor front-end and \textbf{.NET Core (C\#)} backend integrating \textbf{Azure Service Bus}, improving dispatch throughput by 35\% for public-safety workflows.}
            \resumeItem{Implemented T-SQL stored procedures on \textbf{Microsoft SQL Server}, optimizing queries and reducing average transaction latency by 25\% during peak traffic.}
        \resumeItemListEnd
        \vspace{-12pt}

      \resumeProjectHeading
          {\textbf{Real-time graph data analytics} | Docker, Kubernetes, Apache Kafka, Neo4j, Minikube}{ }
        \resumeItemListStart
            \resumeItem{Developed Kafka consumers and \textbf{Kubernetes}-deployed services to process graph updates, handling 1000+ concurrent requests and reducing backlog by 50\% during spikes.}
            \resumeItem{Integrated Neo4j for relationship queries, implementing PageRank and BFS algorithms to improve analytics accuracy by 30\% across monthly reports.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\end{document}