\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Leveraged over \textbf{8+ years} of experience designing and developing scalable, maintainable applications using \textbf{Java} and \textbf{Spring Framework} with strong Object-Oriented principles.}
  \resumeItem{Delivered robust backend systems with expertise in \textbf{concurrent programming}, \textbf{Hibernate}, and \textbf{database optimization} for both \textbf{Oracle} and \textbf{MongoDB} environments.}
  \resumeItem{Applied \textbf{Linux} scripting and administration skills to streamline deployments and automate operational tasks in Agile and DevOps settings.}
  \resumeItem{Implemented CI/CD pipelines and source control using \textbf{GitHub}, \textbf{Jenkins}, and \textbf{SonarQube} to enhance code quality and deployment reliability.}
  \resumeItem{Collaborated across full-stack domains, integrating \textbf{Spring Batch}, \textbf{Spring Integration}, and secure coding practices to deliver enterprise-grade solutions.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Programming \& Frameworks:} & Java, Spring Framework (Core, Integration, Batch, JDBC, Hibernate), Object-Oriented Design, Concurrent Programming \\
\textbf{Databases:} & Oracle RDBMS, MongoDB, SQL, JDBC, Hibernate ORM \\
\textbf{Operating Systems \& Scripting:} & Linux, Shell Scripting, Bash \\
\textbf{DevOps \& CI/CD:} & GitHub, Jenkins, SonarQube, JIRA, Secure Coding Toolkits, CI/CD Pipelines \\
\textbf{Cloud \& Containerization:} & Docker, Kubernetes, AWS, Azure, GCP \\
\textbf{Frontend \& Integration:} & REST APIs, Spring Integration, Angular, React, TypeScript \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Designed and developed concurrent \textbf{Java} backend services using \textbf{Spring Framework}, enhancing scalability and modularity for enterprise applications.}
  \resumeItem{Implemented robust batch processing and integration workflows leveraging \textbf{Spring Batch} and \textbf{Spring Integration}, improving data throughput by 35\%.}
  \resumeItem{Optimized database interactions with \textbf{Hibernate} and \textbf{Oracle}, reducing query latency by 30\% through indexing and query tuning.}
  \resumeItem{Automated deployment pipelines using \textbf{Jenkins} and \textbf{GitHub}, enforcing static code analysis with \textbf{SonarQube} to maintain secure coding standards.}
  \resumeItem{Developed RESTful APIs with \textbf{Spring MVC}, ensuring secure access using \textbf{Spring Security} and OAuth2 protocols.}
  \resumeItem{Enhanced system reliability by containerizing applications with \textbf{Docker} and orchestrating deployments on \textbf{Kubernetes}.}
  \resumeItem{Applied \textbf{Linux} scripting for environment setup and operational automation, reducing manual deployment time by 40\%.}
  \resumeItem{Collaborated with frontend teams delivering UI components using \textbf{Angular} and \textbf{React} to support full-stack integration.}
  \resumeItem{Monitored application health and performance using observability tools integrated with cloud platforms, improving incident response times.}
  \resumeItem{\textit{Environment: Java, Spring Framework, Hibernate, Oracle, MongoDB, Linux, Jenkins, GitHub, SonarQube, Docker, Kubernetes, Angular, React.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Engineered backend services using \textbf{Java} and \textbf{Spring Framework}, focusing on concurrency and robust API design for high-availability systems.}
  \resumeItem{Implemented integration solutions using \textbf{Spring Integration} to facilitate seamless communication between distributed services.}
  \resumeItem{Developed and optimized data persistence layers using \textbf{Hibernate} with \textbf{Oracle} and \textbf{MongoDB}, improving data retrieval efficiency by 25\%.}
  \resumeItem{Automated build and deployment processes using \textbf{Jenkins} and \textbf{GitHub}, incorporating static analysis tools to ensure code security.}
  \resumeItem{Utilized \textbf{Linux} shell scripting to automate routine maintenance and deployment tasks, reducing operational overhead.}
  \resumeItem{Designed and delivered RESTful APIs with secure authentication, leveraging \textbf{Spring Security} and OAuth2 standards.}
  \resumeItem{Containerized microservices using \textbf{Docker} and deployed on \textbf{Kubernetes}, improving scalability and fault tolerance.}
  \resumeItem{Collaborated with cross-functional teams to integrate frontend modules developed in \textbf{Angular} and \textbf{React} for end-to-end solutions.}
  \resumeItem{Enhanced batch processing capabilities using \textbf{Spring Batch}, increasing throughput and reliability of data workflows.}
  \resumeItem{\textit{Environment: Java, Spring Framework, Hibernate, Oracle, MongoDB, Linux, Jenkins, GitHub, Docker, Kubernetes, Angular, React.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Built scalable backend services using \textbf{Java} and \textbf{Spring Framework}, following Object-Oriented Design principles for maintainability.}
  \resumeItem{Developed secure REST APIs with \textbf{Spring MVC} and \textbf{Spring Security}, enforcing OAuth2 and JWT authentication mechanisms.}
  \resumeItem{Implemented asynchronous processing and messaging patterns using \textbf{Spring Integration} and \textbf{Kafka}, improving system resilience.}
  \resumeItem{Optimized database performance using \textbf{Hibernate} ORM with \textbf{Oracle} and \textbf{PostgreSQL}, reducing query times by 20\%.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{Azure DevOps}, integrating \textbf{SonarQube} for continuous code quality checks.}
  \resumeItem{Containerized applications using \textbf{Docker} and managed deployments on \textbf{Kubernetes}, enabling consistent environment provisioning.}
  \resumeItem{Utilized \textbf{Linux} scripting to streamline deployment and monitoring tasks, reducing manual intervention by 30\%.}
  \resumeItem{Collaborated with frontend teams delivering modules in \textbf{Angular} and \textbf{React} to support rich user experiences.}
  \resumeItem{Implemented batch processing jobs using \textbf{Spring Batch}, improving data processing efficiency and reliability.}
  \resumeItem{\textit{Environment: Java, Spring Framework, Hibernate, Oracle, PostgreSQL, Linux, Jenkins, Azure DevOps, SonarQube, Docker, Kubernetes, Angular, React.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Framework}, applying Object-Oriented Design for modular and reusable components.}
  \resumeItem{Built RESTful APIs with \textbf{Spring MVC} and documented endpoints using \textbf{Swagger}, improving API discoverability and consistency.}
  \resumeItem{Implemented batch jobs and scheduled tasks using \textbf{Spring Batch} and \textbf{Quartz}, enhancing automated data processing.}
  \resumeItem{Optimized database queries and indexing strategies with \textbf{Hibernate} and \textbf{Oracle}, improving application response times.}
  \resumeItem{Automated builds and deployments using \textbf{Jenkins} and \textbf{Docker}, standardizing development and test environments.}
  \resumeItem{Applied \textbf{Linux} shell scripting to automate operational tasks, reducing manual workload.}
  \resumeItem{Delivered frontend features using \textbf{Angular} and \textbf{React} to support interactive and responsive user interfaces.}
  \resumeItem{Ensured secure coding practices and compliance with enterprise standards through code reviews and static analysis.}
  \resumeItem{Collaborated in Agile teams to deliver iterative improvements and maintain high code quality.}
  \resumeItem{\textit{Environment: Java, Spring Framework, Hibernate, Oracle, Linux, Jenkins, Docker, Angular, React, Swagger.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}