\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Delivered over \textbf{8+ years} of hands-on software development experience specializing in \textbf{Java}, \textbf{JavaScript/TypeScript}, and cloud-native microservices architectures.}
  \resumeItem{Designed and implemented robust RESTful APIs and microservices with deep expertise in \textbf{Service Oriented Architecture (SOA)} and API versioning best practices.}
  \resumeItem{Built scalable web applications using \textbf{Angular}, \textbf{React}, and \textbf{NodeJS}, integrating modern frontend technologies with backend services.}
  \resumeItem{Leveraged \textbf{AWS} cloud services and container orchestration with \textbf{Docker} and \textbf{Kubernetes} to deploy highly available distributed systems.}
  \resumeItem{Applied \textbf{Kafka}-based event streaming and asynchronous processing to improve system resilience and throughput.}
  \resumeItem{Implemented CI/CD pipelines using \textbf{Jenkins}, \textbf{GitHub Actions}, and \textbf{Maven/NPM} to enable continuous integration and automated delivery.}
  \resumeItem{Collaborated effectively in Agile teams, mentoring junior engineers and driving cross-team technical alignment globally.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java, TypeScript, JavaScript, Angular, React, NodeJS, ExpressJS, Spring Boot \\
\textbf{API \& Integration:} & RESTful services, JSON, OpenAPI/Swagger, GraphQL, API versioning, Microservices, SOA \\
\textbf{Cloud \& Containerization:} & AWS (EKS, Lambda, API Gateway, S3, RDS), Azure, Docker, Kubernetes \\
\textbf{Messaging \& Streaming:} & Kafka, AWS SQS/SNS \\
\textbf{Databases:} & PostgreSQL, MySQL, Oracle, MongoDB, NoSQL \\
\textbf{DevOps \& Testing:} & Jenkins, Maven, GitHub, NPM, Jest, Karma, JUnit, Cypress, Agile (SCRUM, Kanban) \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Designed and developed scalable backend services using \textbf{Java} and \textbf{Spring Boot}, improving modularity and API consistency across microservices.}
  \resumeItem{Built and maintained RESTful APIs with \textbf{OpenAPI} specifications, enforcing versioning and validation to reduce integration errors by 30\%.}
  \resumeItem{Implemented secure authentication and authorization using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT}, enhancing compliance with enterprise security standards.}
  \resumeItem{Developed frontend modules using \textbf{Angular} and \textbf{TypeScript}, improving user experience and reducing UI defects by 25\%.}
  \resumeItem{Created dashboard components with \textbf{React} and \textbf{TypeScript}, accelerating internal tool adoption and reducing development time.}
  \resumeItem{Built asynchronous event-driven workflows leveraging \textbf{Kafka} and \textbf{AWS SQS/SNS}, increasing system throughput and reliability.}
  \resumeItem{Containerized applications using \textbf{Docker} and deployed on \textbf{Kubernetes (EKS)} clusters, enabling consistent and scalable releases.}
  \resumeItem{Automated CI/CD pipelines with \textbf{Jenkins} and \textbf{GitHub Actions}, improving deployment frequency and reducing manual errors.}
  \resumeItem{Instrumented observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling proactive monitoring and faster incident resolution.}
  \resumeItem{\textit{Environment: Java, Spring Boot, REST, OpenAPI, Kafka, AWS (EKS, S3, RDS, SQS/SNS), Docker, Kubernetes, Jenkins, GitHub Actions, Angular, React, TypeScript, JUnit.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed distributed backend services using \textbf{Java} and \textbf{Kotlin}, improving API scalability and reliability across cloud environments.}
  \resumeItem{Built and documented RESTful and gRPC APIs with consistent contract enforcement, enhancing cross-team integration quality.}
  \resumeItem{Implemented event-driven architectures using \textbf{Kafka}, increasing asynchronous processing throughput by 40\%.}
  \resumeItem{Designed data access patterns for \textbf{DynamoDB} and \textbf{Aurora PostgreSQL}, optimizing query performance and reducing latency.}
  \resumeItem{Developed frontend operational tools using \textbf{Angular} and \textbf{React} with \textbf{TypeScript}, improving configuration workflows.}
  \resumeItem{Containerized microservices with \textbf{Docker} and deployed on \textbf{EKS/ECS}, enabling scalable and resilient cloud-native applications.}
  \resumeItem{Automated infrastructure provisioning using \textbf{Terraform} and \textbf{CloudFormation}, ensuring repeatable and auditable deployments.}
  \resumeItem{Implemented CI/CD pipelines with \textbf{Jenkins} and \textbf{GitHub Actions}, reducing deployment times and improving code quality.}
  \resumeItem{Built automated tests using \textbf{JUnit}, \textbf{Mockito}, and integration tests with \textbf{Testcontainers}, increasing release stability.}
  \resumeItem{\textit{Environment: Java, Kotlin, REST, Kafka, AWS (EKS, ECS, Lambda, DynamoDB, Aurora), Docker, Kubernetes, Terraform, Jenkins, Angular, React, TypeScript, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend microservices using \textbf{Java} and \textbf{Spring Boot}, delivering reusable APIs with consistent versioning and error handling.}
  \resumeItem{Built secure RESTful APIs documented with \textbf{OpenAPI/Swagger}, improving integration clarity and reducing defects by 20\%.}
  \resumeItem{Implemented authentication and authorization using \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT} to enforce RBAC policies.}
  \resumeItem{Delivered rich frontend experiences using \textbf{Angular} and \textbf{TypeScript} with \textbf{RxJS} and \textbf{NgRx} for state management.}
  \resumeItem{Built modular dashboard components using \textbf{React (Hooks)} and \textbf{TypeScript}, accelerating UI development cycles.}
  \resumeItem{Implemented asynchronous event processing with \textbf{Kafka}, improving system resilience and message reliability.}
  \resumeItem{Built integration endpoints using \textbf{C\#} and \textbf{ASP.NET Core Web API}, enabling partner orchestration workflows.}
  \resumeItem{Optimized database queries and indexing on \textbf{PostgreSQL} and \textbf{MySQL}, improving response times by 25\%.}
  \resumeItem{Containerized services with \textbf{Docker} and deployed on \textbf{Kubernetes}, enabling scalable cloud-native operations.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, improving deployment reliability and speed.}
  \resumeItem{\textit{Environment: Java, Spring Boot, REST, OpenAPI, Angular, React, TypeScript, Kafka, C\#, ASP.NET Core, PostgreSQL, MySQL, Docker, Kubernetes, Jenkins, Azure DevOps.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, delivering reusable components and clean API layers.}
  \resumeItem{Built RESTful APIs and documented endpoints using \textbf{Swagger}, improving API discoverability and integration.}
  \resumeItem{Delivered frontend features using \textbf{Angular} with \textbf{TypeScript}, creating reusable UI components for web applications.}
  \resumeItem{Built internal dashboards using \textbf{React} with component-based design, enhancing admin workflow efficiency.}
  \resumeItem{Implemented scheduled processing using \textbf{Quartz} and Spring Scheduling, automating periodic backend tasks.}
  \resumeItem{Optimized database performance using query tuning and indexing with \textbf{Hibernate/JPA} on \textbf{Oracle}.}
  \resumeItem{Standardized build and CI pipelines using \textbf{Maven} and \textbf{Jenkins}, improving release consistency.}
  \resumeItem{Containerized development and test environments with \textbf{Docker}, enabling reproducible builds.}
  \resumeItem{Supported cloud deployments on \textbf{AWS EC2} and \textbf{S3}, improving infrastructure scalability.}
  \resumeItem{Enhanced automated testing using \textbf{JUnit} and \textbf{Mockito}, increasing release stability.}
  \resumeItem{\textit{Environment: Java, Spring Boot, REST, Swagger, Angular, React, Quartz, Hibernate, Oracle, Maven, Jenkins, Docker, AWS EC2, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}