\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Sai K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont Sr.\ Full Stack Developer\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont +1\,601\,552\,3184 ~ | ~
    \href{mailto:kanrahuldo4@gmail.com}{kanrahuldo4@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/srrrk/}{\color{blue}\underline{LinkedIn}}
    \vspace{-10pt}
\end{center}

% ===== SUMMARY =====
\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
  \resumeItem{Leveraged \textbf{Java}, \textbf{Kafka}, \textbf{AWS}, and \textbf{Angular} to design and deliver scalable, secure, and high-performance enterprise applications.}
  \resumeItem{Specialized in building microservices and event-driven architectures with robust messaging patterns using \textbf{Kafka} and cloud-native deployment on \textbf{AWS}.}
  \resumeItem{Delivered rich frontend experiences using \textbf{Angular} with strong state management and integration with backend APIs for seamless user workflows.}
  \resumeItem{Implemented secure authentication and authorization mechanisms aligned with enterprise standards, ensuring compliance and data protection.}
  \resumeItem{Automated CI/CD pipelines and containerized deployments to improve release velocity and operational stability across cloud environments.}
\resumeItemListEnd
\vspace{-6pt}

% ===== TECHNICAL SKILLS =====
\section{Technical Skills}
\vspace{-14pt}
\begin{table}[h]
\fontsize{9pt}{10pt}\selectfont
\begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
\textbf{Languages \& Frameworks:} & Java, Spring Boot, Angular, TypeScript, Kafka \\
\textbf{Cloud \& DevOps:} & AWS (EKS, ECS, Lambda, S3, RDS, DynamoDB, IAM, Secrets Manager, CloudWatch), Docker, Kubernetes, Helm, Terraform \\
\textbf{Messaging \& Streaming:} & Kafka, AWS SQS, AWS SNS \\
\textbf{Frontend:} & Angular, TypeScript, RxJS, NgRx, Angular Material \\
\textbf{Security \& API:} & Spring Security, OAuth2/OIDC, JWT, REST, OpenAPI/Swagger \\
\textbf{Testing \& Tools:} & JUnit, Mockito, Jenkins, GitHub Actions, SonarQube, Snyk \\
\end{tabular}
\end{table}
\vspace{-15pt}

% ===== PROFESSIONAL EXPERIENCE =====
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{JP Morgan Chase}{09/2024 -- Present}
{Sr.\ Software Developer}{USA}
\resumeItemListStart
  \resumeItem{Designed and developed scalable backend services using \textbf{Java} and \textbf{Spring Boot}, improving modularity and reducing deployment risks.}
  \resumeItem{Implemented asynchronous event-driven workflows using \textbf{Kafka} and \textbf{AWS SQS/SNS}, enhancing system reliability and throughput.}
  \resumeItem{Built secure APIs with \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT} to enforce enterprise-grade authentication and authorization.}
  \resumeItem{Developed dynamic frontend modules using \textbf{Angular}, \textbf{TypeScript}, and \textbf{NgRx}, improving user interaction and state management.}
  \resumeItem{Containerized microservices with \textbf{Docker} and deployed on \textbf{Kubernetes (EKS)} using \textbf{Helm} charts for consistent releases.}
  \resumeItem{Automated CI/CD pipelines leveraging \textbf{Jenkins} and \textbf{GitHub Actions}, incorporating quality gates and security scans.}
  \resumeItem{Enhanced API performance by optimizing \textbf{JPA/Hibernate} queries and implementing \textbf{Redis} caching, reducing latency by 25\%.}
  \resumeItem{Implemented observability using \textbf{OpenTelemetry} and \textbf{CloudWatch}, enabling proactive monitoring and alerting.}
  \resumeItem{Delivered internal dashboard features using \textbf{React} and \textbf{TypeScript} to accelerate UI development cycles.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Kafka, AWS (EKS, S3, RDS, DynamoDB, SQS/SNS, IAM, Secrets Manager, CloudWatch), Docker, Kubernetes, Helm, Jenkins, GitHub Actions, Angular, React, TypeScript, Redis, OpenTelemetry.}}
\resumeItemListEnd

\resumeSubheading
{Amazon}{10/2022 -- 08/2024}
{Software Development Engineer}{USA}
\resumeItemListStart
  \resumeItem{Developed distributed backend services using \textbf{Java} and \textbf{Kotlin}, improving system scalability and API reliability.}
  \resumeItem{Implemented event-driven processing with \textbf{Kafka}, increasing throughput and decoupling service dependencies.}
  \resumeItem{Built and maintained REST and gRPC APIs, ensuring contract consistency and operational stability.}
  \resumeItem{Designed data access patterns for \textbf{DynamoDB} and \textbf{Aurora PostgreSQL}, optimizing query performance and throughput.}
  \resumeItem{Reduced backend latency by 30\% using \textbf{Redis} caching and query optimizations.}
  \resumeItem{Provisioned and managed cloud infrastructure using \textbf{Terraform} and \textbf{CloudFormation} for repeatable deployments.}
  \resumeItem{Containerized services with \textbf{Docker} and orchestrated deployments on \textbf{EKS/ECS}, enabling smooth rollouts.}
  \resumeItem{Developed frontend operational modules using \textbf{Angular} and \textbf{React} with \textbf{TypeScript} for enhanced user workflows.}
  \resumeItem{Implemented observability and monitoring using \textbf{OpenTelemetry} and \textbf{CloudWatch}, improving incident response times.}
  \resumeItem{\textit{Environment: Java, Kotlin, Kafka, AWS (EKS, ECS, Lambda, DynamoDB, Aurora, S3, SQS/SNS, IAM, Secrets Manager, CloudWatch), Docker, Kubernetes, Terraform, Angular, React, TypeScript, OpenTelemetry.}}
\resumeItemListEnd

\resumeSubheading
{Paypal}{08/2019 -- 07/2022}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, delivering scalable and reusable APIs.}
  \resumeItem{Built and secured REST APIs with \textbf{Spring Security}, \textbf{OAuth2/OIDC}, and \textbf{JWT} aligned with enterprise standards.}
  \resumeItem{Implemented asynchronous messaging using \textbf{Kafka}, improving system reliability with retry and dead-letter queue handling.}
  \resumeItem{Delivered frontend modules with \textbf{Angular}, \textbf{TypeScript}, and \textbf{NgRx} for stateful workflow management.}
  \resumeItem{Built dashboard components using \textbf{React} and \textbf{TypeScript} to accelerate modular UI delivery.}
  \resumeItem{Optimized database queries and indexing on \textbf{PostgreSQL} and \textbf{MySQL}, improving throughput and reducing latency.}
  \resumeItem{Implemented caching strategies with \textbf{Redis}, improving response times by 25\%.}
  \resumeItem{Containerized services using \textbf{Docker} and deployed on \textbf{Kubernetes} with environment-based configurations.}
  \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins} and \textbf{Azure DevOps}, enforcing quality and security standards.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Kafka, Angular, React, TypeScript, PostgreSQL, MySQL, Redis, Docker, Kubernetes, Jenkins, Azure DevOps, AWS/Azure/GCP.}}
\resumeItemListEnd

\resumeSubheading
{Electronic Arts}{01/2018 -- 07/2019}
{Software Engineer}{Bengaluru, KA, India}
\resumeItemListStart
  \resumeItem{Developed backend services using \textbf{Java} and \textbf{Spring Boot}, delivering reusable components and clean APIs.}
  \resumeItem{Built RESTful APIs and documented them with \textbf{Swagger} to standardize integrations.}
  \resumeItem{Delivered frontend features using \textbf{Angular} and \textbf{TypeScript}, creating reusable UI components.}
  \resumeItem{Implemented internal dashboards using \textbf{React} for admin workflows and monitoring.}
  \resumeItem{Optimized database performance with query tuning and indexing using \textbf{Hibernate/JPA}.}
  \resumeItem{Standardized build and deployment pipelines using \textbf{Maven}, \textbf{Gradle}, and \textbf{Jenkins}.}
  \resumeItem{Containerized development and testing environments using \textbf{Docker} to improve consistency.}
  \resumeItem{Supported cloud deployments on \textbf{AWS} using EC2, S3, and RDS services.}
  \resumeItem{Enhanced test coverage with \textbf{JUnit} and \textbf{Mockito}, improving release stability.}
  \resumeItem{\textit{Environment: Java, Spring Boot, Angular, React, AWS, Hibernate, Docker, Jenkins, JUnit, Mockito.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}