\documentclass[letterpaper,11pt]{article}

\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{makecell}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\raggedright\fontsize{9.5pt}{10pt}\selectfont\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\educationItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\fontsize{10pt}{14pt}\selectfont #3}, \textbf{\fontsize{10pt}{14pt}\selectfont #1}, \fontsize{10pt}{14pt}\selectfont #4 & \textbf{\fontsize{10pt}{14pt}\selectfont #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-7pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\courses}[1]{
  \item\textit{\scriptsize#1}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{14pt}{12pt}\selectfont \textbf{\MakeUppercase{Rahul Reddy K}}}\\ \vspace{2pt}
    \fontsize{10pt}{12pt}\selectfont (714) 805-6273 ~ | ~ \href{mailto:kanrahuldo1@gmail.com}{kanrahuldo1@gmail.com}~
    \vspace{-8pt}
\end{center}

\section{Summary}
\fontsize{9pt}{10pt}\selectfont
\resumeItemListStart
    \resumeItem{\textbf{Senior Embedded Software Engineer} with over \textbf{8 years} of expertise in architecture, design, and development of embedded systems using \textbf{modern C++ (C++11/14/17)} on Linux and RTOS platforms.} \vspace{-3pt}
    \resumeItem{Skilled in building and maintaining robust CI/CD pipelines with \textbf{GitHub Actions} and \textbf{Makefile}-based build systems to optimize software delivery and reliability.} \vspace{-3pt}
    \resumeItem{Experienced in inter-process communication (IPC), remote procedure calls (RPC), and deep debugging of HDMI protocols including \textbf{CEC, ARC/eARC}, and \textbf{EDID} structures across multi-device display configurations.} \vspace{-3pt}
    \resumeItem{Proficient in Linux system programming, multithreading, memory management, and performance profiling to deliver high-quality embedded software in fast-paced, collaborative environments.} \vspace{-3pt}
    \resumeItem{Demonstrated ability to collaborate effectively with cross-functional teams, product owners, and architects to deliver complex embedded features and sustain Linux-based OS platforms.}
\resumeItemListEnd
\vspace{-6pt}

\section{Technical Skills}
        \vspace{-14pt}
        \begin{table}[h]
            \fontsize{9pt}{10pt}\selectfont
            \begin{tabular}{p{0.3\linewidth} p{0.7\linewidth}}
                \textbf{Programming Languages:} & C, C++, C++11/14/17, Python, Shell Scripting \\
                \textbf{Operating Systems:} & Linux, QNX, VxWorks, FreeRTOS \\
                \textbf{Build \& CI/CD Tools:} & Make, CMake, Git, GitHub Actions, Jenkins \\
                \textbf{Protocols \& IPC:} & HDMI (CEC, ARC/eARC, EDID), I2C, SPI, CAN, J1939, TCP/IP, UDP/IP, IPC, RPC \\
                \textbf{Debugging \& Testing:} & GDB, Valgrind, Google Test, Google Mock, SonarQube, cppCheck, Coverity \\
                \textbf{Frameworks \& Tools:} & Boost, Qt/QML, MQTT, RabbitMQ, Kafka, Splunk \\
            \end{tabular}
        \end{table}
    \vspace{-15pt}

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Toyota Motors}{Oct 2023 -- Present}
        {C++ Embedded / Application Developer}{TX}
      \resumeItemListStart
        \resumeItem{Architected and implemented multi-threaded \textbf{C++17} embedded software modules for automotive infotainment, improving system responsiveness by 25\%.}
        \resumeItem{Developed and optimized IPC mechanisms and \textbf{RPC} frameworks to enable seamless communication between embedded components, reducing latency by 15\%.}
        \resumeItem{Collaborated with cross-functional teams and product owners to deliver new features aligned with HDMI \textbf{CEC} and \textbf{ARC/eARC} specifications across multi-device display setups.}
        \resumeItem{Enhanced build systems using \textbf{Makefiles} and integrated \textbf{GitHub Actions} pipelines, accelerating build and deployment cycles by 30\%.}
        \resumeItem{Analyzed and debugged HDMI bus communication protocols including \textbf{HDCP} and \textbf{EDID} structures to resolve critical interoperability issues.}
        \resumeItem{Maintained and improved Linux-based OS components, delivering bug fixes and performance enhancements to sustain embedded platform stability.}
        \resumeItem{Implemented advanced memory management and profiling techniques to optimize embedded application performance and reduce footprint by 20\%.}
        \resumeItem{Led unit testing and code reviews, ensuring compliance with modern \textbf{C++} standards and embedded software best practices.}
        \resumeItem{Utilized multithreading and synchronization primitives to improve real-time responsiveness of embedded applications.}
        \resumeItem{Collaborated with architects to design hardware abstraction layers for next-generation automotive platforms, improving modularity and scalability.}
      \resumeItemListEnd

    \resumeSubheading
        {Texas Instruments}{Aug 2022 -- Sep 2023}
        {C/C++ Embedded Developer}{Phoenix, AZ}
      \resumeItemListStart
        \resumeItem{Designed and implemented \textbf{C++14} embedded applications with state machines to ensure device operational stability in real-time environments.}
        \resumeItem{Developed \textbf{IPC} and \textbf{RPC} communication modules to support inter-device messaging and control, enhancing system integration.}
        \resumeItem{Built and maintained \textbf{Jenkins} CI/CD pipelines incorporating static analysis tools like \textbf{SonarQube} and automated tests using \textbf{Google Test/Mock}.}
        \resumeItem{Implemented embedded Linux device drivers and protocol handlers for \textbf{I2C}, \textbf{SPI}, and \textbf{CAN/J1939} buses, improving peripheral communication reliability.}
        \resumeItem{Developed QT/QML UI components on \textbf{QNX RTOS} with \textbf{C++} backend, enabling real-time data visualization and user interaction.}
        \resumeItem{Performed in-depth debugging using \textbf{GDB} and core dump analysis to identify and fix critical system faults.}
        \resumeItem{Collaborated with cross-functional teams to deliver features aligned with automotive communication standards and Linux system programming.}
        \resumeItem{Authored technical documentation and UML diagrams to support software design and maintenance activities.}
      \resumeItemListEnd

    \resumeSubheading
        {Texas Instruments}{May 2021 -- Jul 2022}
        {C/C++ Embedded Developer}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Developed embedded \textbf{C++} software modules for electrophysiology data acquisition and processing, ensuring high accuracy and performance.}
        \resumeItem{Implemented AUTOSAR-compliant modules and integrated SPI, GPT, PWM, CAN, and DIO peripherals on microcontroller platforms.}
        \resumeItem{Created modular QT/QML UI components with \textbf{C++} backend using signals and slots for responsive embedded interfaces.}
        \resumeItem{Automated integration testing and reporting using \textbf{Python} and Linux shell scripts, improving test coverage and reliability.}
      \resumeItemListEnd

    \resumeSubheading
        {Panasonic}{Feb 2020 -- Apr 2021}
        {C++ Developer}{Bengaluru, KA}
      \resumeItemListStart
        \resumeItem{Designed and implemented \textbf{C++11} real-time data processing engines on \textbf{VxWorks RTOS}, enhancing print job throughput by 18\%.}
        \resumeItem{Developed low-level device drivers for \textbf{SPI} and \textbf{I2C} communication with printhead controllers and sensors, improving hardware interface stability.}
        \resumeItem{Implemented embedded TCP/IP stack and REST API for remote monitoring and control of printing devices.}
        \resumeItem{Optimized memory usage and system performance through advanced profiling and multithreading techniques on 32-bit embedded platforms.}
        \resumeItem{Built \textbf{QT/QML} based HMI on \textbf{QNX RTOS} with \textbf{C++} backend, improving user experience and interface responsiveness.}
        \resumeItem{Created CI/CD pipelines using \textbf{CMake} and Jenkins for cross-compilation and automated firmware regression testing.}
        \resumeItem{Resolved critical firmware issues using \textbf{GDB} and \textbf{Valgrind}, reducing crash rates by 30\%.}
      \resumeItemListEnd

    \resumeSubheading
        {JSW Steel}{Aug 2017 -- Dec 2019}
        {C++ Embedded Developer}{India}
      \resumeItemListStart
        \resumeItem{Modernized legacy Fortran code to multi-threaded \textbf{C++11} libraries, improving computational efficiency by 40\%.}
        \resumeItem{Developed \textbf{gSOAP C++} web services to support automotive infotainment content playback with in-process caching for faster responses.}
        \resumeItem{Implemented embedded software using \textbf{C/C++} with IPC, \textbf{TCP/IP}, and \textbf{UDP/IP} protocols for robust inter-device communication.}
        \resumeItem{Created Qt/QML HMI components with \textbf{C++} backend using signals/slots and QStateMachine for voice and user interaction.}
        \resumeItem{Developed embedded interfaces for \textbf{I2C}, \textbf{SPI}, and \textbf{CAN} devices; analyzed bus traffic using protocol analyzers to ensure communication integrity.}
        \resumeItem{Authored SQL queries and Python scripts for automated reporting and log monitoring, enhancing operational visibility.}
        \resumeItem{Migrated source control from SVN to \textbf{Git} and integrated Jenkins pipelines to support continuous integration and deployment.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\end{document}